### 2015-03-27 ms.tex
initial commit

%\documentclass[10pt,preprint]{aastex}
%\documentclass[iop]{emulateapj} \font\sevenrm=cmr7  \usepackage{apjfonts}
%preprint2 produces a double-column, single-spaced document:
%\documentclass[preprint2]{aastex}
\documentclass[apj, twocolappendix]{emulateapj}

\usepackage{epsf}
\usepackage{color}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{appendix}
\usepackage[colorlinks,urlcolor=blue,citecolor=blue,linkcolor=blue]{hyperref}
\usepackage{threeparttable}
\usepackage{multirow}
\usepackage{natbib}
\usepackage{etoolbox}

\bibliographystyle{apj}
\citestyle{aa}

% General commands that are good for any agronomy paper.
\input{commands.tex}

\makeatletter
% Patch case where name and year are separated by aysep
\patchcmd{\NAT@citex}
  {\@citea\NAT@hyper@{%
     \NAT@nmfmt{\NAT@nm}%
     \hyper@natlinkbreak{\NAT@aysep\NAT@spacechar}{\@citeb\@extra@b@citeb}%
     \NAT@date}}
  {\@citea\NAT@nmfmt{\NAT@nm}%
   \NAT@aysep\NAT@spacechar\NAT@hyper@{\NAT@date}}{}{}

% Patch case where name and year are separated by opening bracket
\patchcmd{\NAT@citex}
  {\@citea\NAT@hyper@{%
     \NAT@nmfmt{\NAT@nm}%
     \hyper@natlinkbreak{\NAT@spacechar\NAT@@open\if*#1*\else#1\NAT@spacechar\fi}%
       {\@citeb\@extra@b@citeb}%
     \NAT@date}}
  {\@citea\NAT@nmfmt{\NAT@nm}%
   \NAT@spacechar\NAT@@open\if*#1*\else#1\NAT@spacechar\fi\NAT@hyper@{\NAT@date}}

%Commands specific to the this work
\newcommand{\editorial}[1]{\textcolor{red}{#1} }
\DeclareRobustCommand{\ion}[2]{%
\relax\ifmmode
\ifx\testbx\f@series
{\mathbf{#1\,\mathsc{#2}}}\else
{\mathrm{#1\,\mathsc{#2}}}\fi
\else\textup{#1\,{\mdseries\textsc{#2}}}%
\fi}

%-----------------------------------------------------------------------------------------

\shorttitle{Cluster Paper}
\shortauthors{BOADA ET AL.}

%\slugcomment{\it Draft Version \today}
%\slugcomment{\it Submitted for publication in the Astrophysical Journal}
%\slugcomment{Accepted for Publication in the Astrophysical Journal}

\begin{document}

\title{Cluster Paper}

\author{\sc Steven Boada\altaffilmark{1}, 
C.~Papovich\altaffilmark{1},
B.~Salmon\altaffilmark{1}, 
N.~Merhtens\altaffilmark{1},
T.~Li\altaffilmark{1}, 
R.~Wechsler\altaffilmark{2,3},
E.~Rozo\altaffilmark{2,4},
E.~Rykoff\altaffilmark{2,5}}

\altaffiltext{1}{George P.\ and Cynthia Woods Mitchell Institute for
Fundamental Physics and Astronomy, and Department of Physics and Astronomy,
Texas A\&M University, College Station, TX, 77843-4242;
boada@physics.tamu.edu}
\altaffiltext{2}{Kavli Institute for Particle Astrophysics and Cosmology, Department of Physics, Stanford University, Stanford, CA 94305, USA}
\altaffiltext{3}{Department of Particle Physics and Astrophysics, SLAC National Accelerator Laboratory, Menlo Park, CA 94025, USA}
\altaffiltext{4}{Department of Astronomy, University of Chicago, Chicago, IL 60637, USA}
\altaffiltext{5}{E. O. Lawrence Berkeley National Lab, 1 Cyclotron Road, Berkeley, CA 94720, USA}

\begin{abstract}
\noindent
%
We propose to use the Mitchell Spectrograph to provide accurate mass determinations of 10
massive galaxy clusters at z=0.2-0.3 using integral field spectroscopy of the cluster galaxies.
These clusters are selected optically from the SDSS DR8, and are representative of the hundreds
of thousands of clusters expected from DES and LSST. The cluster counts provide a powerful
measure of cosmological parameters independent of supernovae and the CMB. The dominant
sources of error on these cosmological parameters from counts of optical clusters are systematic
uncertainties on the absolute scale between the cluster mass and optical richness, and the intrinsic
scatter in cluster mass at fixed richness. Here we propose a pilot study using these 10 massive
cluster to measure independently the absolute mass scale and scatter in the cluster-optical richness
relation. We will target each galaxy cluster with 4 pointings with the Mitchell Spectrograph,
obtaining integral field spectroscopy for all the (more than 100) cluster galaxies out to radii of
0.5 Mpc and luminosities down to 0.2 L*. The redshifts will allow us to calculate the line-ofsight
velocity dispersion for each cluster, which is an estimator of the total virial mass, and
calculate the precise cluster center. Using the independent cluster mass estimator from the
velocity dispersions will calibrate the mass-optical richness relation, and can lead to a decrease
on the error bars of key cosmological parameters by as much as 50\%.
%
\end{abstract}

\section{INTRODUCTION}

\section{MOCK CATALOGS}
\subsection{Input Simulations}

\section{MOCK OBSERVATIONS}

\section{ANALYSIS}

\subsection{Membership}
It is expected that some of the galaxies detected will be spurious sources not associated with the any given cluster. To reject these interlopers we employ two methods. For clusters with 20 or more $Q=0$ redshifts we use the  ``shifting gapped" method of \cite{Fadda1996}. This procedure combines both the positional and velocity information. Galaxies are binned in $0.4h^{-1}$ Mpc or larger enough bins to contain at least 10 galaxies. The galaxies in each bin are sorted by their line-of-sight velocity (LOSV),
\begin{equation}
	v = \frac{c (z-z_{cl})}{(1+z_{cl})}
\end{equation}
where $z$ is the redshift of the individual galaxy and $z_{cl}$ is the average redshift of the cluster. Any galaxy with a LOSV greater than 1000 \kms of a neighboring galaxy is rejected as an interloper. The procedure repeats until the number of galaxies stabilizes in the bin.

For galaxy clusters with fewer than 20 $Q=0$ redshifts we employ the method outlined in \cite{Connelly2012,Wilman2005} where we assume an initial velocity dispersion of 500\kms\ and apply both redshift and spatial limits given by:
\begin{equation}
	\delta(r)_{max} = \frac{1}{10}\frac{\delta(z)_{max}}{h_{75}^{-1}\mathrm{Mpc}}
\end{equation}
and
\begin{equation}
	\delta(\theta)_{max} = 206265'' \frac{\delta(r)_{max}}{h_{75}^{-1}\mathrm{Mpc}} \bigg{(}\frac{D_{\theta}}{h_{75}^{-1}\mathrm{Mpc}} \bigg{)}.
\end{equation}
where $\delta(z)_{max} = 2\sigma(v)/c$ and $D_\theta$ is the angular diameter distance.

\subsection{Velocity Dispersion}
The unbiased estimation of a standard deviation (a measure of statistical dispersion) is a technically involved problem. At first, we require that our estimator be unbiased in that the dispersion estimation is equal to the true dispersion, although, in practice this rarely occurs. The most commonly used estimate is the corrected sample standard deviation, given by:
\begin{equation}
	s = \sqrt{\frac{1}{n-1} \sum_{i=1}^n (x_i - \bar{x})^2}
\end{equation}
with $\{x_1, x_2, ..., x_n\}$ is the random sample and $\bar{x}$ is the sample mean. The corrected sample standard deviation has the advantage in that it is unbiased (as opposed to the population standard deviation which is biased), but the removal of bias relies on knowing \textit{a priori} the underlying distribution from which the sample is drawn. An estimator which correctly estimates a standard deviation for a sample drawn from a wide range of distributions and is not adversely effected by outliers is said to be \textit{robust}.

A robust estimator becomes critical as it minimizes the effect that outliers which may remain after the rejection of non-cluster members have on the measured dispersion. \cite{Beers1990} present a robust estimation of scale (yet another term for statistical dispersion) called the biweight scale estimator. \cite{Ruel2014} note that the biweight scale estimator is biased and suggests a correction.

The biweight scale estimator is given by \editorial{This isn't very good and needs to be rewritten but it gets the idea across.}:
\begin{equation}
	\sigma_{BI} = \sqrt{ N_{members} \frac{ \sum_{|u_i|<1} (1-u_i^2)^4 (v_i - \bar{v})^2} {D} }
\end{equation}
with $v_i$, the proper velocities, $\bar{v}$, the average of the proper velocities,
\begin{equation}
	D = \sum_{|u_i|<1} (1-u_i^2)(1-5u_i^2)
\end{equation}
with $u_i$ being the biweight weighting and defined as:
\begin{equation}
	u_i = \frac{v_i - \bar{v}}{9 {\rm MAD}(v_i)}
\end{equation}
where MAD is the median absolute deviation.

\editorial{Need to talk about how the new biweight is different. Also need to talk about how we are using DM halos and not galaxies, so we are only going to do so well when comparing the 3d dispersions and the dispersions that we are calculating.}

%The observed velocity dispersion, $\sigma_v$, of each cluster is calculated in two different ways. For clusters with at least 15 confirmed members, we use the biweight scale estimator \citep{Beers1990} which is less susceptible to outliers which may remain after the rejection of non-cluster members.

%For galaxy clusters with fewer than 15 members, we employ the gapper estimator \citep{Beers1990} which provides accurate dispersions for groups as small as 5 members \citep{Hou2009}. The gapped estimator is given by
%\begin{equation}
%	\sigma_v = 1.135c \frac{\sqrt{\pi}}{n(n-1)} \sum_{i=1}^{n-1} w_i g_i
%\end{equation}
%where the weights are $w_i = i(n-i)$ and the gaps $g_i = z_{i+1} -z_i$. The factor of 1.135 is from \cite{Wilman2005} which corrects for the $2\sigma$ redshift space cut applied during membership determination.

\subsection{Halo Mass}

\editorial{Following \cite{Evrard2008, VanderBurg2014, Sifon2013}}

\subsection{Substructure}

\editorial{Going to use the DS test along with a test for non-gaussian distributions of redshifts.}

\section{RESULTS}
\subsection{Cluster Number}
\subsection{Membership \& Cluster Masses}

\section{IMPROVEMENT}
\section{SUMMARY}

\bibliography{master}

\end{document}

### 2015-03-30 ms.tex
clean up preamble

@@
-%\documentclass[10pt,preprint]{aastex}
-%\documentclass[iop]{emulateapj} \font\sevenrm=cmr7  \usepackage{apjfonts}
-%preprint2 produces a double-column, single-spaced document:
-%\documentclass[preprint2]{aastex}
-\documentclass[apj, twocolappendix]{emulateapj}
+\documentclass[apj, revtex4]{emulateapj}
 
@@
 \usepackage{graphicx}
-\usepackage{appendix}
 \usepackage[colorlinks,urlcolor=blue,citecolor=blue,linkcolor=blue]{hyperref}
@@
 
+\pdfoutput=1
 \bibliographystyle{apj}
@@
 \noindent
-%
-We propose to use the Mitchell Spectrograph to provide accurate mass determinations of 10
-massive galaxy clusters at z=0.2-0.3 using integral field spectroscopy of the cluster galaxies.
-These clusters are selected optically from the SDSS DR8, and are representative of the hundreds
-of thousands of clusters expected from DES and LSST. The cluster counts provide a powerful
-measure of cosmological parameters independent of supernovae and the CMB. The dominant
-sources of error on these cosmological parameters from counts of optical clusters are systematic
-uncertainties on the absolute scale between the cluster mass and optical richness, and the intrinsic
-scatter in cluster mass at fixed richness. Here we propose a pilot study using these 10 massive
-cluster to measure independently the absolute mass scale and scatter in the cluster-optical richness
-relation. We will target each galaxy cluster with 4 pointings with the Mitchell Spectrograph,
-obtaining integral field spectroscopy for all the (more than 100) cluster galaxies out to radii of
-0.5 Mpc and luminosities down to 0.2 L*. The redshifts will allow us to calculate the line-ofsight
-velocity dispersion for each cluster, which is an estimator of the total virial mass, and
-calculate the precise cluster center. Using the independent cluster mass estimator from the
-velocity dispersions will calibrate the mass-optical richness relation, and can lead to a decrease
-on the error bars of key cosmological parameters by as much as 50\%.
-%
+ABSTRACT GOES HERE!!
+Lorem ipsum dolor sit amet, consectetur adipiscing elit.
+Cras malesuada, ante eu scelerisque gravida, augue lacus ullamcorper metus, ac volutpat libero magna rutrum nisi.
+Interdum et malesuada fames ac ante ipsum primis in faucibus.
+Ut eget magna est.
+Nam quis maximus purus, feugiat facilisis lectus.
+Nulla mollis sodales felis a ullamcorper.
+Lorem ipsum dolor sit amet, consectetur adipiscing elit.
+Curabitur rhoncus, ligula vel venenatis ornare, nisi massa sagittis orci, in hendrerit purus libero id mauris.
+Class aptent taciti sociosqu ad litora torquent per conubia nostra, per inceptos himenaeos.
 \end{abstract}

### 2015-03-30 ms.tex
clean up outline

@@
 
-\section{MOCK CATALOGS}
-\subsection{Input Simulations}
+\section{AARDVARK SIMULATION}
 
-\section{MOCK OBSERVATIONS}
+\section{THE HETDEX SURVEY}
 
@@
 
-\subsection{Membership}
-It is expected that some of the galaxies detected will be spurious sources not associated with the any given cluster.
-To reject these interlopers we employ two methods.
-For clusters with 20 or more $Q=0$ redshifts we use the  ``shifting gapped" method of \cite{Fadda1996}.
-This procedure combines both the positional and velocity information.
-Galaxies are binned in $0.4h^{-1}$ Mpc or larger enough bins to contain at least 10 galaxies.
-The galaxies in each bin are sorted by their line-of-sight velocity (LOSV),
-\begin{equation}
-	v = \frac{c (z-z_{cl})}{(1+z_{cl})}
-\end{equation}
-where $z$ is the redshift of the individual galaxy and $z_{cl}$ is the average redshift of the cluster.
-Any galaxy with a LOSV greater than 1000 \kms of a neighboring galaxy is rejected as an interloper.
-The procedure repeats until the number of galaxies stabilizes in the bin.
+\subsection{Mock Observations}
 
-For galaxy clusters with fewer than 20 $Q=0$ redshifts we employ the method outlined in \cite{Connelly2012,Wilman2005} where we assume an initial velocity dispersion of 500\kms\ and apply both redshift and spatial limits given by:
-\begin{equation}
-	\delta(r)_{max} = \frac{1}{10}\frac{\delta(z)_{max}}{h_{75}^{-1}\mathrm{Mpc}}
-\end{equation}
-and
-\begin{equation}
-	\delta(\theta)_{max} = 206265'' \frac{\delta(r)_{max}}{h_{75}^{-1}\mathrm{Mpc}} \bigg{(}\frac{D_{\theta}}{h_{75}^{-1}\mathrm{Mpc}} \bigg{)}.
-\end{equation}
-where $\delta(z)_{max} = 2\sigma(v)/c$ and $D_\theta$ is the angular diameter distance.
-
-\subsection{Velocity Dispersion}
+\subsection{Dynamical Properties}
 The unbiased estimation of a standard deviation (a measure of statistical dispersion) is a technically involved problem.
@@
 
+For the mass \editorial{Following \cite{Evrard2008, VanderBurg2014, Sifon2013}}.
+
+\subsection{Structural Properties}
+\editorial{Going to use the DS test along with a test for non-gaussian distributions of redshifts.}
+
+\subsection{Membership}
+It is expected that some of the galaxies detected will be spurious sources not associated with the any given cluster.
+To reject these interlopers we employ two methods.
+For clusters with 20 or more $Q=0$ redshifts we use the  ``shifting gapped" method of \cite{Fadda1996}.
+This procedure combines both the positional and velocity information.
+Galaxies are binned in $0.4h^{-1}$ Mpc or larger enough bins to contain at least 10 galaxies.
+The galaxies in each bin are sorted by their line-of-sight velocity (LOSV),
+\begin{equation}
+	v = \frac{c (z-z_{cl})}{(1+z_{cl})}
+\end{equation}
+where $z$ is the redshift of the individual galaxy and $z_{cl}$ is the average redshift of the cluster.
+Any galaxy with a LOSV greater than 1000 \kms of a neighboring galaxy is rejected as an interloper.
+The procedure repeats until the number of galaxies stabilizes in the bin.
+
+For galaxy clusters with fewer than 20 $Q=0$ redshifts we employ the method outlined in \cite{Connelly2012,Wilman2005} where we assume an initial velocity dispersion of 500\kms\ and apply both redshift and spatial limits given by:
+\begin{equation}
+	\delta(r)_{max} = \frac{1}{10}\frac{\delta(z)_{max}}{h_{75}^{-1}\mathrm{Mpc}}
+\end{equation}
+and
+\begin{equation}
+	\delta(\theta)_{max} = 206265'' \frac{\delta(r)_{max}}{h_{75}^{-1}\mathrm{Mpc}} \bigg{(}\frac{D_{\theta}}{h_{75}^{-1}\mathrm{Mpc}} \bigg{)}.
+\end{equation}
+where $\delta(z)_{max} = 2\sigma(v)/c$ and $D_\theta$ is the angular diameter distance.
+
 %The observed velocity dispersion, $\sigma_v$, of each cluster is calculated in two different ways.
@@
 
-\subsection{Halo Mass}
-
-\editorial{Following \cite{Evrard2008, VanderBurg2014, Sifon2013}}
-
-\subsection{Substructure}
-
-\editorial{Going to use the DS test along with a test for non-gaussian distributions of redshifts.}
-
 \section{RESULTS}
-\subsection{Cluster Number}
-\subsection{Membership \& Cluster Masses}
 

### 2015-03-30 ms.tex
wrote substructure section

@@
 
-\pdfoutput=1
 \bibliographystyle{apj}
@@
 
-\subsection{Structural Properties}
-\editorial{Going to use the DS test along with a test for non-gaussian distributions of redshifts.}
+\subsection{Evidence of Substructure}
+We leverage the large spectroscopic dataset to study the structural properties of the clusters.
+\cite{Pinkney1996} determine, from a comparison of five different methods that the Dressler-Shectman (DS) test \citep{Dressler1988} is the most sensitive to the presence of substructure.
+
+The DS test, which combines the spatial positions and velocities of the galaxies, provides a method to locate substructure by identifying groups of galaxies which differ significantly from the cluster velocity distribution.
+Galaxy subsets are selected from a cluster of $n_{members}$ and each constituent galaxy deviation is calculated according to
+\begin{equation}
+	\delta_i^2 = \frac{N_{local}+1}{\sigma^2}\bigg{[}(\bar{v}_{local,i} - \bar{v})^2 + (\sigma_{local,i} - \sigma)^2\bigg{]}^2
+\end{equation}
+where $\bar{v}_{local}$ and $\sigma_{local}$ are the mean velocity and velocity dispersion for a subset of $N_{local}$ galaxies and $\bar{v}$ and $\sigma$ are the entire cluster's mean velocity and velocity dispersion.
+The choice of $N_{local}$ is left to the user.
+Originally, \cite{Dressler1988} choose $N_{local}=10$, however \cite{Bird1994} points out that using a fixed value for $N_{local}$ reduces the sensitivity to substructure.
+We follow \cite{Bird1994} in choosing $N_{local} = \sqrt n_{members}$.
+\editorial{doesn't talk about the nearest neighbors which is what we are using.}
+
+The DS statistic is the $\Delta$-value given by, 
+\begin{equation}
+	\Delta = \sum^{n_{members}}_i \delta_i
+\end{equation}
+where a system is considered to contain substructure if $\Delta/n_{members} > 1$ \citep{Dressler1988}.
+A second method, described in \cite{Hou2012}, uses probabilities (P-values) rather than a threshold for the identification of substructure.
+P-values are computed by comparing the observed $\Delta$-value and the $Delta$-value after the velocities (but not positions) have been shuffled through a series of Monte Carlo runs.
+The probability of the existence of substructure becomes
+\begin{equation}
+	P = \sum (\Delta_{shuffled} > \Delta_{Observed}) / n_{shuffle}
+\end{equation}
+where $n_{shuffle}$ is the number of shufflings used. \editorial{This sounds a whole lot like the description given in Hou2012. Make sure that we aren't copying anything word for word. That'd be bad.}
+
+In practice, we use locate the nearest neighbors using an unsupervised k-nearest neighbor algorithm as implemented in Scikit-Learn \citep{Pedregosa2012}.
 

### 2015-03-30 ms.tex
commented membership section

@@
 
-\subsection{Membership}
-It is expected that some of the galaxies detected will be spurious sources not associated with the any given cluster.
+%\subsection{Membership}
+%It is expected that some of the galaxies detected will be spurious sources not associated with the any given cluster.
 To reject these interlopers we employ two methods.
@@
 The galaxies in each bin are sorted by their line-of-sight velocity (LOSV),
-\begin{equation}
-	v = \frac{c (z-z_{cl})}{(1+z_{cl})}
-\end{equation}
-where $z$ is the redshift of the individual galaxy and $z_{cl}$ is the average redshift of the cluster.
+%\begin{equation}
+%	v = \frac{c (z-z_{cl})}{(1+z_{cl})}
+%\end{equation}
+%where $z$ is the redshift of the individual galaxy and $z_{cl}$ is the average redshift of the cluster.
 Any galaxy with a LOSV greater than 1000 \kms of a neighboring galaxy is rejected as an interloper.
@@
 
-For galaxy clusters with fewer than 20 $Q=0$ redshifts we employ the method outlined in \cite{Connelly2012,Wilman2005} where we assume an initial velocity dispersion of 500\kms\ and apply both redshift and spatial limits given by:
-\begin{equation}
-	\delta(r)_{max} = \frac{1}{10}\frac{\delta(z)_{max}}{h_{75}^{-1}\mathrm{Mpc}}
-\end{equation}
-and
-\begin{equation}
-	\delta(\theta)_{max} = 206265'' \frac{\delta(r)_{max}}{h_{75}^{-1}\mathrm{Mpc}} \bigg{(}\frac{D_{\theta}}{h_{75}^{-1}\mathrm{Mpc}} \bigg{)}.
-\end{equation}
-where $\delta(z)_{max} = 2\sigma(v)/c$ and $D_\theta$ is the angular diameter distance.
+%For galaxy clusters with fewer than 20 $Q=0$ redshifts we employ the method outlined in \cite{Connelly2012,Wilman2005} where we assume an initial velocity dispersion of 500\kms\ and apply both redshift and spatial limits given by:
+%\begin{equation}
+%	\delta(r)_{max} = \frac{1}{10}\frac{\delta(z)_{max}}{h_{75}^{-1}\mathrm{Mpc}}
+%\end{equation}
+%and
+%\begin{equation}
+%	\delta(\theta)_{max} = 206265'' \frac{\delta(r)_{max}}{h_{75}^{-1}\mathrm{Mpc}} \bigg{(}\frac{D_{\theta}}{h_{75}^{-1}\mathrm{Mpc}} \bigg{)}.
+%\end{equation}
+%where $\delta(z)_{max} = 2\sigma(v)/c$ and $D_\theta$ is the angular diameter distance.
 

### 2015-03-30 ms.tex
added a bit to the mass section

@@
 \subsection{Dynamical Properties}
+\subsubsection{Velocity Dispersion}
 The unbiased estimation of a standard deviation (a measure of statistical dispersion) is a technically involved problem.
@@
 \editorial{Need to talk about how the new biweight is different.
-Also need to talk about how we are using DM halos and not galaxies, so we are only going to do so well when comparing the 3d dispersions and the dispersions that we are calculating.}
+Also need to talk about how we are using DM halos and not galaxies, so we are only going to do so well when comparing the 3d dispersions and the dispersions that we are calculating.
+Evrard2008 does a good job explaining the DM-galaxy bias we are assuming it is 1}
 
-For the mass \editorial{Following \cite{Evrard2008, VanderBurg2014, Sifon2013}}.
+\subsubsection{Dynamical Mass}
+Recently, the relationship between the velocity dispersion and dynamical mass has been the focus of several studies (\eg, \citealt{Evrard2008, Saro2013, Sifon2013, VanderBurg2014}), and find a best-fitting relation for the mass enclosed by $r_{200c}$ of the form
+\begin{equation}
+	M_{200c} = \frac{10^{15}}{h(z)} \bigg{(}\frac{\sigma_{1D}}{\sigma_{15}} \bigg{)}^{-\alpha} \Msol
+\end{equation}
+where $\sigma_{15} = 1082.9 \pm 4.0 \kms$, $\alpha = 0.3361 \pm 0.0026$, $h(z) = H_0 \sqrt{\Omega_\Lambda + (1+z)^3\Omega_M}$, and $\sigma_{1D}$ is the 1D velocity dispersion of the dark matter particles, which is related to the velocity dispersions of the galaxies.
 

### 2015-03-31 ms.tex
added editorial
made a bunch of notes to myself.

@@
 \section{AARDVARK SIMULATION}
+\editorial{Waiting to get a look at what Casey comes up with for the proposal we are supposedly writing. If he does a decent job then I'll try to expand it a bit and fill out this section.}
 
 \section{THE HETDEX SURVEY}
+\editorial{This should probably go into the introduction. I don't think we need a whole section on something that a bunch of papers have already talked about.}
 
@@
 \subsection{Mock Observations}
+\editorial{Here we need to talk about about how we set up the observations to look like what we think the HETDEX survey will see.
+It should be more techincal than the general discussion about what the survey hopes to accomplish, that'll go in the intro.
+A zoomed figure showing the tiling footprints would be appropriate.}
 
@@
 where $\sigma_{15} = 1082.9 \pm 4.0 \kms$, $\alpha = 0.3361 \pm 0.0026$, $h(z) = H_0 \sqrt{\Omega_\Lambda + (1+z)^3\Omega_M}$, and $\sigma_{1D}$ is the 1D velocity dispersion of the dark matter particles, which is related to the velocity dispersions of the galaxies.
+
+\editorial{Need to talk about how the parameters are some what up for debate, and vary from study to study.
+I think we should just use the params from Evrard2008 and call it a day.
+We can show a figure where we fit the data for the parameters, but that seems kinda silly to calibrate the data on the the data we are trying to fit.}
 

### 2015-03-31 ms.tex
added IFU figure
added this test figure and a junk caption.

@@
 A zoomed figure showing the tiling footprints would be appropriate.}
+
+\begin{figure} 
+	\includegraphics[width=0.49\textwidth]{f01.pdf} 
+	\caption{The ICD as a function of galaxy stellar mass.
+Individual galaxies are shown as gray points.
+The galaxies are then binned together by stellar mass in bins of 0.5 dex (except for the highest mass bin which is 1.0 dex) beginning with $\mathrm{Log~M}/\Msol =8.5$.
+The upper and lower quartiles of ICD are indicated by the blue boxes.
+The median of each bin is indicated by the red line.
+The upper and lower black bars show the 95th and 5th percentiles.
+The ICD for galaxies in our sample is low for low stellar masses, peaks in the intermediate stellar masses, and returns to low values at high stellar masses.} \label{fig:icd_vs_mass}
+\end{figure}
 

### 2015-04-01 ms.tex
added figure for survey area

@@
 \editorial{This should probably go into the introduction. I don't think we need a whole section on something that a bunch of papers have already talked about.}
+\begin{figure} 
+	\includegraphics[width=0.49\textwidth]{surveyArea.pdf} 
+	\caption{A polar azimuthal equidistant projection of the southern sky showing the sky area (approximately a quarter of the sky) covered by the Aardvark Simulations.
+Concentric circles are lines of constant declination, 10 to $-80\degree$ in $10\degree$ increments.
+Radial lines are lines of constant right ascension.
+Opaqueness of the region indicates the overlap of catalog tiles (see text for details).}
+	\label{fig:survey area} 
+\end{figure}
 

### 2015-04-06 ms.tex
added oii luminosity section

--- 2015-03-31 ms.tex
@@
 \editorial{Waiting to get a look at what Casey comes up with for the proposal we are supposedly writing. If he does a decent job then I'll try to expand it a bit and fill out this section.}
+\begin{figure} 
+	\includegraphics[width=0.49\textwidth]{surveyArea.pdf} 
+	\caption{A polar azimuthal equidistant projection of the southern sky showing the sky area (approximately a quarter of the sky) covered by the Aardvark Simulations.
+Concentric circles are lines of constant declination, 10 to $-80\degree$ in $10\degree$ increments.
+Radial lines are lines of constant right ascension.
+Opaqueness of the region indicates the overlap of catalog tiles (see text for details).}
+	\label{fig:survey area} 
+\end{figure}
 
@@
 \editorial{Here we need to talk about about how we set up the observations to look like what we think the HETDEX survey will see.
-It should be more techincal than the general discussion about what the survey hopes to accomplish, that'll go in the intro.
+It should be more technical than the general discussion about what the survey hopes to accomplish, that'll go in the intro.
 A zoomed figure showing the tiling footprints would be appropriate.}
+
+\begin{figure} 
+	\includegraphics[width=0.49\textwidth]{f01.pdf} 
+	\caption{} \label{fig:ifu layout} 
+\end{figure}
 
@@
 
+\subsection{\ion{O}{ii} Luminosity}
+
+HETDEX is designed to detect Lyman-$\alpha$ at redshift two.
+That allows us to detect \ion{O}{ii} emitters to $z\sim 0.49$.
+The catalog does not provide \ion{O}{ii} luminosities so we must assign them empirically.
+We use 177107 galaxies from the Sloan Digital Sky Survey (SDSS) Data Release 12 \citep{Alam2015} from $z = 0.05 - 0.2$.
+Galaxies are selected which have no redshift warning and have an \ion{O}{ii} flux five times greater than the \ion{O}{ii} flux error.
+
+\begin{figure} 
+	\includegraphics[width=0.49\textwidth]{oii_sdss.pdf} 
+	\caption{} \label{fig:oii sdss} 
+\end{figure}
+
+We place each SDSS galaxy on a color-magnitude diagram (CMD) of $M_r$ and $g-r$, see Figure~\ref{fig:oii sdss}.
+To assign an \ion{O}{ii} luminosity to each galaxy in our catalog we place the galaxies on the same and select all SDSS galaxies in a small 2D bin around the galaxy.
+We extract all of the SDSS galaxies inside that bin and create a histogram of their \ion{O}{ii} luminosities.
+Using a slice sampling technique we assign the catalog galaxy an \ion{O}{ii} luminosity based on the distribution of SDSS galaxies extracted.
+
+For catalog galaxies which are placed on the CMD near no, or very few ($n<3$) galaxies we assign it zero \ion{O}{ii} luminosity or the mean luminosity, respectively.
+
 \section{IMPROVEMENT}

### 2015-04-16 ms.tex
removed membership section
updated order, added some text

@@
 ABSTRACT GOES HERE!!
-Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Cras malesuada, ante eu scelerisque gravida, augue lacus ullamcorper metus, ac volutpat libero magna rutrum nisi.
-Interdum et malesuada fames ac ante ipsum primis in faucibus.
-Ut eget magna est.
-Nam quis maximus purus, feugiat facilisis lectus.
-Nulla mollis sodales felis a ullamcorper.
-Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Curabitur rhoncus, ligula vel venenatis ornare, nisi massa sagittis orci, in hendrerit purus libero id mauris.
-Class aptent taciti sociosqu ad litora torquent per conubia nostra, per inceptos himenaeos.
+Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
+Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
+Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
 \end{abstract}
@@
 
-\section{ANALYSIS}
-
-\subsection{Mock Observations}
+\section{Mock Observations}
 \editorial{Here we need to talk about about how we set up the observations to look like what we think the HETDEX survey will see.
@@
 
-\subsection{Dynamical Properties}
-\subsubsection{Velocity Dispersion}
+\section{Recovery of Cluster Parameters, Full Knowledge}
+Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
+Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
+Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+
+\subsection{Cluster Redshift}
+The accurate determination of the cluster redshift is crucial to the reliability of all following measurements.
+An incorrect cluster redshift introduces errors into the measured line of sight velocity (LOSV) and corresponding dispersion, which, in turn, contributes to errors associated with dynamical mass and radius.
+
+In simple terms, the cluster redshift is the mean of the redshifts of all galaxies associated with the cluster.
+
+\subsection{Line of Sight Velocity Dispersion}
 The unbiased estimation of a standard deviation (a measure of statistical dispersion) is a technically involved problem.
@@
 
-\subsection{Evidence of Substructure}
+\section{Evidence of Substructure}
+Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
+Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
+Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+\subsection{From VD profiles}
+Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
+Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
+Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+\subsection{Mod-Dominance}
+Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
+Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
+Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+\subsection{Dressler-Schectman Test}
 We leverage the large spectroscopic dataset to study the structural properties of the clusters.
@@
 
-%\subsection{Membership}
-%It is expected that some of the galaxies detected will be spurious sources not associated with the any given cluster.
-To reject these interlopers we employ two methods.
-For clusters with 20 or more $Q=0$ redshifts we use the  ``shifting gapped" method of \cite{Fadda1996}.
-This procedure combines both the positional and velocity information.
-Galaxies are binned in $0.4h^{-1}$ Mpc or larger enough bins to contain at least 10 galaxies.
-The galaxies in each bin are sorted by their line-of-sight velocity (LOSV),
-%\begin{equation}
-%	v = \frac{c (z-z_{cl})}{(1+z_{cl})}
-%\end{equation}
-%where $z$ is the redshift of the individual galaxy and $z_{cl}$ is the average redshift of the cluster.
-Any galaxy with a LOSV greater than 1000 \kms of a neighboring galaxy is rejected as an interloper.
-The procedure repeats until the number of galaxies stabilizes in the bin.
-
-%For galaxy clusters with fewer than 20 $Q=0$ redshifts we employ the method outlined in \cite{Connelly2012,Wilman2005} where we assume an initial velocity dispersion of 500\kms\ and apply both redshift and spatial limits given by:
-%\begin{equation}
-%	\delta(r)_{max} = \frac{1}{10}\frac{\delta(z)_{max}}{h_{75}^{-1}\mathrm{Mpc}}
-%\end{equation}
-%and
-%\begin{equation}
-%	\delta(\theta)_{max} = 206265'' \frac{\delta(r)_{max}}{h_{75}^{-1}\mathrm{Mpc}} \bigg{(}\frac{D_{\theta}}{h_{75}^{-1}\mathrm{Mpc}} \bigg{)}.
-%\end{equation}
-%where $\delta(z)_{max} = 2\sigma(v)/c$ and $D_\theta$ is the angular diameter distance.
-
-%The observed velocity dispersion, $\sigma_v$, of each cluster is calculated in two different ways.
-For clusters with at least 15 confirmed members, we use the biweight scale estimator \citep{Beers1990} which is less susceptible to outliers which may remain after the rejection of non-cluster members.
-
-%For galaxy clusters with fewer than 15 members, we employ the gapper estimator \citep{Beers1990} which provides accurate dispersions for groups as small as 5 members \citep{Hou2009}.
-The gapped estimator is given by
-%\begin{equation}
-%	\sigma_v = 1.135c \frac{\sqrt{\pi}}{n(n-1)} \sum_{i=1}^{n-1} w_i g_i
-%\end{equation}
-%where the weights are $w_i = i(n-i)$ and the gaps $g_i = z_{i+1} -z_i$.
-The factor of 1.135 is from \cite{Wilman2005} which corrects for the $2\sigma$ redshift space cut applied during membership determination.
-
 \section{RESULTS}
@@
 \section{IMPROVEMENT}
+Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
+Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
+Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
 \section{SUMMARY}
-
+Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
+Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
+Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
 \bibliography{master}

### 2015-04-17 ms.tex
wrote redshift section

@@
 \section{Recovery of Cluster Parameters, Full Knowledge}
+
 Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
@@
 \subsection{Cluster Redshift}
-The accurate determination of the cluster redshift is crucial to the reliability of all following measurements.
+The accurate determination of the cluster redshift ($z_c$) is crucial to the reliability of all following measurements.
 An incorrect cluster redshift introduces errors into the measured line of sight velocity (LOSV) and corresponding dispersion, which, in turn, contributes to errors associated with dynamical mass and radius.
@@
 In simple terms, the cluster redshift is the  mean of the redshifts of all galaxies associated with the cluster.
+However, because the standard mean can be quite sensitive to outliers or otherwise contaminated data, we require a more resistant statistic, and turn to the biweight location estimator \citep{Beers1990} which provides improved performance.
+
+We compare the calculated cluster redshifts to the true redshift ($z_{c,true}$) for 107748 galaxies comprising 1683 unique halos, and we find a RMS$[\delta z/(1+z_{c,true})]= 4\times 10^{-4}$ where $\delta z = z_{c,true} - z_{c}$.
+
+\editorial{The RMS using just the regular mean is 3.8e-4 which is only slightly better than the biweight. I don't think that will be the case when we get more complicated things.}
 
@@
 \cite{Beers1990} present a robust estimation of scale (yet another term for statistical dispersion) called the biweight scale estimator.
-\cite{Ruel2014} note that the biweight scale estimator is biased and suggests a correction.
+\cite{Ruel2014} note that the biweight scale estimator is biased and suggest a correction.
 
@@
 
-\subsubsection{Dynamical Mass}
+\subsection{Dynamical Mass}
 Recently, the relationship between the velocity dispersion and dynamical mass has been the focus of several studies (\eg, \citealt{Evrard2008, Saro2013, Sifon2013, VanderBurg2014}), and find a best-fitting relation for the mass enclosed by $r_{200c}$ of the form
@@
 We can show a figure where we fit the data for the parameters, but that seems kinda silly to calibrate the data on the the data we are trying to fit.}
+
+\subsection{Radial Extent}
+\begin{equation}
+	r_{200} = \bigg{[} \frac{3}{4\pi} \frac{M_{200}}{200\rho_c} \bigg{]}^{1/3}
+\end{equation}
 

### 2015-04-22 ms.tex
continue to add text

@@
 
-\shorttitle{Cluster Paper}
+\shorttitle{HETDEX PAPER}
 \shortauthors{BOADA ET AL.}
@@
 
-\section{Recovery of Cluster Parameters, Full Knowledge}
+\section{Analysis}
 
@@
 
-We compare the calculated cluster redshifts to the true redshift ($z_{c,true}$) for 107748 galaxies comprising 1683 unique halos, and we find a RMS$[\delta z/(1+z_{c,true})]= 4\times 10^{-4}$ where $\delta z = z_{c,true} - z_{c}$.
-
-\editorial{The RMS using just the regular mean is 3.8e-4 which is only slightly better than the biweight. I don't think that will be the case when we get more complicated things.}
+We compare the calculated cluster redshifts to the true redshift ($z_{c,true}$) for 107748 galaxies comprising 1683 unique halos, and we find a RMS$[\delta z/(1+z_{c,true})]= 4\times 10^{-4}$ where $\Delta z = z_{c,true} - z_{c}$.
+\editorial{The RMS using just the regular mean is 3.8e-4 which is only slightly better than the biweight.
+I don't think that will be the case when we get more complicated things.}
 
 \subsection{Line of Sight Velocity Dispersion}
-The unbiased estimation of a standard deviation (a measure of statistical dispersion) is a technically involved problem.
+We first calculate the line of sight velocity (LOSV) to each galaxy, where
+\begin{equation}
+	LOSV = c\frac{z - z_c}{1+z_c}
+\end{equation}
+and $c$ is the speed of light in \kms, $z$ is the redshift of the individual galaxy, and $z_c$ is the overall cluster redshift described in the previous section.
+
+The unbiased estimation of a standard deviation (a measure of statistical dispersion) from these LOSVs is a technically involved problem.
 At first, we require that our estimator be unbiased in that the dispersion estimation is equal to the true dispersion, although, in practice this rarely occurs.
@@
 \end{equation}
-with $\{x_1, x_2, ..., x_n\}$ is the random sample and $\bar{x}$ is the sample mean.
+with $\{x_1, x_2, ..., x_n\}$ being the random sample and $\bar{x}$ the sample mean.
 The corrected sample standard deviation has the advantage in that it is unbiased (as opposed to the population standard deviation which is biased), but the removal of bias relies on knowing \textit{a priori} the underlying distribution from which the sample is drawn.
-An estimator which correctly estimates a standard deviation for a sample drawn from a wide range of distributions and is not adversely effected by outliers is said to be \textit{robust}.
+An estimator which correctly estimates a standard deviation for a sample drawn from a wide range of distributions and is not adversely effected by outliers is said to be robust.
 
-A robust estimator becomes critical as it minimizes the effect that outliers which may remain after the rejection of non-cluster members have on the measured dispersion.
+In our situation, a robust estimator becomes critical as it minimizes the effect of outliers which the inclusion of non-cluster members have on the measured dispersion.
 \cite{Beers1990} present a robust estimation of scale (yet another term for statistical dispersion) called the biweight scale estimator.
-\cite{Ruel2014} note that the biweight scale estimator is biased and suggest a correction.
+\cite{Ruel2014} note, however, that the biweight scale estimator is biased and suggest a correction.
 

### 2015-04-24 ms.tex
Added some structural text

@@
 
-\section{Analysis}
+\editorial{Should show some sort of a figure which demonstrates the number of recovered galaxies per halo compared to the true number of galaxies in each halo.
+Maybe even just a statement that the average number of galaxies is XXX and the average number recovered is XXX.}
+
+\section{Recovery of Parameters}
 
@@
 However, because the standard mean can be quite sensitive to outliers or otherwise contaminated data, we require a more resistant statistic, and turn to the biweight location estimator \citep{Beers1990} which provides improved performance.
-
-We compare the calculated cluster redshifts to the true redshift ($z_{c,true}$) for 107748 galaxies comprising 1683 unique halos, and we find a RMS$[\delta z/(1+z_{c,true})]= 4\times 10^{-4}$ where $\Delta z = z_{c,true} - z_{c}$.
-\editorial{The RMS using just the regular mean is 3.8e-4 which is only slightly better than the biweight.
-I don't think that will be the case when we get more complicated things.}
 
@@
 \subsection{Radial Extent}
+We define the radius of a galaxy cluster as
 \begin{equation}
-	r_{200} = \bigg{[} \frac{3}{4\pi} \frac{M_{200}}{200\rho_c} \bigg{]}^{1/3}
+	r_{200c} = \bigg{[} \frac{3}{4\pi} \frac{M_{200}}{200\rho_c} \bigg{]}^{1/3}
 \end{equation}
+where $\rho_c$ is critical density of the universe and defined as $3H^2/8\pi G$.
 
@@
 Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+
 \subsection{From VD profiles}
-Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
-\subsection{Mod-Dominance}
-Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+We utilize the modality \citep{Oliva-Altamirano2014} which describes the Gaussianity of a LOSV distribution in a galaxy cluster.
+For clusters with Gaussian distributed LOSVs, the modality is close to 1/3.
+It is defined as $(1+\mathrm{skewness}^2)/(3+\mathrm{kurtosis}^2)$.
+\editorial{Do I need to describe what the skewness and kurtosis is?}
+
+\subsection{Dominance}
+\editorial{This is taken pretty directly from the GAMA paper. Will need to be edited to fit.}
+The dominance is defined as the luminosity gap between the brightest and the second brightest galaxy in a cluster ($\Delta m_{1, 2}$).
+The amplitude of the luminosity gap between the BGG/BCG and the second brightest galaxy in the halo, is expected to be a function of both the formation epoch and the recent infall history of the halo.
+A small magnitude gap ($\Delta m_{1, 2} < 1$) indicates a recent halo merger, and larger gaps ($\Delta m_{1, 2} > 1$), common in fossil groups, is perhaps indicative of a cluster or groups that has not undergone a recent merger.
+
 \subsection{Dressler-Schectman Test}
@@
 \section{RESULTS}
+
+\subsection{Full Knowledge}
+We compare the calculated cluster redshifts to the true redshift ($z_{c,true}$) for 107748 galaxies comprising 1683 unique halos, and we find a RMS$[\Delta z/(1+z_{c,true})]= 4\times 10^{-4}$ where $\Delta z = z_{c,true} - z_{c}$.
+\editorial{The RMS using just the regular mean is 3.8e-4 which is only slightly better than the biweight.
+I don't think that will be the case when we get more complicated things.}
 

### 2015-04-24 ms.tex
add cluster CMD

@@
 \subsection{Full Knowledge}
-We compare the calculated cluster redshifts to the true redshift ($z_{c,true}$) for 107748 galaxies comprising 1683 unique halos, and we find a RMS$[\Delta z/(1+z_{c,true})]= 4\times 10^{-4}$ where $\Delta z = z_{c,true} - z_{c}$.
+We compare the calculated cluster redshifts to the true redshift ($z_{c,true}$) for 107748 galaxies comprising 1683 unique halos \editorial{these are old numbers, the current is something like 650,000 galaxies, and 16,000 halos}, and we find a RMS$[\Delta z/(1+z_{c,true})]= 4\times 10^{-4}$ where $\Delta z = z_{c,true} - z_{c}$.
 \editorial{The RMS using just the regular mean is 3.8e-4 which is only slightly better than the biweight.
@@
 	\includegraphics[width=0.49\textwidth]{oii_sdss.pdf} 
-	\caption{} \label{fig:oii sdss} 
+	\caption{177107 galaxies} \label{fig:oii sdss} 
 \end{figure}
@@
 Using a slice sampling technique we assign the catalog galaxy an \ion{O}{ii} luminosity based on the distribution of SDSS galaxies extracted.
+
+\begin{figure}
+	\includegraphics[width=0.49\textwidth]{clustersCMD.pdf}
+	\caption{657916 galaxies}
+	\label{fig:oii clusters}
+\end{figure}
 

### 2015-05-04 ms.tex
added full knowledge figure
started work on hetdex selection

--- 2015-04-24 ms.tex
@@
 \end{equation}
-where $\sigma_{15} = 1082.9 \pm 4.0 \kms$, $\alpha = 0.3361 \pm 0.0026$, $h(z) = H_0 \sqrt{\Omega_\Lambda + (1+z)^3\Omega_M}$, and $\sigma_{1D}$ is the 1D velocity dispersion of the dark matter particles, which is related to the velocity dispersions of the galaxies.
+where $\sigma_{15} = 1082.9 \pm 4.0~\kms$, $\alpha = 0.3361 \pm 0.0026$, $h(z) = H_0 \sqrt{\Omega_\Lambda + (1+z)^3 \Omega_M}$, and $\sigma_{1D}$ is the 1D velocity dispersion of the dark matter particles, which is related to the velocity dispersions of the galaxies.
+\editorial{This doesn't appear to be the formula that I am actually using to calculate the mass.
+I think I am using the relation from Saro2013.}
 
@@
 \subsection{Full Knowledge}
-We compare the calculated cluster redshifts to the true redshift ($z_{c,true}$) for 107748 galaxies comprising 1683 unique halos, and we find a RMS$[\Delta z/(1+z_{c,true})]= 4\times 10^{-4}$ where $\Delta z = z_{c,true} - z_{c}$.
+We compare the calculated cluster redshifts to the true redshift ($z_{c,true}$) for 114903 galaxies comprising 1379 unique halos, and we find a RMS$[\Delta z/(1+z_{c,true})]= 4\times 10^{-4}$ where $\Delta z = z_{c,true} - z_{c}$.
 \editorial{The RMS using just the regular mean is 3.8e-4 which is only slightly better than the biweight.
@@
 
-\subsection{\ion{O}{ii} Luminosity}
+\begin{figure*} 
+	\includegraphics[width=\textwidth]{fullKnowledge.pdf} 
+	\caption{Intrinsic cluster properties versus the recovered cluster properties for 1379 unique halos comprised of 114903 individual galaxies.
+The left panel shows the line of sight velocity dispersion (LOSVD) and the right panel shows the recovered halo mass.
+In both panels, the red line shows the 1:1 relation and the teal line shows the best fit to data.}
+	\label{fig:full} 
+\end{figure*}
+
+\subsection{HETDEX Depth}
+
+Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
+Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
+Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+
+\subsubsection{\ion{O}{ii} Luminosity}
 
@@
 	\includegraphics[width=0.49\textwidth]{oii_sdss.pdf} 
-	\caption{} \label{fig:oii sdss} 
+	\caption{686184 $z<0.2$ galaxies} \label{fig:oii sdss} 
 \end{figure}
@@
 
+\begin{figure}
+	\includegraphics[width=0.49\textwidth]{clustersCMD.pdf}
+	\caption{657916 galaxies}
+	\label{fig:oii clusters}
+\end{figure}
+
 For catalog galaxies which are placed on the CMD near no, or very few ($n<3$) galaxies we assign it zero \ion{O}{ii} luminosity or the mean luminosity, respectively.
+
+\begin{eqnarray}
+	g_{DES} = g_{SDSS} - 0.104*(g-r)_{SDSS} + 0.01 \\
+	r_{DES} = r_{SDSS} - 0.102*(g-r)_{SDSS} + 0.02
+\end{eqnarray}
 
@@
 Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+
 \section{SUMMARY}

### 2015-05-07 ms.tex
work

@@
 	\includegraphics[width=\textwidth]{fullKnowledge.pdf} 
-	\caption{Intrinsic cluster properties versus the recovered cluster properties for 1379 unique halos comprised of 114903 individual galaxies.
+	\caption{Intrinsic cluster properties versus the recovered cluster properties for 16758 unique halos comprised of 657916 individual galaxies.
 The left panel shows the line of sight velocity dispersion (LOSVD) and the right panel shows the recovered halo mass.
@@
 Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+
+\begin{figure*} 
+	\includegraphics[width=\textwidth]{hetdexDepth.pdf} 
+	\caption{HETDEX DEPTH!
+Intrinsic cluster properties versus the recovered cluster properties for 14239 unique halos comprised of 87754 individual galaxies.
+The left panel shows the line of sight velocity dispersion (LOSVD) and the right panel shows the recovered halo mass.
+In both panels, the red line shows the 1:1 relation and the teal line shows the best fit to data.}
+	\label{fig:hetdexDepth} 
+\end{figure*}
 

### 2015-05-21 ms.tex
added stuff
stuff from our proposal and another paper about hetdex

@@
 
-% General commands that are good for any agronomy paper.
+% General commands that are good for any astronomy paper.
 \input{commands.tex}
@@
 
-\title{Cluster Paper}
+\title{HETDEX Paper}
 
@@
 C.~Papovich\altaffilmark{1},
-B.~Salmon\altaffilmark{1}, 
-N.~Merhtens\altaffilmark{1},
-T.~Li\altaffilmark{1}, 
 R.~Wechsler\altaffilmark{2,3},
@@
 \section{INTRODUCTION}
+\editorial{A lot of these words are taken from Casey's proposal to get more funding.}
+
+This support will allow Mr.
+Boada to contribute to the core science of my NSF grant (AST 1413317) for the DECam/IRAC Galaxy Environment Survey (DIRGES).
+He will studying both simulated and real data to understand the reliability in measuring galaxy cluster masses and dynamical states using spectroscopic information for emission-line galaxies.
+DIRGES will identify as many as 100 galaxy cluster progenitors at 0.8 $<$ z $<$ 1.5.
+Significant gains in the understanding of these clusters are possible if we can (1) interpret their dynamical nature through spectroscopy, and (2) if we can link them to clusters at lower redshift, z $<$ 0.5, from within the same dataset to suppress potential observational biases.
+I have plans to obtain the spectroscopy to achieve both of these supplemental goals, but the majority of the spectroscopic redshifts will be for emission-line galaxies.
+It is not straightforward to use these data to interpret the kinematic and dynamical states of the clusters.
+DIRGES is covered by SDSS Stripe 82 (Annis et al.
+2014), the Dark Energy Survey (DES), and the Hobby Eberly Telescope Dark Energy eXperiment (HETDEX).
+One key is HETDEX, which is a spectroscopic survey covering $\sim$400 deg2 and measuring redshifts for as many as ∼106 emission-line galaxies at z $<$ 0.5.
+HETDEX will contain as many as 100 galaxy Virgo-sized clusters (Mdyn$\sim$1015 M⊙) out to z $<$ 0.5.
+And, because HETDEX covers DIRGES, the data will contain both low-redshift and high-redshift clusters in the same imaging dataset, allowing the most homogeneous study of the low-z and high-z universe yet.
 
@@
 \section{THE HETDEX SURVEY}
-\editorial{This should probably go into the introduction. I don't think we need a whole section on something that a bunch of papers have already talked about.}
+\editorial{This should probably go into the introduction.
+I don't think we need a whole section on something that a bunch of papers have already talked about.
+The text below is taken from Chiang 2015 and is NOT original to me.}
+
+The Hobby Eberly Telescope Dark Energy Experiment (HETDEX; Hill et al.
+2008b) is pioneering the instrumentation development and observations of high-redshift large scale structures using wide-field IFUs.
+In a 3-year baseline starting from late 2015, HETDEX will leverage the cosmic evolution of the dark energy equation of state with high redshift (z $>$ 2) constraints imprinted by the Baryon Acoustic Oscillations (BAO; Eisenstein 2005) in the early universe.
+The program will perform a redshift survey of LAEs in 300 deg2 (Spring field) plus 150 deg2 (Fall field) at 1.9 $<$ z $<$ 3.5 (with a filling factor of 1/4.5), with a total survey volume of $\sim$ 8.5 Gpc3.
+The survey uses the 10-m Hobby-Eberly Telescope (HET; Ramsey et al.
+1998) with a wide-field upgrade to reach a 22x22 arcmin2 field-of-view.
+Blind spectroscopy (R $\sim$ 750 in 350–550 nm) with no pre-selection of targets will be performed using the Visible Integral-Field Replicable Unit Spectrograph (VIRUS; Hill et al.
+2012, 2014).
+With the LAE redshifts, HETDEX will pinpoint numerous locations of the highest density concentrations at 1.9 $<$ z $<$ 3.5, generating a substantially large and homogeneous sample of cluster progenitors in the key epoch of cluster formation before virialization.
 

### 2015-05-27 ms.tex
added text to LOSVD discussion

@@
 
-\section{THE HETDEX SURVEY}
+\section{THE HETDEX SURVEY}\label{sec:Hetdex}
 \editorial{This should probably go into the introduction.
@@
 The unbiased estimation of a standard deviation (a measure of statistical dispersion) from these LOSVs is a technically involved problem.
-At first, we require that our estimator be unbiased in that the dispersion estimation is equal to the true dispersion, although, in practice this rarely occurs.
+At first, we require that our estimator be unbiased in that the dispersion estimation is equal to the true dispersion regardless of the number of points sampled, although, in practice this rarely occurs.
 The most commonly used estimate is the corrected sample standard deviation, given by:
@@
 An estimator which correctly estimates a standard deviation for a sample drawn from a wide range of distributions and is not adversely effected by outliers is said to be robust.
+An estimator which correctly identifies the standard deviation, even when a number of points are replaced by different values is said to be resistant.
 
-In our situation, a robust estimator becomes critical as it minimizes the effect of outliers which the inclusion of non-cluster members have on the measured dispersion.
-\cite{Beers1990} present a robust estimation of scale (yet another term for statistical dispersion) called the biweight scale estimator.
-\cite{Ruel2014} note, however, that the biweight scale estimator is biased and suggest a correction.
-
-The biweight scale estimator is given by \editorial{This isn't very good and needs to be rewritten but it gets the idea across.}:
+In our situation, a resistant estimator becomes critical as it minimizes the effect of outliers which the inclusion of non-cluster members have on the measured dispersion.
+\cite{Beers1990} present both a robust and resistant estimation of scale (yet another term for statistical dispersion) called the biweight scale estimator, which has been widely accepted by the community (\eg, \citealt{Milvang-Jensen2008, Owers2011, Murphy2011} and many others).
+It is given by
 \begin{equation}
@@
 where MAD is the median absolute deviation.
+\cite{Ruel2014} note, however, that the biweight scale estimator is biased and suggest a correction of $1/(D-1)$ to $\sigma_{BI}$ referring to it as the biweight sample variance.
+We adopt this method for clusters with at least 15 members.
+For clusters with fewer than 15 members, we adopt the gapper scale estimator \citep{Beers1990} which is shown to accurately recover the dispersion for as few as 5 member galaxies \citep{Hou2009}.
 
-\editorial{Need to talk about how the new biweight is different.
-Also need to talk about how we are using DM halos and not galaxies, so we are only going to do so well when comparing the 3d dispersions and the dispersions that we are calculating.
-Evrard2008 does a good job explaining the DM-galaxy bias we are assuming it is 1}
+There are several situations which can adversely effect the quality of our velocity dispersion measurement.
+The first is due to the nature of our observations.
+Because the HETDEX survey has a 1/4.5 fill factor (see Section~\ref{sec:Hetdex}), there will be many situations where we will not have full spectroscopic information for a cluster.
+Some clusters could also have intrinsic velocity distributions where the observations of only a few members could result in a LOSVD which differs by large percent.
+This gives rise to clusters along a fixed mass having a large range of possible LOSVDs.
+\cite{Saro2013} find this effect to be most pronounced for clusters with fewer than 30 members, and \cite{Ruel2014} show the effect is a net increase in scatter of about 5\% compared to clusters with greater than 30 members.
+\editorial{This section was adapted, pretty heavily from Ruel2014.
+Is that cool?}
+
+A second effect, unique to works such as this, is the difference between the LOSVD computed between dark matter halos and the galaxies that occupy them, the so-called velocity bias (\eg, \citealt{Evrard2008, White2010}).
+This effect is assumed to be small ($\sim5\%$) and for this work we assume there is no bias, or that the galaxies perfectly trace the velocity distribution.
 
@@
 \end{equation}
-where $\sigma_{15} = 1082.9 \pm 4.0~\kms$, $\alpha = 0.3361 \pm 0.0026$, $h(z) = H_0 \sqrt{\Omega_\Lambda + (1+z)^3 \Omega_M}$, and $\sigma_{1D}$ is the 1D velocity dispersion of the dark matter particles, which is related to the velocity dispersions of the galaxies.
+where $\sigma_{15} = 1082.9 \pm 4.0~\kms$, $\alpha = 0.3361 \pm 0.0026$, $h(z) = H_0/100 \sqrt{\Omega_\Lambda + (1+z)^3 \Omega_M}$, and $\sigma_{1D}$ is the 1D velocity dispersion of the dark matter particles, which is related to the velocity dispersions of the galaxies.
 \editorial{This doesn't appear to be the formula that I am actually using to calculate the mass.
@@
 \subsubsection{\ion{O}{ii} Luminosity}
-
 HETDEX is designed to detect Lyman-$\alpha$ at redshift two.

### 2015-05-28 ms.tex
worked on mass section

@@
 \fi}
+
+\newcommand{\citeeg}[1]{(\eg, \citealt{#1})}
 
@@
 
-A second effect, unique to works such as this, is the difference between the LOSVD computed between dark matter halos and the galaxies that occupy them, the so-called velocity bias (\eg, \citealt{Evrard2008, White2010}).
+A second effect, unique to works such as this, is the difference between the LOSVD computed between dark matter halos and the galaxies that occupy them, the so-called velocity bias \citeeg{Evrard2008, White2010}.
 This effect is assumed to be small ($\sim5\%$) and for this work we assume there is no bias, or that the galaxies perfectly trace the velocity distribution.
@@
 \subsection{Dynamical Mass}
-Recently, the relationship between the velocity dispersion and dynamical mass has been the focus of several studies (\eg, \citealt{Evrard2008, Saro2013, Sifon2013, VanderBurg2014}), and find a best-fitting relation for the mass enclosed by $r_{200c}$ of the form
+Recently, the relationship between the LOSVD and dynamical mass has been the focus of several studies \citeeg{Evrard2008, Saro2013, Sifon2013, VanderBurg2014}, and a best fitting relationship for the mass enclosed by $r_{200c}$ of the form
 \begin{equation}
-	M_{200c} = \frac{10^{15}}{h(z)} \bigg{(}\frac{\sigma_{1D}}{\sigma_{15}} \bigg{)}^{-\alpha} \Msol
+	M_{200c} = \frac{10^{15}}{h(z)} \bigg{(}\frac{\sigma_{1D}}{A_{1D}} \bigg{)}^{-\alpha} \Msol
 \end{equation}
-where $\sigma_{15} = 1082.9 \pm 4.0~\kms$, $\alpha = 0.3361 \pm 0.0026$, $h(z) = H_0/100 \sqrt{\Omega_\Lambda + (1+z)^3 \Omega_M}$, and $\sigma_{1D}$ is the 1D velocity dispersion of the dark matter particles, which is related to the velocity dispersions of the galaxies.
-\editorial{This doesn't appear to be the formula that I am actually using to calculate the mass.
-I think I am using the relation from Saro2013.}
+with $A_{1D} =$ 1040-1140 \kms\ (\citealt{Munari2013}; referred to as $\sigma_{15}$ in \citealt{Evrard2008} and other works), $\alpha = 1/3$, $h(z) = H(z)/100$, and $\sigma_{1D}$ is the LOSVD of the velocity tracers (dark matter particles, subhalos or galaxies).
 
-\editorial{Need to talk about how the parameters are some what up for debate, and vary from study to study.
-I think we should just use the params from Evrard2008 and call it a day.
-We can show a figure where we fit the data for the parameters, but that seems kinda silly to calibrate the data on the the data we are trying to fit.}
+The choice $A_{1D}$ and $\alpha$ varies between studies \citeeg{Munari2013, VanderBurg2014} and should be calibrated on a individual basis.
+To do this, we randomly select 47494, $z<0.5$ clusters composed of 36000 $10^{13}$, 6000 $10^{14}$ and two $10^{15}~\Msol$ halos.
+We perform a linear fit to the $\sigma_{1D}-M_{200}$ values allowing both $A_{1D}$ and $\alpha$ to vary.
+We find best fitting parameters of $A_{1D} = 1117.9~\kms$ and $\alpha = 0.3297$, both of which are very near the values from \cite{Evrard2008} of $A_{1D} = 1082.9 \pm 4.0~\kms$ and $\alpha = 0.3361$.
+Therefore, we chose to adopt the parameters from \cite{Evrard2008} to better facilitate with other simulations \citeeg{Old2014}, and observational studies \citeeg{Brodwin2010}.
 

### 2015-06-02 ms.tex
finished? oii section

@@
 
+\section{ {\rm[\ion{O}{ii}]} Luminosity}
+HETDEX is designed to detect Lyman-$\alpha$ at redshift two.
+That allows us to detect [\ion{O}{ii}] ($\lambda\lambda 3727-3729\AAA$ doublet) emitters to $z\sim 0.49$.
+The catalog does not provide [\ion{O}{ii}] luminosities so we must assign them empirically.
+We use 503113 galaxies from the Sloan Digital Sky Survey (SDSS) Data Release 12 \citep{Alam2015} from $z = 0.05 - 0.2$, which are selected which have no redshift warning.
+
+\begin{figure*} 
+	\includegraphics[width=\textwidth]{oii_sdss.pdf} 
+	\caption{\textit{Left}: CMD of 503113 $z<0.2$ galaxies take from the SDSS DR12 where the shading scales with the density of points.
+The two boxes show regions containing potential catalog galaxies.
+\textit{Right}: Probability histograms of the Log [\ion{O}{ii}] luminosity for the SDSS galaxies located in the two highlighted regions on the right.
+New [\ion{O}{ii}] luminosity (and subsequently fluxes) are assigned to catalog galaxies from slice sampling the probability histogram.} \label{fig:oii sdss}
+\end{figure*}
+
+While the difference is small, we convert each SDSS galaxy's observed magnitude to a similar DES magnitude using
+\begin{eqnarray}
+	g_{DES} = g_{SDSS} - 0.104(g-r)_{SDSS} + 0.01 \\
+	r_{DES} = r_{SDSS} - 0.102(g-r)_{SDSS} + 0.02
+\end{eqnarray}
+from \cite{Bechtol2015} and place each on a color-magnitude diagram (CMD) of $M_r$ and $g-r$, see Figure~\ref{fig:oii sdss}.
+To assign an [\ion{O}{ii}] luminosity to each galaxy in our catalog we place the catalog galaxies on the same CMD and select all SDSS galaxies in a small 2D ($M_r$, $g-r$) bin around the galaxy.
+We extract all of the SDSS galaxies inside that bin and create a histogram of their [\ion{O}{ii}] luminosities.
+Using a slice sampling technique \citep{Neal1997} we assign the catalog galaxy an [\ion{O}{ii}] luminosity based on the distribution of SDSS galaxies extracted.
+For catalog galaxies which are placed on the CMD near no, or very few ($1\leq n<10$) galaxies we assign it zero [\ion{O}{ii}] luminosity or the mean luminosity, respectively.
+
+The right panel of Figure~\ref{fig:oii sdss} shows the CMD of all SDSS galaxies.
+Two potential catalog galaxies are also placed on the CMD ($M_r, g-r = -17.7,~0.49$ and $M_r, g-r = -21.4,~1.24$) and indicated by two colored boxes.
+The histograms show in the Figure's left panel shows the probability density histograms of the Log [\ion{O}{ii}] luminosity for the SDSS galaxies in the 2D bin.
+We sample the distribution and assign each catalog galaxy an [\ion{O}{ii}] luminosity which is then converted into a flux.
+
 \section{RESULTS}
+Our results section is broken into two large sections.
+First we analyze our ability to recover cluster parameters from an observing strategy similar to that of HETDEX.
+In the second Section, we apply observational limits, similar to those expected to apply, and investigate how the parameter recovery improves (or worsens) under those conditions.
 
@@
 
+\subsubsection{Dynamical Properties}
 \begin{figure*} 
@@
 \end{figure*}
-
-\subsection{HETDEX Depth}
-
 Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
@@
 
+\subsubsection{Structural Properties}
+Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
+Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
+Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+
+\subsection{HETDEX Depth}
+
+\subsubsection{Dynamical Properties}
 \begin{figure*} 
@@
 \end{figure*}
+Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
+Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
+Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
 
-\subsubsection{\ion{O}{ii} Luminosity}
-HETDEX is designed to detect Lyman-$\alpha$ at redshift two.
-That allows us to detect \ion{O}{ii} emitters to $z\sim 0.49$.
-The catalog does not provide \ion{O}{ii} luminosities so we must assign them empirically.
-We use 177107 galaxies from the Sloan Digital Sky Survey (SDSS) Data Release 12 \citep{Alam2015} from $z = 0.05 - 0.2$.
-Galaxies are selected which have no redshift warning and have an \ion{O}{ii} flux five times greater than the \ion{O}{ii} flux error.
-
-\begin{figure} 
-	\includegraphics[width=0.49\textwidth]{oii_sdss.pdf} 
-	\caption{686184 $z<0.2$ galaxies} \label{fig:oii sdss} 
-\end{figure}
-
-We place each SDSS galaxy on a color-magnitude diagram (CMD) of $M_r$ and $g-r$, see Figure~\ref{fig:oii sdss}.
-To assign an \ion{O}{ii} luminosity to each galaxy in our catalog we place the galaxies on the same and select all SDSS galaxies in a small 2D bin around the galaxy.
-We extract all of the SDSS galaxies inside that bin and create a histogram of their \ion{O}{ii} luminosities.
-Using a slice sampling technique we assign the catalog galaxy an \ion{O}{ii} luminosity based on the distribution of SDSS galaxies extracted.
-
-\begin{figure}
-	\includegraphics[width=0.49\textwidth]{clustersCMD.pdf}
-	\caption{657916 galaxies}
-	\label{fig:oii clusters}
-\end{figure}
-
-For catalog galaxies which are placed on the CMD near no, or very few ($n<3$) galaxies we assign it zero \ion{O}{ii} luminosity or the mean luminosity, respectively.
-
-\begin{eqnarray}
-	g_{DES} = g_{SDSS} - 0.104*(g-r)_{SDSS} + 0.01 \\
-	r_{DES} = r_{SDSS} - 0.102*(g-r)_{SDSS} + 0.02
-\end{eqnarray}
+\subsubsection{Structural Properties}
+Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
+Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
+Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
 

### 2015-06-04 ms.tex
worked on aardvark section

@@
 It is not straightforward to use these data to interpret the kinematic and dynamical states of the clusters.
-DIRGES is covered by SDSS Stripe 82 (Annis et al.
-2014), the Dark Energy Survey (DES), and the Hobby Eberly Telescope Dark Energy eXperiment (HETDEX).
-One key is HETDEX, which is a spectroscopic survey covering $\sim$400 deg2 and measuring redshifts for as many as ∼106 emission-line galaxies at z $<$ 0.5.
-HETDEX will contain as many as 100 galaxy Virgo-sized clusters (Mdyn$\sim$1015 M⊙) out to z $<$ 0.5.
+DIRGES is covered by SDSS Stripe 82 \citep{Annis2014}, the Dark Energy Survey (DES), and the Hobby Eberly Telescope Dark Energy eXperiment (HETDEX).
+One key is HETDEX, which is a spectroscopic survey covering $\sim$400 deg$^2$ and measuring redshifts for as many as ∼106 emission-line galaxies at z $<$ 0.5.
+HETDEX will contain as many as 100 galaxy Virgo-sized clusters ($M_{dyn}\sim10^{15}\msol$) out to z $<$ 0.5.
 And, because HETDEX covers DIRGES, the data will contain both low-redshift and high-redshift clusters in the same imaging dataset, allowing the most homogeneous study of the low-z and high-z universe yet.
 
-\section{AARDVARK SIMULATION}
-\editorial{Waiting to get a look at what Casey comes up with for the proposal we are supposedly writing. If he does a decent job then I'll try to expand it a bit and fill out this section.}
+\editorial{This should probably go into the introduction.
+I don't think we need a whole section on something that a bunch of papers have already talked about.
+The text below is taken from Chiang 2015 and is NOT original to me.}
+
+The Hobby Eberly Telescope Dark Energy Experiment (HETDEX; \citealt{Hill2008}) is pioneering the instrumentation development and observations of high-redshift large scale structures using wide-field IFUs.
+In a 3-year baseline starting from late 2015, HETDEX will leverage the cosmic evolution of the dark energy equation of state with high redshift (z $>$ 2) constraints imprinted by the Baryon Acoustic Oscillations (BAO; Eisenstein 2005) in the early universe.
+The program will perform a redshift survey of LAEs in 300 deg2 (Spring field) plus 150 deg2 (Fall field) at 1.9 $<$ z $<$ 3.5 (with a filling factor of 1/4.5), with a total survey volume of $\sim$ 8.5 Gpc3.
+The survey uses the 10-m Hobby-Eberly Telescope (HET; \citealt{Ramsey1998}) with a wide-field upgrade to reach a 22x22 arcmin2 field-of-view.
+Blind spectroscopy (R $\sim$ 750 in $350–550$ nm) with no pre-selection of targets will be performed using the Visible Integral-Field Replicable Unit Spectrograph (VIRUS; \citealt{Hill2012}).
+With the LAE redshifts, HETDEX will pinpoint numerous locations of the highest density concentrations at 1.9 $<$ z $<$ 3.5, generating a substantially large and homogeneous sample of cluster progenitors in the key epoch of cluster formation before virialization.
+
+\section{Data and Observations}
+
+Blah blah intro stuff...
+
+\subsection{The ``Aardvark'' Catalogs}
 \begin{figure} 
@@
 
-\section{THE HETDEX SURVEY}\label{sec:Hetdex}
-\editorial{This should probably go into the introduction.
-I don't think we need a whole section on something that a bunch of papers have already talked about.
-The text below is taken from Chiang 2015 and is NOT original to me.}
+The ``Aardvark'' mock galaxy catalogs (R.
+Wechsler et al., private communication) are derived from a semi-analytical model (SAM) tied to the Bolshoi cosmological simulation \citep{Klypin2011} and designed for DES.
+They provide a 10313 sq.
+degree (one quarter of the sky) catalog to full DES depth and contains 1.36 billion galaxies which have a signal-to-noise of at least five in one or more DES observing bands.
+The catalog footprint is shown in Figure~\ref{fig:survey area}.
 
-The Hobby Eberly Telescope Dark Energy Experiment (HETDEX; Hill et al.
-2008b) is pioneering the instrumentation development and observations of high-redshift large scale structures using wide-field IFUs.
-In a 3-year baseline starting from late 2015, HETDEX will leverage the cosmic evolution of the dark energy equation of state with high redshift (z $>$ 2) constraints imprinted by the Baryon Acoustic Oscillations (BAO; Eisenstein 2005) in the early universe.
-The program will perform a redshift survey of LAEs in 300 deg2 (Spring field) plus 150 deg2 (Fall field) at 1.9 $<$ z $<$ 3.5 (with a filling factor of 1/4.5), with a total survey volume of $\sim$ 8.5 Gpc3.
-The survey uses the 10-m Hobby-Eberly Telescope (HET; Ramsey et al.
-1998) with a wide-field upgrade to reach a 22x22 arcmin2 field-of-view.
-Blind spectroscopy (R $\sim$ 750 in 350–550 nm) with no pre-selection of targets will be performed using the Visible Integral-Field Replicable Unit Spectrograph (VIRUS; Hill et al.
-2012, 2014).
-With the LAE redshifts, HETDEX will pinpoint numerous locations of the highest density concentrations at 1.9 $<$ z $<$ 3.5, generating a substantially large and homogeneous sample of cluster progenitors in the key epoch of cluster formation before virialization.
+A brief description of the catalog creation is described as follows.
+The initial conditions are generated with a second-order Lagrangian perturbation theory using {\tt2LPTic} \citep{Crocce2006}.
+Dark matter (DM) n-body simulations are run using {\tt LGadget-2} (a version of {\tt Gadget-2}; \citealt{Springel2005}), and four different light cones are stitched together along the line of sight to create the full light cone.
+The DM halos are identified using the {\tt ROCKSTAR} halo finder \citep{Behroozi2013} which also calculates halo masses and other various parameters.
+Galaxies are assigned to halos and subhalos using the ``ADDGals'' method of (R.
+Wechlar \etal, in preparation) which matches galaxy luminosities with local DM densities, not the individual DM halos.
+This becomes important in the velocity dispersion and subsequent dynamical mass recovery, see Section~\ref{sec:LOSVD}.
 
-\section{Mock Observations}
+The catalog information, used in this study, is broken into two large portions.
+The ``truth'' files contain the characteristics of each individual galaxies, such as right ascension (RA), declination (DEC), redshift (z), observed and rest-frame magnitudes, and many others.
+The ``halo'' files contain information for individual halos, to which many individual galaxies may belong.
+This includes five estimations of dynamical mass, RA, DEC, z, three dimensional velocity dispersion, and many others.
+
+However, the catalogs do not include information on emission or absorption lines or estimations of whether the halo is relaxed or not.
+We supplement the catalogs with this information and describe the method in Section~\ref{sec:oii luminosity} and others.
+
+\subsection{Mock Observations}
 \editorial{Here we need to talk about about how we set up the observations to look like what we think the HETDEX survey will see.
@@
 
-\subsection{Line of Sight Velocity Dispersion}
+\subsection{Line of Sight Velocity Dispersion}\label{sec:LOSVD}
 We first calculate the line of sight velocity (LOSV) to each galaxy, where
@@
 
-\subsection{Dynamical Mass}
+\subsection{Dynamical Mass}\label{sec:mass}
 Recently, the relationship between the LOSVD and dynamical mass has been the focus of several studies \citeeg{Evrard2008, Saro2013, Sifon2013, VanderBurg2014}, and a best fitting relationship for the mass enclosed by $r_{200c}$ of the form
@@
 
-\section{ {\rm[\ion{O}{ii}]} Luminosity}
+\section{ {\rm[\ion{O}{ii}]} Luminosity}\label{sec:oii luminosity}
 HETDEX is designed to detect Lyman-$\alpha$ at redshift two.

### 2015-06-05 ms.tex
worked on introduction

@@
 %Commands specific to the this work
-\newcommand{\editorial}[1]{\textcolor{red}{#1} }
+\newcommand{\editorial}[1]{\textcolor{red}{#1}}
 \DeclareRobustCommand{\ion}[2]{%
@@
 
-\shorttitle{HETDEX PAPER}
+\shorttitle{Cluster Dynamics with HETDEX}
 \shortauthors{BOADA ET AL.}
@@
 
-\title{HETDEX Paper}
+\title{Cluster Dynamics Using the Hobby Eberly Telescope Dark Energy Experiment}
 
 \author{\sc Steven Boada\altaffilmark{1}, 
-C.~Papovich\altaffilmark{1},
-R.~Wechsler\altaffilmark{2,3},
-E.~Rozo\altaffilmark{2,4},
-E.~Rykoff\altaffilmark{2,5}}
+C.~Papovich\altaffilmark{1}, and
+R.~Wechsler\altaffilmark{2,3}}
 
@@
 \altaffiltext{3}{Department of Particle Physics and Astrophysics, SLAC National Accelerator Laboratory, Menlo Park, CA 94025, USA}
-\altaffiltext{4}{Department of Astronomy, University of Chicago, Chicago, IL 60637, USA}
-\altaffiltext{5}{E. O. Lawrence Berkeley National Lab, 1 Cyclotron Road, Berkeley, CA 94720, USA}
 
@@
 \section{INTRODUCTION}
-\editorial{A lot of these words are taken from Casey's proposal to get more funding.}
+The Hobby Eberly Telescope Dark Energy eXperiment (HETDEX; \citealt{Hill2008}) is a trailblazing effort to observe high-redshift large scale structures using cutting edge wide-field integral field unit (IFU) spectrographs.
+Designed to probe the evolution of the dark energy equation of state etched onto high redshift ($z>2$) galaxies by the Baryon Acoustic Oscillations \citep{Eisenstein2005} in the first moments of the universe, the survey will observe two fields for a total of 420 \degsq\ from two fields (300 \degsq, Spring field and 120 \degsq, Fall field).
+Tuned to find \lya\ emitting (LAE) galaxies at $1.9<z<3.5$, HETDEX expects to find 800,000 LAEs, and more than one million [\ion{O}{ii}] emitting galaxies at $z<0.5$ masquerading as high-redshift galaxies.
+
+While a large portion of thee $\sim10^6$ interloping [\ion{O}{ii}] galaxies will be field (not associated with a larger structure) galaxies, the large area covered by HETDEX is expected to contain as many as 100 Virgo-sized ($M_{dyn}\sim 10^{15}$ \msol) clusters at $z<0.5$ (\editorial{citation?}).
+The near-complete spectroscopic coverage allows an unprecedentedly detailed look at a large number of clusters ranging from group scales to the very massive.
+In addition to the recovery of accurate dynamical masses, detailed investigations of the of dynamical state of the clusters is possible.
+
+In addition to the spectroscopy, an imaging campaign is require first identify galaxy over densities.
+HETDEX overlaps with the Sloan Digital Sky Survey (SDSS; \citealt{Blanton2001a}), SDSS strip 82 \citep{Annis2014}, the Dark Energy Survey \citep{DES2005}, and the upcoming DECam/IRAC Galaxy Environment Survey (DIRGES; PI: Papovich, C.
+Papovich \etal in preparation).
 
@@
 
-\editorial{This should probably go into the introduction.
-I don't think we need a whole section on something that a bunch of papers have already talked about.
-The text below is taken from Chiang 2015 and is NOT original to me.}
+\editorial{The text below is taken from Chiang 2015 and is NOT original to me.}
 
-The Hobby Eberly Telescope Dark Energy Experiment (HETDEX; \citealt{Hill2008}) is pioneering the instrumentation development and observations of high-redshift large scale structures using wide-field IFUs.
 In a 3-year baseline starting from late 2015, HETDEX will leverage the cosmic evolution of the dark energy equation of state with high redshift (z $>$ 2) constraints imprinted by the Baryon Acoustic Oscillations (BAO; Eisenstein 2005) in the early universe.
@@
 \subsection{Mock Observations}
-\editorial{Here we need to talk about about how we set up the observations to look like what we think the HETDEX survey will see.
-It should be more technical than the general discussion about what the survey hopes to accomplish, that'll go in the intro.
-A zoomed figure showing the tiling footprints would be appropriate.}
-
 \begin{figure} 
 	\includegraphics[width=0.49\textwidth]{f01.pdf} 
-	\caption{} \label{fig:ifu layout} 
+	\caption{Representative observation tiling scheme for the HETDEX $16'$ pointings.
+Each colored square is a single VIRUS IFU and the dashed octagons approximate the size of a single observation.
+See the text for more details.} \label{fig:ifu layout}
 \end{figure}
 
-\editorial{Should show some sort of a figure which demonstrates the number of recovered galaxies per halo compared to the true number of galaxies in each halo.
-Maybe even just a statement that the average number of galaxies is XXX and the average number recovered is XXX.}
+Our ``observations'' consist of placing masks down onto the aardvark catalogs and selecting all galaxies which lie underneath.
+Each mask is created to accurately reproduce the HETDEX IFU pattern, see Figure~\ref{fig:ifu layout}.
+The pattern consists of 78 IFUs, which are comprised of 448 optical fibers subtending a $50'' \times 50''$ region on the sky \citep{Kelz2014}.
+The inter-IFU spacing is also $50''$ spanning a total area of $16'\times 16'$ on the sky.
+
+The individual IFUs have a fill-factor of 1/3, which will be completely filled with three dithers of the telescope at each pointing.
+This means that when selecting galaxies from the aardvark catalog we assume an observation for all galaxies lying within a colored, IFU square in Figure~\ref{fig:ifu layout}.
+Galaxies which lie between the IFUs are missed, as well as the galaxies which lie between the pointings, as there is no overlap between one pointing and the next.
+This gives an overall fill-factor of 1/4.5, meaning that the entire area could be covered with 4.5 dithers of the entire survey.
 
@@
 Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+
+\acknowledgments 
+The authors also wish to thank the anonymous referee whose comments and
+suggestions significantly improved both the quality and clarity of this work.
+Several open source resources are used to complete this study Python \citep{van1991} along with Matplotlib \citep{Hunter2007} and IPython \citep{Perez2007}.
+
 \bibliography{master}

### 2015-06-10 ms.tex
updated
“finished” introduction, reorganized a bit, added section about
membership, and much more.

@@
 Designed to probe the evolution of the dark energy equation of state etched onto high redshift ($z>2$) galaxies by the Baryon Acoustic Oscillations \citep{Eisenstein2005} in the first moments of the universe, the survey will observe two fields for a total of 420 \degsq\ from two fields (300 \degsq, Spring field and 120 \degsq, Fall field).
-Tuned to find \lya\ emitting (LAE) galaxies at $1.9<z<3.5$, HETDEX expects to find 800,000 LAEs, and more than one million [\ion{O}{ii}] emitting galaxies at $z<0.5$ masquerading as high-redshift galaxies.
+Tuned to find \lya\ emitting (LAE) galaxies at $1.9<z<3.5$, HETDEX expects to find 800,000 LAEs, and more than one million [\ion{O}{ii}] emitting galaxies at $z<0.5$ masquerading as high-redshift galaxies \citep{Acquaviva2014}.
 
-While a large portion of thee $\sim10^6$ interloping [\ion{O}{ii}] galaxies will be field (not associated with a larger structure) galaxies, the large area covered by HETDEX is expected to contain as many as 100 Virgo-sized ($M_{dyn}\sim 10^{15}$ \msol) clusters at $z<0.5$ (\editorial{citation?}).
-The near-complete spectroscopic coverage allows an unprecedentedly detailed look at a large number of clusters ranging from group scales to the very massive.
+While a large portion of the $\sim10^6$ interloping [\ion{O}{ii}] galaxies will be field (not associated with a bound structure) galaxies, the large area covered by HETDEX is expected to contain as many as 100 Virgo-sized ($M_{dyn}\sim 10^{15}$ \msol) clusters at $z<0.5$ (\editorial{citation?}).
+The near-complete spectroscopic coverage allows an unprecedentedly detailed look at a very large number of clusters ranging from group scales to the very massive.
 In addition to the recovery of accurate dynamical masses, detailed investigations of the of dynamical state of the clusters is possible.
@@
 In addition to the spectroscopy, an imaging campaign is require first identify galaxy over densities.
-HETDEX overlaps with the Sloan Digital Sky Survey (SDSS; \citealt{Blanton2001a}), SDSS strip 82 \citep{Annis2014}, the Dark Energy Survey \citep{DES2005}, and the upcoming DECam/IRAC Galaxy Environment Survey (DIRGES; PI: Papovich, C.
+HETDEX overlaps with the Sloan Digital Sky Survey (SDSS; \citealt{Blanton2001a}), SDSS stripe 82 \citep{Annis2014}, the Dark Energy Survey (DES; \citealt{DES2005}), and the upcoming DECam/IRAC Galaxy Environment Survey (DIRGES; PI: Papovich, C.
 Papovich \etal in preparation).
 
-This support will allow Mr.
+DIRGES, in particular, will be useful as it will identify as many as 100 galaxy cluster progenitors at 0.8 $<$ z $<$ 1.5 based on similarities in galaxy \spitzer/IRAC colors.
+Significant gains in the understanding of these clusters are possible if we can (1) interpret their dynamical nature through spectroscopy, and (2) if we can link them to galaxy clusters at lower redshift, z $<$ 0.5, from within the same dataset to suppress potential observational biases.
+However, two large issues remain.
+
+It is unclear how a blind spectroscopic survey with an IFU will effect the recovery of galaxy cluster dynamical properties.
+Unlike many previous large cluster surveys \citeeg{Milvang-Jensen2008, Robotham2011, Sifon2015} which use multi-object spectrographs, the Visible Integral-Field Replicable Unit Spectrograph (VIRUS; \citealt{Hill2012}) used by HETDEX samples the sky unevenly which could excluded member galaxies which would otherwise be included.
+Secondly, it is not straightforward to use spectroscopic redshifts predominately from emission-line galaxies to interpret the kinematic and dynamical states of the clusters.
+
+This work plans to address these concerns in the following ways.
+Create and evaluate a HETDEX like selection ``function'' of galaxies over a similarly large portion of the sky, use well adopted techniques to recover the dynamical properties, such as velocity dispersion and mass, and to investigate the presence of substructure.
+This will better allow future work to predict the number and types of galaxy clusters which should be observed with HETDEX.
+
+\editorial{Give outline of paper section.}
+
+Throughout this paper, we adopt the following cosmological model ($\Omega_\Lambda = 0.77$,
+$\Omega_M = 0.23$, $\sigma_8 = 0.83$ and $H_0= 72$ \kms \mpc), assume a Chabrier initial mass function (IMF; \citealt{Chabrier2003}), and use AB magnitudes \citep{Oke1974}.
+
+%This support will allow Mr.
 Boada to contribute to the core science of my NSF grant (AST 1413317) for the DECam/IRAC Galaxy Environment Survey (DIRGES).
@@
 It is not straightforward to use these data to interpret the kinematic and dynamical states of the clusters.
-DIRGES is covered by SDSS Stripe 82 \citep{Annis2014}, the Dark Energy Survey (DES), and the Hobby Eberly Telescope Dark Energy eXperiment (HETDEX).
-One key is HETDEX, which is a spectroscopic survey covering $\sim$400 deg$^2$ and measuring redshifts for as many as ∼106 emission-line galaxies at z $<$ 0.5.
-HETDEX will contain as many as 100 galaxy Virgo-sized clusters ($M_{dyn}\sim10^{15}\msol$) out to z $<$ 0.5.
 And, because HETDEX covers DIRGES, the data will contain both low-redshift and high-redshift clusters in the same imaging dataset, allowing the most homogeneous study of the low-z and high-z universe yet.
-
-\editorial{The text below is taken from Chiang 2015 and is NOT original to me.}
-
-In a 3-year baseline starting from late 2015, HETDEX will leverage the cosmic evolution of the dark energy equation of state with high redshift (z $>$ 2) constraints imprinted by the Baryon Acoustic Oscillations (BAO; Eisenstein 2005) in the early universe.
-The program will perform a redshift survey of LAEs in 300 deg2 (Spring field) plus 150 deg2 (Fall field) at 1.9 $<$ z $<$ 3.5 (with a filling factor of 1/4.5), with a total survey volume of $\sim$ 8.5 Gpc3.
-The survey uses the 10-m Hobby-Eberly Telescope (HET; \citealt{Ramsey1998}) with a wide-field upgrade to reach a 22x22 arcmin2 field-of-view.
-Blind spectroscopy (R $\sim$ 750 in $350–550$ nm) with no pre-selection of targets will be performed using the Visible Integral-Field Replicable Unit Spectrograph (VIRUS; \citealt{Hill2012}).
-With the LAE redshifts, HETDEX will pinpoint numerous locations of the highest density concentrations at 1.9 $<$ z $<$ 3.5, generating a substantially large and homogeneous sample of cluster progenitors in the key epoch of cluster formation before virialization.
 
@@
 The ``Aardvark'' mock galaxy catalogs (R.
-Wechsler et al., private communication) are derived from a semi-analytical model (SAM) tied to the Bolshoi cosmological simulation \citep{Klypin2011} and designed for DES.
-They provide a 10313 sq.
-degree (one quarter of the sky) catalog to full DES depth and contains 1.36 billion galaxies which have a signal-to-noise of at least five in one or more DES observing bands.
+Wechsler et al., private communication) are derived from a semi-analytical model (SAM) tied to an in house n-body cosmological simulation and designed for DES.
+They provide a 10313 \degsq (one quarter of the sky) catalog to full DES depth and contains 1.36 billion galaxies which have a signal-to-noise of at least five in one or more DES observing bands.
 The catalog footprint is shown in Figure~\ref{fig:survey area}.
@@
 
-\subsection{Mock Observations}
+\subsection{ {\rm[\ion{O}{ii}]} Luminosity}\label{sec:oii luminosity}
+The aardvark ``truth'' catalog does not provide [\ion{O}{ii}] luminosities so we must assign them empirically.
+We use 503113 galaxies from the SDSS Data Release 12 \citep{Alam2015} from $z = 0.05 - 0.2$, which are selected with no redshift warning.
+
+\begin{figure*} 
+	\includegraphics[width=\textwidth]{oii_sdss.pdf} 
+	\caption{\textit{Left}: CMD of 503113 $z<0.2$ galaxies take from the SDSS DR12 where the shading scales with the density of points.
+The two boxes show regions containing potential catalog galaxies.
+\textit{Right}: Probability histograms of the Log [\ion{O}{ii}] luminosity for the SDSS galaxies located in the two highlighted regions on the right.
+New [\ion{O}{ii}] luminosity (and subsequently fluxes) are assigned to catalog galaxies from slice sampling the probability histogram.} \label{fig:oii sdss}
+\end{figure*}
+
+While the difference is small, we convert each SDSS galaxy's observed magnitude to a similar DES magnitude using
+\begin{eqnarray}
+	g_{DES} = g_{SDSS} - 0.104(g-r)_{SDSS} + 0.01 \nonumber \\
+	r_{DES} = r_{SDSS} - 0.102(g-r)_{SDSS} + 0.02
+\end{eqnarray}
+from \cite{Bechtol2015} and place each on a color-magnitude diagram (CMD) of $M_r$ and $g-r$, see Figure~\ref{fig:oii sdss}.
+To assign an [\ion{O}{ii}] luminosity to each galaxy in our catalog we place the catalog galaxies on the same CMD and select all SDSS galaxies in a small 2D ($M_r$, $g-r$) bin around the galaxy.
+We extract all of the SDSS galaxies inside that bin and create a histogram of their [\ion{O}{ii}] luminosities.
+Using a slice sampling technique \citep{Neal1997} we assign the catalog galaxy an [\ion{O}{ii}] luminosity based on the distribution of SDSS galaxies extracted.
+For catalog galaxies which are placed on the CMD near no, or very few ($1\leq n<10$) galaxies we assign it zero [\ion{O}{ii}] luminosity or the mean luminosity, respectively.
+
+The right panel of Figure~\ref{fig:oii sdss} shows the CMD of all SDSS galaxies.
+Two potential catalog galaxies are also placed on the CMD ($M_r, g-r = -17.7,~0.49$ and $M_r, g-r = -21.4,~1.24$) and indicated by two colored boxes.
+The histograms show in the Figure's left panel shows the probability density histograms of the Log [\ion{O}{ii}] luminosity for the SDSS galaxies in the 2D bin.
+We sample the distribution and assign each catalog galaxy an [\ion{O}{ii}] luminosity which is then converted into a flux.
+
+\subsection{Mock Observations}\label{sec:observations}
+\editorial{don't think I say what are the actual selection criteria for the spectroscopy. That's an important detail.}
+Tentatively slated to start in the fall of 2015, HETDEX will perform blind spectroscopy (R $\sim$ 750 in $3500 - 5500~\AAA$) over two fields along the celestial equator.
+The 300 \degsq, Spring field and 120 \degsq, Fall field will have no preselected targets.
+Using VIRUS on the 10-m Hobby-Eberly Telescope (HET; \citealt{Ramsey1998}) the completed survey is expected to have an overall fill-factor of 1/4.5, meaning that the entire area could be covered with 4.5 dithers of the entire survey.
+
+The spectral coverage allows for the detection of [\ion{O}{ii}] ($\lambda\lambda 3727-3729~\AAA$ doublet) emitters to $z\sim 0.5$ and Ca H ($\lambda 3968.5~\AAA$) and K ($\lambda 3933.7~\AAA$) absorption features to $z\sim 0.4$.
+HETDEX is expected to detect sources with continuum brighter than 22 mag in SDSS \sdssg, and emission line strengths above $3.5\times10^{-17}$ \ergscm.
+So we ``observe'' $z<0.4$ galaxies which meet either the emission line or the magnitude limit.
+Galaxies $0.4<z<0.5$ are only observed if their emission line strength is sufficient.
+
 \begin{figure} 
@@
 
-Our ``observations'' consist of placing masks down onto the aardvark catalogs and selecting all galaxies which lie underneath.
+Our ``observations'' consist of placing masks down onto the aardvark ``truth'' catalogs and selecting all, $z< 0.5$ also meeting sensitivity limits, galaxies which lie underneath.
 Each mask is created to accurately reproduce the HETDEX IFU pattern, see Figure~\ref{fig:ifu layout}.
@@
 The individual IFUs have a fill-factor of 1/3, which will be completely filled with three dithers of the telescope at each pointing.
-This means that when selecting galaxies from the aardvark catalog we assume an observation for all galaxies lying within a colored, IFU square in Figure~\ref{fig:ifu layout}.
+This means that when selecting galaxies from the aardvark catalog we assume an observation for all galaxies laying within a colored, IFU square in Figure~\ref{fig:ifu layout}.
 Galaxies which lie between the IFUs are missed, as well as the galaxies which lie between the pointings, as there is no overlap between one pointing and the next.
-This gives an overall fill-factor of 1/4.5, meaning that the entire area could be covered with 4.5 dithers of the entire survey.
+
+\section{Cluster Membership}
+In the following sections we assume that the on sky positions and redshifts of the galaxy clusters are already known.
+In reality, galaxy over densities will be detected from imaging surveys \citeeg{Rykoff2014} or through techniques to identify structure in the RA, DEC, z point data (\eg, DBSCAN; \citealt{Ester1996}).
+
+While the galaxy cluster center may be well known, the constituent galaxies will not.
+The identification of member galaxies from photometric data \citeeg{Rozo2014} is promising, however, with spectroscopic information on all galaxies, we choose to utilize the full 3D parameter space.
+\editorial{Not very happy about that sentence}.
+
+We employ the ``shifting gapped" method of \cite{Fadda1996} as outlined in \cite{Owers2011}, which combines both the positional and velocity information.
+After an initial cut of $cz_c \pm 10,000$ \kms, the galaxies are binned in $0.4h^{-1}$ Mpc or larger enough bins to contain at least 10 (arbitrarily chosen) galaxies.
+Galaxies farther than 3 Mpc from the cluster center are also rejected.
+Once binned, the galaxies are sorted by their line-of-sight velocity (LOSV; see Section~\ref{sec:LOSVD}).
+Any galaxy with a LOSV greater than 1000 \kms of a neighboring galaxy is rejected as an interloper.
+The procedure repeats until the number of galaxies stabilizes in the bin.
+
+\editorial{This is taken from the other paper, and needs to be tweaked to make fit better into this framework.
+I think what we'll do is center a 100'' box on all of the clusters and then try to recover the galaxies.
+How many will we get, how many are wrong, and can we do better with a different algorithm?}
 
 \section{Recovery of Parameters}
-
-Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+ In the following sections, we outline the methods we use to derive the dynamical properties of the galaxy clusters in our sample.
+This is not meant to be an exhaustive study of the different methods used to recover these parameters.
+The following is, in many cases, a subset of the available methods to derive any single parameter.
+The specific choice of method may improve or diminish the accuracy of the recovered parameter, but the methods chosen were to facilitate comparison with observational studies.
 
@@
 The first is due to the nature of our observations.
-Because the HETDEX survey has a 1/4.5 fill factor (see Section~\ref{sec:Hetdex}), there will be many situations where we will not have full spectroscopic information for a cluster.
+Because the HETDEX survey has a 1/4.5 fill factor (see Section~\ref{sec:observations}), there will be many situations where we will not have full spectroscopic information for a cluster.
 Some clusters could also have intrinsic velocity distributions where the observations of only a few members could result in a LOSVD which differs by large percent.
@@
 \section{Evidence of Substructure}
-Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+Like the recovery of dynamical parameters discussed in the previous section, the choice of method to investigate the dynamical state of galaxy clusters is heavily debated.
+Perhaps the most widely used metric is the Dressler-Shectman (DS) test \citep{Dressler1988}, and is not without criticism \citeeg{White2010}.
+New methods such as the Caustic Method (\citealt{Yu2015}, and the references therein) offer promise to shed further light on this difficult problem.
 
@@
 We leverage the large spectroscopic dataset to study the structural properties of the clusters.
-\cite{Pinkney1996} determine, from a comparison of five different methods that the Dressler-Shectman (DS) test \citep{Dressler1988} is the most sensitive to the presence of substructure.
+\cite{Pinkney1996} determine, from a comparison of five different methods that the DS test is the most sensitive to the presence of substructure.
 
@@
 In practice, we use locate the nearest neighbors using an unsupervised k-nearest neighbor algorithm as implemented in Scikit-Learn \citep{Pedregosa2012}.
-
-\section{ {\rm[\ion{O}{ii}]} Luminosity}\label{sec:oii luminosity}
-HETDEX is designed to detect Lyman-$\alpha$ at redshift two.
-That allows us to detect [\ion{O}{ii}] ($\lambda\lambda 3727-3729\AAA$ doublet) emitters to $z\sim 0.49$.
-The catalog does not provide [\ion{O}{ii}] luminosities so we must assign them empirically.
-We use 503113 galaxies from the Sloan Digital Sky Survey (SDSS) Data Release 12 \citep{Alam2015} from $z = 0.05 - 0.2$, which are selected which have no redshift warning.
-
-\begin{figure*} 
-	\includegraphics[width=\textwidth]{oii_sdss.pdf} 
-	\caption{\textit{Left}: CMD of 503113 $z<0.2$ galaxies take from the SDSS DR12 where the shading scales with the density of points.
-The two boxes show regions containing potential catalog galaxies.
-\textit{Right}: Probability histograms of the Log [\ion{O}{ii}] luminosity for the SDSS galaxies located in the two highlighted regions on the right.
-New [\ion{O}{ii}] luminosity (and subsequently fluxes) are assigned to catalog galaxies from slice sampling the probability histogram.} \label{fig:oii sdss}
-\end{figure*}
-
-While the difference is small, we convert each SDSS galaxy's observed magnitude to a similar DES magnitude using
-\begin{eqnarray}
-	g_{DES} = g_{SDSS} - 0.104(g-r)_{SDSS} + 0.01 \\
-	r_{DES} = r_{SDSS} - 0.102(g-r)_{SDSS} + 0.02
-\end{eqnarray}
-from \cite{Bechtol2015} and place each on a color-magnitude diagram (CMD) of $M_r$ and $g-r$, see Figure~\ref{fig:oii sdss}.
-To assign an [\ion{O}{ii}] luminosity to each galaxy in our catalog we place the catalog galaxies on the same CMD and select all SDSS galaxies in a small 2D ($M_r$, $g-r$) bin around the galaxy.
-We extract all of the SDSS galaxies inside that bin and create a histogram of their [\ion{O}{ii}] luminosities.
-Using a slice sampling technique \citep{Neal1997} we assign the catalog galaxy an [\ion{O}{ii}] luminosity based on the distribution of SDSS galaxies extracted.
-For catalog galaxies which are placed on the CMD near no, or very few ($1\leq n<10$) galaxies we assign it zero [\ion{O}{ii}] luminosity or the mean luminosity, respectively.
-
-The right panel of Figure~\ref{fig:oii sdss} shows the CMD of all SDSS galaxies.
-Two potential catalog galaxies are also placed on the CMD ($M_r, g-r = -17.7,~0.49$ and $M_r, g-r = -21.4,~1.24$) and indicated by two colored boxes.
-The histograms show in the Figure's left panel shows the probability density histograms of the Log [\ion{O}{ii}] luminosity for the SDSS galaxies in the 2D bin.
-We sample the distribution and assign each catalog galaxy an [\ion{O}{ii}] luminosity which is then converted into a flux.
 

### 2015-07-09 ms.tex
continued work

@@
 \newcommand{\editorial}[1]{\textcolor{red}{#1}}
-\DeclareRobustCommand{\ion}[2]{%
-\relax\ifmmode
-\ifx\testbx\f@series
-{\mathbf{#1\,\mathsc{#2}}}\else
-{\mathrm{#1\,\mathsc{#2}}}\fi
-\else\textup{#1\,{\mdseries\textsc{#2}}}%
-\fi}
-
-\newcommand{\citeeg}[1]{(\eg, \citealt{#1})}
 
@@
 Designed to probe the evolution of the dark energy equation of state etched onto high redshift ($z>2$) galaxies by the Baryon Acoustic Oscillations \citep{Eisenstein2005} in the first moments of the universe, the survey will observe two fields for a total of 420 \degsq\ from two fields (300 \degsq, Spring field and 120 \degsq, Fall field).
-Tuned to find \lya\ emitting (LAE) galaxies at $1.9<z<3.5$, HETDEX expects to find 800,000 LAEs, and more than one million [\ion{O}{ii}] emitting galaxies at $z<0.5$ masquerading as high-redshift galaxies \citep{Acquaviva2014}.
+Tuned to find \lya\ emitting (LAE) galaxies at $1.9<z<3.5$, HETDEX expects to find 800,000 LAEs, and more than one million [\ion{O}{2}] emitting galaxies at $z<0.5$ masquerading as high-redshift galaxies \citep{Acquaviva2014}.
 
-While a large portion of the $\sim10^6$ interloping [\ion{O}{ii}] galaxies will be field (not associated with a bound structure) galaxies, the large area covered by HETDEX is expected to contain as many as 100 Virgo-sized ($M_{dyn}\sim 10^{15}$ \msol) clusters at $z<0.5$ (\editorial{citation?}).
+While a large portion of the $\sim10^6$ interloping [\ion{O}{2}] galaxies will be field (not associated with a bound structure) galaxies, the large area covered by HETDEX is expected to contain as many as 100 Virgo-sized ($M_{dyn}\sim 10^{15}$ \msol) clusters at $z<0.5$ (\editorial{citation?}).
 The near-complete spectroscopic coverage allows an unprecedentedly detailed look at a very large number of clusters ranging from group scales to the very massive.
@@
 
-\subsection{ {\rm[\ion{O}{ii}]} Luminosity}\label{sec:oii luminosity}
-The aardvark ``truth'' catalog does not provide [\ion{O}{ii}] luminosities so we must assign them empirically.
+\subsection{ {\rm[\ion{O}{2}]} Luminosity}\label{sec:oii luminosity}
+The aardvark ``truth'' catalog does not provide [\ion{O}{2}] luminosities so we must assign them empirically.
 We use 503113 galaxies from the SDSS Data Release 12 \citep{Alam2015} from $z = 0.05 - 0.2$, which are selected with no redshift warning.
@@
 The two boxes show regions containing potential catalog galaxies.
-\textit{Right}: Probability histograms of the Log [\ion{O}{ii}] luminosity for the SDSS galaxies located in the two highlighted regions on the right.
-New [\ion{O}{ii}] luminosity (and subsequently fluxes) are assigned to catalog galaxies from slice sampling the probability histogram.} \label{fig:oii sdss}
+\textit{Right}: Probability histograms of the Log [\ion{O}{2}] luminosity for the SDSS galaxies located in the two highlighted regions on the right.
+New [\ion{O}{2}] luminosity (and subsequently fluxes) are assigned to catalog galaxies from slice sampling the probability histogram.} \label{fig:oii sdss}
 \end{figure*}
@@
 from \cite{Bechtol2015} and place each on a color-magnitude diagram (CMD) of $M_r$ and $g-r$, see Figure~\ref{fig:oii sdss}.
-To assign an [\ion{O}{ii}] luminosity to each galaxy in our catalog we place the catalog galaxies on the same CMD and select all SDSS galaxies in a small 2D ($M_r$, $g-r$) bin around the galaxy.
-We extract all of the SDSS galaxies inside that bin and create a histogram of their [\ion{O}{ii}] luminosities.
-Using a slice sampling technique \citep{Neal1997} we assign the catalog galaxy an [\ion{O}{ii}] luminosity based on the distribution of SDSS galaxies extracted.
-For catalog galaxies which are placed on the CMD near no, or very few ($1\leq n<10$) galaxies we assign it zero [\ion{O}{ii}] luminosity or the mean luminosity, respectively.
+To assign an [\ion{O}{2}] luminosity to each galaxy in our catalog we place the catalog galaxies on the same CMD and select all SDSS galaxies in a small 2D ($M_r$, $g-r$) bin around the galaxy.
+We extract all of the SDSS galaxies inside that bin and create a histogram of their [\ion{O}{2}] luminosities.
+Using a slice sampling technique \citep{Neal1997} we assign the catalog galaxy an [\ion{O}{2}] luminosity based on the distribution of SDSS galaxies extracted.
+For catalog galaxies which are placed on the CMD near no, or very few ($1\leq n<10$) galaxies we assign it zero [\ion{O}{2}] luminosity or the mean luminosity, respectively.
 
@@
 Two potential catalog galaxies are also placed on the CMD ($M_r, g-r = -17.7,~0.49$ and $M_r, g-r = -21.4,~1.24$) and indicated by two colored boxes.
-The histograms show in the Figure's left panel shows the probability density histograms of the Log [\ion{O}{ii}] luminosity for the SDSS galaxies in the 2D bin.
-We sample the distribution and assign each catalog galaxy an [\ion{O}{ii}] luminosity which is then converted into a flux.
+The histograms show in the Figure's left panel shows the probability density histograms of the Log [\ion{O}{2}] luminosity for the SDSS galaxies in the 2D bin.
+We sample the distribution and assign each catalog galaxy an [\ion{O}{2}] luminosity which is then converted into a flux.
 
@@
 
-The spectral coverage allows for the detection of [\ion{O}{ii}] ($\lambda\lambda 3727-3729~\AAA$ doublet) emitters to $z\sim 0.5$ and Ca H ($\lambda 3968.5~\AAA$) and K ($\lambda 3933.7~\AAA$) absorption features to $z\sim 0.4$.
+The spectral coverage allows for the detection of [\ion{O}{2}] ($\lambda\lambda 3727-3729~\AAA$ doublet) emitters to $z\sim 0.5$ and Ca H ($\lambda 3968.5~\AAA$) and K ($\lambda 3933.7~\AAA$) absorption features to $z\sim 0.4$.
 HETDEX is expected to detect sources with continuum brighter than 22 mag in SDSS \sdssg, and emission line strengths above $3.5\times10^{-17}$ \ergscm.

### 2015-09-01 ms.tex
reoganized
started on the new version

--- 2015-06-10 ms.tex
@@
 
-\newcommand{\citeeg}[1]{(\eg, \citealt{#1})}
-
 %-----------------------------------------------------------------------------------------
@@
 
-\title{Cluster Dynamics Using the Hobby Eberly Telescope Dark Energy Experiment}
+\title{Cluster Dynamics with HETDEX - I: Mass Distribution and Limits}
 
@@
 \section{INTRODUCTION}
+Our ability to perform precision cosmology with clusters of galaxies has reached a critical turning point.
+The widely accepted $\Lambda$CDM model of cosmology makes explicit predictions about the number and masses of galaxy clusters throughout the universe.
+However, connecting these predictions to a set of, sufficiently large in size, observed clusters remains a principal problem.
+Specifically, the largest threat to modern, precision, cluster cosmology is not the identification of large numbers of clusters (the total number of clusters known is only going up) but the accurate recovery of galaxy cluster mass.
+
+As mass is not a direct observable, a lot of work is underway to characterize galaxy cluster masses with an observable feature of galaxy clusters.
+The goal is to constrain, as best possible, $P(X|M,z)$ the probability ($P$) that a galaxy cluster of given mass ($M$), located at redshift ($z$) determined using observable parameter ($X$).
+The observable parameter most commonly observed X-ray temperatures and luminosities \citeeg{Mantz2010, Rykoff2014, Mantz2015}, cosmic microwave background observations \citeeg{Vanderlinde2010, Sehgal2011} using the Sunyaev--Zel’dovich effect (SZE; \citealt{Sunyaev1972}) or optical studies \citeeg{Rozo2010, Rozo2014} of richness \citeeg{Abell1958,Rykoff2012} or galaxy velocity dispersions \citeeg{Ruel2014, Sifon2015}.
+
 The Hobby Eberly Telescope Dark Energy eXperiment (HETDEX; \citealt{Hill2008}) is a trailblazing effort to observe high-redshift large scale structures using cutting edge wide-field integral field unit (IFU) spectrographs.
@@
 
-\section{Data and Observations}
+\section{Data and Mock Observations}
 
@@
 
-\subsection{The ``Aardvark'' Catalogs}
-\begin{figure} 
-	\includegraphics[width=0.49\textwidth]{surveyArea.pdf} 
-	\caption{A polar azimuthal equidistant projection of the southern sky showing the sky area (approximately a quarter of the sky) covered by the Aardvark Simulations.
-Concentric circles are lines of constant declination, 10 to $-80\degree$ in $10\degree$ increments.
-Radial lines are lines of constant right ascension.
-Opaqueness of the region indicates the overlap of catalog tiles (see text for details).}
-	\label{fig:survey area} 
-\end{figure}
+\subsection{The ``Buzzard'' Catalogs}
+The ``Buzzard'' mock galaxy catalogs (R.
+Wechsler et al., private communication) are derived from a combination of Sub-halo Abundance Matching (ShAM) and ADDSEDs (Adding Density Dependent Spectral Energy Distributions) tied to an in house n-body cosmological simulation.
+A brief description of the catalog creation is described as follows.
+The initial conditions are generated with a second-order Lagrangian perturbation theory using {\tt 2LPTic} \citep{Crocce2006}.
+Dark matter (DM) n-body simulations are run using {\tt LGadget-2} (a version of {\tt Gadget-2}; \citealt{Springel2005}).
+The DM halos are identified using the {\tt ROCKSTAR} halo finder \citep{Behroozi2013} which also calculates halo masses and other various parameters.
 
-The ``Aardvark'' mock galaxy catalogs (R.
-Wechsler et al., private communication) are derived from a semi-analytical model (SAM) tied to an in house n-body cosmological simulation and designed for DES.
-They provide a 10313 \degsq (one quarter of the sky) catalog to full DES depth and contains 1.36 billion galaxies which have a signal-to-noise of at least five in one or more DES observing bands.
-The catalog footprint is shown in Figure~\ref{fig:survey area}.
-
-A brief description of the catalog creation is described as follows.
-The initial conditions are generated with a second-order Lagrangian perturbation theory using {\tt2LPTic} \citep{Crocce2006}.
-Dark matter (DM) n-body simulations are run using {\tt LGadget-2} (a version of {\tt Gadget-2}; \citealt{Springel2005}), and four different light cones are stitched together along the line of sight to create the full light cone.
-The DM halos are identified using the {\tt ROCKSTAR} halo finder \citep{Behroozi2013} which also calculates halo masses and other various parameters.
-Galaxies are assigned to halos and subhalos using the ``ADDGals'' method of (R.
-Wechlar \etal, in preparation) which matches galaxy luminosities with local DM densities, not the individual DM halos.
-This becomes important in the velocity dispersion and subsequent dynamical mass recovery, see Section~\ref{sec:LOSVD}.
+Galaxy $M_r$ luminosities are added to the velocity peaks using ShAM \citep{Reddick2013}, and ADDSEDs (Adding Density Dependent Spectral Energy Distributions) assign luminosities in the other bands.
+A $M_r$-density-SED relation is created using a SDSS training set, and for each mock galaxy the SED of a randomly selected training set galaxy which has a similar $M_r$ and density is assigned.
+The result is a 398.49 sq.
+degree mock catalog occupying a $60 \leq RA \leq 90$ and $-40 \leq DEC \leq -61$ portion of the sky.
+It contains 238 million galaxies with \sdssr\ mag $< 29$ and $z \leq 8.7$.
 
@@
 
+\begin{figure} 
+	\includegraphics[width=0.49\textwidth]{hmf.pdf} 
+	\caption{The cumulative MF of halos above $M_{200c}$ at $z=0.1$. The predicted MF is from \cite{Tinker2008}.} 
+	\label{fig:hmf} 
+\end{figure}
+
+We investigate the accuracy of the halo mass distribution by comparing the cumulative number density of halos above a mass ($M_{200c}$) threshold to the halo mass function (HMF) of \cite{Tinker2008}.
+Shown in Figure~\ref{fig:hmf} the HMF is calculated at central redshifts of 0, 0.2, and 0.4 using {\tt HMFcalc} \citep{Murray2013} and compared to galaxies in a redshift window of $\Delta z\pm0.01$.
+We find a very good agreement between the expected HMF and the observed.
+
 \subsection{ {\rm[\ion{O}{ii}]} Luminosity}\label{sec:oii luminosity}
-The aardvark ``truth'' catalog does not provide [\ion{O}{ii}] luminosities so we must assign them empirically.
-We use 503113 galaxies from the SDSS Data Release 12 \citep{Alam2015} from $z = 0.05 - 0.2$, which are selected with no redshift warning.
-
 \begin{figure*} 
@@
 The two boxes show regions containing potential catalog galaxies.
-\textit{Right}: Probability histograms of the Log [\ion{O}{ii}] luminosity for the SDSS galaxies located in the two highlighted regions on the right.
+\textit{Right}: Probability histograms of the Log [\ion{O}{2}] luminosity for the SDSS galaxies located in the two highlighted regions on the right.
 New [\ion{O}{ii}] luminosity (and subsequently fluxes) are assigned to catalog galaxies from slice sampling the probability histogram.} \label{fig:oii sdss}
@@
 
-While the difference is small, we convert each SDSS galaxy's observed magnitude to a similar DES magnitude using
-\begin{eqnarray}
-	g_{DES} = g_{SDSS} - 0.104(g-r)_{SDSS} + 0.01 \nonumber \\
-	r_{DES} = r_{SDSS} - 0.102(g-r)_{SDSS} + 0.02
-\end{eqnarray}
-from \cite{Bechtol2015} and place each on a color-magnitude diagram (CMD) of $M_r$ and $g-r$, see Figure~\ref{fig:oii sdss}.
+The buzzard ``truth'' catalog does not provide [\ion{O}{ii}] luminosities so we must assign them empirically.
+We use 503113 galaxies from the SDSS Data Release 12 \citep{Alam2015} from $z = 0.05 - 0.2$, which are selected with no redshift warning, and place each galaxy on a color-magnitude diagram (CMD) of $M_r$ and $g-r$, see Figure~\ref{fig:oii sdss}.
+
 To assign an [\ion{O}{ii}] luminosity to each galaxy in our catalog we place the catalog galaxies on the same CMD and select all SDSS galaxies in a small 2D ($M_r$, $g-r$) bin around the galaxy.
@@
 \subsection{Mock Observations}\label{sec:observations}
-\editorial{don't think I say what are the actual selection criteria for the spectroscopy. That's an important detail.}
+\editorial{Not sure this does a good enough job talking about the two different observations.}
 Tentatively slated to start in the fall of 2015, HETDEX will perform blind spectroscopy (R $\sim$ 750 in $3500 - 5500~\AAA$) over two fields along the celestial equator.
@@
 The spectral coverage allows for the detection of [\ion{O}{ii}] ($\lambda\lambda 3727-3729~\AAA$ doublet) emitters to $z\sim 0.5$ and Ca H ($\lambda 3968.5~\AAA$) and K ($\lambda 3933.7~\AAA$) absorption features to $z\sim 0.4$.
-HETDEX is expected to detect sources with continuum brighter than 22 mag in SDSS \sdssg, and emission line strengths above $3.5\times10^{-17}$ \ergscm.
+HETDEX is expected to detect sources with continuum brighter than 22 mag in \sdssg, and emission line strengths above $3.5\times10^{-17}$ \ergscm.
 So we ``observe'' $z<0.4$ galaxies which meet either the emission line or the magnitude limit.
@@
 
-Our ``observations'' consist of placing masks down onto the aardvark ``truth'' catalogs and selecting all, $z< 0.5$ also meeting sensitivity limits, galaxies which lie underneath.
+In this work we consider two separate observation cases.
+The first are targeted observations where we select each galaxy cluster and ``observe'' each galaxy within $8'$ of the center.
+The second is a survey case where observations which are blind to the positions of the clusters are conducted.
+In both cases, our ``observations'' consist of placing masks down onto the buzzard ``truth'' catalogs and selecting all, $z< 0.5$ also meeting sensitivity limits, galaxies which lie underneath.
 Each mask is created to accurately reproduce the HETDEX IFU pattern, see Figure~\ref{fig:ifu layout}.
@@
 The individual IFUs have a fill-factor of 1/3, which will be completely filled with three dithers of the telescope at each pointing.
-This means that when selecting galaxies from the aardvark catalog we assume an observation for all galaxies laying within a colored, IFU square in Figure~\ref{fig:ifu layout}.
+This means that when selecting galaxies from the buzzard catalog we assume an observation for all galaxies laying within a colored, IFU square in Figure~\ref{fig:ifu layout}.
 Galaxies which lie between the IFUs are missed, as well as the galaxies which lie between the pointings, as there is no overlap between one pointing and the next.
@@
 
-\section{Evidence of Substructure}
-Like the recovery of dynamical parameters discussed in the previous section, the choice of method to investigate the dynamical state of galaxy clusters is heavily debated.
-Perhaps the most widely used metric is the Dressler-Shectman (DS) test \citep{Dressler1988}, and is not without criticism \citeeg{White2010}.
-New methods such as the Caustic Method (\citealt{Yu2015}, and the references therein) offer promise to shed further light on this difficult problem.
-
-\subsection{From VD profiles}
-We utilize the modality \citep{Oliva-Altamirano2014} which describes the Gaussianity of a LOSV distribution in a galaxy cluster.
-For clusters with Gaussian distributed LOSVs, the modality is close to 1/3.
-It is defined as $(1+\mathrm{skewness}^2)/(3+\mathrm{kurtosis}^2)$.
-\editorial{Do I need to describe what the skewness and kurtosis is?}
-
-\subsection{Dominance}
-\editorial{This is taken pretty directly from the GAMA paper. Will need to be edited to fit.}
-The dominance is defined as the luminosity gap between the brightest and the second brightest galaxy in a cluster ($\Delta m_{1, 2}$).
-The amplitude of the luminosity gap between the BGG/BCG and the second brightest galaxy in the halo, is expected to be a function of both the formation epoch and the recent infall history of the halo.
-A small magnitude gap ($\Delta m_{1, 2} < 1$) indicates a recent halo merger, and larger gaps ($\Delta m_{1, 2} > 1$), common in fossil groups, is perhaps indicative of a cluster or groups that has not undergone a recent merger.
-
-\subsection{Dressler-Schectman Test}
-We leverage the large spectroscopic dataset to study the structural properties of the clusters.
-\cite{Pinkney1996} determine, from a comparison of five different methods that the DS test is the most sensitive to the presence of substructure.
-
-The DS test, which combines the spatial positions and velocities of the galaxies, provides a method to locate substructure by identifying groups of galaxies which differ significantly from the cluster velocity distribution.
-Galaxy subsets are selected from a cluster of $n_{members}$ and each constituent galaxy deviation is calculated according to
-\begin{equation}
-	\delta_i^2 = \frac{N_{local}+1}{\sigma^2}\bigg{[}(\bar{v}_{local,i} - \bar{v})^2 + (\sigma_{local,i} - \sigma)^2\bigg{]}^2
-\end{equation}
-where $\bar{v}_{local}$ and $\sigma_{local}$ are the mean velocity and velocity dispersion for a subset of $N_{local}$ galaxies and $\bar{v}$ and $\sigma$ are the entire cluster's mean velocity and velocity dispersion.
-The choice of $N_{local}$ is left to the user.
-Originally, \cite{Dressler1988} choose $N_{local}=10$, however \cite{Bird1994} points out that using a fixed value for $N_{local}$ reduces the sensitivity to substructure.
-We follow \cite{Bird1994} in choosing $N_{local} = \sqrt n_{members}$.
-\editorial{doesn't talk about the nearest neighbors which is what we are using.}
-
-The DS statistic is the $\Delta$-value given by, 
-\begin{equation}
-	\Delta = \sum^{n_{members}}_i \delta_i
-\end{equation}
-where a system is considered to contain substructure if $\Delta/n_{members} > 1$ \citep{Dressler1988}.
-A second method, described in \cite{Hou2012}, uses probabilities (P-values) rather than a threshold for the identification of substructure.
-P-values are computed by comparing the observed $\Delta$-value and the $Delta$-value after the velocities (but not positions) have been shuffled through a series of Monte Carlo runs.
-The probability of the existence of substructure becomes
-\begin{equation}
-	P = \sum (\Delta_{shuffled} > \Delta_{Observed}) / n_{shuffle}
-\end{equation}
-where $n_{shuffle}$ is the number of shufflings used. \editorial{This sounds a whole lot like the description given in Hou2012. Make sure that we aren't copying anything word for word. That'd be bad.}
-
-In practice, we use locate the nearest neighbors using an unsupervised k-nearest neighbor algorithm as implemented in Scikit-Learn \citep{Pedregosa2012}.
-
 \section{RESULTS}
@@
 \end{document}
+
+% \section{Evidence of Substructure}
+% Like the recovery of dynamical parameters discussed in the previous section, the choice of method to investigate the dynamical state of galaxy clusters is heavily debated.
+Perhaps the most widely used metric is the Dressler-Shectman (DS) test \citep{Dressler1988}, and is not without criticism \citeeg{White2010}.
+New methods such as the Caustic Method (\citealt{Yu2015}, and the references therein) offer promise to shed further light on this difficult problem.
+%
+% \subsection{From VD profiles}
+% We utilize the modality \citep{Oliva-Altamirano2014} which describes the Gaussianity of a LOSV distribution in a galaxy cluster.
+For clusters with Gaussian distributed LOSVs, the modality is close to 1/3.
+It is defined as $(1+\mathrm{skewness}^2)/(3+\mathrm{kurtosis}^2)$.
+\editorial{Do I need to describe what the skewness and kurtosis is?}
+%
+% \subsection{Dominance}
+% \editorial{This is taken pretty directly from the GAMA paper. Will need to be edited to fit.}
+% The dominance is defined as the luminosity gap between the brightest and the second brightest galaxy in a cluster ($\Delta m_{1, 2}$).
+The amplitude of the luminosity gap between the BGG/BCG and the second brightest galaxy in the halo, is expected to be a function of both the formation epoch and the recent infall history of the halo.
+A small magnitude gap ($\Delta m_{1, 2} < 1$) indicates a recent halo merger, and larger gaps ($\Delta m_{1, 2} > 1$), common in fossil groups, is perhaps indicative of a cluster or groups that has not undergone a recent merger.
+%
+% \subsection{Dressler-Schectman Test}
+% We leverage the large spectroscopic dataset to study the structural properties of the clusters.
+\cite{Pinkney1996} determine, from a comparison of five different methods that the DS test is the most sensitive to the presence of substructure.
+%
+% The DS test, which combines the spatial positions and velocities of the galaxies, provides a method to locate substructure by identifying groups of galaxies which differ significantly from the cluster velocity distribution.
+Galaxy subsets are selected from a cluster of $n_{members}$ and each constituent galaxy deviation is calculated according to
+% \begin{equation}
+% 	\delta_i^2 = \frac{N_{local}+1}{\sigma^2}\bigg{[}(\bar{v}_{local,i} - \bar{v})^2 + (\sigma_{local,i} - \sigma)^2\bigg{]}^2
+% \end{equation}
+% where $\bar{v}_{local}$ and $\sigma_{local}$ are the mean velocity and velocity dispersion for a subset of $N_{local}$ galaxies and $\bar{v}$ and $\sigma$ are the entire cluster's mean velocity and velocity dispersion.
+The choice of $N_{local}$ is left to the user.
+Originally, \cite{Dressler1988} choose $N_{local}=10$, however \cite{Bird1994} points out that using a fixed value for $N_{local}$ reduces the sensitivity to substructure.
+We follow \cite{Bird1994} in choosing $N_{local} = \sqrt n_{members}$.
+\editorial{doesn't talk about the nearest neighbors which is what we are using.}
+%
+% The DS statistic is the $\Delta$-value given by,
+% \begin{equation}
+% 	\Delta = \sum^{n_{members}}_i \delta_i
+% \end{equation}
+% where a system is considered to contain substructure if $\Delta/n_{members} > 1$ \citep{Dressler1988}.
+A second method, described in \cite{Hou2012}, uses probabilities (P-values) rather than a threshold for the identification of substructure.
+P-values are computed by comparing the observed $\Delta$-value and the $Delta$-value after the velocities (but not positions) have been shuffled through a series of Monte Carlo runs.
+The probability of the existence of substructure becomes
+% \begin{equation}
+% 	P = \sum (\Delta_{shuffled} > \Delta_{Observed}) / n_{shuffle}
+% \end{equation}
+% where $n_{shuffle}$ is the number of shufflings used.
+\editorial{This sounds a whole lot like the description given in Hou2012.
+Make sure that we aren't copying anything word for word.
+That'd be bad.}
+%
+% In practice, we use locate the nearest neighbors using an unsupervised k-nearest neighbor algorithm as implemented in Scikit-Learn \citep{Pedregosa2012}.

### 2015-10-01 ms.tex
big update

@@
 
-\title{Cluster Dynamics with HETDEX - I: Mass Distribution and Limits}
+\title{Cluster Dynamics with HETDEX - I: Simulated Performance, Mass Distribution and Limits}
 
@@
 However, connecting these predictions to a set of, sufficiently large in size, observed clusters remains a principal problem.
-Specifically, the largest threat to modern, precision, cluster cosmology is not the identification of large numbers of clusters (the total number of clusters known is only going up) but the accurate recovery of galaxy cluster mass.
+Specifically, the largest threat to modern, precision, cluster cosmology is not the identification of large numbers of clusters (the total number of clusters known is only going up) but the accurate recovery of galaxy cluster mass \citeeg{Sehgal2011,Plank2014, Bocquet2015}.
 
@@
 The observable parameter most commonly observed X-ray temperatures and luminosities \citeeg{Mantz2010, Rykoff2014, Mantz2015}, cosmic microwave background observations \citeeg{Vanderlinde2010, Sehgal2011} using the Sunyaev--Zel’dovich effect (SZE; \citealt{Sunyaev1972}) or optical studies \citeeg{Rozo2010, Rozo2014} of richness \citeeg{Abell1958,Rykoff2012} or galaxy velocity dispersions \citeeg{Ruel2014, Sifon2015}.
+
+Massive surveys, both on going and planned, are revolutionizing cluster cosmology using a large range of wavelengths.
+The South Pole Telescope (SPT; \citealt{Carlstrom2011}) and the Atacama Cosmology Telescope (ACT; \citealt{Swetz2011}) are discovering many clusters through the SZE.
+Optically, the on going The Dark Energy Survey (DES; \citealt{DES2005}) and planned Large Synoptic Survey Telescope (LSST; \citealt{LSST2012}) will identify many thousands of clusters to much lower masses than is possible with SZE measurements.
+However, regardless of the discovery method used, spectroscopic followup is needed to further constrain $P(X|M,z)$.
+But as the cluster dataset grows to many tens of thousands of clusters individual followup becomes increasingly impractical.
+Therefore, large spectroscopic surveys are needed to more fully constrain the observable--mass relation of clusters.
 
@@
 
-In addition to the spectroscopy, an imaging campaign is require first identify galaxy over densities.
+Connecting the dynamical properties derived from spectroscopy to the properties inferred from other studies insures the greatest impact on future work.
 HETDEX overlaps with the Sloan Digital Sky Survey (SDSS; \citealt{Blanton2001a}), SDSS stripe 82 \citep{Annis2014}, the Dark Energy Survey (DES; \citealt{DES2005}), and the upcoming DECam/IRAC Galaxy Environment Survey (DIRGES; PI: Papovich, C.
-Papovich \etal in preparation).
-
-DIRGES, in particular, will be useful as it will identify as many as 100 galaxy cluster progenitors at 0.8 $<$ z $<$ 1.5 based on similarities in galaxy \spitzer/IRAC colors.
-Significant gains in the understanding of these clusters are possible if we can (1) interpret their dynamical nature through spectroscopy, and (2) if we can link them to galaxy clusters at lower redshift, z $<$ 0.5, from within the same dataset to suppress potential observational biases.
-However, two large issues remain.
+Papovich \etal\ in preparation).
+\editorial{SHELA and others?
+Would be good to have a whole list of different things and different wavelengths.} While the potential dataset is very rich, two large issues remain.
 
@@
 This work plans to address these concerns in the following ways.
-Create and evaluate a HETDEX like selection ``function'' of galaxies over a similarly large portion of the sky, use well adopted techniques to recover the dynamical properties, such as velocity dispersion and mass, and to investigate the presence of substructure.
-This will better allow future work to predict the number and types of galaxy clusters which should be observed with HETDEX.
+We use simulated observations which target individual galaxy clusters to investigate the recovery of parameters with such observations.
+Secondly, we create and evaluate a HETDEX like selection ``function'' of galaxies over a similarly large portion of the sky and use well adopted techniques to recover the dynamical properties, such as velocity dispersion and mass.
+Each observation strategy will further be constrained with ``ideal'' and ``realistic'' knowledge.
+Ideal knowledge assumes that we know which individual galaxy is assigned to which cluster.
+With realistic knowledge this is unknown and must be determined prior to the estimation of the cluster properties.
+Both of these strategies will better allow future work to predict the number and types of galaxy clusters which should be observed with VIRUS during both the HETDEX survey portion and through targeted follow up observations.
 
@@
 
-%This support will allow Mr.
-Boada to contribute to the core science of my NSF grant (AST 1413317) for the DECam/IRAC Galaxy Environment Survey (DIRGES).
-He will studying both simulated and real data to understand the reliability in measuring galaxy cluster masses and dynamical states using spectroscopic information for emission-line galaxies.
-DIRGES will identify as many as 100 galaxy cluster progenitors at 0.8 $<$ z $<$ 1.5.
-Significant gains in the understanding of these clusters are possible if we can (1) interpret their dynamical nature through spectroscopy, and (2) if we can link them to clusters at lower redshift, z $<$ 0.5, from within the same dataset to suppress potential observational biases.
-I have plans to obtain the spectroscopy to achieve both of these supplemental goals, but the majority of the spectroscopic redshifts will be for emission-line galaxies.
-It is not straightforward to use these data to interpret the kinematic and dynamical states of the clusters.
-And, because HETDEX covers DIRGES, the data will contain both low-redshift and high-redshift clusters in the same imaging dataset, allowing the most homogeneous study of the low-z and high-z universe yet.
-
-\section{Data and Mock Observations}
+\section{Data and Mock Observations}\label{sec:Data}
 
@@
 
-\section{Recovery of Parameters}
+\section{Recovery of Parameters}\label{sec:recovery}
  In the following sections, we outline the methods we use to derive the dynamical properties of the galaxy clusters in our sample.
@@
 \begin{equation}
-	M_{200c} = \frac{10^{15}}{h(z)} \bigg{(}\frac{\sigma_{1D}}{A_{1D}} \bigg{)}^{-\alpha} \Msol
+	M_{200c} = \frac{10^{15}}{h(z)} \bigg{(}\frac{\sigma_{1D}}{A_{1D}} \bigg{)}^{1/\alpha} \Msol
 \end{equation}
@@
 
-\section{RESULTS}
-Our results section is broken into two large sections.
-First we analyze our ability to recover cluster parameters from an observing strategy similar to that of HETDEX.
-In the second Section, we apply observational limits, similar to those expected to apply, and investigate how the parameter recovery improves (or worsens) under those conditions.
+\section{RESULTS}\label{sec:results}
+The results of this work come in two broad sections.
+The accuracy of which we determine each cluster's LOSVD and dynamical mass, and the probability given a determined mass it is the correct mass.
+We test two different observation strategies with ideal and realistic information about the membership of the observed galaxies.
+Ideal information is knowing the exact membership of the galaxies, and realistic information relies on methods to determine the membership.
+\editorial{The results of this section a shown in Figures XXX and Figures XXX for the LOSVD and masses respectively.}
 
-\subsection{Full Knowledge}
+\subsection{Targeted, Ideal Observations}
+\subsection{Targeted, Realistic Observations}
+\subsection{Blind, Ideal Observations}
+\subsection{Blind, Realistic Observations}
 We compare the calculated cluster redshifts to the true redshift ($z_{c,true}$) for 114903 galaxies comprising 1379 unique halos, and we find a RMS$[\Delta z/(1+z_{c,true})]= 4\times 10^{-4}$ where $\Delta z = z_{c,true} - z_{c}$.
@@
 
-\subsubsection{Dynamical Properties}
 \begin{figure*} 
@@
 \end{figure*}
-Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
 
-\subsubsection{Structural Properties}
-Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
-
-\subsection{HETDEX Depth}
-
-\subsubsection{Dynamical Properties}
 \begin{figure*} 
@@
 
-\subsubsection{Structural Properties}
-Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
-
-\section{IMPROVEMENT}
-Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
-
 \section{SUMMARY}
@@
 \acknowledgments 
-The authors also wish to thank the anonymous referee whose comments and
-suggestions significantly improved both the quality and clarity of this work.
-Several open source resources are used to complete this study Python \citep{van1991} along with Matplotlib \citep{Hunter2007} and IPython \citep{Perez2007}.
+The authors also wish to thank the anonymous referee whose comments and suggestions significantly improved both the quality and clarity of this work.
+This research made use of This research made use of \textsc{APLpy}, an open-source plotting package for Python hosted at http://aplpy.github.com; the \textsc{IPython} package \citep{Perez2007}; \textsc{matplotlib}, a Python library for publication quality graphics \citep{Hunter2007}.
+Funding for the SDSS and SDSS-II has been provided by the Alfred P.
+Sloan Foundation, the Participating Institutions, the National Science Foundation, the U.S.
+Department of Energy, the National Aeronautics and Space Administration, the Japanese Monbukagakusho, the Max Planck Society, and the Higher Education Funding Council for England.
+The SDSS Web Site is http://www.sdss.org/.
+The SDSS is managed by the Astrophysical Research Consortium for the Participating Institutions.
 

### 2015-10-12 ms.tex
keep working

@@
 The ``Buzzard'' mock galaxy catalogs (R.
-Wechsler et al., private communication) are derived from a combination of Sub-halo Abundance Matching (ShAM) and ADDSEDs (Adding Density Dependent Spectral Energy Distributions) tied to an in house n-body cosmological simulation.
+Wechsler et al., private communication) cover 375.68 \degsq\ between $60 < RA < 90$ and $-61 < DEC < -41$ and are derived from a combination of Sub-halo Abundance Matching (ShAM) and ADDSEDs (Adding Density Dependent Spectral Energy Distributions) tied to an in house n-body cosmological simulation.
 A brief description of the catalog creation is described as follows.
@@
 The two boxes show regions containing potential catalog galaxies.
-\textit{Right}: Probability histograms of the Log [\ion{O}{2}] luminosity for the SDSS galaxies located in the two highlighted regions on the right.
+\textit{Right}: Probability histograms of the Log [\ion{O}{ii}] luminosity for the SDSS galaxies located in the two highlighted regions on the right.
 New [\ion{O}{ii}] luminosity (and subsequently fluxes) are assigned to catalog galaxies from slice sampling the probability histogram.} \label{fig:oii sdss}
@@
 
-The buzzard ``truth'' catalog does not provide [\ion{O}{ii}] luminosities so we must assign them empirically.
+The Buzzard ``truth'' catalog does not provide [\ion{O}{ii}] luminosities so we must assign them empirically.
 We use 503113 galaxies from the SDSS Data Release 12 \citep{Alam2015} from $z = 0.05 - 0.2$, which are selected with no redshift warning, and place each galaxy on a color-magnitude diagram (CMD) of $M_r$ and $g-r$, see Figure~\ref{fig:oii sdss}.
@@
 	\includegraphics[width=0.49\textwidth]{f01.pdf} 
-	\caption{Representative observation tiling scheme for the HETDEX $16'$ pointings.
+	\caption{Representative observation tiling scheme for the HETDEX $16' \times 16'$ pointings.
 Each colored square is a single VIRUS IFU and the dashed octagons approximate the size of a single observation.
@@
 The second is a survey case where observations which are blind to the positions of the clusters are conducted.
-In both cases, our ``observations'' consist of placing masks down onto the buzzard ``truth'' catalogs and selecting all, $z< 0.5$ also meeting sensitivity limits, galaxies which lie underneath.
+In both cases, our ``observations'' consist of placing masks down onto the Buzzard ``truth'' catalogs and selecting all, $z< 0.5$ also meeting sensitivity limits, galaxies which lie underneath.
 Each mask is created to accurately reproduce the HETDEX IFU pattern, see Figure~\ref{fig:ifu layout}.
@@
 The individual IFUs have a fill-factor of 1/3, which will be completely filled with three dithers of the telescope at each pointing.
-This means that when selecting galaxies from the buzzard catalog we assume an observation for all galaxies laying within a colored, IFU square in Figure~\ref{fig:ifu layout}.
-Galaxies which lie between the IFUs are missed, as well as the galaxies which lie between the pointings, as there is no overlap between one pointing and the next.
+This means that when selecting galaxies from the Buzzard catalog we assume an observation for all galaxies laying within a colored, IFU square in Figure~\ref{fig:ifu layout}.
+\editorial{This should be updated with the fiber collisions.} Galaxies which lie between the IFUs are missed, as well as the galaxies which lie between the pointings, as there is no overlap between one pointing and the next.
+To cover the 375.67 \degsq\ field of the Buzzard catalog we require 5370 pointings where 0.015 \degsq\ of each pointing is covered by an IFU.
+The total area of the sky covered by an IFU is 80.80 \degsq\ which gives a filling factor of 1/4.65 slight decreased from the expected filling factor of 1/4.5.
 
@@
 The authors also wish to thank the anonymous referee whose comments and suggestions significantly improved both the quality and clarity of this work.
+We also thank Steven W.
+Crawford for many helpful discussions.
 This research made use of This research made use of \textsc{APLpy}, an open-source plotting package for Python hosted at http://aplpy.github.com; the \textsc{IPython} package \citep{Perez2007}; \textsc{matplotlib}, a Python library for publication quality graphics \citep{Hunter2007}.

### 2015-12-08 ms.tex
begin rewrite

@@
 The goal is to constrain, as best possible, $P(X|M,z)$ the probability ($P$) that a galaxy cluster of given mass ($M$), located at redshift ($z$) determined using observable parameter ($X$).
-The observable parameter most commonly observed X-ray temperatures and luminosities \citeeg{Mantz2010, Rykoff2014, Mantz2015}, cosmic microwave background observations \citeeg{Vanderlinde2010, Sehgal2011} using the Sunyaev--Zel’dovich effect (SZE; \citealt{Sunyaev1972}) or optical studies \citeeg{Rozo2010, Rozo2014} of richness \citeeg{Abell1958,Rykoff2012} or galaxy velocity dispersions \citeeg{Ruel2014, Sifon2015}.
+The observable parameter most commonly observed X-ray temperatures and luminosities \citeeg{Mantz2010, Rykoff2014, Mantz2015}, cosmic microwave background observations \citeeg{Vanderlinde2010, Sehgal2011} using the Sunyaev--Zel’dovich effect (SZE; \citealt{Sunyaev1972}) or optical studies \citeeg{Rozo2010, Rozo2015} of richness \citeeg{Abell1958, Rykoff2012} or galaxy velocity dispersions \citeeg{Ruel2014, Sifon2015}.
 
@@
 \editorial{Not sure this does a good enough job talking about the two different observations.}
-Tentatively slated to start in the fall of 2015, HETDEX will perform blind spectroscopy (R $\sim$ 750 in $3500 - 5500~\AAA$) over two fields along the celestial equator.
-The 300 \degsq, Spring field and 120 \degsq, Fall field will have no preselected targets.
+Tentatively slated to start in the spring of 2016, HETDEX will perform blind spectroscopy (R $\sim$ 750 in $3500 - 5500~\AAA$) over two fields along the celestial equator.
+The 300 \degsq, spring field and 120 \degsq, fall field will have no preselected targets.
 Using VIRUS on the 10-m Hobby-Eberly Telescope (HET; \citealt{Ramsey1998}) the completed survey is expected to have an overall fill-factor of 1/4.5, meaning that the entire area could be covered with 4.5 dithers of the entire survey.
@@
 
-\section{Cluster Membership}
-In the following sections we assume that the on sky positions and redshifts of the galaxy clusters are already known.
+% \section{Cluster Membership}
+% In the following sections we assume that the on sky positions and redshifts of the galaxy clusters are already known.
 In reality, galaxy over densities will be detected from imaging surveys \citeeg{Rykoff2014} or through techniques to identify structure in the RA, DEC, z point data (\eg, DBSCAN; \citealt{Ester1996}).
-
-While the galaxy cluster center may be well known, the constituent galaxies will not.
-The identification of member galaxies from photometric data \citeeg{Rozo2014} is promising, however, with spectroscopic information on all galaxies, we choose to utilize the full 3D parameter space.
+%
+% While the galaxy cluster center may be well known, the constituent galaxies will not.
+The identification of member galaxies from photometric data \citeeg{Rozo2015} is promising, however, with spectroscopic information on all galaxies, we choose to utilize the full 3D parameter space.
 \editorial{Not very happy about that sentence}.
-
-We employ the ``shifting gapped" method of \cite{Fadda1996} as outlined in \cite{Owers2011}, which combines both the positional and velocity information.
+%
+% We employ the ``shifting gapped" method of \cite{Fadda1996} as outlined in \cite{Owers2011}, which combines both the positional and velocity information.
 After an initial cut of $cz_c \pm 10,000$ \kms, the galaxies are binned in $0.4h^{-1}$ Mpc or larger enough bins to contain at least 10 (arbitrarily chosen) galaxies.
@@
 The procedure repeats until the number of galaxies stabilizes in the bin.
-
-\editorial{This is taken from the other paper, and needs to be tweaked to make fit better into this framework.
+%
+% \editorial{This is taken from the other paper, and needs to be tweaked to make fit better into this framework.
 I think what we'll do is center a 100'' box on all of the clusters and then try to recover the galaxies.
@@
 
-\subsection{Radial Extent}
-We define the radius of a galaxy cluster as
-\begin{equation}
-	r_{200c} = \bigg{[} \frac{3}{4\pi} \frac{M_{200}}{200\rho_c} \bigg{]}^{1/3}
-\end{equation}
-where $\rho_c$ is critical density of the universe and defined as $3H^2/8\pi G$.
+% \subsection{Radial Extent}
+% We define the radius of a galaxy cluster as
+% \begin{equation}
+% 	r_{200c} = \bigg{[} \frac{3}{4\pi} \frac{M_{200}}{200\rho_c} \bigg{]}^{1/3}
+% \end{equation}
+% where $\rho_c$ is critical density of the universe and defined as $3H^2/8\pi G$.
 
 \section{RESULTS}\label{sec:results}
+
+\subsection{Recovery of Clusters}
+\begin{figure*} 
+	\includegraphics[width=\textwidth]{recovery.pdf} 
+	\caption{\textit{Left}: CMD of 503113 $z<0.2$ galaxies take from the SDSS DR12 where the shading scales with the density of points.
+The two boxes show regions containing potential catalog galaxies.
+\textit{Right}: Probability histograms of the Log [\ion{O}{ii}] luminosity for the SDSS galaxies located in the two highlighted regions on the right.
+New [\ion{O}{ii}] luminosity (and subsequently fluxes) are assigned to catalog galaxies from slice sampling the probability histogram.} \label{fig:recovery}
+\end{figure*}
+
 The results of this work come in two broad sections.
@@
 
-\begin{figure*} 
-	\includegraphics[width=\textwidth]{fullKnowledge.pdf} 
-	\caption{Intrinsic cluster properties versus the recovered cluster properties for 16758 unique halos comprised of 657916 individual galaxies.
-The left panel shows the line of sight velocity dispersion (LOSVD) and the right panel shows the recovered halo mass.
-In both panels, the red line shows the 1:1 relation and the teal line shows the best fit to data.}
-	\label{fig:full} 
-\end{figure*}
-
-\begin{figure*} 
-	\includegraphics[width=\textwidth]{hetdexDepth.pdf} 
-	\caption{HETDEX DEPTH!
-Intrinsic cluster properties versus the recovered cluster properties for 14239 unique halos comprised of 87754 individual galaxies.
-The left panel shows the line of sight velocity dispersion (LOSVD) and the right panel shows the recovered halo mass.
-In both panels, the red line shows the 1:1 relation and the teal line shows the best fit to data.}
-	\label{fig:hetdexDepth} 
-\end{figure*}
 Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.

### 2015-12-17 ms.tex
lots of new text

@@
 \usepackage{graphicx}
-\usepackage[colorlinks,urlcolor=blue,citecolor=blue,linkcolor=blue]{hyperref}
 \usepackage{threeparttable}
@@
 \usepackage{etoolbox}
+\usepackage[breaklinks, backref, colorlinks, urlcolor=magenta, citecolor=blue, linkcolor=magenta]{hyperref}
 
 \bibliographystyle{apj}
+%\bibliographystyle{yahapj}
 \citestyle{aa}
@@
 
-\title{Cluster Dynamics with HETDEX - I: Simulated Performance, Mass Distribution and Limits}
+\title{HETDEX as a Galaxy Cluster Survey - I: Simulated Performance, Mass Distribution and Limits}
 
@@
 
-\section{Data and Mock Observations}\label{sec:Data}
+\section{Data and Mock Observations}\label{sec: Data}
 
@@
 However, the catalogs do not include information on emission or absorption lines or estimations of whether the halo is relaxed or not.
-We supplement the catalogs with this information and describe the method in Section~\ref{sec:oii luminosity} and others.
+We supplement the catalogs with this information and describe the method in Section~\ref{sec: oii luminosity} and others.
 
@@
 	\caption{The cumulative MF of halos above $M_{200c}$ at $z=0.1$. The predicted MF is from \cite{Tinker2008}.} 
-	\label{fig:hmf} 
+	\label{fig: hmf} 
 \end{figure}
@@
 We investigate the accuracy of the halo mass distribution by comparing the cumulative number density of halos above a mass ($M_{200c}$) threshold to the halo mass function (HMF) of \cite{Tinker2008}.
-Shown in Figure~\ref{fig:hmf} the HMF is calculated at central redshifts of 0, 0.2, and 0.4 using {\tt HMFcalc} \citep{Murray2013} and compared to galaxies in a redshift window of $\Delta z\pm0.01$.
+Shown in Figure~\ref{fig: hmf} the HMF is calculated at central redshifts of 0, 0.2, and 0.4 using {\tt HMFcalc} \citep{Murray2013} and compared to galaxies in a redshift window of $\Delta z\pm0.01$.
 We find a very good agreement between the expected HMF and the observed.
 
-\subsection{ {\rm[\ion{O}{ii}]} Luminosity}\label{sec:oii luminosity}
+\subsection{ {\rm[\ion{O}{ii}]} Luminosity}\label{sec: oii luminosity}
 \begin{figure*} 
@@
 \textit{Right}: Probability histograms of the Log [\ion{O}{ii}] luminosity for the SDSS galaxies located in the two highlighted regions on the right.
-New [\ion{O}{ii}] luminosity (and subsequently fluxes) are assigned to catalog galaxies from slice sampling the probability histogram.} \label{fig:oii sdss}
+New [\ion{O}{ii}] luminosity (and subsequently fluxes) are assigned to catalog galaxies from slice sampling the probability histogram.} \label{fig: oii sdss}
 \end{figure*}
@@
 The Buzzard ``truth'' catalog does not provide [\ion{O}{ii}] luminosities so we must assign them empirically.
-We use 503113 galaxies from the SDSS Data Release 12 \citep{Alam2015} from $z = 0.05 - 0.2$, which are selected with no redshift warning, and place each galaxy on a color-magnitude diagram (CMD) of $M_r$ and $g-r$, see Figure~\ref{fig:oii sdss}.
+We use 503113 galaxies from the SDSS Data Release 12 \citep{Alam2015} from $z = 0.05 - 0.2$, which are selected with no redshift warning, and place each galaxy on a color-magnitude diagram (CMD) of $M_r$ and $g-r$, see Figure~\ref{fig: oii sdss}.
 
@@
 
-The right panel of Figure~\ref{fig:oii sdss} shows the CMD of all SDSS galaxies.
+The right panel of Figure~\ref{fig: oii sdss} shows the CMD of all SDSS galaxies.
 Two potential catalog galaxies are also placed on the CMD ($M_r, g-r = -17.7,~0.49$ and $M_r, g-r = -21.4,~1.24$) and indicated by two colored boxes.
@@
 
-\subsection{Mock Observations}\label{sec:observations}
+\subsection{Mock Observations}\label{sec: observations}
 \editorial{Not sure this does a good enough job talking about the two different observations.}
@@
 Galaxies $0.4<z<0.5$ are only observed if their emission line strength is sufficient.
+\editorial{These limits have been changed.
+FIX!}
 
@@
 Each colored square is a single VIRUS IFU and the dashed octagons approximate the size of a single observation.
-See the text for more details.} \label{fig:ifu layout}
+See the text for more details.} \label{fig: ifu layout}
 \end{figure}
@@
 In both cases, our ``observations'' consist of placing masks down onto the Buzzard ``truth'' catalogs and selecting all, $z< 0.5$ also meeting sensitivity limits, galaxies which lie underneath.
-Each mask is created to accurately reproduce the HETDEX IFU pattern, see Figure~\ref{fig:ifu layout}.
+Each mask is created to accurately reproduce the HETDEX IFU pattern, see Figure~\ref{fig: ifu layout}.
 The pattern consists of 78 IFUs, which are comprised of 448 optical fibers subtending a $50'' \times 50''$ region on the sky \citep{Kelz2014}.
@@
 The individual IFUs have a fill-factor of 1/3, which will be completely filled with three dithers of the telescope at each pointing.
-This means that when selecting galaxies from the Buzzard catalog we assume an observation for all galaxies laying within a colored, IFU square in Figure~\ref{fig:ifu layout}.
+This means that when selecting galaxies from the Buzzard catalog we assume an observation for all galaxies laying within a colored, IFU square in Figure~\ref{fig: ifu layout}.
 \editorial{This should be updated with the fiber collisions.} Galaxies which lie between the IFUs are missed, as well as the galaxies which lie between the pointings, as there is no overlap between one pointing and the next.
@@
 
-% \section{Cluster Membership}
-% In the following sections we assume that the on sky positions and redshifts of the galaxy clusters are already known.
-In reality, galaxy over densities will be detected from imaging surveys \citeeg{Rykoff2014} or through techniques to identify structure in the RA, DEC, z point data (\eg, DBSCAN; \citealt{Ester1996}).
-%
-% While the galaxy cluster center may be well known, the constituent galaxies will not.
-The identification of member galaxies from photometric data \citeeg{Rozo2015} is promising, however, with spectroscopic information on all galaxies, we choose to utilize the full 3D parameter space.
-\editorial{Not very happy about that sentence}.
-%
-% We employ the ``shifting gapped" method of \cite{Fadda1996} as outlined in \cite{Owers2011}, which combines both the positional and velocity information.
-After an initial cut of $cz_c \pm 10,000$ \kms, the galaxies are binned in $0.4h^{-1}$ Mpc or larger enough bins to contain at least 10 (arbitrarily chosen) galaxies.
-Galaxies farther than 3 Mpc from the cluster center are also rejected.
-Once binned, the galaxies are sorted by their line-of-sight velocity (LOSV; see Section~\ref{sec:LOSVD}).
-Any galaxy with a LOSV greater than 1000 \kms of a neighboring galaxy is rejected as an interloper.
-The procedure repeats until the number of galaxies stabilizes in the bin.
-%
-% \editorial{This is taken from the other paper, and needs to be tweaked to make fit better into this framework.
-I think what we'll do is center a 100'' box on all of the clusters and then try to recover the galaxies.
-How many will we get, how many are wrong, and can we do better with a different algorithm?}
-
-\section{Recovery of Parameters}\label{sec:recovery}
+\section{Recovery of Parameters}\label{sec: recovery}
  In the following sections, we outline the methods we use to derive the dynamical properties of the galaxy clusters in our sample.
@@
 The accurate determination of the cluster redshift ($z_c$) is crucial to the reliability of all following measurements.
-An incorrect cluster redshift introduces errors into the measured line of sight velocity (LOSV) and corresponding dispersion, which, in turn, contributes to errors associated with dynamical mass and radius.
+An incorrect cluster redshift introduces errors into the measured line-of-sight velocity (LOSV) and corresponding dispersion, which, in turn, contributes to errors associated with dynamical mass and radius.
 
@@
 
-\subsection{Line of Sight Velocity Dispersion}\label{sec:LOSVD}
-We first calculate the line of sight velocity (LOSV) to each galaxy, where
+\subsection{Line-of-Sight Velocity Dispersion}\label{sec: LOSVD}
+We first calculate the line-of-sight velocity (LOSV) to each galaxy, where
 \begin{equation}
@@
 
-The unbiased estimation of a standard deviation (a measure of statistical dispersion) from these LOSVs is a technically involved problem.
-At first, we require that our estimator be unbiased in that the dispersion estimation is equal to the true dispersion regardless of the number of points sampled, although, in practice this rarely occurs.
-The most commonly used estimate is the corrected sample standard deviation, given by:
+The line-of-sight velocity dispersion (LOSVD) is calculated using a method of maximum likelihood following \cite{Walker2006}. We maximize the probability function 
 \begin{equation}
-	s = \sqrt{\frac{1}{n-1} \sum_{i=1}^n (x_i - \bar{x})^2}
+  \label{eq: jointGaussian}
+p(\{v_1, ..., v_N\})=\displaystyle\prod_{i=1}^{N}\frac{1}{\sqrt{2\pi(\sigma_i^2+\sigma_p^2)}}\exp\biggl[-\frac{1}{2}\frac{(v_i-\langle u \rangle)^2}{(\sigma_i^2+\sigma_p^2)}\biggr]
 \end{equation}
-with $\{x_1, x_2, ..., x_n\}$ being the random sample and $\bar{x}$ the sample mean.
-The corrected sample standard deviation has the advantage in that it is unbiased (as opposed to the population standard deviation which is biased), but the removal of bias relies on knowing \textit{a priori} the underlying distribution from which the sample is drawn.
-An estimator which correctly estimates a standard deviation for a sample drawn from a wide range of distributions and is not adversely effected by outliers is said to be robust.
-An estimator which correctly identifies the standard deviation, even when a number of points are replaced by different values is said to be resistant.
+where $\sigma_p$, $\langle\mu\rangle$, and $\sigma_i$ is the LOSVD, the average radial velocity and the error on the individual LOSVs respectively.
+Using a Monte Carlo Markov Chain sampler ({\sc emcee}\footnote{\url{http://dan.iel.fm/emcee/current/}}, \citealt{Foreman-Mackey2013}), we draw twenty thousand samples from the posterior probability distribution.
+Simple priors, $\langle\mu\rangle$ lies between the maximum and minimum LOSV and $0< \sigma_p$, are used.
+When the full distribution of LOSVDs are not used, the final LOSVD is quoted as the median value of the probability distribution with 68\% error bars defined as the 16th and 84th percentiles of the same distribution.
 
-In our situation, a resistant estimator becomes critical as it minimizes the effect of outliers which the inclusion of non-cluster members have on the measured dispersion.
-\cite{Beers1990} present both a robust and resistant estimation of scale (yet another term for statistical dispersion) called the biweight scale estimator, which has been widely accepted by the community (\eg, \citealt{Milvang-Jensen2008, Owers2011, Murphy2011} and many others).
-It is given by
-\begin{equation}
-	\sigma_{BI} = \sqrt{ N_{members} \frac{ \sum_{|u_i|<1} (1-u_i^2)^4 (v_i - \bar{v})^2} {D} }
-\end{equation}
-with $v_i$, the proper velocities, $\bar{v}$, the average of the proper velocities,
-\begin{equation}
-	D = \sum_{|u_i|<1} (1-u_i^2)(1-5u_i^2)
-\end{equation}
-with $u_i$ being the biweight weighting and defined as:
-\begin{equation}
-	u_i = \frac{v_i - \bar{v}}{9 {\rm MAD}(v_i)}
-\end{equation}
-where MAD is the median absolute deviation.
-\cite{Ruel2014} note, however, that the biweight scale estimator is biased and suggest a correction of $1/(D-1)$ to $\sigma_{BI}$ referring to it as the biweight sample variance.
-We adopt this method for clusters with at least 15 members.
-For clusters with fewer than 15 members, we adopt the gapper scale estimator \citep{Beers1990} which is shown to accurately recover the dispersion for as few as 5 member galaxies \citep{Hou2009}.
+In principle, a single statistic such as the biweight scale estimator or the gapper estimator (both from \citealt{Beers1990}) with many bootstrap resamplings could be used to construct a distribution of $\sigma_p$.
+We prefer the maximum likelihood method for its straight forward treatment of the errors in the LOSV measurements.
+\editorial{Maybe run a quick check to see how they compare.}
 
-There are several situations which can adversely effect the quality of our velocity dispersion measurement.
-The first is due to the nature of our observations.
-Because the HETDEX survey has a 1/4.5 fill factor (see Section~\ref{sec:observations}), there will be many situations where we will not have full spectroscopic information for a cluster.
-Some clusters could also have intrinsic velocity distributions where the observations of only a few members could result in a LOSVD which differs by large percent.
-This gives rise to clusters along a fixed mass having a large range of possible LOSVDs.
-\cite{Saro2013} find this effect to be most pronounced for clusters with fewer than 30 members, and \cite{Ruel2014} show the effect is a net increase in scatter of about 5\% compared to clusters with greater than 30 members.
-\editorial{This section was adapted, pretty heavily from Ruel2014.
-Is that cool?}
-
-A second effect, unique to works such as this, is the difference between the LOSVD computed between dark matter halos and the galaxies that occupy them, the so-called velocity bias \citeeg{Evrard2008, White2010}.
-This effect is assumed to be small ($\sim5\%$) and for this work we assume there is no bias, or that the galaxies perfectly trace the velocity distribution.
-
-\subsection{Dynamical Mass}\label{sec:mass}
+\subsection{Dynamical Mass}\label{sec: mass}
 Recently, the relationship between the LOSVD and dynamical mass has been the focus of several studies \citeeg{Evrard2008, Saro2013, Sifon2013, VanderBurg2014}, and a best fitting relationship for the mass enclosed by $r_{200c}$ of the form
-\begin{equation}
+\begin{equation}\label{eq: mass scaling}
 	M_{200c} = \frac{10^{15}}{h(z)} \bigg{(}\frac{\sigma_{1D}}{A_{1D}} \bigg{)}^{1/\alpha} \Msol
 \end{equation}
-with $A_{1D} =$ 1040-1140 \kms\ (\citealt{Munari2013}; referred to as $\sigma_{15}$ in \citealt{Evrard2008} and other works), $\alpha = 1/3$, $h(z) = H(z)/100$, and $\sigma_{1D}$ is the LOSVD of the velocity tracers (dark matter particles, subhalos or galaxies).
+with $A_{1D} = 1177 \pm 4.2$ \kms\ (\citealt{Munari2013}; referred to as $\sigma_{15}$ in \citealt{Evrard2008} and other works), $\alpha = 1/3$, $h(z) = H(z)/100$, and $\sigma_{1D}$ is the LOSVD of the velocity tracers (dark matter particles, subhalos or galaxies).
 
-The choice $A_{1D}$ and $\alpha$ varies between studies \citeeg{Munari2013, VanderBurg2014} and should be calibrated on a individual basis.
+A growing body of work suggests that there is a significant difference in the observed LOSVD depending on the velocity tracers used.
+Specifically, while there is little difference between using galaxies and their host DM subhalos, there is a significant over estimation of the LOSVD when using galaxies/subhalos compared to DM particles \citep{Munari2013}.
+We follow other works \citeeg{Kirk2015, Sifon2015a} using the scaling relation, given in Equation~\ref{eq: mass scaling} from \cite{Munari2013} to facilitate comparisons with other observational studies.
+% \editorial{This all needs to be stripped out and reworked.}
+% The choice $A_{1D}$ and $\alpha$ varies between studies \citeeg{Munari2013, VanderBurg2014} and should be calibrated on a individual basis.
 To do this, we randomly select 47494, $z<0.5$ clusters composed of 36000 $10^{13}$, 6000 $10^{14}$ and two $10^{15}~\Msol$ halos.
@@
 
-% \subsection{Radial Extent}
-% We define the radius of a galaxy cluster as
-% \begin{equation}
-% 	r_{200c} = \bigg{[} \frac{3}{4\pi} \frac{M_{200}}{200\rho_c} \bigg{]}^{1/3}
-% \end{equation}
-% where $\rho_c$ is critical density of the universe and defined as $3H^2/8\pi G$.
+\subsection{Dynamical Mass Corrections}
+In this section we use two methods to predict the mass of a cluster based on other observables.
+Often the cluster mass is estimated based on a single observable, X-ray temperature, velocity dispersion, richness and others.
+Here we combine many observables to attempt to correct the mass inferred solely from the velocity dispersion.
+The first method is traditional probability based where we marginalize over a series of observables to find the most probable mass.
+The second is based on a machine learning (ML) algorithm which attempts to ``learn'' the relationship between the observables and the desired output, the mass.
+Both of these methods are examples of supervised learning algorithms where the relationship between the observable (known) parameters and the target parameter (the mass) are both known.
 
-\section{RESULTS}\label{sec:results}
+As with any predictive analysis it is important to test the model on data that the model has not seen before.
+In this section we take all of the observed clusters, our full sample, split them, and generate a training and testing set.
+The data is randomly split 70\% training and 30\% testing.
+We follow the ML convention and refer to the individual clusters in each set as a ``sample'', and the parameters associated with the cluster ($z$, LOSVD, mass, etc.) as ``features''.
 
-\subsection{Recovery of Clusters}
+\subsubsection{Probability Based}
+We begin with the training sample.
+After selecting the desired features $\vec{x} = \{\sigma, z, ...\}$ we make the joint probability between the true cluster mass (M) and $\vec{x}$.
+Because $\vec{x}$ can be multidimensional, we rely on the corner plot to visualize the relationship between all of the training features.
+Figure~\ref{fig: probability corner} shows all of the one (marginalized probability) and two (joint probability) dimensional projections of the posterior probability distributions of the features of the training data.
+
+\begin{figure} 
+	\includegraphics[width=0.5\textwidth]{cornertest.pdf} 
+	\caption{Corner plot of the \emph{training} data with features $\sigma$ and $z$.
+The corner plots shows all of the one and two dimensional posterior probability distributions used to determine the correct cluster mass.
+The colored rectangles show the slices needed to create a conditional probability distribution of the mass, $P(M|\vec{x})$.
+See text for a complete description.
+} \label{fig: probability corner}
+\end{figure}
+
+The conditional probability of the mass $P(M|\vec{x}= \{ x_1,x_2,...\})$ is determined by taking a slice through the joint probability distributions in bins centered on the desired value.
+The slices show by the colored bars in Figure~\ref{fig: probability corner} are centered on $\sigma = 500$ \kms and $z=0.17$.
+The distribution of mass contained in the three dimensional bin given by the intersection of these slices is $P(M|\vec{x} = \{ \sigma=500 \kms,z=0.17\})$.
+
+For the clusters making up the \emph{test} sample the mass is unknown (it is what we are trying to predict) but the other features are known.
+To determine the mass probability distribution of a test cluster, $P(M)$ we combine the conditional probability distribution, $P(M|\vec{x})$, created previously with the probability distribution of $\sigma$ through Equation~\ref{eq: Pm}.
+\begin{equation}\label{eq: Pm}
+	P(M) = \int P(M|\vec{x}) P(\sigma) d\sigma
+\end{equation}
+The expected mass is determined by integrating the mass probability, $P(M)$ over all mass. This becomes our ``predicted'' mass, $\langle M\rangle$.
+\begin{equation}\label{eq: expected mass}
+	\langle M\rangle = \int M^\prime P(M^\prime)dM^\prime
+\end{equation}
+The confidence interval associated with this prediction can be estimated two ways. First, by calculating the variance about the expected mass through
+\begin{equation}\label{eq: variance}
+	V = \int (M^\prime - \langle M\rangle)^2 P(M^\prime)dM^\prime
+\end{equation}
+or by drawing many samples from $P(M)$ and calculating the values at the 16th and 84th percentile.
+In practice we find that both methods produce similar results for a large number of trials.
+Therefore, we quote predicted masses as the most probable mass given by Equation~\ref{eq: expected mass} and associated 68\% error estimated through Equation~\ref{eq: variance}.
+
+\subsubsection{Machine Learning Based}
+The estimation in this section relies on a ML technique known as an ensemble method, where many estimators are created by a single learning method with the goal of improved generalization and robustness compared to a single estimation.
+Ensemble methods come in two general flavors.
+Averaging methods average (hence the name) the estimators to produce a single prediction.
+Boosting estimators build estimates sequentially by attempting to address poor performing estimators in each previous step, hence ``boosting'' the predictive power.
+
+Here we use an averaging ensemble learning method known as a forest of randomized decision trees often shorten to just random forest (RF).
+Decision trees can be visualized a flow chart where forks are the branches of the tree.
+The path along the tree is decided by the values of the feature at each branch.
+RF estimators use a random subset of the training set at each fork to decide which path should be followed.
+The final prediction is then the average of all the trees.
+We use RF regression methods as implemented in {\sc Scikit-Learn} \citep{Pedregosa2012}.
+
+The 68\% prediction interval is determined by calculating the 16th and 84th percentile of all the predictions made by the ensemble of estimators.
+
+\section{RESULTS}\label{sec: results}
+Here we explore the cluster member recovery rate and mass estimates for the two observing strategies.
+We discuss the accuracy of dynamical mass derived from both the scaling relation (see Equation~\ref{eq: mass scaling}) and through the probability and ML methods.
+
+\subsection{Recovery of Cluster Members}
+As discussed in Section~\ref{sec: observations} the observational constraints place limits on the total number fo clusters member galaxies expected to be recovered.
+Knowing these limits will provide important information for potential future follow up or targeted observations.
+
 \begin{figure*} 
 	\includegraphics[width=\textwidth]{recovery.pdf} 
-	\caption{\textit{Left}: CMD of 503113 $z<0.2$ galaxies take from the SDSS DR12 where the shading scales with the density of points.
-The two boxes show regions containing potential catalog galaxies.
-\textit{Right}: Probability histograms of the Log [\ion{O}{ii}] luminosity for the SDSS galaxies located in the two highlighted regions on the right.
-New [\ion{O}{ii}] luminosity (and subsequently fluxes) are assigned to catalog galaxies from slice sampling the probability histogram.} \label{fig:recovery}
+	\caption{Recovery fractions ($N_{obs}/N_{True}$) of cluster member galaxies as a function of redshift and mass for the targeted (upper row) and survey (lower row) observing strategies.
+The significant decline in galaxies observed with the survey strategy is due to gaps in the VIRUS IFU.} \label{fig: recovery}
 \end{figure*}
 
-The results of this work come in two broad sections.
-The accuracy of which we determine each cluster's LOSVD and dynamical mass, and the probability given a determined mass it is the correct mass.
-We test two different observation strategies with ideal and realistic information about the membership of the observed galaxies.
-Ideal information is knowing the exact membership of the galaxies, and realistic information relies on methods to determine the membership.
-\editorial{The results of this section a shown in Figures XXX and Figures XXX for the LOSVD and masses respectively.}
+Figure~\ref{fig: recovery} shows the recovery fraction of member galaxies, the number of observed versus the number of actual galaxies, as a function of both redshift and cluster mass for the targeted and survey observing strategies.
+As expected, the targeted observing strategy where the individual clusters are targeted through several dithers to ensure near complete coverage, performs significant better than the survey observing strategy for nearly all redshifts and cluster masses.
+This performance gain is due solely to the gaps between the fiber bundles of the IFU.
 
-\subsection{Targeted, Ideal Observations}
-\subsection{Targeted, Realistic Observations}
-\subsection{Blind, Ideal Observations}
-\subsection{Blind, Realistic Observations}
-We compare the calculated cluster redshifts to the true redshift ($z_{c,true}$) for 114903 galaxies comprising 1379 unique halos, and we find a RMS$[\Delta z/(1+z_{c,true})]= 4\times 10^{-4}$ where $\Delta z = z_{c,true} - z_{c}$.
-\editorial{The RMS using just the regular mean is 3.8e-4 which is only slightly better than the biweight.
-I don't think that will be the case when we get more complicated things.}
+\editorial{why does the recovery fraction decrease with redshift?
+Are the clusters smaller?
+Do they not have as many galaxies per cluster at higher redshifts?
+Is it a magnitude effect?
+I also want to add an error bar estimation for several of the percentages to give a feel for how the different recovery levels effect the accuracy of the measurements.}
 
+\subsection{Mass estimates}
+\editorial{It doesn't look like you can use the targeted training sample to train the survey data.
+If you do, it either does worse or about the same if you didn't use any training at all.
+After looking at it, you do have to use the survey training data to get good results about 0.13 dex MAE
+}
+
+Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
+Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
+Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+
+\section{HETDEX as a Galaxy Cluster Survey}
+
+\subsection{Expected Results}
+Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
+Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
+Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+
+\subsection{Potential Improvements}
+Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
+Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
+Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+
+\subsection{Extendability to Other Surveys}
 Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
@@
 Crawford for many helpful discussions.
-This research made use of This research made use of \textsc{APLpy}, an open-source plotting package for Python hosted at http://aplpy.github.com; the \textsc{IPython} package \citep{Perez2007}; \textsc{matplotlib}, a Python library for publication quality graphics \citep{Hunter2007}.
+This research made use of This research made use of the \textsc{IPython} package \citep{Perez2007} and \textsc{matplotlib}, a Python library for publication quality graphics \citep{Hunter2007}.
 Funding for the SDSS and SDSS-II has been provided by the Alfred P.
@@
 Department of Energy, the National Aeronautics and Space Administration, the Japanese Monbukagakusho, the Max Planck Society, and the Higher Education Funding Council for England.
-The SDSS Web Site is http://www.sdss.org/.
 The SDSS is managed by the Astrophysical Research Consortium for the Participating Institutions.
@@
 
+% We compare the calculated cluster redshifts to the true redshift ($z_{c,true}$) for 114903 galaxies comprising 1379 unique halos, and we find a RMS$[\Delta z/(1+z_{c,true})]= 4\times 10^{-4}$ where $\Delta z = z_{c,true} - z_{c}$.
+\editorial{The RMS using just the regular mean is 3.8e-4 which is only slightly better than the biweight.
+I don't think that will be the case when we get more complicated things.}
+
 \end{document}
-
-% \section{Evidence of Substructure}
-% Like the recovery of dynamical parameters discussed in the previous section, the choice of method to investigate the dynamical state of galaxy clusters is heavily debated.
-Perhaps the most widely used metric is the Dressler-Shectman (DS) test \citep{Dressler1988}, and is not without criticism \citeeg{White2010}.
-New methods such as the Caustic Method (\citealt{Yu2015}, and the references therein) offer promise to shed further light on this difficult problem.
-%
-% \subsection{From VD profiles}
-% We utilize the modality \citep{Oliva-Altamirano2014} which describes the Gaussianity of a LOSV distribution in a galaxy cluster.
-For clusters with Gaussian distributed LOSVs, the modality is close to 1/3.
-It is defined as $(1+\mathrm{skewness}^2)/(3+\mathrm{kurtosis}^2)$.
-\editorial{Do I need to describe what the skewness and kurtosis is?}
-%
-% \subsection{Dominance}
-% \editorial{This is taken pretty directly from the GAMA paper. Will need to be edited to fit.}
-% The dominance is defined as the luminosity gap between the brightest and the second brightest galaxy in a cluster ($\Delta m_{1, 2}$).
-The amplitude of the luminosity gap between the BGG/BCG and the second brightest galaxy in the halo, is expected to be a function of both the formation epoch and the recent infall history of the halo.
-A small magnitude gap ($\Delta m_{1, 2} < 1$) indicates a recent halo merger, and larger gaps ($\Delta m_{1, 2} > 1$), common in fossil groups, is perhaps indicative of a cluster or groups that has not undergone a recent merger.
-%
-% \subsection{Dressler-Schectman Test}
-% We leverage the large spectroscopic dataset to study the structural properties of the clusters.
-\cite{Pinkney1996} determine, from a comparison of five different methods that the DS test is the most sensitive to the presence of substructure.
-%
-% The DS test, which combines the spatial positions and velocities of the galaxies, provides a method to locate substructure by identifying groups of galaxies which differ significantly from the cluster velocity distribution.
-Galaxy subsets are selected from a cluster of $n_{members}$ and each constituent galaxy deviation is calculated according to
-% \begin{equation}
-% 	\delta_i^2 = \frac{N_{local}+1}{\sigma^2}\bigg{[}(\bar{v}_{local,i} - \bar{v})^2 + (\sigma_{local,i} - \sigma)^2\bigg{]}^2
-% \end{equation}
-% where $\bar{v}_{local}$ and $\sigma_{local}$ are the mean velocity and velocity dispersion for a subset of $N_{local}$ galaxies and $\bar{v}$ and $\sigma$ are the entire cluster's mean velocity and velocity dispersion.
-The choice of $N_{local}$ is left to the user.
-Originally, \cite{Dressler1988} choose $N_{local}=10$, however \cite{Bird1994} points out that using a fixed value for $N_{local}$ reduces the sensitivity to substructure.
-We follow \cite{Bird1994} in choosing $N_{local} = \sqrt n_{members}$.
-\editorial{doesn't talk about the nearest neighbors which is what we are using.}
-%
-% The DS statistic is the $\Delta$-value given by,
-% \begin{equation}
-% 	\Delta = \sum^{n_{members}}_i \delta_i
-% \end{equation}
-% where a system is considered to contain substructure if $\Delta/n_{members} > 1$ \citep{Dressler1988}.
-A second method, described in \cite{Hou2012}, uses probabilities (P-values) rather than a threshold for the identification of substructure.
-P-values are computed by comparing the observed $\Delta$-value and the $Delta$-value after the velocities (but not positions) have been shuffled through a series of Monte Carlo runs.
-The probability of the existence of substructure becomes
-% \begin{equation}
-% 	P = \sum (\Delta_{shuffled} > \Delta_{Observed}) / n_{shuffle}
-% \end{equation}
-% where $n_{shuffle}$ is the number of shufflings used.
-\editorial{This sounds a whole lot like the description given in Hou2012.
-Make sure that we aren't copying anything word for word.
-That'd be bad.}
-%
-% In practice, we use locate the nearest neighbors using an unsupervised k-nearest neighbor algorithm as implemented in Scikit-Learn \citep{Pedregosa2012}.

### 2016-01-12 ms.tex
new figure

@@
 \subsection{Mass estimates}
+\begin{figure*} 
+	\includegraphics[width=\textwidth]{MLcomparison.pdf} 
+	\caption{Mass predictions for the power law scaling relation (Equation~\ref{eq: mass scaling}) and the ML technique with different input features.
+The bottom row of panels shows the fractional error (Equation~\ref{eq: fractional error}) as a function of mass.
+The solid black line shows the 1:1 relation.
+The colored lines and shaded region show the median value and 68\% bounds respectively.} \label{fig: ML comparison}
+\end{figure*}
+
+\begin{equation}\label{eq: fractional error}
+	\epsilon = (M_{pred} - M)/M
+\end{equation}
+
 \editorial{It doesn't look like you can use the targeted training sample to train the survey data.

### 2016-01-21 ms.tex
now works with the MNRAS

@@
-\documentclass[apj, revtex4]{emulateapj}
+\documentclass[a4paper,fleqn,usenatbib]{mnras}
 
-\usepackage{epsf}
-\usepackage{color}
-\usepackage{amsmath}
-\usepackage{graphicx}
-\usepackage{threeparttable}
-\usepackage{multirow}
-\usepackage{natbib}
-\usepackage{etoolbox}
-\usepackage[breaklinks, backref, colorlinks, urlcolor=magenta, citecolor=blue, linkcolor=magenta]{hyperref}
+% MNRAS is set in Times font. If you don't have this installed (most LaTeX
+% installations will be fine) or prefer the old Computer Modern fonts, comment
+% out the following line
+% \usepackage{newtxtext,newtxmath}
+% Depending on your LaTeX fonts installation, you might get better results with one of these:
+% \usepackage{mathptmx}
+% \usepackage{txfonts}
 
-\bibliographystyle{apj}
-%\bibliographystyle{yahapj}
-\citestyle{aa}
+% Use vector fonts, so it zooms properly in on-screen viewing software
+% Don't change these lines unless you know what you are doing
+\usepackage[T1]{fontenc}
+\usepackage{ae,aecompl}
 
-% General commands that are good for any astronomy paper.
+%%%%% AUTHORS - PLACE YOUR OWN PACKAGES HERE %%%%%
 \input{commands.tex}
 
-\makeatletter
-% Patch case where name and year are separated by aysep
-\patchcmd{\NAT@citex}
-  {\@citea\NAT@hyper@{%
-     \NAT@nmfmt{\NAT@nm}%
-     \hyper@natlinkbreak{\NAT@aysep\NAT@spacechar}{\@citeb\@extra@b@citeb}%
-     \NAT@date}}
-  {\@citea\NAT@nmfmt{\NAT@nm}%
-   \NAT@aysep\NAT@spacechar\NAT@hyper@{\NAT@date}}{}{}
+% Only include extra packages if you really need them. Common packages are:
+%\usepackage{epsf}
+\usepackage{color}
+\usepackage{graphicx}
+\usepackage{amsmath}	% Advanced maths commands
+\usepackage{amssymb}	% Extra maths symbols
+\usepackage{natbib}
+%\usepackage[colorlinks,urlcolor=blue,citecolor=blue,linkcolor=blue]{hyperref}
+\usepackage{multirow}
+\usepackage{etoolbox}
 
-% Patch case where name and year are separated by opening bracket
-\patchcmd{\NAT@citex}
-  {\@citea\NAT@hyper@{%
-     \NAT@nmfmt{\NAT@nm}%
-     \hyper@natlinkbreak{\NAT@spacechar\NAT@@open\if*#1*\else#1\NAT@spacechar\fi}%
-       {\@citeb\@extra@b@citeb}%
-     \NAT@date}}
-  {\@citea\NAT@nmfmt{\NAT@nm}%
-   \NAT@spacechar\NAT@@open\if*#1*\else#1\NAT@spacechar\fi\NAT@hyper@{\NAT@date}}
-
-%Commands specific to the this work
+%%%%% AUTHORS - PLACE YOUR OWN COMMANDS HERE %%%%%
 \newcommand{\editorial}[1]{\textcolor{red}{#1}}
@@
 
-%-----------------------------------------------------------------------------------------
+%%%%%%%%%%%%%%%%%%% TITLE PAGE %%%%%%%%%%%%%%%%%%%
+\title[Short Title]{Cluster Dynamics with HETDEX - I: Simulated Performance, Mass Distribution and Limits}
 
-\shorttitle{Cluster Dynamics with HETDEX}
-\shortauthors{BOADA ET AL.}
+% The list of authors, and the short list which is used in the headers.
+% If you need two or more lines of authors, add an extra line using \newauthor
+\author[S. Boada et al.]{
+Steven Boada,$^{1}$\thanks{E-mail: boada@physics.tamu.edu (SB)}
+C.~Papovich,$^{1}$
+R.~Wechsler$^{2,3}$
+\\
+% List of institutions
+$^{1}$George P.\ and Cynthia Woods Mitchell Institute for
+Fundamental Physics and Astronomy, Texas A\&M University, College Station, TX, 77843-4242\\
+$^{2}$Kavli Institute for Particle Astrophysics and Cosmology, Department of Physics, Stanford University, Stanford, CA 94305, USA\\
+$^{3}$Department of Particle Physics and Astrophysics, SLAC National Accelerator Laboratory, Menlo Park, CA 94025, USA}
 
-%\slugcomment{\it Draft Version \today}
-%\slugcomment{\it Submitted for publication in the Astrophysical Journal}
-%\slugcomment{Accepted for Publication in the Astrophysical Journal}
+% These dates will be filled out by the publisher
+\date{Accepted XXX. Received YYY; in original form ZZZ}
 
+% Enter the current year, for the copyright statements etc.
+\pubyear{2016}
+
+% Don't change these lines
 \begin{document}
-
-\title{HETDEX as a Galaxy Cluster Survey - I: Simulated Performance, Mass Distribution and Limits}
-
-\author{\sc Steven Boada\altaffilmark{1}, 
-C.~Papovich\altaffilmark{1}, and
-R.~Wechsler\altaffilmark{2,3}}
-
-\altaffiltext{1}{George P.\ and Cynthia Woods Mitchell Institute for
-Fundamental Physics and Astronomy, and Department of Physics and Astronomy,
-Texas A\&M University, College Station, TX, 77843-4242;
-boada@physics.tamu.edu}
-\altaffiltext{2}{Kavli Institute for Particle Astrophysics and Cosmology, Department of Physics, Stanford University, Stanford, CA 94305, USA}
-\altaffiltext{3}{Department of Particle Physics and Astrophysics, SLAC National Accelerator Laboratory, Menlo Park, CA 94025, USA}
+\label{firstpage}
+\pagerange{\pageref{firstpage}--\pageref{lastpage}}
+\maketitle
 
@@
 	\includegraphics[width=0.49\textwidth]{hmf.pdf} 
-	\caption{The cumulative MF of halos above $M_{200c}$ at $z=0.1$. The predicted MF is from \cite{Tinker2008}.} 
+	\caption{The cumulative MF of halos above $M_{200c}$ at $z=0.1$. The predicted MF is from tinker2008.} 
 	\label{fig: hmf} 
@@
 
-\acknowledgments 
+\section*{Acknowledgements}
 The authors also wish to thank the anonymous referee whose comments and suggestions significantly improved both the quality and clarity of this work.
@@
 Crawford for many helpful discussions.
-This research made use of This research made use of the \textsc{IPython} package \citep{Perez2007} and \textsc{matplotlib}, a Python library for publication quality graphics \citep{Hunter2007}.
+This research made use of This research made use of \textsc{APLpy}, an open-source plotting package for Python hosted at http://aplpy.github.com; the \textsc{IPython} package \citep{Perez2007}; \textsc{matplotlib}, a Python library for publication quality graphics \citep{Hunter2007}.
 Funding for the SDSS and SDSS-II has been provided by the Alfred P.
@@
 Department of Energy, the National Aeronautics and Space Administration, the Japanese Monbukagakusho, the Max Planck Society, and the Higher Education Funding Council for England.
+The SDSS Web Site is http://www.sdss.org/.
 The SDSS is managed by the Astrophysical Research Consortium for the Participating Institutions.
 
-\bibliography{master}
+%%%%%%%%%%%%%%%%%%%% REFERENCES %%%%%%%%%%%%%%%%%%
+% The best way to enter references is to use BibTeX:
+\bibliographystyle{mnras}
+\bibliography{master} % if your bibtex file is called example.bib
 
-% We compare the calculated cluster redshifts to the true redshift ($z_{c,true}$) for 114903 galaxies comprising 1379 unique halos, and we find a RMS$[\Delta z/(1+z_{c,true})]= 4\times 10^{-4}$ where $\Delta z = z_{c,true} - z_{c}$.
-\editorial{The RMS using just the regular mean is 3.8e-4 which is only slightly better than the biweight.
-I don't think that will be the case when we get more complicated things.}
+%%%%%%%%%%%%%%%%% APPENDICES %%%%%%%%%%%%%%%%%%%%%
+% \appendix
+%
+% \section{Some extra material}
+%
+% If you want to present additional material which would interrupt the flow of the main paper,
+% it can be placed in an Appendix which appears after the list of references.
 
+% Don't change these lines
+\bsp	% typesetting comment
+\label{lastpage}
 \end{document}
+
+% \begin{equation}
+%     x=\frac{-b\pm\sqrt{b^2-4ac}}{2a}.
+% 	\label{eq:quadratic}
+% \end{equation}
+%
+% % Example figure
+% \begin{figure}
+% 	% To include a figure from a file named example.*
+% 	% Allowable file formats are eps or ps if compiling using latex
+% 	% or pdf, png, jpg if compiling using pdflatex
+% 	\includegraphics[width=\columnwidth]{example}
+%     \caption{This is an example figure. Captions appear below each figure.
+% 	Give enough detail for the reader to understand what they're looking at,
+% 	but leave detailed discussion to the main body of the text.}
+%     \label{fig:example_figure}
+% \end{figure}
+%
+% % Example table
+% \begin{table}
+% 	\centering
+% 	\caption{This is an example table. Captions appear above each table.
+% 	Remember to define the quantities, symbols and units used.}
+% 	\label{tab:example_table}
+% 	\begin{tabular}{lccr} % four columns, alignment for each
+% 		\hline
+% 		A & B & C & D\\
+% 		\hline
+% 		1 & 2 & 3 & 4\\
+% 		2 & 4 & 6 & 8\\
+% 		3 & 5 & 7 & 9\\
+% 		\hline
+% 	\end{tabular}
+% \end{table}
+
+% \section{Evidence of Substructure}
+% Like the recovery of dynamical parameters discussed in the previous section, the choice of method to investigate the dynamical state of galaxy clusters is heavily debated.
+Perhaps the most widely used metric is the Dressler-Shectman (DS) test \citep{Dressler1988}, and is not without criticism \citeeg{White2010}.
+New methods such as the Caustic Method (\citealt{Yu2015}, and the references therein) offer promise to shed further light on this difficult problem.
+%
+% \subsection{From VD profiles}
+% We utilize the modality \citep{Oliva-Altamirano2014} which describes the Gaussianity of a LOSV distribution in a galaxy cluster.
+For clusters with Gaussian distributed LOSVs, the modality is close to 1/3.
+It is defined as $(1+\mathrm{skewness}^2)/(3+\mathrm{kurtosis}^2)$.
+\editorial{Do I need to describe what the skewness and kurtosis is?}
+%
+% \subsection{Dominance}
+% \editorial{This is taken pretty directly from the GAMA paper. Will need to be edited to fit.}
+% The dominance is defined as the luminosity gap between the brightest and the second brightest galaxy in a cluster ($\Delta m_{1, 2}$).
+The amplitude of the luminosity gap between the BGG/BCG and the second brightest galaxy in the halo, is expected to be a function of both the formation epoch and the recent infall history of the halo.
+A small magnitude gap ($\Delta m_{1, 2} < 1$) indicates a recent halo merger, and larger gaps ($\Delta m_{1, 2} > 1$), common in fossil groups, is perhaps indicative of a cluster or groups that has not undergone a recent merger.
+%
+% \subsection{Dressler-Schectman Test}
+% We leverage the large spectroscopic dataset to study the structural properties of the clusters.
+\cite{Pinkney1996} determine, from a comparison of five different methods that the DS test is the most sensitive to the presence of substructure.
+%
+% The DS test, which combines the spatial positions and velocities of the galaxies, provides a method to locate substructure by identifying groups of galaxies which differ significantly from the cluster velocity distribution.
+Galaxy subsets are selected from a cluster of $n_{members}$ and each constituent galaxy deviation is calculated according to
+% \begin{equation}
+% 	\delta_i^2 = \frac{N_{local}+1}{\sigma^2}\bigg{[}(\bar{v}_{local,i} - \bar{v})^2 + (\sigma_{local,i} - \sigma)^2\bigg{]}^2
+% \end{equation}
+% where $\bar{v}_{local}$ and $\sigma_{local}$ are the mean velocity and velocity dispersion for a subset of $N_{local}$ galaxies and $\bar{v}$ and $\sigma$ are the entire cluster's mean velocity and velocity dispersion.
+The choice of $N_{local}$ is left to the user.
+Originally, \cite{Dressler1988} choose $N_{local}=10$, however \cite{Bird1994} points out that using a fixed value for $N_{local}$ reduces the sensitivity to substructure.
+We follow \cite{Bird1994} in choosing $N_{local} = \sqrt n_{members}$.
+\editorial{doesn't talk about the nearest neighbors which is what we are using.}
+%
+% The DS statistic is the $\Delta$-value given by,
+% \begin{equation}
+% 	\Delta = \sum^{n_{members}}_i \delta_i
+% \end{equation}
+% where a system is considered to contain substructure if $\Delta/n_{members} > 1$ \citep{Dressler1988}.
+A second method, described in \cite{Hou2012}, uses probabilities (P-values) rather than a threshold for the identification of substructure.
+P-values are computed by comparing the observed $\Delta$-value and the $Delta$-value after the velocities (but not positions) have been shuffled through a series of Monte Carlo runs.
+The probability of the existence of substructure becomes
+% \begin{equation}
+% 	P = \sum (\Delta_{shuffled} > \Delta_{Observed}) / n_{shuffle}
+% \end{equation}
+% where $n_{shuffle}$ is the number of shufflings used.
+\editorial{This sounds a whole lot like the description given in Hou2012.
+Make sure that we aren't copying anything word for word.
+That'd be bad.}
+%
+% In practice, we use locate the nearest neighbors using an unsupervised k-nearest neighbor algorithm as implemented in Scikit-Learn \citep{Pedregosa2012}.

### 2016-01-21 ms.tex
added some text and tweaked
should now be working pretty well.

@@
 % \usepackage{newtxtext,newtxmath}
+\usepackage{times}
 % Depending on your LaTeX fonts installation, you might get better results with one of these:
@@
 %%%%% AUTHORS - PLACE YOUR OWN PACKAGES HERE %%%%%
-\input{commands.tex}
-
-% Only include extra packages if you really need them. Common packages are:
 %\usepackage{epsf}
@@
 %%%%% AUTHORS - PLACE YOUR OWN COMMANDS HERE %%%%%
+\input{commands.tex}
+
 \newcommand{\editorial}[1]{\textcolor{red}{#1}}
@@
 \author[S. Boada et al.]{
-Steven Boada,$^{1}$\thanks{E-mail: boada@physics.tamu.edu (SB)}
+Steven Boada,$^{1}$\thanks{E-mail: boada@physics.tamu.edu}
 C.~Papovich,$^{1}$
-R.~Wechsler$^{2,3}$
+R.~Wechsler,$^{2,3}$
+T. S.~Li,$^{1}$\newauthor\phantom{x}
+K.~Gebhardt,$^{4}$
+E.~Rozo,$^{2}$
+E. S.~Rykoff,$^{2}$
 \\
@@
 $^{2}$Kavli Institute for Particle Astrophysics and Cosmology, Department of Physics, Stanford University, Stanford, CA 94305, USA\\
-$^{3}$Department of Particle Physics and Astrophysics, SLAC National Accelerator Laboratory, Menlo Park, CA 94025, USA}
+$^{3}$Department of Particle Physics and Astrophysics, SLAC National Accelerator Laboratory, Menlo Park, CA 94025, USA\\
+$^{4}$The University of Texas}
 
@@
 \noindent
-ABSTRACT GOES HERE!!
-Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+The study of clusters of galaxies has been argued to be a very effective way to measure cosmological parameters, including measuring dark energy and testing models of gravity.
+The Hobby Eberly Telescope Dark Energy Experiment (HETDEX) will observe many hundreds of square degrees, covering a large sample of galaxy clusters out to $z = 0.5$ based on their optical spectra ($3500-5500\AAA$).
+The spectra will provide important measures of the clusters dynamics and may enable constraints on cosmological parameters, but only if the measurements provide accurate estimates of the total cluster masses.
+We have carried out a study to investigate the ability of HETDEX to recover accurate galaxy cluster masses over a wide range of masses and redshifts.
+We used a detailed mock galaxy catalog and present mock observations of two different scenarios: (1) We targeted individual galaxy clusters to investigate the recovery of parameters with such observations.
+(2) We created and evaluated a HETDEX-like selection "function'' of galaxies over a similarly sized portion of the sky and use well adopted techniques to recover the dynamical properties, such as velocity dispersion and mass.
+Using both observing strategies, we produce cluster mass probability density functions $P(X|M,z)$, which can be used to determine the probability that a galaxy cluster of given mass (M), located at redshift ($z$) determined using observable parameter (X).
+% We then applied these probability functions to ten galaxy clusters selected from the Sloan Digital Sky Survey DR8 and the Chandra-XMM X-ray Cluster Survey at $z=0.2-0.3$, and observed by the HETDEX spectrograph prototype instrument (VIRUS-p).
+We measured spectroscopic redshifts and line-of-sight velocities of the galaxies in and around each cluster, derived a line-of-sight velocity dispersion, and inferred a dynamical mass for each cluster which ranges from $(0.4-24) \times 10^{14} \Msol (M_{200c})$.
+Using the mass probability density functions described above, we updated these masses and compared them to existing literature estimates, or to the masses estimated from other observables such as X-ray temperature or richness.
 \end{abstract}
@@
 The goal is to constrain, as best possible, $P(X|M,z)$ the probability ($P$) that a galaxy cluster of given mass ($M$), located at redshift ($z$) determined using observable parameter ($X$).
-The observable parameter most commonly observed X-ray temperatures and luminosities \citeeg{Mantz2010, Rykoff2014, Mantz2015}, cosmic microwave background observations \citeeg{Vanderlinde2010, Sehgal2011} using the Sunyaev--Zel’dovich effect (SZE; \citealt{Sunyaev1972}) or optical studies \citeeg{Rozo2010, Rozo2015} of richness \citeeg{Abell1958, Rykoff2012} or galaxy velocity dispersions \citeeg{Ruel2014, Sifon2015}.
+The observable parameter most commonly observed X-ray temperatures and luminosities \citeeg{Mantz2010, Rykoff2014, Mantz2015}, cosmic microwave background observations \citeeg{Vanderlinde2010, Sehgal2011} using the Sunyaev-Zel'dovich effect (SZE; \citealt{Sunyaev1972}) or optical studies \citeeg{Rozo2010, Rozo2015} of richness \citeeg{Abell1958, Rykoff2012} or galaxy velocity dispersions \citeeg{Ruel2014, Sifon2015}.
 
@@
 \begin{figure} 
-	\includegraphics[width=0.49\textwidth]{hmf.pdf} 
-	\caption{The cumulative MF of halos above $M_{200c}$ at $z=0.1$. The predicted MF is from tinker2008.} 
+	\includegraphics[width=\columnwidth]{figures/hmf.pdf} 
+	\caption{The cumulative MF (from \citealt{Tinker2008}) of halos above $M_{200c}$ at $z=0.1$} 
 	\label{fig: hmf} 
@@
 \begin{figure*} 
-	\includegraphics[width=\textwidth]{oii_sdss.pdf} 
+	\includegraphics[width=\textwidth]{figures/oii_sdss.pdf} 
 	\caption{\textit{Left}: CMD of 503113 $z<0.2$ galaxies take from the SDSS DR12 where the shading scales with the density of points.
@@
 \begin{figure} 
-	\includegraphics[width=0.49\textwidth]{f01.pdf} 
+	\includegraphics[width=\columnwidth]{figures/f01.pdf} 
 	\caption{Representative observation tiling scheme for the HETDEX $16' \times 16'$ pointings.
@@
 
-\subsubsection{Probability Based}
+\subsubsection{Probability Based}\label{sec:probability method}
 We begin with the training sample.
@@
 \begin{figure} 
-	\includegraphics[width=0.5\textwidth]{cornertest.pdf} 
+	\includegraphics[width=\columnwidth]{figures/cornertest.pdf} 
 	\caption{Corner plot of the \emph{training} data with features $\sigma$ and $z$.
@@
 
-\subsubsection{Machine Learning Based}
+\subsubsection{Machine Learning Based}\label{sec:machine learning method}
 The estimation in this section relies on a ML technique known as an ensemble method, where many estimators are created by a single learning method with the goal of improved generalization and robustness compared to a single estimation.
@@
 The final prediction is then the average of all the trees.
-We use RF regression methods as implemented in {\sc Scikit-Learn} \citep{Pedregosa2012}.
+We use RF regression methods as implemented in {\tt Scikit-Learn} \citep{Pedregosa2012}.
 
@@
 \begin{figure*} 
-	\includegraphics[width=\textwidth]{recovery.pdf} 
+	\includegraphics[width=\textwidth]{figures/recovery.pdf} 
 	\caption{Recovery fractions ($N_{obs}/N_{True}$) of cluster member galaxies as a function of redshift and mass for the targeted (upper row) and survey (lower row) observing strategies.
@@
 \subsection{Mass estimates}
+In this section we discuss the how accurately we are able to reproduce the true cluster mass from a set of observations.
+We report on two methods the probability based approach (Section \ref{sec:probability method}) and the machine learning based method (Section \ref{sec:machine learning method}).
+For each method we consider both targeted and HETDEX-like observing strategies.
+
+All of the figures presented here show the predicted versus true cluster masses for one of the two observing strategies.
+In each panel the solid black line shows the 1:1 relationship, the colored, solid line is the median recovered mass, and the shaded region is the 68\% scatter of the cluster masses.
+The lower panels show the fractional mass error:
+\begin{equation}\label{eq: fractional error}
+	\epsilon = (M_{pred} - M)/M
+\end{equation}
+where $M_{pred}$ is the predicted cluster mass and $M$ is the true cluster mass.
+
+\subsubsection{Probability Based}
+Figures \ref{fig:Probability comparison_survey} and \ref{fig:Probability comparison} show the power law predictions compared to the predictions based on probability propagation.
+
 \begin{figure*} 
-	\includegraphics[width=\textwidth]{MLcomparison.pdf} 
+	\includegraphics[width=\textwidth]{figures/MLcomparison_survey.pdf} 
+	\caption{Mass predictions for the power law scaling relation (Equation~\ref{eq: mass scaling}) and the ML technique with different input features.
+The bottom row of panels shows the fractional error (Equation~\ref{eq: fractional error}) as a function of mass.
+The solid black line shows the 1:1 relation.
+The colored lines and shaded region show the median value and 68\% bounds respectively.} \label{fig:Probability comparison_survey}
+\end{figure*}
+
+\begin{figure*} 
+	\includegraphics[width=\textwidth]{figures/MLcomparison.pdf} 
+	\caption{Mass predictions for the power law scaling relation (Equation~\ref{eq: mass scaling}) and the ML technique with different input features.
+The bottom row of panels shows the fractional error (Equation~\ref{eq: fractional error}) as a function of mass.
+The solid black line shows the 1:1 relation.
+The colored lines and shaded region show the median value and 68\% bounds respectively.} \label{fig:Probability comparison}
+\end{figure*}
+
+\subsubsection{Machine Learning Based}
+Figures \ref{fig: ML comparison_survey} and \ref{fig: ML comparison} show the power law predictions compared to the RF predictions using LOSVD ($\sigma$) combined with both $z$ and the number of galaxies observed, $N_{gal}$.
+
+\begin{figure*} 
+	\includegraphics[width=\textwidth]{figures/MLcomparison_survey.pdf} 
+	\caption{Mass predictions for the power law scaling relation (Equation~\ref{eq: mass scaling}) and the ML technique with different input features.
+The bottom row of panels shows the fractional error (Equation~\ref{eq: fractional error}) as a function of mass.
+The solid black line shows the 1:1 relation.
+The colored lines and shaded region show the median value and 68\% bounds respectively.} \label{fig: ML comparison_survey}
+\end{figure*}
+
+\begin{figure*} 
+	\includegraphics[width=\textwidth]{figures/MLcomparison.pdf} 
 	\caption{Mass predictions for the power law scaling relation (Equation~\ref{eq: mass scaling}) and the ML technique with different input features.
@@
 
-\begin{equation}\label{eq: fractional error}
-	\epsilon = (M_{pred} - M)/M
-\end{equation}
-
-\editorial{It doesn't look like you can use the targeted training sample to train the survey data.
+% \editorial{It doesn't look like you can use the targeted training sample to train the survey data.
 If you do, it either does worse or about the same if you didn't use any training at all.
 After looking at it, you do have to use the survey training data to get good results about 0.13 dex MAE
-}
-
-Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+% }
 
@@
 Crawford for many helpful discussions.
-This research made use of This research made use of \textsc{APLpy}, an open-source plotting package for Python hosted at http://aplpy.github.com; the \textsc{IPython} package \citep{Perez2007}; \textsc{matplotlib}, a Python library for publication quality graphics \citep{Hunter2007}.
+This research made use of This research made use of  the {\tt IPython} package \citep{Perez2007} and {\tt matplotlib}, a Python library for publication quality graphics \citep{Hunter2007}.
 Funding for the SDSS and SDSS-II has been provided by the Alfred P.

### 2016-01-25 ms.tex
continued work

@@
-\documentclass[a4paper,fleqn,usenatbib]{mnras}
+\documentclass[fleqn,usenatbib]{mnras}
 
@@
 %\usepackage[colorlinks,urlcolor=blue,citecolor=blue,linkcolor=blue]{hyperref}
-\usepackage{multirow}
-\usepackage{etoolbox}
+%\usepackage{multirow}
+%\usepackage{etoolbox}
 
@@
 
-Blah blah intro stuff...
+\editorial{Blah blah intro stuff...
+Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
+Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
+Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.}
 
@@
 where $\sigma_p$, $\langle\mu\rangle$, and $\sigma_i$ is the LOSVD, the average radial velocity and the error on the individual LOSVs respectively.
-Using a Monte Carlo Markov Chain sampler ({\sc emcee}\footnote{\url{http://dan.iel.fm/emcee/current/}}, \citealt{Foreman-Mackey2013}), we draw twenty thousand samples from the posterior probability distribution.
-Simple priors, $\langle\mu\rangle$ lies between the maximum and minimum LOSV and $0< \sigma_p$, are used.
-When the full distribution of LOSVDs are not used, the final LOSVD is quoted as the median value of the probability distribution with 68\% error bars defined as the 16th and 84th percentiles of the same distribution.
+Using a Monte Carlo Markov Chain sampler (MCMC; {\tt emcee}\footnote{\url{http://dan.iel.fm/emcee/current/}}, \citealt{Foreman-Mackey2013}), we draw twenty thousand samples from the posterior probability distribution.
+Simple priors, $\langle\mu\rangle$ lies between the maximum and minimum LOSV and $0< \sigma_p$ \editorial{check}, are used.
+When the full distribution of LOSVDs are not used, the final LOSVD is quoted as the median value of the posterior probability distribution with 68\% error bars defined as the 16th and 84th percentiles of the same distribution.
 
 In principle, a single statistic such as the biweight scale estimator or the gapper estimator (both from \citealt{Beers1990}) with many bootstrap resamplings could be used to construct a distribution of $\sigma_p$.
-We prefer the maximum likelihood method for its straight forward treatment of the errors in the LOSV measurements.
-\editorial{Maybe run a quick check to see how they compare.}
+In simple tests where the values of both $\sigma_p$ and $\langle\mu\rangle$ are known.
+The 68\% error bars derived from the MCMC method give slightly better results with the true LOSVD value bracketed by the error bars in $\sim68\%$ of the cases versus $\sim57\%$ with bootstrapping and a single statistic.
+In addition, we prefer the maximum likelihood method for its straight forward treatment of the errors in the LOSV measurements.
 
@@
 The 68\% prediction interval is determined by calculating the 16th and 84th percentile of all the predictions made by the ensemble of estimators.
+\editorial{should talk about how random forests can give error bars on the individual estimates.}
 
@@
 
-Figure~\ref{fig: recovery} shows the recovery fraction of member galaxies, the number of observed versus the number of actual galaxies, as a function of both redshift and cluster mass for the targeted and survey observing strategies.
+Figure \ref{fig: recovery} shows the recovery fraction of member galaxies, the number of observed galaxies divided by the number of actual galaxies, as function of both redshift and cluster mass.
+It is important to note that if few than five member galaxies are observed the cluster is not considered detected, and is excluded from this plot.
 As expected, the targeted observing strategy where the individual clusters are targeted through several dithers to ensure near complete coverage, performs significant better than the survey observing strategy for nearly all redshifts and cluster masses.
+
+\editorial{There is no obvious trend between number of galaxies observed and redshift.
+There is a trend between number of galaxies observed and cluster mass though.
+This is the "richness" and it's something that we should have expected.
+To test where the galaxies go we are going to apply an absolute magnitude cut instead of the apparent magnitude cut and then derive the catalog.
+That will let us know if things are going on.}
+
 This performance gain is due solely to the gaps between the fiber bundles of the IFU.
@@
 where $M_{pred}$ is the predicted cluster mass and $M$ is the true cluster mass.
+
+Any scatter in recovered masses can be attributed to both physical and numerical effects.
+As the cluster mass increases, clusters become more virialized and contain many individual galaxies.
+The presence of any in-falling matter onto lower mass clusters can introduce a significant amount of substructure, which can increase the observed LOSVD increasing the predicted mass.
+Also, as the number of cluster galaxies decreases the LOSVD PDF is poorly sampled leading to poorly recovered cluster masses due to numerical effects.
+The masses presented here are recovered using the best possible conditions, where we have perfect knowledge of the cluster membership.
+In reality, the mass recovery levels presented in this section represent a lower bound on the accuracy achievable through this method.
+\editorial{\cite{Ntampaka2015} does have a discussion about how well they do with contaiminated galaxy catalogs.
+We could do something similar and have a similar discussion, but I'm not sure it is worth it.
+Should be simple enough to do with the targeted catalog, but with the HETDEX catalog it would be pretty bad IMO.}
 

### 2016-01-29 ms.tex
still writing

@@
 % out the following line
-% \usepackage{newtxtext,newtxmath}
-\usepackage{times}
+\usepackage{newtxtext,newtxmath}
+%\usepackage{times}
 % Depending on your LaTeX fonts installation, you might get better results with one of these:
@@
 where $\sigma_p$, $\langle\mu\rangle$, and $\sigma_i$ is the LOSVD, the average radial velocity and the error on the individual LOSVs respectively.
-Using a Monte Carlo Markov Chain sampler (MCMC; {\tt emcee}\footnote{\url{http://dan.iel.fm/emcee/current/}}, \citealt{Foreman-Mackey2013}), we draw twenty thousand samples from the posterior probability distribution.
+Using a Monte Carlo Markov Chain (MCMC) sampler ({\tt emcee}\footnote{\url{http://dan.iel.fm/emcee/current/}}; \citealt{Foreman-Mackey2013}), we draw twenty thousand samples from the posterior probability distribution.
 Simple priors, $\langle\mu\rangle$ lies between the maximum and minimum LOSV and $0< \sigma_p$ \editorial{check}, are used.
@@
 
+Any uncertainties quoted by this method are, in fact, prediction intervals.
+A prediction interval is an estimate of the interval encompassing future observations, with a certain probability.
+And, unlike confidence intervals, which describe certainties on the different moments of a population, a prediction interval is unique to each prediction.
+In many regresson analyses, such as linear fitting, the prediction intervals are based on underlying assumptions of normally distributed residuals.
+However, RF estimators do not have any such assumptions and require special treatment.
+
+The prediction intervals here are based on the general method of quantile regression forests \citep{Meinshausen2006}.
+
 The 68\% prediction interval is determined by calculating the 16th and 84th percentile of all the predictions made by the ensemble of estimators.
@@
 \subsection{Recovery of Cluster Members}
-As discussed in Section~\ref{sec: observations} the observational constraints place limits on the total number fo clusters member galaxies expected to be recovered.
+As discussed in Section \ref{sec: observations} the observational constraints place limits on the total number fo clusters member galaxies expected to be recovered.
 Knowing these limits will provide important information for potential future follow up or targeted observations.
@@
 	\includegraphics[width=\textwidth]{figures/recovery.pdf} 
-	\caption{Recovery fractions ($N_{obs}/N_{True}$) of cluster member galaxies as a function of redshift and mass for the targeted (upper row) and survey (lower row) observing strategies.
+	\caption{Recovery fractions ($N_{obs}/N_{True}$) of cluster member galaxies as a function of redshift and mass for the targeted and survey observing strategies.
+The solide lines are the median values and the shaded regions represent the 68\% scatter.
 The significant decline in galaxies observed with the survey strategy is due to gaps in the VIRUS IFU.} \label{fig: recovery}
@@
 
-Figure \ref{fig: recovery} shows the recovery fraction of member galaxies, the number of observed galaxies divided by the number of actual galaxies, as function of both redshift and cluster mass.
-It is important to note that if few than five member galaxies are observed the cluster is not considered detected, and is excluded from this plot.
-As expected, the targeted observing strategy where the individual clusters are targeted through several dithers to ensure near complete coverage, performs significant better than the survey observing strategy for nearly all redshifts and cluster masses.
+Figure \ref{fig: recovery} shows the recovery fraction of member galaxies, the number of observed galaxies divided by the number of actual galaxies ($N_{obs}/N_{True}$), as function of both redshift and cluster mass.
+It is important to note that if few than five member galaxies are observed the cluster is not considered detected, and is excluded from this figure.
+As expected, the targeted observing strategy where the individual clusters are targeted through several dithers to ensure near complete coverage, performs significantly better than the survey observing strategy across all redshifts and cluster masses.
 
-\editorial{There is no obvious trend between number of galaxies observed and redshift.
-There is a trend between number of galaxies observed and cluster mass though.
-This is the "richness" and it's something that we should have expected.
-To test where the galaxies go we are going to apply an absolute magnitude cut instead of the apparent magnitude cut and then derive the catalog.
-That will let us know if things are going on.}
+For the clusters recovered as a function of redshift, there are two effects at work.
+The decrease in recovery fraction with increasing redshift is a magnitude effect.
+If, instead of being limited to 22 mag in \sdssg apparent, the observations where limited by absolute magnitude, the sharp downward trend disappears.
+The second key feature is the strong decline in clusters recovered from survey observations.
+This is due to gaps in the VIRUS IFU.
+The median recovery fraction in survey observations is almost exactly 4.5 times less than the targeted median recovery fraction.
+As the total filling factor of the survey increases the two lines will converge.
 
-This performance gain is due solely to the gaps between the fiber bundles of the IFU.
-
-\editorial{why does the recovery fraction decrease with redshift?
-Are the clusters smaller?
-Do they not have as many galaxies per cluster at higher redshifts?
-Is it a magnitude effect?
-I also want to add an error bar estimation for several of the percentages to give a feel for how the different recovery levels effect the accuracy of the measurements.}
+The recovery rate as a function of cluster mass, right panel of Figure \ref{fig: recovery}, shows that of the the low mass clusters we detect ($N_{obs} >5$), observe the majority of the galaxies.
+This also shows a rapid decrease in the detection fraction, which can again be explained by considering absolute magnitudes instead of apparent magnitudes.
+Just as before, if the survey was limited by absolute magnitude, we find a much more consistent detection fraction.
 
@@
 In reality, the mass recovery levels presented in this section represent a lower bound on the accuracy achievable through this method.
-\editorial{\cite{Ntampaka2015} does have a discussion about how well they do with contaiminated galaxy catalogs.
+\editorial{\cite{Ntampaka2015} does have a discussion about how well they do with contaminated galaxy catalogs.
 We could do something similar and have a similar discussion, but I'm not sure it is worth it.
-Should be simple enough to do with the targeted catalog, but with the HETDEX catalog it would be pretty bad IMO.}
+Should be simple enough to do with the targeted catalog, but with the HETDEX catalog it would be pretty bad IMO.
+We should also talk about how often the true mass lies within the error bars.
+Many of them are going to be with the 68\% range, but we can drop the error estimates to $0.5\sigma$ if that actually means anything}
 
@@
 \end{figure*}
+
+\editorial{Need to talk about the cluster rotations to fill out the survey data. Otherwise there aren't that many clusters detected.}
 

### 2016-02-03 ms.tex
keep working
also updated the commands file to use the multi column command

@@
 %\usepackage[colorlinks,urlcolor=blue,citecolor=blue,linkcolor=blue]{hyperref}
-%\usepackage{multirow}
-%\usepackage{etoolbox}
+\usepackage{multirow}
+\usepackage{etoolbox}
 
@@
 \fi}
+\newcommand{\multic}[2]{\multicolumn{#1}{c}{#2}}
 
@@
 Recently, the relationship between the LOSVD and dynamical mass has been the focus of several studies \citeeg{Evrard2008, Saro2013, Sifon2013, VanderBurg2014}, and a best fitting relationship for the mass enclosed by $r_{200c}$ of the form
-\begin{equation}\label{eq: mass scaling}
+\begin{equation}\label{eq:power law}
 	M_{200c} = \frac{10^{15}}{h(z)} \bigg{(}\frac{\sigma_{1D}}{A_{1D}} \bigg{)}^{1/\alpha} \Msol
@@
 Specifically, while there is little difference between using galaxies and their host DM subhalos, there is a significant over estimation of the LOSVD when using galaxies/subhalos compared to DM particles \citep{Munari2013}.
-We follow other works \citeeg{Kirk2015, Sifon2015a} using the scaling relation, given in Equation~\ref{eq: mass scaling} from \cite{Munari2013} to facilitate comparisons with other observational studies.
+We follow other works \citeeg{Kirk2015, Sifon2015a} using the scaling relation, given in Equation~\ref{eq:power law} from \cite{Munari2013} to facilitate comparisons with other observational studies.
 % \editorial{This all needs to be stripped out and reworked.}
@@
 
-Any uncertainties quoted by this method are, in fact, prediction intervals.
+Any uncertainties quoted by this method are prediction intervals not confidence intervals.
 A prediction interval is an estimate of the interval encompassing future observations, with a certain probability.
@@
 The prediction intervals here are based on the general method of quantile regression forests \citep{Meinshausen2006}.
-
-The 68\% prediction interval is determined by calculating the 16th and 84th percentile of all the predictions made by the ensemble of estimators.
-\editorial{should talk about how random forests can give error bars on the individual estimates.}
+The general idea is that all response variables are recorded, not just the mean.
+Then the prediction can be returned as the full conditional probability distribution of all responses, which allows us to generate the prediction intervals.
+The 68\% prediction interval is determined by calculating the 16th and 84th percentile of the full conditional probability distribution.
 
@@
 Here we explore the cluster member recovery rate and mass estimates for the two observing strategies.
-We discuss the accuracy of dynamical mass derived from both the scaling relation (see Equation~\ref{eq: mass scaling}) and through the probability and ML methods.
+We discuss the accuracy of dynamical mass derived from both the scaling relation (see Equation \ref{eq:power law}) and through the probability and ML methods.
 
@@
 In this section we discuss the how accurately we are able to reproduce the true cluster mass from a set of observations.
-We report on two methods the probability based approach (Section \ref{sec:probability method}) and the machine learning based method (Section \ref{sec:machine learning method}).
+We report on two methods the probability based approach (Section \ref{sec:probability method}) and the ML based method (Section \ref{sec:machine learning method}).
 For each method we consider both targeted and HETDEX-like observing strategies.
 
-All of the figures presented here show the predicted versus true cluster masses for one of the two observing strategies.
-In each panel the solid black line shows the 1:1 relationship, the colored, solid line is the median recovered mass, and the shaded region is the 68\% scatter of the cluster masses.
-The lower panels show the fractional mass error:
+Both of the figures shown below show the predicted versus true cluster masses for each of the two observing strategries.
+In each panel the solid black line is the 1:1 relationship, the solid colored line is the median recovered mass for the targeted observing, and the colored, dashed line is the median recovered mass for the HETDEX-like observations.
+The shaded regions are the 68\% scatter around the median values (the 16\% and 84\% quartiles).
+The lower panels show the fractional cluster mass error:
 \begin{equation}\label{eq: fractional error}
@@
 
-Any scatter in recovered masses can be attributed to both physical and numerical effects.
+In both figures, we include the cluster masses recovered through the power law scaling relation given in Equation \ref{eq:power law} for both the targeted and survey observations.
+It should serve as baseline to compare the probability based and ML cluster mass recovery methods.
+And, while there are many possible metrics to evaluate performance, we compute two: the median absolute error (MAE) and the root mean squared error (RMSE).
+Both metrics evaluate how closely the ensemble of predicted cluster masses are to the true cluster masses, and in both cases lower numbers are better.
+
+Just because a predicted cluster mass may not exactly match the true value does not mean it is a bad prediction.
+In addition to the MAE and RMSE, we also report the fraction of predictions where the the true cluster mass is contained within the 68\% confidence or prediction intervals (see Sections \ref{sec:probability method} and \ref{sec:machine learning method}).
+
+The cluster masses predicted by Equation \ref{eq:power law} gives the following results.
+The MAE is 0.263 dex and for both the targeted and survey observations.
+The RMSE is 0.396 dex and 0.394 dex for the targeted and survey observations respectively.
+This scatter in recovered masses can be attributed to both physical and numerical effects.
 As the cluster mass increases, clusters become more virialized and contain many individual galaxies.
@@
 The masses presented here are recovered using the best possible conditions, where we have perfect knowledge of the cluster membership.
-In reality, the mass recovery levels presented in this section represent a lower bound on the accuracy achievable through this method.
+In reality, the mass recovery levels presented in this section represent an upper bound (the best) on the accuracy achievable through this method.
 \editorial{\cite{Ntampaka2015} does have a discussion about how well they do with contaminated galaxy catalogs.
@@
 \subsubsection{Probability Based}
-Figures \ref{fig:Probability comparison_survey} and \ref{fig:Probability comparison} show the power law predictions compared to the predictions based on probability propagation.
+Figure \ref{fig:Probability comparison} shows the cluster mass predictions for the power law scaling relation and the probability based method with different input features.
 
 \begin{figure*} 
-	\includegraphics[width=\textwidth]{figures/MLcomparison_survey.pdf} 
-	\caption{Mass predictions for the power law scaling relation (Equation~\ref{eq: mass scaling}) and the ML technique with different input features.
-The bottom row of panels shows the fractional error (Equation~\ref{eq: fractional error}) as a function of mass.
+	\includegraphics[width=\textwidth]{figures/Probcomparison.pdf} 
+	\caption{Mass predictions for the power law scaling relation (Equation~\ref{eq:power law}) and the probability based technique with different input features as a function of true cluster mass.
+The bottom row of panels shows the fractional error (Equation~\ref{eq: fractional error}) also as a function of true cluster mass.
 The solid black line shows the 1:1 relation.
-The colored lines and shaded region show the median value and 68\% bounds respectively.} \label{fig:Probability comparison_survey}
-\end{figure*}
-
-\begin{figure*} 
-	\includegraphics[width=\textwidth]{figures/MLcomparison.pdf} 
-	\caption{Mass predictions for the power law scaling relation (Equation~\ref{eq: mass scaling}) and the ML technique with different input features.
-The bottom row of panels shows the fractional error (Equation~\ref{eq: fractional error}) as a function of mass.
-The solid black line shows the 1:1 relation.
-The colored lines and shaded region show the median value and 68\% bounds respectively.} \label{fig:Probability comparison}
+The solid, colored line is the median predicted mass for the targeted observing, and the colored, dashed line is the median recovered mass for the HETDEX-like observations.
+The shaded regions represent the 68\% scatter around the median values.} \label{fig:Probability comparison}
 \end{figure*}
@@
 \subsubsection{Machine Learning Based}
-Figures \ref{fig: ML comparison_survey} and \ref{fig: ML comparison} show the power law predictions compared to the RF predictions using LOSVD ($\sigma$) combined with both $z$ and the number of galaxies observed, $N_{gal}$.
-
-\begin{figure*} 
-	\includegraphics[width=\textwidth]{figures/MLcomparison_survey.pdf} 
-	\caption{Mass predictions for the power law scaling relation (Equation~\ref{eq: mass scaling}) and the ML technique with different input features.
-The bottom row of panels shows the fractional error (Equation~\ref{eq: fractional error}) as a function of mass.
-The solid black line shows the 1:1 relation.
-The colored lines and shaded region show the median value and 68\% bounds respectively.} \label{fig: ML comparison_survey}
-\end{figure*}
-
+Figure \ref{fig: ML comparison} show the power law predictions compared to the RF predictions using LOSVD ($\sigma$) combined with both $z$ and the number of galaxies observed, $N_{gal}$.  
 \begin{figure*} 
 	\includegraphics[width=\textwidth]{figures/MLcomparison.pdf} 
-	\caption{Mass predictions for the power law scaling relation (Equation~\ref{eq: mass scaling}) and the ML technique with different input features.
-The bottom row of panels shows the fractional error (Equation~\ref{eq: fractional error}) as a function of mass.
+	\caption{Mass predictions for the power law scaling relation (Equation~\ref{eq:power law}) and the ML based technique with different input features as a function of true cluster mass.
+The bottom row of panels shows the fractional error (Equation~\ref{eq: fractional error}) also as a function of true cluster mass.
 The solid black line shows the 1:1 relation.
-The colored lines and shaded region show the median value and 68\% bounds respectively.} \label{fig: ML comparison}
+The solid, colored line is the median predicted mass for the targeted observing, and the colored, dashed line is the median recovered mass for the HETDEX-like observations.
+The shaded regions represent the 68\% scatter around the median values.} \label{fig: ML comparison}
 \end{figure*}
@@
 
+\begin{table*}
+\centering
+\caption{Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
+Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
+Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.}
+	\begin{tabular}{ccccccc}
+		%\hline
+		& \multic{3}{Targeted} & \multic{3}{Survey} \\
+		\cline{2-4} \cline{5-7}
+		Input Features & MAE (dex) & RMSE (dex) & Overlap & MAE (dex) & RMSE (dex) & Overlap \\
+		\hline \hline
+		Power Law & 0.263 & 0.396 & --- & 0.263 & 0.393 & --- \\
+		$\sigma$ & 0.246 & 0.361 & --- & 0.238 & 0.344 & --- \\
+		$\sigma, z$ & 0.193 & 0.285 & --- & 0.171 & 0.260 & --- \\
+		$\sigma, z, N_{gal}$ & 0.117 & 0.193 & --- & 0.093 & 0.179 & --- \\
+
+		\hline
+	\end{tabular}
+\label{tbl: derived parameters}
+\end{table*}
+
 \section{HETDEX as a Galaxy Cluster Survey}
@@
 \subsection{Expected Results}
+\editorial{This is where I am going to discuss the redMapper stuff.}
 Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
@@
 The SDSS is managed by the Astrophysical Research Consortium for the Participating Institutions.
+\editorial{People to thank: Joe, maybe authorship.}
 

### 2016-02-04 ms.tex
keep working

@@
 \newcommand{\multic}[2]{\multicolumn{#1}{c}{#2}}
+\newcommand{\rottext}[2]{\multirow{#1}{*}{\rotatebox[origin=c]{90}{#2}}}
 
@@
 
-\editorial{Give outline of paper section.}
+We begin in Section \ref{sec:Data} by giving an overview of what data is used, how it is created, and how we make our ``observations.'' Details about the determination of cluster parameters, velocity dispersion, total mass, etc., are discussed in Section \ref{sec:recovery}.
+Next, we present the results of our study in Section \ref{sec:results} and discuss their implications in Section \ref{sec:discussion}.
+Finally we summarize our findings in Section \ref{sec:summary}.
 
@@
 
-\section{Data and Mock Observations}\label{sec: Data}
+\section{Data and Mock Observations}\label{sec:Data}
 
@@
 
-\section{Recovery of Parameters}\label{sec: recovery}
+\section{Recovery of Parameters}\label{sec:recovery}
  In the following sections, we outline the methods we use to derive the dynamical properties of the galaxy clusters in our sample.
@@
 
-\section{RESULTS}\label{sec: results}
+\section{RESULTS}\label{sec:results}
 Here we explore the cluster member recovery rate and mass estimates for the two observing strategies.
@@
 
-Both of the figures shown below show the predicted versus true cluster masses for each of the two observing strategries.
-In each panel the solid black line is the 1:1 relationship, the solid colored line is the median recovered mass for the targeted observing, and the colored, dashed line is the median recovered mass for the HETDEX-like observations.
-The shaded regions are the 68\% scatter around the median values (the 16\% and 84\% quartiles).
-The lower panels show the fractional cluster mass error:
-\begin{equation}\label{eq: fractional error}
-	\epsilon = (M_{pred} - M)/M
-\end{equation}
-where $M_{pred}$ is the predicted cluster mass and $M$ is the true cluster mass.
-
 In both figures, we include the cluster masses recovered through the power law scaling relation given in Equation \ref{eq:power law} for both the targeted and survey observations.
@@
 
-\subsubsection{Probability Based}
-Figure \ref{fig:Probability comparison} shows the cluster mass predictions for the power law scaling relation and the probability based method with different input features.
+\begin{table*}
+\centering
+\caption{Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
+Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
+Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.}
+\begin{tabular}{cccccccc}
+	%\hline
+	&& \multic{3}{Targeted} & \multic{3}{Survey} \\
+	\cline{3-5} \cline{6-8}
+	& Input Features & MAE & RMSE & Overlap & MAE & RMSE & Overlap \\
+	& & (dex) & (dex) & (\%) & (dex) & (dex) & (\%) \\
+	\hline
+	\rottext{4}{Prob Based} & Power Law & 0.263 & 0.396 & --- & 0.263 & 0.393 & --- \\
+	&$\sigma$ & 0.220 & 0.335 & --- & 0.222 & 0.329 & --- \\
+	&$\sigma, z$ & 0.189 & 0.286 & --- & 0.194 & 0.278 & --- \\
+	&$\sigma, z, N_{gal}$ & 0.129 & 0.207 & --- & 0.140 & 0.222 & --- \\
+
+	\hline
+	\rottext{4}{ML Based} & Power Law & 0.263 & 0.396 & --- & 0.263 & 0.393 & --- \\
+	&$\sigma$ & 0.246 & 0.361 & --- & 0.238 & 0.344 & --- \\
+	&$\sigma, z$ & 0.193 & 0.285 & --- & 0.171 & 0.260 & --- \\
+	&$\sigma, z, N_{gal}$ & 0.117 & 0.193 & --- & 0.093 & 0.179 & --- \\
+
+	\hline
+\end{tabular}
+\label{tbl:mass comparisons}
+\end{table*}
+
+The MAE and RMSE associated with the ensemble of predictions are summarized in Table \ref{tbl:mass comparisons}.
+As expected, we find that both the probability based and ML based methods out perform the standard power law based methods for both the targeted and survey observations.
+We also find that the ML based method produces lower ensemble error for both the observation strategies when compared to the probability based method, although the MAE and RMSE are reduced by only $\sim0.01$ dex.
+\editorial{here is where we would talk about cross validation on the errors.}
+
+In both Figures \ref{fig:Probability comparison} and \ref{fig: ML comparison}, we show the predicted versus true cluster masses for each of the two observing strategries.
+In each panel the solid black line is the 1:1 relationship, the solid colored line is the median recovered mass for the targeted observing, and the colored, dashed line is the median recovered mass for the HETDEX-like observations.
+The shaded regions are the 68\% scatter around the median values (the 16\% and 84\% quartiles).
+The lower panels show the fractional cluster mass error:
+\begin{equation}\label{eq: fractional error}
+	\epsilon = (M_{pred} - M)/M
+\end{equation}
+where $M_{pred}$ is the predicted cluster mass and $M$ is the true cluster mass.
+
+In both figures we successively add additional information to further contrain the true cluster masses which subsequently reduces the error associated with the ensemble of predictions (see Table \ref{tbl:mass comparisons}).
+The power law derived masses, using the single (not including the cosmological parameters) free parameter, $\sigma$ (the LOSVD), over estimates the predicted cluster mass at all masses.
+Both the probability and ML methods over predict the mass of low mass clusters and under predict the mass of the higher mass clusters.
+When the redshift information is also added, the amount of this over and under prediction is lessened but the cross over point, remains roughly consistent at $\sim10^{14}$ \msol.
+Additionally, the number of galaxies observed, $N_{gal}$, further reduces the MAE and RMSE on the predictions but also lowers the cross over point to $\sim10^{13.5}$ \msol.
 
@@
 
-\subsubsection{Machine Learning Based}
-Figure \ref{fig: ML comparison} show the power law predictions compared to the RF predictions using LOSVD ($\sigma$) combined with both $z$ and the number of galaxies observed, $N_{gal}$.  
 \begin{figure*} 
@@
 
-\begin{table*}
-\centering
-\caption{Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.}
-	\begin{tabular}{ccccccc}
-		%\hline
-		& \multic{3}{Targeted} & \multic{3}{Survey} \\
-		\cline{2-4} \cline{5-7}
-		Input Features & MAE (dex) & RMSE (dex) & Overlap & MAE (dex) & RMSE (dex) & Overlap \\
-		\hline \hline
-		Power Law & 0.263 & 0.396 & --- & 0.263 & 0.393 & --- \\
-		$\sigma$ & 0.246 & 0.361 & --- & 0.238 & 0.344 & --- \\
-		$\sigma, z$ & 0.193 & 0.285 & --- & 0.171 & 0.260 & --- \\
-		$\sigma, z, N_{gal}$ & 0.117 & 0.193 & --- & 0.093 & 0.179 & --- \\
-
-		\hline
-	\end{tabular}
-\label{tbl: derived parameters}
-\end{table*}
-
-\section{HETDEX as a Galaxy Cluster Survey}
+\section{HETDEX as a Galaxy Cluster Survey}\label{sec:discussion}
 
 \subsection{Expected Results}
-\editorial{This is where I am going to discuss the redMapper stuff.}
+\editorial{Expected results in what context?
+How well we can obtain cluster masses?
+How many masses will we get to what accuracy?
+This is sorta talk about in the results section but we don't really come out and say "this is what we think HETDEX will and and how well we think it will do it." That might worth saying, even if we are wrong it will give people a starting point when thinking about this stuff in the future.}
 Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
@@
 \subsection{Potential Improvements}
+\editorial{The potential improvements are really three fold.
+We know that the observing won't cover all of the sky.
+So we can simply tile more and try to get more clusters.
+We can observe deeper.
+I'm not sure the current exposure times (they are in an email that I sent to casey) but if we can extend them, then we can get further down the IMF and try to build up some of the clusters that are really more like groups than anything else.
+The last thing we can do is to attempt to  build better models to make better predictions on the masses.
+That might be something like the study that \cite{Acquaviva2016} did with the stellar metallicities.
+Or we'll need something else that I haven't thought of just yet.}
+
 Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
@@
 \subsection{Extendability to Other Surveys}
+\editorial{This is where I am going to discuss the redMapper stuff.
+In this section I want to talk about the calibration of the red sequence (i think), and how we might be able to use HETDEX to help nail that down and then use those relationships to better calibrate the cluster masses coming out of DES and LSST.
+Other surveys that we can think of that people might apply this sort of method to?
+GOGREEN?
+GAMA?
+There are going to be a good number of blind photometric surveys, but I can't really think of another blind spectroscopy survey or some survey that is designed to one specific thing that we can try to co-opt to do what we want.}
 Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
@@
 
-\section{SUMMARY}
+\section{SUMMARY}\label{sec:summary}
 Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
@@
 Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+
+Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
+Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
+Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+
+Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
+Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
+Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+
+It is our hope that this work may be useful to others when conducting their own research.
+Because this work relies heavily on (often) complex data analysis, and in order to promote transparency, we provide all of the code used to conduct this study at https://github.com/boada/desCluster.
+Regrettably, large file size prevents including the source data with the analysis routines.
+The authors are happy to provide them, if requested.
 

### 2016-02-17 ms.tex
lots of updates

@@
 
-\begin{figure} 
-	\includegraphics[width=\columnwidth]{figures/hmf.pdf} 
-	\caption{The cumulative MF (from \citealt{Tinker2008}) of halos above $M_{200c}$ at $z=0.1$} 
-	\label{fig: hmf} 
-\end{figure}
+% \begin{figure}
+% 	\includegraphics[width=\columnwidth]{figures/hmf.pdf}
+% 	\caption{The cumulative MF (from \citealt{Tinker2008}) of halos above $M_{200c}$ at $z=0.1$}
+% 	\label{fig: hmf}
+% \end{figure}
 
@@
 The 68\% prediction interval is determined by calculating the 16th and 84th percentile of the full conditional probability distribution.
+\editorial{I am going to change this to just the std of the distribution.
+I need the errorbars to be sysmetric to make the fitting routine easy later on.}
 
@@
 We discuss the accuracy of dynamical mass derived from both the scaling relation (see Equation \ref{eq:power law}) and through the probability and ML methods.
-
-\subsection{Recovery of Cluster Members}
-As discussed in Section \ref{sec: observations} the observational constraints place limits on the total number fo clusters member galaxies expected to be recovered.
-Knowing these limits will provide important information for potential future follow up or targeted observations.
 
@@
 \end{figure*}
+
+\subsection{Recovery of Cluster Members}
+As discussed in Section \ref{sec: observations} the observational constraints place limits on the total number fo clusters member galaxies expected to be recovered.
+Knowing these limits will provide important information for potential future follow up or targeted observations.
 
@@
 \centering
-\caption{Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.}
+\caption{Summary of the errors associated with the Targeted and Survey observation strategies, as an ensemble of predictions.
+See the text for discussion about the MAE and RMSE.
+Overlap is the percentage of clusters where the true cluster mass is bracketed by the prediction intervals of the predicted mass.
+See Sections \ref{sec:probability method} and \ref{sec:machine learning method} for a discussion on prediction intervals.}
 \begin{tabular}{cccccccc}
@@
 
-\subsection{Expected Results}
-\editorial{Expected results in what context?
+% \subsection{Expected Results}
+% \editorial{Expected results in what context?
 How well we can obtain cluster masses?
@@
 This is sorta talk about in the results section but we don't really come out and say "this is what we think HETDEX will and and how well we think it will do it." That might worth saying, even if we are wrong it will give people a starting point when thinking about this stuff in the future.}
-Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+% Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
 Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
@@
 That might be something like the study that \cite{Acquaviva2016} did with the stellar metallicities.
-Or we'll need something else that I haven't thought of just yet.}
+Or we'll need something else that I haven't thought of just yet.
+The other idea is to come up with some sort of cheat sheet for HETDEX.
+Basically, a if you detect such and such type of galaxy in the survey model then you should go back and try to follow it up with targeted observations.
+It might be good to talk about the recovery fraction between the two surveys above.
+Like...
+if there are 30 cluster members then we should detect the cluster in both surveys.}
 
@@
 \subsection{Extendability to Other Surveys}
-\editorial{This is where I am going to discuss the redMapper stuff.
-In this section I want to talk about the calibration of the red sequence (i think), and how we might be able to use HETDEX to help nail that down and then use those relationships to better calibrate the cluster masses coming out of DES and LSST.
-Other surveys that we can think of that people might apply this sort of method to?
-GOGREEN?
-GAMA?
-There are going to be a good number of blind photometric surveys, but I can't really think of another blind spectroscopy survey or some survey that is designed to one specific thing that we can try to co-opt to do what we want.}
-Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+Large-scale optical surveys (\eg, DES and LSST) expect to detect hundreds of thousands of galaxy clusters at $z < 1$.
+Because they are photometric, a major challenge for these surveys is relating a cluster observable to the total dark-matter mass.
+One promising mass estimator is the optical richness \citeeg{Abell1958}.
+Specifically, here, we use $\lambda$, the weighted number of galaxies within a scale aperture \citeeg{Rozo2011} as calculated by the redMapper algorithm \citep{Rykoff2012}.
+Previous works \citeeg{Rozo2010} show that the richness correlates strongly with cluster mass on the average, but the absolute mass scale of the optical richness mass estimator and the scatter in cluster mass at fixed optical richness are imprecisely known \citep{Rykoff2012}.
+These systematics remain the major source of uncertainty in deriving cosmological constraints from cluster abundances and must be measured using independent methods to realize the full potential of these surveys.
+
+\begin{figure} 
+	\includegraphics[width=\columnwidth]{figures/massRichness_targeted.pdf} 
+	\caption{The optical richness, $\lambda$, versus the predicted cluster mass.
+The purple and blue points represent clusters with targeted and survey detections respectively.
+Error bars show $1\sigma$ prediction interval.
+The solid and dashed lines are fits to either the targeted or survey sets.
+} \label{fig:mass richness}
+\end{figure}
+
+We leverage the large spectroscopic dataset of HETDEX to estimate its ability to constrain the scatter and absolute scale of the richness-mass relationship.
+We begin by cross matching both the targeted and survey observations with a redMapper catalog.
+The redMapper catalog is limited to $\lambda >= 20$, or at least twenty object assigned to each cluster.
+With the targeted and survey observations, we observe 138 and 58 clusters respectively.
+
+Figure \ref{fig:mass richness} shows the optical richness, $\lambda$, versus the predicted cluster mass.
+The cluster masses are the $ML_{\sigma, z, N_{gal}}$ based and correspond to the correct observation strategy.
+The error bars represent the $1\sigma$ prediction intervals for each cluster mass.
+The solid and dashed lines are fits to the targeted and survey datasets.
+For comparison, the richness-mass relations from \cite{Rykoff2012} (their equation B5) is shown as a dash-dotted line.
+
+To generate the best fitting lines we follow the general procedure of \cite{Hogg2010}, by defining an objective function and then minimizing the loss. Our loss function is
+\begin{equation}
+	\mathrm{ln}L= \frac{-1}{2} \bigg{(} \sum^N_{i=1}\frac{[y_i - mx_i - b]^2}{\sigma_{yi}} + \sum^N_{i=1}\frac{[y_i - mx_i - b]^2}{\sigma_{xi}} \bigg{)}
+\end{equation} 
+where we have taken into account the uncertainties in both the richness and predicted cluster mass.
+We again rely on MCMC samples to sample the posterior probability distribution.
+The best fitting slope and intercept are quoted as the median value of the posterior probability distribution with 68\% error bars defined as the 16th and 84th percentiles of the same distribution.
+
+Following the notation of \cite{Rykoff2012} we find a best-fitting relation for the targeted observations as
+\begin{equation}
+	ln\bigg{(}\frac{M_{200c}}{h_{70}^{-1} 10^{14}\Msol}\bigg{)} = 1\pm0.13 + 1.34\pm0.17 ln\bigg{(}\frac{\lambda}{60}\bigg{)} \nonumber
+\end{equation}
+and the survey observations as
+\begin{equation}
+	ln\bigg{(}\frac{M_{200c}}{h_{70}^{-1} 10^{14}\Msol}\bigg{)} = 1.02\pm0.13 + 0.96\pm0.22 ln\bigg{(}\frac{\lambda}{60}\bigg{)} \nonumber
+\end{equation}
+%Applying my current work to a large photometric survey such as those mentioned above is the logical next step.
+For example, the HETDEX observations overlap with the DES area and SDSS Stripe 82 which provides a wealth of external data.
+Using preexisting datasets, the observations from HETDEX, or through dedicated followup spectroscopic observations, I will be able to measure the absolute mass scale of the richness estimator and measure the scatter of the richness-mass relation, $\sigma_{M|\lambda}$.
+An accurate measure of this scatter can lead to a decrease on the error bar on cosmological measures ($\sigma_8$ and $\Omega_M$) by as much as 50\% \citep{Rozo2010}.
+An absolute calibration of the richness-mass relation will provide a much needed tool for future imaging surveys which will identify clusters to $z=1$ and beyond.
 
@@
 
-Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+Our main conclusions are the following:
+\begin{enumerate}
+	\item Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
 Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
@@
 Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
-
-Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+	\item Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
 Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
@@
 Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+	\item Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
+Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
+Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+\end{enumerate}
 
-It is our hope that this work may be useful to others when conducting their own research.
+It is the author's hope that this work may be useful to others when conducting their own research.
 Because this work relies heavily on (often) complex data analysis, and in order to promote transparency, we provide all of the code used to conduct this study at https://github.com/boada/desCluster.

### 2016-02-28 ms.tex
updated
This is the version that is going to casey for the first round of
comments.

@@
 Using both observing strategies, we produce cluster mass probability density functions $P(X|M,z)$, which can be used to determine the probability that a galaxy cluster of given mass (M), located at redshift ($z$) determined using observable parameter (X).
-% We then applied these probability functions to ten galaxy clusters selected from the Sloan Digital Sky Survey DR8 and the Chandra-XMM X-ray Cluster Survey at $z=0.2-0.3$, and observed by the HETDEX spectrograph prototype instrument (VIRUS-p).
-We measured spectroscopic redshifts and line-of-sight velocities of the galaxies in and around each cluster, derived a line-of-sight velocity dispersion, and inferred a dynamical mass for each cluster which ranges from $(0.4-24) \times 10^{14} \Msol (M_{200c})$.
-Using the mass probability density functions described above, we updated these masses and compared them to existing literature estimates, or to the masses estimated from other observables such as X-ray temperature or richness.
 \end{abstract}
@@
 
-This work plans to address these concerns in the following ways.
+\editorial{The wording here needs to be updated when the time comes.} This work plans to address these concerns in the following ways.
 We use simulated observations which target individual galaxy clusters to investigate the recovery of parameters with such observations.
@@
 \section{Data and Mock Observations}\label{sec:Data}
-
-\editorial{Blah blah intro stuff...
-Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.}
+In this section, we describe the data products and the techniques used to replicate the HETDEX survey.
+We use the information from a large mock galaxy catalog supplemented by galaxies from the SDSS to create a realistic ``sky'' and ``observe'' it with a HETDEX-like observing strategy.
 
 \subsection{The ``Buzzard'' Catalogs}
+\begin{figure*} 
+	\includegraphics[width=\textwidth]{figures/oii_sdss.pdf} 
+	\caption{\textit{Left}: CMD of 503113 $z<0.2$ galaxies take from the SDSS DR12 where the shading scales with the density of points.
+The two colored boxes show regions containing potential catalog galaxies.
+\textit{Right}: Probability histograms of the Log [\ion{O}{ii}] luminosity for the SDSS galaxies located in the two highlighted regions on the right.
+New [\ion{O}{ii}] luminosity (and subsequently fluxes) are assigned to catalog galaxies from slice sampling the probability histogram.
+See the text for a full description of the process.} \label{fig: oii sdss}
+\end{figure*}
+
 The ``Buzzard'' mock galaxy catalogs (R.
@@
 The catalog information, used in this study, is broken into two large portions.
-The ``truth'' files contain the characteristics of each individual galaxies, such as right ascension (RA), declination (DEC), redshift (z), observed and rest-frame magnitudes, and many others.
+The ``truth'' files contain the characteristics of each individual galaxies, such as right ascension (RA), declination (DEC), redshift ($z$), observed and rest-frame magnitudes, and many others.
 The ``halo'' files contain information for individual halos, to which many individual galaxies may belong.
 This includes five estimations of dynamical mass, RA, DEC, z, three dimensional velocity dispersion, and many others.
-
-However, the catalogs do not include information on emission or absorption lines or estimations of whether the halo is relaxed or not.
-We supplement the catalogs with this information and describe the method in Section~\ref{sec: oii luminosity} and others.
+However, the catalogs do not include information for emission lines.
+We supplement the catalogs by generating this information; the process is described in Section~\ref{sec: oii luminosity}.
 
@@
 We investigate the accuracy of the halo mass distribution by comparing the cumulative number density of halos above a mass ($M_{200c}$) threshold to the halo mass function (HMF) of \cite{Tinker2008}.
-Shown in Figure~\ref{fig: hmf} the HMF is calculated at central redshifts of 0, 0.2, and 0.4 using {\tt HMFcalc} \citep{Murray2013} and compared to galaxies in a redshift window of $\Delta z\pm0.01$.
-We find a very good agreement between the expected HMF and the observed.
+We calculate the HMF is calculated at central redshifts of 0.1, 0.2, and 0.4 using {\tt HMFcalc} \citep{Murray2013} and compared to galaxies in a redshift window of $\Delta z\pm0.01$.
+We find a very good agreement between the predicted HMF and the observed distribution of clusters.
 
 \subsection{ {\rm[\ion{O}{ii}]} Luminosity}\label{sec: oii luminosity}
-\begin{figure*} 
-	\includegraphics[width=\textwidth]{figures/oii_sdss.pdf} 
-	\caption{\textit{Left}: CMD of 503113 $z<0.2$ galaxies take from the SDSS DR12 where the shading scales with the density of points.
-The two boxes show regions containing potential catalog galaxies.
-\textit{Right}: Probability histograms of the Log [\ion{O}{ii}] luminosity for the SDSS galaxies located in the two highlighted regions on the right.
-New [\ion{O}{ii}] luminosity (and subsequently fluxes) are assigned to catalog galaxies from slice sampling the probability histogram.} \label{fig: oii sdss}
-\end{figure*}
-
 The Buzzard ``truth'' catalog does not provide [\ion{O}{ii}] luminosities so we must assign them empirically.
-We use 503113 galaxies from the SDSS Data Release 12 \citep{Alam2015} from $z = 0.05 - 0.2$, which are selected with no redshift warning, and place each galaxy on a color-magnitude diagram (CMD) of $M_r$ and $g-r$, see Figure~\ref{fig: oii sdss}.
+We use 503113 galaxies from the SDSS Data Release 12 \citep{Alam2015} from $z = 0.05 - 0.2$, which are selected with no redshift warning, and place each galaxy on a color-magnitude diagram (CMD) of $M_r$ and $g-r$; see the left panel of Figure \ref{fig: oii sdss}.
 
@@
 The right panel of Figure~\ref{fig: oii sdss} shows the CMD of all SDSS galaxies.
-Two potential catalog galaxies are also placed on the CMD ($M_r, g-r = -17.7,~0.49$ and $M_r, g-r = -21.4,~1.24$) and indicated by two colored boxes.
-The histograms show in the Figure's left panel shows the probability density histograms of the Log [\ion{O}{ii}] luminosity for the SDSS galaxies in the 2D bin.
+Two potential catalog galaxies are also placed on the CMD ($M_r, g-r = -17.7,~0.49$ and $M_r, g-r = -21.4,~1.24$) and indicated by the two colored boxes.
+The histograms show in the Figure's right panel show the probability density histograms of the Log [\ion{O}{ii}] luminosity for the SDSS galaxies in the 2D bin around the individual catalog galaxies.
 We sample the distribution and assign each catalog galaxy an [\ion{O}{ii}] luminosity which is then converted into a flux.
@@
 \subsection{Mock Observations}\label{sec: observations}
-\editorial{Not sure this does a good enough job talking about the two different observations.}
-Tentatively slated to start in the spring of 2016, HETDEX will perform blind spectroscopy (R $\sim$ 750 in $3500 - 5500~\AAA$) over two fields along the celestial equator.
-The 300 \degsq, spring field and 120 \degsq, fall field will have no preselected targets.
-Using VIRUS on the 10-m Hobby-Eberly Telescope (HET; \citealt{Ramsey1998}) the completed survey is expected to have an overall fill-factor of 1/4.5, meaning that the entire area could be covered with 4.5 dithers of the entire survey.
-
-The spectral coverage allows for the detection of [\ion{O}{ii}] ($\lambda\lambda 3727-3729~\AAA$ doublet) emitters to $z\sim 0.5$ and Ca H ($\lambda 3968.5~\AAA$) and K ($\lambda 3933.7~\AAA$) absorption features to $z\sim 0.4$.
-HETDEX is expected to detect sources with continuum brighter than 22 mag in \sdssg, and emission line strengths above $3.5\times10^{-17}$ \ergscm.
-So we ``observe'' $z<0.4$ galaxies which meet either the emission line or the magnitude limit.
-Galaxies $0.4<z<0.5$ are only observed if their emission line strength is sufficient.
-\editorial{These limits have been changed.
-FIX!}
-
 \begin{figure} 
-	\includegraphics[width=\columnwidth]{figures/f01.pdf} 
+	\includegraphics[width=\columnwidth]{figures/pointings.pdf} 
 	\caption{Representative observation tiling scheme for the HETDEX $16' \times 16'$ pointings.
@@
 
-In this work we consider two separate observation cases.
-The first are targeted observations where we select each galaxy cluster and ``observe'' each galaxy within $8'$ of the center.
-The second is a survey case where observations which are blind to the positions of the clusters are conducted.
-In both cases, our ``observations'' consist of placing masks down onto the Buzzard ``truth'' catalogs and selecting all, $z< 0.5$ also meeting sensitivity limits, galaxies which lie underneath.
+Tentatively slated to start in the spring of 2016, HETDEX will perform blind spectroscopy (R $\sim$ 750 in $3500 - 5500~\AAA$) over two fields along the celestial equator.
+The 300 \degsq, spring field and 120 \degsq, fall field will have no preselected targets.
+Using VIRUS on the 10-m Hobby-Eberly Telescope (HET; \citealt{Ramsey1998}) the completed survey is expected to have an overall fill-factor of 1/4.5, meaning that the entire area could be covered with 4.5 dithers of the entire survey.
+
 Each mask is created to accurately reproduce the HETDEX IFU pattern, see Figure~\ref{fig: ifu layout}.
@@
 This means that when selecting galaxies from the Buzzard catalog we assume an observation for all galaxies laying within a colored, IFU square in Figure~\ref{fig: ifu layout}.
-\editorial{This should be updated with the fiber collisions.} Galaxies which lie between the IFUs are missed, as well as the galaxies which lie between the pointings, as there is no overlap between one pointing and the next.
+Galaxies which lie between the IFUs are missed, as well as the galaxies which lie between the pointings, as there is no overlap between one pointing and the next.
 To cover the 375.67 \degsq\ field of the Buzzard catalog we require 5370 pointings where 0.015 \degsq\ of each pointing is covered by an IFU.
 The total area of the sky covered by an IFU is 80.80 \degsq\ which gives a filling factor of 1/4.65 slight decreased from the expected filling factor of 1/4.5.
+
+The spectral coverage allows for the detection of [\ion{O}{ii}] ($\lambda\lambda 3727-3729~\AAA$ doublet) emitters to $z\sim 0.5$ and Ca H ($\lambda 3968.5~\AAA$) and K ($\lambda 3933.7~\AAA$) absorption features to $z\sim 0.4$.
+HETDEX is expected to detect sources with continuum brighter than $\sdssg=22$ mag, and emission line strengths above $3.5\times10^{-17}$ \ergscm.
+
+In this work we consider two separate observing strategies and two detection limits.
+The two observing strategies are targeted and survey-like.
+The targeted observations use ``direct'' observations where each cluster is targeted individual, and every cluster member galaxy is assumed to be observed.
+The survey observations mimic the HETDEX observation pattern across the sky, where no cluster is directly targeted and not all cluster member galaxies are observed.
+In both cases we use two detection thresholds.
+``Perfect'' observations assume no detection threshold, if a cluster member galaxy is observed, it is also detected.
+``Realistic'' observations assume the HETDEX-like detection thresholds where a galaxy may be observed but not necessarily detected.
+
+These observations provide four levels of quality with targeted-perfect being the highest and survey-realistic being the lowest.
 
@@
 where $\sigma_p$, $\langle\mu\rangle$, and $\sigma_i$ is the LOSVD, the average radial velocity and the error on the individual LOSVs respectively.
-Using a Monte Carlo Markov Chain (MCMC) sampler ({\tt emcee}\footnote{\url{http://dan.iel.fm/emcee/current/}}; \citealt{Foreman-Mackey2013}), we draw twenty thousand samples from the posterior probability distribution.
-Simple priors, $\langle\mu\rangle$ lies between the maximum and minimum LOSV and $0< \sigma_p$ \editorial{check}, are used.
+Using a Monte Carlo Markov Chain (MCMC) sampler ({\tt emcee}\footnote{\url{http://dan.iel.fm/emcee/current/}}; \citealt{Foreman-Mackey2013}) which is based on affine-invariant ensemble sampler (see \citealt{Goodman2010} for details on affine-invariant samplers).
+We draw twenty thousand samples from the posterior probability distribution.
+Simple priors, $\langle\mu\rangle$ lies between the maximum and minimum LOSV and $0< \sigma_p < 1400$ \kms, are used.
 When the full distribution of LOSVDs are not used, the final LOSVD is quoted as the median value of the posterior probability distribution with 68\% error bars defined as the 16th and 84th percentiles of the same distribution.
@@
 The corner plots shows all of the one and two dimensional posterior probability distributions used to determine the correct cluster mass.
-The colored rectangles show the slices needed to create a conditional probability distribution of the mass, $P(M|\vec{x})$.
+The colored rectangles, which have been enlarged for clarity, show the slices needed to create a conditional probability distribution of the mass, $P(M|\vec{x})$.
 See text for a complete description.
@@
 The conditional probability of the mass $P(M|\vec{x}= \{ x_1,x_2,...\})$ is determined by taking a slice through the joint probability distributions in bins centered on the desired value.
-The slices show by the colored bars in Figure~\ref{fig: probability corner} are centered on $\sigma = 500$ \kms and $z=0.17$.
-The distribution of mass contained in the three dimensional bin given by the intersection of these slices is $P(M|\vec{x} = \{ \sigma=500 \kms,z=0.17\})$.
+The slices show by the colored bars in Figure~\ref{fig: probability corner} are centered on $\sigma = 400$ \kms and $z=0.17$.
+The distribution of mass contained in the three dimensional bin given by the intersection of these slices is $P(M|\vec{x} = \{ \sigma=400 \kms,z=0.17\})$.
+
+\begin{figure*}
+	\includegraphics[width=0.8\textwidth]{figures/recovery.pdf} 
+	\caption{Recovery fractions ($N_{obs}/N_{True}$) of cluster member galaxies as a function of redshift and mass for the targeted and survey observing strategies.
+The solide lines are the median values and the shaded regions represent the 68\% scatter.
+The significant decline in galaxies observed with the survey strategy is due to gaps in the VIRUS IFU.} \label{fig: recovery}
+\end{figure*}
 
@@
 
-\begin{figure*}
-	\includegraphics[width=\textwidth]{figures/recovery.pdf} 
-	\caption{Recovery fractions ($N_{obs}/N_{True}$) of cluster member galaxies as a function of redshift and mass for the targeted and survey observing strategies.
-The solide lines are the median values and the shaded regions represent the 68\% scatter.
-The significant decline in galaxies observed with the survey strategy is due to gaps in the VIRUS IFU.} \label{fig: recovery}
-\end{figure*}
-
 \subsection{Recovery of Cluster Members}
@@
 The decrease in recovery fraction with increasing redshift is a magnitude effect.
-If, instead of being limited to 22 mag in \sdssg apparent, the observations where limited by absolute magnitude, the sharp downward trend disappears.
+If, instead of being limited to $\sdssg= 22$ mag, the observations where limited by absolute magnitude, the sharp downward trend disappears.
 The second key feature is the strong decline in clusters recovered from survey observations.
@@
 	\hline
-	\rottext{4}{Prob Based} & Power Law & 0.263 & 0.396 & --- & 0.263 & 0.393 & --- \\
-	&$\sigma$ & 0.220 & 0.335 & --- & 0.222 & 0.329 & --- \\
-	&$\sigma, z$ & 0.189 & 0.286 & --- & 0.194 & 0.278 & --- \\
-	&$\sigma, z, N_{gal}$ & 0.129 & 0.207 & --- & 0.140 & 0.222 & --- \\
+	\rottext{4}{Prob Based} & Power Law & 0.259 & 0.394 & \nd & 0.243 & 0.357 & \nd \\
+	&$\sigma$ & 0.220 & 0.337 & \nd & 0.210 & 0.310 & \nd \\
+	&$\sigma, z$ & 0.193 & 0.283 & \nd & 0.184 & 0.271 & \nd \\
+	&$\sigma, z, N_{gal}$ & 0.128 & 0.204 & \nd & 0.141 & 0.215 & \nd \\
 
 	\hline
-	\rottext{4}{ML Based} & Power Law & 0.263 & 0.396 & --- & 0.263 & 0.393 & --- \\
-	&$\sigma$ & 0.246 & 0.361 & --- & 0.238 & 0.344 & --- \\
-	&$\sigma, z$ & 0.193 & 0.285 & --- & 0.171 & 0.260 & --- \\
-	&$\sigma, z, N_{gal}$ & 0.117 & 0.193 & --- & 0.093 & 0.179 & --- \\
+	\rottext{4}{ML Based} & Power Law & 0.258 & 0.394 & \nd & 0.255 & 0.380 & \nd \\
+	&$\sigma$ & 0.241 & 0.359 & \nd & 0.223 & 0.342 & \nd \\
+	&$\sigma, z$ & 0.193 & 0.282 & \nd & 0.197 & 0.290 & \nd \\
+	&$\sigma, z, N_{gal}$ & 0.118 & 0.192 & \nd & 0.140 & 0.221 & \nd \\
 
@@
 
-% \subsection{Expected Results}
-% \editorial{Expected results in what context?
-How well we can obtain cluster masses?
-How many masses will we get to what accuracy?
-This is sorta talk about in the results section but we don't really come out and say "this is what we think HETDEX will and and how well we think it will do it." That might worth saying, even if we are wrong it will give people a starting point when thinking about this stuff in the future.}
-% Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
-
-\subsection{Potential Improvements}
-\editorial{The potential improvements are really three fold.
-We know that the observing won't cover all of the sky.
-So we can simply tile more and try to get more clusters.
-We can observe deeper.
-I'm not sure the current exposure times (they are in an email that I sent to casey) but if we can extend them, then we can get further down the IMF and try to build up some of the clusters that are really more like groups than anything else.
-The last thing we can do is to attempt to  build better models to make better predictions on the masses.
-That might be something like the study that \cite{Acquaviva2016} did with the stellar metallicities.
-Or we'll need something else that I haven't thought of just yet.
-The other idea is to come up with some sort of cheat sheet for HETDEX.
-Basically, a if you detect such and such type of galaxy in the survey model then you should go back and try to follow it up with targeted observations.
-It might be good to talk about the recovery fraction between the two surveys above.
-Like...
-if there are 30 cluster members then we should detect the cluster in both surveys.}
-
-Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+\begin{table*}
+\centering
+\caption{Associated mass prediction errors (MAE) for different bins of predicted mass.
+This table shows the relative error for the targeted (top section) and survey (bottom section) observations for different predicted mass bins.
+The values in the table correspond to the MAE for the galaxies in the predicted mass bin (top row) for the different mass recovery strategies (leftmost column).
+It can be used to understand how precise the predicted cluster mass is.}
+\begin{tabular}{cccccccccc} 
+		&& \multic{8}{Bins -- Log $M_{pred}$ ($\Msol$)} \\
+		\cline{3-10} 
+		\multicolumn{2}{c}{Input Features} & $11.5-12$ & $12-12.5$ & $12.5-13$ & $13-13.5$ & $13.5-14$ & $14-14.5$ & $14.5-15$ & $15-15.5$ \\
+		\hline 
+		\rottext{4}{Prob Based} & Power Law & 0.602 & 0.376 & 0.340 & 0.278 & 0.225 & 0.177 & 0.114 & 0.041 \\
+		&$\sigma$ & 1.030 & 0.655 & 0.389 & 0.212 & 0.160 & 0.158 & 0.224 & 0.328 \\
+		&$\sigma, z$ & 0.804 & 0.476 & 0.242 & 0.173 & 0.170 & 0.210 & 0.353 & 0.529 \\
+		&$\sigma, z, N_{gal}$ & 0.649 & 0.372 & 0.163 & 0.124 & 0.113 & 0.111 & 0.105 & 0.241 \\
+		\hline
+		\rottext{4}{ML Based} & Power Law & 0.602 & 0.376 & 0.340 & 0.278 & 0.225 & 0.177 & 0.114 & 0.041 \\
+		&$\sigma$ & 0.773 & 0.557 & 0.287 & 0.210 & 0.230 & 0.267 & 0.337 & 0.323 \\
+		&$\sigma, z$ & 0.631 & 0.380 & 0.211 & 0.172 & 0.182 & 0.236 & 0.284 & 0.265 \\
+		&$\sigma, z, N_{gal}$ & 0.539 & 0.304 & 0.148 & 0.117 & 0.105 & 0.095 & 0.078 & 0.110 \\
+		\hline 
+		\hline
+		\rottext{4}{Prob Based} & Power Law & \nd & \nd & 0.520 & 0.319 & 0.263 & 0.214 & 0.140 & 0.069 \\
+		&$\sigma$ & \nd & \nd & 0.765 & 0.434 & 0.198 & 0.149 & 0.163 & 0.346 \\
+		&$\sigma, z$ & \nd & \nd & 0.592 & 0.305 & 0.162 & 0.165 & 0.257 & 0.396 \\
+		&$\sigma, z, N_{gal}$ & \nd & \nd & 0.476 & 0.171 & 0.125 & 0.141 & 0.141 & 15.002 \\
+		\hline
+		\rottext{4}{ML Based} & Power Law & \nd & 0.583 & 0.316 & 0.337 & 0.278 & 0.214 & 0.140 & 0.069 \\
+		&$\sigma$ & \nd & 0.606 & 0.551 & 0.263 & 0.201 & 0.227 & 0.200 & 0.192 \\
+		&$\sigma, z$ & \nd & 0.916 & 0.434 & 0.206 & 0.171 & 0.205 & 0.249 & 0.202 \\
+		&$\sigma, z, N_{gal}$ & \nd & 0.780 & 0.401 & 0.155 & 0.129 & 0.136 & 0.145 & 0.142 \\
+		\hline
+	\end{tabular}
+\label{tbl:sersic number bins}
+\end{table*}
 
@@
 \end{equation}
+
+The bottom panel of Figure \ref{fig:mass richness} shows the scatter in cluster masses at fixed richness, $\sigma_{M|\lambda}$.
+The solid and dashed lines represent the targeted and survey observations respectively, and have been offset from one another for clarity.
+The cluster masses are binned in increasing ten richness intervals ($20-30$, $30-40$, etc.).
+The two horizontal lines show the mean scatter of 0.26 dex for the targeted observations and 0.21 dex for the survey observations.
+While not shown in the figure, we find a mean scatter of 0.27 dex if we replace $M_{pred}$ with the true cluster mass for the clusters identified with targeted observations.
+The reduction in scatter from the targeted to survey observations is due to fewer objects detected in survey mode.
+
+%Much like the MAE and RMSE associated with the cluster mass recovery, comparing the individual $\sigma_{M|\lambda}$ values directly is incorrect.
+When comparing only the clusters with observations in both the targeted and survey strategies we
+
 %Applying my current work to a large photometric survey such as those mentioned above is the logical next step.
@@
 
-\section{SUMMARY}\label{sec:summary}
+\subsection{Potential Improvements}
+\editorial{The potential improvements are really three fold.
+We know that the observing won't cover all of the sky.
+So we can simply tile more and try to get more clusters.
+We can observe deeper.
+I'm not sure the current exposure times (they are in an email that I sent to casey) but if we can extend them, then we can get further down the IMF and try to build up some of the clusters that are really more like groups than anything else.
+The last thing we can do is to attempt to  build better models to make better predictions on the masses.
+That might be something like the study that \cite{Acquaviva2016} did with the stellar metallicities.
+Or we'll need something else that I haven't thought of just yet.
+The other idea is to come up with some sort of cheat sheet for HETDEX.
+Basically, a if you detect such and such type of galaxy in the survey model then you should go back and try to follow it up with targeted observations.
+It might be good to talk about the recovery fraction between the two surveys above.
+Like...
+if there are 30 cluster members then we should detect the cluster in both surveys.}
+
 Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
@@
 
+\section{SUMMARY}\label{sec:summary}
+Here, we present detailed simulations of the upcoming HETDEX survey's applicability to the detection and total mass measurement of galaxy clusters.
+We use mock galaxy catalogs, and simulated HETDEX-like observational strategies to estimate the number of clusters observed and the precision of their total mass estimates, using three different mass estimates.
+With an eye to galaxy cluster studies, we discuss potential improvements to the HETDEX survey, and comment on how HETDEX may improve current and future photometric large-area sky surveys' cluster mass estimates derived from optical richness.
+
 Our main conclusions are the following:
 \begin{enumerate}
-	\item Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
-	\item Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
-	\item Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+	\item HETDEX-like observations do a good job observing galaxy clusters.
+The number of galaxy clusters detected in the HETDEX-like observations is almost exact 4.5 times less than in the targeted observations.
+This difference is the same as the overall HETDEX fill factor.
+	\item Overall, we find that a traditional power-law conversion from LOSVD to cluster mass performs significantly poorer than either the probability based or ML based methods also tested.
+We find the MAE and RMSE of survey detected cluster mass estimates to be approximately 38\% and 65\% respectively, compared to approximately 123\% when a power-law is used alone.
+	\item While the power-law may be outperformed, overall, comparisons of similar mass galaxy clusters shows that above Log M $=14.5$ \Msol, the power-law gives a lower MAE than either the probability based or ML based methods.
+For HETDEX-like observations and clusters with $13 < Log M <14.5$ \Msol, we find the $ML_{\sigma, z, N_{gal}}$ method performs the best.
+Below Log M $=13$ \Msol\ no method with survey observations gives an MAE of less than 50\%.
+	\item For followup targeted observations only galaxy clusters with masses inferred to be Log M $<13$ \Msol\ from survey observations should be targeted.
+Galaxy clusters with inferred masses below Log M $=13$ \Msol\ can see as much as an 81\% improvement in cluster mass estimation with targeted observations.
+While the improvement of clusters with masses above Log M $=13$ \Msol\ is often approximately 10\%.
+	\item \editorial{Something about the richness.}
 \end{enumerate}
@@
 This research made use of This research made use of  the {\tt IPython} package \citep{Perez2007} and {\tt matplotlib}, a Python library for publication quality graphics \citep{Hunter2007}.
+Figure \ref{fig: probability corner} is heavily based on \cite{Foreman-Mackey2016}.
 Funding for the SDSS and SDSS-II has been provided by the Alfred P.

### 2016-03-02 ms.tex
first few casey comments

@@
 \usepackage{newtxtext,newtxmath}
-%\usepackage{times}
+\usepackage{times}
 % Depending on your LaTeX fonts installation, you might get better results with one of these:
@@
 %%%%%%%%%%%%%%%%%%% TITLE PAGE %%%%%%%%%%%%%%%%%%%
-\title[Short Title]{Cluster Dynamics with HETDEX - I: Simulated Performance, Mass Distribution and Limits}
+\title[Short Title]{Cluster Dynamics with HETDEX at z < 0.5 - I: Simulated Performance, Mass Distribution and Limits}
 
@@
 % If you need two or more lines of authors, add an extra line using \newauthor
-\author[S. Boada et al.]{
-Steven Boada,$^{1}$\thanks{E-mail: boada@physics.tamu.edu}
+\author[S. Boada et al.]
+{\parbox{\textwidth}{Steven Boada,$^{1}$\thanks{E-mail: boada@physics.tamu.edu}
 C.~Papovich,$^{1}$
 R.~Wechsler,$^{2,3}$
-T. S.~Li,$^{1}$\newauthor\phantom{x}
-K.~Gebhardt,$^{4}$
-E.~Rozo,$^{2}$
-E. S.~Rykoff,$^{2}$
+T. S.~Li,$^{1}$
+K.~Gebhardt,$^{5}$
+E.~Rozo,$^{2,4}$
+E. S.~Rykoff,$^{2}$}\vspace{0.4cm}\
 \\
-% List of institutions
-$^{1}$George P.\ and Cynthia Woods Mitchell Institute for
-Fundamental Physics and Astronomy, Texas A\&M University, College Station, TX, 77843-4242\\
+\parbox{\textwidth}{$^{1}$George P.\ and Cynthia Woods Mitchell Institute for Fundamental Physics and Astronomy, and Department of Physics and Astronomy, Texas A\&M University, College Station, TX, 77843-4242, USA\\
 $^{2}$Kavli Institute for Particle Astrophysics and Cosmology, Department of Physics, Stanford University, Stanford, CA 94305, USA\\
 $^{3}$Department of Particle Physics and Astrophysics, SLAC National Accelerator Laboratory, Menlo Park, CA 94025, USA\\
-$^{4}$The University of Texas}
+$^{4}$Department of Physics, University of Arizona, Tucson, AZ 85721, USA\\
+$^{5}$Department of Astronomy, The University of Texas at Austin, Austin, TX 78712, USA}}
 
@@
 
-Throughout this paper, we adopt the following cosmological model ($\Omega_\Lambda = 0.77$,
-$\Omega_M = 0.23$, $\sigma_8 = 0.83$ and $H_0= 72$ \kms \mpc), assume a Chabrier initial mass function (IMF; \citealt{Chabrier2003}), and use AB magnitudes \citep{Oke1974}.
+Throughout this paper, we adopt the following cosmological model: $\Omega_\Lambda = 0.714$,
+$\Omega_M = 0.286$, $\sigma_8 = 0.82$ and $H_0= 70$ \kms \mpc (taken from the Buzzard catalogs; see below), assume a Chabrier initial mass function (IMF; \citealt{Chabrier2003}), and use AB magnitudes \citep{Oke1974}.
 
@@
 The ``Buzzard'' mock galaxy catalogs (R.
-Wechsler et al., private communication) cover 375.68 \degsq\ between $60 < RA < 90$ and $-61 < DEC < -41$ and are derived from a combination of Sub-halo Abundance Matching (ShAM) and ADDSEDs (Adding Density Dependent Spectral Energy Distributions) tied to an in house n-body cosmological simulation.
+Wechsler et al., private communication) cover 375.68 \degsq\ between $4^h< RA < 6^h$ and $-61\degree < DEC < -41\degree$ and are derived from a combination of Sub-halo Abundance Matching (ShAM) and ADDSEDs (Adding Density Dependent Spectral Energy Distributions) tied to an in house n-body cosmological simulation.
 A brief description of the catalog creation is described as follows.

### 2016-03-06 ms.tex
more comments from casey

@@
 E.~Rozo,$^{2,4}$
-E. S.~Rykoff,$^{2}$}\vspace{0.4cm}\
+E. S.~Rykoff$^{2}$}\vspace{0.4cm}\
 \\
@@
 We used a detailed mock galaxy catalog and present mock observations of two different scenarios: (1) We targeted individual galaxy clusters to investigate the recovery of parameters with such observations.
-(2) We created and evaluated a HETDEX-like selection "function'' of galaxies over a similarly sized portion of the sky and use well adopted techniques to recover the dynamical properties, such as velocity dispersion and mass.
+(2) We created and evaluated a HETDEX-like selection "function'' of galaxies over a similarly sized portion of the sky and use well adopted techniques to recover the dynamical properties, such as velocity dispersion and mass, and benchmark these against observations with perfect knowledge.
 Using both observing strategies, we produce cluster mass probability density functions $P(X|M,z)$, which can be used to determine the probability that a galaxy cluster of given mass (M), located at redshift ($z$) determined using observable parameter (X).
+\editorial{This sentence will summarize how well HETDEX will do, and how that might be improved with targeted observations.}
 \end{abstract}
@@
 \section{INTRODUCTION}
+\editorial{The introduction is now much longer because I talked about the cons to the different cluster mass recovery methods.
+I don't much care for really long introductions, so if there is anything that could by cut to shorten it, I would be ok.}
 Our ability to perform precision cosmology with clusters of galaxies has reached a critical turning point.
@@
 As mass is not a direct observable, a lot of work is underway to characterize galaxy cluster masses with an observable feature of galaxy clusters.
-The goal is to constrain, as best possible, $P(X|M,z)$ the probability ($P$) that a galaxy cluster of given mass ($M$), located at redshift ($z$) determined using observable parameter ($X$).
-The observable parameter most commonly observed X-ray temperatures and luminosities \citeeg{Mantz2010, Rykoff2014, Mantz2015}, cosmic microwave background observations \citeeg{Vanderlinde2010, Sehgal2011} using the Sunyaev-Zel'dovich effect (SZE; \citealt{Sunyaev1972}) or optical studies \citeeg{Rozo2010, Rozo2015} of richness \citeeg{Abell1958, Rykoff2012} or galaxy velocity dispersions \citeeg{Ruel2014, Sifon2015}.
+The goal is to constrain, as best possible, $P(M|x)$ the probability ($P$) that a galaxy cluster of given mass ($M$), located at redshift ($z$) determined using observable parameter ($X$).
+Generally, cluster mass calibrations fall into two distinct camps, simulation based and direct or statistical calibration.
+
+One could use various simulations to attempt to calibrate this observable--mass relation \citeeg{Vanderlinde2010, Sehgal2011}.
+However, the primary challenge to this method is the incomplete understanding of the baryonic physics which take place in galaxy cluster environments.
+While there have been (and continue to be) many improvements in the accuracy and power of simulations it is doubtful that in the coming years they will reach the accuracy level required to the point where the observable--mass relation is dominated only by statistics \citep{Weinberg2013}.
+
+The second broad camp is the direct calibration of cluster masses.
+This recipe has two distinct but not always independent tracks.
+The ``direct'' method uses the direct observations of a small set of clusters and then uses known mass estimators, X-ray temperatures and luminosities \citeeg{Mantz2010, Rykoff2014}, cosmic microwave background (CMB) observations \citeeg{Vanderlinde2010, Sehgal2011}, optical richness \citeeg{Abell1958, Rykoff2012} or weak lensing (WL) \citeeg{Rozo2010} as examples, which provide a ``true'' mass.
+This directly calibrates the observable--mass relation which is then applied to a much larger sample.
+The complications lie in that the ``true'' masses are in fact estimations, and the methods used to recover these masses are subject to their own limitations.
+X-ray hydrostatic estimations assume hydrostatic equilibrium \citeeg{Mantz2015} which may only be valid for a very small number and range of cluster masses.
+The Sunyaev--Zel'dovich Effect (SZE; \citealt{Sunyaev1972}), which uses the up--scattering of CMB photons to estimate cluster masses, provides accurate estimations of mass, but the ability to detect low mass galaxy clusters is currently limited by technology \citeeg{Carlstrom2002a}.
+WL estimates are, in principle, correct in the mean, but they suffer from signal-to-noise requirements, limiting their usefulness in low mass clusters, and potentially suffer from line-of-sight effects as the effect is sensitive to all mass along the line of sight.
+Virial mass estimators which determine the cluster mass based on the motions of the member galaxies \citeeg{Ruel2014, Sifon2015} are promising in that it is a direct measurement of the depth of clusters potential well, but suffers from systematics due to cluster formation physics which disrupts the velocity field.
+
+The statistical method of determining galaxy cluster mass relies not on direct measurements of individual clusters but the calibration of observables for the entire sample which correlate with cluster mass.
+One example is the spatial clustering of the galaxy clusters themselves.
+See \cite{Weinberg2013} for a comprehensive review.
+In practice, it will be a combination of the three methods touched on that will provide the most reliable determination of cluster masses.
 
@@
 
-While a large portion of the $\sim10^6$ interloping [\ion{O}{ii}] galaxies will be field (not associated with a bound structure) galaxies, the large area covered by HETDEX is expected to contain as many as 100 Virgo-sized ($M_{dyn}\sim 10^{15}$ \msol) clusters at $z<0.5$ (\editorial{citation?}).
+While a large portion of the $\sim10^6$ interloping [\ion{O}{ii}] galaxies will be field (not associated with a bound structure) galaxies, the large area covered by HETDEX is expected to contain as many as 50 Virgo-sized ($M_{dyn}\sim 10^{15}$ \msol) clusters at $z<0.5$ (\editorial{talk to casey about how I calculated this number}).
 The near-complete spectroscopic coverage allows an unprecedentedly detailed look at a very large number of clusters ranging from group scales to the very massive.
@@
 HETDEX overlaps with the Sloan Digital Sky Survey (SDSS; \citealt{Blanton2001a}), SDSS stripe 82 \citep{Annis2014}, the Dark Energy Survey (DES; \citealt{DES2005}), and the upcoming DECam/IRAC Galaxy Environment Survey (DIRGES; PI: Papovich, C.
-Papovich \etal\ in preparation).
-\editorial{SHELA and others?
-Would be good to have a whole list of different things and different wavelengths.} While the potential dataset is very rich, two large issues remain.
+Papovich \etal\ in preparation), the The \emph{Spitzer}/HETDEX Exploratory Large-Area Survey (SHELA; Papovich \etal\ 2016, ApJS, submitted), and The \emph{Spitzer} IRAC Equatorial Survey (SpIES; Timlin \etal\ 2016, ApJ, submitted).
+While the potential dataset is very rich, two large issues remain.
 
@@
 
-\editorial{The wording here needs to be updated when the time comes.} This work plans to address these concerns in the following ways.
+\editorial{The wording here needs to be updated when we settle on the verbage for everything else.} This work plans to address these concerns in the following ways.
 We use simulated observations which target individual galaxy clusters to investigate the recovery of parameters with such observations.
@@
 We find a very good agreement between the predicted HMF and the observed distribution of clusters.
+\editorial{Could show a figure comparing the Buzzard catalog to a plot of the HMF for a couple of redshifts.
+Might be helpful, might not matter.}
 
@@
 For catalog galaxies which are placed on the CMD near no, or very few ($1\leq n<10$) galaxies we assign it zero [\ion{O}{ii}] luminosity or the mean luminosity, respectively.
+For the galaxies in the Buzzard catalog, 1.3\% of the galaxies brighter than $\sdssg = 22$ mag (HETDEX's detection limit) have exactly zero [\ion{O}{ii}] luminosity.
+Of the 1.3\%, only 3.3\% (0.05\% of all galaxies) have $g-r < 1.5$ suggesting the galaxies which are assigned zero [\ion{O}{ii}] luminosity are not significantly biasing our simulations.
 
@@
 We sample the distribution and assign each catalog galaxy an [\ion{O}{ii}] luminosity which is then converted into a flux.
+\editorial{We could add a plot like the corner plot to show the multi-dimensionality of this process.}
 
@@
 
-The spectral coverage allows for the detection of [\ion{O}{ii}] ($\lambda\lambda 3727-3729~\AAA$ doublet) emitters to $z\sim 0.5$ and Ca H ($\lambda 3968.5~\AAA$) and K ($\lambda 3933.7~\AAA$) absorption features to $z\sim 0.4$.
+The spectral coverage allows for the detection of [\ion{O}{ii}] ($\lambda\lambda 3727,3729~\AAA$ doublet) emitters to $z\sim 0.5$ and Ca H ($\lambda 3968.5~\AAA$) and K ($\lambda 3933.7~\AAA$) absorption features to $z\sim 0.4$.
 HETDEX is expected to detect sources with continuum brighter than $\sdssg=22$ mag, and emission line strengths above $3.5\times10^{-17}$ \ergscm.
 
-In this work we consider two separate observing strategies and two detection limits.
-The two observing strategies are targeted and survey-like.
+In this work we consider two separate observing strategies, targeted and survey-like.
 The targeted observations use ``direct'' observations where each cluster is targeted individual, and every cluster member galaxy is assumed to be observed.
 The survey observations mimic the HETDEX observation pattern across the sky, where no cluster is directly targeted and not all cluster member galaxies are observed.
-In both cases we use two detection thresholds.
+Both of these observations have HETDEX-like galaxy detection thresholds, for comparison we also include a set of targeted observations with ``perfect'' knowledge.
 ``Perfect'' observations assume no detection threshold, if a cluster member galaxy is observed, it is also detected.
-``Realistic'' observations assume the HETDEX-like detection thresholds where a galaxy may be observed but not necessarily detected.
-
-These observations provide four levels of quality with targeted-perfect being the highest and survey-realistic being the lowest.
+This provides an important best-case scenario, and differs from the true cluster properties because the recovered cluster properties are still calculated.
+These observations provide three levels of quality with ``perfect knowledge'' being the highest and survey being the lowest.
 
@@
 Using a Monte Carlo Markov Chain (MCMC) sampler ({\tt emcee}\footnote{\url{http://dan.iel.fm/emcee/current/}}; \citealt{Foreman-Mackey2013}) which is based on affine-invariant ensemble sampler (see \citealt{Goodman2010} for details on affine-invariant samplers).
-We draw twenty thousand samples from the posterior probability distribution.
-Simple priors, $\langle\mu\rangle$ lies between the maximum and minimum LOSV and $0< \sigma_p < 1400$ \kms, are used.
+We draw twenty thousand samples from the posterior probability distribution using simple priors, $\langle\mu\rangle$ lies between the maximum and minimum LOSV and $0< \sigma_p < 1400$ \kms.
 When the full distribution of LOSVDs are not used, the final LOSVD is quoted as the median value of the posterior probability distribution with 68\% error bars defined as the 16th and 84th percentiles of the same distribution.
@@
 \subsection{Dynamical Mass}\label{sec: mass}
-Recently, the relationship between the LOSVD and dynamical mass has been the focus of several studies \citeeg{Evrard2008, Saro2013, Sifon2013, VanderBurg2014}, and a best fitting relationship for the mass enclosed by $r_{200c}$ of the form
+The relationship between the LOSVD and dynamical mass has been the focus of several studies \citeeg{Evrard2008, Saro2013, Sifon2013, VanderBurg2014}, and a best fitting relationship for the mass enclosed by $r_{200c}$ of the form
 \begin{equation}\label{eq:power law}
@@
 After selecting the desired features $\vec{x} = \{\sigma, z, ...\}$ we make the joint probability between the true cluster mass (M) and $\vec{x}$.
-Because $\vec{x}$ can be multidimensional, we rely on the corner plot to visualize the relationship between all of the training features.
+Because $\vec{x}$ can be multidimensional, we rely on the ``corner plot'' as an aid to visualize the relationship between all of the training features.
 Figure~\ref{fig: probability corner} shows all of the one (marginalized probability) and two (joint probability) dimensional projections of the posterior probability distributions of the features of the training data.
@@
 	\includegraphics[width=0.8\textwidth]{figures/recovery.pdf} 
-	\caption{Recovery fractions ($N_{obs}/N_{True}$) of cluster member galaxies as a function of redshift and mass for the targeted and survey observing strategies.
-The solide lines are the median values and the shaded regions represent the 68\% scatter.
+	\caption{Recovery fractions ($N_{obs}/N_{True}$) of cluster member galaxies as a function of redshift and true cluster mass for the targeted and survey observing strategies.
+We have applied HETDEX-like observational limits on the cluster galaxy detection, and require at least five galaxies to be detected for a cluster to be recovered.
+The solid lines are the median values and the shaded regions represent the 68\% scatter.
 The significant decline in galaxies observed with the survey strategy is due to gaps in the VIRUS IFU.} \label{fig: recovery}
@@
 \begin{equation}\label{eq: variance}
-	V = \int (M^\prime - \langle M\rangle)^2 P(M^\prime)dM^\prime
+	\mathrm{Var} = \int (M^\prime - \langle M\rangle)^2 P(M^\prime)dM^\prime
 \end{equation}
@@
 Knowing these limits will provide important information for potential future follow up or targeted observations.
+In this section we discuss the number of cluster members recovered for both the targeted and survey observation strategies, taking into account all observational limits.
 
 Figure \ref{fig: recovery} shows the recovery fraction of member galaxies, the number of observed galaxies divided by the number of actual galaxies ($N_{obs}/N_{True}$), as function of both redshift and cluster mass.
-It is important to note that if few than five member galaxies are observed the cluster is not considered detected, and is excluded from this figure.
+It is important to note that if fewer than five member galaxies are observed $N_{obs} <5$ the cluster is not considered detected, and is excluded from this figure.
 As expected, the targeted observing strategy where the individual clusters are targeted through several dithers to ensure near complete coverage, performs significantly better than the survey observing strategy across all redshifts and cluster masses.
@@
 The decrease in recovery fraction with increasing redshift is a magnitude effect.
-If, instead of being limited to $\sdssg= 22$ mag, the observations where limited by absolute magnitude, the sharp downward trend disappears.
+We check this by limiting the cluster galaxy detection by absolute magnitude which increases the recovery fraction $>70\%$ at all redshifts, implying the decline is a result of the apparent magnitude cluster galaxy detection threshold.
 The second key feature is the strong decline in clusters recovered from survey observations.
@@
 
-The recovery rate as a function of cluster mass, right panel of Figure \ref{fig: recovery}, shows that of the the low mass clusters we detect ($N_{obs} >5$), observe the majority of the galaxies.
-This also shows a rapid decrease in the detection fraction, which can again be explained by considering absolute magnitudes instead of apparent magnitudes.
-Just as before, if the survey was limited by absolute magnitude, we find a much more consistent detection fraction.
+The recovery rate as a function of cluster mass, right panel of Figure \ref{fig: recovery}, shows that of the the low mass clusters we detect ($N_{obs} >5$), we observe the majority of the galaxies.
+This also shows a rapid decrease in the detection fraction, which can again be explained by considering absolute magnitudes instead of apparent magnitudes, as above.
+Also, high mass clusters are rare, so inorder to detect them we must probe a large volume of space.
+The higher redshift cluster members suffer from the limiting apparent magnitude and suppress the recovery fraction at fixed mass.
+If we were to limit the survey to $z<0.2$ we find the recovery fraction of clusters, at all masses, increases substantially, and we find a much more consistent detection fraction across masses.
 
 \subsection{Mass estimates}
+\begin{table*}
+\centering
+\caption{Summary of the errors associated with the Targeted and Survey observation strategies, as an ensemble of predictions.
+See the text for discussion about the MAE and RMSE.
+Overlap is the percentage of clusters where the true cluster mass is bracketed by the prediction intervals of the predicted mass.
+See Sections \ref{sec:probability method} and \ref{sec:machine learning method} for a discussion on prediction intervals.}
+\begin{tabular}{cccccccc}
+	%\hline
+	&& \multic{3}{Targeted} & \multic{3}{Survey} \\
+	\cline{3-5} \cline{6-8}
+	& Input Features & MAE & RMSE & Overlap & MAE & RMSE & Overlap \\
+	& & (dex) & (dex) & (\%) & (dex) & (dex) & (\%) \\
+	\hline
+	\rottext{4}{Prob Based} & Power Law & 0.259 & 0.394 & \nd & 0.243 & 0.357 & \nd \\
+	&$\sigma$ & 0.220 & 0.337 & \nd & 0.210 & 0.310 & \nd \\
+	&$\sigma, z$ & 0.193 & 0.283 & \nd & 0.184 & 0.271 & \nd \\
+	&$\sigma, z, N_{gal}$ & 0.128 & 0.204 & \nd & 0.141 & 0.215 & \nd \\
+	\hline
+	\rottext{4}{ML Based} & Power Law & 0.258 & 0.394 & \nd & 0.255 & 0.380 & \nd \\
+	&$\sigma$ & 0.241 & 0.359 & \nd & 0.223 & 0.342 & \nd \\
+	&$\sigma, z$ & 0.193 & 0.282 & \nd & 0.197 & 0.290 & \nd \\
+	&$\sigma, z, N_{gal}$ & 0.118 & 0.192 & \nd & 0.140 & 0.221 & \nd \\
+	\hline
+\end{tabular}
+\label{tbl:mass comparisons}
+\end{table*}
+
 In this section we discuss the how accurately we are able to reproduce the true cluster mass from a set of observations.
@@
 
-In both figures, we include the cluster masses recovered through the power law scaling relation given in Equation \ref{eq:power law} for both the targeted and survey observations.
+We include the cluster masses recovered through the power law scaling relation given in Equation \ref{eq:power law} for the perfect, targeted and survey observations.
 It should serve as baseline to compare the probability based and ML cluster mass recovery methods.
-And, while there are many possible metrics to evaluate performance, we compute two: the median absolute error (MAE) and the root mean squared error (RMSE).
+And, while there are many possible metrics to evaluate performance, we compute two: the median absolute error (MAE)
+\begin{equation}
+\mathrm{MAE}(y,\hat{y}) = \mathrm{median}(|y_1 - \hat{y_1}|, \ldots, |y_n - \hat{y_n}|) \nonumber
+\end{equation}
+where $y$ is the true value and $\hat{y}$ is the predicted value, and the root mean squared error (RMSE)
+\begin{equation}
+	\mathrm{RMSE}(y,\hat{y}) = \bigg{[}\frac{1}{N} \sum_{i=0}^N (y_i - \hat{y_i})^2 \bigg{]}^{1/2}.\nonumber
+\end{equation} 
 Both metrics evaluate how closely the ensemble of predicted cluster masses are to the true cluster masses, and in both cases lower numbers are better.
@@
 
-\begin{table*}
-\centering
-\caption{Summary of the errors associated with the Targeted and Survey observation strategies, as an ensemble of predictions.
-See the text for discussion about the MAE and RMSE.
-Overlap is the percentage of clusters where the true cluster mass is bracketed by the prediction intervals of the predicted mass.
-See Sections \ref{sec:probability method} and \ref{sec:machine learning method} for a discussion on prediction intervals.}
-\begin{tabular}{cccccccc}
-	%\hline
-	&& \multic{3}{Targeted} & \multic{3}{Survey} \\
-	\cline{3-5} \cline{6-8}
-	& Input Features & MAE & RMSE & Overlap & MAE & RMSE & Overlap \\
-	& & (dex) & (dex) & (\%) & (dex) & (dex) & (\%) \\
-	\hline
-	\rottext{4}{Prob Based} & Power Law & 0.259 & 0.394 & \nd & 0.243 & 0.357 & \nd \\
-	&$\sigma$ & 0.220 & 0.337 & \nd & 0.210 & 0.310 & \nd \\
-	&$\sigma, z$ & 0.193 & 0.283 & \nd & 0.184 & 0.271 & \nd \\
-	&$\sigma, z, N_{gal}$ & 0.128 & 0.204 & \nd & 0.141 & 0.215 & \nd \\
+\begin{figure*} 
+	\includegraphics[width=\textwidth]{figures/Probcomparison.pdf} 
+	\caption{Mass predictions for the power law scaling relation (Equation~\ref{eq:power law}) and the probability based technique with different input features as a function of true cluster mass.
+The bottom row of panels shows the fractional error (Equation~\ref{eq: fractional error}) also as a function of true cluster mass.
+The solid black line shows the 1:1 relation.
+The solid, colored line is the median predicted mass for the targeted observing, and the colored, dashed line is the median recovered mass for the HETDEX-like observations.
+The shaded regions represent the 68\% scatter around the median values.} \label{fig:Probability comparison}
+\end{figure*}
 
-	\hline
-	\rottext{4}{ML Based} & Power Law & 0.258 & 0.394 & \nd & 0.255 & 0.380 & \nd \\
-	&$\sigma$ & 0.241 & 0.359 & \nd & 0.223 & 0.342 & \nd \\
-	&$\sigma, z$ & 0.193 & 0.282 & \nd & 0.197 & 0.290 & \nd \\
-	&$\sigma, z, N_{gal}$ & 0.118 & 0.192 & \nd & 0.140 & 0.221 & \nd \\
-
-	\hline
-\end{tabular}
-\label{tbl:mass comparisons}
-\end{table*}
+\begin{figure*} 
+	\includegraphics[width=\textwidth]{figures/MLcomparison.pdf} 
+	\caption{Mass predictions for the power law scaling relation (Equation~\ref{eq:power law}) and the ML based technique with different input features as a function of true cluster mass.
+The bottom row of panels shows the fractional error (Equation~\ref{eq: fractional error}) also as a function of true cluster mass.
+The solid black line shows the 1:1 relation.
+The solid, colored line is the median predicted mass for the targeted observing, and the colored, dashed line is the median recovered mass for the HETDEX-like observations.
+The shaded regions represent the 68\% scatter around the median values.} \label{fig: ML comparison}
+\end{figure*}
 
@@
 
-In both figures we successively add additional information to further contrain the true cluster masses which subsequently reduces the error associated with the ensemble of predictions (see Table \ref{tbl:mass comparisons}).
+In both figures we successively add additional information to further constrain the true cluster masses which subsequently reduces the error associated with the ensemble of predictions (see Table \ref{tbl:mass comparisons}).
 The power law derived masses, using the single (not including the cosmological parameters) free parameter, $\sigma$ (the LOSVD), over estimates the predicted cluster mass at all masses.
@@
 Additionally, the number of galaxies observed, $N_{gal}$, further reduces the MAE and RMSE on the predictions but also lowers the cross over point to $\sim10^{13.5}$ \msol.
-
-\begin{figure*} 
-	\includegraphics[width=\textwidth]{figures/Probcomparison.pdf} 
-	\caption{Mass predictions for the power law scaling relation (Equation~\ref{eq:power law}) and the probability based technique with different input features as a function of true cluster mass.
-The bottom row of panels shows the fractional error (Equation~\ref{eq: fractional error}) also as a function of true cluster mass.
-The solid black line shows the 1:1 relation.
-The solid, colored line is the median predicted mass for the targeted observing, and the colored, dashed line is the median recovered mass for the HETDEX-like observations.
-The shaded regions represent the 68\% scatter around the median values.} \label{fig:Probability comparison}
-\end{figure*}
-
-\editorial{Need to talk about the cluster rotations to fill out the survey data. Otherwise there aren't that many clusters detected.}
-
-\begin{figure*} 
-	\includegraphics[width=\textwidth]{figures/MLcomparison.pdf} 
-	\caption{Mass predictions for the power law scaling relation (Equation~\ref{eq:power law}) and the ML based technique with different input features as a function of true cluster mass.
-The bottom row of panels shows the fractional error (Equation~\ref{eq: fractional error}) also as a function of true cluster mass.
-The solid black line shows the 1:1 relation.
-The solid, colored line is the median predicted mass for the targeted observing, and the colored, dashed line is the median recovered mass for the HETDEX-like observations.
-The shaded regions represent the 68\% scatter around the median values.} \label{fig: ML comparison}
-\end{figure*}
 
@@
 
-\section{HETDEX as a Galaxy Cluster Survey}\label{sec:discussion}
+\section{HETDEX as a Galaxy Cluster Survey at $z < 0.5$}\label{sec:discussion}
 

### 2016-03-09 ms.tex
more casey corrections

@@
 The result is a 398.49 sq.
-degree mock catalog occupying a $60 \leq RA \leq 90$ and $-40 \leq DEC \leq -61$ portion of the sky.
+degree mock catalog occupying a $4^h \leq RA \leq 6^h$ and $-61\degree < DEC < -41\degree$ portion of the sky.
 It contains 238 million galaxies with \sdssr\ mag $< 29$ and $z \leq 8.7$.
@@
 \subsection{Mass estimates}
-\begin{table*}
-\centering
-\caption{Summary of the errors associated with the Targeted and Survey observation strategies, as an ensemble of predictions.
+% \begin{table*}
+% \centering
+% \caption{Summary of the errors associated with the Targeted and Survey observation strategies, as an ensemble of predictions.
 See the text for discussion about the MAE and RMSE.
@@
 See Sections \ref{sec:probability method} and \ref{sec:machine learning method} for a discussion on prediction intervals.}
-\begin{tabular}{cccccccc}
-	%\hline
-	&& \multic{3}{Targeted} & \multic{3}{Survey} \\
-	\cline{3-5} \cline{6-8}
-	& Input Features & MAE & RMSE & Overlap & MAE & RMSE & Overlap \\
-	& & (dex) & (dex) & (\%) & (dex) & (dex) & (\%) \\
-	\hline
-	\rottext{4}{Prob Based} & Power Law & 0.259 & 0.394 & \nd & 0.243 & 0.357 & \nd \\
-	&$\sigma$ & 0.220 & 0.337 & \nd & 0.210 & 0.310 & \nd \\
-	&$\sigma, z$ & 0.193 & 0.283 & \nd & 0.184 & 0.271 & \nd \\
-	&$\sigma, z, N_{gal}$ & 0.128 & 0.204 & \nd & 0.141 & 0.215 & \nd \\
-	\hline
-	\rottext{4}{ML Based} & Power Law & 0.258 & 0.394 & \nd & 0.255 & 0.380 & \nd \\
-	&$\sigma$ & 0.241 & 0.359 & \nd & 0.223 & 0.342 & \nd \\
-	&$\sigma, z$ & 0.193 & 0.282 & \nd & 0.197 & 0.290 & \nd \\
-	&$\sigma, z, N_{gal}$ & 0.118 & 0.192 & \nd & 0.140 & 0.221 & \nd \\
-	\hline
-\end{tabular}
-\label{tbl:mass comparisons}
-\end{table*}
-
-In this section we discuss the how accurately we are able to reproduce the true cluster mass from a set of observations.
-We report on two methods the probability based approach (Section \ref{sec:probability method}) and the ML based method (Section \ref{sec:machine learning method}).
-For each method we consider both targeted and HETDEX-like observing strategies.
-
-We include the cluster masses recovered through the power law scaling relation given in Equation \ref{eq:power law} for the perfect, targeted and survey observations.
-It should serve as baseline to compare the probability based and ML cluster mass recovery methods.
-And, while there are many possible metrics to evaluate performance, we compute two: the median absolute error (MAE)
-\begin{equation}
-\mathrm{MAE}(y,\hat{y}) = \mathrm{median}(|y_1 - \hat{y_1}|, \ldots, |y_n - \hat{y_n}|) \nonumber
-\end{equation}
-where $y$ is the true value and $\hat{y}$ is the predicted value, and the root mean squared error (RMSE)
-\begin{equation}
-	\mathrm{RMSE}(y,\hat{y}) = \bigg{[}\frac{1}{N} \sum_{i=0}^N (y_i - \hat{y_i})^2 \bigg{]}^{1/2}.\nonumber
-\end{equation} 
-Both metrics evaluate how closely the ensemble of predicted cluster masses are to the true cluster masses, and in both cases lower numbers are better.
-
-Just because a predicted cluster mass may not exactly match the true value does not mean it is a bad prediction.
-In addition to the MAE and RMSE, we also report the fraction of predictions where the the true cluster mass is contained within the 68\% confidence or prediction intervals (see Sections \ref{sec:probability method} and \ref{sec:machine learning method}).
-
-The cluster masses predicted by Equation \ref{eq:power law} gives the following results.
-The MAE is 0.263 dex and for both the targeted and survey observations.
-The RMSE is 0.396 dex and 0.394 dex for the targeted and survey observations respectively.
-This scatter in recovered masses can be attributed to both physical and numerical effects.
-As the cluster mass increases, clusters become more virialized and contain many individual galaxies.
-The presence of any in-falling matter onto lower mass clusters can introduce a significant amount of substructure, which can increase the observed LOSVD increasing the predicted mass.
-Also, as the number of cluster galaxies decreases the LOSVD PDF is poorly sampled leading to poorly recovered cluster masses due to numerical effects.
-The masses presented here are recovered using the best possible conditions, where we have perfect knowledge of the cluster membership.
-In reality, the mass recovery levels presented in this section represent an upper bound (the best) on the accuracy achievable through this method.
-\editorial{\cite{Ntampaka2015} does have a discussion about how well they do with contaminated galaxy catalogs.
-We could do something similar and have a similar discussion, but I'm not sure it is worth it.
-Should be simple enough to do with the targeted catalog, but with the HETDEX catalog it would be pretty bad IMO.
-We should also talk about how often the true mass lies within the error bars.
-Many of them are going to be with the 68\% range, but we can drop the error estimates to $0.5\sigma$ if that actually means anything}
+% \begin{tabular}{cccccccc}
+% 	%\hline
+% 	&& \multic{3}{Targeted} & \multic{3}{Survey} \\
+% 	\cline{3-5} \cline{6-8}
+% 	& Input Features & MAE & RMSE & Overlap & MAE & RMSE & Overlap \\
+% 	& & (dex) & (dex) & (\%) & (dex) & (dex) & (\%) \\
+% 	\hline
+% 	\rottext{4}{Prob Based} & Power Law & 0.259 & 0.394 & \nd & 0.243 & 0.357 & \nd \\
+% 	&$\sigma$ & 0.220 & 0.337 & \nd & 0.210 & 0.310 & \nd \\
+% 	&$\sigma, z$ & 0.193 & 0.283 & \nd & 0.184 & 0.271 & \nd \\
+% 	&$\sigma, z, N_{gal}$ & 0.128 & 0.204 & \nd & 0.141 & 0.215 & \nd \\
+% 	\hline
+% 	\rottext{4}{ML Based} & Power Law & 0.258 & 0.394 & \nd & 0.255 & 0.380 & \nd \\
+% 	&$\sigma$ & 0.241 & 0.359 & \nd & 0.223 & 0.342 & \nd \\
+% 	&$\sigma, z$ & 0.193 & 0.282 & \nd & 0.197 & 0.290 & \nd \\
+% 	&$\sigma, z, N_{gal}$ & 0.118 & 0.192 & \nd & 0.140 & 0.221 & \nd \\
+% 	\hline
+% \end{tabular}
+% \label{tbl:mass comparisons}
+% \end{table*}
 
@@
 
+In this section we discuss the how accurately we are able to reproduce the true cluster mass from a set of observations.
+We report on three methods, the power law based approach (Eq.
+\ref{eq:power law}), the probability based approach (Section \ref{sec:probability method}) and the ML based method (Section \ref{sec:machine learning method}).
+For each method we consider observations with perfect knowledge, targeted observations and survey observations.
+
+Because it represents the best possible scenario, the perfect knowledge observations should serve as baseline to compare the probability based and ML cluster mass recovery methods.
+And, while there are many possible metrics to evaluate performance, we compute two: the average bias
+\begin{equation}
+\mathrm{\mu_{bias}}(y,\hat{y}) = \frac{1}{N} \sum_{i=0}^N (\hat{y_i} - y_i).\nonumber
+\end{equation}
+where $y$ is the true value and $\hat{y}$ is the predicted value, and the scatter about the bias
+\begin{equation}
+	\sigma_{bias}(y,\hat{y}, \mu_{bias}) = \bigg{[}\frac{1}{N-1} \sum_{i=0}^N (\hat{y_i} - y_i - \mu_{bias})^2 \bigg{]}^{1/2}\nonumber
+\end{equation}
+for different bins of cluster mass. Both metrics evaluate how closely the ensemble of predicted cluster masses are to the true cluster masses, and in both cases values closer to zero are better.
+
+We begin with the perfect knowledge observations.
+These observations are of the same clusters as the targeted observations but without any observational limits.
+The cluster masses predicted by Equation \ref{eq:power law} gives the following results.
+Across all cluster masses, we find $\mu_{bias} = 0.15\pm{0.24}$ dex.
+The scatter in recovered masses can be attributed to both physical and numerical effects.
+The presence of any in-falling matter onto lower mass clusters can introduce a significant amount of substructure, which increases the observed LOSVD increasing the predicted mass \citeeg{Ntampaka2015}.
+Also, as the number of cluster galaxies decreases the LOSVD PDF is poorly sampled leading to poorly recovered cluster masses due to numerical effects.
+The masses presented here are recovered using the best possible conditions, where we have perfect knowledge of the cluster membership.
+In reality, the mass recovery levels presented in this section represent an upper bound (the best) on the accuracy achievable through this method.
+
+\editorial{\cite{Ntampaka2015} does have a discussion about how well they do with contaminated galaxy catalogs.
+We could do something similar and have a similar discussion, but I'm not sure it is worth it.
+Should be simple enough to do with the targeted catalog, but with the HETDEX catalog it would be pretty bad IMO.
+We should also talk about how often the true mass lies within the error bars.
+Many of them are going to be with the 68\% range, but we can drop the error estimates to $0.5\sigma$ if that actually means anything}
+
+For the targeted and survey observations the power law predicted cluster masses give $\mu_{bias} =0.13\pm{0.37}$ dex and $\mu_{bias} =0.11\pm{0.36}$ dex, respectively.
+So while, both realistic observations have similar levels of bias, the amount of scatter significantly decreases as more cluster member galaxies are detected, better sampling the LOSVD PDF.
+
 \begin{figure*} 
@@
 
-The MAE and RMSE associated with the ensemble of predictions are summarized in Table \ref{tbl:mass comparisons}.
-As expected, we find that both the probability based and ML based methods out perform the standard power law based methods for both the targeted and survey observations.
-We also find that the ML based method produces lower ensemble error for both the observation strategies when compared to the probability based method, although the MAE and RMSE are reduced by only $\sim0.01$ dex.
-\editorial{here is where we would talk about cross validation on the errors.}
-
 In both Figures \ref{fig:Probability comparison} and \ref{fig: ML comparison}, we show the predicted versus true cluster masses for each of the two observing strategries.
-In each panel the solid black line is the 1:1 relationship, the solid colored line is the median recovered mass for the targeted observing, and the colored, dashed line is the median recovered mass for the HETDEX-like observations.
+In each panel the solid black line is the 1:1 relationship, the solid purple line is the median recovered mass for the targeted observing, and the turquoise, dashed line is the median recovered mass for the HETDEX-like observations.
 The shaded regions are the 68\% scatter around the median values (the 16\% and 84\% quartiles).
+For reference we also show the median masses recovered with perfect knowledge as a solid orange line.
 The lower panels show the fractional cluster mass error:
@@
 
-In both figures we successively add additional information to further constrain the true cluster masses which subsequently reduces the error associated with the ensemble of predictions (see Table \ref{tbl:mass comparisons}).
+Qualitatively, the top panels of Figures \ref{fig:Probability comparison} and \ref{fig: ML comparison} show that both the probability based and ML based methods out perform (closer to the black 1:1 relation) the power law method when taking advantage of other cluster observables ($z$, $N_{gal}$, etc.).
+Generally, we find that the single parameter probability and ML methods perform significantly poorer than the power law method, especially at low cluster masses.
+When combined with the cluster redshift, the predicted cluster masses are improved, even though it is unclear exactly why the additional information should effect the predicted cluster mass.
+The final addition of the number of observed galaxies, $N_{gal}$ acts as a type of richness estimate, and significantly improves both the bias and the amount of scatter in the predicted masses.
+
+% In both figures we successively add additional information to further constrain the true cluster masses which subsequently reduces the error associated with the ensemble of predictions (see Table \ref{tbl:mass comparisons}).
 The power law derived masses, using the single (not including the cosmological parameters) free parameter, $\sigma$ (the LOSVD), over estimates the predicted cluster mass at all masses.
@@
 % }
-
-\section{HETDEX as a Galaxy Cluster Survey at $z < 0.5$}\label{sec:discussion}
-
 \begin{table*}
 \centering
-\caption{Associated mass prediction errors (MAE) for different bins of predicted mass.
-This table shows the relative error for the targeted (top section) and survey (bottom section) observations for different predicted mass bins.
-The values in the table correspond to the MAE for the galaxies in the predicted mass bin (top row) for the different mass recovery strategies (leftmost column).
-It can be used to understand how precise the predicted cluster mass is.}
+\caption{Bias and scatter of the true cluster mass for different bins of predicted cluster mass.
+This table shows the offset and scatter in the true cluster mass for the perfect (top section), targeted (middle section), and survey (bottom section) observations in different predicted mass bins.
+The different mass recovery strategies are given in the leftmost column.
+It can be used to understand how the predicted cluster mass differs from the true cluster masses.
+Positive numbers indicate the predicted cluster mass over estimates when compared to the true cluster mass.}
 \begin{tabular}{cccccccccc} 
@@
 		\cline{3-10} 
-		\multicolumn{2}{c}{Input Features} & $11.5-12$ & $12-12.5$ & $12.5-13$ & $13-13.5$ & $13.5-14$ & $14-14.5$ & $14.5-15$ & $15-15.5$ \\
+		\multicolumn{2}{c}{Method} & $11.5-12$ & $12-12.5$ & $12.5-13$ & $13-13.5$ & $13.5-14$ & $14-14.5$ & $14.5-15$ & $15-15.5$ \\
 		\hline 
-		\rottext{4}{Prob Based} & Power Law & 0.602 & 0.376 & 0.340 & 0.278 & 0.225 & 0.177 & 0.114 & 0.041 \\
-		&$\sigma$ & 1.030 & 0.655 & 0.389 & 0.212 & 0.160 & 0.158 & 0.224 & 0.328 \\
-		&$\sigma, z$ & 0.804 & 0.476 & 0.242 & 0.173 & 0.170 & 0.210 & 0.353 & 0.529 \\
-		&$\sigma, z, N_{gal}$ & 0.649 & 0.372 & 0.163 & 0.124 & 0.113 & 0.111 & 0.105 & 0.241 \\
+		\rottext{4}{Prob Based} & Power Law & $0.49\pm{0.34}$ & $0.28\pm{0.39}$ & $0.23\pm{0.34}$ & $0.16\pm{0.22}$ & $0.11\pm{0.16}$ & $0.07\pm{0.14}$ & $0.02\pm{0.14}$ & $-0.07\pm{0.10}$ \\
+		&$\sigma$ & $0.87\pm{0.15}$ & $0.53\pm{0.24}$ & $0.32\pm{0.26}$ & $0.16\pm{0.20}$ & $0.10\pm{0.16}$ & $0.07\pm{0.14}$ & $0.05\pm{0.16}$ & $-0.18\pm{0.17}$ \\
+		&$\sigma, z$ & $0.76\pm{0.16}$ & $0.42\pm{0.21}$ & $0.17\pm{0.23}$ & $0.01\pm{0.19}$ & $-0.06\pm{0.16}$ & $-0.11\pm{0.55}$ & $-0.14\pm{0.16}$ & $-0.38\pm{0.34}$ \\
+		&$\sigma, z, N_{gal}$ & $0.65\pm{0.10}$ & $0.28\pm{0.14}$ & $0.04\pm{0.47}$ & $-0.02\pm{0.14}$ & $-0.02\pm{0.10}$ & $-0.05\pm{0.54}$ & $-0.22\pm{1.61}$ & $-6.62\pm{8.08}$ \\
 		\hline
-		\rottext{4}{ML Based} & Power Law & 0.602 & 0.376 & 0.340 & 0.278 & 0.225 & 0.177 & 0.114 & 0.041 \\
-		&$\sigma$ & 0.773 & 0.557 & 0.287 & 0.210 & 0.230 & 0.267 & 0.337 & 0.323 \\
-		&$\sigma, z$ & 0.631 & 0.380 & 0.211 & 0.172 & 0.182 & 0.236 & 0.284 & 0.265 \\
-		&$\sigma, z, N_{gal}$ & 0.539 & 0.304 & 0.148 & 0.117 & 0.105 & 0.095 & 0.078 & 0.110 \\
+		\rottext{4}{ML Based} & Power Law & $0.49\pm{0.34}$ & $0.28\pm{0.39}$ & $0.23\pm{0.34}$ & $0.16\pm{0.22}$ & $0.11\pm{0.16}$ & $0.07\pm{0.14}$ & $0.02\pm{0.14}$ & $-0.07\pm{0.10}$ \\
+		&$\sigma$ & $0.69\pm{0.20}$ & $0.36\pm{0.27}$ & $0.15\pm{0.29}$ & $-0.02\pm{0.24}$ & $-0.07\pm{0.21}$ & $-0.09\pm{0.19}$ & $-0.11\pm{0.18}$ & $-0.12\pm{0.19}$ \\
+		&$\sigma, z$ & $0.62\pm{0.18}$ & $0.33\pm{0.22}$ & $0.12\pm{0.25}$ & $-0.01\pm{0.20}$ & $-0.06\pm{0.18}$ & $-0.09\pm{0.16}$ & $-0.11\pm{0.17}$ & $-0.19\pm{0.13}$ \\
+		&$\sigma, z, N_{gal}$ & $0.51\pm{0.14}$ & $0.23\pm{0.18}$ & $0.05\pm{0.17}$ & $-0.02\pm{0.14}$ & $-0.02\pm{0.10}$ & $-0.02\pm{0.08}$ & $-0.02\pm{0.08}$ & $-0.08\pm{0.08}$ \\
 		\hline 
 		\hline
-		\rottext{4}{Prob Based} & Power Law & \nd & \nd & 0.520 & 0.319 & 0.263 & 0.214 & 0.140 & 0.069 \\
-		&$\sigma$ & \nd & \nd & 0.765 & 0.434 & 0.198 & 0.149 & 0.163 & 0.346 \\
-		&$\sigma, z$ & \nd & \nd & 0.592 & 0.305 & 0.162 & 0.165 & 0.257 & 0.396 \\
-		&$\sigma, z, N_{gal}$ & \nd & \nd & 0.476 & 0.171 & 0.125 & 0.141 & 0.141 & 15.002 \\
+		\rottext{4}{Prob Based} & Power Law & $0.49\pm{0.31}$ & $0.27\pm{0.41}$ & $0.20\pm{0.43}$ & $0.13\pm{0.39}$ & $0.10\pm{0.33}$ & $0.09\pm{0.27}$ & $0.02\pm{0.18}$ & $-0.08\pm{0.09}$ \\
+		&$\sigma$ & $1.02\pm{0.13}$ & $0.66\pm{0.19}$ & $0.40\pm{0.24}$ & $0.17\pm{0.25}$ & $0.02\pm{0.25}$ & $-0.08\pm{0.22}$ & $-0.19\pm{0.19}$ & $-0.35\pm{0.26}$ \\
+		&$\sigma, z$ & $0.85\pm{0.18}$ & $0.49\pm{0.20}$ & $0.25\pm{0.24}$ & $0.08\pm{0.24}$ & $-0.06\pm{0.23}$ & $-0.21\pm{0.56}$ & $-0.35\pm{0.21}$ & $-0.59\pm{0.31}$ \\
+		&$\sigma, z, N_{gal}$ & $0.70\pm{0.13}$ & $0.37\pm{0.18}$ & $0.13\pm{0.20}$ & $0.01\pm{0.19}$ & $-0.05\pm{0.17}$ & $-0.12\pm{0.67}$ & $-0.44\pm{2.26}$ & $-4.45\pm{7.44}$ \\
 		\hline
-		\rottext{4}{ML Based} & Power Law & \nd & 0.583 & 0.316 & 0.337 & 0.278 & 0.214 & 0.140 & 0.069 \\
-		&$\sigma$ & \nd & 0.606 & 0.551 & 0.263 & 0.201 & 0.227 & 0.200 & 0.192 \\
-		&$\sigma, z$ & \nd & 0.916 & 0.434 & 0.206 & 0.171 & 0.205 & 0.249 & 0.202 \\
-		&$\sigma, z, N_{gal}$ & \nd & 0.780 & 0.401 & 0.155 & 0.129 & 0.136 & 0.145 & 0.142 \\
+		\rottext{4}{ML Based} & Power Law & $0.49\pm{0.31}$ & $0.27\pm{0.41}$ & $0.20\pm{0.43}$ & $0.13\pm{0.39}$ & $0.10\pm{0.33}$ & $0.09\pm{0.27}$ & $0.02\pm{0.18}$ & $-0.08\pm{0.09}$ \\
+		&$\sigma$ & $0.76\pm{0.28}$ & $0.54\pm{0.29}$ & $0.26\pm{0.31}$ & $0.01\pm{0.31}$ & $-0.13\pm{0.32}$ & $-0.23\pm{0.30}$ & $-0.33\pm{0.29}$ & $-0.32\pm{0.09}$ \\
+		&$\sigma, z$ & $0.66\pm{0.13}$ & $0.37\pm{0.23}$ & $0.17\pm{0.26}$ & $0.03\pm{0.25}$ & $-0.09\pm{0.24}$ & $-0.21\pm{0.22}$ & $-0.31\pm{0.25}$ & $-0.28\pm{0.13}$ \\
+		&$\sigma, z, N_{gal}$ & $0.57\pm{0.12}$ & $0.28\pm{0.21}$ & $0.09\pm{0.21}$ & $-0.01\pm{0.18}$ & $-0.05\pm{0.16}$ & $-0.08\pm{0.14}$ & $-0.07\pm{0.12}$ & $-0.14\pm{0.13}$ \\
+		\hline
+		\hline
+		\rottext{4}{Prob Based} & Power Law & \nd & \nd & $0.53\pm{0.15}$ & $0.30\pm{0.29}$ & $0.16\pm{0.33}$ & $0.07\pm{0.31}$ & $0.01\pm{0.24}$ & $-0.09\pm{0.13}$ \\
+		&$\sigma$ & \nd & \nd & $0.77\pm{0.10}$ & $0.42\pm{0.18}$ & $0.18\pm{0.22}$ & $-0.03\pm{0.22}$ & $-0.18\pm{0.19}$ & $-0.39\pm{0.22}$ \\
+		&$\sigma, z$ & \nd & \nd & $0.61\pm{0.12}$ & $0.29\pm{0.19}$ & $0.08\pm{0.22}$ & $-0.11\pm{0.21}$ & $-0.38\pm{1.30}$ & $-0.48\pm{0.27}$ \\
+		&$\sigma, z, N_{gal}$ & \nd & \nd & $0.48\pm{0.13}$ & $0.18\pm{0.18}$ & $0.02\pm{0.19}$ & $-0.08\pm{0.19}$ & $-0.50\pm{2.25}$ & $-8.81\pm{7.98}$ \\
+		\hline
+		\rottext{4}{ML Based} & Power Law & \nd & $0.06\pm{0.80}$ & $0.17\pm{0.39}$ & $0.17\pm{0.41}$ & $0.13\pm{0.38}$ & $0.07\pm{0.32}$ & $0.01\pm{0.24}$ & $-0.09\pm{0.13}$ \\
+		&$\sigma$ & \nd & $0.58\pm{0.17}$ & $0.54\pm{0.26}$ & $0.24\pm{0.28}$ & $0.03\pm{0.30}$ & $-0.17\pm{0.30}$ & $-0.26\pm{0.30}$ & $-0.30\pm{0.25}$ \\
+		&$\sigma, z$ & \nd & $1.02\pm{0.35}$ & $0.42\pm{0.21}$ & $0.19\pm{0.25}$ & $0.03\pm{0.25}$ & $-0.14\pm{0.25}$ & $-0.25\pm{0.24}$ & $-0.31\pm{0.26}$ \\
+		&$\sigma, z, N_{gal}$ & \nd & $0.91\pm{0.45}$ & $0.39\pm{0.19}$ & $0.12\pm{0.21}$ & $-0.00\pm{0.20}$ & $-0.08\pm{0.19}$ & $-0.14\pm{0.19}$ & $-0.21\pm{0.20}$ \\
 	\hline
 	\end{tabular}
-\label{tbl:sersic number bins}
+\label{tbl:mass bias}
 \end{table*}
+
+We quantify the bias and scatter for all of the different cluster mass recovery strategies and observing methods in Table \ref{tbl:mass bias}.
+It should serve as a type of look up table for future cluster observations with HETDEX.
+The columns represent bins of predicted galaxy cluster mass and the individual values show the bias and scatter of the true cluster mass.
+The three horizontal sections represent represent perfect, targeted and survey observations respectively.
+So, for example, if a cluster mass is predicted using the $ML_{\sigma, z}$ method and targeted observations to be Log M $=13-13.5$ \Msol, it is biased upward by $0.03\pm0.25$ dex.
+
+ A few caveats apply to the numbers given in Table \ref{tbl:mass bias}.
+While we provide corrections for cluster masses above $10^{15}$, they are estimated from only a handful of objects, and do not constitute a representative sample of clusters.
+On the oposite end of the cluster mass spectrum, survey observations of low mass clusters are incomplete for two potential reasons.
+There are very few, if any, clusters detected with survey observations below $10^{12}$.
+Missing corrections above $10^{12}$ in the probability based methods are due to low number statstics and an inability to sample the cluster mass PDF well enough to assign cluster mass predictions.
+
+\section{HETDEX as a Galaxy Cluster Survey at $z < 0.5$}\label{sec:discussion}
 
@@
 
-Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
-
 \section{SUMMARY}\label{sec:summary}
@@
 It is the author's hope that this work may be useful to others when conducting their own research.
-Because this work relies heavily on (often) complex data analysis, and in order to promote transparency, we provide all of the code used to conduct this study at https://github.com/boada/desCluster.
+Because this work relies heavily on (often) complex data analysis, and in order to promote transparency and reproducible science, we provide all of the code used to conduct this study at https://github.com/boada/desCluster.
 Regrettably, large file size prevents including the source data with the analysis routines.

### 2016-03-10 ms.tex
last of casey's initial comments.

@@
 The study of clusters of galaxies has been argued to be a very effective way to measure cosmological parameters, including measuring dark energy and testing models of gravity.
-The Hobby Eberly Telescope Dark Energy Experiment (HETDEX) will observe many hundreds of square degrees, covering a large sample of galaxy clusters out to $z = 0.5$ based on their optical spectra ($3500-5500\AAA$).
+The Hobby Eberly Telescope Dark Energy Experiment (HETDEX) will observe many hundreds of square degrees, covering a large sample of galaxy clusters to $z < 0.5$ based on their optical spectra ($3500-5500\AAA$).
 The spectra will provide important measures of the clusters dynamics and may enable constraints on cosmological parameters, but only if the measurements provide accurate estimates of the total cluster masses.
-We have carried out a study to investigate the ability of HETDEX to recover accurate galaxy cluster masses over a wide range of masses and redshifts.
-We used a detailed mock galaxy catalog and present mock observations of two different scenarios: (1) We targeted individual galaxy clusters to investigate the recovery of parameters with such observations.
-(2) We created and evaluated a HETDEX-like selection "function'' of galaxies over a similarly sized portion of the sky and use well adopted techniques to recover the dynamical properties, such as velocity dispersion and mass, and benchmark these against observations with perfect knowledge.
-Using both observing strategies, we produce cluster mass probability density functions $P(X|M,z)$, which can be used to determine the probability that a galaxy cluster of given mass (M), located at redshift ($z$) determined using observable parameter (X).
+We carry out a study to investigate the ability of HETDEX to recover accurate galaxy cluster masses over a wide range of masses and redshifts.
+We use a detailed mock galaxy catalog and present mock observations of two different scenarios: (1) We targeted individual galaxy clusters to investigate the recovery of parameters with such observations.
+(2) We created and evaluated a HETDEX-like selection ``function'' of galaxies over a similarly sized portion of the sky and use well adopted techniques to recover the dynamical properties, such as velocity dispersion and mass, and benchmark these against observations with perfect knowledge.
+Using both observing strategies, we produce cluster mass probability density functions $P(M|z, X)$, which can be used to determine the probability that a galaxy cluster of given mass (M), located at redshift ($z$) determined using observable parameter (X).
 \editorial{This sentence will summarize how well HETDEX will do, and how that might be improved with targeted observations.}
@@
 As mass is not a direct observable, a lot of work is underway to characterize galaxy cluster masses with an observable feature of galaxy clusters.
-The goal is to constrain, as best possible, $P(M|x)$ the probability ($P$) that a galaxy cluster of given mass ($M$), located at redshift ($z$) determined using observable parameter ($X$).
+The goal is to constrain, as best possible, $P(M|z, X)$ the probability ($P$) that a galaxy cluster of given mass ($M$), located at redshift ($z$) determined using observable parameter ($X$).
 Generally, cluster mass calibrations fall into two distinct camps, simulation based and direct or statistical calibration.
@@
 This recipe has two distinct but not always independent tracks.
-The ``direct'' method uses the direct observations of a small set of clusters and then uses known mass estimators, X-ray temperatures and luminosities \citeeg{Mantz2010, Rykoff2014}, cosmic microwave background (CMB) observations \citeeg{Vanderlinde2010, Sehgal2011}, optical richness \citeeg{Abell1958, Rykoff2012} or weak lensing (WL) \citeeg{Rozo2010} as examples, which provide a ``true'' mass.
+The ``direct'' method uses direct observations of a small set of clusters and then uses known mass estimators, X-ray temperatures and luminosities \citeeg{Mantz2010, Rykoff2014}, cosmic microwave background (CMB) observations \citeeg{Vanderlinde2010, Sehgal2011}, optical richness \citeeg{Abell1958, Rykoff2012} or weak lensing (WL; \eg\ \citealt{Rozo2010}) as examples, which provide a ``true'' mass.
 This directly calibrates the observable--mass relation which is then applied to a much larger sample.
@@
 The Sunyaev--Zel'dovich Effect (SZE; \citealt{Sunyaev1972}), which uses the up--scattering of CMB photons to estimate cluster masses, provides accurate estimations of mass, but the ability to detect low mass galaxy clusters is currently limited by technology \citeeg{Carlstrom2002a}.
-WL estimates are, in principle, correct in the mean, but they suffer from signal-to-noise requirements, limiting their usefulness in low mass clusters, and potentially suffer from line-of-sight effects as the effect is sensitive to all mass along the line of sight.
+WL estimates are, in principle, correct in the mean, but they suffer from signal-to-noise requirements, limiting their usefulness in low mass clusters, and potentially suffer from line-of-sight effects as WL is sensitive to all mass along the line-of-sight.
 Virial mass estimators which determine the cluster mass based on the motions of the member galaxies \citeeg{Ruel2014, Sifon2015} are promising in that it is a direct measurement of the depth of clusters potential well, but suffers from systematics due to cluster formation physics which disrupts the velocity field.
@@
 The South Pole Telescope (SPT; \citealt{Carlstrom2011}) and the Atacama Cosmology Telescope (ACT; \citealt{Swetz2011}) are discovering many clusters through the SZE.
-Optically, the on going The Dark Energy Survey (DES; \citealt{DES2005}) and planned Large Synoptic Survey Telescope (LSST; \citealt{LSST2012}) will identify many thousands of clusters to much lower masses than is possible with SZE measurements.
-However, regardless of the discovery method used, spectroscopic followup is needed to further constrain $P(X|M,z)$.
+Optically, the on going Dark Energy Survey (DES; \citealt{DES2005}) and planned Large Synoptic Survey Telescope (LSST; \citealt{LSST2012}) will identify many thousands of clusters to much lower masses than is possible with SZE measurements.
+However, regardless of the discovery method used, spectroscopic followup is needed to further constrain $P(M|z,X)$.
 But as the cluster dataset grows to many tens of thousands of clusters individual followup becomes increasingly impractical.
@@
 The Hobby Eberly Telescope Dark Energy eXperiment (HETDEX; \citealt{Hill2008}) is a trailblazing effort to observe high-redshift large scale structures using cutting edge wide-field integral field unit (IFU) spectrographs.
-Designed to probe the evolution of the dark energy equation of state etched onto high redshift ($z>2$) galaxies by the Baryon Acoustic Oscillations \citep{Eisenstein2005} in the first moments of the universe, the survey will observe two fields for a total of 420 \degsq\ from two fields (300 \degsq, Spring field and 120 \degsq, Fall field).
+Designed to probe the evolution of the dark energy equation of state etched onto high redshift ($z>2$) galaxies by the Baryon Acoustic Oscillations \citep{Eisenstein2005} in the first moments of the universe, the survey will observe two fields for a total of 420 \degsq\ (300 \degsq, Spring field and 120 \degsq, Fall field).
 Tuned to find \lya\ emitting (LAE) galaxies at $1.9<z<3.5$, HETDEX expects to find 800,000 LAEs, and more than one million [\ion{O}{ii}] emitting galaxies at $z<0.5$ masquerading as high-redshift galaxies \citep{Acquaviva2014}.
 
-While a large portion of the $\sim10^6$ interloping [\ion{O}{ii}] galaxies will be field (not associated with a bound structure) galaxies, the large area covered by HETDEX is expected to contain as many as 50 Virgo-sized ($M_{dyn}\sim 10^{15}$ \msol) clusters at $z<0.5$ (\editorial{talk to casey about how I calculated this number}).
+While a large portion of the $\sim10^6$ interloping [\ion{O}{ii}] galaxies will be field (not associated with a bound structure) galaxies, the large area covered by HETDEX is expected to contain as many as 50 Virgo-sized ($M_{dyn}>10^{15}$ \msol) clusters at $z<0.5$ (\editorial{talk to casey about how I calculated this number}).
 The near-complete spectroscopic coverage allows an unprecedentedly detailed look at a very large number of clusters ranging from group scales to the very massive.
@@
 Connecting the dynamical properties derived from spectroscopy to the properties inferred from other studies insures the greatest impact on future work.
-HETDEX overlaps with the Sloan Digital Sky Survey (SDSS; \citealt{Blanton2001a}), SDSS stripe 82 \citep{Annis2014}, the Dark Energy Survey (DES; \citealt{DES2005}), and the upcoming DECam/IRAC Galaxy Environment Survey (DIRGES; PI: Papovich, C.
-Papovich \etal\ in preparation), the The \emph{Spitzer}/HETDEX Exploratory Large-Area Survey (SHELA; Papovich \etal\ 2016, ApJS, submitted), and The \emph{Spitzer} IRAC Equatorial Survey (SpIES; Timlin \etal\ 2016, ApJ, submitted).
+HETDEX overlaps with the Sloan Digital Sky Survey (SDSS; \citealt{Blanton2001a}), SDSS stripe 82 \citep{Annis2014}, DES, and the upcoming DECam/IRAC Galaxy Environment Survey (DIRGES; PI: Papovich, C.
+Papovich \etal\ in preparation), the \emph{Spitzer}/HETDEX Exploratory Large-Area Survey (SHELA; Papovich \etal\ 2016, ApJS, submitted), and the \emph{Spitzer} IRAC Equatorial Survey (SpIES; Timlin \etal\ 2016, ApJ, submitted).
 While the potential dataset is very rich, two large issues remain.
@@
 The ``Buzzard'' mock galaxy catalogs (R.
-Wechsler et al., private communication) cover 375.68 \degsq\ between $4^h< RA < 6^h$ and $-61\degree < DEC < -41\degree$ and are derived from a combination of Sub-halo Abundance Matching (ShAM) and ADDSEDs (Adding Density Dependent Spectral Energy Distributions) tied to an in house n-body cosmological simulation.
+Wechsler et al., private communication) cover 398.49 \degsq\ between $4^h< RA < 6^h$ and $-61\degree < DEC < -41\degree$ and are derived from a combination of Sub-halo Abundance Matching (ShAM) and ADDSEDs (Adding Density Dependent Spectral Energy Distributions) tied to an in house n-body cosmological simulation.
 A brief description of the catalog creation is described as follows.
@@
 
-Galaxy $M_r$ luminosities are added to the velocity peaks using ShAM \citep{Reddick2013}, and ADDSEDs (Adding Density Dependent Spectral Energy Distributions) assign luminosities in the other bands.
+Galaxy $M_r$ luminosities are added to the velocity peaks using ShAM \citep{Reddick2013}, and ADDSEDs assign luminosities in the other bands.
 A $M_r$-density-SED relation is created using a SDSS training set, and for each mock galaxy the SED of a randomly selected training set galaxy which has a similar $M_r$ and density is assigned.
-The result is a 398.49 sq.
-degree mock catalog occupying a $4^h \leq RA \leq 6^h$ and $-61\degree < DEC < -41\degree$ portion of the sky.
-It contains 238 million galaxies with \sdssr\ mag $< 29$ and $z \leq 8.7$.
+The result is a 398.49 \degsq\ mock catalog containing 238 million galaxies with $\sdssr < 29$ mag and $z \leq 8.7$.
 
@@
 We investigate the accuracy of the halo mass distribution by comparing the cumulative number density of halos above a mass ($M_{200c}$) threshold to the halo mass function (HMF) of \cite{Tinker2008}.
-We calculate the HMF is calculated at central redshifts of 0.1, 0.2, and 0.4 using {\tt HMFcalc} \citep{Murray2013} and compared to galaxies in a redshift window of $\Delta z\pm0.01$.
+We calculate the HMF at central redshifts of 0.1, 0.2, and 0.4 using {\tt HMFcalc} \citep{Murray2013} and compared to galaxies in a redshift window of $\Delta z\pm0.01$.
 We find a very good agreement between the predicted HMF and the observed distribution of clusters.
@@
 To assign an [\ion{O}{ii}] luminosity to each galaxy in our catalog we place the catalog galaxies on the same CMD and select all SDSS galaxies in a small 2D ($M_r$, $g-r$) bin around the galaxy.
-We extract all of the SDSS galaxies inside that bin and create a histogram of their [\ion{O}{ii}] luminosities.
+We extract all of the SDSS galaxies inside that bin and create a histogram of their [\ion{O}{ii}] luminosities, the right panel of Figure \ref{fig: oii sdss}.
 Using a slice sampling technique \citep{Neal1997} we assign the catalog galaxy an [\ion{O}{ii}] luminosity based on the distribution of SDSS galaxies extracted.
@@
 
-The right panel of Figure~\ref{fig: oii sdss} shows the CMD of all SDSS galaxies.
+The left panel of Figure~\ref{fig: oii sdss} shows the CMD of all SDSS galaxies.
 Two potential catalog galaxies are also placed on the CMD ($M_r, g-r = -17.7,~0.49$ and $M_r, g-r = -21.4,~1.24$) and indicated by the two colored boxes.
@@
 Tentatively slated to start in the spring of 2016, HETDEX will perform blind spectroscopy (R $\sim$ 750 in $3500 - 5500~\AAA$) over two fields along the celestial equator.
-The 300 \degsq, spring field and 120 \degsq, fall field will have no preselected targets.
-Using VIRUS on the 10-m Hobby-Eberly Telescope (HET; \citealt{Ramsey1998}) the completed survey is expected to have an overall fill-factor of 1/4.5, meaning that the entire area could be covered with 4.5 dithers of the entire survey.
+The 300 \degsq, spring field and 120 \degsq\ fall field will have no preselected targets.
+Using VIRUS on the 10-m Hobby-Eberly Telescope \citep{Ramsey1998} the completed survey is expected to have an overall fill-factor of 1/4.5, meaning that the entire area could be covered with 4.5 dithers of the entire survey.
 
@@
 Galaxies which lie between the IFUs are missed, as well as the galaxies which lie between the pointings, as there is no overlap between one pointing and the next.
-To cover the 375.67 \degsq\ field of the Buzzard catalog we require 5370 pointings where 0.015 \degsq\ of each pointing is covered by an IFU.
-The total area of the sky covered by an IFU is 80.80 \degsq\ which gives a filling factor of 1/4.65 slight decreased from the expected filling factor of 1/4.5.
+To cover the 398.49 \degsq\ field of the Buzzard catalog we require 5370 pointings where 0.015 \degsq\ of each pointing is covered by an IFU.
+The total area of the sky covered by an IFU is 80.80 \degsq\ which gives a filling factor of 1/4.65 slightly decreased from the expected filling factor of 1/4.5.
 
@@
 The 68\% error bars derived from the MCMC method give slightly better results with the true LOSVD value bracketed by the error bars in $\sim68\%$ of the cases versus $\sim57\%$ with bootstrapping and a single statistic.
-In addition, we prefer the maximum likelihood method for its straight forward treatment of the errors in the LOSV measurements.
+In addition, we prefer the maximum likelihood method for its straight forward treatment of the errors in the LOSV measurements, which will become important in future observations of real clusters.
 
-\subsection{Dynamical Mass}\label{sec: mass}
+\subsection{Dynamical Mass from Scaling Relations}\label{sec: mass}
 The relationship between the LOSVD and dynamical mass has been the focus of several studies \citeeg{Evrard2008, Saro2013, Sifon2013, VanderBurg2014}, and a best fitting relationship for the mass enclosed by $r_{200c}$ of the form
@@
 with $A_{1D} = 1177 \pm 4.2$ \kms\ (\citealt{Munari2013}; referred to as $\sigma_{15}$ in \citealt{Evrard2008} and other works), $\alpha = 1/3$, $h(z) = H(z)/100$, and $\sigma_{1D}$ is the LOSVD of the velocity tracers (dark matter particles, subhalos or galaxies).
+$H(z) = H_0 E(z)$ and $E(z) = \sqrt{\Omega_m(1+z^3)+\Omega_{\Lambda}}$.
 
@@
 
-\subsection{Dynamical Mass Corrections}
+\subsection{Other Estimates of Dynamical Mass}
 In this section we use two methods to predict the mass of a cluster based on other observables.
@@
 The second is based on a machine learning (ML) algorithm which attempts to ``learn'' the relationship between the observables and the desired output, the mass.
-Both of these methods are examples of supervised learning algorithms where the relationship between the observable (known) parameters and the target parameter (the mass) are both known.
+Both of these methods are examples of supervised learning algorithms where the relationship between the observable parameters and the target parameter (the mass) are both known.
 
@@
 Because $\vec{x}$ can be multidimensional, we rely on the ``corner plot'' as an aid to visualize the relationship between all of the training features.
-Figure~\ref{fig: probability corner} shows all of the one (marginalized probability) and two (joint probability) dimensional projections of the posterior probability distributions of the features of the training data.
+Figure~\ref{fig: probability corner}, a corner plot, shows all of the one (marginalized probability) and two (joint probability) dimensional projections of the posterior probability distributions of the features of the training data.
 
@@
 For the clusters making up the \emph{test} sample the mass is unknown (it is what we are trying to predict) but the other features are known.
-To determine the mass probability distribution of a test cluster, $P(M)$ we combine the conditional probability distribution, $P(M|\vec{x})$, created previously with the probability distribution of $\sigma$ through Equation~\ref{eq: Pm}.
+To determine the mass probability distribution of a test cluster, $P(M)$, we combine the conditional probability distribution, $P(M|\vec{x})$, created previously with the probability distribution of $\sigma$ through Equation~\ref{eq: Pm}.
 \begin{equation}\label{eq: Pm}
@@
 A prediction interval is an estimate of the interval encompassing future observations, with a certain probability.
-And, unlike confidence intervals, which describe certainties on the different moments of a population, a prediction interval is unique to each prediction.
+And, unlike confidence intervals, which describe uncertainties on the different moments of a population, a prediction interval is unique to each prediction.
 In many regresson analyses, such as linear fitting, the prediction intervals are based on underlying assumptions of normally distributed residuals.
@@
 Figure \ref{fig: recovery} shows the recovery fraction of member galaxies, the number of observed galaxies divided by the number of actual galaxies ($N_{obs}/N_{True}$), as function of both redshift and cluster mass.
-It is important to note that if fewer than five member galaxies are observed $N_{obs} <5$ the cluster is not considered detected, and is excluded from this figure.
+It is important to note that if fewer than five member galaxies are observed ($N_{obs} <5$) the cluster is not considered detected, and is excluded from this figure.
 As expected, the targeted observing strategy where the individual clusters are targeted through several dithers to ensure near complete coverage, performs significantly better than the survey observing strategy across all redshifts and cluster masses.
@@
 The decrease in recovery fraction with increasing redshift is a magnitude effect.
-We check this by limiting the cluster galaxy detection by absolute magnitude which increases the recovery fraction $>70\%$ at all redshifts, implying the decline is a result of the apparent magnitude cluster galaxy detection threshold.
+We check this by limiting the cluster galaxy detection by absolute magnitude which increases the recovery fraction to $>70\%$ at all redshifts, implying the decline is a result of the apparent magnitude cluster galaxy detection threshold.
 The second key feature is the strong decline in clusters recovered from survey observations.
@@
 This also shows a rapid decrease in the detection fraction, which can again be explained by considering absolute magnitudes instead of apparent magnitudes, as above.
-Also, high mass clusters are rare, so inorder to detect them we must probe a large volume of space.
+Also, high mass clusters are rare, so in order to detect them we must probe a large volume of space.
 The higher redshift cluster members suffer from the limiting apparent magnitude and suppress the recovery fraction at fixed mass.
-If we were to limit the survey to $z<0.2$ we find the recovery fraction of clusters, at all masses, increases substantially, and we find a much more consistent detection fraction across masses.
+If we were to limit the survey to $z<0.2$ we find the recovery fraction of clusters, at all masses, increases substantially, and we find a much more consistent detection fraction across all masses.
 
@@
 For the targeted and survey observations the power law predicted cluster masses give $\mu_{bias} =0.13\pm{0.37}$ dex and $\mu_{bias} =0.11\pm{0.36}$ dex, respectively.
-So while, both realistic observations have similar levels of bias, the amount of scatter significantly decreases as more cluster member galaxies are detected, better sampling the LOSVD PDF.
+So for the clusters that we detect with survey observations, we obtain similar levels of accuracy as to the targeted observations, on the average.
+This does not mean that the survey observations cannot be improved by targeted observations.
+In fact, when comparing only the galaxies which overlap between the two samples the bias and scatter of the targeted observations is significantly decreased as more cluster member galaxies are detected, better sampling the LOSVD PDF.
+The targeted observations performs similarly on the average because many lower mass clusters are included in the sample, increasing the bias of the overall sample.
 
@@
 
-In both Figures \ref{fig:Probability comparison} and \ref{fig: ML comparison}, we show the predicted versus true cluster masses for each of the two observing strategries.
+In both Figures \ref{fig:Probability comparison} and \ref{fig: ML comparison}, we show the predicted ($M_{pred}$) versus true (M) cluster masses for each of the two observing strategries.
 In each panel the solid black line is the 1:1 relationship, the solid purple line is the median recovered mass for the targeted observing, and the turquoise, dashed line is the median recovered mass for the HETDEX-like observations.
@@
 The columns represent bins of predicted galaxy cluster mass and the individual values show the bias and scatter of the true cluster mass.
-The three horizontal sections represent represent perfect, targeted and survey observations respectively.
+The three horizontal sections represent perfect, targeted and survey observations respectively.
 So, for example, if a cluster mass is predicted using the $ML_{\sigma, z}$ method and targeted observations to be Log M $=13-13.5$ \Msol, it is biased upward by $0.03\pm0.25$ dex.

### 2016-03-15 ms.tex

@@
 K.~Gebhardt,$^{5}$
+J.~DeRose,$^{2}$
 E.~Rozo,$^{2,4}$
@@
 \noindent
-The study of clusters of galaxies has been argued to be a very effective way to measure cosmological parameters, including measuring dark energy and testing models of gravity.
-The Hobby Eberly Telescope Dark Energy Experiment (HETDEX) will observe many hundreds of square degrees, covering a large sample of galaxy clusters to $z < 0.5$ based on their optical spectra ($3500-5500\AAA$).
-The spectra will provide important measures of the clusters dynamics and may enable constraints on cosmological parameters, but only if the measurements provide accurate estimates of the total cluster masses.
-We carry out a study to investigate the ability of HETDEX to recover accurate galaxy cluster masses over a wide range of masses and redshifts.
-We use a detailed mock galaxy catalog and present mock observations of two different scenarios: (1) We targeted individual galaxy clusters to investigate the recovery of parameters with such observations.
-(2) We created and evaluated a HETDEX-like selection ``function'' of galaxies over a similarly sized portion of the sky and use well adopted techniques to recover the dynamical properties, such as velocity dispersion and mass, and benchmark these against observations with perfect knowledge.
-Using both observing strategies, we produce cluster mass probability density functions $P(M|z, X)$, which can be used to determine the probability that a galaxy cluster of given mass (M), located at redshift ($z$) determined using observable parameter (X).
-\editorial{This sentence will summarize how well HETDEX will do, and how that might be improved with targeted observations.}
+The distribution of massive clusters of galaxies depends strongly on the total cosmic mass density, the mass variance, and the dark energy equation of state.
+As such, measures of galaxy clusters can provide constraints on these parameters and even test models of gravity, but only if observables of clusters can lead to accurate estimates of their total masses.
+Here, we carry out a study to investigate the ability of a blind spectroscopic survey to recover accurate galaxy cluster masses through their velocity dispersion.
+We focus on the Hobby Eberly Telescope Dark Energy Experiment (HETDEX), which will observe many hundreds of square degrees.
+HETDEX will employ the new VIRUS instrument, an integral field unit (IFU), covering the blue/optical portion of the spectrum (3500--5500~\AAA) blindly in two fields for a total of 420 \degsq\ on the sky with fibers with a 1/4.5 fill factor.
+This allows surveys with VIRUS to measure redshifts for a large sample of galaxies out to $z < 0.5$ based on their absorption features or [\ion{O}{ii}] $\lambda$3727 emission (and Lyman-$\alpha$ over $1.9 < z < 3.5$).
+We use a detailed mock galaxy catalog from a semi-analytic model to simulate surveys observed with VIRUS, including: (1) a blind, HETDEX-like survey with an incomplete but uniform spectroscopic selection function; and (2) IFU surveys that target clusters directly, obtaining spectra of all galaxies in a VIRUS-sized field.
+For both surveys, we include realistic uncertainties from galaxy magnitude and line-flux limits.
+We benchmark both surveys against spectroscopic observations with ``perfect" knowledge of galaxy line-of-sight velocities.
+Using both observing strategies, we produce cluster mass probability density functions $P(M_{200}|\vec{x})$ of a cluster mass ($M_{200}$) as a function of an observable parameter or set of observable parameters, $\vec{x}$, where we consider cases of where $\vec{x} = \{\sigma\}$, $=\{\sigma, z\}$, and $=\{\sigma,z, N_{gal}\}$ for velocity dispersion, $\sigma$, redshift, and number of observed galaxies, $N_{gal}$.
+\editorial{This sentence will summarize how well HETDEX will do, and how that might be improved with targeted observations}.
 \end{abstract}
@@
 Connecting the dynamical properties derived from spectroscopy to the properties inferred from other studies insures the greatest impact on future work.
-HETDEX overlaps with the Sloan Digital Sky Survey (SDSS; \citealt{Blanton2001a}), SDSS stripe 82 \citep{Annis2014}, DES, and the upcoming DECam/IRAC Galaxy Environment Survey (DIRGES; PI: Papovich, C.
-Papovich \etal\ in preparation), the \emph{Spitzer}/HETDEX Exploratory Large-Area Survey (SHELA; Papovich \etal\ 2016, ApJS, submitted), and the \emph{Spitzer} IRAC Equatorial Survey (SpIES; Timlin \etal\ 2016, ApJ, submitted).
+HETDEX overlaps with the Sloan Digital Sky Survey (SDSS; \citealt{Blanton2001a}), SDSS stripe 82 \citep{Annis2014}, DES, the \emph{Spitzer}/HETDEX Exploratory Large-Area Survey (SHELA; Papovich \etal\ 2016, ApJS, submitted), and the \emph{Spitzer} IRAC Equatorial Survey (SpIES; Timlin \etal\ 2016, ApJ, submitted).
 While the potential dataset is very rich, two large issues remain.
@@
 
-\subsection{The ``Buzzard'' Catalogs}
+\subsection{The Buzzard Mock Catalogs}
 \begin{figure*} 
@@
 
-The ``Buzzard'' mock galaxy catalogs (R.
+The Buzzard mock galaxy catalogs (R.
 Wechsler et al., private communication) cover 398.49 \degsq\ between $4^h< RA < 6^h$ and $-61\degree < DEC < -41\degree$ and are derived from a combination of Sub-halo Abundance Matching (ShAM) and ADDSEDs (Adding Density Dependent Spectral Energy Distributions) tied to an in house n-body cosmological simulation.
@@
 Dark matter (DM) n-body simulations are run using {\tt LGadget-2} (a version of {\tt Gadget-2}; \citealt{Springel2005}).
-The DM halos are identified using the {\tt ROCKSTAR} halo finder \citep{Behroozi2013} which also calculates halo masses and other various parameters.
+The DM halos are identified using the {\tt ROCKSTAR} halo finder \citep{Behroozi2013} which also calculates halo masses.
 
@@
 
-Tentatively slated to start in the spring of 2016, HETDEX will perform blind spectroscopy (R $\sim$ 750 in $3500 - 5500~\AAA$) over two fields along the celestial equator.
+HETDEX will perform blind spectroscopy (R $\sim$ 750 in $3500 - 5500~\AAA$) over two fields along the celestial equator.
 The 300 \degsq, spring field and 120 \degsq\ fall field will have no preselected targets.
@@
 
-Each mask is created to accurately reproduce the HETDEX IFU pattern, see Figure~\ref{fig: ifu layout}.
+Each mask is created to reproduce the HETDEX IFU pattern, see Figure~\ref{fig: ifu layout}.
 The pattern consists of 78 IFUs, which are comprised of 448 optical fibers subtending a $50'' \times 50''$ region on the sky \citep{Kelz2014}.
@@
 
-The spectral coverage allows for the detection of [\ion{O}{ii}] ($\lambda\lambda 3727,3729~\AAA$ doublet) emitters to $z\sim 0.5$ and Ca H ($\lambda 3968.5~\AAA$) and K ($\lambda 3933.7~\AAA$) absorption features to $z\sim 0.4$.
+The spectral coverage allows for the detection of [\ion{O}{ii}] ($\lambda\lambda 3727,3729$) emitters to $z\sim 0.5$ and Ca H ($\lambda 3968.5$) and K ($\lambda 3933.7$) absorption features to $z\sim 0.4$.
 HETDEX is expected to detect sources with continuum brighter than $\sdssg=22$ mag, and emission line strengths above $3.5\times10^{-17}$ \ergscm.
@@
 The line-of-sight velocity dispersion (LOSVD) is calculated using a method of maximum likelihood following \cite{Walker2006}. We maximize the probability function 
-\begin{equation}
-  \label{eq: jointGaussian}
+\begin{equation}\label{eq: jointGaussian}
 p(\{v_1, ..., v_N\})=\displaystyle\prod_{i=1}^{N}\frac{1}{\sqrt{2\pi(\sigma_i^2+\sigma_p^2)}}\exp\biggl[-\frac{1}{2}\frac{(v_i-\langle u \rangle)^2}{(\sigma_i^2+\sigma_p^2)}\biggr]
@@
 The second is based on a machine learning (ML) algorithm which attempts to ``learn'' the relationship between the observables and the desired output, the mass.
-Both of these methods are examples of supervised learning algorithms where the relationship between the observable parameters and the target parameter (the mass) are both known.
+Both of these methods are examples of supervised learning algorithms where the relationship between the observable parameters and the target parameter (the cluster mass) are both known.
 
@@
 We begin with the training sample.
-After selecting the desired features $\vec{x} = \{\sigma, z, ...\}$ we make the joint probability between the true cluster mass (M) and $\vec{x}$.
-Because $\vec{x}$ can be multidimensional, we rely on the ``corner plot'' as an aid to visualize the relationship between all of the training features.
+After selecting the desired features $\vec{x} = \{\sigma, z, ...\}$ we make the joint probability between the true cluster mass ($M_{200c}$) and $\vec{x}$.
 Figure~\ref{fig: probability corner}, a corner plot, shows all of the one (marginalized probability) and two (joint probability) dimensional projections of the posterior probability distributions of the features of the training data.
@@
 The corner plots shows all of the one and two dimensional posterior probability distributions used to determine the correct cluster mass.
-The colored rectangles, which have been enlarged for clarity, show the slices needed to create a conditional probability distribution of the mass, $P(M|\vec{x})$.
+The colored rectangles, which have been enlarged for clarity, show the slices needed to create a conditional probability distribution of the mass, $P(M_{200c}|\vec{x})$.
 See text for a complete description.
@@
 
-The conditional probability of the mass $P(M|\vec{x}= \{ x_1,x_2,...\})$ is determined by taking a slice through the joint probability distributions in bins centered on the desired value.
+The conditional probability of the mass $P(M_{200c}|\vec{x}= \{ x_1,x_2,...\})$ is determined by taking a slice through the joint probability distributions in bins centered on the desired value.
 The slices show by the colored bars in Figure~\ref{fig: probability corner} are centered on $\sigma = 400$ \kms and $z=0.17$.
-The distribution of mass contained in the three dimensional bin given by the intersection of these slices is $P(M|\vec{x} = \{ \sigma=400 \kms,z=0.17\})$.
+The distribution of mass contained in the three dimensional bin given by the intersection of these slices is $P(M_{200c}|\vec{x} = \{\sigma=400 \kms,z=0.17\})$.
 
@@
 For the clusters making up the \emph{test} sample the mass is unknown (it is what we are trying to predict) but the other features are known.
-To determine the mass probability distribution of a test cluster, $P(M)$, we combine the conditional probability distribution, $P(M|\vec{x})$, created previously with the probability distribution of $\sigma$ through Equation~\ref{eq: Pm}.
+To determine the mass probability distribution of a test cluster, $P(M_{200c})$, we combine the conditional probability distribution, $P(M_{200c}|\vec{x})$, created previously with the probability distribution of $\sigma$ through Equation~\ref{eq: Pm}.
 \begin{equation}\label{eq: Pm}
-	P(M) = \int P(M|\vec{x}) P(\sigma) d\sigma
+	P(M_{200c}) = \int P(M_{200c}|\vec{x}) P(\sigma) d\sigma
 \end{equation}
-The expected mass is determined by integrating the mass probability, $P(M)$ over all mass. This becomes our ``predicted'' mass, $\langle M\rangle$.
+The expected mass is determined by calculating the first moment of the probability density. This becomes our ``predicted'' mass, $M_{pred}$.
 \begin{equation}\label{eq: expected mass}
-	\langle M\rangle = \int M^\prime P(M^\prime)dM^\prime
+	M_{pred}= \int M_{200c} P(M_{200c})dM_{200c}
 \end{equation}
-The confidence interval associated with this prediction can be estimated two ways. First, by calculating the variance about the expected mass through
+The confidence interval associated with this prediction can be estimated two ways. First, by calculating the second moment of the probability density through
 \begin{equation}\label{eq: variance}
-	\mathrm{Var} = \int (M^\prime - \langle M\rangle)^2 P(M^\prime)dM^\prime
+	\mathrm{Var} = \int (M_{200c} - M_{pred})^2 P(M_{200c})dM_{200c}
 \end{equation}
-or by drawing many samples from $P(M)$ and calculating the values at the 16th and 84th percentile.
+or by drawing many samples from $P(M_{200c})$ and calculating the values at the 16th and 84th percentile.
 In practice we find that both methods produce similar results for a large number of trials.
@@
 \editorial{I am going to change this to just the std of the distribution.
-I need the errorbars to be sysmetric to make the fitting routine easy later on.}
+I need the errorbars to be symmetric to make the fitting routine easy later on.}
 
 \section{RESULTS}\label{sec:results}
-Here we explore the cluster member recovery rate and mass estimates for the two observing strategies.
+Here we explore the cluster member recovery rate and mass estimates for the two observing strategies, targeted, and survey.
+Targeted observations are direct observations of a cluster where each cluster member galaxy, above the detection thresholds (see Section \ref{sec: observations}), is observed.
+Survey observations mimic the HETDEX observation strategy such that no cluster is directly observed, and only the cluster member galaxies above the detection threshold and within an IFU (see Figure \ref{fig: ifu layout}) are observed.
 We discuss the accuracy of dynamical mass derived from both the scaling relation (see Equation \ref{eq:power law}) and through the probability and ML methods.
@@
 Knowing these limits will provide important information for potential future follow up or targeted observations.
-In this section we discuss the number of cluster members recovered for both the targeted and survey observation strategies, taking into account all observational limits.
-
 Figure \ref{fig: recovery} shows the recovery fraction of member galaxies, the number of observed galaxies divided by the number of actual galaxies ($N_{obs}/N_{True}$), as function of both redshift and cluster mass.
@@
 \begin{equation}
-\mathrm{\mu_{bias}}(y,\hat{y}) = \frac{1}{N} \sum_{i=0}^N (\hat{y_i} - y_i).\nonumber
+\mathrm{\mu_{bias}}(y,\hat{y}) = \frac{1}{N} \sum_{i=0}^N (\hat{y_i} - y_i).
 \end{equation}
@@
 \begin{equation}
-	\sigma_{bias}(y,\hat{y}, \mu_{bias}) = \bigg{[}\frac{1}{N-1} \sum_{i=0}^N (\hat{y_i} - y_i - \mu_{bias})^2 \bigg{]}^{1/2}\nonumber
+	\sigma_{bias}(y,\hat{y}, \mu_{bias}) = \bigg{[}\frac{1}{N-1} \sum_{i=0}^N (\hat{y_i} - y_i - \mu_{bias})^2 \bigg{]}^{1/2}
 \end{equation}
@@
 
-For the targeted and survey observations the power law predicted cluster masses give $\mu_{bias} =0.13\pm{0.37}$ dex and $\mu_{bias} =0.11\pm{0.36}$ dex, respectively.
+For the targeted and survey observations the power law predicted cluster masses give $\mu_{bias} =0.13\pm{0.003}$ dex and $\mu_{bias} =0.11\pm{0.009}$ dex, respectively.
 So for the clusters that we detect with survey observations, we obtain similar levels of accuracy as to the targeted observations, on the average.
@@
 \caption{Bias and scatter of the true cluster mass for different bins of predicted cluster mass.
-This table shows the offset and scatter in the true cluster mass for the perfect (top section), targeted (middle section), and survey (bottom section) observations in different predicted mass bins.
+This table shows the bias in the true cluster mass for the perfect (top section), targeted (middle section), and survey (bottom section) observations in different predicted mass bins.
 The different mass recovery strategies are given in the leftmost column.
@@
 		\hline 
-		\rottext{4}{Prob Based} & Power Law & $0.49\pm{0.34}$ & $0.28\pm{0.39}$ & $0.23\pm{0.34}$ & $0.16\pm{0.22}$ & $0.11\pm{0.16}$ & $0.07\pm{0.14}$ & $0.02\pm{0.14}$ & $-0.07\pm{0.10}$ \\
-		&$\sigma$ & $0.87\pm{0.15}$ & $0.53\pm{0.24}$ & $0.32\pm{0.26}$ & $0.16\pm{0.20}$ & $0.10\pm{0.16}$ & $0.07\pm{0.14}$ & $0.05\pm{0.16}$ & $-0.18\pm{0.17}$ \\
-		&$\sigma, z$ & $0.76\pm{0.16}$ & $0.42\pm{0.21}$ & $0.17\pm{0.23}$ & $0.01\pm{0.19}$ & $-0.06\pm{0.16}$ & $-0.11\pm{0.55}$ & $-0.14\pm{0.16}$ & $-0.38\pm{0.34}$ \\
-		&$\sigma, z, N_{gal}$ & $0.65\pm{0.10}$ & $0.28\pm{0.14}$ & $0.04\pm{0.47}$ & $-0.02\pm{0.14}$ & $-0.02\pm{0.10}$ & $-0.05\pm{0.54}$ & $-0.22\pm{1.61}$ & $-6.62\pm{8.08}$ \\
+		\rottext{4}{Prob Based} & Power Law & $0.49\pm{0.09}$ & $0.28\pm{0.02}$ & $0.23\pm{0.01}$ & $0.16\pm{0.00}$ & $0.11\pm{0.00}$ & $0.07\pm{0.00}$ & $0.02\pm{0.01}$ & $-0.07\pm{0.04}$ \\
+		&$\sigma$ & $0.87\pm{0.04}$ & $0.53\pm{0.01}$ & $0.32\pm{0.01}$ & $0.16\pm{0.00}$ & $0.10\pm{0.00}$ & $0.07\pm{0.00}$ & $0.05\pm{0.01}$ & $-0.18\pm{0.06}$ \\
+		&$\sigma, z$ & $0.76\pm{0.04}$ & $0.42\pm{0.01}$ & $0.17\pm{0.00}$ & $0.01\pm{0.00}$ & $-0.06\pm{0.00}$ & $-0.11\pm{0.01}$ & $-0.14\pm{0.01}$ & $-0.38\pm{0.13}$ \\
+		&$\sigma, z, N_{gal}$ & $0.65\pm{0.03}$ & $0.28\pm{0.01}$ & $0.04\pm{0.01}$ & $-0.02\pm{0.00}$ & $-0.02\pm{0.00}$ & $-0.05\pm{0.01}$ & $-0.22\pm{0.12}$ & $-6.62\pm{3.06}$ \\
 		\hline
-		\rottext{4}{ML Based} & Power Law & $0.49\pm{0.34}$ & $0.28\pm{0.39}$ & $0.23\pm{0.34}$ & $0.16\pm{0.22}$ & $0.11\pm{0.16}$ & $0.07\pm{0.14}$ & $0.02\pm{0.14}$ & $-0.07\pm{0.10}$ \\
-		&$\sigma$ & $0.69\pm{0.20}$ & $0.36\pm{0.27}$ & $0.15\pm{0.29}$ & $-0.02\pm{0.24}$ & $-0.07\pm{0.21}$ & $-0.09\pm{0.19}$ & $-0.11\pm{0.18}$ & $-0.12\pm{0.19}$ \\
-		&$\sigma, z$ & $0.62\pm{0.18}$ & $0.33\pm{0.22}$ & $0.12\pm{0.25}$ & $-0.01\pm{0.20}$ & $-0.06\pm{0.18}$ & $-0.09\pm{0.16}$ & $-0.11\pm{0.17}$ & $-0.19\pm{0.13}$ \\
-		&$\sigma, z, N_{gal}$ & $0.51\pm{0.14}$ & $0.23\pm{0.18}$ & $0.05\pm{0.17}$ & $-0.02\pm{0.14}$ & $-0.02\pm{0.10}$ & $-0.02\pm{0.08}$ & $-0.02\pm{0.08}$ & $-0.08\pm{0.08}$ \\
+		\rottext{4}{ML Based} & Power Law & $0.49\pm{0.09}$ & $0.28\pm{0.02}$ & $0.23\pm{0.01}$ & $0.16\pm{0.00}$ & $0.11\pm{0.00}$ & $0.07\pm{0.00}$ & $0.02\pm{0.01}$ & $-0.07\pm{0.04}$ \\
+		&$\sigma$ & $0.69\pm{0.05}$ & $0.36\pm{0.01}$ & $0.15\pm{0.01}$ & $-0.02\pm{0.00}$ & $-0.07\pm{0.00}$ & $-0.09\pm{0.01}$ & $-0.11\pm{0.01}$ & $-0.12\pm{0.07}$ \\
+		&$\sigma, z$ & $0.62\pm{0.05}$ & $0.33\pm{0.01}$ & $0.12\pm{0.00}$ & $-0.01\pm{0.00}$ & $-0.06\pm{0.00}$ & $-0.09\pm{0.00}$ & $-0.11\pm{0.01}$ & $-0.19\pm{0.05}$ \\
+		&$\sigma, z, N_{gal}$ & $0.51\pm{0.04}$ & $0.23\pm{0.01}$ & $0.05\pm{0.00}$ & $-0.02\pm{0.00}$ & $-0.02\pm{0.00}$ & $-0.02\pm{0.00}$ & $-0.02\pm{0.01}$ & $-0.08\pm{0.03}$ \\
 		\hline 
 		\hline
-		\rottext{4}{Prob Based} & Power Law & $0.49\pm{0.31}$ & $0.27\pm{0.41}$ & $0.20\pm{0.43}$ & $0.13\pm{0.39}$ & $0.10\pm{0.33}$ & $0.09\pm{0.27}$ & $0.02\pm{0.18}$ & $-0.08\pm{0.09}$ \\
-		&$\sigma$ & $1.02\pm{0.13}$ & $0.66\pm{0.19}$ & $0.40\pm{0.24}$ & $0.17\pm{0.25}$ & $0.02\pm{0.25}$ & $-0.08\pm{0.22}$ & $-0.19\pm{0.19}$ & $-0.35\pm{0.26}$ \\
-		&$\sigma, z$ & $0.85\pm{0.18}$ & $0.49\pm{0.20}$ & $0.25\pm{0.24}$ & $0.08\pm{0.24}$ & $-0.06\pm{0.23}$ & $-0.21\pm{0.56}$ & $-0.35\pm{0.21}$ & $-0.59\pm{0.31}$ \\
-		&$\sigma, z, N_{gal}$ & $0.70\pm{0.13}$ & $0.37\pm{0.18}$ & $0.13\pm{0.20}$ & $0.01\pm{0.19}$ & $-0.05\pm{0.17}$ & $-0.12\pm{0.67}$ & $-0.44\pm{2.26}$ & $-4.45\pm{7.44}$ \\
+		\rottext{4}{Prob Based} & Power Law & $0.49\pm{0.08}$ & $0.27\pm{0.02}$ & $0.20\pm{0.01}$ & $0.13\pm{0.01}$ & $0.10\pm{0.01}$ & $0.09\pm{0.01}$ & $0.02\pm{0.01}$ & $-0.08\pm{0.03}$ \\
+		&$\sigma$ & $1.02\pm{0.03}$ & $0.66\pm{0.01}$ & $0.40\pm{0.00}$ & $0.17\pm{0.00}$ & $0.02\pm{0.00}$ & $-0.08\pm{0.01}$ & $-0.19\pm{0.01}$ & $-0.35\pm{0.10}$ \\
+		&$\sigma, z$ & $0.85\pm{0.05}$ & $0.49\pm{0.01}$ & $0.25\pm{0.00}$ & $0.08\pm{0.00}$ & $-0.06\pm{0.00}$ & $-0.21\pm{0.02}$ & $-0.35\pm{0.02}$ & $-0.59\pm{0.12}$ \\
+		&$\sigma, z, N_{gal}$ & $0.70\pm{0.03}$ & $0.37\pm{0.01}$ & $0.13\pm{0.00}$ & $0.01\pm{0.00}$ & $-0.05\pm{0.00}$ & $-0.12\pm{0.02}$ & $-0.44\pm{0.18}$ & $-4.45\pm{2.81}$ \\
 		\hline
-		\rottext{4}{ML Based} & Power Law & $0.49\pm{0.31}$ & $0.27\pm{0.41}$ & $0.20\pm{0.43}$ & $0.13\pm{0.39}$ & $0.10\pm{0.33}$ & $0.09\pm{0.27}$ & $0.02\pm{0.18}$ & $-0.08\pm{0.09}$ \\
-		&$\sigma$ & $0.76\pm{0.28}$ & $0.54\pm{0.29}$ & $0.26\pm{0.31}$ & $0.01\pm{0.31}$ & $-0.13\pm{0.32}$ & $-0.23\pm{0.30}$ & $-0.33\pm{0.29}$ & $-0.32\pm{0.09}$ \\
-		&$\sigma, z$ & $0.66\pm{0.13}$ & $0.37\pm{0.23}$ & $0.17\pm{0.26}$ & $0.03\pm{0.25}$ & $-0.09\pm{0.24}$ & $-0.21\pm{0.22}$ & $-0.31\pm{0.25}$ & $-0.28\pm{0.13}$ \\
-		&$\sigma, z, N_{gal}$ & $0.57\pm{0.12}$ & $0.28\pm{0.21}$ & $0.09\pm{0.21}$ & $-0.01\pm{0.18}$ & $-0.05\pm{0.16}$ & $-0.08\pm{0.14}$ & $-0.07\pm{0.12}$ & $-0.14\pm{0.13}$ \\
+		\rottext{4}{ML Based} & Power Law & $0.49\pm{0.08}$ & $0.27\pm{0.02}$ & $0.20\pm{0.01}$ & $0.13\pm{0.01}$ & $0.10\pm{0.01}$ & $0.09\pm{0.01}$ & $0.02\pm{0.01}$ & $-0.08\pm{0.03}$ \\
+		&$\sigma$ & $0.76\pm{0.07}$ & $0.54\pm{0.01}$ & $0.26\pm{0.01}$ & $0.01\pm{0.00}$ & $-0.13\pm{0.00}$ & $-0.23\pm{0.01}$ & $-0.33\pm{0.02}$ & $-0.32\pm{0.03}$ \\
+		&$\sigma, z$ & $0.66\pm{0.03}$ & $0.37\pm{0.01}$ & $0.17\pm{0.01}$ & $0.03\pm{0.00}$ & $-0.09\pm{0.00}$ & $-0.21\pm{0.01}$ & $-0.31\pm{0.02}$ & $-0.28\pm{0.05}$ \\
+		&$\sigma, z, N_{gal}$ & $0.57\pm{0.03}$ & $0.28\pm{0.01}$ & $0.09\pm{0.00}$ & $-0.01\pm{0.00}$ & $-0.05\pm{0.00}$ & $-0.08\pm{0.00}$ & $-0.07\pm{0.01}$ & $-0.14\pm{0.05}$ \\
 		\hline
 		\hline
-		\rottext{4}{Prob Based} & Power Law & \nd & \nd & $0.53\pm{0.15}$ & $0.30\pm{0.29}$ & $0.16\pm{0.33}$ & $0.07\pm{0.31}$ & $0.01\pm{0.24}$ & $-0.09\pm{0.13}$ \\
-		&$\sigma$ & \nd & \nd & $0.77\pm{0.10}$ & $0.42\pm{0.18}$ & $0.18\pm{0.22}$ & $-0.03\pm{0.22}$ & $-0.18\pm{0.19}$ & $-0.39\pm{0.22}$ \\
-		&$\sigma, z$ & \nd & \nd & $0.61\pm{0.12}$ & $0.29\pm{0.19}$ & $0.08\pm{0.22}$ & $-0.11\pm{0.21}$ & $-0.38\pm{1.30}$ & $-0.48\pm{0.27}$ \\
-		&$\sigma, z, N_{gal}$ & \nd & \nd & $0.48\pm{0.13}$ & $0.18\pm{0.18}$ & $0.02\pm{0.19}$ & $-0.08\pm{0.19}$ & $-0.50\pm{2.25}$ & $-8.81\pm{7.98}$ \\
+		\rottext{4}{Prob Based} & Power Law & \nd & \nd & $0.53\pm{0.04}$ & $0.30\pm{0.02}$ & $0.16\pm{0.01}$ & $0.07\pm{0.01}$ & $0.01\pm{0.02}$ & $-0.09\pm{0.05}$ \\
+		&$\sigma$ & \nd & \nd & $0.77\pm{0.03}$ & $0.42\pm{0.01}$ & $0.18\pm{0.01}$ & $-0.03\pm{0.01}$ & $-0.18\pm{0.02}$ & $-0.39\pm{0.08}$ \\
+		&$\sigma, z$ & \nd & \nd & $0.61\pm{0.03}$ & $0.29\pm{0.01}$ & $0.08\pm{0.01}$ & $-0.11\pm{0.01}$ & $-0.38\pm{0.12}$ & $-0.48\pm{0.10}$ \\
+		&$\sigma, z, N_{gal}$ & \nd & \nd & $0.48\pm{0.04}$ & $0.18\pm{0.01}$ & $0.02\pm{0.01}$ & $-0.08\pm{0.01}$ & $-0.50\pm{0.20}$ & $-8.81\pm{3.02}$ \\
 		\hline
-		\rottext{4}{ML Based} & Power Law & \nd & $0.06\pm{0.80}$ & $0.17\pm{0.39}$ & $0.17\pm{0.41}$ & $0.13\pm{0.38}$ & $0.07\pm{0.32}$ & $0.01\pm{0.24}$ & $-0.09\pm{0.13}$ \\
-		&$\sigma$ & \nd & $0.58\pm{0.17}$ & $0.54\pm{0.26}$ & $0.24\pm{0.28}$ & $0.03\pm{0.30}$ & $-0.17\pm{0.30}$ & $-0.26\pm{0.30}$ & $-0.30\pm{0.25}$ \\
-		&$\sigma, z$ & \nd & $1.02\pm{0.35}$ & $0.42\pm{0.21}$ & $0.19\pm{0.25}$ & $0.03\pm{0.25}$ & $-0.14\pm{0.25}$ & $-0.25\pm{0.24}$ & $-0.31\pm{0.26}$ \\
-		&$\sigma, z, N_{gal}$ & \nd & $0.91\pm{0.45}$ & $0.39\pm{0.19}$ & $0.12\pm{0.21}$ & $-0.00\pm{0.20}$ & $-0.08\pm{0.19}$ & $-0.14\pm{0.19}$ & $-0.21\pm{0.20}$ \\
+		\rottext{4}{ML Based} & Power Law & \nd & $0.06\pm{0.46}$ & $0.17\pm{0.07}$ & $0.17\pm{0.02}$ & $0.13\pm{0.01}$ & $0.07\pm{0.01}$ & $0.01\pm{0.02}$ & $-0.09\pm{0.05}$ \\
+		&$\sigma$ & \nd & $0.58\pm{0.10}$ & $0.54\pm{0.04}$ & $0.24\pm{0.02}$ & $0.03\pm{0.01}$ & $-0.17\pm{0.01}$ & $-0.26\pm{0.03}$ & $-0.30\pm{0.10}$ \\
+		&$\sigma, z$ & \nd & $1.02\pm{0.20}$ & $0.42\pm{0.04}$ & $0.19\pm{0.01}$ & $0.03\pm{0.01}$ & $-0.14\pm{0.01}$ & $-0.25\pm{0.02}$ & $-0.31\pm{0.10}$ \\
+		&$\sigma, z, N_{gal}$ & \nd & $0.91\pm{0.26}$ & $0.39\pm{0.03}$ & $0.12\pm{0.01}$ & $-0.00\pm{0.01}$ & $-0.08\pm{0.01}$ & $-0.14\pm{0.02}$ & $-0.21\pm{0.08}$ \\
 	\hline
@@
 The three horizontal sections represent perfect, targeted and survey observations respectively.
-So, for example, if a cluster mass is predicted using the $ML_{\sigma, z}$ method and targeted observations to be Log M $=13-13.5$ \Msol, it is biased upward by $0.03\pm0.25$ dex.
+So, for example, if a cluster mass is predicted using the $ML_{\sigma, z}$ method and targeted observations to be Log M $=13-13.5$ \Msol, it is biased upward by $0.03\pm{0.00}$ dex.
 
@@
 \section{HETDEX as a Galaxy Cluster Survey at $z < 0.5$}\label{sec:discussion}
+
+\subsection{Impact on Cluster Cosmology}
+\editorial{This is a place holder section.
+One of the things missing to bring this work full circle is a discussion about how the uncertainties in cluster masses impact the derived cosmological parameters.
+I am currently doing a literature review looking for references that discuss how the mass errors impact the derived parameters.
+Here we want to be able to say ``so and so show that errors on clusters masses need to be better than blah to recover $\sigma_8$ and $\Omega_m$ to better than blah, which is useful for blah.
+We show that with XXXX kind of data spectroscopic surveys like HETDEX can achieve this but only with YYYY kind of data quality.'' If it isn't going to do that well, then how much constraint could HETDEX/HETDEX-like surveys put on cosmological parameters?
+How good would they have to get to test gravity?
+(or the dark energy equation of state)}
 
@@
 \begin{equation}
-	\mathrm{ln}L= \frac{-1}{2} \bigg{(} \sum^N_{i=1}\frac{[y_i - mx_i - b]^2}{\sigma_{yi}} + \sum^N_{i=1}\frac{[y_i - mx_i - b]^2}{\sigma_{xi}} \bigg{)}
+	\mathrm{ln}L= \frac{-1}{2} \bigg{(} \sum^N_{i=1}\frac{[y_i - mx_i - b]^2}{\sigma_{y,i}} + \sum^N_{i=1}\frac{[y_i - mx_i - b]^2}{\sigma_{x,i}} \bigg{)}
 \end{equation} 
@@
 The SDSS is managed by the Astrophysical Research Consortium for the Participating Institutions.
-\editorial{People to thank: Joe, maybe authorship.}
 

### 2016-03-24 ms.tex
update with collaborators comments

@@
 The Hobby Eberly Telescope Dark Energy eXperiment (HETDEX; \citealt{Hill2008}) is a trailblazing effort to observe high-redshift large scale structures using cutting edge wide-field integral field unit (IFU) spectrographs.
-Designed to probe the evolution of the dark energy equation of state etched onto high redshift ($z>2$) galaxies by the Baryon Acoustic Oscillations \citep{Eisenstein2005} in the first moments of the universe, the survey will observe two fields for a total of 420 \degsq\ (300 \degsq, Spring field and 120 \degsq, Fall field).
+Designed to probe the evolution of the dark energy equation of state etched onto high redshift ($z>2$) galaxies by the Baryon Acoustic Oscillations (BAO) \citep{Eisenstein2005} in the first moments of the universe, the survey will observe two fields for a total of 420 \degsq\ (300 \degsq, Spring field and 120 \degsq, Fall field).
 Tuned to find \lya\ emitting (LAE) galaxies at $1.9<z<3.5$, HETDEX expects to find 800,000 LAEs, and more than one million [\ion{O}{ii}] emitting galaxies at $z<0.5$ masquerading as high-redshift galaxies \citep{Acquaviva2014}.
@@
 Connecting the dynamical properties derived from spectroscopy to the properties inferred from other studies insures the greatest impact on future work.
-HETDEX overlaps with the Sloan Digital Sky Survey (SDSS; \citealt{Blanton2001a}), SDSS stripe 82 \citep{Annis2014}, DES, the \emph{Spitzer}/HETDEX Exploratory Large-Area Survey (SHELA; Papovich \etal\ 2016, ApJS, submitted), and the \emph{Spitzer} IRAC Equatorial Survey (SpIES; Timlin \etal\ 2016, ApJ, submitted).
+HETDEX overlaps with the Sloan Digital Sky Survey (SDSS; \citealt{Blanton2001a}), SDSS stripe 82 \citep{Annis2014}, DES, the \emph{Spitzer}/HETDEX Exploratory Large-Area Survey (SHELA; \citealt{Papovich2016}), and the \emph{Spitzer} IRAC Equatorial Survey (SpIES; Timlin \etal\ 2016, ApJ, submitted).
 While the potential dataset is very rich, two large issues remain.
@@
 
-Throughout this paper, we adopt the following cosmological model: $\Omega_\Lambda = 0.714$,
-$\Omega_M = 0.286$, $\sigma_8 = 0.82$ and $H_0= 70$ \kms \mpc (taken from the Buzzard catalogs; see below), assume a Chabrier initial mass function (IMF; \citealt{Chabrier2003}), and use AB magnitudes \citep{Oke1974}.
+Throughout this paper, we adopt the following cosmological model: $\Omega_\Lambda = 0.714$, $\Omega_M = 0.286$, $\sigma_8 = 0.82$ and $H_0= 70$ \kms \mpc (taken from the Buzzard catalogs; see below), assume a Chabrier initial mass function (IMF; \citealt{Chabrier2003}), and use AB magnitudes \citep{Oke1974}.
 
@@
 The cluster masses predicted by Equation \ref{eq:power law} gives the following results.
-Across all cluster masses, we find $\mu_{bias} = 0.15\pm{0.24}$ dex.
+Across all cluster masses, we find $\mu_{bias} = 0.15\pm{0.002}$ dex.
 The scatter in recovered masses can be attributed to both physical and numerical effects.
@@
  A few caveats apply to the numbers given in Table \ref{tbl:mass bias}.
-While we provide corrections for cluster masses above $10^{15}$, they are estimated from only a handful of objects, and do not constitute a representative sample of clusters.
+While we provide corrections for cluster masses above $10^{15}$ \msol, they are estimated from only a handful of objects, and do not constitute a representative sample of clusters.
 On the oposite end of the cluster mass spectrum, survey observations of low mass clusters are incomplete for two potential reasons.
-There are very few, if any, clusters detected with survey observations below $10^{12}$.
-Missing corrections above $10^{12}$ in the probability based methods are due to low number statstics and an inability to sample the cluster mass PDF well enough to assign cluster mass predictions.
+There are very few, if any, clusters detected with survey observations below $10^{12}$ \msol.
+Missing corrections above $10^{12}$ \msol\ in the probability based methods are due to low number statstics and an inability to sample the cluster mass PDF well enough to assign cluster mass predictions.
+
+\subsubsection{Significance of Cosmology Choice}
+The underlying simulation used to produce the Buzzard catalogs, as with every simulation, makes specific assumptions about the cosmology used and how the galaxies are populated into the dark matter halos.
+When using simulation data to train ML methods, we incorporate all of those assumptions into the learned feature associations.
+This could lead to a notable bias when applying the ML method to data (real or simulated) which has significantly different cosmological assumptions.
+
+To investigate this, we select cluster halo and galaxy catalogs from the Millennium simulation \citep{Springel2005b} obtained via querying the Millennium online database\footnote{http://gavo.mpa-garching.mpg.de/Millennium/} \citep{Lemson2006}.
+The Millennium simulation tracks $2160^3$ dark matter particles of $8.6\times 10^8 ~h^{-1}$ \Msol\ inside a comoving 500 $(h^{-1} \mathrm{Mpc})^3$ box from $z=127$ to 0.
+It adopts a flat cosmological model based of the values derived from the Two-degree Field Galaxy Redshift Survey \citep{Colless2001} and the first year data of the \emph{Wilkinson Microwave Anisotropy Probe} (WMAP; \citealt{Spergel2003}): $\Omega_\Lambda = 0.75$, $\Omega_M = 0.25$, $\sigma_8 = 0.9$, $n_s = 1$ and $H_0= 73$ \kms \mpc.
+
+The halo catalogs are created using a friends-of-friends algorithm \citeeg{Turner1976} with linking length, $b=0.2$.
+The halos are populated with galaxies using a semi-analytical model described in \cite{Croton2006, DeLucia2006, DeLucia2007a}.
+
+We select 4806 clusters, comprised of 623663 galaxies, at $0.02 < z < 0.5$ and $M > 10^{13}$ \Msol, and apply the same data processing as with the Buzzard galaxies.
+We begin by assigning each galaxy an [\ion{O}{ii}] flux value (see Section \ref{sec: oii luminosity}), and ``observe'' each galaxy using realistic (see Section \ref{sec: observations}) observational limits.
+After recovering 3750 clusters which have at least five galaxies observed, we calculate the LOSVD of each cluster as in Section \ref{sec: LOSVD}.
+
+Cluster masses are assigned using the ML methods (see Section \ref{sec:machine learning method}) using two different training sets.
+We use the full set of clusters detected in the Buzzard catalogs (14000 clusters with $M > 10^{11}$ \msol) and a training-testing split of the Millennium clusters.
+
+\begin{figure} 
+	\includegraphics[width=\columnwidth]{figures/millBuzzComparison.pdf} 
+	\caption{Mass predictions for the power law scaling relation (Equation~\ref{eq:power law}) and the ML based technique with different input features as a function of true cluster mass.
+The bottom row of panels shows the fractional error (Equation~\ref{eq: fractional error}) also as a function of true cluster mass.
+The solid black line shows the 1:1 relation.
+The solid, colored line is the median predicted mass for the targeted observing, and the colored, dashed line is the median recovered mass for the HETDEX-like observations.
+The shaded regions represent the 68\% scatter around the median values.} \label{fig: mill buzz comparison}
+\end{figure}
+
+The predicted cluster masses for the 4000 millennium cluster are very similar regardless of the training set used.
+I've attached a plot that shows the probability of the predicted masses using the two different training sets.
+I also computed the mean squared error (MSE) of each set, compared to the *true* cluster mass.
+I like the MSE because it takes into account both the scatter and the bias.
+For the millennium clusters I found MSE $= 0.015$, and for the Buzzard clusters MSE $= 0.029$.
+Smaller numbers are better, and I think the difference is because I have chosen not to exclude clusters with $Msol < 1e13$ from the Buzzard catalogs when training.
+That allows the ML method to assign clusters below that which ups the MSE.
+
+I'm hoping that Millennium is different enough from Buzzard that this will address your concern.
+Another option would be just to include training samples from a few different mocks.
+Or, we could derive masses using different training sets and then marginalize over them to get a final predicted mass.
 
@@
 \subsection{Impact on Cluster Cosmology}
-\editorial{This is a place holder section.
+% \editorial{This is a place holder section.
 One of the things missing to bring this work full circle is a discussion about how the uncertainties in cluster masses impact the derived cosmological parameters.
@@
 (or the dark energy equation of state)}
+
+Galaxy clusters are sensitive probes of $\Omega_m$, the total mass ($\Omega_b + \Omega_c$) density in the universe, through tracing the peaks in the universal matter density often referred to as the power spectrum of matter density fluctuations or the matter power spectrum and $\sigma_8h^{-1}$, the normalization of the power spectrum, by the comparison of the number density of observed halos to that predicted in cosmological models.
+Although, in reality, one measures $\sigma_8h^{-1}\Omega_m^q$, where the value of $q$ depends on the masses and redshifts of the halos considered.
+
+To get a sense of how well HETDEX will be able to constrain cosmological parameters we follow the discussion of \cite{Weinberg2013}, and begin with a few simplifying assumptions.
+While sensitive to $\Omega_m$, the number density of clusters do not necessarily provide the strongest contraint, so we assume that some combination of other data sets (\eg, CMB, BAO, supernovae, WL, etc.) will constrain $\Omega_m$ to high precision.
+
+To estimate the error associated with a measurement of $\sigma_8h^{-1}$ (which \citealt{Weinberg2013} refer to as $\sigma_{11,abs}$), \cite{Weinberg2013} consider two sources of uncertainty, the systematic uncertainties in cluster mass calibration and the statistical uncertainty in the observed number density of clusters.
+The authors combine these two uncertainties though (their Eq.
+141):
+\begin{equation}
+	\Delta~\mathrm{ln}~\sigma_{11,abs}(z) = q \times \mathrm{max}[\Delta~\mathrm{ln}~M,\alpha^{-1}\Delta\mathrm{ln}~N]
+\end{equation}
+where $q$ is the degeneracy exponent between $\sigma_8h^{-1}$ and $\Omega_m$, $\Delta\mathrm{ln}M$ is the mass scale uncertainty, $\Delta\mathrm{ln}N$ is the cluster statistical uncertainty, and $\alpha$ is slope of the cumulative HMF.
+Using the \cite{Tinker2008} HMF \cite{Weinberg2013} estimate $q\sim0.4$, and find that for any cluster survey with more than 10-20 clusters is dominated by the uncertainty in the overall mass scale.
+
+For a survey such as HETDEX, with a power law derived overall cluster mass biases of $>0.15$ dex (about 41\%) the uncertainty on $\sigma_8h^{-1}$ is $0.4 \times 0.41 \approx 16\%$.
+If we consider only clusters with masses above $10^{14}$ \Msol, with perfect knowledge, and the ML based cluster mass estimates the mass scale uncertainty is reduced to $\sim -0.02$ dex or about 5\%.
+This gives a uncertainty on $\sigma_8h^{-1}$ of 2\%.
+For clusters above $10^{14}$ \Msol, survey observations can constrain the masses to about 20\% which, in turn, constrains $\sigma_8h^{-1}$ to 8\%.
+
+Because of the simplifying assumptions, and the superior quality of the data (no contamination, signal-to-noise issues, etc.), realistic expectations for HETDEX is to directly constrain $\sigma_8h^{-1}$ to better precision than other methods (\eg, CMB, WL, X-ray) seems bleak.
+For the $\sim1500$ clusters detected with survey observations to constrain $\sigma_8h^{-1}$ and to be dominated by cluster statistics alone ($\Delta\mathrm{ln}N \sim N^{-1/2}$), the absolute cluster calibration would need to be better than 2.5\%.
+For a fully targeted survey, about 14000 clusters, this cluster mass calibration uncertainty reduces to $>1\%$.
+\editorial{Here I want to say a word or two about how all hope isn't lost.
+We can still use HETDEX to reduce the scatter on the richness-mass relationship which can help other estimators get down to the levels we need to really nail down these numbers.}
 

### 2016-04-11 ms.tex
continue updating

@@
 %%%%%%%%%%%%%%%%%%% TITLE PAGE %%%%%%%%%%%%%%%%%%%
-\title[Short Title]{Cluster Dynamics with HETDEX at z < 0.5 - I: Simulated Performance, Mass Distribution and Limits}
+\title[Galaxy Clusters with HETDEX]{Cluster Dynamics with HETDEX at z < 0.5 - I: Simulated Performance, Mass Recovery, and Limits to Cosmology}
 
@@
 \section{INTRODUCTION}
-\editorial{The introduction is now much longer because I talked about the cons to the different cluster mass recovery methods.
-I don't much care for really long introductions, so if there is anything that could by cut to shorten it, I would be ok.}
 Our ability to perform precision cosmology with clusters of galaxies has reached a critical turning point.
@@
 However, the primary challenge to this method is the incomplete understanding of the baryonic physics which take place in galaxy cluster environments.
-While there have been (and continue to be) many improvements in the accuracy and power of simulations it is doubtful that in the coming years they will reach the accuracy level required to the point where the observable--mass relation is dominated only by statistics \citep{Weinberg2013}.
+While there have been (and continue to be) many improvements in the accuracy and power of simulations it is doubtful that in the coming years they will reach the accuracy level required where the observable--mass relation is dominated only by statistics \citep{Weinberg2013}.
 
@@
 The statistical method of determining galaxy cluster mass relies not on direct measurements of individual clusters but the calibration of observables for the entire sample which correlate with cluster mass.
-One example is the spatial clustering of the galaxy clusters themselves.
+One example is the spatial clustering of the galaxy clusters themselves \citeeg{Baxter2016}.
 See \cite{Weinberg2013} for a comprehensive review.
@@
 
-While a large portion of the $\sim10^6$ interloping [\ion{O}{ii}] galaxies will be field (not associated with a bound structure) galaxies, the large area covered by HETDEX is expected to contain as many as 50 Virgo-sized ($M_{dyn}>10^{15}$ \msol) clusters at $z<0.5$ (\editorial{talk to casey about how I calculated this number}).
+While a large portion of the $\sim10^6$ interloping [\ion{O}{ii}] galaxies will be field (not associated with a bound structure) galaxies, the large area covered by HETDEX is expected to contain as many as 50 Virgo-sized ($M_{dyn}>10^{15}$ \msol) clusters at $z<0.5$.
 The near-complete spectroscopic coverage allows an unprecedentedly detailed look at a very large number of clusters ranging from group scales to the very massive.
@@
 A $M_r$-density-SED relation is created using a SDSS training set, and for each mock galaxy the SED of a randomly selected training set galaxy which has a similar $M_r$ and density is assigned.
-The result is a 398.49 \degsq\ mock catalog containing 238 million galaxies with $\sdssr < 29$ mag and $z \leq 8.7$.
+The result is a mock catalog containing 238 million galaxies with $\sdssr < 29$ mag and $z \leq 8.7$.
 
 The catalog information, used in this study, is broken into two large portions.
-The ``truth'' files contain the characteristics of each individual galaxies, such as right ascension (RA), declination (DEC), redshift ($z$), observed and rest-frame magnitudes, and many others.
+The ``truth'' files contain the characteristics of each individual galaxy, such as right ascension (RA), declination (DEC), redshift ($z$), observed and rest-frame magnitudes, and many others.
 The ``halo'' files contain information for individual halos, to which many individual galaxies may belong.
@@
 We investigate the accuracy of the halo mass distribution by comparing the cumulative number density of halos above a mass ($M_{200c}$) threshold to the halo mass function (HMF) of \cite{Tinker2008}.
-We calculate the HMF at central redshifts of 0.1, 0.2, and 0.4 using {\tt HMFcalc} \citep{Murray2013} and compared to galaxies in a redshift window of $\Delta z\pm0.01$.
+We calculate the HMF at central redshifts of 0.1, 0.2, and 0.4 using {\tt HMFcalc} \citep{Murray2013} and compare it galaxies in a redshift window of $\Delta z\pm0.01$.
 We find a very good agreement between the predicted HMF and the observed distribution of clusters.
@@
 
-To assign an [\ion{O}{ii}] luminosity to each galaxy in our catalog we place the catalog galaxies on the same CMD and select all SDSS galaxies in a small 2D ($M_r$, $g-r$) bin around the galaxy.
+To assign an [\ion{O}{ii}] luminosity to each galaxy in our catalog, we place the catalog galaxies on the same CMD and select all SDSS galaxies in a small 2D ($M_r$, $g-r$) bin around the galaxy.
 We extract all of the SDSS galaxies inside that bin and create a histogram of their [\ion{O}{ii}] luminosities, the right panel of Figure \ref{fig: oii sdss}.
@@
 In this work we consider two separate observing strategies, targeted and survey-like.
-The targeted observations use ``direct'' observations where each cluster is targeted individual, and every cluster member galaxy is assumed to be observed.
+The targeted observations use ``direct'' observations where each cluster is targeted individually, and every cluster member galaxy is assumed to be observed.
 The survey observations mimic the HETDEX observation pattern across the sky, where no cluster is directly targeted and not all cluster member galaxies are observed.
 Both of these observations have HETDEX-like galaxy detection thresholds, for comparison we also include a set of targeted observations with ``perfect'' knowledge.
-``Perfect'' observations assume no detection threshold, if a cluster member galaxy is observed, it is also detected.
+Perfect observations assume no detection threshold, if a cluster member galaxy is observed, it is also detected.
 This provides an important best-case scenario, and differs from the true cluster properties because the recovered cluster properties are still calculated.
@@
 The following is, in many cases, a subset of the available methods to derive any single parameter.
-The specific choice of method may improve or diminish the accuracy of the recovered parameter, but the methods chosen were to facilitate comparison with observational studies.
+The specific choice of method may improve or diminish the accuracy of the recovered parameter, but the methods chosen were to facilitate comparison with other observational studies.
 
@@
 We draw twenty thousand samples from the posterior probability distribution using simple priors, $\langle\mu\rangle$ lies between the maximum and minimum LOSV and $0< \sigma_p < 1400$ \kms.
-When the full distribution of LOSVDs are not used, the final LOSVD is quoted as the median value of the posterior probability distribution with 68\% error bars defined as the 16th and 84th percentiles of the same distribution.
+When the full distribution of LOSVDs is not used, the final LOSVD is quoted as the median value of the posterior probability distribution with 68\% error bars defined as the 16th and 84th percentiles of the same distribution.
 
@@
 The 68\% error bars derived from the MCMC method give slightly better results with the true LOSVD value bracketed by the error bars in $\sim68\%$ of the cases versus $\sim57\%$ with bootstrapping and a single statistic.
-In addition, we prefer the maximum likelihood method for its straight forward treatment of the errors in the LOSV measurements, which will become important in future observations of real clusters.
+In addition, we prefer the maximum likelihood method for its straight forward treatment of the errors in the LOSV measurements, which will become important in future observations of real clusters \citeeg{Boada2016a}.
 
@@
 The conditional probability of the mass $P(M_{200c}|\vec{x}= \{ x_1,x_2,...\})$ is determined by taking a slice through the joint probability distributions in bins centered on the desired value.
-The slices show by the colored bars in Figure~\ref{fig: probability corner} are centered on $\sigma = 400$ \kms and $z=0.17$.
+The slices shown by the colored bars in Figure~\ref{fig: probability corner} are centered on $\sigma = 400$ \kms and $z=0.17$.
 The distribution of mass contained in the three dimensional bin given by the intersection of these slices is $P(M_{200c}|\vec{x} = \{\sigma=400 \kms,z=0.17\})$.
@@
 \subsubsection{Machine Learning Based}\label{sec:machine learning method}
-The estimation in this section relies on a ML technique known as an ensemble method, where many estimators are created by a single learning method with the goal of improved generalization and robustness compared to a single estimation.
+The cluster mass estimation in this section relies on a ML technique known as an ensemble method, where many estimators are created by a single learning method with the goal of improved generalization and robustness compared to a single estimation.
 Ensemble methods come in two general flavors.
@@
 The final prediction is then the average of all the trees.
-We use RF regression methods as implemented in {\tt Scikit-Learn} \citep{Pedregosa2012}.
+We use RF regression methods as implemented in {\sc Scikit-Learn} \citep{Pedregosa2012}.
 
@@
 \subsection{Recovery of Cluster Members}
-As discussed in Section \ref{sec: observations} the observational constraints place limits on the total number fo clusters member galaxies expected to be recovered.
+As discussed in Section \ref{sec: observations} the observational constraints place limits on the total number of clusters member galaxies expected to be recovered.
 Knowing these limits will provide important information for potential future follow up or targeted observations.
 Figure \ref{fig: recovery} shows the recovery fraction of member galaxies, the number of observed galaxies divided by the number of actual galaxies ($N_{obs}/N_{True}$), as function of both redshift and cluster mass.
-It is important to note that if fewer than five member galaxies are observed ($N_{obs} <5$) the cluster is not considered detected, and is excluded from this figure.
+It is important to note that if fewer than five member galaxies are observed ($N_{obs} <5$) the cluster is not considered detected, and is excluded from this Figure.
 As expected, the targeted observing strategy where the individual clusters are targeted through several dithers to ensure near complete coverage, performs significantly better than the survey observing strategy across all redshifts and cluster masses.
 
-For the clusters recovered as a function of redshift, there are two effects at work.
+For the clusters recovered as a function of redshift (left panel of Figure \ref{fig: recovery}), there are two effects at work.
 The decrease in recovery fraction with increasing redshift is a magnitude effect.
@@
 \subsection{Mass estimates}
-% \begin{table*}
-% \centering
-% \caption{Summary of the errors associated with the Targeted and Survey observation strategies, as an ensemble of predictions.
-See the text for discussion about the MAE and RMSE.
-Overlap is the percentage of clusters where the true cluster mass is bracketed by the prediction intervals of the predicted mass.
-See Sections \ref{sec:probability method} and \ref{sec:machine learning method} for a discussion on prediction intervals.}
-% \begin{tabular}{cccccccc}
-% 	%\hline
-% 	&& \multic{3}{Targeted} & \multic{3}{Survey} \\
-% 	\cline{3-5} \cline{6-8}
-% 	& Input Features & MAE & RMSE & Overlap & MAE & RMSE & Overlap \\
-% 	& & (dex) & (dex) & (\%) & (dex) & (dex) & (\%) \\
-% 	\hline
-% 	\rottext{4}{Prob Based} & Power Law & 0.259 & 0.394 & \nd & 0.243 & 0.357 & \nd \\
-% 	&$\sigma$ & 0.220 & 0.337 & \nd & 0.210 & 0.310 & \nd \\
-% 	&$\sigma, z$ & 0.193 & 0.283 & \nd & 0.184 & 0.271 & \nd \\
-% 	&$\sigma, z, N_{gal}$ & 0.128 & 0.204 & \nd & 0.141 & 0.215 & \nd \\
-% 	\hline
-% 	\rottext{4}{ML Based} & Power Law & 0.258 & 0.394 & \nd & 0.255 & 0.380 & \nd \\
-% 	&$\sigma$ & 0.241 & 0.359 & \nd & 0.223 & 0.342 & \nd \\
-% 	&$\sigma, z$ & 0.193 & 0.282 & \nd & 0.197 & 0.290 & \nd \\
-% 	&$\sigma, z, N_{gal}$ & 0.118 & 0.192 & \nd & 0.140 & 0.221 & \nd \\
-% 	\hline
-% \end{tabular}
-% \label{tbl:mass comparisons}
-% \end{table*}
-
 \begin{figure*} 
@@
 
-In this section we discuss the how accurately we are able to reproduce the true cluster mass from a set of observations.
+In this section we discuss the how accurately we recover the true cluster mass from a set of observations.
 We report on three methods, the power law based approach (Eq.
@@
 Because it represents the best possible scenario, the perfect knowledge observations should serve as baseline to compare the probability based and ML cluster mass recovery methods.
-And, while there are many possible metrics to evaluate performance, we compute two: the average bias
+And, while there are many possible metrics to evaluate performance, we compute two: the average bias (given in Table \ref{tbl:mass bias})
 \begin{equation}
@@
 \end{equation}
-where $y$ is the true value and $\hat{y}$ is the predicted value, and the scatter about the bias
+where $y$ are the true values and $\hat{y}$ are the predicted values, and the scatter about the bias (given in Table \ref{tbl:mass scatter})
 \begin{equation}
@@
 Also, as the number of cluster galaxies decreases the LOSVD PDF is poorly sampled leading to poorly recovered cluster masses due to numerical effects.
-The masses presented here are recovered using the best possible conditions, where we have perfect knowledge of the cluster membership.
+The cluster masses presented here are recovered using the best possible conditions, where we have perfect knowledge of the cluster membership.
 In reality, the mass recovery levels presented in this section represent an upper bound (the best) on the accuracy achievable through this method.
 
-\editorial{\cite{Ntampaka2015} does have a discussion about how well they do with contaminated galaxy catalogs.
+% \editorial{\cite{Ntampaka2015} does have a discussion about how well they do with contaminated galaxy catalogs.
 We could do something similar and have a similar discussion, but I'm not sure it is worth it.
@@
 
-In both Figures \ref{fig:Probability comparison} and \ref{fig: ML comparison}, we show the predicted ($M_{pred}$) versus true (M) cluster masses for each of the two observing strategries.
+In both Figures \ref{fig:Probability comparison} and \ref{fig: ML comparison}, we show the predicted ($M_{pred}$) versus true ($M_{200c}$) cluster masses for each of the two observing strategries.
 In each panel the solid black line is the 1:1 relationship, the solid purple line is the median recovered mass for the targeted observing, and the turquoise, dashed line is the median recovered mass for the HETDEX-like observations.
@@
 \begin{equation}\label{eq: fractional error}
-	\epsilon = (M_{pred} - M)/M
+	\epsilon = (M_{pred} - M_{200c})/M_{200c}
 \end{equation}
-where $M_{pred}$ is the predicted cluster mass and $M$ is the true cluster mass.
+where $M_{pred}$ is the predicted cluster mass and $M_{200c}$ is the true cluster mass.
 
@@
 \centering
-\caption{Bias and scatter of the true cluster mass for different bins of predicted cluster mass.
-This table shows the bias in the true cluster mass for the perfect (top section), targeted (middle section), and survey (bottom section) observations in different predicted mass bins.
+\caption{Mean bias ($M_{pred}$ - $M_{200c}$) for different bins of predicted cluster mass.
+This table shows the bias in the predicted cluster mass for the perfect (top section), targeted (middle section), and survey (bottom section) observations in different predicted mass bins.
 The different mass recovery strategies are given in the leftmost column.
@@
 \begin{tabular}{cccccccccc} 
-		&& \multic{8}{Bins -- Log $M_{pred}$ ($\Msol$)} \\
+		&& \multic{8}{Bins -- Log $M_{pred}$} \\
 		\cline{3-10} 
@@
 
-We quantify the bias and scatter for all of the different cluster mass recovery strategies and observing methods in Table \ref{tbl:mass bias}.
+We quantify the bias and scatter for all of the different cluster mass recovery strategies and observing methods in Table \ref{tbl:mass bias} and Table \ref{tbl:mass scatter}.
 It should serve as a type of look up table for future cluster observations with HETDEX.
@@
 
- A few caveats apply to the numbers given in Table \ref{tbl:mass bias}.
+ A few caveats apply to the numbers given in Table \ref{tbl:mass bias} and Table \ref{tbl:mass scatter}.
 While we provide corrections for cluster masses above $10^{15}$ \msol, they are estimated from only a handful of objects, and do not constitute a representative sample of clusters.
@@
 
+\begin{figure} 
+	\includegraphics[width=\columnwidth]{figures/millBuzzComparison.pdf} 
+	\caption{\emph{Top:} ML based cluster mass predictions for the Millennium simulation clusters where the ML method has been trained with either a subset of the Millennium clusters (solid line) or the Buzzard catalog (dashed line).
+The shaded areas show the 68\% scatter around the median.
+The solid black line shows the 1:1 relation.The solid black line shows the 1:1 relation.
+\emph{Bottom:} The fractional error (Equation~\ref{eq: fractional error}) also as a function of true cluster mass.
+The similarity of the predictions with the different training sets demonstrates how the ML method is not sensitive to the underlying cosmological assumptions.} \label{fig: mill buzz comparison}
+\end{figure}
+
 Cluster masses are assigned using the ML methods (see Section \ref{sec:machine learning method}) using two different training sets.
 We use the full set of clusters detected in the Buzzard catalogs (14000 clusters with $M > 10^{11}$ \msol) and a training-testing split of the Millennium clusters.
+The top pandel of Figure \ref{fig: mill buzz comparison} shows the ML predicted cluster masses as a function of true cluster mass for the $\sim$4000 Millennium clusters with the two different training sets.
+The median (solid and dashed lines) predicted cluster masses show similar trends regardless of the training data set used.
+Figure \ref{fig: mill buzz comparison}'s bottom panel show the fraction error (Equation~\ref{eq: fractional error}) also as a function of true cluster mass.
+The large amount of scatter (the shaded area) in the fractional error for the Buzzard trained predictions is due to the training set including clusters with masses below the $M = 10^{13}$ \Msol\ threshold for the Millennium clusters.
+This allows the ML method to predict masses which can be significantly different, whereas the Millennium training set does not include $M < 10^{13}$ \Msol\ clusters, which reduces the scatter of the predicted masses.
 
-\begin{figure} 
-	\includegraphics[width=\columnwidth]{figures/millBuzzComparison.pdf} 
-	\caption{Mass predictions for the power law scaling relation (Equation~\ref{eq:power law}) and the ML based technique with different input features as a function of true cluster mass.
-The bottom row of panels shows the fractional error (Equation~\ref{eq: fractional error}) also as a function of true cluster mass.
-The solid black line shows the 1:1 relation.
-The solid, colored line is the median predicted mass for the targeted observing, and the colored, dashed line is the median recovered mass for the HETDEX-like observations.
-The shaded regions represent the 68\% scatter around the median values.} \label{fig: mill buzz comparison}
-\end{figure}
-
-The predicted cluster masses for the 4000 millennium cluster are very similar regardless of the training set used.
-I've attached a plot that shows the probability of the predicted masses using the two different training sets.
-I also computed the mean squared error (MSE) of each set, compared to the *true* cluster mass.
-I like the MSE because it takes into account both the scatter and the bias.
-For the millennium clusters I found MSE $= 0.015$, and for the Buzzard clusters MSE $= 0.029$.
-Smaller numbers are better, and I think the difference is because I have chosen not to exclude clusters with $Msol < 1e13$ from the Buzzard catalogs when training.
-That allows the ML method to assign clusters below that which ups the MSE.
-
-I'm hoping that Millennium is different enough from Buzzard that this will address your concern.
-Another option would be just to include training samples from a few different mocks.
-Or, we could derive masses using different training sets and then marginalize over them to get a final predicted mass.
+\editorial{Maybe a sentence or two that specifically say we don't think this is a problem.}
 
@@
 \subsection{Impact on Cluster Cosmology}
+
+\begin{table*}
+\centering
+\caption{Scatter in cluster mass after bias correction for different bins of predicted cluster mass.
+This table shows the scatter in the predicted cluster mass for the perfect (top section), targeted (middle section), and survey (bottom section) observations in different predicted mass bins.
+The different mass recovery strategies are given in the leftmost column.
+It can be used to understand how the predicted cluster mass differs from the true cluster masses.}
+\begin{tabular}{cccccccccc} 
+		&& \multic{8}{Bins -- Log $M_{pred}$ ($\Msol$)} \\
+		\cline{3-10} 
+		\multicolumn{2}{c}{Method} & $11.5-12$ & $12-12.5$ & $12.5-13$ & $13-13.5$ & $13.5-14$ & $14-14.5$ & $14.5-15$ & $15-15.5$ \\
+		\hline 
+		\rottext{4}{Prob Based} & Power Law & $0.36\pm{0.07}$ & $0.39\pm{0.01}$ & $0.34\pm{0.00}$ & $0.22\pm{0.00}$ & $0.16\pm{0.00}$ & $0.14\pm{0.00}$ & $0.14\pm{0.01}$ & $0.11\pm{0.04}$ \\
+		&$\sigma$ & $0.16\pm{0.03}$ & $0.24\pm{0.01}$ & $0.26\pm{0.00}$ & $0.20\pm{0.00}$ & $0.16\pm{0.00}$ & $0.14\pm{0.00}$ & $0.16\pm{0.01}$ & $0.19\pm{0.07}$ \\
+		&$\sigma, z$ & $0.17\pm{0.03}$ & $0.21\pm{0.01}$ & $0.23\pm{0.00}$ & $0.19\pm{0.00}$ & $0.16\pm{0.00}$ & $0.55\pm{0.01}$ & $0.16\pm{0.01}$ & $0.39\pm{0.14}$ \\
+		&$\sigma, z, N_{gal}$ & $0.10\pm{0.02}$ & $0.14\pm{0.01}$ & $0.47\pm{0.01}$ & $0.14\pm{0.00}$ & $0.10\pm{0.00}$ & $0.54\pm{0.01}$ & $1.62\pm{0.09}$ & $9.31\pm{3.38}$ \\
+		\hline
+		\rottext{4}{ML Based} & Power Law & $0.36\pm{0.07}$ & $0.39\pm{0.01}$ & $0.34\pm{0.00}$ & $0.22\pm{0.00}$ & $0.16\pm{0.00}$ & $0.14\pm{0.00}$ & $0.14\pm{0.01}$ & $0.11\pm{0.04}$ \\
+		&$\sigma$ & $0.22\pm{0.04}$ & $0.27\pm{0.01}$ & $0.29\pm{0.00}$ & $0.24\pm{0.00}$ & $0.21\pm{0.00}$ & $0.19\pm{0.00}$ & $0.18\pm{0.01}$ & $0.22\pm{0.08}$ \\
+		&$\sigma, z$ & $0.19\pm{0.04}$ & $0.22\pm{0.01}$ & $0.25\pm{0.00}$ & $0.20\pm{0.00}$ & $0.18\pm{0.00}$ & $0.16\pm{0.00}$ & $0.17\pm{0.01}$ & $0.15\pm{0.05}$ \\
+		&$\sigma, z, N_{gal}$ & $0.15\pm{0.03}$ & $0.18\pm{0.01}$ & $0.17\pm{0.00}$ & $0.14\pm{0.00}$ & $0.10\pm{0.00}$ & $0.08\pm{0.00}$ & $0.08\pm{0.00}$ & $0.10\pm{0.03}$ \\
+		\hline 
+		\hline
+		\rottext{4}{Prob Based} & Power Law & $0.33\pm{0.07}$ & $0.41\pm{0.01}$ & $0.43\pm{0.01}$ & $0.39\pm{0.00}$ & $0.33\pm{0.00}$ & $0.27\pm{0.01}$ & $0.18\pm{0.01}$ & $0.11\pm{0.04}$ \\
+		&$\sigma$ & $0.14\pm{0.03}$ & $0.19\pm{0.01}$ & $0.24\pm{0.00}$ & $0.25\pm{0.00}$ & $0.25\pm{0.00}$ & $0.22\pm{0.00}$ & $0.19\pm{0.01}$ & $0.30\pm{0.11}$ \\
+		&$\sigma, z$ & $0.19\pm{0.04}$ & $0.20\pm{0.01}$ & $0.24\pm{0.00}$ & $0.24\pm{0.00}$ & $0.23\pm{0.00}$ & $0.56\pm{0.01}$ & $0.21\pm{0.01}$ & $0.36\pm{0.13}$ \\
+		&$\sigma, z, N_{gal}$ & $0.14\pm{0.03}$ & $0.18\pm{0.01}$ & $0.20\pm{0.00}$ & $0.19\pm{0.00}$ & $0.17\pm{0.00}$ & $0.67\pm{0.01}$ & $2.28\pm{0.13}$ & $8.56\pm{3.11}$ \\
+		\hline
+		\rottext{4}{ML Based} & Power Law & $0.33\pm{0.07}$ & $0.41\pm{0.01}$ & $0.43\pm{0.01}$ & $0.39\pm{0.00}$ & $0.33\pm{0.00}$ & $0.27\pm{0.01}$ & $0.18\pm{0.01}$ & $0.11\pm{0.04}$ \\
+		&$\sigma$ & $0.29\pm{0.06}$ & $0.29\pm{0.01}$ & $0.31\pm{0.00}$ & $0.31\pm{0.00}$ & $0.32\pm{0.00}$ & $0.30\pm{0.01}$ & $0.29\pm{0.02}$ & $0.11\pm{0.04}$ \\
+		&$\sigma, z$ & $0.14\pm{0.03}$ & $0.23\pm{0.01}$ & $0.26\pm{0.00}$ & $0.25\pm{0.00}$ & $0.24\pm{0.00}$ & $0.22\pm{0.00}$ & $0.25\pm{0.01}$ & $0.15\pm{0.05}$ \\
+		&$\sigma, z, N_{gal}$ & $0.13\pm{0.03}$ & $0.21\pm{0.01}$ & $0.21\pm{0.00}$ & $0.18\pm{0.00}$ & $0.16\pm{0.00}$ & $0.14\pm{0.00}$ & $0.12\pm{0.01}$ & $0.15\pm{0.05}$ \\
+		\hline
+		\hline
+		\rottext{4}{Prob Based} & Power Law & \nd & \nd & $0.16\pm{0.03}$ & $0.29\pm{0.01}$ & $0.33\pm{0.01}$ & $0.31\pm{0.01}$ & $0.25\pm{0.02}$ & $0.15\pm{0.06}$ \\
+		&$\sigma$ & \nd & \nd & $0.11\pm{0.02}$ & $0.18\pm{0.01}$ & $0.22\pm{0.01}$ & $0.22\pm{0.01}$ & $0.19\pm{0.01}$ & $0.25\pm{0.09}$ \\
+		&$\sigma, z$ & \nd & \nd & $0.13\pm{0.03}$ & $0.19\pm{0.01}$ & $0.22\pm{0.01}$ & $0.21\pm{0.01}$ & $1.31\pm{0.08}$ & $0.32\pm{0.11}$ \\
+		&$\sigma, z, N_{gal}$ & \nd & \nd & $0.14\pm{0.03}$ & $0.18\pm{0.01}$ & $0.19\pm{0.01}$ & $0.19\pm{0.01}$ & $2.27\pm{0.15}$ & $9.19\pm{3.34}$ \\
+		\hline
+		\rottext{4}{ML Based} & Power Law & \nd & $1.41\pm{inf}$ & $0.40\pm{0.05}$ & $0.41\pm{0.02}$ & $0.38\pm{0.01}$ & $0.32\pm{0.01}$ & $0.25\pm{0.02}$ & $0.15\pm{0.06}$ \\
+		&$\sigma$ & \nd & $0.30\pm{inf}$ & $0.27\pm{0.03}$ & $0.28\pm{0.01}$ & $0.30\pm{0.01}$ & $0.30\pm{0.01}$ & $0.30\pm{0.02}$ & $0.29\pm{0.11}$ \\
+		&$\sigma, z$ & \nd & $0.61\pm{inf}$ & $0.22\pm{0.03}$ & $0.25\pm{0.01}$ & $0.25\pm{0.01}$ & $0.25\pm{0.01}$ & $0.25\pm{0.02}$ & $0.30\pm{0.11}$ \\
+		&$\sigma, z, N_{gal}$ & \nd & $0.80\pm{inf}$ & $0.19\pm{0.02}$ & $0.21\pm{0.01}$ & $0.20\pm{0.01}$ & $0.19\pm{0.01}$ & $0.19\pm{0.01}$ & $0.23\pm{0.08}$ \\
+	\hline
+	\end{tabular}
+\label{tbl:mass scatter}
+\end{table*}
+
 % \editorial{This is a place holder section.
@@
 
-Galaxy clusters are sensitive probes of $\Omega_m$, the total mass ($\Omega_b + \Omega_c$) density in the universe, through tracing the peaks in the universal matter density often referred to as the power spectrum of matter density fluctuations or the matter power spectrum and $\sigma_8h^{-1}$, the normalization of the power spectrum, by the comparison of the number density of observed halos to that predicted in cosmological models.
+Galaxy clusters are sensitive probes of $\Omega_m$, the total mass ($\Omega_b + \Omega_c$) density in the universe, by tracing the peaks in the universal matter density often referred to as the power spectrum of matter density fluctuations or the matter power spectrum and $\sigma_8h^{-1}$, the normalization of the power spectrum, by the comparison of the number density of observed halos to that predicted in cosmological models.
 Although, in reality, one measures $\sigma_8h^{-1}\Omega_m^q$, where the value of $q$ depends on the masses and redshifts of the halos considered.
@@
 To get a sense of how well HETDEX will be able to constrain cosmological parameters we follow the discussion of \cite{Weinberg2013}, and begin with a few simplifying assumptions.
-While sensitive to $\Omega_m$, the number density of clusters do not necessarily provide the strongest contraint, so we assume that some combination of other data sets (\eg, CMB, BAO, supernovae, WL, etc.) will constrain $\Omega_m$ to high precision.
+While sensitive to $\Omega_m$, the number density of clusters do not necessarily provide the strongest contraint, so we assume that some combination of other data sets (\eg, CMB, BAO, supernovae, WL, etc.) will constrain $\Omega_m$ to higher precision than is possible with clusters alone.
 
@@
 \begin{equation}
-	\Delta~\mathrm{ln}~\sigma_{11,abs}(z) = q \times \mathrm{max}[\Delta~\mathrm{ln}~M,\alpha^{-1}\Delta\mathrm{ln}~N]
+\Delta \ln \sigma_8h^{-1}(z) \approx q(z)\times 
+        \max\left[ \Delta \ln M, \alpha(z)^{-1} \Delta \ln N \right].
+\label{eq:sigElapprox}
 \end{equation}
-where $q$ is the degeneracy exponent between $\sigma_8h^{-1}$ and $\Omega_m$, $\Delta\mathrm{ln}M$ is the mass scale uncertainty, $\Delta\mathrm{ln}N$ is the cluster statistical uncertainty, and $\alpha$ is slope of the cumulative HMF.
-Using the \cite{Tinker2008} HMF \cite{Weinberg2013} estimate $q\sim0.4$, and find that for any cluster survey with more than 10-20 clusters is dominated by the uncertainty in the overall mass scale.
+where $q$ is the degeneracy exponent between $\sigma_8h^{-1}$ and $\Omega_m$, $\Delta \ln M$ is the mass scale uncertainty, $\Delta \ln N$ is the cluster statistical uncertainty, and $\alpha$ is slope of the cumulative HMF.
+Using the \cite{Tinker2008} HMF at $z\sim0.2$ and a limiting cluster mass of $10^{14}$ \Msol, \cite{Weinberg2013} estimate $q\sim0.4$, $\alpha\sim3$, and find that any cluster survey with more than 10-20 clusters is dominated by the uncertainty in the overall mass scale.
 
-For a survey such as HETDEX, with a power law derived overall cluster mass biases of $>0.15$ dex (about 41\%) the uncertainty on $\sigma_8h^{-1}$ is $0.4 \times 0.41 \approx 16\%$.
-If we consider only clusters with masses above $10^{14}$ \Msol, with perfect knowledge, and the ML based cluster mass estimates the mass scale uncertainty is reduced to $\sim -0.02$ dex or about 5\%.
-This gives a uncertainty on $\sigma_8h^{-1}$ of 2\%.
-For clusters above $10^{14}$ \Msol, survey observations can constrain the masses to about 20\% which, in turn, constrains $\sigma_8h^{-1}$ to 8\%.
+For a survey such as HETDEX, we can estimate the constraints on $\sigma_8h^{-1}$ using Equation \ref{eq:sigElapprox}.
+Considering clusters with masses above $10^{14}$ \Msol, with perfect knowledge, and the ML based cluster mass estimates the mass scale uncertainty is reduced to $\sim 0.075$ dex or about 20\%.
+This gives a uncertainty on $\sigma_8h^{-1}$ of 7\%.
+For clusters above $10^{14}$ \Msol, survey observations can constrain the masses to about 51\% which, in turn, constrains $\sigma_8h^{-1}$ to 20\%.
 
 Because of the simplifying assumptions, and the superior quality of the data (no contamination, signal-to-noise issues, etc.), realistic expectations for HETDEX is to directly constrain $\sigma_8h^{-1}$ to better precision than other methods (\eg, CMB, WL, X-ray) seems bleak.
-For the $\sim1500$ clusters detected with survey observations to constrain $\sigma_8h^{-1}$ and to be dominated by cluster statistics alone ($\Delta\mathrm{ln}N \sim N^{-1/2}$), the absolute cluster calibration would need to be better than 2.5\%.
+For the $\sim1500$ clusters detected with survey observations to constrain $\sigma_8h^{-1}$ and to be dominated by cluster statistics alone ($\Delta \ln N \sim N^{-1/2}$), the absolute cluster calibration would need to be better than 2.5\%.
 For a fully targeted survey, about 14000 clusters, this cluster mass calibration uncertainty reduces to $>1\%$.
@@
 
-\subsection{Potential Improvements}
-\editorial{The potential improvements are really three fold.
+% \subsection{Potential Improvements}
+% \editorial{The potential improvements are really three fold.
 We know that the observing won't cover all of the sky.

### 2016-04-11 ms.tex
more edits

@@
 Here, we carry out a study to investigate the ability of a blind spectroscopic survey to recover accurate galaxy cluster masses through their velocity dispersion.
-We focus on the Hobby Eberly Telescope Dark Energy Experiment (HETDEX), which will observe many hundreds of square degrees.
-HETDEX will employ the new VIRUS instrument, an integral field unit (IFU), covering the blue/optical portion of the spectrum (3500--5500~\AAA) blindly in two fields for a total of 420 \degsq\ on the sky with fibers with a 1/4.5 fill factor.
-This allows surveys with VIRUS to measure redshifts for a large sample of galaxies out to $z < 0.5$ based on their absorption features or [\ion{O}{ii}] $\lambda$3727 emission (and Lyman-$\alpha$ over $1.9 < z < 3.5$).
+We focus on the Hobby Eberly Telescope Dark Energy Experiment (HETDEX), which will employ the new VIRUS integral field unit (IFU) spectrograph, over 420 \degsq\ on the sky with a 1/4.5 fill factor.
+The instrument covers the blue/optical portion of the spectrum (3500--5500~\AAA), allowing surveys with VIRUS to measure redshifts for a large sample of galaxies out to $z < 0.5$ based on their absorption features or [\ion{O}{ii}] $\lambda$3727 emission (and Lyman-$\alpha$ over $1.9 < z < 3.5$).
 We use a detailed mock galaxy catalog from a semi-analytic model to simulate surveys observed with VIRUS, including: (1) a blind, HETDEX-like survey with an incomplete but uniform spectroscopic selection function; and (2) IFU surveys that target clusters directly, obtaining spectra of all galaxies in a VIRUS-sized field.
@@
 We benchmark both surveys against spectroscopic observations with ``perfect" knowledge of galaxy line-of-sight velocities.
-Using both observing strategies, we produce cluster mass probability density functions $P(M_{200}|\vec{x})$ of a cluster mass ($M_{200}$) as a function of an observable parameter or set of observable parameters, $\vec{x}$, where we consider cases of where $\vec{x} = \{\sigma\}$, $=\{\sigma, z\}$, and $=\{\sigma,z, N_{gal}\}$ for velocity dispersion, $\sigma$, redshift, and number of observed galaxies, $N_{gal}$.
+Using both observing strategies, we produce cluster mass probability density functions $P(M_{200c}|\vec{x})$ of a cluster mass ($M_{200c}$) as a function of an observable parameter or set of observable parameters, $\vec{x}$, where we consider cases of where $\vec{x} = \{\sigma\}$, $=\{\sigma, z\}$, and $=\{\sigma,z, N_{gal}\}$ for velocity dispersion, $\sigma$, redshift, and number of observed galaxies, $N_{gal}$.
 \editorial{This sentence will summarize how well HETDEX will do, and how that might be improved with targeted observations}.
@@
 
-\editorial{The wording here needs to be updated when we settle on the verbage for everything else.} This work plans to address these concerns in the following ways.
-We use simulated observations which target individual galaxy clusters to investigate the recovery of parameters with such observations.
-Secondly, we create and evaluate a HETDEX like selection ``function'' of galaxies over a similarly large portion of the sky and use well adopted techniques to recover the dynamical properties, such as velocity dispersion and mass.
-Each observation strategy will further be constrained with ``ideal'' and ``realistic'' knowledge.
-Ideal knowledge assumes that we know which individual galaxy is assigned to which cluster.
-With realistic knowledge this is unknown and must be determined prior to the estimation of the cluster properties.
-Both of these strategies will better allow future work to predict the number and types of galaxy clusters which should be observed with VIRUS during both the HETDEX survey portion and through targeted follow up observations.
+This work plans to address these concerns in the following ways.
+We create and evaluate a HETDEX like selection ``function'' of galaxies over a similarly large portion of the sky and use well adopted techniques to recover the dynamical properties, such as velocity dispersion and mass.
+We compare these results to a series of targeted galaxy cluster observations, where each member galaxy is assumed to be observed.
+Each of these observations use realistic uncertainties from galaxy magnitude and line-flux limits.
+These strategies will better allow future work to predict the number and types of galaxy clusters which should be observed with VIRUS during both the HETDEX survey portion and through targeted follow up observations.
 
@@
 A brief description of the catalog creation is described as follows.
-The initial conditions are generated with a second-order Lagrangian perturbation theory using {\tt 2LPTic} \citep{Crocce2006}.
-Dark matter (DM) n-body simulations are run using {\tt LGadget-2} (a version of {\tt Gadget-2}; \citealt{Springel2005}).
-The DM halos are identified using the {\tt ROCKSTAR} halo finder \citep{Behroozi2013} which also calculates halo masses.
+The initial conditions are generated with a second-order Lagrangian perturbation theory using {\sc 2LPTic} \citep{Crocce2006}.
+Dark matter (DM) n-body simulations are run using {\sc LGadget-2} (a version of {\sc Gadget-2}; \citealt{Springel2005}).
+The DM halos are identified using the {\sc ROCKSTAR} halo finder \citep{Behroozi2013} which also calculates halo masses.
 
@@
 We investigate the accuracy of the halo mass distribution by comparing the cumulative number density of halos above a mass ($M_{200c}$) threshold to the halo mass function (HMF) of \cite{Tinker2008}.
-We calculate the HMF at central redshifts of 0.1, 0.2, and 0.4 using {\tt HMFcalc} \citep{Murray2013} and compare it galaxies in a redshift window of $\Delta z\pm0.01$.
+We calculate the HMF at central redshifts of 0.1, 0.2, and 0.4 using {\sc HMFcalc} \citep{Murray2013} and compare it galaxies in a redshift window of $\Delta z\pm0.01$.
 We find a very good agreement between the predicted HMF and the observed distribution of clusters.
-\editorial{Could show a figure comparing the Buzzard catalog to a plot of the HMF for a couple of redshifts.
-Might be helpful, might not matter.}
 
@@
 We sample the distribution and assign each catalog galaxy an [\ion{O}{ii}] luminosity which is then converted into a flux.
-\editorial{We could add a plot like the corner plot to show the multi-dimensionality of this process.}
 
@@
 
-Each mask is created to reproduce the HETDEX IFU pattern, see Figure~\ref{fig: ifu layout}.
-The pattern consists of 78 IFUs, which are comprised of 448 optical fibers subtending a $50'' \times 50''$ region on the sky \citep{Kelz2014}.
+The HETDEX IFU pattern is illustrated in Figure~\ref{fig: ifu layout.} The pattern consists of 78 IFUs, which are comprised of 448 optical fibers subtending a $50'' \times 50''$ region on the sky \citep{Kelz2014}.
 The inter-IFU spacing is also $50''$ spanning a total area of $16'\times 16'$ on the sky.
+The individual IFUs have a fill-factor of 1/3, which will be completely filled with three dithers of the telescope at each pointing.
 
-The individual IFUs have a fill-factor of 1/3, which will be completely filled with three dithers of the telescope at each pointing.
 This means that when selecting galaxies from the Buzzard catalog we assume an observation for all galaxies laying within a colored, IFU square in Figure~\ref{fig: ifu layout}.
@@
 The accurate determination of the cluster redshift ($z_c$) is crucial to the reliability of all following measurements.
-An incorrect cluster redshift introduces errors into the measured line-of-sight velocity (LOSV) and corresponding dispersion, which, in turn, contributes to errors associated with dynamical mass and radius.
+An incorrect cluster redshift introduces error into the measured line-of-sight velocity (LOSV) and corresponding dispersion, which, in turn, contributes to errors associated with dynamical mass and radius.
 
 In simple terms, the cluster redshift is the mean of the redshifts of all galaxies associated with the cluster.
-However, because the standard mean can be quite sensitive to outliers or otherwise contaminated data, we require a more resistant statistic, and turn to the biweight location estimator \citep{Beers1990} which provides improved performance.
+For this work we rely on the biweight location estimator \citep{Beers1990} because it is resistant to outlying galaxies.
+Although this work assumes that we know each galaxy's redshift to infinite precision, in practice, we find a simple weighted mean provides a reliable estimate of $z_c$ when there are uncertainties on the individual galaxy redshifts.
 
@@
 where $\sigma_p$, $\langle\mu\rangle$, and $\sigma_i$ is the LOSVD, the average radial velocity and the error on the individual LOSVs respectively.
-Using a Monte Carlo Markov Chain (MCMC) sampler ({\tt emcee}\footnote{\url{http://dan.iel.fm/emcee/current/}}; \citealt{Foreman-Mackey2013}) which is based on affine-invariant ensemble sampler (see \citealt{Goodman2010} for details on affine-invariant samplers).
+Using a Monte Carlo Markov Chain (MCMC) sampler ({\sc emcee}\footnote{\url{http://dan.iel.fm/emcee/current/}}; \citealt{Foreman-Mackey2013}) which is based on affine-invariant ensemble sampler (see \citealt{Goodman2010} for details on affine-invariant samplers).
 We draw twenty thousand samples from the posterior probability distribution using simple priors, $\langle\mu\rangle$ lies between the maximum and minimum LOSV and $0< \sigma_p < 1400$ \kms.
@@
 The cluster masses predicted by Equation \ref{eq:power law} gives the following results.
-Across all cluster masses, we find $\mu_{bias} = 0.15\pm{0.002}$ dex.
+Across all cluster masses, we find $\mu_{bias} = 0.15\pm{0.002}$ dex and $\sigma_{bias} = 0.24\pm{0.001}$.
 The scatter in recovered masses can be attributed to both physical and numerical effects.
@@
 
-For the targeted and survey observations the power law predicted cluster masses give $\mu_{bias} =0.13\pm{0.003}$ dex and $\mu_{bias} =0.11\pm{0.009}$ dex, respectively.
+For the targeted and survey observations the power law predicted cluster masses give $\mu_{bias} =0.13\pm{0.003}$ dex, $\sigma_{bias} = 0.37\pm{0.002}$ and $\mu_{bias} =0.11\pm{0.009}$ dex, $\sigma_{bias} = 0.36\pm{0.006}$ , respectively.
 So for the clusters that we detect with survey observations, we obtain similar levels of accuracy as to the targeted observations, on the average.
@@
 
-\editorial{Maybe a sentence or two that specifically say we don't think this is a problem.}
+Based on these tests, we do not find a significant cause for concern with using trained ML methods to predict our galaxy cluster masses when the underlying cosmological choices are different.
+This highlights the versatility of our chosen ML method.
+The ML method could be further diversified by including cluster measurements from a wide range of cosmological simulations (or observations) which, in affect, marginalizes over all the cosmological assumptions further reducing the dependence.
+
+Based on these tests, we do not find a significant cause for concern about training our ML methods using simulations which may have a different cosmology than the target observations. We
 
@@
 		\hline
-		\rottext{4}{ML Based} & Power Law & \nd & $1.41\pm{inf}$ & $0.40\pm{0.05}$ & $0.41\pm{0.02}$ & $0.38\pm{0.01}$ & $0.32\pm{0.01}$ & $0.25\pm{0.02}$ & $0.15\pm{0.06}$ \\
-		&$\sigma$ & \nd & $0.30\pm{inf}$ & $0.27\pm{0.03}$ & $0.28\pm{0.01}$ & $0.30\pm{0.01}$ & $0.30\pm{0.01}$ & $0.30\pm{0.02}$ & $0.29\pm{0.11}$ \\
-		&$\sigma, z$ & \nd & $0.61\pm{inf}$ & $0.22\pm{0.03}$ & $0.25\pm{0.01}$ & $0.25\pm{0.01}$ & $0.25\pm{0.01}$ & $0.25\pm{0.02}$ & $0.30\pm{0.11}$ \\
-		&$\sigma, z, N_{gal}$ & \nd & $0.80\pm{inf}$ & $0.19\pm{0.02}$ & $0.21\pm{0.01}$ & $0.20\pm{0.01}$ & $0.19\pm{0.01}$ & $0.19\pm{0.01}$ & $0.23\pm{0.08}$ \\
+		\rottext{4}{ML Based} & Power Law & \nd & $1.41\pm{...}$ & $0.40\pm{0.05}$ & $0.41\pm{0.02}$ & $0.38\pm{0.01}$ & $0.32\pm{0.01}$ & $0.25\pm{0.02}$ & $0.15\pm{0.06}$ \\
+		&$\sigma$ & \nd & $0.30\pm{...}$ & $0.27\pm{0.03}$ & $0.28\pm{0.01}$ & $0.30\pm{0.01}$ & $0.30\pm{0.01}$ & $0.30\pm{0.02}$ & $0.29\pm{0.11}$ \\
+		&$\sigma, z$ & \nd & $0.61\pm{...}$ & $0.22\pm{0.03}$ & $0.25\pm{0.01}$ & $0.25\pm{0.01}$ & $0.25\pm{0.01}$ & $0.25\pm{0.02}$ & $0.30\pm{0.11}$ \\
+		&$\sigma, z, N_{gal}$ & \nd & $0.80\pm{...}$ & $0.19\pm{0.02}$ & $0.21\pm{0.01}$ & $0.20\pm{0.01}$ & $0.19\pm{0.01}$ & $0.19\pm{0.01}$ & $0.23\pm{0.08}$ \\
 	\hline
@@
 \end{table*}
-
-% \editorial{This is a place holder section.
-One of the things missing to bring this work full circle is a discussion about how the uncertainties in cluster masses impact the derived cosmological parameters.
-I am currently doing a literature review looking for references that discuss how the mass errors impact the derived parameters.
-Here we want to be able to say ``so and so show that errors on clusters masses need to be better than blah to recover $\sigma_8$ and $\Omega_m$ to better than blah, which is useful for blah.
-We show that with XXXX kind of data spectroscopic surveys like HETDEX can achieve this but only with YYYY kind of data quality.'' If it isn't going to do that well, then how much constraint could HETDEX/HETDEX-like surveys put on cosmological parameters?
-How good would they have to get to test gravity?
-(or the dark energy equation of state)}
 
@@
 For a survey such as HETDEX, we can estimate the constraints on $\sigma_8h^{-1}$ using Equation \ref{eq:sigElapprox}.
-Considering clusters with masses above $10^{14}$ \Msol, with perfect knowledge, and the ML based cluster mass estimates the mass scale uncertainty is reduced to $\sim 0.075$ dex or about 20\%.
+Considering clusters with masses above $10^{14}$ \Msol, with perfect knowledge, and the ML based cluster mass estimates the mass scale uncertainty (given in Table~\ref{tbl:mass scatter}) is reduced to $\sim 0.075$ dex or about 20\%.
 This gives a uncertainty on $\sigma_8h^{-1}$ of 7\%.
@@
 Because of the simplifying assumptions, and the superior quality of the data (no contamination, signal-to-noise issues, etc.), realistic expectations for HETDEX is to directly constrain $\sigma_8h^{-1}$ to better precision than other methods (\eg, CMB, WL, X-ray) seems bleak.
+For example \cite{deHaan2016} constrain $\sigma_8h^{-1}$ to $\sim5$\% using a sample of 337 SZE detected clusters from the SPT-SZE survey.
 For the $\sim1500$ clusters detected with survey observations to constrain $\sigma_8h^{-1}$ and to be dominated by cluster statistics alone ($\Delta \ln N \sim N^{-1/2}$), the absolute cluster calibration would need to be better than 2.5\%.
 For a fully targeted survey, about 14000 clusters, this cluster mass calibration uncertainty reduces to $>1\%$.
-\editorial{Here I want to say a word or two about how all hope isn't lost.
-We can still use HETDEX to reduce the scatter on the richness-mass relationship which can help other estimators get down to the levels we need to really nail down these numbers.}
 
@@
 Crawford for many helpful discussions.
-This research made use of This research made use of the {\tt IPython} package \citep{Perez2007} and {\tt matplotlib}, a Python library for publication quality graphics \citep{Hunter2007}.
+This research made use of This research made use of the {\sc IPython} package \citep{Perez2007} and {\sc matplotlib}, a Python library for publication quality graphics \citep{Hunter2007}.
 Figure \ref{fig: probability corner} is heavily based on \cite{Foreman-Mackey2016}.

### 2016-04-20 ms.tex
test for ting
remove change for ting

@@
 \usepackage{amssymb}	% Extra maths symbols
+\usepackage{mathrsfs}
 \usepackage{natbib}
@@
 Using both observing strategies, we produce cluster mass probability density functions $P(M_{200c}|\vec{x})$ of a cluster mass ($M_{200c}$) as a function of an observable parameter or set of observable parameters, $\vec{x}$, where we consider cases of where $\vec{x} = \{\sigma\}$, $=\{\sigma, z\}$, and $=\{\sigma,z, N_{gal}\}$ for velocity dispersion, $\sigma$, redshift, and number of observed galaxies, $N_{gal}$.
-\editorial{This sentence will summarize how well HETDEX will do, and how that might be improved with targeted observations}.
+\editorial{This sentence will summarize how well HETDEX will do, and how that might be improved with targeted observations.}
 \end{abstract}
 
-\section{INTRODUCTION}
+\section{Introduction}
 Our ability to perform precision cosmology with clusters of galaxies has reached a critical turning point.
@@
 This directly calibrates the observable--mass relation which is then applied to a much larger sample.
-The complications lie in that the ``true'' masses are in fact estimations, and the methods used to recover these masses are subject to their own limitations.
-X-ray hydrostatic estimations assume hydrostatic equilibrium \citeeg{Mantz2015} which may only be valid for a very small number and range of cluster masses.
+The complications lie in that the ``true'' masses are, in fact, estimations, and the methods used to recover these cluster masses are subject to their own limitations.
+X-ray based cluster masses assume hydrostatic equilibrium \citeeg{Mantz2015} which may only be valid for a very small number and range of cluster masses.
 The Sunyaev--Zel'dovich Effect (SZE; \citealt{Sunyaev1972}), which uses the up--scattering of CMB photons to estimate cluster masses, provides accurate estimations of mass, but the ability to detect low mass galaxy clusters is currently limited by technology \citeeg{Carlstrom2002a}.
@@
 
-Massive surveys, both on going and planned, are revolutionizing cluster cosmology using a large range of wavelengths.
+Large-area sky surveys, both on going and planned, are revolutionizing cluster cosmology using a large range of wavelengths.
 The South Pole Telescope (SPT; \citealt{Carlstrom2011}) and the Atacama Cosmology Telescope (ACT; \citealt{Swetz2011}) are discovering many clusters through the SZE.
@@
 It is unclear how a blind spectroscopic survey with an IFU will effect the recovery of galaxy cluster dynamical properties.
-Unlike many previous large cluster surveys \citeeg{Milvang-Jensen2008, Robotham2011, Sifon2015} which use multi-object spectrographs, the Visible Integral-Field Replicable Unit Spectrograph (VIRUS; \citealt{Hill2012}) used by HETDEX samples the sky unevenly which could excluded member galaxies which would otherwise be included.
+Unlike many previous large cluster surveys \citeeg{Milvang-Jensen2008, Robotham2011, Sifon2015} which use multi-object spectrographs, the Visible Integral-Field Replicable Unit Spectrograph (VIRUS; \citealt{Hill2012}) used by HETDEX samples the sky in a uniform but sparse way which could excluded member galaxies which would otherwise be included.
 Secondly, it is not straightforward to use spectroscopic redshifts predominately from emission-line galaxies to interpret the kinematic and dynamical states of the clusters.
@@
 This work plans to address these concerns in the following ways.
-We create and evaluate a HETDEX like selection ``function'' of galaxies over a similarly large portion of the sky and use well adopted techniques to recover the dynamical properties, such as velocity dispersion and mass.
+We create and evaluate a HETDEX like selection ``function'' of galaxies over a similarly large portion of the sky and use well adopted techniques to recover the dynamical properties, such as velocity dispersion and cluster mass.
 We compare these results to a series of targeted galaxy cluster observations, where each member galaxy is assumed to be observed.
@@
 Finally we summarize our findings in Section \ref{sec:summary}.
+A followup to this work \citep{Boada2016a} will investigate how the techniques developed here will work in practice.
 
@@
 For catalog galaxies which are placed on the CMD near no, or very few ($1\leq n<10$) galaxies we assign it zero [\ion{O}{ii}] luminosity or the mean luminosity, respectively.
+We find no evidence of a significant bias due to galaxies being assigned zero [\ion{O}{ii}] luminosity.
 For the galaxies in the Buzzard catalog, 1.3\% of the galaxies brighter than $\sdssg = 22$ mag (HETDEX's detection limit) have exactly zero [\ion{O}{ii}] luminosity.
-Of the 1.3\%, only 3.3\% (0.05\% of all galaxies) have $g-r < 1.5$ suggesting the galaxies which are assigned zero [\ion{O}{ii}] luminosity are not significantly biasing our simulations.
+Of the 1.3\%, only 3.3\% (0.05\% of all galaxies) have $g-r < 1.5$.
 
@@
 
-The HETDEX IFU pattern is illustrated in Figure~\ref{fig: ifu layout.} The pattern consists of 78 IFUs, which are comprised of 448 optical fibers subtending a $50'' \times 50''$ region on the sky \citep{Kelz2014}.
+The HETDEX IFU pattern is illustrated in Figure~\ref{fig: ifu layout} and consists of 78 IFUs, which are comprised of 448 optical fibers subtending a $50'' \times 50''$ region on the sky \citep{Kelz2014}.
 The inter-IFU spacing is also $50''$ spanning a total area of $16'\times 16'$ on the sky.
@@
 To cover the 398.49 \degsq\ field of the Buzzard catalog we require 5370 pointings where 0.015 \degsq\ of each pointing is covered by an IFU.
-The total area of the sky covered by an IFU is 80.80 \degsq\ which gives a filling factor of 1/4.65 slightly decreased from the expected filling factor of 1/4.5.
+The total area of the sky covered by an IFU is 80.80 \degsq\ which gives a filling factor of 1/4.65, slightly decreased from the expected filling factor of 1/4.5.
 
@@
 The survey observations mimic the HETDEX observation pattern across the sky, where no cluster is directly targeted and not all cluster member galaxies are observed.
-Both of these observations have HETDEX-like galaxy detection thresholds, for comparison we also include a set of targeted observations with ``perfect'' knowledge.
+Both of these observations have HETDEX-like galaxy detection thresholds, and for comparison we also include a set of targeted observations with ``perfect'' knowledge.
 Perfect observations assume no detection threshold, if a cluster member galaxy is observed, it is also detected.
-This provides an important best-case scenario, and differs from the true cluster properties because the recovered cluster properties are still calculated.
+This provides an important best-case scenario, and differs from the true cluster properties because the cluster properties are still calculated.
 These observations provide three levels of quality with ``perfect knowledge'' being the highest and survey being the lowest.
@@
 The following is, in many cases, a subset of the available methods to derive any single parameter.
-The specific choice of method may improve or diminish the accuracy of the recovered parameter, but the methods chosen were to facilitate comparison with other observational studies.
+The specific choice of method may improve or diminish the accuracy of the recovered parameter, but the methods chosen were to facilitate comparison with other observational studies \citeeg{Boada2016a}.
 
@@
 \subsection{Line-of-Sight Velocity Dispersion}\label{sec: LOSVD}
-We first calculate the line-of-sight velocity (LOSV) to each galaxy, where
+We first calculate the LOSV to each galaxy, where
 \begin{equation}
@@
 \end{equation}
-where $\sigma_p$, $\langle\mu\rangle$, and $\sigma_i$ is the LOSVD, the average radial velocity and the error on the individual LOSVs respectively.
-Using a Monte Carlo Markov Chain (MCMC) sampler ({\sc emcee}\footnote{\url{http://dan.iel.fm/emcee/current/}}; \citealt{Foreman-Mackey2013}) which is based on affine-invariant ensemble sampler (see \citealt{Goodman2010} for details on affine-invariant samplers).
+where $\sigma_p$, $\langle\mu\rangle$, and $\sigma_i$ is the LOSVD, the average radial velocity and the error on the individual LOSVs respectively, using a Monte Carlo Markov Chain (MCMC) sampler ({\sc emcee}\footnote{\url{http://dan.iel.fm/emcee/current/}}; \citealt{Foreman-Mackey2013}) which is based on affine-invariant ensemble sampler (see \citealt{Goodman2010} for details on affine-invariant samplers).
 We draw twenty thousand samples from the posterior probability distribution using simple priors, $\langle\mu\rangle$ lies between the maximum and minimum LOSV and $0< \sigma_p < 1400$ \kms.
@@
 \subsection{Dynamical Mass from Scaling Relations}\label{sec: mass}
-The relationship between the LOSVD and dynamical mass has been the focus of several studies \citeeg{Evrard2008, Saro2013, Sifon2013, VanderBurg2014}, and a best fitting relationship for the mass enclosed by $r_{200c}$ of the form
+The relationship between the LOSVD and cluster dynamical mass has been the focus of several studies \citeeg{Evrard2008, Saro2013, Sifon2013, VanderBurg2014}, and a best fitting relationship for the mass enclosed by $r_{200c}$ of the form
 \begin{equation}\label{eq:power law}
@@
 Specifically, while there is little difference between using galaxies and their host DM subhalos, there is a significant over estimation of the LOSVD when using galaxies/subhalos compared to DM particles \citep{Munari2013}.
-We follow other works \citeeg{Kirk2015, Sifon2015a} using the scaling relation, given in Equation~\ref{eq:power law} from \cite{Munari2013} to facilitate comparisons with other observational studies.
+We follow other works \citeeg{Kirk2015, Sifon2015a} using the scaling relation, given in Equation~\ref{eq:power law} from \cite{Munari2013} to facilitate comparisons with other observational studies, which rely on galaxies are tracers.
 % \editorial{This all needs to be stripped out and reworked.}
@@
 In this section we use two methods to predict the mass of a cluster based on other observables.
-Often the cluster mass is estimated based on a single observable, X-ray temperature, velocity dispersion, richness and others.
+Often the cluster mass is estimated based on a single observable, X-ray temperature, LOSVD, richness and others.
 Here we combine many observables to attempt to correct the mass inferred solely from the velocity dispersion.
-The first method is traditional probability based where we marginalize over a series of observables to find the most probable mass.
-The second is based on a machine learning (ML) algorithm which attempts to ``learn'' the relationship between the observables and the desired output, the mass.
+The first method is traditional probability based where we marginalize over a series of observables to find the most probable cluster mass.
+The second is based on a machine learning (ML) algorithm which attempts to ``learn'' the relationship between the observables and the desired output, the cluster mass.
 Both of these methods are examples of supervised learning algorithms where the relationship between the observable parameters and the target parameter (the cluster mass) are both known.
@@
 The conditional probability of the mass $P(M_{200c}|\vec{x}= \{ x_1,x_2,...\})$ is determined by taking a slice through the joint probability distributions in bins centered on the desired value.
-The slices shown by the colored bars in Figure~\ref{fig: probability corner} are centered on $\sigma = 400$ \kms and $z=0.17$.
-The distribution of mass contained in the three dimensional bin given by the intersection of these slices is $P(M_{200c}|\vec{x} = \{\sigma=400 \kms,z=0.17\})$.
+The slices, shown by the colored bars in Figure~\ref{fig: probability corner}, are centered on $\sigma = 400$ \kms and $z=0.17$.
+The distribution of cluster mass contained in the three dimensional bin given by the intersection of these slices is $P(M_{200c}|\vec{x} = \{\sigma=400 \kms,z=0.17\})$.
 
@@
 \end{equation}
-The expected mass is determined by calculating the first moment of the probability density. This becomes our ``predicted'' mass, $M_{pred}$.
+The expected mass is determined by calculating the first moment of the probability density. This becomes our ``predicted'' cluster mass, $M_{pred}$.
 \begin{equation}\label{eq: expected mass}
@@
 Decision trees can be visualized a flow chart where forks are the branches of the tree.
-The path along the tree is decided by the values of the feature at each branch.
+The path along the tree is decided by the values of the feature(s) at each branch.
 RF estimators use a random subset of the training set at each fork to decide which path should be followed.
-The final prediction is then the average of all the trees.
+The final prediction is then the average of all the final predictions from the trees.
 We use RF regression methods as implemented in {\sc Scikit-Learn} \citep{Pedregosa2012}.
@@
 The 68\% prediction interval is determined by calculating the 16th and 84th percentile of the full conditional probability distribution.
-\editorial{I am going to change this to just the std of the distribution.
-I need the errorbars to be symmetric to make the fitting routine easy later on.}
 
@@
 Survey observations mimic the HETDEX observation strategy such that no cluster is directly observed, and only the cluster member galaxies above the detection threshold and within an IFU (see Figure \ref{fig: ifu layout}) are observed.
-We discuss the accuracy of dynamical mass derived from both the scaling relation (see Equation \ref{eq:power law}) and through the probability and ML methods.
+We discuss the accuracy of cluster dynamical mass derived from both the power-law scaling relation (see Equation \ref{eq:power law}) and through the probability and ML methods.
 
@@
 The shaded regions are the 68\% scatter around the median values (the 16\% and 84\% quartiles).
-For reference we also show the median masses recovered with perfect knowledge as a solid orange line.
+For reference we also show the median masses recovered with perfect knowledge as a dash-dotted orange line.
 The lower panels show the fractional cluster mass error:
@@
 The three horizontal sections represent perfect, targeted and survey observations respectively.
-So, for example, if a cluster mass is predicted using the $ML_{\sigma, z}$ method and targeted observations to be Log M $=13-13.5$ \Msol, it is biased upward by $0.03\pm{0.00}$ dex.
+So, for example, if a cluster mass is predicted using the $ML_{\sigma, z}$ method and targeted observations to be Log M/\Msol\ $=13-13.5$, it is biased upward by $0.03\pm{0.00}$ dex.
 
@@
 \subsubsection{Significance of Cosmology Choice}
-The underlying simulation used to produce the Buzzard catalogs, as with every simulation, makes specific assumptions about the cosmology used and how the galaxies are populated into the dark matter halos.
+The underlying simulation used to produce the Buzzard catalogs, as with every simulation, makes specific assumptions about the cosmology used and how the galaxies are populated into the DM halos.
 When using simulation data to train ML methods, we incorporate all of those assumptions into the learned feature associations.
@@
 
-To investigate this, we select cluster halo and galaxy catalogs from the Millennium simulation \citep{Springel2005b} obtained via querying the Millennium online database\footnote{http://gavo.mpa-garching.mpg.de/Millennium/} \citep{Lemson2006}.
+To investigate this, we select cluster halo and galaxy catalogs from the Millennium simulation \citep{Springel2005a} obtained via querying the Millennium online database\footnote{http://gavo.mpa-garching.mpg.de/Millennium/} \citep{Lemson2006}.
 The Millennium simulation tracks $2160^3$ dark matter particles of $8.6\times 10^8 ~h^{-1}$ \Msol\ inside a comoving 500 $(h^{-1} \mathrm{Mpc})^3$ box from $z=127$ to 0.
@@
 We use the full set of clusters detected in the Buzzard catalogs (14000 clusters with $M > 10^{11}$ \msol) and a training-testing split of the Millennium clusters.
-The top pandel of Figure \ref{fig: mill buzz comparison} shows the ML predicted cluster masses as a function of true cluster mass for the $\sim$4000 Millennium clusters with the two different training sets.
+The top panel of Figure \ref{fig: mill buzz comparison} shows the ML predicted cluster masses as a function of true cluster mass for the $\sim$4000 Millennium clusters with the two different training sets.
 The median (solid and dashed lines) predicted cluster masses show similar trends regardless of the training data set used.
@@
 
-Based on these tests, we do not find a significant cause for concern about training our ML methods using simulations which may have a different cosmology than the target observations. We
-
 \section{HETDEX as a Galaxy Cluster Survey at $z < 0.5$}\label{sec:discussion}
@@
 \subsection{Impact on Cluster Cosmology}
-
 \begin{table*}
@@
 
-Galaxy clusters are sensitive probes of $\Omega_m$, the total mass ($\Omega_b + \Omega_c$) density in the universe, by tracing the peaks in the universal matter density often referred to as the power spectrum of matter density fluctuations or the matter power spectrum and $\sigma_8h^{-1}$, the normalization of the power spectrum, by the comparison of the number density of observed halos to that predicted in cosmological models.
+Galaxy clusters are sensitive probes of $\Omega_m$, the total mass ($\Omega_b + \Omega_c$) density in the universe, by tracing the peaks in the universal matter density often referred to as the power spectrum of matter density fluctuations or the matter power spectrum and $\sigma_8h^{-1}$, the normalization of the power spectrum, by the comparison of the number density of observed clusters to that predicted in cosmological models.
 Although, in reality, one measures $\sigma_8h^{-1}\Omega_m^q$, where the value of $q$ depends on the masses and redshifts of the halos considered.
@@
 Because of the simplifying assumptions, and the superior quality of the data (no contamination, signal-to-noise issues, etc.), realistic expectations for HETDEX is to directly constrain $\sigma_8h^{-1}$ to better precision than other methods (\eg, CMB, WL, X-ray) seems bleak.
-For example \cite{deHaan2016} constrain $\sigma_8h^{-1}$ to $\sim5$\% using a sample of 337 SZE detected clusters from the SPT-SZE survey.
+For example, \cite{deHaan2016} constrain $\sigma_8h^{-1}$ to $\sim5$\% using a sample of 337 SZE detected clusters from the SPT-SZE survey.
 For the $\sim1500$ clusters detected with survey observations to constrain $\sigma_8h^{-1}$ and to be dominated by cluster statistics alone ($\Delta \ln N \sim N^{-1/2}$), the absolute cluster calibration would need to be better than 2.5\%.
@@
 
-\subsection{Extendability to Other Surveys}
+\subsection{Calibration of the Richness-Cluster Mass Relation}
 Large-scale optical surveys (\eg, DES and LSST) expect to detect hundreds of thousands of galaxy clusters at $z < 1$.
-Because they are photometric, a major challenge for these surveys is relating a cluster observable to the total dark-matter mass.
-One promising mass estimator is the optical richness \citeeg{Abell1958}.
+Because they produce photometry only, a major challenge for these surveys is relating a cluster observable to the total DM mass.
+One promising cluster mass estimator is the optical richness \citeeg{Abell1958}.
 Specifically, here, we use $\lambda$, the weighted number of galaxies within a scale aperture \citeeg{Rozo2011} as calculated by the redMapper algorithm \citep{Rykoff2012}.
 Previous works \citeeg{Rozo2010} show that the richness correlates strongly with cluster mass on the average, but the absolute mass scale of the optical richness mass estimator and the scatter in cluster mass at fixed optical richness are imprecisely known \citep{Rykoff2012}.
-These systematics remain the major source of uncertainty in deriving cosmological constraints from cluster abundances and must be measured using independent methods to realize the full potential of these surveys.
+These systematics remain the major source of uncertainty in deriving cosmological constraints from cluster abundances and must be measured using independent methods to realize the full potential of these types of surveys.
 
 \begin{figure} 
-	\includegraphics[width=\columnwidth]{figures/massRichness_targeted.pdf} 
-	\caption{The optical richness, $\lambda$, versus the predicted cluster mass.
-The purple and blue points represent clusters with targeted and survey detections respectively.
-Error bars show $1\sigma$ prediction interval.
-The solid and dashed lines are fits to either the targeted or survey sets.
-} \label{fig:mass richness}
+	\includegraphics[width=\columnwidth]{figures/massRichness.pdf} 
+	\caption{\emph{Top}: The optical richness, $\lambda$, versus the predicted cluster mass.
+The solid, colored line is the median predicted mass for the targeted observing, and the colored, dashed line is the median recovered mass for the HETDEX-like observations.
+The shaded regions represent the 68\% scatter around the median values.
+\emph{Bottom}: The scatter in the relation at fixed richness.
+The solid black line shows the intrinsic scatter of $\sigma_{true}=0.25$ dex.
+Color coding is the same as the top panel.
+\emph{Inset}: The evolution of the intrinsic scatter versus the average recovered scatter, $\sigma_{rec}$.
+We find good agreement when intrinsic scatter is $\sim0.25$ dex.} \label{fig:mass richness}
 \end{figure}
 
-We leverage the large spectroscopic dataset of HETDEX to estimate its ability to constrain the scatter and absolute scale of the richness-mass relationship.
-We begin by cross matching both the targeted and survey observations with a redMapper catalog.
-The redMapper catalog is limited to $\lambda >= 20$, or at least twenty object assigned to each cluster.
-With the targeted and survey observations, we observe 138 and 58 clusters respectively.
+The Buzzard cluster catalogs do not contain measurements of $\lambda$, so we supplement it by generating richnesses based on the true cluster masses.
+For testing we assume two versions of the richness-mass relationship.
+\cite{Farahi2016} base the relation on stacked velocity dispersions, and \cite{Simet2016} use weak lensing measurements to construct their relation.
+Because we are investigating HETDEX's ability to recover the underlying scatter in the mass-richness relationship, we use the true cluster masses perturbed by a known amount to estimate the observed richness.
 
-Figure \ref{fig:mass richness} shows the optical richness, $\lambda$, versus the predicted cluster mass.
-The cluster masses are the $ML_{\sigma, z, N_{gal}}$ based and correspond to the correct observation strategy.
-The error bars represent the $1\sigma$ prediction intervals for each cluster mass.
-The solid and dashed lines are fits to the targeted and survey datasets.
-For comparison, the richness-mass relations from \cite{Rykoff2012} (their equation B5) is shown as a dash-dotted line.
+As a check, after generating richness values we calculate the scatter of the masses at fixed $\lambda$, $\sigma_{M|\lambda}$ by comparing the true, unperturbed cluster masses against the richness and find that we do recover the expected scatter.
+We repeat the process with both assumed richness-mass relationships and recover the expected scatter in both instances.
 
-To generate the best fitting lines we follow the general procedure of \cite{Hogg2010}, by defining an objective function and then minimizing the loss. Our loss function is
-\begin{equation}
-	\mathrm{ln}L= \frac{-1}{2} \bigg{(} \sum^N_{i=1}\frac{[y_i - mx_i - b]^2}{\sigma_{y,i}} + \sum^N_{i=1}\frac{[y_i - mx_i - b]^2}{\sigma_{x,i}} \bigg{)}
+Figure \ref{fig:mass richness} summarizes the main results of this investigation.
+The top panel shows the generated optical richness, $\lambda$, versus the predicted cluster mass.
+The cluster masses are the $ML_{\sigma, z, N_{gal}}$ based and correspond to the targeted and survey observation strategies.
+The bottom panel of Figure \ref{fig:mass richness} shows the scatter in the predicted cluster masses at fixed richness, $\sigma_{M|\lambda}$.
+The solid line represents the intrinsic amount of scatter added to the masses.
+The cluster masses are binned in increasing ten richness intervals ($10-20$, $20-30$, etc.).
+The inset upper panel shows the intrinsic scatter versus the recovered average scatter at fixed richness, $\langle \sigma_{M|\lambda} \rangle$ and illustrates how well the two observation strategies recover the intrinsic scatter.
+
+We exclude clusters with $\lambda>130$ both because there are very few of them which does not accurately reproduce a scatter and because the observational studies which we base our richnesses on do not include these clusters.
+We find that we are able to accurately recover an average intrinsic scatter of $0.2 <\langle \sigma_{M|\lambda} \rangle <0.3$ dex, finding $\langle \sigma_{M|\lambda} \rangle = 0.255\pm{0.02}$ at $\sigma_{true} = 0.25$ with survey observations.
+This is very promising as other observational studies have estimated the intrinsic scatter of real clusters to be $\sim0.25$ dex \citeeg{Rozo2014, Rozo2015}.
+As the intrinsic scatter increases or decreases, we fail to recover the scatter as accurately.
+
+To get an idea of how well HETDEX will constrain the absolute mass scale we can find the best fitting relation to our richness-mass data.
+To generate the best fitting lines we follow the general procedure of \cite{Hogg2010}, by defining an objective function and then minimizing the loss.
+Our objective function is
+\begin{equation}\label{eq:objectivei}
+p(y_i|x_i,\sigma_{yi},m,b,\sigma) = \frac{1}{\sqrt{2\,\pi\,(\sigma_{yi}^2+\sigma^2)}}
+ \,\exp\left(-\frac{[y_i - m\,x_i - b]^2}{2\,(\sigma_{yi}^2+\sigma^2)}\right)
 \end{equation}
-where we have taken into account the uncertainties in both the richness and predicted cluster mass.
-We again rely on MCMC samples to sample the posterior probability distribution.
+where we consider both measurement errors in $y_i$, $\sigma_{yi}$, and intrinsic scatter, $\sigma$, in the relation between $x_i$ and $y_i$.
+We assume that the intrinsic scatter is constant from point to point and that all of the measurement errors are Gaussian.
+We convert this objective function into a likelihood by multiplying all of the individual probabilities together,
+\begin{equation}\label{eq:like}
+\mathscr{L} = \prod_{i=1}^N \ p(y_i|x_i,\sigma_{yi},m,b, \sigma).
+\end{equation}
+We again rely on MCMC samples to sample the posterior probability distribution and thus maximize the likelihood.
 The best fitting slope and intercept are quoted as the median value of the posterior probability distribution with 68\% error bars defined as the 16th and 84th percentiles of the same distribution.
 
-Following the notation of \cite{Rykoff2012} we find a best-fitting relation for the targeted observations as
+For a richness-mass relation with an intrinsic scatter of $\langle \sigma_{M|\lambda} \rangle = 0.25$, and following the more traditional parameterization of the richness-mass relation \citeeg{Rykoff2012, Farahi2016}, we find a best-fitting relation for the targeted observations as
 \begin{equation}
-	ln\bigg{(}\frac{M_{200c}}{h_{70}^{-1} 10^{14}\Msol}\bigg{)} = 1\pm0.13 + 1.34\pm0.17 ln\bigg{(}\frac{\lambda}{60}\bigg{)} \nonumber
+	\ln\bigg{(}\frac{M_{200c}}{h_{70}^{-1} 10^{14}\Msol}\bigg{)} = 0.09\pm0.01 + 0.90\pm0.01 \ln\bigg{(}\frac{\lambda}{60}\bigg{)}
 \end{equation}
@@
 \begin{equation}
-	ln\bigg{(}\frac{M_{200c}}{h_{70}^{-1} 10^{14}\Msol}\bigg{)} = 1.02\pm0.13 + 0.96\pm0.22 ln\bigg{(}\frac{\lambda}{60}\bigg{)} \nonumber
+	\ln\bigg{(}\frac{M_{200c}}{h_{70}^{-1} 10^{14}\Msol}\bigg{)} = 0.31\pm0.02 + 0.77\pm0.02 \ln\bigg{(}\frac{\lambda}{60}\bigg{)}.
 \end{equation}
-
-The bottom panel of Figure \ref{fig:mass richness} shows the scatter in cluster masses at fixed richness, $\sigma_{M|\lambda}$.
-The solid and dashed lines represent the targeted and survey observations respectively, and have been offset from one another for clarity.
-The cluster masses are binned in increasing ten richness intervals ($20-30$, $30-40$, etc.).
-The two horizontal lines show the mean scatter of 0.26 dex for the targeted observations and 0.21 dex for the survey observations.
-While not shown in the figure, we find a mean scatter of 0.27 dex if we replace $M_{pred}$ with the true cluster mass for the clusters identified with targeted observations.
-The reduction in scatter from the targeted to survey observations is due to fewer objects detected in survey mode.
+This gives $M_{200c} = (1.09\pm0.01)\times10^{14} h^{-1}$ \Msol  and  $M_{200c} = (1.36\pm0.03)\times10^{14}h^{-1}$ \Msol\ at $\lambda=40$ for the targeted and survey observations respectively.
+If the intrinsic scatter is reduced to $\sim 0.05$ dex we recover an overall normalization of $M_{200c} = (1.6\pm0.02)\times10^{14} h^{-1}$ \Msol\ and $M_{200c} = (1.65\pm0.03)\times10^{14} h^{-1}$ for the targeted and survey observations at $\lambda=40$.
+In both cases, this normalization differs significantly from the $M_{200c} \approx 2.1\times10^{14} h^{-1}$ \Msol\ found in recent work by \cite{Li2016, Simet2016}.
 
@@
 Here, we present detailed simulations of the upcoming HETDEX survey's applicability to the detection and total mass measurement of galaxy clusters.
-We use mock galaxy catalogs, and simulated HETDEX-like observational strategies to estimate the number of clusters observed and the precision of their total mass estimates, using three different mass estimates.
-With an eye to galaxy cluster studies, we discuss potential improvements to the HETDEX survey, and comment on how HETDEX may improve current and future photometric large-area sky surveys' cluster mass estimates derived from optical richness.
+We use mock galaxy catalogs, and simulated, HETDEX-like observational strategies to estimate the number of clusters observed and the precision of their total mass estimates, using three different cluster mass estimators.
+We discuss HETDEX's ability to constrain the cosmological parameter $\sigma_8 h^{-1}$ and comment on how HETDEX may improve current and future photometric large-area sky surveys' cluster mass estimates derived from optical richness.
 
@@
 \begin{enumerate}
-	\item HETDEX-like observations do a good job observing galaxy clusters.
-The number of galaxy clusters detected in the HETDEX-like observations is almost exact 4.5 times less than in the targeted observations.
-This difference is the same as the overall HETDEX fill factor.
-	\item Overall, we find that a traditional power-law conversion from LOSVD to cluster mass performs significantly poorer than either the probability based or ML based methods also tested.
-We find the MAE and RMSE of survey detected cluster mass estimates to be approximately 38\% and 65\% respectively, compared to approximately 123\% when a power-law is used alone.
-	\item While the power-law may be outperformed, overall, comparisons of similar mass galaxy clusters shows that above Log M $=14.5$ \Msol, the power-law gives a lower MAE than either the probability based or ML based methods.
-For HETDEX-like observations and clusters with $13 < Log M <14.5$ \Msol, we find the $ML_{\sigma, z, N_{gal}}$ method performs the best.
-Below Log M $=13$ \Msol\ no method with survey observations gives an MAE of less than 50\%.
-	\item For followup targeted observations only galaxy clusters with masses inferred to be Log M $<13$ \Msol\ from survey observations should be targeted.
-Galaxy clusters with inferred masses below Log M $=13$ \Msol\ can see as much as an 81\% improvement in cluster mass estimation with targeted observations.
-While the improvement of clusters with masses above Log M $=13$ \Msol\ is often approximately 10\%.
-	\item \editorial{Something about the richness.}
+	\item We find approximately 14000 clusters with at least five cluster members in the HETDEX cluster survey volume.
+Of those, approximately 1500 clusters are detected with HETDEX-like survey observations.
+The number of cluster members recovered is almost exactly 4.5 times fewer than a fully targeted survey, across both a wide range of redshifts and cluster masses.
+	\item Overall, we find a traditional power-law conversion from LOSVD to cluster mass performs significantly poorer than either the probability based or ML based methods also tested.
+The probability based and ML based cluster mass estimators are able to more accurately predict cluster mass when combined with information other than just the LOSVD.
+While the power-law may be outperformed, overall, comparisons of similar mass galaxy clusters shows that above Log M/\Msol\ $=14.5$, the power-law gives a lower bias than either the probability based or ML based methods.
+For HETDEX-like observations and clusters with $13 < \mathrm{Log}\, M/\Msol <14.5$, we find the $ML_{\sigma, z, N_{gal}}$ method performs the best.
+Below Log M/\Msol\ $=13$ no method with survey observations gives an bias of less than 50\%.
+	\item For followup targeted observations only galaxy clusters with masses inferred to be Log M/\Msol\ $<13$ from survey observations should be targeted.
+Galaxy clusters with inferred masses below Log M/\Msol\ $=13$ can see as much as an 81\% improvement in cluster mass estimation with targeted observations.
+While the improvement of clusters with masses above Log M/\Msol\ $=13$ is often approximately 10\%.
+	\item For a cluster survey limited to $M > 10^{14}$ \Msol\, HETDEX's ability to constrain the cosmological parameter $\sigma_8 h^{-1}$ is at best $\sim20\%$.
+This is significantly different than recent constraints from SZE surveys.
+	\item HETDEX will be able to place important constraints on the amount of scatter in the optical richness-mass relationship.
+It will to a less extent constrain the overall normalization of the relation.
+This should provide an important too in the calibration of large-area sky surveys which rely on photometric data only to estimate cluster masses.
 \end{enumerate}

### 2016-05-04 ms.tex
add extra math symbols
first big round of Casey comments

@@
 \usepackage{amssymb}	% Extra maths symbols
-\usepackage{mathrsfs}
+\usepackage{mathrsfs}	% Extra extra math symbols
 \usepackage{natbib}
@@
 Using both observing strategies, we produce cluster mass probability density functions $P(M_{200c}|\vec{x})$ of a cluster mass ($M_{200c}$) as a function of an observable parameter or set of observable parameters, $\vec{x}$, where we consider cases of where $\vec{x} = \{\sigma\}$, $=\{\sigma, z\}$, and $=\{\sigma,z, N_{gal}\}$ for velocity dispersion, $\sigma$, redshift, and number of observed galaxies, $N_{gal}$.
-\editorial{This sentence will summarize how well HETDEX will do, and how that might be improved with targeted observations.}
+\editorial{This sentence will summarize how well HETDEX will do, and how that might be improved with Targeted observations.}
 \end{abstract}
 
-\section{Introduction}
-Our ability to perform precision cosmology with clusters of galaxies has reached a critical turning point.
-The widely accepted $\Lambda$CDM model of cosmology makes explicit predictions about the number and masses of galaxy clusters throughout the universe.
-However, connecting these predictions to a set of, sufficiently large in size, observed clusters remains a principal problem.
-Specifically, the largest threat to modern, precision, cluster cosmology is not the identification of large numbers of clusters (the total number of clusters known is only going up) but the accurate recovery of galaxy cluster mass \citeeg{Sehgal2011,Plank2014, Bocquet2015}.
+\section{Introduction}\label{sec: Introduction}
+Our ability to perform precision cosmology with clusters of galaxies has reached a critical point.
+The widely accepted $\Lambda$CDM model of cosmology makes explicit predictions about the mass function of galaxy clusters in the universe.
+Measuring this mass function across many redshifts, in turn, provides constraints on the cosmology.
+Today, large-area sky surveys are providing observations of large numbers of clusters, but systematics in deriving cluster masses dominate the error budget \citeeg{Sehgal2011,Plank2014, Bocquet2015}.
+To place further constraints on the $\Lambda$CDM model of cosmology, we must decrease these systematics.
 
 As mass is not a direct observable, a lot of work is underway to characterize galaxy cluster masses with an observable feature of galaxy clusters.
-The goal is to constrain, as best possible, $P(M|z, X)$ the probability ($P$) that a galaxy cluster of given mass ($M$), located at redshift ($z$) determined using observable parameter ($X$).
+The goal is to constrain, as best possible, $P(M|z, \vec{x})$ the probability ($P$) that a galaxy cluster of given mass ($M$), located at redshift ($z$) determined using an observable parameter or parameters ($\vec{x}$).
 Generally, cluster mass calibrations fall into two distinct camps, simulation based and direct or statistical calibration.
@@
 This recipe has two distinct but not always independent tracks.
-The ``direct'' method uses direct observations of a small set of clusters and then uses known mass estimators, X-ray temperatures and luminosities \citeeg{Mantz2010, Rykoff2014}, cosmic microwave background (CMB) observations \citeeg{Vanderlinde2010, Sehgal2011}, optical richness \citeeg{Abell1958, Rykoff2012} or weak lensing (WL; \eg\ \citealt{Rozo2010}) as examples, which provide a ``true'' mass.
+The ``direct'' method uses direct observations of a small set of clusters and then uses known mass estimators, including X-ray temperatures and luminosities \citeeg{Mantz2010, Rykoff2014}, cosmic microwave background (CMB) observations \citeeg{Vanderlinde2010, Sehgal2011}, optical richness \citeeg{Abell1958, Rykoff2012} or weak lensing (WL; \eg\ \citealt{Rozo2010}) as examples, which provide a ``true'' mass.
 This directly calibrates the observable--mass relation which is then applied to a much larger sample.
@@
 X-ray based cluster masses assume hydrostatic equilibrium \citeeg{Mantz2015} which may only be valid for a very small number and range of cluster masses.
-The Sunyaev--Zel'dovich Effect (SZE; \citealt{Sunyaev1972}), which uses the up--scattering of CMB photons to estimate cluster masses, provides accurate estimations of mass, but the ability to detect low mass galaxy clusters is currently limited by technology \citeeg{Carlstrom2002a}.
+The Sunyaev-Zel'dovich Effect (SZE; \citealt{Sunyaev1972}), which uses the up-scattering of CMB photons to estimate cluster masses, provides accurate estimations of mass, but the ability to detect low mass galaxy clusters is currently limited by technology \citeeg{Carlstrom2002a}.
 WL estimates are, in principle, correct in the mean, but they suffer from signal-to-noise requirements, limiting their usefulness in low mass clusters, and potentially suffer from line-of-sight effects as WL is sensitive to all mass along the line-of-sight.
-Virial mass estimators which determine the cluster mass based on the motions of the member galaxies \citeeg{Ruel2014, Sifon2015} are promising in that it is a direct measurement of the depth of clusters potential well, but suffers from systematics due to cluster formation physics which disrupts the velocity field.
+Virial mass estimators which determine the cluster mass based on the motions of the member galaxies \citeeg{Ruel2014, Sifon2015} are promising in that it is a direct measurement of the depth of clusters potential well, but suffer from systematics due to cluster formation physics which disrupts the velocity field.
 
@@
 
-While a large portion of the $\sim10^6$ interloping [\ion{O}{ii}] galaxies will be field (not associated with a bound structure) galaxies, the large area covered by HETDEX is expected to contain as many as 50 Virgo-sized ($M_{dyn}>10^{15}$ \msol) clusters at $z<0.5$.
+While a large portion of the $\sim10^6$ interloping lower redshift galaxies will be field (not associated with a bound structure) galaxies, the large area covered by HETDEX is expected to contain as many as 50 Virgo-sized (halo mass $>10^{15}$ \msol) clusters at $z<0.5$.
 The near-complete spectroscopic coverage allows an unprecedentedly detailed look at a very large number of clusters ranging from group scales to the very massive.
 In addition to the recovery of accurate dynamical masses, detailed investigations of the of dynamical state of the clusters is possible.
-
-Connecting the dynamical properties derived from spectroscopy to the properties inferred from other studies insures the greatest impact on future work.
-HETDEX overlaps with the Sloan Digital Sky Survey (SDSS; \citealt{Blanton2001a}), SDSS stripe 82 \citep{Annis2014}, DES, the \emph{Spitzer}/HETDEX Exploratory Large-Area Survey (SHELA; \citealt{Papovich2016}), and the \emph{Spitzer} IRAC Equatorial Survey (SpIES; Timlin \etal\ 2016, ApJ, submitted).
-While the potential dataset is very rich, two large issues remain.
 
@@
 We create and evaluate a HETDEX like selection ``function'' of galaxies over a similarly large portion of the sky and use well adopted techniques to recover the dynamical properties, such as velocity dispersion and cluster mass.
+In addition to standard techniques of cluster mass estimation, we investigate probability based and machine learning based approaches of cluster mass prediction.
 We compare these results to a series of targeted galaxy cluster observations, where each member galaxy is assumed to be observed.
@@
 In this section, we describe the data products and the techniques used to replicate the HETDEX survey.
-We use the information from a large mock galaxy catalog supplemented by galaxies from the SDSS to create a realistic ``sky'' and ``observe'' it with a HETDEX-like observing strategy.
+We use the information from a large mock galaxy catalog enhanced by the emission line properties of galaxies in the SDSS to create a realistic ``sky'' and ``observe'' it with a HETDEX-like observing strategy.
 
@@
 \textit{Right}: Probability histograms of the Log [\ion{O}{ii}] luminosity for the SDSS galaxies located in the two highlighted regions on the right.
-New [\ion{O}{ii}] luminosity (and subsequently fluxes) are assigned to catalog galaxies from slice sampling the probability histogram.
-See the text for a full description of the process.} \label{fig: oii sdss}
+The [\ion{O}{ii}] luminosities are assigned to catalog galaxies from slice sampling the probability histogram and converted to fluxes using the redshift of each galaxy.} \label{fig: oii sdss}
 \end{figure*}
 
-The Buzzard mock galaxy catalogs (R.
-Wechsler et al., private communication) cover 398.49 \degsq\ between $4^h< RA < 6^h$ and $-61\degree < DEC < -41\degree$ and are derived from a combination of Sub-halo Abundance Matching (ShAM) and ADDSEDs (Adding Density Dependent Spectral Energy Distributions) tied to an in house n-body cosmological simulation.
+The Buzzard mock galaxy catalogs cover 398.49 \degsq\ between $4^h< RA < 6^h$ and $-61\degree < DEC < -41\degree$ and are derived from a combination of Sub-halo Abundance Matching (ShAM) and ADDSEDs (Adding Density Dependent Spectral Energy Distributions) tied to an in house n-body cosmological simulation.
 A brief description of the catalog creation is described as follows.
@@
 
-\subsection{ {\rm[\ion{O}{ii}]} Luminosity}\label{sec: oii luminosity}
-The Buzzard ``truth'' catalog does not provide [\ion{O}{ii}] luminosities so we must assign them empirically.
-We use 503113 galaxies from the SDSS Data Release 12 \citep{Alam2015} from $z = 0.05 - 0.2$, which are selected with no redshift warning, and place each galaxy on a color-magnitude diagram (CMD) of $M_r$ and $g-r$; see the left panel of Figure \ref{fig: oii sdss}.
+\subsection{Conditional [\ion{O}{ii}] Flux Probability Distribution Functions}\label{sec: oii luminosity}
+We use the SDSS DR12 \citep{Alam2015} catalogs to assign [\ion{O}{ii}] emission line strengths to the galaxies in the Buzzard catalog.
+We use 503113 galaxies from $z = 0.05 - 0.2$, which are selected with no redshift warning, and place each galaxy on a color-magnitude diagram (CMD) of $M_r$ and $g-r$; see the left panel of Figure \ref{fig: oii sdss}.
 
@@
 We extract all of the SDSS galaxies inside that bin and create a histogram of their [\ion{O}{ii}] luminosities, the right panel of Figure \ref{fig: oii sdss}.
-Using a slice sampling technique \citep{Neal1997} we assign the catalog galaxy an [\ion{O}{ii}] luminosity based on the distribution of SDSS galaxies extracted.
-For catalog galaxies which are placed on the CMD near no, or very few ($1\leq n<10$) galaxies we assign it zero [\ion{O}{ii}] luminosity or the mean luminosity, respectively.
-We find no evidence of a significant bias due to galaxies being assigned zero [\ion{O}{ii}] luminosity.
-For the galaxies in the Buzzard catalog, 1.3\% of the galaxies brighter than $\sdssg = 22$ mag (HETDEX's detection limit) have exactly zero [\ion{O}{ii}] luminosity.
-Of the 1.3\%, only 3.3\% (0.05\% of all galaxies) have $g-r < 1.5$.
+Using a slice sampling technique \citep{Neal1997} we assign the catalog galaxy an [\ion{O}{ii}] luminosity based on the distribution of SDSS galaxies in that bin.
+In very few cases (1.3\% of galaxies) do the $g-r$ and $M_r$ magnitudes of the galaxies in the Buzzard catalog not overlap with the distributions in SDSS.
+For these objects, we assign them zero [\ion{O}{ii}] flux, but this has no impact on our analysis.
+For catalog galaxies with have very few ($1\leq N<10$) SDSS galaxies in their respective bin, we assign it the mean [\ion{O}{ii}] flux.
 
-The left panel of Figure~\ref{fig: oii sdss} shows the CMD of all SDSS galaxies.
-Two potential catalog galaxies are also placed on the CMD ($M_r, g-r = -17.7,~0.49$ and $M_r, g-r = -21.4,~1.24$) and indicated by the two colored boxes.
-The histograms show in the Figure's right panel show the probability density histograms of the Log [\ion{O}{ii}] luminosity for the SDSS galaxies in the 2D bin around the individual catalog galaxies.
-We sample the distribution and assign each catalog galaxy an [\ion{O}{ii}] luminosity which is then converted into a flux.
+Figure~\ref{fig: oii sdss} illustrates this process.
+The numbered boxes in the left panel show two bins ($M_r, g-r = -17.7,~0.49$ and $M_r, g-r = -21.4,~1.24$) in the CMD of $0.05 < z < 0.2$ SDSS galaxies.
+The right panel shows the Log [\ion{O}{ii}] luminosity distribution functions, $p($[\ion{O}{ii}]$| M_r, g-r)$, which we use to assign [\ion{O}{ii}] luminosity to each object.
+The luminosity is then converted into an [\ion{O}{ii}] flux through
+\begin{equation}
+	F = \frac{L}{4\pi D_L}
+\end{equation}
+where $D_L$ is the luminosity distance \citeeg{Hogg2010}.
 
-\subsection{Mock Observations}\label{sec: observations}
+\subsection{HETDEX}\label{sec: hetdex}
 \begin{figure} 
@@
 
-HETDEX will perform blind spectroscopy (R $\sim$ 750 in $3500 - 5500~\AAA$) over two fields along the celestial equator.
-The 300 \degsq, spring field and 120 \degsq\ fall field will have no preselected targets.
-Using VIRUS on the 10-m Hobby-Eberly Telescope \citep{Ramsey1998} the completed survey is expected to have an overall fill-factor of 1/4.5, meaning that the entire area could be covered with 4.5 dithers of the entire survey.
+\editorial{There are quite a few words copied from Casey's SHELA paper.}
+HETDEX will perform a blind survey which will measure the redshifts of $8 \times \sim 10^5$ Ly$\alpha$ emitting galaxies (LAEs) between $1.9 < z < 3.5$ using a collection of 78 wide-field IFUs spectrographs covering the wavelength region $3500 - 5500$~\AAA\ at R $\sim$ 750 \citep{Hill2008}.
+The goal of these observations will be to provide sub-percent level measurements of the Hubble expansion parameter and the angular diameter distance at $z \sim 2$ via the large scale distribution of galaxies in the redshift range of HETDEX.
+The result will be a significant constraint on the evolution of dark energy that is competitive with (and independent of) values based on surveys of the Ly$\alpha$ forest.
+
+The entire HETDEX survey will cover 420 \degsq\ with a 1/4.5 filling factor over two fields: a $\sim 300$ \degsq\ northern field, and a $\sim 140$ \degsq\ equatorial region.
+The $10 \sigma$ detection limit for these spectra will be $3.5\times10^{-17}$ \ergscm\ at 5000 \AAA, or equivalently for continuum objects, $g = 21.9$ mag.
+The spectral coverage allows for the detection of [\ion{O}{ii}] ($\lambda\lambda 3727,3729$) emitters to $z\sim 0.5$ and Ca H ($\lambda 3968.5$) and K ($\lambda 3933.7$) absorption features to $z\sim 0.4$.
 
@@
 
+\subsection{Mock Observations}\label{sec: observations}
 This means that when selecting galaxies from the Buzzard catalog we assume an observation for all galaxies laying within a colored, IFU square in Figure~\ref{fig: ifu layout}.
@@
 
-The spectral coverage allows for the detection of [\ion{O}{ii}] ($\lambda\lambda 3727,3729$) emitters to $z\sim 0.5$ and Ca H ($\lambda 3968.5$) and K ($\lambda 3933.7$) absorption features to $z\sim 0.4$.
-HETDEX is expected to detect sources with continuum brighter than $\sdssg=22$ mag, and emission line strengths above $3.5\times10^{-17}$ \ergscm.
-
-In this work we consider two separate observing strategies, targeted and survey-like.
-The targeted observations use ``direct'' observations where each cluster is targeted individually, and every cluster member galaxy is assumed to be observed.
-The survey observations mimic the HETDEX observation pattern across the sky, where no cluster is directly targeted and not all cluster member galaxies are observed.
-Both of these observations have HETDEX-like galaxy detection thresholds, and for comparison we also include a set of targeted observations with ``perfect'' knowledge.
+In this work we consider two separate observing strategies, Targeted and Survey-like.
+The Targeted observations use ``direct'' observations where each cluster is targeted individually, and every cluster member galaxy is assumed to be observed.
+The Survey observations mimic the HETDEX observation pattern across the sky, where no cluster is directly targeted and not all cluster member galaxies are observed.
+Both of these observations have HETDEX-like galaxy detection thresholds, and for comparison we also include a set of Targeted observations with ``perfect'' knowledge.
 Perfect observations assume no detection threshold, if a cluster member galaxy is observed, it is also detected.
 This provides an important best-case scenario, and differs from the true cluster properties because the cluster properties are still calculated.
-These observations provide three levels of quality with ``perfect knowledge'' being the highest and survey being the lowest.
+These observations provide three levels of quality with ``Perfect knowledge'' being the highest and Survey being the lowest.
 
 \section{Recovery of Parameters}\label{sec:recovery}
- In the following sections, we outline the methods we use to derive the dynamical properties of the galaxy clusters in our sample.
-This is not meant to be an exhaustive study of the different methods used to recover these parameters.
+In the following subsections, we outline the methods we use to derive the dynamical properties of the galaxy clusters in our sample.
 The following is, in many cases, a subset of the available methods to derive any single parameter.
@@
 
-In simple terms, the cluster redshift is the mean of the redshifts of all galaxies associated with the cluster.
-For this work we rely on the biweight location estimator \citep{Beers1990} because it is resistant to outlying galaxies.
+In simple terms, the cluster redshift is the mean of the redshifts of all galaxies associated with the cluster, where the mean is the first moment of the velocity (redshift) distribution function $p(z)$.
+In practice, the first moment is strongly subject to outliers, so we rely instead on the biweight location estimator \citep{Beers1990} through\footnote{Implemented as part of the {\sc astLib} Python library.
+See \hbox{\url{http://astlib.sourceforge.net}}}:
+\begin{equation}
+C_{BI} = M + \frac{\sum_{|u_i| < 1} (x_i - M)(1-u_i^2)^2}{\sum_{|u_i| < 1}(1-u_i^2)^2}
+\end{equation}
+where $x_i$ are the individual redshifts, $M$ is the median redshift and $u_i$ is given by:
+\begin{equation}
+	u_i = \frac{(x_i - M)}{c\mathrm{MAD}}
+\end{equation}.
+MAD is the median absolute deviation, also defined in \cite{Beers1990}, and $c$ is the a tuning constant.
+We choose $c=6$ (the suggested value) which balances computational speed and location accuracy.
+
 Although this work assumes that we know each galaxy's redshift to infinite precision, in practice, we find a simple weighted mean provides a reliable estimate of $z_c$ when there are uncertainties on the individual galaxy redshifts.
@@
 \subsection{Line-of-Sight Velocity Dispersion}\label{sec: LOSVD}
-We first calculate the LOSV to each galaxy, where
+We calculate the LOSV to each galaxy, where
 \begin{equation}
-	LOSV = c\frac{z - z_c}{1+z_c}
+	\mathrm{LOSV} = c\frac{z - z_c}{1+z_c}
 \end{equation}
@@
 
-The line-of-sight velocity dispersion (LOSVD) is calculated using a method of maximum likelihood following \cite{Walker2006}. We maximize the probability function 
+We follow the maximum likelihood method of \cite{Walk2006} to estimate the line-of-sight velocity dispersion (LOSVD). We maximize the probability function 
 \begin{equation}\label{eq: jointGaussian}
@@
 We draw twenty thousand samples from the posterior probability distribution using simple priors, $\langle\mu\rangle$ lies between the maximum and minimum LOSV and $0< \sigma_p < 1400$ \kms.
+We set the upper limit on the LOSVD as the LOSVD corresponding to a $10^{16}$ \Msol\ cluster at $z\sim0.0$, higher mass than any expected cluster.
 When the full distribution of LOSVDs is not used, the final LOSVD is quoted as the median value of the posterior probability distribution with 68\% error bars defined as the 16th and 84th percentiles of the same distribution.
@@
 In principle, a single statistic such as the biweight scale estimator or the gapper estimator (both from \citealt{Beers1990}) with many bootstrap resamplings could be used to construct a distribution of $\sigma_p$.
-In simple tests where the values of both $\sigma_p$ and $\langle\mu\rangle$ are known.
-The 68\% error bars derived from the MCMC method give slightly better results with the true LOSVD value bracketed by the error bars in $\sim68\%$ of the cases versus $\sim57\%$ with bootstrapping and a single statistic.
-In addition, we prefer the maximum likelihood method for its straight forward treatment of the errors in the LOSV measurements, which will become important in future observations of real clusters \citeeg{Boada2016a}.
+In simple tests where the values of both $\sigma_p$ and $\langle\mu\rangle$ are known, the 68\% error bars derived from the MCMC method give slightly better results with the true LOSVD value bracketed by the error bars in $\sim68\%$ of the cases versus $\sim57\%$ with bootstrapping and a single statistic.
+In addition, we prefer the maximum likelihood method for its straight forward treatment of the errors in the LOSV measurements, which will become important in the practical application to real data \citeeg{Boada2016a}.
 
-\subsection{Dynamical Mass from Scaling Relations}\label{sec: mass}
-The relationship between the LOSVD and cluster dynamical mass has been the focus of several studies \citeeg{Evrard2008, Saro2013, Sifon2013, VanderBurg2014}, and a best fitting relationship for the mass enclosed by $r_{200c}$ of the form
+\subsection{Estimates of Cluster Mass}\label{sec: mass}
+\subsubsection{Power Law Based Method}
+The relationship between the LOSVD and cluster dynamical mass has been the focus of several many \citeeg{Evrard2008, Saro2013, Sifon2013, VanderBurg2014}, where the relationship for the mass enclosed by $r_{200c}$ takes the form
 \begin{equation}\label{eq:power law}
@@
 Specifically, while there is little difference between using galaxies and their host DM subhalos, there is a significant over estimation of the LOSVD when using galaxies/subhalos compared to DM particles \citep{Munari2013}.
-We follow other works \citeeg{Kirk2015, Sifon2015a} using the scaling relation, given in Equation~\ref{eq:power law} from \cite{Munari2013} to facilitate comparisons with other observational studies, which rely on galaxies are tracers.
-% \editorial{This all needs to be stripped out and reworked.}
-% The choice $A_{1D}$ and $\alpha$ varies between studies \citeeg{Munari2013, VanderBurg2014} and should be calibrated on a individual basis.
-To do this, we randomly select 47494, $z<0.5$ clusters composed of 36000 $10^{13}$, 6000 $10^{14}$ and two $10^{15}~\Msol$ halos.
-We perform a linear fit to the $\sigma_{1D}-M_{200}$ values allowing both $A_{1D}$ and $\alpha$ to vary.
-We find best fitting parameters of $A_{1D} = 1117.9~\kms$ and $\alpha = 0.3297$, both of which are very near the values from \cite{Evrard2008} of $A_{1D} = 1082.9 \pm 4.0~\kms$ and $\alpha = 0.3361$.
-Therefore, we chose to adopt the parameters from \cite{Evrard2008} to better facilitate with other simulations \citeeg{Old2014}, and observational studies \citeeg{Brodwin2010}.
+We follow other works \citeeg{Kirk2015, Sifon2015a} using the scaling relation, given in Equation~\ref{eq:power law} from \cite{Munari2013} to facilitate comparisons with other observational studies, which rely on galaxies as tracers.
 
-\subsection{Other Estimates of Dynamical Mass}
+\subsubsection{Other Estimates of Dynamical Mass -- Introduction}
 In this section we use two methods to predict the mass of a cluster based on other observables.
-Often the cluster mass is estimated based on a single observable, X-ray temperature, LOSVD, richness and others.
+Often the cluster mass is estimated based on a single observable, X-ray temperature, LOSVD, richness and others (see Section~\ref{sec: Introduction} for referenced examples).
 Here we combine many observables to attempt to correct the mass inferred solely from the velocity dispersion.
-The first method is traditional probability based where we marginalize over a series of observables to find the most probable cluster mass.
-The second is based on a machine learning (ML) algorithm which attempts to ``learn'' the relationship between the observables and the desired output, the cluster mass.
+The first method is traditional ``probability based'' where we marginalize over a series of observables to find the most probable cluster mass.
+The second is based on a machine learning (ML) algorithm which attempts to infer the relationship between the observables and the desired output, the cluster mass.
 Both of these methods are examples of supervised learning algorithms where the relationship between the observable parameters and the target parameter (the cluster mass) are both known.
@@
 As with any predictive analysis it is important to test the model on data that the model has not seen before.
-In this section we take all of the observed clusters, our full sample, split them, and generate a training and testing set.
-The data is randomly split 70\% training and 30\% testing.
+This prevents over-fitting.
+In the following subsections we take all of the observed clusters, our full sample, split them, and generate a \emph{training} and \emph{testing} set \citeeg{Ripley2007, Xu2013, Ntampaka2015, Ntampaka2015a, Acquaviva2016}.
+Traditionally, the training set is a set of data used to infer possibly predictive relationships.
+The test set of data is then used to assess the correctness of the predictive relationship.
+Our data is randomly split into 70\% training and 30\% testing.
 We follow the ML convention and refer to the individual clusters in each set as a ``sample'', and the parameters associated with the cluster ($z$, LOSVD, mass, etc.) as ``features''.
@@
 \subsubsection{Probability Based}\label{sec:probability method}
-We begin with the training sample.
-After selecting the desired features $\vec{x} = \{\sigma, z, ...\}$ we make the joint probability between the true cluster mass ($M_{200c}$) and $\vec{x}$.
-Figure~\ref{fig: probability corner}, a corner plot, shows all of the one (marginalized probability) and two (joint probability) dimensional projections of the posterior probability distributions of the features of the training data.
+For internal consistency between this and the ML based method we use 70\% of the clusters to establish a conditional probability density of $p(M_{200c} | \vec{x})$ which we then use as the mass probability density for the remaining clusters with similar features.
+In this way we, ``train'' the probability density using the existing simulated data, and apply it to the ``test'' sample (the remaining 30\% of the data not used as the ``training'' set).
+
+Figure~\ref{fig: probability corner} shows all of the one (marginalized probability) and two (joint probability) dimensional projections of the posterior probability distributions of the features of the training data.
 
@@
 	\includegraphics[width=0.8\textwidth]{figures/recovery.pdf} 
-	\caption{Recovery fractions ($N_{obs}/N_{True}$) of cluster member galaxies as a function of redshift and true cluster mass for the targeted and survey observing strategies.
+	\caption{Recovery fractions ($N_{obs}/N_{True}$) of cluster member galaxies as a function of redshift and true cluster mass for the Targeted and Survey observing strategies.
 We have applied HETDEX-like observational limits on the cluster galaxy detection, and require at least five galaxies to be detected for a cluster to be recovered.
 The solid lines are the median values and the shaded regions represent the 68\% scatter.
-The significant decline in galaxies observed with the survey strategy is due to gaps in the VIRUS IFU.} \label{fig: recovery}
+The significant decline in galaxies observed with the Survey strategy is due to gaps in the VIRUS IFU.} \label{fig: recovery}
 \end{figure*}
@@
 \begin{equation}\label{eq: Pm}
-	P(M_{200c}) = \int P(M_{200c}|\vec{x}) P(\sigma) d\sigma
+	P(M_{200c}) = \int P(M_{200c}|\vec{x})\ P(\sigma)\ d\sigma
 \end{equation}
@@
 \begin{equation}\label{eq: expected mass}
-	M_{pred}= \int M_{200c} P(M_{200c})dM_{200c}
+	M_{pred}= \int M_{200c}\ P(M_{200c})\ dM_{200c}
 \end{equation}
@@
 \begin{equation}\label{eq: variance}
-	\mathrm{Var} = \int (M_{200c} - M_{pred})^2 P(M_{200c})dM_{200c}
+	\mathrm{Var} = \int (M_{200c} - M_{pred})^2\ P(M_{200c})\ dM_{200c}
 \end{equation}
@@
 The cluster mass estimation in this section relies on a ML technique known as an ensemble method, where many estimators are created by a single learning method with the goal of improved generalization and robustness compared to a single estimation.
-Ensemble methods come in two general flavors.
+Ensemble methods \citeeg{Caruana2006} come in two general flavors.
 Averaging methods average (hence the name) the estimators to produce a single prediction.
@@
 
-Here we use an averaging ensemble learning method known as a forest of randomized decision trees often shorten to just random forest (RF).
+Here we use an averaging ensemble learning method known as a forest of randomized decision trees, often shorten to just random forest (RF; \citealt{Ho1995, Ho1998}).
 Decision trees can be visualized a flow chart where forks are the branches of the tree.
@@
 
-Any uncertainties quoted by this method are prediction intervals not confidence intervals.
+We note the subtle distinction that the ML method generates ``prediction intervals'' between observed and derived quantities (rather than ``confidence intervals'').
 A prediction interval is an estimate of the interval encompassing future observations, with a certain probability.
@@
 \section{RESULTS}\label{sec:results}
-Here we explore the cluster member recovery rate and mass estimates for the two observing strategies, targeted, and survey.
+Here we explore the cluster member recovery rate and mass estimates for the two observing strategies, Targeted, and Survey.
 Targeted observations are direct observations of a cluster where each cluster member galaxy, above the detection thresholds (see Section \ref{sec: observations}), is observed.
 Survey observations mimic the HETDEX observation strategy such that no cluster is directly observed, and only the cluster member galaxies above the detection threshold and within an IFU (see Figure \ref{fig: ifu layout}) are observed.
-We discuss the accuracy of cluster dynamical mass derived from both the power-law scaling relation (see Equation \ref{eq:power law}) and through the probability and ML methods.
+We discuss the accuracy of cluster dynamical mass derived from both the power law scaling relation (see Equation \ref{eq:power law}) and through the probability and ML methods.
+
+We compare the results from the Targeted and Survey observing strategies to the results of a ``Perfect'' survey, where the redshift (and therefore LOSV) of each galaxy in the cluster is known perfectly).
 
@@
 As discussed in Section \ref{sec: observations} the observational constraints place limits on the total number of clusters member galaxies expected to be recovered.
-Knowing these limits will provide important information for potential future follow up or targeted observations.
-Figure \ref{fig: recovery} shows the recovery fraction of member galaxies, the number of observed galaxies divided by the number of actual galaxies ($N_{obs}/N_{True}$), as function of both redshift and cluster mass.
-It is important to note that if fewer than five member galaxies are observed ($N_{obs} <5$) the cluster is not considered detected, and is excluded from this Figure.
-As expected, the targeted observing strategy where the individual clusters are targeted through several dithers to ensure near complete coverage, performs significantly better than the survey observing strategy across all redshifts and cluster masses.
+Knowing these limits will provide important information for potential future follow up or Targeted observations.
+Figure \ref{fig: recovery} shows the recovery fraction of member galaxies, the number of observed galaxies divided by the number of actual galaxies ($N_{obs}/N_{True}$), as a function of both redshift and cluster mass.
+We require a detection of ($N_{obs} >=5$) galaxies for a cluster to be “detected” and included in this figure.
+As expected, the Targeted observing strategy where the individual clusters are targeted through several dithers to ensure near complete coverage, performs significantly better than the Survey observing strategy across all redshifts and cluster masses.
+With Perfect knowledge, recovery fraction would be unity across all redshifts and cluster masses.
 
@@
 We check this by limiting the cluster galaxy detection by absolute magnitude which increases the recovery fraction to $>70\%$ at all redshifts, implying the decline is a result of the apparent magnitude cluster galaxy detection threshold.
-The second key feature is the strong decline in clusters recovered from survey observations.
+The second key feature is the strong decline in clusters recovered from Survey observations.
 This is due to gaps in the VIRUS IFU.
-The median recovery fraction in survey observations is almost exactly 4.5 times less than the targeted median recovery fraction.
-As the total filling factor of the survey increases the two lines will converge.
+The median recovery fraction in Survey observations is almost exactly 4.5 times less than the Targeted median recovery fraction.
+As the total filling factor of the Survey increases the two lines will converge.
 
@@
 The higher redshift cluster members suffer from the limiting apparent magnitude and suppress the recovery fraction at fixed mass.
-If we were to limit the survey to $z<0.2$ we find the recovery fraction of clusters, at all masses, increases substantially, and we find a much more consistent detection fraction across all masses.
+If we were to limit the Survey to $z<0.2$ we find the recovery fraction of clusters, at all masses, increases substantially, and we find a much more consistent detection fraction across all masses.
 
@@
 The solid black line shows the 1:1 relation.
-The solid, colored line is the median predicted mass for the targeted observing, and the colored, dashed line is the median recovered mass for the HETDEX-like observations.
+The solid, colored line is the median predicted mass for the Targeted observing, and the colored, dashed line is the median recovered mass for the HETDEX-like observations.
 The shaded regions represent the 68\% scatter around the median values.} \label{fig:Probability comparison}
@@
 \ref{eq:power law}), the probability based approach (Section \ref{sec:probability method}) and the ML based method (Section \ref{sec:machine learning method}).
-For each method we consider observations with perfect knowledge, targeted observations and survey observations.
+For each method we consider observations with Perfect knowledge, Targeted observations and Survey observations.
 
-Because it represents the best possible scenario, the perfect knowledge observations should serve as baseline to compare the probability based and ML cluster mass recovery methods.
+Because it represents the best possible scenario, the Perfect knowledge observations should serve as baseline to compare the power law based, probability based and ML cluster mass recovery methods.
 And, while there are many possible metrics to evaluate performance, we compute two: the average bias (given in Table \ref{tbl:mass bias})
 \begin{equation}
-\mathrm{\mu_{bias}}(y,\hat{y}) = \frac{1}{N} \sum_{i=0}^N (\hat{y_i} - y_i).
+\mathrm{\mu_{bias}}(y,\hat{y}) = \frac{1}{N} \sum_{i=1}^N (\hat{y_i} - y_i).
 \end{equation}
@@
 \begin{equation}
-	\sigma_{bias}(y,\hat{y}, \mu_{bias}) = \bigg{[}\frac{1}{N-1} \sum_{i=0}^N (\hat{y_i} - y_i - \mu_{bias})^2 \bigg{]}^{1/2}
+	\sigma_{bias}(y,\hat{y}, \mu_{bias}) = \bigg{[}\frac{1}{N-1} \sum_{i=1}^N (\hat{y_i} - y_i - \mu_{bias})^2 \bigg{]}^{1/2}
 \end{equation}
-for different bins of cluster mass. Both metrics evaluate how closely the ensemble of predicted cluster masses are to the true cluster masses, and in both cases values closer to zero are better.
+with $N$ clusters in a given bin. Both metrics evaluate how closely the ensemble of predicted cluster masses are to the true cluster masses, and in both cases values closer to zero are better.
 
-We begin with the perfect knowledge observations.
-These observations are of the same clusters as the targeted observations but without any observational limits.
+We begin with the Perfect knowledge observations.
+These observations are of the same clusters as the Targeted observations but without any observational limits.
 The cluster masses predicted by Equation \ref{eq:power law} gives the following results.
-Across all cluster masses, we find $\mu_{bias} = 0.15\pm{0.002}$ dex and $\sigma_{bias} = 0.24\pm{0.001}$.
+For clusters with masses between Log M/\Msol $= 13 - 15.5$, we find $\mu_{bias} = 0.15\pm{0.002}$ dex and $\sigma_{bias} = 0.24\pm{0.001}$.
 The scatter in recovered masses can be attributed to both physical and numerical effects.
-The presence of any in-falling matter onto lower mass clusters can introduce a significant amount of substructure, which increases the observed LOSVD increasing the predicted mass \citeeg{Ntampaka2015}.
+The presence of any in-falling matter onto lower mass clusters can introduce a significant amount of substructure, leading to artificial biasing of the measured LOSVD to higher values, increasing the predicted mass \citeeg{Ntampaka2015}.
 Also, as the number of cluster galaxies decreases the LOSVD PDF is poorly sampled leading to poorly recovered cluster masses due to numerical effects.
-The cluster masses presented here are recovered using the best possible conditions, where we have perfect knowledge of the cluster membership.
+The cluster masses presented here are recovered using the best possible conditions, where we have Perfect knowledge of the cluster membership.
 In reality, the mass recovery levels presented in this section represent an upper bound (the best) on the accuracy achievable through this method.
@@
 We could do something similar and have a similar discussion, but I'm not sure it is worth it.
-Should be simple enough to do with the targeted catalog, but with the HETDEX catalog it would be pretty bad IMO.
+Should be simple enough to do with the Targeted catalog, but with the HETDEX catalog it would be pretty bad IMO.
 We should also talk about how often the true mass lies within the error bars.
@@
 
-For the targeted and survey observations the power law predicted cluster masses give $\mu_{bias} =0.13\pm{0.003}$ dex, $\sigma_{bias} = 0.37\pm{0.002}$ and $\mu_{bias} =0.11\pm{0.009}$ dex, $\sigma_{bias} = 0.36\pm{0.006}$ , respectively.
-So for the clusters that we detect with survey observations, we obtain similar levels of accuracy as to the targeted observations, on the average.
-This does not mean that the survey observations cannot be improved by targeted observations.
-In fact, when comparing only the galaxies which overlap between the two samples the bias and scatter of the targeted observations is significantly decreased as more cluster member galaxies are detected, better sampling the LOSVD PDF.
-The targeted observations performs similarly on the average because many lower mass clusters are included in the sample, increasing the bias of the overall sample.
+For the Targeted and Survey observations the power law predicted cluster masses give $\mu_{bias} =0.13\pm{0.003}$ dex, $\sigma_{bias} = 0.37\pm{0.002}$ and $\mu_{bias} =0.11\pm{0.009}$ dex, $\sigma_{bias} = 0.36\pm{0.006}$ , respectively.
+So for the clusters that we detect with Survey observations, we obtain similar levels of accuracy as to the Targeted observations, on the average.
+This does not mean that the Survey observations cannot be improved by Targeted observations.
+In fact, when comparing only the galaxies which overlap between the two samples the bias and scatter of the Targeted observations is significantly decreased as more cluster member galaxies are detected, better sampling the LOSVD PDF.
+The Targeted observations performs similarly on the average because many lower mass clusters are included in the sample, increasing the bias of the overall sample.
 
@@
 The solid black line shows the 1:1 relation.
-The solid, colored line is the median predicted mass for the targeted observing, and the colored, dashed line is the median recovered mass for the HETDEX-like observations.
+The solid, colored line is the median predicted mass for the Targeted observing, and the colored, dashed line is the median recovered mass for the HETDEX-like observations.
 The shaded regions represent the 68\% scatter around the median values.} \label{fig: ML comparison}
@@
 In both Figures \ref{fig:Probability comparison} and \ref{fig: ML comparison}, we show the predicted ($M_{pred}$) versus true ($M_{200c}$) cluster masses for each of the two observing strategries.
-In each panel the solid black line is the 1:1 relationship, the solid purple line is the median recovered mass for the targeted observing, and the turquoise, dashed line is the median recovered mass for the HETDEX-like observations.
+In each panel the solid black line is the 1:1 relationship, the solid purple line is the median recovered mass for the Targeted observing, and the turquoise, dashed line is the median recovered mass for the HETDEX-like observations.
 The shaded regions are the 68\% scatter around the median values (the 16\% and 84\% quartiles).
-For reference we also show the median masses recovered with perfect knowledge as a dash-dotted orange line.
-The lower panels show the fractional cluster mass error:
+For reference we also show the median masses recovered with Perfect knowledge as a dash-dotted orange line.
+The lower panels show the fractional cluster mass error defined as:
 \begin{equation}\label{eq: fractional error}
@@
 
-% In both figures we successively add additional information to further constrain the true cluster masses which subsequently reduces the error associated with the ensemble of predictions (see Table \ref{tbl:mass comparisons}).
-The power law derived masses, using the single (not including the cosmological parameters) free parameter, $\sigma$ (the LOSVD), over estimates the predicted cluster mass at all masses.
-Both the probability and ML methods over predict the mass of low mass clusters and under predict the mass of the higher mass clusters.
-When the redshift information is also added, the amount of this over and under prediction is lessened but the cross over point, remains roughly consistent at $\sim10^{14}$ \msol.
-Additionally, the number of galaxies observed, $N_{gal}$, further reduces the MAE and RMSE on the predictions but also lowers the cross over point to $\sim10^{13.5}$ \msol.
-
-% \editorial{It doesn't look like you can use the targeted training sample to train the survey data.
-If you do, it either does worse or about the same if you didn't use any training at all.
-After looking at it, you do have to use the survey training data to get good results about 0.13 dex MAE
-% }
 \begin{table*}
@@
 \caption{Mean bias ($M_{pred}$ - $M_{200c}$) for different bins of predicted cluster mass.
-This table shows the bias in the predicted cluster mass for the perfect (top section), targeted (middle section), and survey (bottom section) observations in different predicted mass bins.
+This table shows the bias in the predicted cluster mass for the perfect (top section), Targeted (middle section), and Survey (bottom section) observations in different predicted mass bins.
 The different mass recovery strategies are given in the leftmost column.
@@
 We quantify the bias and scatter for all of the different cluster mass recovery strategies and observing methods in Table \ref{tbl:mass bias} and Table \ref{tbl:mass scatter}.
-It should serve as a type of look up table for future cluster observations with HETDEX.
+It serves as a type of look up table for future cluster observations with HETDEX.
 The columns represent bins of predicted galaxy cluster mass and the individual values show the bias and scatter of the true cluster mass.
-The three horizontal sections represent perfect, targeted and survey observations respectively.
-So, for example, if a cluster mass is predicted using the $ML_{\sigma, z}$ method and targeted observations to be Log M/\Msol\ $=13-13.5$, it is biased upward by $0.03\pm{0.00}$ dex.
+The three horizontal sections represent perfect, Targeted and Survey observations respectively.
+So, for example, if a cluster mass is predicted using the $ML_{\sigma, z}$ method and Targeted observations to be Log M/\Msol\ $=13-13.5$, it is biased upward by $0.03\pm{0.00}$ dex.
 
@@
 While we provide corrections for cluster masses above $10^{15}$ \msol, they are estimated from only a handful of objects, and do not constitute a representative sample of clusters.
-On the oposite end of the cluster mass spectrum, survey observations of low mass clusters are incomplete for two potential reasons.
-There are very few, if any, clusters detected with survey observations below $10^{12}$ \msol.
+On the opposite end of the cluster mass spectrum, Survey observations of low mass clusters are incomplete for two potential reasons.
+There are very few, if any, clusters detected with Survey observations below $10^{12}$ \msol.
 Missing corrections above $10^{12}$ \msol\ in the probability based methods are due to low number statstics and an inability to sample the cluster mass PDF well enough to assign cluster mass predictions.
 
-\subsubsection{Significance of Cosmology Choice}
-The underlying simulation used to produce the Buzzard catalogs, as with every simulation, makes specific assumptions about the cosmology used and how the galaxies are populated into the DM halos.
+\subsection{Significance of Training Sample Cosmology Choice}
+All simulations (including that used for Buzzard) use specific choices for cosmological parameters.
 When using simulation data to train ML methods, we incorporate all of those assumptions into the learned feature associations.
@@
 \caption{Scatter in cluster mass after bias correction for different bins of predicted cluster mass.
-This table shows the scatter in the predicted cluster mass for the perfect (top section), targeted (middle section), and survey (bottom section) observations in different predicted mass bins.
+This table shows the scatter in the predicted cluster mass for the perfect (top section), Targeted (middle section), and Survey (bottom section) observations in different predicted mass bins.
 The different mass recovery strategies are given in the leftmost column.
@@
 For a survey such as HETDEX, we can estimate the constraints on $\sigma_8h^{-1}$ using Equation \ref{eq:sigElapprox}.
-Considering clusters with masses above $10^{14}$ \Msol, with perfect knowledge, and the ML based cluster mass estimates the mass scale uncertainty (given in Table~\ref{tbl:mass scatter}) is reduced to $\sim 0.075$ dex or about 20\%.
+Considering clusters with masses above $10^{14}$ \Msol, with Perfect knowledge, and the ML based cluster mass estimates the mass scale uncertainty (given in Table~\ref{tbl:mass scatter}) is reduced to $\sim 0.075$ dex or about 20\%.
 This gives a uncertainty on $\sigma_8h^{-1}$ of 7\%.
-For clusters above $10^{14}$ \Msol, survey observations can constrain the masses to about 51\% which, in turn, constrains $\sigma_8h^{-1}$ to 20\%.
+For clusters above $10^{14}$ \Msol, Survey observations can constrain the masses to about 51\% which, in turn, constrains $\sigma_8h^{-1}$ to 20\%.
 
@@
 For example, \cite{deHaan2016} constrain $\sigma_8h^{-1}$ to $\sim5$\% using a sample of 337 SZE detected clusters from the SPT-SZE survey.
-For the $\sim1500$ clusters detected with survey observations to constrain $\sigma_8h^{-1}$ and to be dominated by cluster statistics alone ($\Delta \ln N \sim N^{-1/2}$), the absolute cluster calibration would need to be better than 2.5\%.
-For a fully targeted survey, about 14000 clusters, this cluster mass calibration uncertainty reduces to $>1\%$.
+For the $\sim1500$ clusters detected with Survey observations to constrain $\sigma_8h^{-1}$ and to be dominated by cluster statistics alone ($\Delta \ln N \sim N^{-1/2}$), the absolute cluster calibration would need to be better than 2.5\%.
+For a fully Targeted survey, about 14000 clusters, this cluster mass calibration uncertainty reduces to $>1\%$.
 
@@
 	\caption{\emph{Top}: The optical richness, $\lambda$, versus the predicted cluster mass.
-The solid, colored line is the median predicted mass for the targeted observing, and the colored, dashed line is the median recovered mass for the HETDEX-like observations.
+The solid, colored line is the median predicted mass for the Targeted observing, and the colored, dashed line is the median recovered mass for the HETDEX-like observations.
 The shaded regions represent the 68\% scatter around the median values.
@@
 The top panel shows the generated optical richness, $\lambda$, versus the predicted cluster mass.
-The cluster masses are the $ML_{\sigma, z, N_{gal}}$ based and correspond to the targeted and survey observation strategies.
+The cluster masses are the $ML_{\sigma, z, N_{gal}}$ based and correspond to the Targeted and Survey observation strategies.
 The bottom panel of Figure \ref{fig:mass richness} shows the scatter in the predicted cluster masses at fixed richness, $\sigma_{M|\lambda}$.
@@
 We exclude clusters with $\lambda>130$ both because there are very few of them which does not accurately reproduce a scatter and because the observational studies which we base our richnesses on do not include these clusters.
-We find that we are able to accurately recover an average intrinsic scatter of $0.2 <\langle \sigma_{M|\lambda} \rangle <0.3$ dex, finding $\langle \sigma_{M|\lambda} \rangle = 0.255\pm{0.02}$ at $\sigma_{true} = 0.25$ with survey observations.
+We find that we are able to accurately recover an average intrinsic scatter of $0.2 <\langle \sigma_{M|\lambda} \rangle <0.3$ dex, finding $\langle \sigma_{M|\lambda} \rangle = 0.255\pm{0.02}$ at $\sigma_{true} = 0.25$ with Survey observations.
 This is very promising as other observational studies have estimated the intrinsic scatter of real clusters to be $\sim0.25$ dex \citeeg{Rozo2014, Rozo2015}.
@@
 
-For a richness-mass relation with an intrinsic scatter of $\langle \sigma_{M|\lambda} \rangle = 0.25$, and following the more traditional parameterization of the richness-mass relation \citeeg{Rykoff2012, Farahi2016}, we find a best-fitting relation for the targeted observations as
+For a richness-mass relation with an intrinsic scatter of $\langle \sigma_{M|\lambda} \rangle = 0.25$, and following the more traditional parameterization of the richness-mass relation \citeeg{Rykoff2012, Farahi2016}, we find a best-fitting relation for the Targeted observations as
 \begin{equation}
@@
 \end{equation}
-and the survey observations as
+and the Survey observations as
 \begin{equation}
@@
 \end{equation}
-This gives $M_{200c} = (1.09\pm0.01)\times10^{14} h^{-1}$ \Msol  and  $M_{200c} = (1.36\pm0.03)\times10^{14}h^{-1}$ \Msol\ at $\lambda=40$ for the targeted and survey observations respectively.
-If the intrinsic scatter is reduced to $\sim 0.05$ dex we recover an overall normalization of $M_{200c} = (1.6\pm0.02)\times10^{14} h^{-1}$ \Msol\ and $M_{200c} = (1.65\pm0.03)\times10^{14} h^{-1}$ for the targeted and survey observations at $\lambda=40$.
+This gives $M_{200c} = (1.09\pm0.01)\times10^{14} h^{-1}$ \Msol  and  $M_{200c} = (1.36\pm0.03)\times10^{14}h^{-1}$ \Msol\ at $\lambda=40$ for the Targeted and Survey observations respectively.
+If the intrinsic scatter is reduced to $\sim 0.05$ dex we recover an overall normalization of $M_{200c} = (1.6\pm0.02)\times10^{14} h^{-1}$ \Msol\ and $M_{200c} = (1.65\pm0.03)\times10^{14} h^{-1}$ for the Targeted and Survey observations at $\lambda=40$.
 In both cases, this normalization differs significantly from the $M_{200c} \approx 2.1\times10^{14} h^{-1}$ \Msol\ found in recent work by \cite{Li2016, Simet2016}.
-
-%Much like the MAE and RMSE associated with the cluster mass recovery, comparing the individual $\sigma_{M|\lambda}$ values directly is incorrect.
-When comparing only the clusters with observations in both the targeted and survey strategies we
-
-%Applying my current work to a large photometric survey such as those mentioned above is the logical next step.
-For example, the HETDEX observations overlap with the DES area and SDSS Stripe 82 which provides a wealth of external data.
-Using preexisting datasets, the observations from HETDEX, or through dedicated followup spectroscopic observations, I will be able to measure the absolute mass scale of the richness estimator and measure the scatter of the richness-mass relation, $\sigma_{M|\lambda}$.
-An accurate measure of this scatter can lead to a decrease on the error bar on cosmological measures ($\sigma_8$ and $\Omega_M$) by as much as 50\% \citep{Rozo2010}.
-An absolute calibration of the richness-mass relation will provide a much needed tool for future imaging surveys which will identify clusters to $z=1$ and beyond.
-
-% \subsection{Potential Improvements}
-% \editorial{The potential improvements are really three fold.
-We know that the observing won't cover all of the sky.
-So we can simply tile more and try to get more clusters.
-We can observe deeper.
-I'm not sure the current exposure times (they are in an email that I sent to casey) but if we can extend them, then we can get further down the IMF and try to build up some of the clusters that are really more like groups than anything else.
-The last thing we can do is to attempt to build better models to make better predictions on the masses.
-That might be something like the study that \cite{Acquaviva2016} did with the stellar metallicities.
-Or we'll need something else that I haven't thought of just yet.
-The other idea is to come up with some sort of cheat sheet for HETDEX.
-Basically, a if you detect such and such type of galaxy in the survey model then you should go back and try to follow it up with targeted observations.
-It might be good to talk about the recovery fraction between the two surveys above.
-Like...
-if there are 30 cluster members then we should detect the cluster in both surveys.}
 
@@
 Of those, approximately 1500 clusters are detected with HETDEX-like survey observations.
-The number of cluster members recovered is almost exactly 4.5 times fewer than a fully targeted survey, across both a wide range of redshifts and cluster masses.
-	\item Overall, we find a traditional power-law conversion from LOSVD to cluster mass performs significantly poorer than either the probability based or ML based methods also tested.
+The number of cluster members recovered is almost exactly 4.5 times fewer than a fully Targeted survey, across both a wide range of redshifts and cluster masses.
+	\item Overall, we find a traditional power law conversion from LOSVD to cluster mass performs significantly poorer than either the probability based or ML based methods also tested.
 The probability based and ML based cluster mass estimators are able to more accurately predict cluster mass when combined with information other than just the LOSVD.
-While the power-law may be outperformed, overall, comparisons of similar mass galaxy clusters shows that above Log M/\Msol\ $=14.5$, the power-law gives a lower bias than either the probability based or ML based methods.
+While the power law may be outperformed, overall, comparisons of similar mass galaxy clusters shows that above Log M/\Msol\ $=14.5$, the power law gives a lower bias than either the probability based or ML based methods.
 For HETDEX-like observations and clusters with $13 < \mathrm{Log}\, M/\Msol <14.5$, we find the $ML_{\sigma, z, N_{gal}}$ method performs the best.
-Below Log M/\Msol\ $=13$ no method with survey observations gives an bias of less than 50\%.
-	\item For followup targeted observations only galaxy clusters with masses inferred to be Log M/\Msol\ $<13$ from survey observations should be targeted.
-Galaxy clusters with inferred masses below Log M/\Msol\ $=13$ can see as much as an 81\% improvement in cluster mass estimation with targeted observations.
+Below Log M/\Msol\ $=13$ no method with Survey observations gives an bias of less than 50\%.
+	\item For followup Targeted observations only galaxy clusters with masses inferred to be Log M/\Msol\ $<13$ from Survey observations should be targeted.
+Galaxy clusters with inferred masses below Log M/\Msol\ $=13$ can see as much as an 81\% improvement in cluster mass estimation with Targeted observations.
 While the improvement of clusters with masses above Log M/\Msol\ $=13$ is often approximately 10\%.
@@
 
+% \editorial{This all needs to be stripped out and reworked.}
+% The choice $A_{1D}$ and $\alpha$ varies between studies \citeeg{Munari2013, VanderBurg2014} and should be calibrated on a individual basis.
+To do this, we randomly select 47494, $z<0.5$ clusters composed of 36000 $10^{13}$, 6000 $10^{14}$ and two $10^{15}~\Msol$ halos.
+We perform a linear fit to the $\sigma_{1D}-M_{200}$ values allowing both $A_{1D}$ and $\alpha$ to vary.
+We find best fitting parameters of $A_{1D} = 1117.9~\kms$ and $\alpha = 0.3297$, both of which are very near the values from \cite{Evrard2008} of $A_{1D} = 1082.9 \pm 4.0~\kms$ and $\alpha = 0.3361$.
+Therefore, we chose to adopt the parameters from \cite{Evrard2008} to better facilitate with other simulations \citeeg{Old2014}, and observational studies \citeeg{Brodwin2010}.
+
+%Much like the MAE and RMSE associated with the cluster mass recovery, comparing the individual $\sigma_{M|\lambda}$ values directly is incorrect.
+When comparing only the clusters with observations in both the targeted and survey strategies we
+
+%Applying my current work to a large photometric survey such as those mentioned above is the logical next step.
+For example, the HETDEX observations overlap with the DES area and SDSS Stripe 82 which provides a wealth of external data.
+Using preexisting datasets, the observations from HETDEX, or through dedicated followup spectroscopic observations, I will be able to measure the absolute mass scale of the richness estimator and measure the scatter of the richness-mass relation, $\sigma_{M|\lambda}$.
+An accurate measure of this scatter can lead to a decrease on the error bar on cosmological measures ($\sigma_8$ and $\Omega_M$) by as much as 50\% \citep{Rozo2010}.
+An absolute calibration of the richness-mass relation will provide a much needed tool for future imaging surveys which will identify clusters to $z=1$ and beyond.
+
+% \subsection{Potential Improvements}
+% \editorial{The potential improvements are really three fold.
+We know that the observing won't cover all of the sky.
+So we can simply tile more and try to get more clusters.
+We can observe deeper.
+I'm not sure the current exposure times (they are in an email that I sent to casey) but if we can extend them, then we can get further down the IMF and try to build up some of the clusters that are really more like groups than anything else.
+The last thing we can do is to attempt to build better models to make better predictions on the masses.
+That might be something like the study that \cite{Acquaviva2016} did with the stellar metallicities.
+Or we'll need something else that I haven't thought of just yet.
+The other idea is to come up with some sort of cheat sheet for HETDEX.
+Basically, a if you detect such and such type of galaxy in the survey model then you should go back and try to follow it up with targeted observations.
+It might be good to talk about the recovery fraction between the two surveys above.
+Like...
+if there are 30 cluster members then we should detect the cluster in both surveys.}
+
 % \section{Evidence of Substructure}
@@
 % In practice, we use locate the nearest neighbors using an unsupervised k-nearest neighbor algorithm as implemented in Scikit-Learn \citep{Pedregosa2012}.
+
+% In both figures we successively add additional information to further constrain the true cluster masses which subsequently reduces the error associated with the ensemble of predictions (see Table \ref{tbl:mass comparisons}).
+The power law derived masses, using the single (not including the cosmological parameters) free parameter, $\sigma$ (the LOSVD), over estimates the predicted cluster mass at all masses.
+Both the probability and ML methods over predict the mass of low mass clusters and under predict the mass of the higher mass clusters.
+When the redshift information is also added, the amount of this over and under prediction is lessened but the cross over point, remains roughly consistent at $\sim10^{14}$ \msol.
+Additionally, the number of galaxies observed, $N_{gal}$, further reduces the MAE and RMSE on the predictions but also lowers the cross over point to $\sim10^{13.5}$ \msol.
+
+% \editorial{It doesn't look like you can use the targeted training sample to train the survey data.
+If you do, it either does worse or about the same if you didn't use any training at all.
+After looking at it, you do have to use the survey training data to get good results about 0.13 dex MAE
+% }

### 2016-05-05 ms.tex
more casey edits

@@
 \end{equation}
-where $D_L$ is the luminosity distance \citeeg{Hogg2010}.
+where $D_L$ is the luminosity distance \citeeg{Hogg1999}.
 
@@
 
-To investigate this, we select cluster halo and galaxy catalogs from the Millennium simulation \citep{Springel2005a} obtained via querying the Millennium online database\footnote{http://gavo.mpa-garching.mpg.de/Millennium/} \citep{Lemson2006}.
+We turn to the Millennium simulation where the underlying cosmological assumptions differ substantially from Buzzard.
+The Millennium simulation adopts a flat cosmological model based of the values derived from the Two-degree Field Galaxy Redshift Survey \citep{Colless2001} and the first year data of the \emph{Wilkinson Microwave Anisotropy Probe} (WMAP; \citealt{Spergel2003}): $\Omega_\Lambda = 0.75$, $\Omega_M = 0.25$, $\sigma_8 = 0.9$, $n_s = 1$ and $H_0= 73$ \kms \mpc.
+The clusters in Millennium provide a testing sample to understand how a training sample derived from Buzzard will impact the mass recovery on a wholly new dataset.
+
+We repeat our analysis using cluster halo and galaxy catalogs from the Millennium simulation \citep{Springel2005a} obtained via querying the Millennium online database\footnote{http://gavo.mpa-garching.mpg.de/Millennium/} \citep{Lemson2006}.
 The Millennium simulation tracks $2160^3$ dark matter particles of $8.6\times 10^8 ~h^{-1}$ \Msol\ inside a comoving 500 $(h^{-1} \mathrm{Mpc})^3$ box from $z=127$ to 0.
-It adopts a flat cosmological model based of the values derived from the Two-degree Field Galaxy Redshift Survey \citep{Colless2001} and the first year data of the \emph{Wilkinson Microwave Anisotropy Probe} (WMAP; \citealt{Spergel2003}): $\Omega_\Lambda = 0.75$, $\Omega_M = 0.25$, $\sigma_8 = 0.9$, $n_s = 1$ and $H_0= 73$ \kms \mpc.
-
 The halo catalogs are created using a friends-of-friends algorithm \citeeg{Turner1976} with linking length, $b=0.2$.
@@
 
-We select 4806 clusters, comprised of 623663 galaxies, at $0.02 < z < 0.5$ and $M > 10^{13}$ \Msol, and apply the same data processing as with the Buzzard galaxies.
+We select 4806 clusters, comprised of 623,663 galaxies, at $0.02 < z < 0.5$ and $M > 10^{13}$ \Msol, and apply the same data processing as with the Buzzard galaxies.
 We begin by assigning each galaxy an [\ion{O}{ii}] flux value (see Section \ref{sec: oii luminosity}), and ``observe'' each galaxy using realistic (see Section \ref{sec: observations}) observational limits.
@@
 
-Cluster masses are assigned using the ML methods (see Section \ref{sec:machine learning method}) using two different training sets.
-We use the full set of clusters detected in the Buzzard catalogs (14000 clusters with $M > 10^{11}$ \msol) and a training-testing split of the Millennium clusters.
-The top panel of Figure \ref{fig: mill buzz comparison} shows the ML predicted cluster masses as a function of true cluster mass for the $\sim$4000 Millennium clusters with the two different training sets.
+We conduct our test in two ways.
+Both use the ML methods (see Section \ref{sec:machine learning method}) to predict the cluster masses of the Millennium clusters, but each test uses a different training set.
+First, we use the full set of clusters detected in the Buzzard catalogs (14,000 clusters with $M > 10^{11}$ \msol) to train the ML.
+Second, the Millennium clusters are split into training-testing samples.
+This provides a test case where we have different cosmological choices between the training and testing samples, and the same cosmological assumptions in both samples.
+
+The top panel of Figure \ref{fig: mill buzz comparison} shows the ML predicted cluster masses for the $\sim$4000 Millennium clusters as a function of true cluster mass.
+The orange (Millennium) and green (Buzzard) colors indicate the two different training samples.
 The median (solid and dashed lines) predicted cluster masses show similar trends regardless of the training data set used.
-Figure \ref{fig: mill buzz comparison}'s bottom panel show the fraction error (Equation~\ref{eq: fractional error}) also as a function of true cluster mass.
+Figure \ref{fig: mill buzz comparison}'s bottom panel shows the fraction error (Equation~\ref{eq: fractional error}) also as a function of true cluster mass.
 The large amount of scatter (the shaded area) in the fractional error for the Buzzard trained predictions is due to the training set including clusters with masses below the $M = 10^{13}$ \Msol\ threshold for the Millennium clusters.
@@
 
-\subsection{Impact on Cluster Cosmology}
+\subsection{Constraints on Cosmological Parameters}
 \begin{table*}
@@
 
-To get a sense of how well HETDEX will be able to constrain cosmological parameters we follow the discussion of \cite{Weinberg2013}, and begin with a few simplifying assumptions.
-While sensitive to $\Omega_m$, the number density of clusters do not necessarily provide the strongest contraint, so we assume that some combination of other data sets (\eg, CMB, BAO, supernovae, WL, etc.) will constrain $\Omega_m$ to higher precision than is possible with clusters alone.
+To get a sense of how well HETDEX will be able to constrain cosmological parameters we follow the discussion of \defcitealias{Weinberg2013}{W13}\cite{Weinberg2013} (hereafter \citetalias{Weinberg2013}), and begin with a few simplifying assumptions.
+While sensitive to $\Omega_m$, the number density of clusters does not necessarily provide the strongest contraint, so we assume that some combination of other data sets (\eg, CMB, BAO, supernovae, WL, etc.) will constrain $\Omega_m$ to higher precision than is possible with clusters alone.
 
-To estimate the error associated with a measurement of $\sigma_8h^{-1}$ (which \citealt{Weinberg2013} refer to as $\sigma_{11,abs}$), \cite{Weinberg2013} consider two sources of uncertainty, the systematic uncertainties in cluster mass calibration and the statistical uncertainty in the observed number density of clusters.
+To estimate the error associated with a measurement of $\sigma_8h^{-1}$ (which \citetalias{Weinberg2013} refer to as $\sigma_{11,abs}$), \citetalias{Weinberg2013} consider two sources of uncertainty, the systematic uncertainties in cluster mass calibration and the statistical uncertainty in the observed number density of clusters.
 The authors combine these two uncertainties though (their Eq.
@@
 where $q$ is the degeneracy exponent between $\sigma_8h^{-1}$ and $\Omega_m$, $\Delta \ln M$ is the mass scale uncertainty, $\Delta \ln N$ is the cluster statistical uncertainty, and $\alpha$ is slope of the cumulative HMF.
-Using the \cite{Tinker2008} HMF at $z\sim0.2$ and a limiting cluster mass of $10^{14}$ \Msol, \cite{Weinberg2013} estimate $q\sim0.4$, $\alpha\sim3$, and find that any cluster survey with more than 10-20 clusters is dominated by the uncertainty in the overall mass scale.
+Using the \cite{Tinker2008} HMF at $z\sim0.2$ and a limiting cluster mass of $10^{14}$ \Msol, \citetalias{Weinberg2013} estimate $q\sim0.4$, $\alpha\sim3$, and find that any cluster survey with more than 10-20 clusters is dominated by the uncertainty in the overall mass scale.
 
 For a survey such as HETDEX, we can estimate the constraints on $\sigma_8h^{-1}$ using Equation \ref{eq:sigElapprox}.
-Considering clusters with masses above $10^{14}$ \Msol, with Perfect knowledge, and the ML based cluster mass estimates the mass scale uncertainty (given in Table~\ref{tbl:mass scatter}) is reduced to $\sim 0.075$ dex or about 20\%.
+Considering clusters with masses above $10^{14}$ \Msol, with Perfect knowledge, and the ML based cluster mass estimates the mass scale uncertainty (given in Table~\ref{tbl:mass scatter}) is reduced to $\Delta_{log_{10}}M \sim 0.075$ dex or about 20\%.
 This gives a uncertainty on $\sigma_8h^{-1}$ of 7\%.
@@
 For the $\sim1500$ clusters detected with Survey observations to constrain $\sigma_8h^{-1}$ and to be dominated by cluster statistics alone ($\Delta \ln N \sim N^{-1/2}$), the absolute cluster calibration would need to be better than 2.5\%.
-For a fully Targeted survey, about 14000 clusters, this cluster mass calibration uncertainty reduces to $>1\%$.
+For a fully Targeted survey, about 14,000 clusters, this cluster mass calibration uncertainty reduces to $>1\%$.
 
@@
 These systematics remain the major source of uncertainty in deriving cosmological constraints from cluster abundances and must be measured using independent methods to realize the full potential of these types of surveys.
+
+The Buzzard cluster catalogs do not contain measurements of $\lambda$, so we supplement it by generating richnesses based on the true cluster masses.
+For testing we assume two versions of the richness-mass relationship.
+\cite{Farahi2016} base the relation on stacked velocity dispersions, and \cite{Simet2016} use weak lensing measurements to construct their relation.
+Because we are investigating HETDEX's ability to recover the overall cluster mass scale and underlying scatter in the mass-richness relationship, we use the true cluster masses perturbed by a known amount to estimate the observed richness.
+
+To confirm that measuring the underlying scatter is possible, after generating richness values we calculate the scatter of the cluster masses at fixed $\lambda$, $\sigma_{M|\lambda}$, by comparing the true, unperturbed cluster masses against the richness and find that we do recover the expected scatter.
+We repeat the process with both assumed richness-mass relationships and recover the expected scatter in both instances.
+
+Primarily, we are interested in the intrinsic scatter of the richness-mass relationship.
+This is because HETDEX is uniquely situated to estimate the scatter, whereas studies rely on stacked data \citeeg{Farahi2016,Simet2016} lose that information.
+However, for technical reasons we begin by estimating how well HETDEX will constrain the absolute mass scale (something stacked studies excel at).
+As part of our fitting process to constrain the mass scale, we estimate the overall scatter in the relationship, so it makes sense to begin here.
+
+To get an idea of how well HETDEX will constrain the absolute mass scale, we can find the best fitting relation to our richness-mass data.
+To generate the best fitting lines we follow the general procedure of \cite{Hogg2010}, by defining an objective function and then minimizing the loss.
+Our objective function is
+\begin{equation}\label{eq:objectivei}
+p(y_i|x_i,\sigma_{yi},m,b,\sigma) = \frac{1}{\sqrt{2\,\pi\,(\sigma_{yi}^2+\sigma^2)}}
+ \,\exp\left(-\frac{[y_i - m\,x_i - b]^2}{2\,(\sigma_{yi}^2+\sigma^2)}\right)
+\end{equation}
+where $y_i$ is the observed cluster mass, $x_i$ is the observed richness, $\sigma_{yi}$ is the uncertainty in observed cluster mass, $m$ is the power law slope, $b$ is the overall cluster mass scale, and $\sigma$ is the intrinsic scatter between richness and cluster mass.
+We assume that the intrinsic scatter is constant from point to point and that all of the measurement errors are Gaussian.
+We convert this objective function into a likelihood by multiplying all of the individual probabilities together,
+\begin{equation}\label{eq:like}
+\mathscr{L} = \prod_{i=1}^N \ p(y_i|x_i,\sigma_{yi},m,b, \sigma).
+\end{equation}
+We again rely on MCMC samples to sample the posterior probability distribution and thus maximize the likelihood.
+The best fitting slope and intercept are quoted as the median value of the posterior probability distribution with 68\% error bars defined as the second moment of the same distribution.
+
+We limit our clusters to those with $10 \leq \lambda < 130$ in our fitting analysis because there are very few clusters with $\lambda>130$ and to better coincide with other observational studies \citeeg{Saro2015}.
+For a richness-mass relation with an intrinsic scatter of $\langle \sigma_{M|\lambda} \rangle = 0.25$ dex, we find a best-fitting relation for the Targeted observations as
+\begin{equation}
+	\mathrm{Log}\ M_{200c}/\Msol = 12.54\pm0.02 + 0.97\pm0.02\ \mathrm{Log}\ \lambda
+\end{equation} 
+and the Survey observations as
+\begin{equation}
+	\mathrm{Log}\ M_{200c}/\Msol = 12.78\pm0.04 + 0.86\pm0.03\ \mathrm{Log}\ \lambda
+\end{equation} 
+This gives $M_{200c} = (1.22\pm...)\times10^{14}$ \Msol and $M_{200c} = (1.44\pm...)\times10^{14}$ \Msol\ at $\lambda=40$ for the Targeted and Survey observations respectively.
+In both cases, this normalization differs significantly from the $M_{200c} \approx 2.1\times10^{14} h^{-1}$ \Msol\ found in recent work \cite{Li2016, Simet2016}.
+If the intrinsic scatter is reduced to $\sim 0.05$ dex we recover an overall normalization of $M_{200c} = (1.8\pm...)\times10^{14}$ \Msol\ and $M_{200c} = (1.78\pm...)\times10^{14}$ for the Targeted and Survey observations at $\lambda=40$.
+
+The intrinsic scatter is also estimated during the fitting process.
+For observations with a richness-mass relation intrinsic scatter of $\langle \sigma_{M|\lambda} \rangle = 0.25$ dex, we recover $\langle \sigma_{M|\lambda} \rangle = 0.22\pm0.003$ dex and $\langle \sigma_{M|\lambda} \rangle = 0.20\pm0.01$ dex for Targeted and Survey observations respectively.
+The discrepancy between the intrinsic value and the measured value is due to the uncertainties in the individual cluster mass predictions.
+As the prediction intervals are narrowed, the recovered intrinsic scatter approaches the true value.
+For example, with cluster mass prediction intervals half the size of the current intervals we measure $\langle \sigma_{M|\lambda} \rangle$ to be $\sim 0.25$ and $\sim 0.23$ for the two sets of observations.
 
@@
 
-The Buzzard cluster catalogs do not contain measurements of $\lambda$, so we supplement it by generating richnesses based on the true cluster masses.
-For testing we assume two versions of the richness-mass relationship.
-\cite{Farahi2016} base the relation on stacked velocity dispersions, and \cite{Simet2016} use weak lensing measurements to construct their relation.
-Because we are investigating HETDEX's ability to recover the underlying scatter in the mass-richness relationship, we use the true cluster masses perturbed by a known amount to estimate the observed richness.
-
-As a check, after generating richness values we calculate the scatter of the masses at fixed $\lambda$, $\sigma_{M|\lambda}$ by comparing the true, unperturbed cluster masses against the richness and find that we do recover the expected scatter.
-We repeat the process with both assumed richness-mass relationships and recover the expected scatter in both instances.
-
 Figure \ref{fig:mass richness} summarizes the main results of this investigation.
 The top panel shows the generated optical richness, $\lambda$, versus the predicted cluster mass.
-The cluster masses are the $ML_{\sigma, z, N_{gal}}$ based and correspond to the Targeted and Survey observation strategies.
+The cluster masses are the $\mathrm{ML}_{\sigma, z, N_{gal}}$ based and correspond to the Targeted and Survey observation strategies.
 The bottom panel of Figure \ref{fig:mass richness} shows the scatter in the predicted cluster masses at fixed richness, $\sigma_{M|\lambda}$.
@@
 
-We exclude clusters with $\lambda>130$ both because there are very few of them which does not accurately reproduce a scatter and because the observational studies which we base our richnesses on do not include these clusters.
  We find that we are able to accurately recover an average intrinsic scatter of $0.2 <\langle \sigma_{M|\lambda} \rangle <0.3$ dex, finding $\langle \sigma_{M|\lambda} \rangle = 0.255\pm{0.02}$ at $\sigma_{true} = 0.25$ with Survey observations.
@@
 As the intrinsic scatter increases or decreases, we fail to recover the scatter as accurately.
-
-To get an idea of how well HETDEX will constrain the absolute mass scale we can find the best fitting relation to our richness-mass data.
-To generate the best fitting lines we follow the general procedure of \cite{Hogg2010}, by defining an objective function and then minimizing the loss.
-Our objective function is
-\begin{equation}\label{eq:objectivei}
-p(y_i|x_i,\sigma_{yi},m,b,\sigma) = \frac{1}{\sqrt{2\,\pi\,(\sigma_{yi}^2+\sigma^2)}}
- \,\exp\left(-\frac{[y_i - m\,x_i - b]^2}{2\,(\sigma_{yi}^2+\sigma^2)}\right)
-\end{equation}
-where we consider both measurement errors in $y_i$, $\sigma_{yi}$, and intrinsic scatter, $\sigma$, in the relation between $x_i$ and $y_i$.
-We assume that the intrinsic scatter is constant from point to point and that all of the measurement errors are Gaussian.
-We convert this objective function into a likelihood by multiplying all of the individual probabilities together,
-\begin{equation}\label{eq:like}
-\mathscr{L} = \prod_{i=1}^N \ p(y_i|x_i,\sigma_{yi},m,b, \sigma).
-\end{equation}
-We again rely on MCMC samples to sample the posterior probability distribution and thus maximize the likelihood.
-The best fitting slope and intercept are quoted as the median value of the posterior probability distribution with 68\% error bars defined as the 16th and 84th percentiles of the same distribution.
-
-For a richness-mass relation with an intrinsic scatter of $\langle \sigma_{M|\lambda} \rangle = 0.25$, and following the more traditional parameterization of the richness-mass relation \citeeg{Rykoff2012, Farahi2016}, we find a best-fitting relation for the Targeted observations as
-\begin{equation}
-	\ln\bigg{(}\frac{M_{200c}}{h_{70}^{-1} 10^{14}\Msol}\bigg{)} = 0.09\pm0.01 + 0.90\pm0.01 \ln\bigg{(}\frac{\lambda}{60}\bigg{)}
-\end{equation}
-and the Survey observations as
-\begin{equation}
-	\ln\bigg{(}\frac{M_{200c}}{h_{70}^{-1} 10^{14}\Msol}\bigg{)} = 0.31\pm0.02 + 0.77\pm0.02 \ln\bigg{(}\frac{\lambda}{60}\bigg{)}.
-\end{equation}
-This gives $M_{200c} = (1.09\pm0.01)\times10^{14} h^{-1}$ \Msol  and  $M_{200c} = (1.36\pm0.03)\times10^{14}h^{-1}$ \Msol\ at $\lambda=40$ for the Targeted and Survey observations respectively.
-If the intrinsic scatter is reduced to $\sim 0.05$ dex we recover an overall normalization of $M_{200c} = (1.6\pm0.02)\times10^{14} h^{-1}$ \Msol\ and $M_{200c} = (1.65\pm0.03)\times10^{14} h^{-1}$ for the Targeted and Survey observations at $\lambda=40$.
-In both cases, this normalization differs significantly from the $M_{200c} \approx 2.1\times10^{14} h^{-1}$ \Msol\ found in recent work by \cite{Li2016, Simet2016}.
 
@@
 The SDSS Web Site is http://www.sdss.org/.
-The SDSS is managed by the Astrophysical Research Consortium for the Participating Institutions.
 

### 2016-05-06 ms.tex
more changes for casey

@@
 
-\begin{figure} 
-	\includegraphics[width=\columnwidth]{figures/cornertest.pdf} 
+\begin{figure*} 
+	\includegraphics[width=\textwidth]{figures/prob_example.pdf} 
 	\caption{Corner plot of the \emph{training} data with features $\sigma$ and $z$.
@@
 } \label{fig: probability corner}
-\end{figure}
+\end{figure*}
 
@@
 		\hline
+		&& \multic{8}{Perfect Observations} \\
+		\hline 
 		\rottext{4}{Prob Based} & Power Law & $0.49\pm{0.09}$ & $0.28\pm{0.02}$ & $0.23\pm{0.01}$ & $0.16\pm{0.00}$ & $0.11\pm{0.00}$ & $0.07\pm{0.00}$ & $0.02\pm{0.01}$ & $-0.07\pm{0.04}$ \\
@@
 		\hline
+		&& \multic{8}{Targeted Observations} \\
 		\hline
@@
 		\hline
+		&& \multic{8}{Survey Observations} \\
 		\hline
@@
 		\hline 
+		&& \multic{8}{Perfect Observations} \\
+		\hline 
 		\rottext{4}{Prob Based} & Power Law & $0.36\pm{0.07}$ & $0.39\pm{0.01}$ & $0.34\pm{0.00}$ & $0.22\pm{0.00}$ & $0.16\pm{0.00}$ & $0.14\pm{0.00}$ & $0.14\pm{0.01}$ & $0.11\pm{0.04}$ \\
@@
 Primarily, we are interested in the intrinsic scatter of the richness-mass relationship.
-This is because HETDEX is uniquely situated to estimate the scatter, whereas studies rely on stacked data \citeeg{Farahi2016,Simet2016} lose that information.
-However, for technical reasons we begin by estimating how well HETDEX will constrain the absolute mass scale (something stacked studies excel at).
+This is because HETDEX is uniquely situated to estimate the scatter, whereas studies relying on stacked data \citeeg{Farahi2016,Simet2016} lose that information.
+However, for technical reasons, we begin by estimating how well HETDEX will constrain the absolute mass scale (something stacked studies excel at).
 As part of our fitting process to constrain the mass scale, we estimate the overall scatter in the relationship, so it makes sense to begin here.
@@
 
-We limit our clusters to those with $10 \leq \lambda < 130$ in our fitting analysis because there are very few clusters with $\lambda>130$ and to better coincide with other observational studies \citeeg{Saro2015}.
+We limit our clusters to those with $10 \leq \lambda < 130$ in our fitting analysis because there are very few clusters with $\lambda>130$ and to better coincide with other observational studies \citeeg{Saro2015} which have lower limits on $\lambda$.
 For a richness-mass relation with an intrinsic scatter of $\langle \sigma_{M|\lambda} \rangle = 0.25$ dex, we find a best-fitting relation for the Targeted observations as
@@
 As the intrinsic scatter increases or decreases, we fail to recover the scatter as accurately.
+
+For
 

### 2016-05-13 ms.tex
another round of casey comments

@@
 As such, measures of galaxy clusters can provide constraints on these parameters and even test models of gravity, but only if observables of clusters can lead to accurate estimates of their total masses.
-Here, we carry out a study to investigate the ability of a blind spectroscopic survey to recover accurate galaxy cluster masses through their velocity dispersion.
-We focus on the Hobby Eberly Telescope Dark Energy Experiment (HETDEX), which will employ the new VIRUS integral field unit (IFU) spectrograph, over 420 \degsq\ on the sky with a 1/4.5 fill factor.
-The instrument covers the blue/optical portion of the spectrum (3500--5500~\AAA), allowing surveys with VIRUS to measure redshifts for a large sample of galaxies out to $z < 0.5$ based on their absorption features or [\ion{O}{ii}] $\lambda$3727 emission (and Lyman-$\alpha$ over $1.9 < z < 3.5$).
+Here, we carry out a study to investigate the ability of a blind spectroscopic survey to recover accurate galaxy cluster masses through their velocity dispersion using probability based and machine learning methods.
+We focus on the Hobby Eberly Telescope Dark Energy Experiment (HETDEX), which will employ new Visible Integral-Field Replicable Unit Spectrographs (VIRUS), over 420 \degsq\ on the sky with a 1/4.5 fill factor.
+The instrument covers the blue/optical portion of the spectrum ($3500-5500~\AAA$), allowing surveys with VIRUS to measure redshifts for a large sample of galaxies out to $z < 0.5$ based on their absorption features or [\ion{O}{ii}] $\lambda$3727 emission (and Lyman-$\alpha$ over $1.9 < z < 3.5$).
 We use a detailed mock galaxy catalog from a semi-analytic model to simulate surveys observed with VIRUS, including: (1) a blind, HETDEX-like survey with an incomplete but uniform spectroscopic selection function; and (2) IFU surveys that target clusters directly, obtaining spectra of all galaxies in a VIRUS-sized field.
@@
 This recipe has two distinct but not always independent tracks.
-The ``direct'' method uses direct observations of a small set of clusters and then uses known mass estimators, including X-ray temperatures and luminosities \citeeg{Mantz2010, Rykoff2014}, cosmic microwave background (CMB) observations \citeeg{Vanderlinde2010, Sehgal2011}, optical richness \citeeg{Abell1958, Rykoff2012} or weak lensing (WL; \eg\ \citealt{Rozo2010}) as examples, which provide a ``true'' mass.
+The ``direct'' method uses direct observations of a small set of clusters and then uses known mass estimators, including X-ray temperatures and luminosities \citeeg{Mantz2010, Rykoff2014}, microwave observations \citeeg{Vanderlinde2010, Sehgal2011}, optical richness \citeeg{Abell1958, Rykoff2012} or weak lensing (WL; \eg\ \citealt{Rozo2010}) as examples, which provide a ``true'' mass.
 This directly calibrates the observable--mass relation which is then applied to a much larger sample.
@@
 X-ray based cluster masses assume hydrostatic equilibrium \citeeg{Mantz2015} which may only be valid for a very small number and range of cluster masses.
-The Sunyaev-Zel'dovich Effect (SZE; \citealt{Sunyaev1972}), which uses the up-scattering of CMB photons to estimate cluster masses, provides accurate estimations of mass, but the ability to detect low mass galaxy clusters is currently limited by technology \citeeg{Carlstrom2002a}.
-WL estimates are, in principle, correct in the mean, but they suffer from signal-to-noise requirements, limiting their usefulness in low mass clusters, and potentially suffer from line-of-sight effects as WL is sensitive to all mass along the line-of-sight.
+The Sunyaev-Zel'dovich Effect (SZE; \citealt{Sunyaev1972}), which uses the up-scattering of cosmic microwave background (CMB) photons to estimate cluster masses, provides accurate estimations of mass, but the ability to detect low mass galaxy clusters is currently limited by technology \citeeg{Carlstrom2002a}.
+WL estimates are, in principle, correct in the mean, but they suffer from signal-to-noise requirements, limiting their usefulness in low mass clusters (where the lensing signal is particularly weak), and potentially suffer from line-of-sight effects as WL is sensitive to all mass along the line-of-sight.
 Virial mass estimators which determine the cluster mass based on the motions of the member galaxies \citeeg{Ruel2014, Sifon2015} are promising in that it is a direct measurement of the depth of clusters potential well, but suffer from systematics due to cluster formation physics which disrupts the velocity field.
@@
 	\includegraphics[width=\textwidth]{figures/oii_sdss.pdf} 
-	\caption{\textit{Left}: CMD of 503113 $z<0.2$ galaxies take from the SDSS DR12 where the shading scales with the density of points.
+	\caption{\textit{Left}: CMD of 503,113 $z<0.2$ galaxies take from the SDSS DR12 where the shading scales with the density of points.
 The two colored boxes show regions containing potential catalog galaxies.
@@
 We use the SDSS DR12 \citep{Alam2015} catalogs to assign [\ion{O}{ii}] emission line strengths to the galaxies in the Buzzard catalog.
-We use 503113 galaxies from $z = 0.05 - 0.2$, which are selected with no redshift warning, and place each galaxy on a color-magnitude diagram (CMD) of $M_r$ and $g-r$; see the left panel of Figure \ref{fig: oii sdss}.
+We use 503,113 galaxies from $z = 0.05 - 0.2$, which are selected with no redshift warning, and place each galaxy on a color-magnitude diagram (CMD) of $M_r$ and $g-r$; see the left panel of Figure \ref{fig: oii sdss}.
 
@@
 \begin{equation}
-	u_i = \frac{(x_i - M)}{c\mathrm{MAD}}
-\end{equation}.
+	u_i = \frac{(x_i - M)}{c\mathrm{MAD}}.
+\end{equation}
 MAD is the median absolute deviation, also defined in \cite{Beers1990}, and $c$ is the a tuning constant.
@@
 
-We follow the maximum likelihood method of \cite{Walk2006} to estimate the line-of-sight velocity dispersion (LOSVD). We maximize the probability function 
+We follow the maximum likelihood method of \cite{Walker2006} to estimate the line-of-sight velocity dispersion (LOSVD). We maximize the probability function 
 \begin{equation}\label{eq: jointGaussian}
-p(\{v_1, ..., v_N\})=\displaystyle\prod_{i=1}^{N}\frac{1}{\sqrt{2\pi(\sigma_i^2+\sigma_p^2)}}\exp\biggl[-\frac{1}{2}\frac{(v_i-\langle u \rangle)^2}{(\sigma_i^2+\sigma_p^2)}\biggr]
+p(\{v_1, ..., v_N\})=\displaystyle\prod_{i=1}^{N}\frac{1}{\sqrt{2\pi(\sigma_i^2+\sigma_{1D}^2)}}\exp\biggl[-\frac{1}{2}\frac{(v_i-\langle u \rangle)^2}{(\sigma_i^2+\sigma_{1D}^2)}\biggr]
 \end{equation}
-where $\sigma_p$, $\langle\mu\rangle$, and $\sigma_i$ is the LOSVD, the average radial velocity and the error on the individual LOSVs respectively, using a Monte Carlo Markov Chain (MCMC) sampler ({\sc emcee}\footnote{\url{http://dan.iel.fm/emcee/current/}}; \citealt{Foreman-Mackey2013}) which is based on affine-invariant ensemble sampler (see \citealt{Goodman2010} for details on affine-invariant samplers).
-We draw twenty thousand samples from the posterior probability distribution using simple priors, $\langle\mu\rangle$ lies between the maximum and minimum LOSV and $0< \sigma_p < 1400$ \kms.
+where $\sigma_{1D}$, $\langle\mu\rangle$, and $\sigma_i$ is the LOSVD, the average radial velocity and the error on the individual LOSVs (which we have assumed to be normally distributed) respectively, using a Monte Carlo Markov Chain (MCMC) sampler ({\sc emcee}\footnote{\url{http://dan.iel.fm/emcee/current/}}; \citealt{Foreman-Mackey2013}) which is based on affine-invariant ensemble sampler (see \citealt{Goodman2010} for details on affine-invariant samplers).
+We draw twenty thousand samples from the posterior probability distribution using simple priors, $\langle\mu\rangle$ lies between the maximum and minimum LOSV and $0< \sigma_{1D} < 1400$ \kms.
 We set the upper limit on the LOSVD as the LOSVD corresponding to a $10^{16}$ \Msol\ cluster at $z\sim0.0$, higher mass than any expected cluster.
@@
 \subsubsection{Other Estimates of Dynamical Mass -- Introduction}
-In this section we use two methods to predict the mass of a cluster based on other observables.
+In the following sections we use two methods to predict the mass of a cluster based on other observables.
 Often the cluster mass is estimated based on a single observable, X-ray temperature, LOSVD, richness and others (see Section~\ref{sec: Introduction} for referenced examples).
@@
 \subsubsection{Probability Based}\label{sec:probability method}
-For internal consistency between this and the ML based method we use 70\% of the clusters to establish a conditional probability density of $p(M_{200c} | \vec{x})$ which we then use as the mass probability density for the remaining clusters with similar features.
+For internal consistency between this and the ML based method we use 70\% of the clusters to establish a conditional probability density of $p(M_{200c} | \vec{x})$ which we then use as the cluster mass probability density for the remaining clusters with similar features.
 In this way we, ``train'' the probability density using the existing simulated data, and apply it to the ``test'' sample (the remaining 30\% of the data not used as the ``training'' set).
-
-Figure~\ref{fig: probability corner} shows all of the one (marginalized probability) and two (joint probability) dimensional projections of the posterior probability distributions of the features of the training data.
 
@@
 	\includegraphics[width=\textwidth]{figures/prob_example.pdf} 
-	\caption{Corner plot of the \emph{training} data with features $\sigma$ and $z$.
-The corner plots shows all of the one and two dimensional posterior probability distributions used to determine the correct cluster mass.
-The colored rectangles, which have been enlarged for clarity, show the slices needed to create a conditional probability distribution of the mass, $P(M_{200c}|\vec{x})$.
-See text for a complete description.
-} \label{fig: probability corner}
+	\caption{Illustration of the probability based cluster mass prediction method.
+\emph{Left}: The two dimensional posterior probability distribution of LOSVD and redshift used to determine the correct cluster mass.
+The pink and green rectangles show the locations of two example galaxies used to create the conditional probability distribution of the mass, $P(M_{200c}|\vec{x})$.
+\emph{Right}: The conditional probability distribution of the cluster mass for the two example galaxies.
+See text for a complete description.} \label{fig: probability corner}
 \end{figure*}
 
-The conditional probability of the mass $P(M_{200c}|\vec{x}= \{ x_1,x_2,...\})$ is determined by taking a slice through the joint probability distributions in bins centered on the desired value.
-The slices, shown by the colored bars in Figure~\ref{fig: probability corner}, are centered on $\sigma = 400$ \kms and $z=0.17$.
-The distribution of cluster mass contained in the three dimensional bin given by the intersection of these slices is $P(M_{200c}|\vec{x} = \{\sigma=400 \kms,z=0.17\})$.
-
-\begin{figure*}
-	\includegraphics[width=0.8\textwidth]{figures/recovery.pdf} 
-	\caption{Recovery fractions ($N_{obs}/N_{True}$) of cluster member galaxies as a function of redshift and true cluster mass for the Targeted and Survey observing strategies.
-We have applied HETDEX-like observational limits on the cluster galaxy detection, and require at least five galaxies to be detected for a cluster to be recovered.
-The solid lines are the median values and the shaded regions represent the 68\% scatter.
-The significant decline in galaxies observed with the Survey strategy is due to gaps in the VIRUS IFU.} \label{fig: recovery}
-\end{figure*}
+In this method, the cluster masses are predicted much in the same way we assign [\ion{O}{ii}] flux to the Buzzard catalog galaxies.
+Figure~\ref{fig: probability corner} illustrates the process.
+The left panel shows the two dimensional (joint probability) projections of the posterior probability distributions of the feature training data.
+The conditional probability of the cluster mass $P(M_{200c}|\vec{x}= \{ x_1,x_2,...\})$ (shown in the right panel) is determined by selecting a region in the joint probability distribution.
+For example, using the LOSVD and redshift features we create $P(M_{200c}|\vec{x})$ for two test galaxies, shown by the green and pink boxes in the left panel of Figure~\ref{fig: probability corner}.
+These example galaxies have features $\vec{x} = \{\sigma=200\, \kms,z=0.16\}$ and $\vec{x} = \{\sigma=400\, \kms,z=0.36\}$.
+We select all galaxies in our training sample with similar features and create the conditional probability distributions shown in the right panel.
 
@@
 Then the prediction can be returned as the full conditional probability distribution of all responses, which allows us to generate the prediction intervals.
-The 68\% prediction interval is determined by calculating the 16th and 84th percentile of the full conditional probability distribution.
+We report the 68\% prediction interval as the second moment of the full conditional probability distribution.
 
@@
 \subsection{Recovery of Cluster Members}
+\begin{figure*}
+	\includegraphics[width=0.8\textwidth]{figures/recovery.pdf} 
+	\caption{Recovery fractions ($N_{obs}/N_{True}$) of cluster member galaxies as a function of redshift and true cluster mass for the Targeted and Survey observing strategies.
+We have applied HETDEX-like observational limits on the cluster galaxy detection, and require at least five galaxies to be detected for a cluster to be recovered.
+The shading indicates the mean recovery fraction for clusters within each small bin of redshift and cluster mass.
+We find a significant decrease in the recovery of galaxies with increasing redshift.
+This leads to lower recovery fractions of high mass clusters as many only exist at larger redshifts.
+The significant decline in the number of galaxies observed with the Survey strategy is due to gaps in the VIRUS IFU, where the galaxies are missed.} \label{fig: recovery}
+\end{figure*}
+
 As discussed in Section \ref{sec: observations} the observational constraints place limits on the total number of clusters member galaxies expected to be recovered.
@@
 
-For the clusters recovered as a function of redshift (left panel of Figure \ref{fig: recovery}), there are two effects at work.
+For the clusters recovered as a function of redshift (y-direction of Figure~\ref{fig: recovery}), there are two effects at work.
 The decrease in recovery fraction with increasing redshift is a magnitude effect.
-We check this by limiting the cluster galaxy detection by absolute magnitude which increases the recovery fraction to $>70\%$ at all redshifts, implying the decline is a result of the apparent magnitude cluster galaxy detection threshold.
+Increasing redshift results in a lower galaxy recovery fraction.
+Because HETDEX is limited in apparent magnitude, we expect to recovery fewer galaxies at higher redshift.
+We confirm this by limiting the cluster galaxy detection by absolute magnitude, by observing all galaxies with $M_g < -11$.
+This increases the recovery fraction to $>70\%$ at all redshifts, implying the decline is a result of the apparent magnitude cluster galaxy detection threshold.
 The second key feature is the strong decline in clusters recovered from Survey observations.
@@
 
-The recovery rate as a function of cluster mass, right panel of Figure \ref{fig: recovery}, shows that of the the low mass clusters we detect ($N_{obs} >5$), we observe the majority of the galaxies.
+The recovery rate as a function of cluster mass, x-direction of Figure \ref{fig: recovery}, shows that of the the low mass clusters we detect ($N_{obs} >5$), we observe the majority of the galaxies.
 This also shows a rapid decrease in the detection fraction, which can again be explained by considering absolute magnitudes instead of apparent magnitudes, as above.
-Also, high mass clusters are rare, so in order to detect them we must probe a large volume of space.
-The higher redshift cluster members suffer from the limiting apparent magnitude and suppress the recovery fraction at fixed mass.
+Because there are few high mass ($M>5\times10^{14}$ \Msol) clusters, many of which are at moderately high redshift, the higher redshift cluster members suffer from the limiting apparent magnitude and suppress the recovery fraction at fixed mass.
 If we were to limit the Survey to $z<0.2$ we find the recovery fraction of clusters, at all masses, increases substantially, and we find a much more consistent detection fraction across all masses.
+Again perfect observations would detect all members, at all masses, so in this way, Figure~\ref{fig: recovery} is really just a statement about the magnitude limit and [\ion{O}{ii}] line-flux limit of the survey.
 
@@
 The bottom row of panels shows the fractional error (Equation~\ref{eq: fractional error}) also as a function of true cluster mass.
-The solid black line shows the 1:1 relation.
-The solid, colored line is the median predicted mass for the Targeted observing, and the colored, dashed line is the median recovered mass for the HETDEX-like observations.
+The solid black line shows the 1:1 relation, in both panels, between $M_{200c}$ and $M_{pred}$.
+The orange, dash-dotted line is the median predicted mass for perfect observations.
+The solid, purple line is the median predicted mass for the Targeted observing, and the green, dashed line is the median recovered mass for the HETDEX-like observations.
 The shaded regions represent the 68\% scatter around the median values.} \label{fig:Probability comparison}
@@
 For each method we consider observations with Perfect knowledge, Targeted observations and Survey observations.
+The cluster masses presented here are recovered using the best possible conditions, where we have Perfect knowledge of the cluster membership.
+In reality, the mass recovery levels presented in this section represent an upper bound (the best) on the accuracy achievable through this method.
 
@@
 \begin{equation}
-\mathrm{\mu_{bias}}(y,\hat{y}) = \frac{1}{N} \sum_{i=1}^N (\hat{y_i} - y_i).
+\mathrm{\mu_{bias}}(y,y_{pred}) = \frac{1}{N} \sum_{i=1}^N (y_{pred,i} - y_i).
 \end{equation}
-where $y$ are the true values and $\hat{y}$ are the predicted values, and the scatter about the bias (given in Table \ref{tbl:mass scatter})
+where $y$ are the true values and $y_{pred}$ are the predicted values, and the scatter about the bias (given in Table \ref{tbl:mass scatter})
 \begin{equation}
-	\sigma_{bias}(y,\hat{y}, \mu_{bias}) = \bigg{[}\frac{1}{N-1} \sum_{i=1}^N (\hat{y_i} - y_i - \mu_{bias})^2 \bigg{]}^{1/2}
+	\sigma_{bias}(y,y_{pred}, \mu_{bias}) = \bigg{[}\frac{1}{N-1} \sum_{i=1}^N (y_{pred,i} - y_i - \mu_{bias})^2 \bigg{]}^{1/2}
 \end{equation}
@@
 The cluster masses predicted by Equation \ref{eq:power law} gives the following results.
-For clusters with masses between Log M/\Msol $= 13 - 15.5$, we find $\mu_{bias} = 0.15\pm{0.002}$ dex and $\sigma_{bias} = 0.24\pm{0.001}$.
+For clusters with masses between Log M/\Msol $= 13 - 15.5$, we find $\mu_{bias} = 0.148\pm{0.008}$ dex and $\sigma_{bias} = 0.193\pm{0.001}$.
 The scatter in recovered masses can be attributed to both physical and numerical effects.
@@
 Also, as the number of cluster galaxies decreases the LOSVD PDF is poorly sampled leading to poorly recovered cluster masses due to numerical effects.
-The cluster masses presented here are recovered using the best possible conditions, where we have Perfect knowledge of the cluster membership.
-In reality, the mass recovery levels presented in this section represent an upper bound (the best) on the accuracy achievable through this method.
 
@@
 
-For the Targeted and Survey observations the power law predicted cluster masses give $\mu_{bias} =0.13\pm{0.003}$ dex, $\sigma_{bias} = 0.37\pm{0.002}$ and $\mu_{bias} =0.11\pm{0.009}$ dex, $\sigma_{bias} = 0.36\pm{0.006}$ , respectively.
+For the Targeted and Survey observations the power law predicted cluster masses give $\mu_{bias} =0.135\pm{0.003}$ dex, $\sigma_{bias} = 0.370\pm{0.002}$ and $\mu_{bias} =0.148\pm{0.008}$ dex, $\sigma_{bias} = 0.324\pm{0.006}$ , respectively.
 So for the clusters that we detect with Survey observations, we obtain similar levels of accuracy as to the Targeted observations, on the average.
@@
 The solid black line shows the 1:1 relation.
-The solid, colored line is the median predicted mass for the Targeted observing, and the colored, dashed line is the median recovered mass for the HETDEX-like observations.
+The orange, dash-dotted line is the median predicted mass for perfect observations.
+The solid, purple line is the median predicted mass for the Targeted observing, and the green, dashed line is the median recovered mass for the HETDEX-like observations.
 The shaded regions represent the 68\% scatter around the median values.} \label{fig: ML comparison}
@@
 Positive numbers indicate the predicted cluster mass over estimates when compared to the true cluster mass.}
-\begin{tabular}{cccccccccc} 
-		&& \multic{8}{Bins -- Log $M_{pred}$} \\
-		\cline{3-10} 
-		\multicolumn{2}{c}{Method} & $11.5-12$ & $12-12.5$ & $12.5-13$ & $13-13.5$ & $13.5-14$ & $14-14.5$ & $14.5-15$ & $15-15.5$ \\
+\begin{tabular}{cccccccc} 
+		&& \multic{6}{Bins -- Log $M_{pred}$} \\
+		\cline{3-8} 
+		\multicolumn{2}{c}{Method} & $12.5-13$ & $13-13.5$ & $13.5-14$ & $14-14.5$ & $14.5-15$ & $15-15.5$ \\
 		\hline
-		&& \multic{8}{Perfect Observations} \\
+		&& \multic{6}{Perfect Observations} \\
 		\hline 
-		\rottext{4}{Prob Based} & Power Law & $0.49\pm{0.09}$ & $0.28\pm{0.02}$ & $0.23\pm{0.01}$ & $0.16\pm{0.00}$ & $0.11\pm{0.00}$ & $0.07\pm{0.00}$ & $0.02\pm{0.01}$ & $-0.07\pm{0.04}$ \\
-		&$\sigma$ & $0.87\pm{0.04}$ & $0.53\pm{0.01}$ & $0.32\pm{0.01}$ & $0.16\pm{0.00}$ & $0.10\pm{0.00}$ & $0.07\pm{0.00}$ & $0.05\pm{0.01}$ & $-0.18\pm{0.06}$ \\
-		&$\sigma, z$ & $0.76\pm{0.04}$ & $0.42\pm{0.01}$ & $0.17\pm{0.00}$ & $0.01\pm{0.00}$ & $-0.06\pm{0.00}$ & $-0.11\pm{0.01}$ & $-0.14\pm{0.01}$ & $-0.38\pm{0.13}$ \\
-		&$\sigma, z, N_{gal}$ & $0.65\pm{0.03}$ & $0.28\pm{0.01}$ & $0.04\pm{0.01}$ & $-0.02\pm{0.00}$ & $-0.02\pm{0.00}$ & $-0.05\pm{0.01}$ & $-0.22\pm{0.12}$ & $-6.62\pm{3.06}$ \\
+		\rottext{4}{Prob Based} & Power Law & $0.23\pm{0.007}$ & $0.16\pm{0.003}$ & $0.11\pm{0.002}$ & $0.07\pm{0.004}$ & $0.02\pm{0.011}$ & $-0.07\pm{0.045}$ \\
+		&$\sigma$ & $0.32\pm{0.005}$ & $0.16\pm{0.003}$ & $0.10\pm{0.002}$ & $0.07\pm{0.004}$ & $0.05\pm{0.012}$ & $-0.18\pm{0.078}$ \\
+		&$\sigma, z$ & $0.17\pm{0.005}$ & $0.01\pm{0.003}$ & $-0.06\pm{0.002}$ & $-0.11\pm{0.015}$ & $-0.14\pm{0.012}$ & $-0.38\pm{0.159}$ \\
+		&$\sigma, z, N_{gal}$ & $0.04\pm{0.009}$ & $-0.02\pm{0.002}$ & $-0.02\pm{0.002}$ & $-0.05\pm{0.014}$ & $-0.22\pm{0.126}$ & $-6.62\pm{3.742}$ \\
 		\hline
-		\rottext{4}{ML Based} & Power Law & $0.49\pm{0.09}$ & $0.28\pm{0.02}$ & $0.23\pm{0.01}$ & $0.16\pm{0.00}$ & $0.11\pm{0.00}$ & $0.07\pm{0.00}$ & $0.02\pm{0.01}$ & $-0.07\pm{0.04}$ \\
-		&$\sigma$ & $0.69\pm{0.05}$ & $0.36\pm{0.01}$ & $0.15\pm{0.01}$ & $-0.02\pm{0.00}$ & $-0.07\pm{0.00}$ & $-0.09\pm{0.01}$ & $-0.11\pm{0.01}$ & $-0.12\pm{0.07}$ \\
-		&$\sigma, z$ & $0.62\pm{0.05}$ & $0.33\pm{0.01}$ & $0.12\pm{0.00}$ & $-0.01\pm{0.00}$ & $-0.06\pm{0.00}$ & $-0.09\pm{0.00}$ & $-0.11\pm{0.01}$ & $-0.19\pm{0.05}$ \\
-		&$\sigma, z, N_{gal}$ & $0.51\pm{0.04}$ & $0.23\pm{0.01}$ & $0.05\pm{0.00}$ & $-0.02\pm{0.00}$ & $-0.02\pm{0.00}$ & $-0.02\pm{0.00}$ & $-0.02\pm{0.01}$ & $-0.08\pm{0.03}$ \\
+		\rottext{5}{ML Based} & Power Law & $0.23\pm{0.007}$ & $0.16\pm{0.003}$ & $0.11\pm{0.002}$ & $0.07\pm{0.004}$ & $0.02\pm{0.011}$ & $-0.07\pm{0.045}$ \\
+		&$\sigma$ & $0.14\pm{0.006}$ & $-0.01\pm{0.003}$ & $-0.07\pm{0.003}$ & $-0.09\pm{0.005}$ & $-0.11\pm{0.014}$ & $-0.17\pm{0.090}$ \\
+		&$\sigma, z$ & $0.12\pm{0.005}$ & $-0.01\pm{0.003}$ & $-0.06\pm{0.003}$ & $-0.08\pm{0.004}$ & $-0.11\pm{0.012}$ & $-0.24\pm{0.076}$ \\
+		&$\sigma, N_{gal}$ & $0.04\pm{0.004}$ & $-0.02\pm{0.002}$ & $-0.02\pm{0.002}$ & $-0.02\pm{0.002}$ & $-0.02\pm{0.006}$ & $-0.08\pm{0.041}$ \\
+		&$\sigma, z, N_{gal}$ & $0.04\pm{0.003}$ & $-0.02\pm{0.002}$ & $-0.02\pm{0.001}$ & $-0.02\pm{0.002}$ & $-0.02\pm{0.005}$ & $-0.08\pm{0.043}$ \\
 		\hline
-		&& \multic{8}{Targeted Observations} \\
+
+		&& \multic{6}{Targeted Observations} \\
 		\hline
-		\rottext{4}{Prob Based} & Power Law & $0.49\pm{0.08}$ & $0.27\pm{0.02}$ & $0.20\pm{0.01}$ & $0.13\pm{0.01}$ & $0.10\pm{0.01}$ & $0.09\pm{0.01}$ & $0.02\pm{0.01}$ & $-0.08\pm{0.03}$ \\
-		&$\sigma$ & $1.02\pm{0.03}$ & $0.66\pm{0.01}$ & $0.40\pm{0.00}$ & $0.17\pm{0.00}$ & $0.02\pm{0.00}$ & $-0.08\pm{0.01}$ & $-0.19\pm{0.01}$ & $-0.35\pm{0.10}$ \\
-		&$\sigma, z$ & $0.85\pm{0.05}$ & $0.49\pm{0.01}$ & $0.25\pm{0.00}$ & $0.08\pm{0.00}$ & $-0.06\pm{0.00}$ & $-0.21\pm{0.02}$ & $-0.35\pm{0.02}$ & $-0.59\pm{0.12}$ \\
-		&$\sigma, z, N_{gal}$ & $0.70\pm{0.03}$ & $0.37\pm{0.01}$ & $0.13\pm{0.00}$ & $0.01\pm{0.00}$ & $-0.05\pm{0.00}$ & $-0.12\pm{0.02}$ & $-0.44\pm{0.18}$ & $-4.45\pm{2.81}$ \\
+		\rottext{4}{Prob Based} & Power Law & $0.20\pm{0.008}$ & $0.13\pm{0.005}$ & $0.10\pm{0.005}$ & $0.09\pm{0.007}$ & $0.02\pm{0.014}$ & $-0.08\pm{0.043}$ \\
+		&$\sigma$ & $0.40\pm{0.005}$ & $0.17\pm{0.003}$ & $0.02\pm{0.004}$ & $-0.08\pm{0.006}$ & $-0.19\pm{0.015}$ & $-0.35\pm{0.122}$ \\
+		&$\sigma, z$ & $0.25\pm{0.005}$ & $0.08\pm{0.003}$ & $-0.06\pm{0.003}$ & $-0.21\pm{0.015}$ & $-0.35\pm{0.016}$ & $-0.59\pm{0.145}$ \\
+		&$\sigma, z, N_{gal}$ & $0.13\pm{0.004}$ & $0.01\pm{0.003}$ & $-0.05\pm{0.003}$ & $-0.12\pm{0.018}$ & $-0.44\pm{0.177}$ & $-4.45\pm{3.444}$ \\
 		\hline
-		\rottext{4}{ML Based} & Power Law & $0.49\pm{0.08}$ & $0.27\pm{0.02}$ & $0.20\pm{0.01}$ & $0.13\pm{0.01}$ & $0.10\pm{0.01}$ & $0.09\pm{0.01}$ & $0.02\pm{0.01}$ & $-0.08\pm{0.03}$ \\
-		&$\sigma$ & $0.76\pm{0.07}$ & $0.54\pm{0.01}$ & $0.26\pm{0.01}$ & $0.01\pm{0.00}$ & $-0.13\pm{0.00}$ & $-0.23\pm{0.01}$ & $-0.33\pm{0.02}$ & $-0.32\pm{0.03}$ \\
-		&$\sigma, z$ & $0.66\pm{0.03}$ & $0.37\pm{0.01}$ & $0.17\pm{0.01}$ & $0.03\pm{0.00}$ & $-0.09\pm{0.00}$ & $-0.21\pm{0.01}$ & $-0.31\pm{0.02}$ & $-0.28\pm{0.05}$ \\
-		&$\sigma, z, N_{gal}$ & $0.57\pm{0.03}$ & $0.28\pm{0.01}$ & $0.09\pm{0.00}$ & $-0.01\pm{0.00}$ & $-0.05\pm{0.00}$ & $-0.08\pm{0.00}$ & $-0.07\pm{0.01}$ & $-0.14\pm{0.05}$ \\
+		\rottext{5}{ML Based} & Power Law & $0.20\pm{0.008}$ & $0.13\pm{0.005}$ & $0.10\pm{0.005}$ & $0.09\pm{0.007}$ & $0.02\pm{0.014}$ & $-0.08\pm{0.043}$ \\
+		&$\sigma$ & $0.26\pm{0.006}$ & $0.02\pm{0.004}$ & $-0.13\pm{0.005}$ & $-0.24\pm{0.008}$ & $-0.35\pm{0.022}$ & $-0.39\pm{0.054}$ \\
+		&$\sigma, z$ & $0.18\pm{0.005}$ & $0.03\pm{0.003}$ & $-0.10\pm{0.004}$ & $-0.21\pm{0.006}$ & $-0.31\pm{0.021}$ & $-0.33\pm{0.063}$ \\
+		&$\sigma, N_{gal}$ & $0.22\pm{0.005}$ & $0.00\pm{0.004}$ & $-0.13\pm{0.004}$ & $-0.16\pm{0.007}$ & $-0.13\pm{0.014}$ & $-0.19\pm{0.059}$ \\
+		&$\sigma, z, N_{gal}$ & $0.09\pm{0.004}$ & $-0.01\pm{0.002}$ & $-0.05\pm{0.002}$ & $-0.08\pm{0.004}$ & $-0.08\pm{0.010}$ & $-0.19\pm{0.060}$ \\
 		\hline
-		&& \multic{8}{Survey Observations} \\
+
+		&& \multic{6}{Survey Observations} \\
 		\hline
-		\rottext{4}{Prob Based} & Power Law & \nd & \nd & $0.53\pm{0.04}$ & $0.30\pm{0.02}$ & $0.16\pm{0.01}$ & $0.07\pm{0.01}$ & $0.01\pm{0.02}$ & $-0.09\pm{0.05}$ \\
-		&$\sigma$ & \nd & \nd & $0.77\pm{0.03}$ & $0.42\pm{0.01}$ & $0.18\pm{0.01}$ & $-0.03\pm{0.01}$ & $-0.18\pm{0.02}$ & $-0.39\pm{0.08}$ \\
-		&$\sigma, z$ & \nd & \nd & $0.61\pm{0.03}$ & $0.29\pm{0.01}$ & $0.08\pm{0.01}$ & $-0.11\pm{0.01}$ & $-0.38\pm{0.12}$ & $-0.48\pm{0.10}$ \\
-		&$\sigma, z, N_{gal}$ & \nd & \nd & $0.48\pm{0.04}$ & $0.18\pm{0.01}$ & $0.02\pm{0.01}$ & $-0.08\pm{0.01}$ & $-0.50\pm{0.20}$ & $-8.81\pm{3.02}$ \\
+		\rottext{4}{Prob Based} & Power Law & $0.53\pm{0.043}$ & $0.30\pm{0.018}$ & $0.16\pm{0.013}$ & $0.07\pm{0.013}$ & $0.01\pm{0.022}$ & $-0.09\pm{0.062}$ \\
+		&$\sigma$ & $0.77\pm{0.030}$ & $0.42\pm{0.011}$ & $0.18\pm{0.008}$ & $-0.03\pm{0.009}$ & $-0.18\pm{0.017}$ & $-0.39\pm{0.102}$ \\
+		&$\sigma, z$ & $0.61\pm{0.036}$ & $0.29\pm{0.012}$ & $0.08\pm{0.008}$ & $-0.11\pm{0.009}$ & $-0.38\pm{0.118}$ & $-0.48\pm{0.127}$ \\
+		&$\sigma, z, N_{gal}$ & $0.48\pm{0.038}$ & $0.18\pm{0.011}$ & $0.02\pm{0.007}$ & $-0.08\pm{0.008}$ & $-0.50\pm{0.203}$ & $-8.81\pm{3.695}$ \\
 		\hline
-		\rottext{4}{ML Based} & Power Law & \nd & $0.06\pm{0.46}$ & $0.17\pm{0.07}$ & $0.17\pm{0.02}$ & $0.13\pm{0.01}$ & $0.07\pm{0.01}$ & $0.01\pm{0.02}$ & $-0.09\pm{0.05}$ \\
-		&$\sigma$ & \nd & $0.58\pm{0.10}$ & $0.54\pm{0.04}$ & $0.24\pm{0.02}$ & $0.03\pm{0.01}$ & $-0.17\pm{0.01}$ & $-0.26\pm{0.03}$ & $-0.30\pm{0.10}$ \\
-		&$\sigma, z$ & \nd & $1.02\pm{0.20}$ & $0.42\pm{0.04}$ & $0.19\pm{0.01}$ & $0.03\pm{0.01}$ & $-0.14\pm{0.01}$ & $-0.25\pm{0.02}$ & $-0.31\pm{0.10}$ \\
-		&$\sigma, z, N_{gal}$ & \nd & $0.91\pm{0.26}$ & $0.39\pm{0.03}$ & $0.12\pm{0.01}$ & $-0.00\pm{0.01}$ & $-0.08\pm{0.01}$ & $-0.14\pm{0.02}$ & $-0.21\pm{0.08}$ \\
+		\rottext{5}{ML Based} & Power Law & $0.17\pm{0.068}$ & $0.17\pm{0.023}$ & $0.13\pm{0.014}$ & $0.07\pm{0.014}$ & $0.01\pm{0.022}$ & $-0.09\pm{0.062}$ \\
+		&$\sigma$ & $0.57\pm{0.046}$ & $0.24\pm{0.015}$ & $0.02\pm{0.012}$ & $-0.17\pm{0.013}$ & $-0.28\pm{0.027}$ & $-0.27\pm{0.117}$ \\
+		&$\sigma, z$ & $0.48\pm{0.034}$ & $0.20\pm{0.013}$ & $0.03\pm{0.009}$ & $-0.13\pm{0.011}$ & $-0.26\pm{0.021}$ & $-0.31\pm{0.110}$ \\
+		&$\sigma, N_{gal}$ & $0.55\pm{0.043}$ & $0.22\pm{0.013}$ & $0.00\pm{0.010}$ & $-0.14\pm{0.011}$ & $-0.22\pm{0.025}$ & $-0.19\pm{0.079}$ \\
+		&$\sigma, z, N_{gal}$ & $0.42\pm{0.029}$ & $0.13\pm{0.011}$ & $-0.00\pm{0.007}$ & $-0.08\pm{0.008}$ & $-0.14\pm{0.016}$ & $-0.19\pm{0.079}$ \\
 	\hline
@@
 The three horizontal sections represent perfect, Targeted and Survey observations respectively.
-So, for example, if a cluster mass is predicted using the $ML_{\sigma, z}$ method and Targeted observations to be Log M/\Msol\ $=13-13.5$, it is biased upward by $0.03\pm{0.00}$ dex.
+So, for example, if a cluster mass is predicted using the $ML_{\sigma, z}$ method and Targeted observations to be Log M/\Msol\ $=13-13.5$, it is biased upward by $0.03\pm{0.003}$ dex.
 
@@
 It can be used to understand how the predicted cluster mass differs from the true cluster masses.}
-\begin{tabular}{cccccccccc} 
-		&& \multic{8}{Bins -- Log $M_{pred}$} \\
-		\cline{3-10} 
-		\multicolumn{2}{c}{Method} & $11.5-12$ & $12-12.5$ & $12.5-13$ & $13-13.5$ & $13.5-14$ & $14-14.5$ & $14.5-15$ & $15-15.5$ \\
+\begin{tabular}{cccccccc} 
+		&& \multic{6}{Bins -- Log $M_{pred}$} \\
+		\cline{3-8} 
+		\multicolumn{2}{c}{Method} & $12.5-13$ & $13-13.5$ & $13.5-14$ & $14-14.5$ & $14.5-15$ & $15-15.5$ \\
 		\hline 
-		&& \multic{8}{Perfect Observations} \\
+		&& \multic{6}{Perfect Observations} \\
 		\hline 
-		\rottext{4}{Prob Based} & Power Law & $0.36\pm{0.07}$ & $0.39\pm{0.01}$ & $0.34\pm{0.00}$ & $0.22\pm{0.00}$ & $0.16\pm{0.00}$ & $0.14\pm{0.00}$ & $0.14\pm{0.01}$ & $0.11\pm{0.04}$ \\
-		&$\sigma$ & $0.16\pm{0.03}$ & $0.24\pm{0.01}$ & $0.26\pm{0.00}$ & $0.20\pm{0.00}$ & $0.16\pm{0.00}$ & $0.14\pm{0.00}$ & $0.16\pm{0.01}$ & $0.19\pm{0.07}$ \\
-		&$\sigma, z$ & $0.17\pm{0.03}$ & $0.21\pm{0.01}$ & $0.23\pm{0.00}$ & $0.19\pm{0.00}$ & $0.16\pm{0.00}$ & $0.55\pm{0.01}$ & $0.16\pm{0.01}$ & $0.39\pm{0.14}$ \\
-		&$\sigma, z, N_{gal}$ & $0.10\pm{0.02}$ & $0.14\pm{0.01}$ & $0.47\pm{0.01}$ & $0.14\pm{0.00}$ & $0.10\pm{0.00}$ & $0.54\pm{0.01}$ & $1.62\pm{0.09}$ & $9.31\pm{3.38}$ \\
+		\rottext{4}{Prob Based} & Power Law & $0.34\pm{0.005}$ & $0.22\pm{0.002}$ & $0.16\pm{0.002}$ & $0.14\pm{0.003}$ & $0.14\pm{0.008}$ & $0.11\pm{0.040}$ \\
+		&$\sigma$ & $0.26\pm{0.004}$ & $0.20\pm{0.002}$ & $0.16\pm{0.002}$ & $0.14\pm{0.003}$ & $0.16\pm{0.009}$ & $0.19\pm{0.071}$ \\
+		&$\sigma, z$ & $0.23\pm{0.003}$ & $0.19\pm{0.002}$ & $0.16\pm{0.002}$ & $0.55\pm{0.010}$ & $0.16\pm{0.009}$ & $0.39\pm{0.143}$ \\
+		&$\sigma, z, N_{gal}$ & $0.47\pm{0.007}$ & $0.14\pm{0.001}$ & $0.10\pm{0.001}$ & $0.54\pm{0.010}$ & $1.62\pm{0.090}$ & $9.31\pm{3.378}$ \\
 		\hline
-		\rottext{4}{ML Based} & Power Law & $0.36\pm{0.07}$ & $0.39\pm{0.01}$ & $0.34\pm{0.00}$ & $0.22\pm{0.00}$ & $0.16\pm{0.00}$ & $0.14\pm{0.00}$ & $0.14\pm{0.01}$ & $0.11\pm{0.04}$ \\
-		&$\sigma$ & $0.22\pm{0.04}$ & $0.27\pm{0.01}$ & $0.29\pm{0.00}$ & $0.24\pm{0.00}$ & $0.21\pm{0.00}$ & $0.19\pm{0.00}$ & $0.18\pm{0.01}$ & $0.22\pm{0.08}$ \\
-		&$\sigma, z$ & $0.19\pm{0.04}$ & $0.22\pm{0.01}$ & $0.25\pm{0.00}$ & $0.20\pm{0.00}$ & $0.18\pm{0.00}$ & $0.16\pm{0.00}$ & $0.17\pm{0.01}$ & $0.15\pm{0.05}$ \\
-		&$\sigma, z, N_{gal}$ & $0.15\pm{0.03}$ & $0.18\pm{0.01}$ & $0.17\pm{0.00}$ & $0.14\pm{0.00}$ & $0.10\pm{0.00}$ & $0.08\pm{0.00}$ & $0.08\pm{0.00}$ & $0.10\pm{0.03}$ \\
+		\rottext{5}{ML Based} & Power Law & $0.34\pm{0.005}$ & $0.22\pm{0.002}$ & $0.16\pm{0.002}$ & $0.14\pm{0.003}$ & $0.14\pm{0.008}$ & $0.11\pm{0.040}$ \\
+		&$\sigma$ & $0.29\pm{0.004}$ & $0.24\pm{0.002}$ & $0.21\pm{0.002}$ & $0.19\pm{0.004}$ & $0.18\pm{0.010}$ & $0.22\pm{0.081}$ \\
+		&$\sigma, z$ & $0.24\pm{0.003}$ & $0.20\pm{0.002}$ & $0.18\pm{0.002}$ & $0.16\pm{0.003}$ & $0.16\pm{0.009}$ & $0.19\pm{0.068}$ \\
+		&$\sigma, N_{gal}$ & $0.19\pm{0.003}$ & $0.14\pm{0.001}$ & $0.10\pm{0.001}$ & $0.08\pm{0.002}$ & $0.07\pm{0.004}$ & $0.10\pm{0.037}$ \\
+		&$\sigma, z, N_{gal}$ & $0.17\pm{0.002}$ & $0.13\pm{0.001}$ & $0.10\pm{0.001}$ & $0.07\pm{0.001}$ & $0.07\pm{0.004}$ & $0.11\pm{0.039}$ \\
 		\hline
-		&& \multic{8}{Targeted Observations} \\
+
+		&& \multic{6}{Targeted Observations} \\
 		\hline
-		\rottext{4}{Prob Based} & Power Law & $0.33\pm{0.07}$ & $0.41\pm{0.01}$ & $0.43\pm{0.01}$ & $0.39\pm{0.00}$ & $0.33\pm{0.00}$ & $0.27\pm{0.01}$ & $0.18\pm{0.01}$ & $0.11\pm{0.04}$ \\
-		&$\sigma$ & $0.14\pm{0.03}$ & $0.19\pm{0.01}$ & $0.24\pm{0.00}$ & $0.25\pm{0.00}$ & $0.25\pm{0.00}$ & $0.22\pm{0.00}$ & $0.19\pm{0.01}$ & $0.30\pm{0.11}$ \\
-		&$\sigma, z$ & $0.19\pm{0.04}$ & $0.20\pm{0.01}$ & $0.24\pm{0.00}$ & $0.24\pm{0.00}$ & $0.23\pm{0.00}$ & $0.56\pm{0.01}$ & $0.21\pm{0.01}$ & $0.36\pm{0.13}$ \\
-		&$\sigma, z, N_{gal}$ & $0.14\pm{0.03}$ & $0.18\pm{0.01}$ & $0.20\pm{0.00}$ & $0.19\pm{0.00}$ & $0.17\pm{0.00}$ & $0.67\pm{0.01}$ & $2.28\pm{0.13}$ & $8.56\pm{3.11}$ \\
+		\rottext{4}{Prob Based} & Power Law & $0.43\pm{0.006}$ & $0.39\pm{0.004}$ & $0.33\pm{0.004}$ & $0.27\pm{0.005}$ & $0.18\pm{0.010}$ & $0.11\pm{0.039}$ \\
+		&$\sigma$ & $0.24\pm{0.003}$ & $0.25\pm{0.002}$ & $0.25\pm{0.003}$ & $0.22\pm{0.004}$ & $0.19\pm{0.011}$ & $0.30\pm{0.110}$ \\
+		&$\sigma, z$ & $0.24\pm{0.003}$ & $0.24\pm{0.002}$ & $0.23\pm{0.002}$ & $0.56\pm{0.011}$ & $0.21\pm{0.012}$ & $0.36\pm{0.131}$ \\
+		&$\sigma, z, N_{gal}$ & $0.20\pm{0.003}$ & $0.19\pm{0.002}$ & $0.17\pm{0.002}$ & $0.67\pm{0.013}$ & $2.28\pm{0.126}$ & $8.56\pm{3.109}$ \\
 		\hline
-		\rottext{4}{ML Based} & Power Law & $0.33\pm{0.07}$ & $0.41\pm{0.01}$ & $0.43\pm{0.01}$ & $0.39\pm{0.00}$ & $0.33\pm{0.00}$ & $0.27\pm{0.01}$ & $0.18\pm{0.01}$ & $0.11\pm{0.04}$ \\
-		&$\sigma$ & $0.29\pm{0.06}$ & $0.29\pm{0.01}$ & $0.31\pm{0.00}$ & $0.31\pm{0.00}$ & $0.32\pm{0.00}$ & $0.30\pm{0.01}$ & $0.29\pm{0.02}$ & $0.11\pm{0.04}$ \\
-		&$\sigma, z$ & $0.14\pm{0.03}$ & $0.23\pm{0.01}$ & $0.26\pm{0.00}$ & $0.25\pm{0.00}$ & $0.24\pm{0.00}$ & $0.22\pm{0.00}$ & $0.25\pm{0.01}$ & $0.15\pm{0.05}$ \\
-		&$\sigma, z, N_{gal}$ & $0.13\pm{0.03}$ & $0.21\pm{0.01}$ & $0.21\pm{0.00}$ & $0.18\pm{0.00}$ & $0.16\pm{0.00}$ & $0.14\pm{0.00}$ & $0.12\pm{0.01}$ & $0.15\pm{0.05}$ \\
+		\rottext{5}{ML Based} & Power Law & $0.43\pm{0.006}$ & $0.39\pm{0.004}$ & $0.33\pm{0.004}$ & $0.27\pm{0.005}$ & $0.18\pm{0.010}$ & $0.11\pm{0.039}$ \\
+		&$\sigma$ & $0.30\pm{0.004}$ & $0.32\pm{0.003}$ & $0.32\pm{0.003}$ & $0.30\pm{0.006}$ & $0.29\pm{0.016}$ & $0.13\pm{0.049}$ \\
+		&$\sigma, z$ & $0.26\pm{0.004}$ & $0.25\pm{0.002}$ & $0.24\pm{0.003}$ & $0.23\pm{0.004}$ & $0.27\pm{0.015}$ & $0.16\pm{0.057}$ \\
+		&$\sigma, N_{gal}$ & $0.27\pm{0.004}$ & $0.27\pm{0.003}$ & $0.27\pm{0.003}$ & $0.25\pm{0.005}$ & $0.18\pm{0.010}$ & $0.15\pm{0.053}$ \\
+		&$\sigma, z, N_{gal}$ & $0.21\pm{0.003}$ & $0.18\pm{0.002}$ & $0.16\pm{0.002}$ & $0.14\pm{0.003}$ & $0.12\pm{0.007}$ & $0.15\pm{0.054}$ \\
 		\hline
-		&& \multic{8}{Survey Observations} \\
+
+		&& \multic{6}{Survey Observations} \\
 		\hline
-		\rottext{4}{Prob Based} & Power Law & \nd & \nd & $0.16\pm{0.03}$ & $0.29\pm{0.01}$ & $0.33\pm{0.01}$ & $0.31\pm{0.01}$ & $0.25\pm{0.02}$ & $0.15\pm{0.06}$ \\
-		&$\sigma$ & \nd & \nd & $0.11\pm{0.02}$ & $0.18\pm{0.01}$ & $0.22\pm{0.01}$ & $0.22\pm{0.01}$ & $0.19\pm{0.01}$ & $0.25\pm{0.09}$ \\
-		&$\sigma, z$ & \nd & \nd & $0.13\pm{0.03}$ & $0.19\pm{0.01}$ & $0.22\pm{0.01}$ & $0.21\pm{0.01}$ & $1.31\pm{0.08}$ & $0.32\pm{0.11}$ \\
-		&$\sigma, z, N_{gal}$ & \nd & \nd & $0.14\pm{0.03}$ & $0.18\pm{0.01}$ & $0.19\pm{0.01}$ & $0.19\pm{0.01}$ & $2.27\pm{0.15}$ & $9.19\pm{3.34}$ \\
+		\rottext{4}{Prob Based} & Power Law & $0.16\pm{0.034}$ & $0.29\pm{0.013}$ & $0.33\pm{0.009}$ & $0.31\pm{0.010}$ & $0.25\pm{0.016}$ & $0.15\pm{0.056}$ \\
+		&$\sigma$ & $0.11\pm{0.024}$ & $0.18\pm{0.008}$ & $0.22\pm{0.006}$ & $0.22\pm{0.007}$ & $0.19\pm{0.012}$ & $0.25\pm{0.092}$ \\
+		&$\sigma, z$ & $0.13\pm{0.028}$ & $0.19\pm{0.008}$ & $0.22\pm{0.006}$ & $0.21\pm{0.007}$ & $1.31\pm{0.084}$ & $0.32\pm{0.115}$ \\
+		&$\sigma, z, N_{gal}$ & $0.14\pm{0.030}$ & $0.18\pm{0.008}$ & $0.19\pm{0.005}$ & $0.19\pm{0.006}$ & $2.27\pm{0.145}$ & $9.19\pm{3.336}$ \\
 		\hline
-		\rottext{4}{ML Based} & Power Law & \nd & $1.41\pm{...}$ & $0.40\pm{0.05}$ & $0.41\pm{0.02}$ & $0.38\pm{0.01}$ & $0.32\pm{0.01}$ & $0.25\pm{0.02}$ & $0.15\pm{0.06}$ \\
-		&$\sigma$ & \nd & $0.30\pm{...}$ & $0.27\pm{0.03}$ & $0.28\pm{0.01}$ & $0.30\pm{0.01}$ & $0.30\pm{0.01}$ & $0.30\pm{0.02}$ & $0.29\pm{0.11}$ \\
-		&$\sigma, z$ & \nd & $0.61\pm{...}$ & $0.22\pm{0.03}$ & $0.25\pm{0.01}$ & $0.25\pm{0.01}$ & $0.25\pm{0.01}$ & $0.25\pm{0.02}$ & $0.30\pm{0.11}$ \\
-		&$\sigma, z, N_{gal}$ & \nd & $0.80\pm{...}$ & $0.19\pm{0.02}$ & $0.21\pm{0.01}$ & $0.20\pm{0.01}$ & $0.19\pm{0.01}$ & $0.19\pm{0.01}$ & $0.23\pm{0.08}$ \\
+		\rottext{5}{ML Based} & Power Law &$0.40\pm{0.050}$ & $0.41\pm{0.016}$ & $0.38\pm{0.010}$ & $0.32\pm{0.010}$ & $0.25\pm{0.016}$ & $0.15\pm{0.056}$ \\
+		&$\sigma$ & $0.27\pm{0.034}$ & $0.27\pm{0.011}$ & $0.31\pm{0.008}$ & $0.30\pm{0.009}$ & $0.30\pm{0.019}$ & $0.29\pm{0.106}$ \\
+		&$\sigma, z$ & $0.20\pm{0.025}$ & $0.24\pm{0.009}$ & $0.24\pm{0.006}$ & $0.25\pm{0.008}$ & $0.24\pm{0.015}$ & $0.27\pm{0.100}$ \\
+		&$\sigma, N_{gal}$ & $0.25\pm{0.032}$ & $0.23\pm{0.009}$ & $0.27\pm{0.007}$ & $0.26\pm{0.008}$ & $0.27\pm{0.018}$ & $0.20\pm{0.072}$ \\
+		&$\sigma, z, N_{gal}$ & $0.17\pm{0.021}$ & $0.21\pm{0.008}$ & $0.20\pm{0.005}$ & $0.19\pm{0.006}$ & $0.17\pm{0.011}$ & $0.20\pm{0.071}$ \\
 		 \hline

### 2016-05-13 ms.tex
final initial casey comments

@@
 The distribution of massive clusters of galaxies depends strongly on the total cosmic mass density, the mass variance, and the dark energy equation of state.
-As such, measures of galaxy clusters can provide constraints on these parameters and even test models of gravity, but only if observables of clusters can lead to accurate estimates of their total masses.
+As such, measures of galaxy clusters can provide constraints on these parameters and even test models of gravity, but only if observations of clusters can lead to accurate estimates of their total masses.
 Here, we carry out a study to investigate the ability of a blind spectroscopic survey to recover accurate galaxy cluster masses through their velocity dispersion using probability based and machine learning methods.
 We focus on the Hobby Eberly Telescope Dark Energy Experiment (HETDEX), which will employ new Visible Integral-Field Replicable Unit Spectrographs (VIRUS), over 420 \degsq\ on the sky with a 1/4.5 fill factor.
-The instrument covers the blue/optical portion of the spectrum ($3500-5500~\AAA$), allowing surveys with VIRUS to measure redshifts for a large sample of galaxies out to $z < 0.5$ based on their absorption features or [\ion{O}{ii}] $\lambda$3727 emission (and Lyman-$\alpha$ over $1.9 < z < 3.5$).
+VIRUS covers the blue/optical portion of the spectrum ($3500-5500~\AAA$), allowing surveys to measure redshifts for a large sample of galaxies out to $z < 0.5$ based on their absorption features or [\ion{O}{ii}] $\lambda$3727 emission (and Lyman-$\alpha$ over $1.9 < z < 3.5$).
 We use a detailed mock galaxy catalog from a semi-analytic model to simulate surveys observed with VIRUS, including: (1) a blind, HETDEX-like survey with an incomplete but uniform spectroscopic selection function; and (2) IFU surveys that target clusters directly, obtaining spectra of all galaxies in a VIRUS-sized field.
@@
 We benchmark both surveys against spectroscopic observations with ``perfect" knowledge of galaxy line-of-sight velocities.
-Using both observing strategies, we produce cluster mass probability density functions $P(M_{200c}|\vec{x})$ of a cluster mass ($M_{200c}$) as a function of an observable parameter or set of observable parameters, $\vec{x}$, where we consider cases of where $\vec{x} = \{\sigma\}$, $=\{\sigma, z\}$, and $=\{\sigma,z, N_{gal}\}$ for velocity dispersion, $\sigma$, redshift, and number of observed galaxies, $N_{gal}$.
-\editorial{This sentence will summarize how well HETDEX will do, and how that might be improved with Targeted observations.}
+We find that with HETDEX we can recover cluster masses to $\sim0.1$ dex which can be further improved to $<0.1$ dex with targeted followup observations.
+This level of cluster mass recovery enables us to place $<20$\% constraints on $\sigma_8$, and leverage the unique properties of the observations to provide important calibrations for the optical richness-cluster mass relation.
 \end{abstract}
+% Using both observing strategies, we produce cluster mass probability density functions $P(M_{200c}|\vec{x})$ of a cluster mass ($M_{200c}$) as a function of an observable parameter or set of observable parameters, $\vec{x}$, where we consider cases of where $\vec{x} = \{\sigma\}$, $=\{\sigma, z\}$, and $=\{\sigma,z, N_{gal}\}$ for velocity dispersion, $\sigma$, redshift, and number of observed galaxies, $N_{gal}$.
+% \end{abstract}
 
@@
 \editorial{There are quite a few words copied from Casey's SHELA paper.}
-HETDEX will perform a blind survey which will measure the redshifts of $8 \times \sim 10^5$ Ly$\alpha$ emitting galaxies (LAEs) between $1.9 < z < 3.5$ using a collection of 78 wide-field IFUs spectrographs covering the wavelength region $3500 - 5500$~\AAA\ at R $\sim$ 750 \citep{Hill2008}.
+HETDEX will perform a blind survey which will measure the redshifts of $8 \times 10^5$ LAE galaxies between $1.9 < z < 3.5$ using a collection of 78 wide-field IFUs spectrographs covering the wavelength region $3500 - 5500$~\AAA\ at R $\sim$ 750 \citep{Hill2008}.
 The goal of these observations will be to provide sub-percent level measurements of the Hubble expansion parameter and the angular diameter distance at $z \sim 2$ via the large scale distribution of galaxies in the redshift range of HETDEX.
@@
 \subsection{Mock Observations}\label{sec: observations}
-This means that when selecting galaxies from the Buzzard catalog we assume an observation for all galaxies laying within a colored, IFU square in Figure~\ref{fig: ifu layout}.
+This means that when selecting galaxies from the Buzzard catalog we assume an observation for all galaxies laying within a turquoise, IFU square in Figure~\ref{fig: ifu layout}.
 Galaxies which lie between the IFUs are missed, as well as the galaxies which lie between the pointings, as there is no overlap between one pointing and the next.
@@
 
-In this work we consider two separate observing strategies, Targeted and Survey-like.
+In this work we consider two separate observing strategies, Targeted and Survey.
 The Targeted observations use ``direct'' observations where each cluster is targeted individually, and every cluster member galaxy is assumed to be observed.
@@
 The following is, in many cases, a subset of the available methods to derive any single parameter.
-The specific choice of method may improve or diminish the accuracy of the recovered parameter, but the methods chosen were to facilitate comparison with other observational studies \citeeg{Boada2016a}.
+The specific choice of method may improve or diminish the accuracy of the recovered parameter, but the methods chosen were to facilitate comparison with other observational studies \citeeg{Kirk2015, Boada2016a}.
 
@@
 \begin{equation}
-	u_i = \frac{(x_i - M)}{c\mathrm{MAD}}.
+	u_i = \frac{(x_i - M)}{C\,\mathrm{MAD}}.
 \end{equation}
-MAD is the median absolute deviation, also defined in \cite{Beers1990}, and $c$ is the a tuning constant.
-We choose $c=6$ (the suggested value) which balances computational speed and location accuracy.
+MAD is the median absolute deviation, also defined in \cite{Beers1990}, and $C$ is the a tuning constant.
+We choose $C=6$ (the suggested value) which balances computational speed and location accuracy.
 
@@
 \end{equation}
-and $c$ is the speed of light in \kms, $z$ is the redshift of the individual galaxy, and $z_c$ is the overall cluster redshift described in the previous section.
+and $c$ is the speed of light in \kms, $z$ is the redshift of the individual galaxy, and $z_c$ is the overall cluster redshift described in the previous subsection.
 
@@
 We draw twenty thousand samples from the posterior probability distribution using simple priors, $\langle\mu\rangle$ lies between the maximum and minimum LOSV and $0< \sigma_{1D} < 1400$ \kms.
-We set the upper limit on the LOSVD as the LOSVD corresponding to a $10^{16}$ \Msol\ cluster at $z\sim0.0$, higher mass than any expected cluster.
-When the full distribution of LOSVDs is not used, the final LOSVD is quoted as the median value of the posterior probability distribution with 68\% error bars defined as the 16th and 84th percentiles of the same distribution.
+We set the upper limit on the LOSVD as the LOSVD corresponding to a $10^{16}$ \Msol\ cluster at $z\sim0.0$, higher mass than any expected cluster in Buzzard.
+When the full distribution of LOSVDs is not used, the final LOSVD is quoted as the median value of the posterior probability distribution with 68\% error bars defined as the second momment of the same distribution.
 
-In principle, a single statistic such as the biweight scale estimator or the gapper estimator (both from \citealt{Beers1990}) with many bootstrap resamplings could be used to construct a distribution of $\sigma_p$.
-In simple tests where the values of both $\sigma_p$ and $\langle\mu\rangle$ are known, the 68\% error bars derived from the MCMC method give slightly better results with the true LOSVD value bracketed by the error bars in $\sim68\%$ of the cases versus $\sim57\%$ with bootstrapping and a single statistic.
+In principle, a single statistic such as the biweight scale estimator or the gapper estimator (both from \citealt{Beers1990}) with many bootstrap resamplings could be used to construct a distribution of $\sigma_{1D}$.
+In simple tests where the values of both $\sigma_{1D}$ and $\langle\mu\rangle$ are known, the 68\% error bars derived from the MCMC method give slightly better results with the true LOSVD value bracketed by the error bars in $\sim68\%$ of the cases versus $\sim57\%$ with bootstrapping and a single statistic.
 In addition, we prefer the maximum likelihood method for its straight forward treatment of the errors in the LOSV measurements, which will become important in the practical application to real data \citeeg{Boada2016a}.
@@
 Specifically, while there is little difference between using galaxies and their host DM subhalos, there is a significant over estimation of the LOSVD when using galaxies/subhalos compared to DM particles \citep{Munari2013}.
-We follow other works \citeeg{Kirk2015, Sifon2015a} using the scaling relation, given in Equation~\ref{eq:power law} from \cite{Munari2013} to facilitate comparisons with other observational studies, which rely on galaxies as tracers.
+We follow other works \citeeg{Kirk2015, Sifon2015a} using the scaling relation, given in Equation~\ref{eq:power law} to facilitate comparisons with other observational studies, which rely on galaxies as tracers.
 
@@
 For internal consistency between this and the ML based method we use 70\% of the clusters to establish a conditional probability density of $p(M_{200c} | \vec{x})$ which we then use as the cluster mass probability density for the remaining clusters with similar features.
-In this way we, ``train'' the probability density using the existing simulated data, and apply it to the ``test'' sample (the remaining 30\% of the data not used as the ``training'' set).
+In this way we, ``train'' the probability density using the existing simulated data, and apply it to the ``test'' sample (the remaining 30\% of the data not used as the training set).
 
@@
 For the clusters making up the \emph{test} sample the mass is unknown (it is what we are trying to predict) but the other features are known.
-To determine the mass probability distribution of a test cluster, $P(M_{200c})$, we combine the conditional probability distribution, $P(M_{200c}|\vec{x})$, created previously with the probability distribution of $\sigma$ through Equation~\ref{eq: Pm}.
+To determine the mass probability distribution of a test cluster, $P(M_{200c})$, we combine the conditional probability distribution, $P(M_{200c}|\vec{x})$, created previously with the probability distribution of $\sigma$, the LOSVD, through Equation~\ref{eq: Pm}.
 \begin{equation}\label{eq: Pm}
@@
 
-We compare the results from the Targeted and Survey observing strategies to the results of a ``Perfect'' survey, where the redshift (and therefore LOSV) of each galaxy in the cluster is known perfectly).
+We compare the results from the Targeted and Survey observing strategies to the results of a ``Perfect'' survey, where the redshift (and therefore LOSV) of each galaxy, regardless of observational limits, in the cluster is known perfectly.
 
@@
 
-As discussed in Section \ref{sec: observations} the observational constraints place limits on the total number of clusters member galaxies expected to be recovered.
+As discussed in Section \ref{sec: observations}, the observational constraints place limits on the total number of clusters member galaxies expected to be recovered.
 Knowing these limits will provide important information for potential future follow up or Targeted observations.
 Figure \ref{fig: recovery} shows the recovery fraction of member galaxies, the number of observed galaxies divided by the number of actual galaxies ($N_{obs}/N_{True}$), as a function of both redshift and cluster mass.
-We require a detection of ($N_{obs} >=5$) galaxies for a cluster to be “detected” and included in this figure.
+We require a detection of $N_{obs} >=5$ galaxies for a cluster to be ``detected'' and included in this figure.
 As expected, the Targeted observing strategy where the individual clusters are targeted through several dithers to ensure near complete coverage, performs significantly better than the Survey observing strategy across all redshifts and cluster masses.
-With Perfect knowledge, recovery fraction would be unity across all redshifts and cluster masses.
+With Perfect knowledge, recovery fraction would be unity across all redshifts and cluster masses where clusters exist.
 
-For the clusters recovered as a function of redshift (y-direction of Figure~\ref{fig: recovery}), there are two effects at work.
-The decrease in recovery fraction with increasing redshift is a magnitude effect.
-Increasing redshift results in a lower galaxy recovery fraction.
-Because HETDEX is limited in apparent magnitude, we expect to recovery fewer galaxies at higher redshift.
-We confirm this by limiting the cluster galaxy detection by absolute magnitude, by observing all galaxies with $M_g < -11$.
-This increases the recovery fraction to $>70\%$ at all redshifts, implying the decline is a result of the apparent magnitude cluster galaxy detection threshold.
-The second key feature is the strong decline in clusters recovered from Survey observations.
-This is due to gaps in the VIRUS IFU.
+For the Targeted observations, shown in the left panel of Figure~\ref{fig: recovery}, the pattern of decreasing recovery fraction as a function of redshift (y-direction) is due to the observational limits imposed.
+Because HETDEX is limited in apparent magnitude, we expect to recovery fewer galaxies at higher redshift, where the galaxies are often below our $5\sigma$ detection threshold.
+We confirm this by converting all observed galaxies apparent magnitudes into absolute magnitudes and then limiting our survey to galaxies with $M_g < -11$ Mag.
+This increases the recovery fraction to $>70\%$ at all redshifts.
+
+For the recovery fraction as a function of true cluster mass (x-direction), we find a general decrease in the recovery fraction of member galaxies with increasing cluster mass.
+We also find that, in general, cluster mass increasing with increasing redshift.
+This causes our recovery fraction as a function of cluster mass to suffer from the same magnitude effects as discussed previously.
+Because there are few high mass ($M_{200c}>5\times10^{14}$ \Msol) clusters, many of which are at moderately high redshift, the higher redshift cluster members suffer from the limiting apparent magnitude and suppress the recovery fraction at fixed mass.
+If we were to limit the Survey to $z<0.2$ we find the recovery fraction of clusters, across all masses, increases substantially, and we find a much more consistent detection fraction across all masses.
+
+For the Survey observations, the right panel of Figure~\ref{fig: recovery}, all of the same effects are at work.
+In addition we find that the fill factor, due to the gaps between the VIRUS IFUs, further reduces the number of cluster members detected.
 The median recovery fraction in Survey observations is almost exactly 4.5 times less than the Targeted median recovery fraction.
-As the total filling factor of the Survey increases the two lines will converge.
+As the total filling factor of the Survey observations increases the two lines will converge.
 
-The recovery rate as a function of cluster mass, x-direction of Figure \ref{fig: recovery}, shows that of the the low mass clusters we detect ($N_{obs} >5$), we observe the majority of the galaxies.
-This also shows a rapid decrease in the detection fraction, which can again be explained by considering absolute magnitudes instead of apparent magnitudes, as above.
-Because there are few high mass ($M>5\times10^{14}$ \Msol) clusters, many of which are at moderately high redshift, the higher redshift cluster members suffer from the limiting apparent magnitude and suppress the recovery fraction at fixed mass.
-If we were to limit the Survey to $z<0.2$ we find the recovery fraction of clusters, at all masses, increases substantially, and we find a much more consistent detection fraction across all masses.
-Again perfect observations would detect all members, at all masses, so in this way, Figure~\ref{fig: recovery} is really just a statement about the magnitude limit and [\ion{O}{ii}] line-flux limit of the survey.
+Figure~\ref{fig: recovery} is really just a statement about the magnitude limit and [\ion{O}{ii}] line-flux limit of the survey.
+For Perfect observations, we would detect all members across all cluster masses and redshifts.
+Recovery fractions of clusters located a the low end of the redshift distribution will improve the most by followup targeted observations.
+But generally, the number of members observed (and subsequently more accurate cluster mass estimates) will benefit from followup observations regardless of the redshift.
+So followup observations should be tailored to the specific science goal.
 
@@
 For each method we consider observations with Perfect knowledge, Targeted observations and Survey observations.
-The cluster masses presented here are recovered using the best possible conditions, where we have Perfect knowledge of the cluster membership.
+The cluster masses presented here are recovered using the best possible conditions, where we have perfect knowledge of the cluster membership.
 In reality, the mass recovery levels presented in this section represent an upper bound (the best) on the accuracy achievable through this method.
@@
 And, while there are many possible metrics to evaluate performance, we compute two: the average bias (given in Table \ref{tbl:mass bias})
-\begin{equation}
+\begin{equation}\label{eqn: bias}
 \mathrm{\mu_{bias}}(y,y_{pred}) = \frac{1}{N} \sum_{i=1}^N (y_{pred,i} - y_i).
@@
 where $y$ are the true values and $y_{pred}$ are the predicted values, and the scatter about the bias (given in Table \ref{tbl:mass scatter})
-\begin{equation}
+\begin{equation}\label{eqn: scatter}
 	\sigma_{bias}(y,y_{pred}, \mu_{bias}) = \bigg{[}\frac{1}{N-1} \sum_{i=1}^N (y_{pred,i} - y_i - \mu_{bias})^2 \bigg{]}^{1/2}
@@
 Also, as the number of cluster galaxies decreases the LOSVD PDF is poorly sampled leading to poorly recovered cluster masses due to numerical effects.
-
-% \editorial{\cite{Ntampaka2015} does have a discussion about how well they do with contaminated galaxy catalogs.
-We could do something similar and have a similar discussion, but I'm not sure it is worth it.
-Should be simple enough to do with the Targeted catalog, but with the HETDEX catalog it would be pretty bad IMO.
-We should also talk about how often the true mass lies within the error bars.
-Many of them are going to be with the 68\% range, but we can drop the error estimates to $0.5\sigma$ if that actually means anything}
 
@@
 Generally, we find that the single parameter probability and ML methods perform significantly poorer than the power law method, especially at low cluster masses.
-When combined with the cluster redshift, the predicted cluster masses are improved, even though it is unclear exactly why the additional information should effect the predicted cluster mass.
+When combined with the cluster redshift, the predicted cluster masses are improved, because the range of cluster masses decrease with increasing redshift (see Figure~\ref{fig: recovery}).
 The final addition of the number of observed galaxies, $N_{gal}$ acts as a type of richness estimate, and significantly improves both the bias and the amount of scatter in the predicted masses.
@@
 \centering
-\caption{Mean bias ($M_{pred}$ - $M_{200c}$) for different bins of predicted cluster mass.
+\caption{Mean bias (Eqn.~\ref{eqn: bias}) for different bins of predicted cluster mass.
 This table shows the bias in the predicted cluster mass for the perfect (top section), Targeted (middle section), and Survey (bottom section) observations in different predicted mass bins.
@@
 The columns represent bins of predicted galaxy cluster mass and the individual values show the bias and scatter of the true cluster mass.
-The three horizontal sections represent perfect, Targeted and Survey observations respectively.
+The three horizontal sections represent Perfect, Targeted and Survey observations respectively.
 So, for example, if a cluster mass is predicted using the $ML_{\sigma, z}$ method and Targeted observations to be Log M/\Msol\ $=13-13.5$, it is biased upward by $0.03\pm{0.003}$ dex.
 
- A few caveats apply to the numbers given in Table \ref{tbl:mass bias} and Table \ref{tbl:mass scatter}.
-While we provide corrections for cluster masses above $10^{15}$ \msol, they are estimated from only a handful of objects, and do not constitute a representative sample of clusters.
-On the opposite end of the cluster mass spectrum, Survey observations of low mass clusters are incomplete for two potential reasons.
-There are very few, if any, clusters detected with Survey observations below $10^{12}$ \msol.
-Missing corrections above $10^{12}$ \msol\ in the probability based methods are due to low number statstics and an inability to sample the cluster mass PDF well enough to assign cluster mass predictions.
-
-\subsection{Significance of Training Sample Cosmology Choice}
-All simulations (including that used for Buzzard) use specific choices for cosmological parameters.
-When using simulation data to train ML methods, we incorporate all of those assumptions into the learned feature associations.
-This could lead to a notable bias when applying the ML method to data (real or simulated) which has significantly different cosmological assumptions.
-
-We turn to the Millennium simulation where the underlying cosmological assumptions differ substantially from Buzzard.
-The Millennium simulation adopts a flat cosmological model based of the values derived from the Two-degree Field Galaxy Redshift Survey \citep{Colless2001} and the first year data of the \emph{Wilkinson Microwave Anisotropy Probe} (WMAP; \citealt{Spergel2003}): $\Omega_\Lambda = 0.75$, $\Omega_M = 0.25$, $\sigma_8 = 0.9$, $n_s = 1$ and $H_0= 73$ \kms \mpc.
-The clusters in Millennium provide a testing sample to understand how a training sample derived from Buzzard will impact the mass recovery on a wholly new dataset.
-
-We repeat our analysis using cluster halo and galaxy catalogs from the Millennium simulation \citep{Springel2005a} obtained via querying the Millennium online database\footnote{http://gavo.mpa-garching.mpg.de/Millennium/} \citep{Lemson2006}.
-The Millennium simulation tracks $2160^3$ dark matter particles of $8.6\times 10^8 ~h^{-1}$ \Msol\ inside a comoving 500 $(h^{-1} \mathrm{Mpc})^3$ box from $z=127$ to 0.
-The halo catalogs are created using a friends-of-friends algorithm \citeeg{Turner1976} with linking length, $b=0.2$.
-The halos are populated with galaxies using a semi-analytical model described in \cite{Croton2006, DeLucia2006, DeLucia2007a}.
-
-We select 4806 clusters, comprised of 623,663 galaxies, at $0.02 < z < 0.5$ and $M > 10^{13}$ \Msol, and apply the same data processing as with the Buzzard galaxies.
-We begin by assigning each galaxy an [\ion{O}{ii}] flux value (see Section \ref{sec: oii luminosity}), and ``observe'' each galaxy using realistic (see Section \ref{sec: observations}) observational limits.
-After recovering 3750 clusters which have at least five galaxies observed, we calculate the LOSVD of each cluster as in Section \ref{sec: LOSVD}.
-
-\begin{figure} 
-	\includegraphics[width=\columnwidth]{figures/millBuzzComparison.pdf} 
-	\caption{\emph{Top:} ML based cluster mass predictions for the Millennium simulation clusters where the ML method has been trained with either a subset of the Millennium clusters (solid line) or the Buzzard catalog (dashed line).
-The shaded areas show the 68\% scatter around the median.
-The solid black line shows the 1:1 relation.The solid black line shows the 1:1 relation.
-\emph{Bottom:} The fractional error (Equation~\ref{eq: fractional error}) also as a function of true cluster mass.
-The similarity of the predictions with the different training sets demonstrates how the ML method is not sensitive to the underlying cosmological assumptions.} \label{fig: mill buzz comparison}
-\end{figure}
-
-We conduct our test in two ways.
-Both use the ML methods (see Section \ref{sec:machine learning method}) to predict the cluster masses of the Millennium clusters, but each test uses a different training set.
-First, we use the full set of clusters detected in the Buzzard catalogs (14,000 clusters with $M > 10^{11}$ \msol) to train the ML.
-Second, the Millennium clusters are split into training-testing samples.
-This provides a test case where we have different cosmological choices between the training and testing samples, and the same cosmological assumptions in both samples.
-
-The top panel of Figure \ref{fig: mill buzz comparison} shows the ML predicted cluster masses for the $\sim$4000 Millennium clusters as a function of true cluster mass.
-The orange (Millennium) and green (Buzzard) colors indicate the two different training samples.
-The median (solid and dashed lines) predicted cluster masses show similar trends regardless of the training data set used.
-Figure \ref{fig: mill buzz comparison}'s bottom panel shows the fraction error (Equation~\ref{eq: fractional error}) also as a function of true cluster mass.
-The large amount of scatter (the shaded area) in the fractional error for the Buzzard trained predictions is due to the training set including clusters with masses below the $M = 10^{13}$ \Msol\ threshold for the Millennium clusters.
-This allows the ML method to predict masses which can be significantly different, whereas the Millennium training set does not include $M < 10^{13}$ \Msol\ clusters, which reduces the scatter of the predicted masses.
-
-Based on these tests, we do not find a significant cause for concern with using trained ML methods to predict our galaxy cluster masses when the underlying cosmological choices are different.
-This highlights the versatility of our chosen ML method.
-The ML method could be further diversified by including cluster measurements from a wide range of cosmological simulations (or observations) which, in affect, marginalizes over all the cosmological assumptions further reducing the dependence.
-
-\section{HETDEX as a Galaxy Cluster Survey at $z < 0.5$}\label{sec:discussion}
-
-\subsection{Constraints on Cosmological Parameters}
 \begin{table*}
 \centering
-\caption{Scatter in cluster mass after bias correction for different bins of predicted cluster mass.
+\caption{Scatter (Eqn.~\ref{eqn: scatter}) in cluster mass after bias correction for different bins of predicted cluster mass.
 This table shows the scatter in the predicted cluster mass for the perfect (top section), Targeted (middle section), and Survey (bottom section) observations in different predicted mass bins.
@@
 
+ A few caveats apply to the numbers given in Table \ref{tbl:mass bias} and Table \ref{tbl:mass scatter}.
+While we provide corrections for cluster masses above $10^{15}$ \msol, they are estimated from only a handful of objects, and do not constitute a representative sample of clusters.
+This becomes particularly apparent for the probability methods with many features.
+As the number of observed features increases the number of training clusters in any particular bin decreases.
+This leads to the strange behavior seen for the high mass clusters and probability methods.
+On the opposite end of the cluster mass spectrum, Survey observations of low mass clusters are incomplete for two potential reasons.
+There are very few, if any, clusters detected with Survey observations below $5\times10^{12}$ \msol.
+Therefore, while we show these points in Figures~\ref{fig:Probability comparison} and \ref{fig: ML comparison}, we exclude their biases and scatters from Tables~\ref{tbl:mass bias} and \ref{tbl:mass scatter}.
+
+We find that the method which produce the lowest scatter and bias depends on the mass of the cluster in question and the type of observations used.
+For the Targeted observations, the power law method outperforms all other methods, in terms of bias and scatter, for the highest mass clusters.
+But outside of the two highest mass bins, the $ML_{\sigma, z, N_{gal}}$ method shows the smallest amount of scatter and bias most consistently.
+With Survey observations, the power law again provides the lowest bias in the highest cluster mass bins, but is outperformed in terms of scatter by the other two methods.
+Again we find that the $ML_{\sigma, z, N_{gal}}$ method shows the smallest amount of scatter and bias most consistently across the cluster mass range in question.
+
+\subsection{Significance of Training Sample Cosmology Choice}
+All simulations (including that used for Buzzard) use specific choices for cosmological parameters.
+When using simulation data to train ML methods, we incorporate all of those assumptions into the learned feature associations.
+This could lead to a notable bias when applying the ML method to data (real or simulated) which has significantly different cosmological assumptions.
+
+We turn to the Millennium simulation where the underlying cosmological assumptions differ substantially from Buzzard.
+The Millennium simulation adopts a flat cosmological model based of the values derived from the Two-degree Field Galaxy Redshift Survey \citep{Colless2001} and the first year data of the \emph{Wilkinson Microwave Anisotropy Probe} (WMAP; \citealt{Spergel2003}): $\Omega_\Lambda = 0.75$, $\Omega_M = 0.25$, $\sigma_8 = 0.9$, $n_s = 1$ and $H_0= 73$ \kms \mpc.
+The clusters in Millennium provide a testing sample to understand how a training sample derived from Buzzard will impact the mass recovery on a wholly new dataset.
+
+We repeat our analysis using cluster halo and galaxy catalogs from the Millennium simulation \citep{Springel2005a} obtained via querying the Millennium online database\footnote{http://gavo.mpa-garching.mpg.de/Millennium/} \citep{Lemson2006}.
+The Millennium simulation tracks $2160^3$ dark matter particles of $8.6\times 10^8 ~h^{-1}$ \Msol\ inside a comoving 500 $(h^{-1} \mathrm{Mpc})^3$ box from $z=127$ to 0.
+The halo catalogs are created using a friends-of-friends algorithm \citeeg{Turner1976} with linking length, $b=0.2$.
+The halos are populated with galaxies using a semi-analytical model described in \cite{Croton2006, DeLucia2006, DeLucia2007a}.
+
+We select 4806 clusters, comprised of 623,663 galaxies, at $0.02 < z < 0.5$ and $M > 10^{13}$ \Msol, and apply the same data processing as with the Buzzard galaxies.
+We begin by assigning each galaxy an [\ion{O}{ii}] flux value (see Section \ref{sec: oii luminosity}), and ``observe'' each galaxy using realistic (see Section \ref{sec: observations}) observational limits.
+After recovering 3750 clusters which have at least five galaxies observed, we calculate the LOSVD of each cluster as in Section \ref{sec: LOSVD}.
+
+\begin{figure} 
+	\includegraphics[width=\columnwidth]{figures/millBuzzComparison.pdf} 
+	\caption{\emph{Top:} ML based cluster mass predictions for the Millennium simulation clusters where the ML method has been trained with either a subset of the Millennium clusters (solid line) or the Buzzard catalog (dashed line).
+The shaded areas show the 68\% scatter around the median.
+The solid black line shows the 1:1 relation.
+\emph{Bottom:} The fractional error (Equation~\ref{eq: fractional error}) also as a function of true cluster mass.
+The similarity of the predictions with the different training sets demonstrates how the ML method is not sensitive to the underlying cosmological assumptions.} \label{fig: mill buzz comparison}
+\end{figure}
+
+We conduct our test in two ways.
+Both use the ML methods (see Section \ref{sec:machine learning method}) to predict the cluster masses of the Millennium clusters, but each test uses a different training set.
+First, we use the full set of clusters detected in the Buzzard catalogs (14,000 clusters with $M > 10^{11}$ \msol) to train the ML.
+Second, the Millennium clusters are split into training-testing samples.
+This provides a test case where we have different cosmological choices between the training and testing samples, and the same cosmological assumptions in both samples.
+
+The top panel of Figure \ref{fig: mill buzz comparison} shows the ML predicted cluster masses for the $\sim$4000 Millennium clusters as a function of true cluster mass.
+The orange (Millennium) and green (Buzzard) colors indicate the two different training samples.
+The median (solid and dashed lines) predicted cluster masses show similar trends regardless of the training data set used.
+Figure \ref{fig: mill buzz comparison}'s bottom panel shows the fraction error (Equation~\ref{eq: fractional error}) also as a function of true cluster mass.
+The large amount of scatter (the shaded area) in the fractional error for the Buzzard trained predictions is due to the training set including clusters with masses below the $M = 10^{13}$ \Msol\ threshold for the Millennium clusters.
+This allows the ML method to predict masses which can be significantly different, whereas the Millennium training set does not include $M < 10^{13}$ \Msol\ clusters, which reduces the scatter of the predicted masses.
+
+Based on these tests, we do not find a significant cause for concern with using trained ML methods to predict our galaxy cluster masses when the underlying cosmological choices are different.
+This highlights the versatility of our chosen ML method.
+The ML method could be further diversified by including cluster measurements from a wide range of cosmological simulations (or observations) which, in affect, marginalizes over all the cosmological assumptions further reducing the dependence.
+
+\section{HETDEX as a Galaxy Cluster Survey at $z < 0.5$}\label{sec:discussion}
+
+\subsection{Constraints on Cosmological Parameters}
 Galaxy clusters are sensitive probes of $\Omega_m$, the total mass ($\Omega_b + \Omega_c$) density in the universe, by tracing the peaks in the universal matter density often referred to as the power spectrum of matter density fluctuations or the matter power spectrum and $\sigma_8h^{-1}$, the normalization of the power spectrum, by the comparison of the number density of observed clusters to that predicted in cosmological models.
@@
 
-Because of the simplifying assumptions, and the superior quality of the data (no contamination, signal-to-noise issues, etc.), realistic expectations for HETDEX is to directly constrain $\sigma_8h^{-1}$ to better precision than other methods (\eg, CMB, WL, X-ray) seems bleak.
+Because of the simplifying assumptions, and the superior quality of the data (no contamination, signal-to-noise issues, etc.), realistic expectations for HETDEX is to directly constrain $\sigma_8h^{-1}$ is not yet competitive with other methods (\eg, CMB, WL, X-ray).
 For example, \cite{deHaan2016} constrain $\sigma_8h^{-1}$ to $\sim5$\% using a sample of 337 SZE detected clusters from the SPT-SZE survey.
@@
 For a fully Targeted survey, about 14,000 clusters, this cluster mass calibration uncertainty reduces to $>1\%$.
+So while, the contraints produced by HETDEX will be larger than some other studies, the type of data provided by HETDEX will enable an independent calibration from other cluster mass measurements.
+This will provide important systematics checks on other studies and will ultimately improve the measurements of $\sigma_8h^{-1}$ .
 
@@
 
-We limit our clusters to those with $10 \leq \lambda < 130$ in our fitting analysis because there are very few clusters with $\lambda>130$ and to better coincide with other observational studies \citeeg{Saro2015} which have lower limits on $\lambda$.
+We limit our clusters to those with $10 \leq \lambda < 130$ in our fitting analysis because above $\lambda=130$ there are too few clusters and number-counting errors dominate.
+Other observational studies \citeeg{Saro2015} which have lower limits on $\lambda$, so we exclude anything less than $\lambda=10$.
 For a richness-mass relation with an intrinsic scatter of $\langle \sigma_{M|\lambda} \rangle = 0.25$ dex, we find a best-fitting relation for the Targeted observations as
@@
 \end{equation} 
-This gives $M_{200c} = (1.22\pm...)\times10^{14}$ \Msol and $M_{200c} = (1.44\pm...)\times10^{14}$ \Msol\ at $\lambda=40$ for the Targeted and Survey observations respectively.
+This gives $M_{200c} = (1.22\pm...)\times10^{14}$ \Msol\ and $M_{200c} = (1.44\pm...)\times10^{14}$ \Msol\ at $\lambda=40$ for the Targeted and Survey observations respectively.
 In both cases, this normalization differs significantly from the $M_{200c} \approx 2.1\times10^{14} h^{-1}$ \Msol\ found in recent work \cite{Li2016, Simet2016}.
@@
 % }
+
+% \editorial{\cite{Ntampaka2015} does have a discussion about how well they do with contaminated galaxy catalogs.
+We could do something similar and have a similar discussion, but I'm not sure it is worth it.
+Should be simple enough to do with the Targeted catalog, but with the HETDEX catalog it would be pretty bad IMO.
+We should also talk about how often the true mass lies within the error bars.
+Many of them are going to be with the 68\% range, but we can drop the error estimates to $0.5\sigma$ if that actually means anything}

### 2016-05-18 paper1.tex
more casey comments

--- 2016-05-13 ms.tex
@@
 We benchmark both surveys against spectroscopic observations with ``perfect" knowledge of galaxy line-of-sight velocities.
-We find that with HETDEX we can recover cluster masses to $\sim0.1$ dex which can be further improved to $<0.1$ dex with targeted followup observations.
-This level of cluster mass recovery enables us to place $<20$\% constraints on $\sigma_8$, and leverage the unique properties of the observations to provide important calibrations for the optical richness-cluster mass relation.
+With HETDEX, we can recover cluster masses to $\sim0.1$ dex which can be further improved to $<0.1$ dex with targeted follow-up observations.
+This level of cluster mass recovery enables constraints on $\sigma_8$ to $<20$\%, and the unique properties of the observations will provide important calibrations for the optical richness-cluster mass relation.
 \end{abstract}
@@
 As mass is not a direct observable, a lot of work is underway to characterize galaxy cluster masses with an observable feature of galaxy clusters.
-The goal is to constrain, as best possible, $P(M|z, \vec{x})$ the probability ($P$) that a galaxy cluster of given mass ($M$), located at redshift ($z$) determined using an observable parameter or parameters ($\vec{x}$).
-Generally, cluster mass calibrations fall into two distinct camps, simulation based and direct or statistical calibration.
+The goal is to constrain $P(M|z, \vec{x})$ the probability density ($P$) that a galaxy cluster of given mass ($M$), located at redshift ($z$) determined using an observable parameter or parameters ($\vec{x}$).
+Generally, cluster mass calibrations are done in one of two ways, through simulations or direct or statistical calibration.
 
-One could use various simulations to attempt to calibrate this observable--mass relation \citeeg{Vanderlinde2010, Sehgal2011}.
+One could use various simulations to attempt to calibrate this observable-mass relation \citeeg{Vanderlinde2010, Sehgal2011}.
 However, the primary challenge to this method is the incomplete understanding of the baryonic physics which take place in galaxy cluster environments.
@@
 
-The second broad camp is the direct calibration of cluster masses.
+The second broad method is the direct calibration of cluster masses.
 This recipe has two distinct but not always independent tracks.
-The ``direct'' method uses direct observations of a small set of clusters and then uses known mass estimators, including X-ray temperatures and luminosities \citeeg{Mantz2010, Rykoff2014}, microwave observations \citeeg{Vanderlinde2010, Sehgal2011}, optical richness \citeeg{Abell1958, Rykoff2012} or weak lensing (WL; \eg\ \citealt{Rozo2010}) as examples, which provide a ``true'' mass.
-This directly calibrates the observable--mass relation which is then applied to a much larger sample.
+The ``direct'' method uses observations of a relatively small set of clusters and then uses known mass estimators, including X-ray temperatures and luminosities \citeeg{Mantz2010, Rykoff2014}, microwave observations \citeeg{Vanderlinde2010, Sehgal2011}, optical richness \citeeg{Abell1958, Rykoff2012} or weak lensing (WL; \eg\ \citealt{Rozo2010}) as examples, which provide a ``true'' mass.
+This directly calibrates the observable-mass relation which is then applied to a much larger sample.
 The complications lie in that the ``true'' masses are, in fact, estimations, and the methods used to recover these cluster masses are subject to their own limitations.
@@
 Optically, the on going Dark Energy Survey (DES; \citealt{DES2005}) and planned Large Synoptic Survey Telescope (LSST; \citealt{LSST2012}) will identify many thousands of clusters to much lower masses than is possible with SZE measurements.
-However, regardless of the discovery method used, spectroscopic followup is needed to further constrain $P(M|z,X)$.
-But as the cluster dataset grows to many tens of thousands of clusters individual followup becomes increasingly impractical.
+However, regardless of the discovery method used, spectroscopic follow-up is needed to further constrain $P(M|z,X)$.
+But as the cluster dataset grows to many tens of thousands of clusters individual follow-up becomes increasingly impractical.
 Therefore, large spectroscopic surveys are needed to more fully constrain the observable--mass relation of clusters.
@@
 Finally we summarize our findings in Section \ref{sec:summary}.
-A followup to this work \citep{Boada2016a} will investigate how the techniques developed here will work in practice.
+A follow-up to this work \citep{Boada2016a} will investigate how the techniques developed here will work in practice.
 
@@
 \subsection{The Buzzard Mock Catalogs}
-\begin{figure*} 
-	\includegraphics[width=\textwidth]{figures/oii_sdss.pdf} 
-	\caption{\textit{Left}: CMD of 503,113 $z<0.2$ galaxies take from the SDSS DR12 where the shading scales with the density of points.
-The two colored boxes show regions containing potential catalog galaxies.
-\textit{Right}: Probability histograms of the Log [\ion{O}{ii}] luminosity for the SDSS galaxies located in the two highlighted regions on the right.
-The [\ion{O}{ii}] luminosities are assigned to catalog galaxies from slice sampling the probability histogram and converted to fluxes using the redshift of each galaxy.} \label{fig: oii sdss}
-\end{figure*}
-
 The Buzzard mock galaxy catalogs cover 398.49 \degsq\ between $4^h< RA < 6^h$ and $-61\degree < DEC < -41\degree$ and are derived from a combination of Sub-halo Abundance Matching (ShAM) and ADDSEDs (Adding Density Dependent Spectral Energy Distributions) tied to an in house n-body cosmological simulation.
@@
 Dark matter (DM) n-body simulations are run using {\sc LGadget-2} (a version of {\sc Gadget-2}; \citealt{Springel2005}).
+The Buzzard catalogs adopt the following cosmological parameters: $\Omega_m = 0.286$, $\Omega_\Lambda = 0.714$, $H_0 = 70$ \kms \mpc, $\sigma_8 = 0.82$, and $n_s = 0.96$.
 The DM halos are identified using the {\sc ROCKSTAR} halo finder \citep{Behroozi2013} which also calculates halo masses.
@@
 \subsection{Conditional [\ion{O}{ii}] Flux Probability Distribution Functions}\label{sec: oii luminosity}
+\begin{figure*} 
+	\includegraphics[width=\textwidth]{figures/oii_sdss.pdf} 
+	\caption{\textit{Left}: CMD of 503,113 $z<0.2$ galaxies take from the SDSS DR12 where the shading scales with the density of points.
+The two colored boxes show regions containing potential catalog galaxies.
+\textit{Right}: Probability histograms of the Log [\ion{O}{ii}] luminosity for the SDSS galaxies located in the two highlighted regions on the right.
+The [\ion{O}{ii}] luminosities are assigned to catalog galaxies from slice sampling the probability histogram and converted to fluxes using the redshift of each galaxy.} \label{fig: oii sdss}
+\end{figure*}
 We use the SDSS DR12 \citep{Alam2015} catalogs to assign [\ion{O}{ii}] emission line strengths to the galaxies in the Buzzard catalog.
-We use 503,113 galaxies from $z = 0.05 - 0.2$, which are selected with no redshift warning, and place each galaxy on a color-magnitude diagram (CMD) of $M_r$ and $g-r$; see the left panel of Figure \ref{fig: oii sdss}.
+We use 503,113 objects classified as galaxies selected over $z = 0.02 - 0.2$ with {\sc zwarning $=0$} and a measured [\ion{O}{ii}] line flux signal-to-noise of five.
+Figure~\ref{fig: oii sdss} shows the color-magnitude diagram (CMD) of $M_r$ and $g-r$ for these galaxies.
 
@@
 Figure~\ref{fig: oii sdss} illustrates this process.
-The numbered boxes in the left panel show two bins ($M_r, g-r = -17.7,~0.49$ and $M_r, g-r = -21.4,~1.24$) in the CMD of $0.05 < z < 0.2$ SDSS galaxies.
+The numbered boxes in the left panel show the bins corresponding to two example Buzzard galaxies ($M_r, g-r = -17.7,~0.49$ and $M_r, g-r = -21.4,~1.24$).
 The right panel shows the Log [\ion{O}{ii}] luminosity distribution functions, $p($[\ion{O}{ii}]$| M_r, g-r)$, which we use to assign [\ion{O}{ii}] luminosity to each object.
@@
 	\caption{Representative observation tiling scheme for the HETDEX $16' \times 16'$ pointings.
-Each colored square is a single VIRUS IFU and the dashed octagons approximate the size of a single observation.
+Each turqoise square represents the position of a single VIRUS IFU, and the dashed octagons approximate the size of a single observation.
+Inside each IFU HETDEX will achieve near complete coverage through three dithers.
 See the text for more details.} \label{fig: ifu layout}
@@
 
-\editorial{There are quite a few words copied from Casey's SHELA paper.}
-HETDEX will perform a blind survey which will measure the redshifts of $8 \times 10^5$ LAE galaxies between $1.9 < z < 3.5$ using a collection of 78 wide-field IFUs spectrographs covering the wavelength region $3500 - 5500$~\AAA\ at R $\sim$ 750 \citep{Hill2008}.
+We designed the results study here to be used with HETDEX, a large blind spectroscopic survey.
+HETDEX will measure the redshifts of $8 \times 10^5$ LAE galaxies between $1.9 < z < 3.5$ using a collection of 78 wide-field IFU spectrographs covering the wavelength region $3500 - 5500$~\AAA\ at R $\sim$ 750 \citep{Hill2008}.
 The goal of these observations will be to provide sub-percent level measurements of the Hubble expansion parameter and the angular diameter distance at $z \sim 2$ via the large scale distribution of galaxies in the redshift range of HETDEX.
@@
 \subsection{Mock Observations}\label{sec: observations}
-This means that when selecting galaxies from the Buzzard catalog we assume an observation for all galaxies laying within a turquoise, IFU square in Figure~\ref{fig: ifu layout}.
+When selecting galaxies from the Buzzard catalog we assume an observation for all galaxies laying within a turquoise, IFU square in Figure~\ref{fig: ifu layout}.
+In practice, this is achieved by three dither positions at each pointing.
 Galaxies which lie between the IFUs are missed, as well as the galaxies which lie between the pointings, as there is no overlap between one pointing and the next.
@@
 The Survey observations mimic the HETDEX observation pattern across the sky, where no cluster is directly targeted and not all cluster member galaxies are observed.
-Both of these observations have HETDEX-like galaxy detection thresholds, and for comparison we also include a set of Targeted observations with ``perfect'' knowledge.
-Perfect observations assume no detection threshold, if a cluster member galaxy is observed, it is also detected.
-This provides an important best-case scenario, and differs from the true cluster properties because the cluster properties are still calculated.
+Both of these observations have HETDEX-like galaxy detection thresholds (described in the previous subsection), so while a galaxy may be observed, a redshift will only be measured if the galaxy satisfies the continuum brightness or emission line flux limits for the HETDEX survey.
+For comparison we also include a set of Targeted observations with ``perfect'' knowledge which assume no detection threshold, if a cluster member galaxy is observed, it is also detected.
+This provides an important best-case scenario, and differs from the true cluster properties between we are still calculating the cluster mass from the observed member galaxy velocity dispersions, and represent the best possible mass estimates using velocity dispersion as the observable.
 These observations provide three levels of quality with ``Perfect knowledge'' being the highest and Survey being the lowest.
@@
 \begin{equation}
-C_{BI} = M + \frac{\sum_{|u_i| < 1} (x_i - M)(1-u_i^2)^2}{\sum_{|u_i| < 1}(1-u_i^2)^2}
+C_{BI} = M + \frac{\sum_{|u_i| < 1} (z_i - M)(1-u_i^2)^2}{\sum_{|u_i| < 1}(1-u_i^2)^2}
 \end{equation}
-where $x_i$ are the individual redshifts, $M$ is the median redshift and $u_i$ is given by:
+where $z_i$ are the individual redshifts, $M$ is the median redshift and $u_i$ is given by:
 \begin{equation}
-	u_i = \frac{(x_i - M)}{C\,\mathrm{MAD}}.
+	u_i = \frac{(z_i - M)}{C\,\mathrm{MAD}}.
 \end{equation}
@@
 \end{equation}
-and $c$ is the speed of light in \kms, $z$ is the redshift of the individual galaxy, and $z_c$ is the overall cluster redshift described in the previous subsection.
+and $c$ is the speed of light, $z$ is the redshift of the individual galaxy, and $z_c$ is the overall cluster redshift described in the previous subsection.
 
@@
 We set the upper limit on the LOSVD as the LOSVD corresponding to a $10^{16}$ \Msol\ cluster at $z\sim0.0$, higher mass than any expected cluster in Buzzard.
-When the full distribution of LOSVDs is not used, the final LOSVD is quoted as the median value of the posterior probability distribution with 68\% error bars defined as the second momment of the same distribution.
+When the full distribution of LOSVDs is not used, the final LOSVD is quoted as the median value of the posterior probability distribution with 68\% error bars defined as the square root of second moment of the same distribution, the standard deviation.
 
@@
 \subsubsection{Other Estimates of Dynamical Mass -- Introduction}
-In the following sections we use two methods to predict the mass of a cluster based on other observables.
+In the following subsections we use two methods to predict the mass of a cluster based on other observables.
 Often the cluster mass is estimated based on a single observable, X-ray temperature, LOSVD, richness and others (see Section~\ref{sec: Introduction} for referenced examples).
@@
 
-In this method, the cluster masses are predicted much in the same way we assign [\ion{O}{ii}] flux to the Buzzard catalog galaxies.
-Figure~\ref{fig: probability corner} illustrates the process.
+In this method, the cluster masses are predicted using the method illustrated in Figure~\ref{fig: probability corner}.
 The left panel shows the two dimensional (joint probability) projections of the posterior probability distributions of the feature training data.
@@
 In practice we find that both methods produce similar results for a large number of trials.
-Therefore, we quote predicted masses as the most probable mass given by Equation~\ref{eq: expected mass} and associated 68\% error estimated through Equation~\ref{eq: variance}.
+Therefore, we quote predicted masses as the most probable mass given by Equation~\ref{eq: expected mass} and associated 68\% error estimated through the square root of Equation~\ref{eq: variance}.
 
@@
 RF estimators use a random subset of the training set at each fork to decide which path should be followed.
-The final prediction is then the average of all the final predictions from the trees.
+The final prediction is then the mean of all the final predictions from the trees.
 We use RF regression methods as implemented in {\sc Scikit-Learn} \citep{Pedregosa2012}.
 
-We note the subtle distinction that the ML method generates ``prediction intervals'' between observed and derived quantities (rather than ``confidence intervals'').
+The ML method generates ``prediction intervals'' between observed and derived quantities (rather than ``confidence intervals'').
 A prediction interval is an estimate of the interval encompassing future observations, with a certain probability.
@@
 Then the prediction can be returned as the full conditional probability distribution of all responses, which allows us to generate the prediction intervals.
-We report the 68\% prediction interval as the second moment of the full conditional probability distribution.
+We report the 68\% prediction interval as the square root of the second moment of the full conditional probability distribution.
 
@@
 We discuss the accuracy of cluster dynamical mass derived from both the power law scaling relation (see Equation \ref{eq:power law}) and through the probability and ML methods.
-
-We compare the results from the Targeted and Survey observing strategies to the results of a ``Perfect'' survey, where the redshift (and therefore LOSV) of each galaxy, regardless of observational limits, in the cluster is known perfectly.
+We also compare the results from the Targeted and Survey observing strategies to the results of a ``Perfect'' survey, where the redshift of each galaxy, regardless of observational limits, in the cluster is known perfectly.
 
@@
 Knowing these limits will provide important information for potential future follow up or Targeted observations.
+We recover 14,189 clusters with Targeted observations and 1,760 clusters with Survey observations, where we require a detection of $N_{obs} >=5$ galaxies for a cluster to be detected.
 Figure \ref{fig: recovery} shows the recovery fraction of member galaxies, the number of observed galaxies divided by the number of actual galaxies ($N_{obs}/N_{True}$), as a function of both redshift and cluster mass.
-We require a detection of $N_{obs} >=5$ galaxies for a cluster to be ``detected'' and included in this figure.
 As expected, the Targeted observing strategy where the individual clusters are targeted through several dithers to ensure near complete coverage, performs significantly better than the Survey observing strategy across all redshifts and cluster masses.
@@
 For the Targeted observations, shown in the left panel of Figure~\ref{fig: recovery}, the pattern of decreasing recovery fraction as a function of redshift (y-direction) is due to the observational limits imposed.
-Because HETDEX is limited in apparent magnitude, we expect to recovery fewer galaxies at higher redshift, where the galaxies are often below our $5\sigma$ detection threshold.
-We confirm this by converting all observed galaxies apparent magnitudes into absolute magnitudes and then limiting our survey to galaxies with $M_g < -11$ Mag.
-This increases the recovery fraction to $>70\%$ at all redshifts.
+Because HETDEX is limited in apparent magnitude, we expect to recover fewer galaxies at higher redshift, where the galaxies are often below our $5\sigma$ detection threshold.
+For example, we tested this by constructing an artificial HETDEX-like survey, limited by volume for all galaxies with $M_g < -11$.
+In this case, our recovery fraction increases to $>70$\%, which shows that the flux limit is dominating the (lower) recovery of our flux-limited survey.
 
 For the recovery fraction as a function of true cluster mass (x-direction), we find a general decrease in the recovery fraction of member galaxies with increasing cluster mass.
-We also find that, in general, cluster mass increasing with increasing redshift.
-This causes our recovery fraction as a function of cluster mass to suffer from the same magnitude effects as discussed previously.
+This  is entirely a result of the flux limited survey (see previous paragraph).
 Because there are few high mass ($M_{200c}>5\times10^{14}$ \Msol) clusters, many of which are at moderately high redshift, the higher redshift cluster members suffer from the limiting apparent magnitude and suppress the recovery fraction at fixed mass.
@@
 
-Figure~\ref{fig: recovery} is really just a statement about the magnitude limit and [\ion{O}{ii}] line-flux limit of the survey.
+The recovery fractions in Figure~\ref{fig: recovery} are an outcome of the magnitude limit and [\ion{O}{ii}] line-flux limit of the survey.
 For Perfect observations, we would detect all members across all cluster masses and redshifts.
-Recovery fractions of clusters located a the low end of the redshift distribution will improve the most by followup targeted observations.
-But generally, the number of members observed (and subsequently more accurate cluster mass estimates) will benefit from followup observations regardless of the redshift.
-So followup observations should be tailored to the specific science goal.
+Recovery fractions of clusters located a the low end of the redshift distribution will improve the most by follow-up targeted observations.
+But generally, the number of members observed (and subsequently more accurate cluster mass estimates) will benefit from follow-up observations regardless of the redshift.
+So follow-up observations should be tailored to the specific science goal.
 
@@
 
-In this section we discuss the how accurately we recover the true cluster mass from a set of observations.
+In this section we discuss the accuracy of the recovered masses compared to the true cluster mass from a set of observations.
 We report on three methods, the power law based approach (Eq.
@@
 
-Because it represents the best possible scenario, the Perfect knowledge observations should serve as baseline to compare the power law based, probability based and ML cluster mass recovery methods.
+Because it represents the best possible scenario, the Perfect knowledge observations should serve as a baseline to compare the power law based, probability based and ML cluster mass recovery methods.
 And, while there are many possible metrics to evaluate performance, we compute two: the average bias (given in Table \ref{tbl:mass bias})
@@
 \end{equation}
-with $N$ clusters in a given bin. Both metrics evaluate how closely the ensemble of predicted cluster masses are to the true cluster masses, and in both cases values closer to zero are better.
+with $N$ clusters in a given bin. Both metrics evaluate how closely the ensemble of predicted cluster masses are to the true cluster masses.
 
@@
 In both Figures \ref{fig:Probability comparison} and \ref{fig: ML comparison}, we show the predicted ($M_{pred}$) versus true ($M_{200c}$) cluster masses for each of the two observing strategries.
-In each panel the solid black line is the 1:1 relationship, the solid purple line is the median recovered mass for the Targeted observing, and the turquoise, dashed line is the median recovered mass for the HETDEX-like observations.
-The shaded regions are the 68\% scatter around the median values (the 16\% and 84\% quartiles).
-For reference we also show the median masses recovered with Perfect knowledge as a dash-dotted orange line.
 The lower panels show the fractional cluster mass error defined as:
@@
 \end{equation}
-where $M_{pred}$ is the predicted cluster mass and $M_{200c}$ is the true cluster mass.
+where $M_{pred}$ is the predicted cluster mass and $M_{200c}$ is the true cluster mass. Higher values of $\epsilon$ indicate the predicted cluster mass exceeds the true cluster mass.
 
@@
 		&$\sigma, z$ & $0.25\pm{0.005}$ & $0.08\pm{0.003}$ & $-0.06\pm{0.003}$ & $-0.21\pm{0.015}$ & $-0.35\pm{0.016}$ & $-0.59\pm{0.145}$ \\
-		&$\sigma, z, N_{gal}$ & $0.13\pm{0.004}$ & $0.01\pm{0.003}$ & $-0.05\pm{0.003}$ & $-0.12\pm{0.018}$ & $-0.44\pm{0.177}$ & $-4.45\pm{3.444}$ \\
+		&$\sigma, z, N_{gal}$ & $0.13\pm{0.004}$ & $0.01\pm{0.003}$ & $-0.05\pm{0.003}$ & $-0.12\pm{0.018}$ & $-0.44\pm{0.177}$ & \nd \\
 		\hline
@@
 		&$\sigma, z$ & $0.61\pm{0.036}$ & $0.29\pm{0.012}$ & $0.08\pm{0.008}$ & $-0.11\pm{0.009}$ & $-0.38\pm{0.118}$ & $-0.48\pm{0.127}$ \\
-		&$\sigma, z, N_{gal}$ & $0.48\pm{0.038}$ & $0.18\pm{0.011}$ & $0.02\pm{0.007}$ & $-0.08\pm{0.008}$ & $-0.50\pm{0.203}$ & $-8.81\pm{3.695}$ \\
+		&$\sigma, z, N_{gal}$ & $0.48\pm{0.038}$ & $0.18\pm{0.011}$ & $0.02\pm{0.007}$ & $-0.08\pm{0.008}$ & $-0.50\pm{0.203}$ & \nd \\
 		\hline
@@
 		&$\sigma, z$ & $0.23\pm{0.003}$ & $0.19\pm{0.002}$ & $0.16\pm{0.002}$ & $0.55\pm{0.010}$ & $0.16\pm{0.009}$ & $0.39\pm{0.143}$ \\
-		&$\sigma, z, N_{gal}$ & $0.47\pm{0.007}$ & $0.14\pm{0.001}$ & $0.10\pm{0.001}$ & $0.54\pm{0.010}$ & $1.62\pm{0.090}$ & $9.31\pm{3.378}$ \\
+		&$\sigma, z, N_{gal}$ & $0.47\pm{0.007}$ & $0.14\pm{0.001}$ & $0.10\pm{0.001}$ & $0.54\pm{0.010}$ & \nd & \nd \\
 		\hline
@@
 		&$\sigma, z$ & $0.24\pm{0.003}$ & $0.24\pm{0.002}$ & $0.23\pm{0.002}$ & $0.56\pm{0.011}$ & $0.21\pm{0.012}$ & $0.36\pm{0.131}$ \\
-		&$\sigma, z, N_{gal}$ & $0.20\pm{0.003}$ & $0.19\pm{0.002}$ & $0.17\pm{0.002}$ & $0.67\pm{0.013}$ & $2.28\pm{0.126}$ & $8.56\pm{3.109}$ \\
+		&$\sigma, z, N_{gal}$ & $0.20\pm{0.003}$ & $0.19\pm{0.002}$ & $0.17\pm{0.002}$ & $0.67\pm{0.013}$ & \nd & \nd \\
 		\hline
@@
 		&$\sigma, z$ & $0.13\pm{0.028}$ & $0.19\pm{0.008}$ & $0.22\pm{0.006}$ & $0.21\pm{0.007}$ & $1.31\pm{0.084}$ & $0.32\pm{0.115}$ \\
-		&$\sigma, z, N_{gal}$ & $0.14\pm{0.030}$ & $0.18\pm{0.008}$ & $0.19\pm{0.005}$ & $0.19\pm{0.006}$ & $2.27\pm{0.145}$ & $9.19\pm{3.336}$ \\
+		&$\sigma, z, N_{gal}$ & $0.14\pm{0.030}$ & $0.18\pm{0.008}$ & $0.19\pm{0.005}$ & $0.19\pm{0.006}$ & \nd & \nd \\
 		\hline
@@
 This becomes particularly apparent for the probability methods with many features.
-As the number of observed features increases the number of training clusters in any particular bin decreases.
-This leads to the strange behavior seen for the high mass clusters and probability methods.
-On the opposite end of the cluster mass spectrum, Survey observations of low mass clusters are incomplete for two potential reasons.
-There are very few, if any, clusters detected with Survey observations below $5\times10^{12}$ \msol.
+As the number of observed features increases, the number of training clusters in any particular bin decreases.
+This leads to highly skewed biases and scatters for the high mass clusters and probability methods.
+We do not report any bin where such small number statistics dominate in Tables~\ref{tbl:mass bias} and \ref{tbl:mass scatter}.
+On the opposite end of the cluster mass spectrum, there are very few, if any, clusters detected with Targeted or Survey observations below $5\times10^{12}$ \msol.
 Therefore, while we show these points in Figures~\ref{fig:Probability comparison} and \ref{fig: ML comparison}, we exclude their biases and scatters from Tables~\ref{tbl:mass bias} and \ref{tbl:mass scatter}.
 
-We find that the method which produce the lowest scatter and bias depends on the mass of the cluster in question and the type of observations used.
+The method which produce the lowest scatter and bias depends on the mass of the cluster in question and the type of observations used.
 For the Targeted observations, the power law method outperforms all other methods, in terms of bias and scatter, for the highest mass clusters.
@@
 With Survey observations, the power law again provides the lowest bias in the highest cluster mass bins, but is outperformed in terms of scatter by the other two methods.
-Again we find that the $ML_{\sigma, z, N_{gal}}$ method shows the smallest amount of scatter and bias most consistently across the cluster mass range in question.
+The $ML_{\sigma, z, N_{gal}}$ method shows the smallest amount of scatter and bias most consistently across the cluster mass range in question.
 
-\subsection{Significance of Training Sample Cosmology Choice}
-All simulations (including that used for Buzzard) use specific choices for cosmological parameters.
+\subsection{Impact of Training Sample Cosmology}
+All simulations (including that used for Buzzard) use specific values for cosmological parameters.
 When using simulation data to train ML methods, we incorporate all of those assumptions into the learned feature associations.
-This could lead to a notable bias when applying the ML method to data (real or simulated) which has significantly different cosmological assumptions.
+One could imagine that the specific values of the cosmological parameters in the training sample could bias the ML results when applied to data (real or simulated) created from an unknown true set of cosmological parameters.
 
-We turn to the Millennium simulation where the underlying cosmological assumptions differ substantially from Buzzard.
+To test for this, we used the Millennium simulation as an alternative data set.
+The Millennium simulation uses a set of cosmological parameters that are substantially different from Buzzard.
 The Millennium simulation adopts a flat cosmological model based of the values derived from the Two-degree Field Galaxy Redshift Survey \citep{Colless2001} and the first year data of the \emph{Wilkinson Microwave Anisotropy Probe} (WMAP; \citealt{Spergel2003}): $\Omega_\Lambda = 0.75$, $\Omega_M = 0.25$, $\sigma_8 = 0.9$, $n_s = 1$ and $H_0= 73$ \kms \mpc.
@@
 The Millennium simulation tracks $2160^3$ dark matter particles of $8.6\times 10^8 ~h^{-1}$ \Msol\ inside a comoving 500 $(h^{-1} \mathrm{Mpc})^3$ box from $z=127$ to 0.
-The halo catalogs are created using a friends-of-friends algorithm \citeeg{Turner1976} with linking length, $b=0.2$.
-The halos are populated with galaxies using a semi-analytical model described in \cite{Croton2006, DeLucia2006, DeLucia2007a}.
 
-We select 4806 clusters, comprised of 623,663 galaxies, at $0.02 < z < 0.5$ and $M > 10^{13}$ \Msol, and apply the same data processing as with the Buzzard galaxies.
+We select 4,806 clusters, comprised of 623,663 galaxies, at $0.02 < z < 0.5$ and $M > 10^{13}$ \Msol, and apply the same data processing as with the Buzzard galaxies.
 We begin by assigning each galaxy an [\ion{O}{ii}] flux value (see Section \ref{sec: oii luminosity}), and ``observe'' each galaxy using realistic (see Section \ref{sec: observations}) observational limits.
@@
 
-The top panel of Figure \ref{fig: mill buzz comparison} shows the ML predicted cluster masses for the $\sim$4000 Millennium clusters as a function of true cluster mass.
+The top panel of Figure~\ref{fig: mill buzz comparison} shows the ML predicted cluster masses for the $\sim$4000 Millennium clusters as a function of true cluster mass.
 The orange (Millennium) and green (Buzzard) colors indicate the two different training samples.
 The median (solid and dashed lines) predicted cluster masses show similar trends regardless of the training data set used.
-Figure \ref{fig: mill buzz comparison}'s bottom panel shows the fraction error (Equation~\ref{eq: fractional error}) also as a function of true cluster mass.
-The large amount of scatter (the shaded area) in the fractional error for the Buzzard trained predictions is due to the training set including clusters with masses below the $M = 10^{13}$ \Msol\ threshold for the Millennium clusters.
+The bottom panel of Figure~\ref{fig: mill buzz comparison} shows the fraction error (Equation~\ref{eq: fractional error}) also as a function of true cluster mass.
+The large amount of scatter (the shaded area) in the fractional error for the Buzzard-trained predictions is due to the training set including clusters with masses below the $M = 10^{13}$ \Msol\ threshold for the Millennium clusters.
 This allows the ML method to predict masses which can be significantly different, whereas the Millennium training set does not include $M < 10^{13}$ \Msol\ clusters, which reduces the scatter of the predicted masses.
@@
 \subsection{Constraints on Cosmological Parameters}
-Galaxy clusters are sensitive probes of $\Omega_m$, the total mass ($\Omega_b + \Omega_c$) density in the universe, by tracing the peaks in the universal matter density often referred to as the power spectrum of matter density fluctuations or the matter power spectrum and $\sigma_8h^{-1}$, the normalization of the power spectrum, by the comparison of the number density of observed clusters to that predicted in cosmological models.
+Galaxy clusters trace the peaks in the universal matter density, often referred to as the power spectrum of matter density fluctuations or the matter power spectrum.
+This enables them to be sensitive probes of $\Omega_m$, the total mass ($\Omega_b + \Omega_c$) density, and $\sigma_8h^{-1}$, the normalization of the power spectrum.
+We constrain these parameters by the comparison of the number density of observed clusters to that predicted in cosmological models.
 Although, in reality, one measures $\sigma_8h^{-1}\Omega_m^q$, where the value of $q$ depends on the masses and redshifts of the halos considered.
@@
 To get a sense of how well HETDEX will be able to constrain cosmological parameters we follow the discussion of \defcitealias{Weinberg2013}{W13}\cite{Weinberg2013} (hereafter \citetalias{Weinberg2013}), and begin with a few simplifying assumptions.
-While sensitive to $\Omega_m$, the number density of clusters does not necessarily provide the strongest contraint, so we assume that some combination of other data sets (\eg, CMB, BAO, supernovae, WL, etc.) will constrain $\Omega_m$ to higher precision than is possible with clusters alone.
+While sensitive to $\Omega_m$, the number density of clusters does not necessarily provide the strongest contraint, but combined with other data sets (\eg, CMB, BAO, supernovae, WL, etc.) it will constrain $\Omega_m$ to higher precision.
 
@@
 For a survey such as HETDEX, we can estimate the constraints on $\sigma_8h^{-1}$ using Equation \ref{eq:sigElapprox}.
-Considering clusters with masses above $10^{14}$ \Msol, with Perfect knowledge, and the ML based cluster mass estimates the mass scale uncertainty (given in Table~\ref{tbl:mass scatter}) is reduced to $\Delta_{log_{10}}M \sim 0.075$ dex or about 20\%.
+If we consider clusters with masses above $10^{14}$ \Msol\ and with Perfect knowledge observations, the lowest mass scale uncertainty (given in Table~\ref{tbl:mass scatter}) is $\Delta_{log_{10}}M \sim 0.075$ dex or about 20\%.
 This gives a uncertainty on $\sigma_8h^{-1}$ of 7\%.
-For clusters above $10^{14}$ \Msol, Survey observations can constrain the masses to about 51\% which, in turn, constrains $\sigma_8h^{-1}$ to 20\%.
+For clusters above $10^{14}$ \Msol, Survey observations constrain the masses to about 51\% which, in turn, constrains $\sigma_8h^{-1}$ to 20\%.
 
@@
 
-\subsection{Calibration of the Richness-Cluster Mass Relation}
+\subsection{Scale and Scatter of the Richness-Cluster Mass Relation}
 Large-scale optical surveys (\eg, DES and LSST) expect to detect hundreds of thousands of galaxy clusters at $z < 1$.
@@
 
-To confirm that measuring the underlying scatter is possible, after generating richness values we calculate the scatter of the cluster masses at fixed $\lambda$, $\sigma_{M|\lambda}$, by comparing the true, unperturbed cluster masses against the richness and find that we do recover the expected scatter.
+To confirm that measuring the underlying scatter is possible, after generating richness values we calculate the scatter of the cluster masses at fixed $\lambda$, $\sigma_{M|\lambda}$, by comparing the true, unperturbed cluster masses against the richness.
+We do recover the expected scatter, often, to well within 0.01 dex.
 We repeat the process with both assumed richness-mass relationships and recover the expected scatter in both instances.
@@
 
-To get an idea of how well HETDEX will constrain the absolute mass scale, we can find the best fitting relation to our richness-mass data.
-To generate the best fitting lines we follow the general procedure of \cite{Hogg2010}, by defining an objective function and then minimizing the loss.
+In order to understand how HETDEX will constrain the absolute mass scale, we find the best fitting relation to our richness-mass data.
+To generate the best fitting lines, we follow the general procedure of \cite{Hogg2010}, by defining an objective function and then minimizing the loss.
 Our objective function is
@@
 We assume that the intrinsic scatter is constant from point to point and that all of the measurement errors are Gaussian.
-We convert this objective function into a likelihood by multiplying all of the individual probabilities together,
+We convert this objective function into a likelihood by taking the product of all the individual probabilities:
 \begin{equation}\label{eq:like}
@@
 We again rely on MCMC samples to sample the posterior probability distribution and thus maximize the likelihood.
-The best fitting slope and intercept are quoted as the median value of the posterior probability distribution with 68\% error bars defined as the second moment of the same distribution.
+The best fitting slope and intercept are quoted as the median value of the posterior probability distribution with 68\% error bars defined as the square root of the second moment of the same distribution.
 
@@
 \end{equation} 
-This gives $M_{200c} = (1.22\pm...)\times10^{14}$ \Msol\ and $M_{200c} = (1.44\pm...)\times10^{14}$ \Msol\ at $\lambda=40$ for the Targeted and Survey observations respectively.
+This gives $M_{200c} = (1.24\pm0.11)\times10^{14}$ \Msol\ and $M_{200c} = (1.44\pm0.21)\times10^{14}$ \Msol\ at $\lambda=40$ for the Targeted and Survey observations respectively.
 In both cases, this normalization differs significantly from the $M_{200c} \approx 2.1\times10^{14} h^{-1}$ \Msol\ found in recent work \cite{Li2016, Simet2016}.
-If the intrinsic scatter is reduced to $\sim 0.05$ dex we recover an overall normalization of $M_{200c} = (1.8\pm...)\times10^{14}$ \Msol\ and $M_{200c} = (1.78\pm...)\times10^{14}$ for the Targeted and Survey observations at $\lambda=40$.
+If the intrinsic scatter is reduced to $\sim 0.05$ dex we recover an overall normalization of $M_{200c} = (1.80\pm0.09)\times10^{14}$ \Msol\ and $M_{200c} = (1.72\pm0.18)\times10^{14}$ for the Targeted and Survey observations at $\lambda=40$.
 
-The intrinsic scatter is also estimated during the fitting process.
-For observations with a richness-mass relation intrinsic scatter of $\langle \sigma_{M|\lambda} \rangle = 0.25$ dex, we recover $\langle \sigma_{M|\lambda} \rangle = 0.22\pm0.003$ dex and $\langle \sigma_{M|\lambda} \rangle = 0.20\pm0.01$ dex for Targeted and Survey observations respectively.
+We also estimate the intrinsic scatter.
+For observations with a richness-mass relation intrinsic scatter of $\langle \sigma_{M|\lambda} \rangle = 0.25$ dex, we recover $\langle \sigma_{M|\lambda} \rangle = 0.22\pm0.003$ dex and $\langle \sigma_{M|\lambda} \rangle = 0.20\pm0.01$ dex for the Targeted and Survey observations respectively.
 The discrepancy between the intrinsic value and the measured value is due to the uncertainties in the individual cluster mass predictions.
 As the prediction intervals are narrowed, the recovered intrinsic scatter approaches the true value.
-For example, with cluster mass prediction intervals half the size of the current intervals we measure $\langle \sigma_{M|\lambda} \rangle$ to be $\sim 0.25$ and $\sim 0.23$ for the two sets of observations.
+For example, with cluster mass prediction intervals half the size of the current intervals we measure $\langle \sigma_{M|\lambda} \rangle$ to be $\sim 0.25$ and $\sim 0.23$ dex for the two sets of observations.
 
@@
 Color coding is the same as the top panel.
-\emph{Inset}: The evolution of the intrinsic scatter versus the average recovered scatter, $\sigma_{rec}$.
-We find good agreement when intrinsic scatter is $\sim0.25$ dex.} \label{fig:mass richness}
+\emph{Inset}: The evolution of the intrinsic scatter versus the average recovered scatter, $\sigma_{rec}$.} \label{fig:mass richness}
 \end{figure}
@@
 
-For
+For the richness range $10 \leq \lambda < 130$ the intrinsic scatter in between the $\mathrm{ML}_{\sigma, z, N_{gal}}$ predicted cluster masses and the true cluster mass (the basis of our richnesses) is $\sim0.15$ dex for Targeted observations and $\sim0.20$ dex for Survey observations.
+This forms an effective floor on the amount of scatter we are able to recover from our fitting process.
+As we reduce the overall scatter in our cluster mass recovery, this floor will lower.
+The scatter ceiling of $\sim0.32$ dex in both observations is the result of
 
-\section{SUMMARY}\label{sec:summary}
+\section{Summary}\label{sec:summary}
 Here, we present detailed simulations of the upcoming HETDEX survey's applicability to the detection and total mass measurement of galaxy clusters.
@@
 \begin{enumerate}
-	\item We find approximately 14000 clusters with at least five cluster members in the HETDEX cluster survey volume.
-Of those, approximately 1500 clusters are detected with HETDEX-like survey observations.
+	\item We find 14,189 clusters with at least five cluster members in the HETDEX cluster survey volume.
+Of those, approximately 1,760 clusters are detected with HETDEX-like survey observations.
 The number of cluster members recovered is almost exactly 4.5 times fewer than a fully Targeted survey, across both a wide range of redshifts and cluster masses.
@@
 For HETDEX-like observations and clusters with $13 < \mathrm{Log}\, M/\Msol <14.5$, we find the $ML_{\sigma, z, N_{gal}}$ method performs the best.
-Below Log M/\Msol\ $=13$ no method with Survey observations gives an bias of less than 50\%.
-	\item For followup Targeted observations only galaxy clusters with masses inferred to be Log M/\Msol\ $<13$ from Survey observations should be targeted.
+Below Log M/\Msol\ $=13$ no method with Survey observations gives a bias of less than 50\%.
+	\item For follow-up Targeted observations only galaxy clusters with masses inferred to be Log M/\Msol\ $<13$ from Survey observations should be targeted.
 Galaxy clusters with inferred masses below Log M/\Msol\ $=13$ can see as much as an 81\% improvement in cluster mass estimation with Targeted observations.
 While the improvement of clusters with masses above Log M/\Msol\ $=13$ is often approximately 10\%.
-	\item For a cluster survey limited to $M > 10^{14}$ \Msol\, HETDEX's ability to constrain the cosmological parameter $\sigma_8 h^{-1}$ is at best $\sim20\%$.
-This is significantly different than recent constraints from SZE surveys.
-	\item HETDEX will be able to place important constraints on the amount of scatter in the optical richness-mass relationship.
+	\item HETDEX will be able to place important, independent constraints on the amount of scatter in the optical richness-mass relationship.
 It will to a less extent constrain the overall normalization of the relation.
@@
 % The best way to enter references is to use BibTeX:
-\bibliographystyle{mnras}
+\bibliographystyle{apj}
 \bibliography{master} % if your bibtex file is called example.bib
@@
 For example, the HETDEX observations overlap with the DES area and SDSS Stripe 82 which provides a wealth of external data.
-Using preexisting datasets, the observations from HETDEX, or through dedicated followup spectroscopic observations, I will be able to measure the absolute mass scale of the richness estimator and measure the scatter of the richness-mass relation, $\sigma_{M|\lambda}$.
+Using preexisting datasets, the observations from HETDEX, or through dedicated follow-up spectroscopic observations, I will be able to measure the absolute mass scale of the richness estimator and measure the scatter of the richness-mass relation, $\sigma_{M|\lambda}$.
 An accurate measure of this scatter can lead to a decrease on the error bar on cosmological measures ($\sigma_8$ and $\Omega_M$) by as much as 50\% \citep{Rozo2010}.

### 2016-05-20 paper1.tex
last of casey changes

@@
 \end{abstract}
-% Using both observing strategies, we produce cluster mass probability density functions $P(M_{200c}|\vec{x})$ of a cluster mass ($M_{200c}$) as a function of an observable parameter or set of observable parameters, $\vec{x}$, where we consider cases of where $\vec{x} = \{\sigma\}$, $=\{\sigma, z\}$, and $=\{\sigma,z, N_{gal}\}$ for velocity dispersion, $\sigma$, redshift, and number of observed galaxies, $N_{gal}$.
-% \end{abstract}
 
@@
 X-ray based cluster masses assume hydrostatic equilibrium \citeeg{Mantz2015} which may only be valid for a very small number and range of cluster masses.
-The Sunyaev-Zel'dovich Effect (SZE; \citealt{Sunyaev1972}), which uses the up-scattering of cosmic microwave background (CMB) photons to estimate cluster masses, provides accurate estimations of mass, but the ability to detect low mass galaxy clusters is currently limited by technology \citeeg{Carlstrom2002a}.
+The Sunyaev-Zel'dovich Effect (SZE; \citealt{Sunyaev1972}), which uses the up-scattering of cosmic microwave background (CMB) photons to estimate cluster masses, provides accurate estimations of mass, but the ability to detect low mass galaxy clusters is currently limited by technology \citeeg{Carlstrom2002a} and can also be effected by the properties of the intracluster medium \citeeg{Pipino2010}.
 WL estimates are, in principle, correct in the mean, but they suffer from signal-to-noise requirements, limiting their usefulness in low mass clusters (where the lensing signal is particularly weak), and potentially suffer from line-of-sight effects as WL is sensitive to all mass along the line-of-sight.
@@
 However, regardless of the discovery method used, spectroscopic follow-up is needed to further constrain $P(M|z,X)$.
+This follow-up becomes increasing important to help constrain the scatter in the mass estimates of other methods, and provides an additional, independent check of the observable-mass relationship used.
 But as the cluster dataset grows to many tens of thousands of clusters individual follow-up becomes increasingly impractical.
-Therefore, large spectroscopic surveys are needed to more fully constrain the observable--mass relation of clusters.
+Therefore, large spectroscopic surveys are needed to more fully understand the observable-mass relation of clusters.
 
@@
 Secondly, it is not straightforward to use spectroscopic redshifts predominately from emission-line galaxies to interpret the kinematic and dynamical states of the clusters.
+
+\begin{figure*} 
+	\includegraphics[width=0.9\textwidth]{figures/oii_sdss.pdf} 
+	\caption{\textit{Left}: CMD of 503,113 $z<0.2$ galaxies take from the SDSS DR12 where the shading scales with the density of points.
+The two colored boxes show regions containing potential catalog galaxies.
+\textit{Right}: Probability histograms of the Log [\ion{O}{ii}] luminosity for the SDSS galaxies located in the two highlighted regions on the right.
+The [\ion{O}{ii}] luminosities are assigned to catalog galaxies from slice sampling the probability histogram and converted to fluxes using the redshift of each galaxy.} \label{fig: oii sdss}
+\end{figure*}
 
@@
 \subsection{Conditional [\ion{O}{ii}] Flux Probability Distribution Functions}\label{sec: oii luminosity}
-\begin{figure*} 
-	\includegraphics[width=\textwidth]{figures/oii_sdss.pdf} 
-	\caption{\textit{Left}: CMD of 503,113 $z<0.2$ galaxies take from the SDSS DR12 where the shading scales with the density of points.
-The two colored boxes show regions containing potential catalog galaxies.
-\textit{Right}: Probability histograms of the Log [\ion{O}{ii}] luminosity for the SDSS galaxies located in the two highlighted regions on the right.
-The [\ion{O}{ii}] luminosities are assigned to catalog galaxies from slice sampling the probability histogram and converted to fluxes using the redshift of each galaxy.} \label{fig: oii sdss}
-\end{figure*}
 We use the SDSS DR12 \citep{Alam2015} catalogs to assign [\ion{O}{ii}] emission line strengths to the galaxies in the Buzzard catalog.
@@
 The numbered boxes in the left panel show the bins corresponding to two example Buzzard galaxies ($M_r, g-r = -17.7,~0.49$ and $M_r, g-r = -21.4,~1.24$).
-The right panel shows the Log [\ion{O}{ii}] luminosity distribution functions, $p($[\ion{O}{ii}]$| M_r, g-r)$, which we use to assign [\ion{O}{ii}] luminosity to each object.
+The right panel shows the Log [\ion{O}{ii}] luminosity distribution functions, $P($[\ion{O}{ii}]$| M_r, g-r)$, which we use to assign [\ion{O}{ii}] luminosity to each object.
 The luminosity is then converted into an [\ion{O}{ii}] flux through
@@
 	\caption{Representative observation tiling scheme for the HETDEX $16' \times 16'$ pointings.
-Each turqoise square represents the position of a single VIRUS IFU, and the dashed octagons approximate the size of a single observation.
+Each turquoise square represents the position of a single VIRUS IFU, and the dashed octagons approximate the size of a single observation.
 Inside each IFU HETDEX will achieve near complete coverage through three dithers.
@@
 
-We designed the results study here to be used with HETDEX, a large blind spectroscopic survey.
+We designed the results of this study to be used in conjunction with HETDEX, a large, blind, spectroscopic survey.
 HETDEX will measure the redshifts of $8 \times 10^5$ LAE galaxies between $1.9 < z < 3.5$ using a collection of 78 wide-field IFU spectrographs covering the wavelength region $3500 - 5500$~\AAA\ at R $\sim$ 750 \citep{Hill2008}.
-The goal of these observations will be to provide sub-percent level measurements of the Hubble expansion parameter and the angular diameter distance at $z \sim 2$ via the large scale distribution of galaxies in the redshift range of HETDEX.
-The result will be a significant constraint on the evolution of dark energy that is competitive with (and independent of) values based on surveys of the Ly$\alpha$ forest.
+The primary science goal of these observations is to provide $<1\%$ accuracy measurements of the Hubble expansion parameter and the angular diameter distance at $z\sim2$.
+This result will provide significant constraints on the evolution of the dark energy equation of state which is both competitive with, and independent of, constraints derived from observations of the \lya forest.
 
 The entire HETDEX survey will cover 420 \degsq\ with a 1/4.5 filling factor over two fields: a $\sim 300$ \degsq\ northern field, and a $\sim 140$ \degsq\ equatorial region.
-The $10 \sigma$ detection limit for these spectra will be $3.5\times10^{-17}$ \ergscm\ at 5000 \AAA, or equivalently for continuum objects, $g = 21.9$ mag.
 The spectral coverage allows for the detection of [\ion{O}{ii}] ($\lambda\lambda 3727,3729$) emitters to $z\sim 0.5$ and Ca H ($\lambda 3968.5$) and K ($\lambda 3933.7$) absorption features to $z\sim 0.4$.
+The $10 \sigma$ detection threshold for spectral features will be $3.5\times10^{-17}$ \ergscm\ at 5000 \AAA, or equivalently, $g = 21.9$ mag for continuum objects.
 
-The HETDEX IFU pattern is illustrated in Figure~\ref{fig: ifu layout} and consists of 78 IFUs, which are comprised of 448 optical fibers subtending a $50'' \times 50''$ region on the sky \citep{Kelz2014}.
-The inter-IFU spacing is also $50''$ spanning a total area of $16'\times 16'$ on the sky.
+The HETDEX IFU pattern is illustrated in Figure~\ref{fig: ifu layout} by the turquoise squares.
+Each of the 78 IFUs, are comprised of 448 optical fibers subtending a $50'' \times 50''$ region on the sky \citep{Kelz2014}.
+The inter-IFU spacing is also $50''$, spanning a total area of $16'\times 16'$ on the sky.
 The individual IFUs have a fill-factor of 1/3, which will be completely filled with three dithers of the telescope at each pointing.
@@
 
-In simple terms, the cluster redshift is the mean of the redshifts of all galaxies associated with the cluster, where the mean is the first moment of the velocity (redshift) distribution function $p(z)$.
+In simple terms, the cluster redshift is the mean of the redshifts of all galaxies associated with the cluster, where the mean is the first moment of the velocity (redshift) distribution function $P(z)$.
 In practice, the first moment is strongly subject to outliers, so we rely instead on the biweight location estimator \citep{Beers1990} through\footnote{Implemented as part of the {\sc astLib} Python library.
@@
 \begin{equation}\label{eq: jointGaussian}
-p(\{v_1, ..., v_N\})=\displaystyle\prod_{i=1}^{N}\frac{1}{\sqrt{2\pi(\sigma_i^2+\sigma_{1D}^2)}}\exp\biggl[-\frac{1}{2}\frac{(v_i-\langle u \rangle)^2}{(\sigma_i^2+\sigma_{1D}^2)}\biggr]
+P(\{v_1, ..., v_N\})=\displaystyle\prod_{i=1}^{N}\frac{1}{\sqrt{2\pi(\sigma_i^2+\sigma_{1D}^2)}}\exp\biggl[-\frac{1}{2}\frac{(v_i-\langle u \rangle)^2}{(\sigma_i^2+\sigma_{1D}^2)}\biggr]
 \end{equation}
@@
 \subsubsection{Probability Based}\label{sec:probability method}
-For internal consistency between this and the ML based method we use 70\% of the clusters to establish a conditional probability density of $p(M_{200c} | \vec{x})$ which we then use as the cluster mass probability density for the remaining clusters with similar features.
+For internal consistency between this and the ML based method we use 70\% of the clusters to establish a conditional probability density of $P(M_{200c} | \vec{x})$ which we then use as the cluster mass probability density for the remaining clusters with similar features.
 In this way we, ``train'' the probability density using the existing simulated data, and apply it to the ``test'' sample (the remaining 30\% of the data not used as the training set).
@@
 \begin{equation}\label{eq: Pm}
-	P(M_{200c}) = \int P(M_{200c}|\vec{x})\ P(\sigma)\ d\sigma
+	P(M_{200c}) = \int P(M_{200c}|\vec{x})\ P(\sigma)\ d\sigma\ P(z)\ dz
 \end{equation}
@@
 		\hline
-		\rottext{4}{Prob Based} & Power Law & $0.23\pm{0.007}$ & $0.16\pm{0.003}$ & $0.11\pm{0.002}$ & $0.07\pm{0.004}$ & $0.02\pm{0.011}$ & $-0.07\pm{0.045}$ \\
-		&$\sigma$ & $0.32\pm{0.005}$ & $0.16\pm{0.003}$ & $0.10\pm{0.002}$ & $0.07\pm{0.004}$ & $0.05\pm{0.012}$ & $-0.18\pm{0.078}$ \\
+		\multicolumn{2}{c}{Power Law} & $0.23\pm{0.007}$ & $0.16\pm{0.003}$ & $0.11\pm{0.002}$ & $0.07\pm{0.004}$ & $0.02\pm{0.011}$ & $-0.07\pm{0.045}$ \\
+		\hline 
+		\rottext{3}{Prob} &$\sigma$ & $0.32\pm{0.005}$ & $0.16\pm{0.003}$ & $0.10\pm{0.002}$ & $0.07\pm{0.004}$ & $0.05\pm{0.012}$ & $-0.18\pm{0.078}$ \\
 		&$\sigma, z$ & $0.17\pm{0.005}$ & $0.01\pm{0.003}$ & $-0.06\pm{0.002}$ & $-0.11\pm{0.015}$ & $-0.14\pm{0.012}$ & $-0.38\pm{0.159}$ \\
-		&$\sigma, z, N_{gal}$ & $0.04\pm{0.009}$ & $-0.02\pm{0.002}$ & $-0.02\pm{0.002}$ & $-0.05\pm{0.014}$ & $-0.22\pm{0.126}$ & $-6.62\pm{3.742}$ \\
+		&$\sigma, z, N_{gal}$ & $0.04\pm{0.009}$ & $-0.02\pm{0.002}$ & $-0.02\pm{0.002}$ & $-0.05\pm{0.014}$ & $-0.22\pm{0.126}$ & \nd \\
 		\hline
-		\rottext{5}{ML Based} & Power Law & $0.23\pm{0.007}$ & $0.16\pm{0.003}$ & $0.11\pm{0.002}$ & $0.07\pm{0.004}$ & $0.02\pm{0.011}$ & $-0.07\pm{0.045}$ \\
-		&$\sigma$ & $0.14\pm{0.006}$ & $-0.01\pm{0.003}$ & $-0.07\pm{0.003}$ & $-0.09\pm{0.005}$ & $-0.11\pm{0.014}$ & $-0.17\pm{0.090}$ \\
+		\rottext{4}{ML} &$\sigma$ & $0.14\pm{0.006}$ & $-0.01\pm{0.003}$ & $-0.07\pm{0.003}$ & $-0.09\pm{0.005}$ & $-0.11\pm{0.014}$ & $-0.17\pm{0.090}$ \\
 		&$\sigma, z$ & $0.12\pm{0.005}$ & $-0.01\pm{0.003}$ & $-0.06\pm{0.003}$ & $-0.08\pm{0.004}$ & $-0.11\pm{0.012}$ & $-0.24\pm{0.076}$ \\
@@
 		\hline
-		\rottext{4}{Prob Based} & Power Law & $0.20\pm{0.008}$ & $0.13\pm{0.005}$ & $0.10\pm{0.005}$ & $0.09\pm{0.007}$ & $0.02\pm{0.014}$ & $-0.08\pm{0.043}$ \\
-		&$\sigma$ & $0.40\pm{0.005}$ & $0.17\pm{0.003}$ & $0.02\pm{0.004}$ & $-0.08\pm{0.006}$ & $-0.19\pm{0.015}$ & $-0.35\pm{0.122}$ \\
+		\multicolumn{2}{c}{Power Law} & $0.20\pm{0.008}$ & $0.13\pm{0.005}$ & $0.10\pm{0.005}$ & $0.09\pm{0.007}$ & $0.02\pm{0.014}$ & $-0.08\pm{0.043}$ \\
+		\hline
+		\rottext{3}{Prob} &$\sigma$ & $0.40\pm{0.005}$ & $0.17\pm{0.003}$ & $0.02\pm{0.004}$ & $-0.08\pm{0.006}$ & $-0.19\pm{0.015}$ & $-0.35\pm{0.122}$ \\
 		&$\sigma, z$ & $0.25\pm{0.005}$ & $0.08\pm{0.003}$ & $-0.06\pm{0.003}$ & $-0.21\pm{0.015}$ & $-0.35\pm{0.016}$ & $-0.59\pm{0.145}$ \\
@@
 		\hline
-		\rottext{5}{ML Based} & Power Law & $0.20\pm{0.008}$ & $0.13\pm{0.005}$ & $0.10\pm{0.005}$ & $0.09\pm{0.007}$ & $0.02\pm{0.014}$ & $-0.08\pm{0.043}$ \\
-		&$\sigma$ & $0.26\pm{0.006}$ & $0.02\pm{0.004}$ & $-0.13\pm{0.005}$ & $-0.24\pm{0.008}$ & $-0.35\pm{0.022}$ & $-0.39\pm{0.054}$ \\
+		\rottext{4}{ML} &$\sigma$ & $0.26\pm{0.006}$ & $0.02\pm{0.004}$ & $-0.13\pm{0.005}$ & $-0.24\pm{0.008}$ & $-0.35\pm{0.022}$ & $-0.39\pm{0.054}$ \\
 		&$\sigma, z$ & $0.18\pm{0.005}$ & $0.03\pm{0.003}$ & $-0.10\pm{0.004}$ & $-0.21\pm{0.006}$ & $-0.31\pm{0.021}$ & $-0.33\pm{0.063}$ \\
@@
 		\hline
-		\rottext{4}{Prob Based} & Power Law & $0.53\pm{0.043}$ & $0.30\pm{0.018}$ & $0.16\pm{0.013}$ & $0.07\pm{0.013}$ & $0.01\pm{0.022}$ & $-0.09\pm{0.062}$ \\
-		&$\sigma$ & $0.77\pm{0.030}$ & $0.42\pm{0.011}$ & $0.18\pm{0.008}$ & $-0.03\pm{0.009}$ & $-0.18\pm{0.017}$ & $-0.39\pm{0.102}$ \\
+		\multicolumn{2}{c}{Power Law} & $0.17\pm{0.068}$ & $0.17\pm{0.023}$ & $0.13\pm{0.014}$ & $0.07\pm{0.014}$ & $0.01\pm{0.022}$ & $-0.09\pm{0.062}$ \\
+		\hline
+		\rottext{3}{Prob} & $\sigma$ & $0.77\pm{0.030}$ & $0.42\pm{0.011}$ & $0.18\pm{0.008}$ & $-0.03\pm{0.009}$ & $-0.18\pm{0.017}$ & $-0.39\pm{0.102}$ \\
 		&$\sigma, z$ & $0.61\pm{0.036}$ & $0.29\pm{0.012}$ & $0.08\pm{0.008}$ & $-0.11\pm{0.009}$ & $-0.38\pm{0.118}$ & $-0.48\pm{0.127}$ \\
@@
 		\hline
-		\rottext{5}{ML Based} & Power Law & $0.17\pm{0.068}$ & $0.17\pm{0.023}$ & $0.13\pm{0.014}$ & $0.07\pm{0.014}$ & $0.01\pm{0.022}$ & $-0.09\pm{0.062}$ \\
-		&$\sigma$ & $0.57\pm{0.046}$ & $0.24\pm{0.015}$ & $0.02\pm{0.012}$ & $-0.17\pm{0.013}$ & $-0.28\pm{0.027}$ & $-0.27\pm{0.117}$ \\
+		\rottext{4}{ML} &$\sigma$ & $0.57\pm{0.046}$ & $0.24\pm{0.015}$ & $0.02\pm{0.012}$ & $-0.17\pm{0.013}$ & $-0.28\pm{0.027}$ & $-0.27\pm{0.117}$ \\
 		&$\sigma, z$ & $0.48\pm{0.034}$ & $0.20\pm{0.013}$ & $0.03\pm{0.009}$ & $-0.13\pm{0.011}$ & $-0.26\pm{0.021}$ & $-0.31\pm{0.110}$ \\
@@
 The three horizontal sections represent Perfect, Targeted and Survey observations respectively.
-So, for example, if a cluster mass is predicted using the $ML_{\sigma, z}$ method and Targeted observations to be Log M/\Msol\ $=13-13.5$, it is biased upward by $0.03\pm{0.003}$ dex.
+So, for example, if a cluster mass is predicted using the $\mathrm{ML}_{\sigma, z}$ method and Targeted observations to be Log M/\Msol\ $=13-13.5$, it is biased upward by $0.03\pm{0.003}$ dex and has a scatter of $0.24\pm0.009$ dex.
 
@@
 		\hline
-		\rottext{4}{Prob Based} & Power Law & $0.34\pm{0.005}$ & $0.22\pm{0.002}$ & $0.16\pm{0.002}$ & $0.14\pm{0.003}$ & $0.14\pm{0.008}$ & $0.11\pm{0.040}$ \\
-		&$\sigma$ & $0.26\pm{0.004}$ & $0.20\pm{0.002}$ & $0.16\pm{0.002}$ & $0.14\pm{0.003}$ & $0.16\pm{0.009}$ & $0.19\pm{0.071}$ \\
+		\multicolumn{2}{c}{Power Law} & $0.34\pm{0.005}$ & $0.22\pm{0.002}$ & $0.16\pm{0.002}$ & $0.14\pm{0.003}$ & $0.14\pm{0.008}$ & $0.11\pm{0.040}$ \\
+		\hline 
+		\rottext{3}{Prob} &$\sigma$ & $0.26\pm{0.004}$ & $0.20\pm{0.002}$ & $0.16\pm{0.002}$ & $0.14\pm{0.003}$ & $0.16\pm{0.009}$ & $0.19\pm{0.071}$ \\
 		&$\sigma, z$ & $0.23\pm{0.003}$ & $0.19\pm{0.002}$ & $0.16\pm{0.002}$ & $0.55\pm{0.010}$ & $0.16\pm{0.009}$ & $0.39\pm{0.143}$ \\
@@
 		\hline
-		\rottext{5}{ML Based} & Power Law & $0.34\pm{0.005}$ & $0.22\pm{0.002}$ & $0.16\pm{0.002}$ & $0.14\pm{0.003}$ & $0.14\pm{0.008}$ & $0.11\pm{0.040}$ \\
-		&$\sigma$ & $0.29\pm{0.004}$ & $0.24\pm{0.002}$ & $0.21\pm{0.002}$ & $0.19\pm{0.004}$ & $0.18\pm{0.010}$ & $0.22\pm{0.081}$ \\
+		\rottext{4}{ML}	&$\sigma$ & $0.29\pm{0.004}$ & $0.24\pm{0.002}$ & $0.21\pm{0.002}$ & $0.19\pm{0.004}$ & $0.18\pm{0.010}$ & $0.22\pm{0.081}$ \\
 		&$\sigma, z$ & $0.24\pm{0.003}$ & $0.20\pm{0.002}$ & $0.18\pm{0.002}$ & $0.16\pm{0.003}$ & $0.16\pm{0.009}$ & $0.19\pm{0.068}$ \\
@@
 		\hline
-		\rottext{4}{Prob Based} & Power Law & $0.43\pm{0.006}$ & $0.39\pm{0.004}$ & $0.33\pm{0.004}$ & $0.27\pm{0.005}$ & $0.18\pm{0.010}$ & $0.11\pm{0.039}$ \\
-		&$\sigma$ & $0.24\pm{0.003}$ & $0.25\pm{0.002}$ & $0.25\pm{0.003}$ & $0.22\pm{0.004}$ & $0.19\pm{0.011}$ & $0.30\pm{0.110}$ \\
+		 \multicolumn{2}{c}{Power Law} & $0.43\pm{0.006}$ & $0.39\pm{0.004}$ & $0.33\pm{0.004}$ & $0.27\pm{0.005}$ & $0.18\pm{0.010}$ & $0.11\pm{0.039}$ \\
+		 \hline
+		\rottext{3}{Prob} &$\sigma$ & $0.24\pm{0.003}$ & $0.25\pm{0.002}$ & $0.25\pm{0.003}$ & $0.22\pm{0.004}$ & $0.19\pm{0.011}$ & $0.30\pm{0.110}$ \\
 		&$\sigma, z$ & $0.24\pm{0.003}$ & $0.24\pm{0.002}$ & $0.23\pm{0.002}$ & $0.56\pm{0.011}$ & $0.21\pm{0.012}$ & $0.36\pm{0.131}$ \\
@@
 		\hline
-		\rottext{5}{ML Based} & Power Law & $0.43\pm{0.006}$ & $0.39\pm{0.004}$ & $0.33\pm{0.004}$ & $0.27\pm{0.005}$ & $0.18\pm{0.010}$ & $0.11\pm{0.039}$ \\
-		&$\sigma$ & $0.30\pm{0.004}$ & $0.32\pm{0.003}$ & $0.32\pm{0.003}$ & $0.30\pm{0.006}$ & $0.29\pm{0.016}$ & $0.13\pm{0.049}$ \\
+		\rottext{4}{ML} &$\sigma$ & $0.30\pm{0.004}$ & $0.32\pm{0.003}$ & $0.32\pm{0.003}$ & $0.30\pm{0.006}$ & $0.29\pm{0.016}$ & $0.13\pm{0.049}$ \\
 		&$\sigma, z$ & $0.26\pm{0.004}$ & $0.25\pm{0.002}$ & $0.24\pm{0.003}$ & $0.23\pm{0.004}$ & $0.27\pm{0.015}$ & $0.16\pm{0.057}$ \\
@@
 		\hline
-		\rottext{4}{Prob Based} & Power Law & $0.16\pm{0.034}$ & $0.29\pm{0.013}$ & $0.33\pm{0.009}$ & $0.31\pm{0.010}$ & $0.25\pm{0.016}$ & $0.15\pm{0.056}$ \\
-		&$\sigma$ & $0.11\pm{0.024}$ & $0.18\pm{0.008}$ & $0.22\pm{0.006}$ & $0.22\pm{0.007}$ & $0.19\pm{0.012}$ & $0.25\pm{0.092}$ \\
+		\multicolumn{2}{c}{Power Law} &$0.40\pm{0.050}$ & $0.41\pm{0.016}$ & $0.38\pm{0.010}$ & $0.32\pm{0.010}$ & $0.25\pm{0.016}$ & $0.15\pm{0.056}$ \\
+		\hline
+		\rottext{3}{Prob} &$\sigma$ & $0.11\pm{0.024}$ & $0.18\pm{0.008}$ & $0.22\pm{0.006}$ & $0.22\pm{0.007}$ & $0.19\pm{0.012}$ & $0.25\pm{0.092}$ \\
 		&$\sigma, z$ & $0.13\pm{0.028}$ & $0.19\pm{0.008}$ & $0.22\pm{0.006}$ & $0.21\pm{0.007}$ & $1.31\pm{0.084}$ & $0.32\pm{0.115}$ \\
@@
 		\hline
-		\rottext{5}{ML Based} & Power Law &$0.40\pm{0.050}$ & $0.41\pm{0.016}$ & $0.38\pm{0.010}$ & $0.32\pm{0.010}$ & $0.25\pm{0.016}$ & $0.15\pm{0.056}$ \\
-		&$\sigma$ & $0.27\pm{0.034}$ & $0.27\pm{0.011}$ & $0.31\pm{0.008}$ & $0.30\pm{0.009}$ & $0.30\pm{0.019}$ & $0.29\pm{0.106}$ \\
+		\rottext{4}{ML} &$\sigma$ & $0.27\pm{0.034}$ & $0.27\pm{0.011}$ & $0.31\pm{0.008}$ & $0.30\pm{0.009}$ & $0.30\pm{0.019}$ & $0.29\pm{0.106}$ \\
 		&$\sigma, z$ & $0.20\pm{0.025}$ & $0.24\pm{0.009}$ & $0.24\pm{0.006}$ & $0.25\pm{0.008}$ & $0.24\pm{0.015}$ & $0.27\pm{0.100}$ \\
@@
 On the opposite end of the cluster mass spectrum, there are very few, if any, clusters detected with Targeted or Survey observations below $5\times10^{12}$ \msol.
-Therefore, while we show these points in Figures~\ref{fig:Probability comparison} and \ref{fig: ML comparison}, we exclude their biases and scatters from Tables~\ref{tbl:mass bias} and \ref{tbl:mass scatter}.
+Therefore, while we show these points in Figures~\ref{fig:Probability comparison} and \ref{fig: ML comparison}, we exclude their biases and scatters from Tables~\ref{tbl:mass bias} and \ref{tbl:mass scatter} for the same reasons.
 
@@
 For the Targeted observations, the power law method outperforms all other methods, in terms of bias and scatter, for the highest mass clusters.
-But outside of the two highest mass bins, the $ML_{\sigma, z, N_{gal}}$ method shows the smallest amount of scatter and bias most consistently.
+But outside of the two highest mass bins, the $\mathrm{ML}_{\sigma, z, N_{gal}}$ method shows the smallest amount of scatter and bias most consistently.
 With Survey observations, the power law again provides the lowest bias in the highest cluster mass bins, but is outperformed in terms of scatter by the other two methods.
-The $ML_{\sigma, z, N_{gal}}$ method shows the smallest amount of scatter and bias most consistently across the cluster mass range in question.
+The $\mathrm{ML}_{\sigma, z, N_{gal}}$ method shows the smallest amount of scatter and bias most consistently across the cluster mass range in question.
 
@@
 
-The Buzzard cluster catalogs do not contain measurements of $\lambda$, so we supplement it by generating richnesses based on the true cluster masses.
-For testing we assume two versions of the richness-mass relationship.
+One of the main goals of this study is to understand how well HETDEX will be able to measure the scatter in the richness-mass relationship.
+To this end, we choose to impose a richness-mass relation onto the clusters in the Buzzard catalogs.
+The true richness-mass relation could depend strongly on the number and types of environmental effects, because such effects have a strong impact on the number and types of galaxies observed in clusters \citeeg{Gunn1972,Balogh2000,White2010}.
+Any environmental effects included in Buzzard could potentially impact our observed richness.
+The imposition of an empirical richness-mass relation ensures the richness values correspond correctly to the clusters in our sample, could provide direct observational tests in the future.
+
+We generate richnesses based on the true cluster masses, and for testing, we assume two versions of the richness-mass relationship.
 \cite{Farahi2016} base the relation on stacked velocity dispersions, and \cite{Simet2016} use weak lensing measurements to construct their relation.
@@
 
+We use the lambda values generated above in combination with the $\mathrm{M}_{\sigma,z,N_{gal}}$ predicted cluster mass which have been bias corrected using the values in Table~\ref{tbl:mass bias} and denoted $\mathrm{M_{pred,corr}}$.
+The use of biased cluster mass predictions inhibits our ability to accurately recover any scatter in richness-mass relationship, and is discussed further below.
+
 Primarily, we are interested in the intrinsic scatter of the richness-mass relationship.
 This is because HETDEX is uniquely situated to estimate the scatter, whereas studies relying on stacked data \citeeg{Farahi2016,Simet2016} lose that information.
-However, for technical reasons, we begin by estimating how well HETDEX will constrain the absolute mass scale (something stacked studies excel at).
-As part of our fitting process to constrain the mass scale, we estimate the overall scatter in the relationship, so it makes sense to begin here.
-
+We begin by attempting to constrain the absolute mass scale, and as part of our fitting process, we estimate the overall scatter in the relationship.
 In order to understand how HETDEX will constrain the absolute mass scale, we find the best fitting relation to our richness-mass data.
@@
 \begin{equation}\label{eq:objectivei}
-p(y_i|x_i,\sigma_{yi},m,b,\sigma) = \frac{1}{\sqrt{2\,\pi\,(\sigma_{yi}^2+\sigma^2)}}
+P(y_i|x_i,\sigma_{yi},m,b,\sigma) = \frac{1}{\sqrt{2\,\pi\,(\sigma_{yi}^2+\sigma^2)}}
  \,\exp\left(-\frac{[y_i - m\,x_i - b]^2}{2\,(\sigma_{yi}^2+\sigma^2)}\right)
@@
 \begin{equation}\label{eq:like}
-\mathscr{L} = \prod_{i=1}^N \ p(y_i|x_i,\sigma_{yi},m,b, \sigma).
+\mathscr{L} = \prod_{i=1}^N \ P(y_i|x_i,\sigma_{yi},m,b, \sigma).
 \end{equation}
@@
 \begin{equation}
-	\mathrm{Log}\ M_{200c}/\Msol = 12.54\pm0.02 + 0.97\pm0.02\ \mathrm{Log}\ \lambda
+	\mathrm{Log}\ M_{200c}/\Msol = 12.46\pm0.02 + 1.07\pm0.02\ \mathrm{Log}\ \lambda
 \end{equation} 
@@
 \begin{equation}
-	\mathrm{Log}\ M_{200c}/\Msol = 12.78\pm0.04 + 0.86\pm0.03\ \mathrm{Log}\ \lambda
+	\mathrm{Log}\ M_{200c}/\Msol = 12.64\pm0.05 + 0.98\pm0.03\ \mathrm{Log}\ \lambda
 \end{equation} 
-This gives $M_{200c} = (1.24\pm0.11)\times10^{14}$ \Msol\ and $M_{200c} = (1.44\pm0.21)\times10^{14}$ \Msol\ at $\lambda=40$ for the Targeted and Survey observations respectively.
+This gives $M_{200c} = (1.45\pm0.12)\times10^{14}$ \Msol\ and $M_{200c} = (1.59\pm0.27)\times10^{14}$ \Msol\ at $\lambda=40$ for the Targeted and Survey observations respectively.
 In both cases, this normalization differs significantly from the $M_{200c} \approx 2.1\times10^{14} h^{-1}$ \Msol\ found in recent work \cite{Li2016, Simet2016}.
-If the intrinsic scatter is reduced to $\sim 0.05$ dex we recover an overall normalization of $M_{200c} = (1.80\pm0.09)\times10^{14}$ \Msol\ and $M_{200c} = (1.72\pm0.18)\times10^{14}$ for the Targeted and Survey observations at $\lambda=40$.
+If the intrinsic scatter is reduced to $\sim 0.05$ dex we recover an overall normalization of $M_{200c} = (2.14\pm0.12)\times10^{14}$ \Msol\ and $M_{200c} = (2.10\pm0.26)\times10^{14}$ for the Targeted and Survey observations at $\lambda=40$.
 
 We also estimate the intrinsic scatter.
-For observations with a richness-mass relation intrinsic scatter of $\langle \sigma_{M|\lambda} \rangle = 0.25$ dex, we recover $\langle \sigma_{M|\lambda} \rangle = 0.22\pm0.003$ dex and $\langle \sigma_{M|\lambda} \rangle = 0.20\pm0.01$ dex for the Targeted and Survey observations respectively.
-The discrepancy between the intrinsic value and the measured value is due to the uncertainties in the individual cluster mass predictions.
+For observations with a richness-mass relation intrinsic scatter of $\langle \sigma_{M|\lambda} \rangle = 0.25$ dex, we recover $\langle \sigma_{M|\lambda} \rangle = 0.236\pm0.003$ dex and $\langle \sigma_{M|\lambda} \rangle = 0.257\pm0.007$ dex for the Targeted and Survey observations respectively.
+
+%The discrepancy between the intrinsic value and the measured value is due to the uncertainties in the individual cluster mass predictions.
 As the prediction intervals are narrowed, the recovered intrinsic scatter approaches the true value.
@@
 	\includegraphics[width=\columnwidth]{figures/massRichness.pdf} 
-	\caption{\emph{Top}: The optical richness, $\lambda$, versus the predicted cluster mass.
-The solid, colored line is the median predicted mass for the Targeted observing, and the colored, dashed line is the median recovered mass for the HETDEX-like observations.
+	\caption{\emph{Top}: The optical richness, $\lambda$, versus the corrected predicted cluster mass.
+The solid, purple line is the median predicted mass for the Targeted observing, and the turquoise, dashed line is the median recovered mass for the HETDEX-like observations.
 The shaded regions represent the 68\% scatter around the median values.
@@
 
- We find that we are able to accurately recover an average intrinsic scatter of $0.2 <\langle \sigma_{M|\lambda} \rangle <0.3$ dex, finding $\langle \sigma_{M|\lambda} \rangle = 0.255\pm{0.02}$ at $\sigma_{true} = 0.25$ with Survey observations.
+We find that we are able to accurately recover an average intrinsic scatter of $0.2 <\langle \sigma_{M|\lambda} \rangle <0.3$ dex, finding $\langle \sigma_{M|\lambda} \rangle = 0.257\pm0.007$ at $\sigma_{true} = 0.25$ with Survey observations.
 This is very promising as other observational studies have estimated the intrinsic scatter of real clusters to be $\sim0.25$ dex \citeeg{Rozo2014, Rozo2015}.
@@
 
-For the richness range $10 \leq \lambda < 130$ the intrinsic scatter in between the $\mathrm{ML}_{\sigma, z, N_{gal}}$ predicted cluster masses and the true cluster mass (the basis of our richnesses) is $\sim0.15$ dex for Targeted observations and $\sim0.20$ dex for Survey observations.
+For the richness range $10 \leq \lambda < 130$ the intrinsic scatter in between the $\mathrm{M_{pred,corr}}$ predicted cluster masses and the true cluster mass (the basis of our richnesses) is $\sim0.15$ dex for Targeted observations and $\sim0.20$ dex for Survey observations.
 This forms an effective floor on the amount of scatter we are able to recover from our fitting process.
 As we reduce the overall scatter in our cluster mass recovery, this floor will lower.
-The scatter ceiling of $\sim0.32$ dex in both observations is the result of
+We underestimate the scatter in high intrinsic scatter relations because any residual bias remaining in the predicted clusters masses after correction reduces the observed scatter.
+Because the bias subtraction when creating $\mathrm{M_{pred,corr}}$ subtracts the mean bias, we are left with a small amount of residual bias, lowering the measured scatter for high scatter relationships.
 
@@
 Here, we present detailed simulations of the upcoming HETDEX survey's applicability to the detection and total mass measurement of galaxy clusters.
-We use mock galaxy catalogs, and simulated, HETDEX-like observational strategies to estimate the number of clusters observed and the precision of their total mass estimates, using three different cluster mass estimators.
-We discuss HETDEX's ability to constrain the cosmological parameter $\sigma_8 h^{-1}$ and comment on how HETDEX may improve current and future photometric large-area sky surveys' cluster mass estimates derived from optical richness.
+Using mock galaxy catalogs and HETDEX-like observational strategies and limits, we observe our simulated sky, estimate the number of clusters observed, and derive basic cluster parameters, redshift, line-of-sight velocity dispersion (LOSVD).
+Using a traditional power law-based, velocity dispersion, scaling relation along with more advanced probability and machine learning (ML) techniques, we estimate each cluster's total mass.
+We discuss each cluster mass estimate's precision, and discuss HETDEX's ability to constrain the cosmological parameter $\sigma_8 h^{-1}$ based on those predicted cluster masses.
+In addition, we comment on how HETDEX may improve current and future photometric large-area sky surveys' cluster mass estimates derived from optical richness.
 
@@
 \begin{enumerate}
-	\item We find 14,189 clusters with at least five cluster members in the HETDEX cluster survey volume.
-Of those, approximately 1,760 clusters are detected with HETDEX-like survey observations.
-The number of cluster members recovered is almost exactly 4.5 times fewer than a fully Targeted survey, across both a wide range of redshifts and cluster masses.
-	\item Overall, we find a traditional power law conversion from LOSVD to cluster mass performs significantly poorer than either the probability based or ML based methods also tested.
-The probability based and ML based cluster mass estimators are able to more accurately predict cluster mass when combined with information other than just the LOSVD.
-While the power law may be outperformed, overall, comparisons of similar mass galaxy clusters shows that above Log M/\Msol\ $=14.5$, the power law gives a lower bias than either the probability based or ML based methods.
-For HETDEX-like observations and clusters with $13 < \mathrm{Log}\, M/\Msol <14.5$, we find the $ML_{\sigma, z, N_{gal}}$ method performs the best.
+	\item After considering HETDEX's observational limits, we find 14,189 clusters with at least five cluster members in the HETDEX survey volume.
+Of those, 1,760 clusters are detected with HETDEX-like survey observations.
+The number of cluster members recovered with Survey observations is almost exactly 4.5 times fewer than a fully Targeted survey, across both a wide range of redshifts and cluster masses.
+
+	\item We find a traditional power law conversion from LOSVD to cluster mass predicts the true cluster mass with little bias or scatter for clusters Log M/\Msol\ $=14.5$ and above.
+Below this mass the bias and scatter rapidly increases.
+In contrast, the probability based and ML based cluster mass estimators are able to predict cluster mass with similar or smaller scatter across all cluster masses.
+The scatter further decreases when the probability based and ML estimators are combined with other cluster observables besides the LOSVD.
+For HETDEX-like observations and clusters with $13 < \mathrm{Log}\, M/\Msol <14.5$, we find the $\mathrm{ML}_{\sigma, z, N_{gal}}$ method results in the smallest scatter.
 Below Log M/\Msol\ $=13$ no method with Survey observations gives a bias of less than 50\%.
-	\item For follow-up Targeted observations only galaxy clusters with masses inferred to be Log M/\Msol\ $<13$ from Survey observations should be targeted.
-Galaxy clusters with inferred masses below Log M/\Msol\ $=13$ can see as much as an 81\% improvement in cluster mass estimation with Targeted observations.
-While the improvement of clusters with masses above Log M/\Msol\ $=13$ is often approximately 10\%.
+For the highest mass clusters the power law method gives the lowest bias and scatter.
+In short, no single method is superior in all regards.
+The technique should be chosen to minimize the desired systematic, but we find $\mathrm{ML}_{\sigma, z, N_{gal}}$ provides the best performance across the large range of cluster masses, and observation strategies.
+
+	\item In general, we find that the measured scatter of cluster masses decreases when considering Targeted versus Survey observations.
+Clusters at all masses can benefit from targeted follow-up observations, although the accuracy gain will be smaller than can be achieved from cluster mass prediction method changes.
+Targeted follow-up observations reduces the measured scatter by $\sim10\%$ when comparing like recovery methods.
+
+	\item The $\sim51\%$ cluster mass accuracy of Survey observations places approximately a 20\% constraint on $\sigma_8 h^{-1}$.
+This can be tightened to approximately 12\% with follow-up targeted observations.
+Most importantly, the observations from HETDEX will provide systematics checks on other studies, ultimately improving all future measurements of $\sigma_8 h^{-1}$
+
 	\item HETDEX will be able to place important, independent constraints on the amount of scatter in the optical richness-mass relationship.
 It will to a less extent constrain the overall normalization of the relation.
-This should provide an important too in the calibration of large-area sky surveys which rely on photometric data only to estimate cluster masses.
+This should provide an important tool in the calibration of large-area sky surveys which rely on photometric data only to estimate cluster masses.
 \end{enumerate}
@@
 The authors also wish to thank the anonymous referee whose comments and suggestions significantly improved both the quality and clarity of this work.
-We also thank Steven W.
-Crawford for many helpful discussions.
 This research made use of This research made use of the {\sc IPython} package \citep{Perez2007} and {\sc matplotlib}, a Python library for publication quality graphics \citep{Hunter2007}.
-Figure \ref{fig: probability corner} is heavily based on \cite{Foreman-Mackey2016}.
 Funding for the SDSS and SDSS-II has been provided by the Alfred P.

### 2016-06-05 paper1.tex
redMaPPer formating

@@
 One promising cluster mass estimator is the optical richness \citeeg{Abell1958}.
-Specifically, here, we use $\lambda$, the weighted number of galaxies within a scale aperture \citeeg{Rozo2011} as calculated by the redMapper algorithm \citep{Rykoff2012}.
+Specifically, here, we use $\lambda$, the weighted number of galaxies within a scale aperture \citeeg{Rozo2011} as calculated by the redMaPPer algorithm \citep{Rykoff2012}.
 Previous works \citeeg{Rozo2010} show that the richness correlates strongly with cluster mass on the average, but the absolute mass scale of the optical richness mass estimator and the scatter in cluster mass at fixed optical richness are imprecisely known \citep{Rykoff2012}.

### 2016-06-20 paper1.tex
add sql

@@
 \usepackage{etoolbox}
+\usepackage{listings}
 
@@
 The Millennium simulation tracks $2160^3$ dark matter particles of $8.6\times 10^8 ~h^{-1}$ \Msol\ inside a comoving 500 $(h^{-1} \mathrm{Mpc})^3$ box from $z=127$ to 0.
+The following SQL query selects the cluster halos:
+\begin{lstlisting}[language=SQL]
+SELECT * 
+FROM   mfield..fof 
+WHERE  snapnum IN (SELECT snapnum 
+                   FROM   snapshots..mr 
+                   WHERE  z BETWEEN 0.01 AND 0.5) 
+       AND m_crit200 > 100 
+       AND random BETWEEN 0 AND 10000 
+\end{lstlisting}
+To select the corresponding galaxies, we use:
+\begin{lstlisting}[language=SQL, breaklines=true]
+SELECT sh.fofid, 
+       sh.subhaloid, 
+       g.galaxyid, 
+       g.x, 
+       g.y, 
+       g.z, 
+       g.redshift, 
+       g.velx, 
+       g.vely, 
+       g.velz, 
+       sdss.g_sdss, 
+       sdss.r_sdss, 
+       sdss.i_sdss 
+FROM   mfield..fofsubhalo AS sh 
+       INNER JOIN mpagalaxies..delucia2006a AS g 
+               ON sh.subhaloid = g.subhaloid 
+       INNER JOIN mpagalaxies..delucia2006a_sdss2mass AS sdss 
+               ON g.galaxyid = sdss.galaxyid 
+WHERE  sh.fofid IN (SELECT fofid 
+                FROM   mfield..fof 
+                WHERE  snapnum IN (SELECT snapnum 
+                               FROM   snapshots..mr 
+                               WHERE  z BETWEEN 0.01 AND 0.5) 
+                       AND m_crit200 > 1000 
+                       AND random BETWEEN 0 AND 10000) 
+\end{lstlisting}
 

### 2016-06-27 paper1.tex
copy and paste from thesis

@@
 \newcommand{\editorial}[1]{\textcolor{red}{#1}}
-\DeclareRobustCommand{\ion}[2]{%
-\relax\ifmmode
-\ifx\testbx\f@series
-{\mathbf{#1\,\mathsc{#2}}}\else
-{\mathrm{#1\,\mathsc{#2}}}\fi
-\else\textup{#1\,{\mdseries\textsc{#2}}}%
-\fi}
 \newcommand{\multic}[2]{\multicolumn{#1}{c}{#2}}
@@
 Designed to probe the evolution of the dark energy equation of state etched onto high redshift ($z>2$) galaxies by the Baryon Acoustic Oscillations (BAO) \citep{Eisenstein2005} in the first moments of the universe, the survey will observe two fields for a total of 420 \degsq\ (300 \degsq, Spring field and 120 \degsq, Fall field).
-Tuned to find \lya\ emitting (LAE) galaxies at $1.9<z<3.5$, HETDEX expects to find 800,000 LAEs, and more than one million [\ion{O}{ii}] emitting galaxies at $z<0.5$ masquerading as high-redshift galaxies \citep{Acquaviva2014}.
+Tuned to find \lya\ emitting (LAE) galaxies at $1.9<z<3.5$, HETDEX expects to find 800,000 LAEs, and more than one million \hbox{[\ion{O}{II}]} emitting galaxies at $z<0.5$ masquerading as high-redshift galaxies \citep{Acquaviva2014}.
 
@@
 \begin{figure*}
-	\includegraphics[width=0.9\textwidth]{figures/oii_sdss.pdf} 
-	\caption{\textit{Left}: CMD of 503,113 $z<0.2$ galaxies take from the SDSS DR12 where the shading scales with the density of points.
+	\includegraphics[width=\textwidth]{figures/oii_sdss.pdf} 
+	\caption[Illustration of the probability based \hbox{[\ion{O}{II}]} flux prediction method.]{\textit{Left}: CMD of 503,113 $z<0.2$ galaxies take from the SDSS DR12 where the shading scales with the density of points.
 The two colored boxes show regions containing potential catalog galaxies.
-\textit{Right}: Probability histograms of the Log [\ion{O}{ii}] luminosity for the SDSS galaxies located in the two highlighted regions on the right.
-The [\ion{O}{ii}] luminosities are assigned to catalog galaxies from slice sampling the probability histogram and converted to fluxes using the redshift of each galaxy.} \label{fig: oii sdss}
+\textit{Right}: Probability histograms of the Log \hbox{[\ion{O}{II}]} luminosity for the SDSS galaxies located in the two highlighted regions on the right.
+The \hbox{[\ion{O}{II}]} luminosities are assigned to catalog galaxies from slice sampling the probability histogram and converted to fluxes using the redshift of each galaxy.}
+	\label{fig: oii sdss} 
 \end{figure*}
@@
 Finally we summarize our findings in Section \ref{sec:summary}.
-A follow-up to this work \citep{Boada2016a} will investigate how the techniques developed here will work in practice.
+A follow-up to this work Boada \etal\ (in Preparation) will investigate how the techniques developed here will work in practice.
 
@@
 % \begin{figure}
-% 	\includegraphics[width=\columnwidth]{figures/hmf.pdf}
+% 	\includegraphics[width=\textwidth]{figures1/hmf.pdf}
 % 	\caption{The cumulative MF (from \citealt{Tinker2008}) of halos above $M_{200c}$ at $z=0.1$}
@@
 
-\subsection{Conditional [\ion{O}{ii}] Flux Probability Distribution Functions}\label{sec: oii luminosity}
-We use the SDSS DR12 \citep{Alam2015} catalogs to assign [\ion{O}{ii}] emission line strengths to the galaxies in the Buzzard catalog.
-We use 503,113 objects classified as galaxies selected over $z = 0.02 - 0.2$ with {\sc zwarning $=0$} and a measured [\ion{O}{ii}] line flux signal-to-noise of five.
+\subsection{Conditional [\ion{O}{II}] Flux Probability Distribution Functions}\label{sec: oii luminosity}
+We use the SDSS DR12 \citep{Alam2015} catalogs to assign \hbox{[\ion{O}{II}]} emission line strengths to the galaxies in the Buzzard catalog.
+We use 503,113 objects classified as galaxies selected over $z = 0.02 - 0.2$ with {\sc zwarning $=0$} and a measured \hbox{[\ion{O}{II}]} line flux signal-to-noise of five.
 Figure~\ref{fig: oii sdss} shows the color-magnitude diagram (CMD) of $M_r$ and $g-r$ for these galaxies.
 
-To assign an [\ion{O}{ii}] luminosity to each galaxy in our catalog, we place the catalog galaxies on the same CMD and select all SDSS galaxies in a small 2D ($M_r$, $g-r$) bin around the galaxy.
-We extract all of the SDSS galaxies inside that bin and create a histogram of their [\ion{O}{ii}] luminosities, the right panel of Figure \ref{fig: oii sdss}.
-Using a slice sampling technique \citep{Neal1997} we assign the catalog galaxy an [\ion{O}{ii}] luminosity based on the distribution of SDSS galaxies in that bin.
+To assign an [\ion{O}{II}] luminosity to each galaxy in our catalog, we place the catalog galaxies on the same CMD and select all SDSS galaxies in a small 2D ($M_r$, $g-r$) bin around the galaxy.
+We extract all of the SDSS galaxies inside that bin and create a histogram of their [\ion{O}{II}] luminosities, the right panel of Figure \ref{fig: oii sdss}.
+Using a slice sampling technique \citep{Neal1997} we assign the catalog galaxy an [\ion{O}{II}] luminosity based on the distribution of SDSS galaxies in that bin.
 In very few cases (1.3\% of galaxies) do the $g-r$ and $M_r$ magnitudes of the galaxies in the Buzzard catalog not overlap with the distributions in SDSS.
-For these objects, we assign them zero [\ion{O}{ii}] flux, but this has no impact on our analysis.
-For catalog galaxies with have very few ($1\leq N<10$) SDSS galaxies in their respective bin, we assign it the mean [\ion{O}{ii}] flux.
+For these objects, we assign them zero [\ion{O}{II}] flux, but this has no impact on our analysis.
+For catalog galaxies with have very few ($1\leq N<10$) SDSS galaxies in their respective bin, we assign it the mean [\ion{O}{II}] flux.
 
@@
 The numbered boxes in the left panel show the bins corresponding to two example Buzzard galaxies ($M_r, g-r = -17.7,~0.49$ and $M_r, g-r = -21.4,~1.24$).
-The right panel shows the Log [\ion{O}{ii}] luminosity distribution functions, $P($[\ion{O}{ii}]$| M_r, g-r)$, which we use to assign [\ion{O}{ii}] luminosity to each object.
-The luminosity is then converted into an [\ion{O}{ii}] flux through
+The right panel shows the Log [\ion{O}{II}] luminosity distribution functions, $P($[\ion{O}{II}]$| M_r, g-r)$, which we use to assign [\ion{O}{II}] luminosity to each object.
+The luminosity is then converted into an [\ion{O}{II}] flux through
 \begin{equation}
@@
 \includegraphics[width=\columnwidth]{figures/pointings.pdf} 
-	\caption{Representative observation tiling scheme for the HETDEX $16' \times 16'$ pointings.
+	\caption[HETDEX pointing strategy.]{Representative observation tiling scheme for the HETDEX $16' \times 16'$ pointings.
 Each turquoise square represents the position of a single VIRUS IFU, and the dashed octagons approximate the size of a single observation.
 Inside each IFU HETDEX will achieve near complete coverage through three dithers.
-See the text for more details.} \label{fig: ifu layout}
+See the text for more details.}
+	\label{fig: ifu layout} 
 \end{figure}
@@
 The entire HETDEX survey will cover 420 \degsq\ with a 1/4.5 filling factor over two fields: a $\sim 300$ \degsq\ northern field, and a $\sim 140$ \degsq\ equatorial region.
-The spectral coverage allows for the detection of [\ion{O}{ii}] ($\lambda\lambda 3727,3729$) emitters to $z\sim 0.5$ and Ca H ($\lambda 3968.5$) and K ($\lambda 3933.7$) absorption features to $z\sim 0.4$.
+The spectral coverage allows for the detection of [\ion{O}{II}] ($\lambda\lambda 3727,3729$) emitters to $z\sim 0.5$ and Ca H ($\lambda 3968.5$) and K ($\lambda 3933.7$) absorption features to $z\sim 0.4$.
 The $10 \sigma$ detection threshold for spectral features will be $3.5\times10^{-17}$ \ergscm\ at 5000 \AAA, or equivalently, $g = 21.9$ mag for continuum objects.
@@
 The following is, in many cases, a subset of the available methods to derive any single parameter.
-The specific choice of method may improve or diminish the accuracy of the recovered parameter, but the methods chosen were to facilitate comparison with other observational studies \citeeg{Kirk2015, Boada2016a}.
+The specific choice of method may improve or diminish the accuracy of the recovered parameter, but the methods chosen were to facilitate comparison with other observational studies \citeeg{Kirk2015}.
 
@@
 In practice, the first moment is strongly subject to outliers, so we rely instead on the biweight location estimator \citep{Beers1990} through\footnote{Implemented as part of the {\sc astLib} Python library.
-See \hbox{\url{http://astlib.sourceforge.net}}}:
+See \hbox{http://astlib.sourceforge.net}}:
 \begin{equation}
@@
 \end{equation}
-where $\sigma_{1D}$, $\langle\mu\rangle$, and $\sigma_i$ is the LOSVD, the average radial velocity and the error on the individual LOSVs (which we have assumed to be normally distributed) respectively, using a Monte Carlo Markov Chain (MCMC) sampler ({\sc emcee}\footnote{\url{http://dan.iel.fm/emcee/current/}}; \citealt{Foreman-Mackey2013}) which is based on affine-invariant ensemble sampler (see \citealt{Goodman2010} for details on affine-invariant samplers).
+where $\sigma_{1D}$, $\langle\mu\rangle$, and $\sigma_i$ is the LOSVD, the average radial velocity and the error on the individual LOSVs (which we have assumed to be normally distributed) respectively, using a Monte Carlo Markov Chain (MCMC) sampler ({\sc emcee}\footnote{http://dan.iel.fm/emcee/current/}; \citealt{Foreman-Mackey2013}) which is based on affine-invariant ensemble sampler (see \citealt{Goodman2010} for details on affine-invariant samplers).
 We draw twenty thousand samples from the posterior probability distribution using simple priors, $\langle\mu\rangle$ lies between the maximum and minimum LOSV and $0< \sigma_{1D} < 1400$ \kms.
@@
 In simple tests where the values of both $\sigma_{1D}$ and $\langle\mu\rangle$ are known, the 68\% error bars derived from the MCMC method give slightly better results with the true LOSVD value bracketed by the error bars in $\sim68\%$ of the cases versus $\sim57\%$ with bootstrapping and a single statistic.
-In addition, we prefer the maximum likelihood method for its straight forward treatment of the errors in the LOSV measurements, which will become important in the practical application to real data \citeeg{Boada2016a}.
+In addition, we prefer the maximum likelihood method for its straight forward treatment of the errors in the LOSV measurements, which will become important in the practical application to real data (\eg, Boada \etal\ in Preparation).
 
@@
 		\includegraphics[width=\textwidth]{figures/prob_example.pdf} 
-	\caption{Illustration of the probability based cluster mass prediction method.
+	\caption[Illustration of the probability based cluster mass prediction method.]{Illustration of the probability based cluster mass prediction method.
 \emph{Left}: The two dimensional posterior probability distribution of LOSVD and redshift used to determine the correct cluster mass.
@@
 \emph{Right}: The conditional probability distribution of the cluster mass for the two example galaxies.
-See text for a complete description.} \label{fig: probability corner}
+See text for a complete description.}
+	\label{fig: probability corner} 
 \end{figure*}
@@
 
-\section{RESULTS}\label{sec:results}
+\section{Results}\label{sec:results}
 Here we explore the cluster member recovery rate and mass estimates for the two observing strategies, Targeted, and Survey.
@@
 	\includegraphics[width=0.8\textwidth]{figures/recovery.pdf} 
-	\caption{Recovery fractions ($N_{obs}/N_{True}$) of cluster member galaxies as a function of redshift and true cluster mass for the Targeted and Survey observing strategies.
+	\caption[Recovery fractions for the Targeted and Survey observations.]{Recovery fractions ($N_{obs}/N_{True}$) of cluster member galaxies as a function of redshift and true cluster mass for the Targeted and Survey observing strategies.
 We have applied HETDEX-like observational limits on the cluster galaxy detection, and require at least five galaxies to be detected for a cluster to be recovered.
@@
 This leads to lower recovery fractions of high mass clusters as many only exist at larger redshifts.
-The significant decline in the number of galaxies observed with the Survey strategy is due to gaps in the VIRUS IFU, where the galaxies are missed.} \label{fig: recovery}
+The significant decline in the number of galaxies observed with the Survey strategy is due to gaps in the VIRUS IFU, where the galaxies are missed.}
+	\label{fig: recovery} 
 \end{figure*}
@@
 
-The recovery fractions in Figure~\ref{fig: recovery} are an outcome of the magnitude limit and [\ion{O}{ii}] line-flux limit of the survey.
+The recovery fractions in Figure~\ref{fig: recovery} are an outcome of the magnitude limit and \hbox{[\ion{O}{II}]} line-flux limit of the survey.
 For Perfect observations, we would detect all members across all cluster masses and redshifts.
@@
 	\includegraphics[width=\textwidth]{figures/Probcomparison.pdf} 
-	\caption{Mass predictions for the power law scaling relation (Equation~\ref{eq:power law}) and the probability based technique with different input features as a function of true cluster mass.
+	\caption[Probability based cluster mass predictions.]{Mass predictions for the power law scaling relation (Equation~\ref{eq:power law}) and the probability based technique with different input features as a function of true cluster mass.
 The bottom row of panels shows the fractional error (Equation~\ref{eq: fractional error}) also as a function of true cluster mass.
@@
 The solid, purple line is the median predicted mass for the Targeted observing, and the green, dashed line is the median recovered mass for the HETDEX-like observations.
-The shaded regions represent the 68\% scatter around the median values.} \label{fig:Probability comparison}
+The shaded regions represent the 68\% scatter around the median values.}
+	\label{fig:Probability comparison} 
 \end{figure*}
@@
 	\includegraphics[width=\textwidth]{figures/MLcomparison.pdf} 
-	\caption{Mass predictions for the power law scaling relation (Equation~\ref{eq:power law}) and the ML based technique with different input features as a function of true cluster mass.
+	\caption[ML based cluster mass predictions]{Mass predictions for the power law scaling relation (Equation~\ref{eq:power law}) and the ML based technique with different input features as a function of true cluster mass.
 The bottom row of panels shows the fractional error (Equation~\ref{eq: fractional error}) also as a function of true cluster mass.
@@
 The solid, purple line is the median predicted mass for the Targeted observing, and the green, dashed line is the median recovered mass for the HETDEX-like observations.
-The shaded regions represent the 68\% scatter around the median values.} \label{fig: ML comparison}
+The shaded regions represent the 68\% scatter around the median values.}
+	\label{fig: ML comparison} 
 \end{figure*}
@@
 \centering
-\caption{Mean bias (Eqn.~\ref{eqn: bias}) for different bins of predicted cluster mass.
+\caption[Mean bias for different bins of predicted cluster mass.]{Mean bias (Eqn.~\ref{eqn: bias}) for different bins of predicted cluster mass.
 This table shows the bias in the predicted cluster mass for the perfect (top section), Targeted (middle section), and Survey (bottom section) observations in different predicted mass bins.
@@
 \centering
-\caption{Scatter (Eqn.~\ref{eqn: scatter}) in cluster mass after bias correction for different bins of predicted cluster mass.
+\caption[Mean scatter in cluster mass after bias correction for different bins of predicted cluster mass.]{Mean scatter (Eqn.~\ref{eqn: scatter}) in cluster mass after bias correction for different bins of predicted cluster mass.
 This table shows the scatter in the predicted cluster mass for the perfect (top section), Targeted (middle section), and Survey (bottom section) observations in different predicted mass bins.
@@
 We select 4,806 clusters, comprised of 623,663 galaxies, at $0.02 < z < 0.5$ and $M > 10^{13}$ \Msol, and apply the same data processing as with the Buzzard galaxies.
-We begin by assigning each galaxy an [\ion{O}{ii}] flux value (see Section \ref{sec: oii luminosity}), and ``observe'' each galaxy using realistic (see Section \ref{sec: observations}) observational limits.
+We begin by assigning each galaxy an \hbox{[\ion{O}{II}]} flux value (see Section \ref{sec: oii luminosity}), and ``observe'' each galaxy using realistic (see Section \ref{sec: observations}) observational limits.
 After recovering 3750 clusters which have at least five galaxies observed, we calculate the LOSVD of each cluster as in Section \ref{sec: LOSVD}.
@@
 	\includegraphics[width=\columnwidth]{figures/millBuzzComparison.pdf} 
-	\caption{\emph{Top:} ML based cluster mass predictions for the Millennium simulation clusters where the ML method has been trained with either a subset of the Millennium clusters (solid line) or the Buzzard catalog (dashed line).
+	\caption[ML based cluster mass predictions in the Millennium Simulation]{\emph{Top:} ML based cluster mass predictions for the Millennium simulation clusters where the ML method has been trained with either a subset of the Millennium clusters (solid line) or the Buzzard catalog (dashed line).
 The shaded areas show the 68\% scatter around the median.
@@
 Because of the simplifying assumptions, and the superior quality of the data (no contamination, signal-to-noise issues, etc.), realistic expectations for HETDEX is to directly constrain $\sigma_8h^{-1}$ is not yet competitive with other methods (\eg, CMB, WL, X-ray).
-For example, \cite{deHaan2016} constrain $\sigma_8h^{-1}$ to $\sim5$\% using a sample of 337 SZE detected clusters from the SPT-SZE survey.
+For example, \cite{DeHaan2016} constrain $\sigma_8h^{-1}$ to $\sim5$\% using a sample of 337 SZE detected clusters from the SPT-SZE survey.
 For the $\sim1500$ clusters detected with Survey observations to constrain $\sigma_8h^{-1}$ and to be dominated by cluster statistics alone ($\Delta \ln N \sim N^{-1/2}$), the absolute cluster calibration would need to be better than 2.5\%.
@@
 	\includegraphics[width=\columnwidth]{figures/massRichness.pdf} 
-	\caption{\emph{Top}: The optical richness, $\lambda$, versus the corrected predicted cluster mass.
+	\caption[Optical richness versus corrected cluster mass]{\emph{Top}: The optical richness, $\lambda$, versus the corrected predicted cluster mass.
 The solid, purple line is the median predicted mass for the Targeted observing, and the turquoise, dashed line is the median recovered mass for the HETDEX-like observations.
@@
 Color coding is the same as the top panel.
-\emph{Inset}: The evolution of the intrinsic scatter versus the average recovered scatter, $\sigma_{rec}$.} \label{fig:mass richness}
+\emph{Inset}: The evolution of the intrinsic scatter versus the average recovered scatter, $\sigma_{rec}$.}
+	\label{fig:mass richness} 
 \end{figure}

### 2016-07-06 paper1.tex
more comments
so many comments.

@@
 With HETDEX, we can recover cluster masses to $\sim0.1$ dex which can be further improved to $<0.1$ dex with targeted follow-up observations.
-This level of cluster mass recovery enables constraints on $\sigma_8$ to $<20$\%, and the unique properties of the observations will provide important calibrations for the optical richness-cluster mass relation.
+This level of cluster mass recovery enables independent constraints on $\sigma_8$ to $<20$\%, and the unique properties of the observations will provide important calibrations for the zeropoint and scatter in the optical richness-mass relation.
 \end{abstract}
@@
 
-As mass is not a direct observable, a lot of work is underway to characterize galaxy cluster masses with an observable feature of galaxy clusters.
-The goal is to constrain $P(M|z, \vec{x})$ the probability density ($P$) that a galaxy cluster of given mass ($M$), located at redshift ($z$) determined using an observable parameter or parameters ($\vec{x}$).
+As mass is not a direct observable, a lot of work is underway to characterize galaxy cluster masses with an observable feature of galaxy clusters \citeeg{Mantz2016,Bocquet2015,Old2015,Old2014, Pearson2015}.
+The goal is to constrain $P(M|z, \vec{x})$ the probability density ($P$) that a galaxy cluster of given mass ($M$), located at a specific redshift ($z$), determined using an observable parameter or parameters ($\vec{x}$).
 Generally, cluster mass calibrations are done in one of two ways, through simulations or direct or statistical calibration.
@@
 Optically, the on going Dark Energy Survey (DES; \citealt{DES2005}) and planned Large Synoptic Survey Telescope (LSST; \citealt{LSST2012}) will identify many thousands of clusters to much lower masses than is possible with SZE measurements.
-However, regardless of the discovery method used, spectroscopic follow-up is needed to further constrain $P(M|z,X)$.
+However, regardless of the discovery method used, spectroscopic follow-up is needed to further constrain $P(M|z,\vec{x})$.
 This follow-up becomes increasing important to help constrain the scatter in the mass estimates of other methods, and provides an additional, independent check of the observable-mass relationship used.
@@
 
-The Hobby Eberly Telescope Dark Energy eXperiment (HETDEX; \citealt{Hill2008}) is a trailblazing effort to observe high-redshift large scale structures using cutting edge wide-field integral field unit (IFU) spectrographs.
-Designed to probe the evolution of the dark energy equation of state etched onto high redshift ($z>2$) galaxies by the Baryon Acoustic Oscillations (BAO) \citep{Eisenstein2005} in the first moments of the universe, the survey will observe two fields for a total of 420 \degsq\ (300 \degsq, Spring field and 120 \degsq, Fall field).
-Tuned to find \lya\ emitting (LAE) galaxies at $1.9<z<3.5$, HETDEX expects to find 800,000 LAEs, and more than one million \hbox{[\ion{O}{II}]} emitting galaxies at $z<0.5$ masquerading as high-redshift galaxies \citep{Acquaviva2014}.
+The Hobby Eberly Telescope Dark Energy eXperiment (HETDEX; \citealt{Hill2008}) will observe high-redshift large scale structures using cutting edge wide-field integral field unit (IFU) spectrographs.
+Designed to probe the evolution of the dark energy equation of state etched onto high redshift ($z>2$) galaxies by the Baryon Acoustic Oscillations (BAO) \citep{Eisenstein2005}, the survey will observe two fields for a total of 420 \degsq\ (300 \degsq, Spring field and 120 \degsq, Fall field).
+Tuned to find \lya\ emitting (LAE) galaxies at $1.9<z<3.5$, HETDEX expects to find 800,000 LAEs, and more than one million [\ion{O}{II}] emitting galaxies at $z<0.5$ masquerading as high-redshift galaxies \citep{Acquaviva2014}.
 
@@
 It is unclear how a blind spectroscopic survey with an IFU will effect the recovery of galaxy cluster dynamical properties.
-Unlike many previous large cluster surveys \citeeg{Milvang-Jensen2008, Robotham2011, Sifon2015} which use multi-object spectrographs, the Visible Integral-Field Replicable Unit Spectrograph (VIRUS; \citealt{Hill2012}) used by HETDEX samples the sky in a uniform but sparse way which could excluded member galaxies which would otherwise be included.
+Unlike many previous large cluster surveys \citeeg{Milvang-Jensen2008, Robotham2011, Sifon2015} which use multi-object spectrographs, the Visible Integral-Field Replicable Unit Spectrograph (VIRUS; \citealt{Hill2012}) used by HETDEX samples the sky in a uniform but sparse way which could exclude member galaxies which would otherwise be included.
 Secondly, it is not straightforward to use spectroscopic redshifts predominately from emission-line galaxies to interpret the kinematic and dynamical states of the clusters.
@@
 
-\subsection{The Buzzard Mock Catalogs}
-The Buzzard mock galaxy catalogs cover 398.49 \degsq\ between $4^h< RA < 6^h$ and $-61\degree < DEC < -41\degree$ and are derived from a combination of Sub-halo Abundance Matching (ShAM) and ADDSEDs (Adding Density Dependent Spectral Energy Distributions) tied to an in house n-body cosmological simulation.
+\subsection{The Buzzard Mock Catalogs}\label{sec: Buzzard}
+The Buzzard mock galaxy catalogs provide a light cone covering 398.49 \degsq\ between $4^h< RA < 6^h$ and $-61\degree < DEC < -41\degree$ and are derived from a combination of Sub-halo Abundance Matching (ShAM) and ADDSEDs (Adding Density Dependent Spectral Energy Distributions) tied to an in house n-body cosmological simulation.
 A brief description of the catalog creation is described as follows.
@@
 A $M_r$-density-SED relation is created using a SDSS training set, and for each mock galaxy the SED of a randomly selected training set galaxy which has a similar $M_r$ and density is assigned.
+The assigned SED is also used to determine additional $ugiz$ magnitudes.
 The result is a mock catalog containing 238 million galaxies with $\sdssr < 29$ mag and $z \leq 8.7$.
@@
 
-\subsection{Conditional [\ion{O}{II}] Flux Probability Distribution Functions}\label{sec: oii luminosity}
-We use the SDSS DR12 \citep{Alam2015} catalogs to assign \hbox{[\ion{O}{II}]} emission line strengths to the galaxies in the Buzzard catalog.
-We use 503,113 objects classified as galaxies selected over $z = 0.02 - 0.2$ with {\sc zwarning $=0$} and a measured \hbox{[\ion{O}{II}]} line flux signal-to-noise of five.
+\subsection{Conditional {\rm[\ion{O}{II}]} Flux Probability Distribution Functions}\label{sec: oii luminosity}
+We use the SDSS DR12 \citep{Alam2015} catalogs to assign [\ion{O}{II}] emission line strengths to the galaxies in the Buzzard catalog.
+We use 503,113 objects classified as galaxies selected over $z = 0.02 - 0.2$ with {\sc zwarning $=0$} and a measured [\ion{O}{II}] line flux signal-to-noise of five.
 Figure~\ref{fig: oii sdss} shows the color-magnitude diagram (CMD) of $M_r$ and $g-r$ for these galaxies.
@@
 Using a slice sampling technique \citep{Neal1997} we assign the catalog galaxy an [\ion{O}{II}] luminosity based on the distribution of SDSS galaxies in that bin.
-In very few cases (1.3\% of galaxies) do the $g-r$ and $M_r$ magnitudes of the galaxies in the Buzzard catalog not overlap with the distributions in SDSS.
+In very few cases (1.3\% of galaxies), the $g-r$ and $M_r$ magnitudes of the galaxies in the Buzzard catalog do not overlap with the distributions in SDSS.
 For these objects, we assign them zero [\ion{O}{II}] flux, but this has no impact on our analysis.
@@
 Both of these observations have HETDEX-like galaxy detection thresholds (described in the previous subsection), so while a galaxy may be observed, a redshift will only be measured if the galaxy satisfies the continuum brightness or emission line flux limits for the HETDEX survey.
-For comparison we also include a set of Targeted observations with ``perfect'' knowledge which assume no detection threshold, if a cluster member galaxy is observed, it is also detected.
-This provides an important best-case scenario, and differs from the true cluster properties between we are still calculating the cluster mass from the observed member galaxy velocity dispersions, and represent the best possible mass estimates using velocity dispersion as the observable.
-These observations provide three levels of quality with ``Perfect knowledge'' being the highest and Survey being the lowest.
+For comparison we also include a Perfect observation, in which we assume all galaxies in a field are observed and all redshifts measured.
+This provides a baseline where the cluster properties are calculated under the best possible conditions and against which we can compare the results of the ``Targeted'' and ``Survey'' observing strategies.
 
 \section{Recovery of Parameters}\label{sec:recovery}
-In the following subsections, we outline the methods we use to derive the dynamical properties of the galaxy clusters in our sample.
-The following is, in many cases, a subset of the available methods to derive any single parameter.
-The specific choice of method may improve or diminish the accuracy of the recovered parameter, but the methods chosen were to facilitate comparison with other observational studies \citeeg{Kirk2015}.
-
 \subsection{Cluster Redshift}
@@
 \begin{equation}
-C_{BI} = M + \frac{\sum_{|u_i| < 1} (z_i - M)(1-u_i^2)^2}{\sum_{|u_i| < 1}(1-u_i^2)^2}
-\end{equation}
-where $z_i$ are the individual redshifts, $M$ is the median redshift and $u_i$ is given by:
+z_c = z_{med} + \frac{\sum_{|u_i| < 1} (z_i - M)(1-u_i^2)^2}{\sum_{|u_i| < 1}(1-u_i^2)^2}
+\end{equation}
+where $z_i$ are the individual redshifts, $z_{med}$ is the median redshift and $u_i$ is given by:
 \begin{equation}
@@
 We choose $C=6$ (the suggested value) which balances computational speed and location accuracy.
-
-Although this work assumes that we know each galaxy's redshift to infinite precision, in practice, we find a simple weighted mean provides a reliable estimate of $z_c$ when there are uncertainties on the individual galaxy redshifts.
+% Although this work assumes that we know each galaxy's redshift to infinite precision, in practice, we find a simple weighted mean provides a reliable estimate of $z_c$ when there are uncertainties on the individual galaxy redshifts.
 
@@
 
-We follow the maximum likelihood method of \cite{Walker2006} to estimate the line-of-sight velocity dispersion (LOSVD). We maximize the probability function 
+We follow the maximum likelihood method of \cite{Walker2006} to estimate the line-of-sight velocity dispersion (LOSVD).
+Using the previously calculated LOSVs ($v_i$ in the following discussion), we maximize the probability function:
 \begin{equation}\label{eq: jointGaussian}
@@
 \end{equation}
-where $\sigma_{1D}$, $\langle\mu\rangle$, and $\sigma_i$ is the LOSVD, the average radial velocity and the error on the individual LOSVs (which we have assumed to be normally distributed) respectively, using a Monte Carlo Markov Chain (MCMC) sampler ({\sc emcee}\footnote{http://dan.iel.fm/emcee/current/}; \citealt{Foreman-Mackey2013}) which is based on affine-invariant ensemble sampler (see \citealt{Goodman2010} for details on affine-invariant samplers).
-We draw twenty thousand samples from the posterior probability distribution using simple priors, $\langle\mu\rangle$ lies between the maximum and minimum LOSV and $0< \sigma_{1D} < 1400$ \kms.
-We set the upper limit on the LOSVD as the LOSVD corresponding to a $10^{16}$ \Msol\ cluster at $z\sim0.0$, higher mass than any expected cluster in Buzzard.
-When the full distribution of LOSVDs is not used, the final LOSVD is quoted as the median value of the posterior probability distribution with 68\% error bars defined as the square root of second moment of the same distribution, the standard deviation.
+where $\sigma_{1D}$, $\langle u \rangle$, and $\sigma_i$ is the LOSVD, the average radial velocity and the error (which we have assumed to be normally distributed) on the individual $v_i$ measurements respectively.
+To maximize Equation~\ref{eq: jointGaussian}, we employ a Monte Carlo Markov Chain (MCMC) sampler ({\sc emcee}\footnote{http://dan.iel.fm/emcee/current/}; \citealt{Foreman-Mackey2013}) which is based on affine-invariant ensemble sampler (see \citealt{Goodman2010} for details on affine-invariant samplers).
+We draw twenty thousand samples from the posterior probability distribution using simple priors, $\langle\mu\rangle$ lies between the maximum and minimum LOSV and $0< \sigma_{1D} < 1400$ \kms, for each cluster.
+We set the upper limit on the LOSVD as the LOSVD corresponding to a $10^{16}$ \Msol\ cluster at $z\sim0.0$, higher mass than any expected cluster in the Buzzard catalogs.
+When the complete sampling of the posterior probability distribution is not used, the final LOSVD is quoted as the median value of the posterior probability distribution with 68\% error bars defined as the square root of second moment of the same distribution, the standard deviation.
 
@@
 \subsubsection{Power Law Based Method}
-The relationship between the LOSVD and cluster dynamical mass has been the focus of several many \citeeg{Evrard2008, Saro2013, Sifon2013, VanderBurg2014}, where the relationship for the mass enclosed by $r_{200c}$ takes the form
+The relationship between the LOSVD and cluster dynamical mass has been the focus of several previous works \citeeg{Evrard2008, Saro2013, Sifon2013, VanderBurg2014}, where the relationship for the mass enclosed by $r_{200c}$ takes the form
 \begin{equation}\label{eq:power law}
@@
 \end{equation}
-with $A_{1D} = 1177 \pm 4.2$ \kms\ (\citealt{Munari2013}; referred to as $\sigma_{15}$ in \citealt{Evrard2008} and other works), $\alpha = 1/3$, $h(z) = H(z)/100$, and $\sigma_{1D}$ is the LOSVD of the velocity tracers (dark matter particles, subhalos or galaxies).
-$H(z) = H_0 E(z)$ and $E(z) = \sqrt{\Omega_m(1+z^3)+\Omega_{\Lambda}}$.
+with $A_{1D} = 1177 \pm 4.2$ \kms\ (\citealt{Munari2013}; referred to as $\sigma_{15}$ in \citealt{Evrard2008} and other works), $\alpha = 1/3$, $h(z) = H(z)/100$ \kms\ \mpc, and $\sigma_{1D}$ is the LOSVD of the velocity tracers (dark matter particles, subhalos or galaxies).
+$H(z) = H_0\, E(z)$ and $E(z) = \sqrt{\Omega_m(1+z^3)+\Omega_{\Lambda}}$ (assuming a flat cosmology).
 
@@
 \emph{Left}: The two dimensional posterior probability distribution of LOSVD and redshift used to determine the correct cluster mass.
-The pink and green rectangles show the locations of two example galaxies used to create the conditional probability distribution of the mass, $P(M_{200c}|\vec{x})$.
+The pink and green rectangles show the locations of two example galaxies used to create the conditional probability distribution of the mass, $P(M_{200c}|z, \mathrm{Log}\, \sigma)$.
 \emph{Right}: The conditional probability distribution of the cluster mass for the two example galaxies.
@@
 As expected, the Targeted observing strategy where the individual clusters are targeted through several dithers to ensure near complete coverage, performs significantly better than the Survey observing strategy across all redshifts and cluster masses.
-With Perfect knowledge, recovery fraction would be unity across all redshifts and cluster masses where clusters exist.
+By definition, with Perfect knowledge, recovery fraction would be unity across all redshifts and cluster masses where clusters exist.
 
 For the Targeted observations, shown in the left panel of Figure~\ref{fig: recovery}, the pattern of decreasing recovery fraction as a function of redshift (y-direction) is due to the observational limits imposed.
-Because HETDEX is limited in apparent magnitude, we expect to recover fewer galaxies at higher redshift, where the galaxies are often below our $5\sigma$ detection threshold.
+Because the redshift success rate of HETDEX is limited by apparent magnitude, we expect to recover fewer galaxies at higher redshift, where the galaxies are often below our $5\sigma$ detection threshold.
 For example, we tested this by constructing an artificial HETDEX-like survey, limited by volume for all galaxies with $M_g < -11$.
@@
 If we were to limit the Survey to $z<0.2$ we find the recovery fraction of clusters, across all masses, increases substantially, and we find a much more consistent detection fraction across all masses.
+However, doing so limits severely the number of clusters at masses greater than $10^{14}$ \Msol.
 
@@
 
-The recovery fractions in Figure~\ref{fig: recovery} are an outcome of the magnitude limit and \hbox{[\ion{O}{II}]} line-flux limit of the survey.
+The recovery fractions in Figure~\ref{fig: recovery} are an outcome of the magnitude limit and [\ion{O}{II}] line-flux limit of the survey.
 For Perfect observations, we would detect all members across all cluster masses and redshifts.
@@
 For each method we consider observations with Perfect knowledge, Targeted observations and Survey observations.
-The cluster masses presented here are recovered using the best possible conditions, where we have perfect knowledge of the cluster membership.
-In reality, the mass recovery levels presented in this section represent an upper bound (the best) on the accuracy achievable through this method.
 
@@
 The cluster masses predicted by Equation \ref{eq:power law} gives the following results.
-For clusters with masses between Log M/\Msol $= 13 - 15.5$, we find $\mu_{bias} = 0.148\pm{0.008}$ dex and $\sigma_{bias} = 0.193\pm{0.001}$.
+For clusters with masses between Log M/\Msol $= 13 - 15.5$, we find $\mu_{bias} = 0.148\pm{0.008}$ dex and $\sigma_{bias} = 0.193\pm{0.001}$, but the bias does vary with cluster mass.
 The scatter in recovered masses can be attributed to both physical and numerical effects.
 The presence of any in-falling matter onto lower mass clusters can introduce a significant amount of substructure, leading to artificial biasing of the measured LOSVD to higher values, increasing the predicted mass \citeeg{Ntampaka2015}.
-Also, as the number of cluster galaxies decreases the LOSVD PDF is poorly sampled leading to poorly recovered cluster masses due to numerical effects.
+Also, as the number of cluster galaxies decreases the LOSVD probability distribution function is poorly sampled leading to poorly recovered cluster masses due to numerical effects.
 
@@
 This does not mean that the Survey observations cannot be improved by Targeted observations.
-In fact, when comparing only the galaxies which overlap between the two samples the bias and scatter of the Targeted observations is significantly decreased as more cluster member galaxies are detected, better sampling the LOSVD PDF.
-The Targeted observations performs similarly on the average because many lower mass clusters are included in the sample, increasing the bias of the overall sample.
+In fact, when comparing only the galaxies which overlap between the two samples the bias and scatter of the Targeted observations is significantly decreased as more cluster member galaxies are detected, better sampling the LOSVD probability distribution function.
+The Targeted observations perform similarly on the average because many lower mass clusters are included in the sample, increasing the bias of the overall sample.
 
@@
 We quantify the bias and scatter for all of the different cluster mass recovery strategies and observing methods in Table \ref{tbl:mass bias} and Table \ref{tbl:mass scatter}.
-It serves as a type of look up table for future cluster observations with HETDEX.
+It serves as a reference for future cluster observations with HETDEX.
 The columns represent bins of predicted galaxy cluster mass and the individual values show the bias and scatter of the true cluster mass.
@@
 A few caveats apply to the numbers given in Table \ref{tbl:mass bias} and Table \ref{tbl:mass scatter}.
-While we provide corrections for cluster masses above $10^{15}$ \msol, they are estimated from only a handful of objects, and do not constitute a representative sample of clusters.
+While we provide corrections for cluster masses above $10^{15}$ \msol, they are estimated from only a handful of objects, and may not constitute a representative sample of clusters.
 This becomes particularly apparent for the probability methods with many features.
@@
 
-To test for this, we used the Millennium simulation as an alternative data set.
-The Millennium simulation uses a set of cosmological parameters that are substantially different from Buzzard.
+To test for this, we used the Millennium simulation \citep{Springel2005a} as an alternative data set.
 The Millennium simulation adopts a flat cosmological model based of the values derived from the Two-degree Field Galaxy Redshift Survey \citep{Colless2001} and the first year data of the \emph{Wilkinson Microwave Anisotropy Probe} (WMAP; \citealt{Spergel2003}): $\Omega_\Lambda = 0.75$, $\Omega_M = 0.25$, $\sigma_8 = 0.9$, $n_s = 1$ and $H_0= 73$ \kms \mpc.
-The clusters in Millennium provide a testing sample to understand how a training sample derived from Buzzard will impact the mass recovery on a wholly new dataset.
-
-We repeat our analysis using cluster halo and galaxy catalogs from the Millennium simulation \citep{Springel2005a} obtained via querying the Millennium online database\footnote{http://gavo.mpa-garching.mpg.de/Millennium/} \citep{Lemson2006}.
+As this cosmology differs dramatically from that assumed in the Buzzard catalogs (see Section~\ref{sec: Buzzard}, the clusters in Millennium provide a testing sample to understand how a training sample derived from Buzzard will impact the mass recovery on a wholly new dataset.
+
+We repeat our analysis using cluster halo and galaxy catalogs from the Millennium simulation obtained via querying the Millennium online database\footnote{http://gavo.mpa-garching.mpg.de/Millennium/} \citep{Lemson2006}.
 The Millennium simulation tracks $2160^3$ dark matter particles of $8.6\times 10^8 ~h^{-1}$ \Msol\ inside a comoving 500 $(h^{-1} \mathrm{Mpc})^3$ box from $z=127$ to 0.
@@
 This provides a test case where we have different cosmological choices between the training and testing samples, and the same cosmological assumptions in both samples.
+In addition, it provides two different treatments of galaxy evolution in cluster environments.
+The differing galaxy evolution effects can impact observed galaxy magnitude and color evolution.
+This provides an important check to understand whether the specific assumptions made in the models affect the results of this analysis.
 
@@
 
-Based on these tests, we do not find a significant cause for concern with using trained ML methods to predict our galaxy cluster masses when the underlying cosmological choices are different.
+Based on these tests, the choice of cosmological parameters does not cause any significant offset in the predicted cluster masses from the trained ML methods.
 This highlights the versatility of our chosen ML method.
@@
 
-To get a sense of how well HETDEX will be able to constrain cosmological parameters we follow the discussion of \defcitealias{Weinberg2013}{W13}\cite{Weinberg2013} (hereafter \citetalias{Weinberg2013}), and begin with a few simplifying assumptions.
+To get a sense of how well observations of z < 0.5 galaxy clusters from HETDEX will be able to constrain cosmological parameters we follow the discussion of \defcitealias{Weinberg2013}{W13}\cite{Weinberg2013} (hereafter \citetalias{Weinberg2013}), and begin with a few simplifying assumptions.
 While sensitive to $\Omega_m$, the number density of clusters does not necessarily provide the strongest contraint, but combined with other data sets (\eg, CMB, BAO, supernovae, WL, etc.) it will constrain $\Omega_m$ to higher precision.
@@
 For a fully Targeted survey, about 14,000 clusters, this cluster mass calibration uncertainty reduces to $>1\%$.
-So while, the contraints produced by HETDEX will be larger than some other studies, the type of data provided by HETDEX will enable an independent calibration from other cluster mass measurements.
-This will provide important systematics checks on other studies and will ultimately improve the measurements of $\sigma_8h^{-1}$ .
+Nevertheless, while analysis of HETDEX clusters may not provide the most accurate constraint on $\sigma_8h^{-1}$, it will provide important systematics checks on other studies and will ultimately improve the measurements of $\sigma_8h^{-1}$.
 
@@
 One promising cluster mass estimator is the optical richness \citeeg{Abell1958}.
-Specifically, here, we use $\lambda$, the weighted number of galaxies within a scale aperture \citeeg{Rozo2011} as calculated by the redMaPPer algorithm \citep{Rykoff2012}.
+Specifically, here, we use as the richness, $\lambda$, which is the weighted number of galaxies within a scale aperture \citeeg{Rozo2011} as calculated by the redMaPPer algorithm \citep{Rykoff2012}.
 Previous works \citeeg{Rozo2010} show that the richness correlates strongly with cluster mass on the average, but the absolute mass scale of the optical richness mass estimator and the scatter in cluster mass at fixed optical richness are imprecisely known \citep{Rykoff2012}.
@@
 \section{Summary}\label{sec:summary}
-Here, we present detailed simulations of the upcoming HETDEX survey's applicability to the detection and total mass measurement of galaxy clusters.
+Here, we present detailed simulations of the upcoming HETDEX survey's applicability to the detection and total mass measurement of galaxy clusters based on emission line and continuum redshifts for galaxies at z < 0.5.
 Using mock galaxy catalogs and HETDEX-like observational strategies and limits, we observe our simulated sky, estimate the number of clusters observed, and derive basic cluster parameters, redshift, line-of-sight velocity dispersion (LOSVD).
-Using a traditional power law-based, velocity dispersion, scaling relation along with more advanced probability and machine learning (ML) techniques, we estimate each cluster's total mass.
-We discuss each cluster mass estimate's precision, and discuss HETDEX's ability to constrain the cosmological parameter $\sigma_8 h^{-1}$ based on those predicted cluster masses.
+Using a traditional power law-based, velocity dispersion, scaling relation along with more advanced probability and machine learning (ML) techniques, we estimate the total mass for each cluster.
+We discuss each cluster mass estimate's precision, and discuss the ability of HETDEX to constrain the cosmological parameter $\sigma_8 h^{-1}$ based on those predicted cluster masses.
 In addition, we comment on how HETDEX may improve current and future photometric large-area sky surveys' cluster mass estimates derived from optical richness.
@@
 \begin{enumerate}
-	\item After considering HETDEX's observational limits, we find 14,189 clusters with at least five cluster members in the HETDEX survey volume.
+	\item After considering the observational limits of HETDEX, we find 14,189 clusters with at least five cluster members in the HETDEX survey volume.
 Of those, 1,760 clusters are detected with HETDEX-like survey observations.
@@
 It is the author's hope that this work may be useful to others when conducting their own research.
-Because this work relies heavily on (often) complex data analysis, and in order to promote transparency and reproducible science, we provide all of the code used to conduct this study at https://github.com/boada/desCluster.
+Because this work relies heavily on (often) complex data analysis, and in order to promote transparency and reproducible science, we provide all of the code used to conduct this study at https://github.com/boada/HETDEXCluster.
 Regrettably, large file size prevents including the source data with the analysis routines.
@@
 \section*{Acknowledgements}
+This work is supported by the National Science Foundation through grant AST-1413317.
 The authors also wish to thank the anonymous referee whose comments and suggestions significantly improved both the quality and clarity of this work.

### 2016-07-11 paper1.tex
Eduardo's comments

@@
 \usepackage{natbib}
-%\usepackage[colorlinks,urlcolor=blue,citecolor=blue,linkcolor=blue]{hyperref}
+\usepackage[colorlinks,urlcolor=magenta,citecolor=blue,linkcolor=blue]{hyperref}
 \usepackage{multirow}
@@
 VIRUS covers the blue/optical portion of the spectrum ($3500-5500~\AAA$), allowing surveys to measure redshifts for a large sample of galaxies out to $z < 0.5$ based on their absorption features or [\ion{O}{ii}] $\lambda$3727 emission (and Lyman-$\alpha$ over $1.9 < z < 3.5$).
-We use a detailed mock galaxy catalog from a semi-analytic model to simulate surveys observed with VIRUS, including: (1) a blind, HETDEX-like survey with an incomplete but uniform spectroscopic selection function; and (2) IFU surveys that target clusters directly, obtaining spectra of all galaxies in a VIRUS-sized field.
+We use a detailed mock galaxy catalog from a semi-analytic model to simulate surveys observed with VIRUS, including: (1) a blind, HETDEX-like survey with an incomplete but uniform spectroscopic selection function; and (2) integral field unit surveys that target clusters directly, obtaining spectra of all galaxies in a VIRUS-sized field.
 For both surveys, we include realistic uncertainties from galaxy magnitude and line-flux limits.
@@
 With HETDEX, we can recover cluster masses to $\sim0.1$ dex which can be further improved to $<0.1$ dex with targeted follow-up observations.
-This level of cluster mass recovery enables independent constraints on $\sigma_8$ to $<20$\%, and the unique properties of the observations will provide important calibrations for the zeropoint and scatter in the optical richness-mass relation.
+This level of cluster mass recovery enables independent constraints on $\sigma_8$ to $<20$\%, and the unique properties of the observations will provide important calibrations for the zeropoint and scatter in the optical richness--mass relation.
 \end{abstract}
@@
 The goal is to constrain $P(M|z, \vec{x})$ the probability density ($P$) that a galaxy cluster of given mass ($M$), located at a specific redshift ($z$), determined using an observable parameter or parameters ($\vec{x}$).
-Generally, cluster mass calibrations are done in one of two ways, through simulations or direct or statistical calibration.
+Generally, cluster mass calibrations are done in one of three ways, through simulations, direct or statistical calibration.
 
@@
 This recipe has two distinct but not always independent tracks.
-The ``direct'' method uses observations of a relatively small set of clusters and then uses known mass estimators, including X-ray temperatures and luminosities \citeeg{Mantz2010, Rykoff2014}, microwave observations \citeeg{Vanderlinde2010, Sehgal2011}, optical richness \citeeg{Abell1958, Rykoff2012} or weak lensing (WL; \eg\ \citealt{Rozo2010}) as examples, which provide a ``true'' mass.
+The ``direct'' method uses observations of a relatively small set of clusters and then uses observable mass proxies, including X-ray temperatures and luminosities \citeeg{Mantz2010, Rykoff2014}, microwave observations \citeeg{Vanderlinde2010, Sehgal2011}, optical richness \citeeg{Abell1958, Rykoff2012} or weak lensing (WL; \eg\ \citealt{Rozo2010}) as examples, which provide a ``true'' mass.
 This directly calibrates the observable-mass relation which is then applied to a much larger sample.
@@
 	\includegraphics[width=\textwidth]{figures/oii_sdss.pdf} 
-	\caption[Illustration of the probability based \hbox{[\ion{O}{II}]} flux prediction method.]{\textit{Left}: CMD of 503,113 $z<0.2$ galaxies take from the SDSS DR12 where the shading scales with the density of points.
+	\caption{\textit{Left}: CMD of 503,113 $z<0.2$ galaxies take from the SDSS DR12 where the shading scales with the density of points.
 The two colored boxes show regions containing potential catalog galaxies.
@@
 Finally we summarize our findings in Section \ref{sec:summary}.
-A follow-up to this work Boada \etal\ (in Preparation) will investigate how the techniques developed here will work in practice.
+A follow-up to this work Boada \etal\ (in Preparation) will will apply these techniques to real data so as to empirically validate our conclusions.
 
@@
 
-The catalog information, used in this study, is broken into two large portions.
+The catalog information used in this study is broken into two large portions.
 The ``truth'' files contain the characteristics of each individual galaxy, such as right ascension (RA), declination (DEC), redshift ($z$), observed and rest-frame magnitudes, and many others.
 The ``halo'' files contain information for individual halos, to which many individual galaxies may belong.
-This includes five estimations of dynamical mass, RA, DEC, z, three dimensional velocity dispersion, and many others.
+This includes estimations of dynamical mass, RA, DEC, z, three dimensional velocity dispersion, and many others.
 However, the catalogs do not include information for emission lines.
@@
 We investigate the accuracy of the halo mass distribution by comparing the cumulative number density of halos above a mass ($M_{200c}$) threshold to the halo mass function (HMF) of \cite{Tinker2008}.
-We calculate the HMF at central redshifts of 0.1, 0.2, and 0.4 using {\sc HMFcalc} \citep{Murray2013} and compare it galaxies in a redshift window of $\Delta z\pm0.01$.
+We calculate the HMF at central redshifts of 0.1, 0.2, and 0.4 using {\sc HMFcalc} \citep{Murray2013} and compare it to galaxy clusters in a redshift window of $\Delta z\pm0.01$.
 We find a very good agreement between the predicted HMF and the observed distribution of clusters.
@@
 We use 503,113 objects classified as galaxies selected over $z = 0.02 - 0.2$ with {\sc zwarning $=0$} and a measured [\ion{O}{II}] line flux signal-to-noise of five.
-Figure~\ref{fig: oii sdss} shows the color-magnitude diagram (CMD) of $M_r$ and $g-r$ for these galaxies.
+Figure~\ref{fig: oii sdss} shows the color-magnitude diagram (CMD) of $M_r$ and $g-r$ for these galaxies, and the following SQL query selects the appropriate galaxies:
+\begin{lstlisting}[language=SQL]
+SELECT GAL.objid, 
+       GAL.u, 
+       GAL.err_u, 
+       GAL.g, 
+       GAl.err_g, 
+       GAL.r, 
+       GAL.err_r, 
+       GAL.i, 
+       GAl.err_i, 
+       GAL.z, 
+       GAL.err_z, 
+       g.oii_3726_flux, 
+       g.oii_3726_flux_err, 
+       s.z 
+FROM   galaxy AS GAL 
+       JOIN specobj AS s 
+         ON s.bestobjid = GAL.objid 
+       JOIN galspecline AS g 
+         ON g.specobjid = s.specobjid 
+WHERE  oii_3726_flux > oii_3726_flux_err * 5 
+       AND oii_3726_flux_err > 0 
+       AND s.class = 'GALAXY' 
+       AND s.zwarning = 0 
+\end{lstlisting}
 
@@
 The numbered boxes in the left panel show the bins corresponding to two example Buzzard galaxies ($M_r, g-r = -17.7,~0.49$ and $M_r, g-r = -21.4,~1.24$).
-The right panel shows the Log [\ion{O}{II}] luminosity distribution functions, $P($[\ion{O}{II}]$| M_r, g-r)$, which we use to assign [\ion{O}{II}] luminosity to each object.
+The right panel shows the [\ion{O}{II}] luminosity distribution functions, $P(\log\ L_{[\ion{O}{II}]}| M_r, g-r)$, which we use to assign [\ion{O}{II}] luminosity to each object.
 The luminosity is then converted into an [\ion{O}{II}] flux through
 \begin{equation}
-	F = \frac{L}{4\pi D_L}
+	F = \frac{L}{4\pi D_L^2}
 \end{equation}
@@
 In practice, the first moment is strongly subject to outliers, so we rely instead on the biweight location estimator \citep{Beers1990} through\footnote{Implemented as part of the {\sc astLib} Python library.
-See \hbox{http://astlib.sourceforge.net}}:
+See \hbox{\url{http://astlib.sourceforge.net}}}:
 \begin{equation}
@@
 	where $\sigma_{1D}$, $\langle u \rangle$, and $\sigma_i$ is the LOSVD, the average radial velocity and the error (which we have assumed to be normally distributed) on the individual $v_i$ measurements respectively.
-To maximize Equation~\ref{eq: jointGaussian}, we employ a Monte Carlo Markov Chain (MCMC) sampler ({\sc emcee}\footnote{http://dan.iel.fm/emcee/current/}; \citealt{Foreman-Mackey2013}) which is based on affine-invariant ensemble sampler (see \citealt{Goodman2010} for details on affine-invariant samplers).
+To maximize Equation~\ref{eq: jointGaussian}, we employ a Monte Carlo Markov Chain (MCMC) sampler ({\sc emcee}\footnote{\url{http://dan.iel.fm/emcee/current/}}; \citealt{Foreman-Mackey2013}) which is based on affine-invariant ensemble sampler (see \citealt{Goodman2010} for details on affine-invariant samplers).
 We draw twenty thousand samples from the posterior probability distribution using simple priors, $\langle\mu\rangle$ lies between the maximum and minimum LOSV and $0< \sigma_{1D} < 1400$ \kms, for each cluster.
@@
 
-A growing body of work suggests that there is a significant difference in the observed LOSVD depending on the velocity tracers used.
-Specifically, while there is little difference between using galaxies and their host DM subhalos, there is a significant over estimation of the LOSVD when using galaxies/subhalos compared to DM particles \citep{Munari2013}.
+Recent work suggests that there is a significant difference in the observed LOSVD depending on the velocity tracers used \citep{Munari2013}.
+Specifically, while there is little difference between using galaxies and their host DM subhalos, there is a significant over estimation of the LOSVD when using galaxies/subhalos compared to DM particles.
 We follow other works \citeeg{Kirk2015, Sifon2015a} using the scaling relation, given in Equation~\ref{eq:power law} to facilitate comparisons with other observational studies, which rely on galaxies as tracers.
@@
 \subsubsection{Probability Based}\label{sec:probability method}
-For internal consistency between this and the ML based method we use 70\% of the clusters to establish a conditional probability density of $P(M_{200c} | \vec{x})$ which we then use as the cluster mass probability density for the remaining clusters with similar features.
+For internal consistency between this and the ML based method we use 70\% of the clusters to establish a conditional probability density of $P(\log\ M_{200c} | \vec{x})$ which we then use as the cluster mass probability density for the remaining clusters with similar features.
 In this way we, ``train'' the probability density using the existing simulated data, and apply it to the ``test'' sample (the remaining 30\% of the data not used as the training set).
@@
 \emph{Left}: The two dimensional posterior probability distribution of LOSVD and redshift used to determine the correct cluster mass.
-The pink and green rectangles show the locations of two example galaxies used to create the conditional probability distribution of the mass, $P(M_{200c}|z, \mathrm{Log}\, \sigma)$.
+The pink and green rectangles show the locations of two example galaxy clusters used to create the conditional probability distribution of the mass, $P(\log\ M_{200c}|z, \mathrm{Log}\, \sigma)$.
 \emph{Right}: The conditional probability distribution of the cluster mass for the two example galaxies.
@@
 The left panel shows the two dimensional (joint probability) projections of the posterior probability distributions of the feature training data.
-The conditional probability of the cluster mass $P(M_{200c}|\vec{x}= \{ x_1,x_2,...\})$ (shown in the right panel) is determined by selecting a region in the joint probability distribution.
-For example, using the LOSVD and redshift features we create $P(M_{200c}|\vec{x})$ for two test galaxies, shown by the green and pink boxes in the left panel of Figure~\ref{fig: probability corner}.
+The conditional probability of the cluster mass $P(\log\ M_{200c}|\vec{x}= \{ x_1,x_2,...\})$ (shown in the right panel) is determined by selecting a region in the joint probability distribution.
+For example, using the LOSVD and redshift features we create $P(\log\ M_{200c}|\vec{x})$ for two test galaxies, shown by the green and pink boxes in the left panel of Figure~\ref{fig: probability corner}.
 These example galaxies have features $\vec{x} = \{\sigma=200\, \kms,z=0.16\}$ and $\vec{x} = \{\sigma=400\, \kms,z=0.36\}$.
@@
 For the clusters making up the \emph{test} sample the mass is unknown (it is what we are trying to predict) but the other features are known.
-To determine the mass probability distribution of a test cluster, $P(M_{200c})$, we combine the conditional probability distribution, $P(M_{200c}|\vec{x})$, created previously with the probability distribution of $\sigma$, the LOSVD, through Equation~\ref{eq: Pm}.
+To determine the mass probability distribution of a test cluster, $P(\log\ M_{200c})$, we combine the conditional probability distribution, $P(\log\ M_{200c}|\vec{x})$, created previously with the probability distribution of $\sigma$, the LOSVD, through Equation~\ref{eq: Pm}.
 \begin{equation}\label{eq: Pm}
-	P(M_{200c}) = \int P(M_{200c}|\vec{x})\ P(\sigma)\ d\sigma\ P(z)\ dz
+	P(\log\ M_{200c}) = \int P(\log\ M_{200c}|\vec{x})\ P(\log\ \sigma)\ d\log\ \sigma\ P(z)\ dz
 \end{equation}
@@
 \begin{equation}\label{eq: expected mass}
-	M_{pred}= \int M_{200c}\ P(M_{200c})\ dM_{200c}
+	\log\ M_{pred}= \int \log\ M_{200c}\ P(\log\ M_{200c})\ d\log\ M_{200c}
 \end{equation}
@@
 \begin{equation}\label{eq: variance}
-	\mathrm{Var} = \int (M_{200c} - M_{pred})^2\ P(M_{200c})\ dM_{200c}
-\end{equation}
-or by drawing many samples from $P(M_{200c})$ and calculating the values at the 16th and 84th percentile.
+	\mathrm{Var} = \int (\log\ M_{200c} - \log\ M_{pred})^2\ P(\log\ M_{200c})\ d\log\ M_{200c}
+\end{equation}
+or by drawing many samples from $P(\log\ M_{200c})$ and calculating the values at the 16th and 84th percentile.
 In practice we find that both methods produce similar results for a large number of trials.
@@
 The cluster mass estimation in this section relies on a ML technique known as an ensemble method, where many estimators are created by a single learning method with the goal of improved generalization and robustness compared to a single estimation.
-Ensemble methods \citeeg{Caruana2006} come in two general flavors.
+Ensemble methods \hbox{\citeeg{Caruana2006}} come in two general flavors.
 Averaging methods average (hence the name) the estimators to produce a single prediction.
@@
 We recover 14,189 clusters with Targeted observations and 1,760 clusters with Survey observations, where we require a detection of $N_{obs} >=5$ galaxies for a cluster to be detected.
+It is worth noting that we are using galaxies which are a priori known to belong to each cluster.
+This is not possible to do when analyzing real data, but this will be investigated in a follow up paper, Boada \etal\ (in Preparation).
+
 Figure \ref{fig: recovery} shows the recovery fraction of member galaxies, the number of observed galaxies divided by the number of actual galaxies ($N_{obs}/N_{True}$), as a function of both redshift and cluster mass.
@@
 The bottom row of panels shows the fractional error (Equation~\ref{eq: fractional error}) also as a function of true cluster mass.
-The solid black line shows the 1:1 relation, in both panels, between $M_{200c}$ and $M_{pred}$.
+The solid black line shows the 1:1 relation.
 The orange, dash-dotted line is the median predicted mass for perfect observations.
@@
 One could imagine that the specific values of the cosmological parameters in the training sample could bias the ML results when applied to data (real or simulated) created from an unknown true set of cosmological parameters.
+In addition, each simulation realizes galaxy populations in slightly different ways.
+The details of the simulation affect which galaxies are observed or not, and thus influences our ability to recover the desired cluster properties.
 
@@
 
-We repeat our analysis using cluster halo and galaxy catalogs from the Millennium simulation obtained via querying the Millennium online database\footnote{http://gavo.mpa-garching.mpg.de/Millennium/} \citep{Lemson2006}.
+We repeat our analysis using cluster halo and galaxy catalogs from the Millennium simulation obtained via querying the Millennium online database\footnote{\url{http://gavo.mpa-garching.mpg.de/Millennium/}} \citep{Lemson2006}.
 The Millennium simulation tracks $2160^3$ dark matter particles of $8.6\times 10^8 ~h^{-1}$ \Msol\ inside a comoving 500 $(h^{-1} \mathrm{Mpc})^3$ box from $z=127$ to 0.
@@
 Galaxy clusters trace the peaks in the universal matter density, often referred to as the power spectrum of matter density fluctuations or the matter power spectrum.
-This enables them to be sensitive probes of $\Omega_m$, the total mass ($\Omega_b + \Omega_c$) density, and $\sigma_8h^{-1}$, the normalization of the power spectrum.
+This enables them to be sensitive probes of $\Omega_m$, the total mass ($\Omega_b + \Omega_c$) density, and $\sigma_8$, the normalization of the power spectrum.
 We constrain these parameters by the comparison of the number density of observed clusters to that predicted in cosmological models.
-Although, in reality, one measures $\sigma_8h^{-1}\Omega_m^q$, where the value of $q$ depends on the masses and redshifts of the halos considered.
+Although, in reality, one measures $\sigma_8\Omega_m^q$, where the value of $q$ depends on the masses and redshifts of the halos considered.
 
@@
 
-To estimate the error associated with a measurement of $\sigma_8h^{-1}$ (which \citetalias{Weinberg2013} refer to as $\sigma_{11,abs}$), \citetalias{Weinberg2013} consider two sources of uncertainty, the systematic uncertainties in cluster mass calibration and the statistical uncertainty in the observed number density of clusters.
+To estimate the error associated with a measurement of $\sigma_8$ (which \citetalias{Weinberg2013} refer to as $\sigma_{11,abs}$), \citetalias{Weinberg2013} consider two sources of uncertainty, the systematic uncertainties in cluster mass calibration and the statistical uncertainty in the observed number density of clusters.
 The authors combine these two uncertainties though (their Eq.
@@
 \begin{equation}
-\Delta \ln \sigma_8h^{-1}(z) \approx q(z)\times 
+\Delta \ln \sigma_8(z) \approx q(z)\times 
         \max\left[ \Delta \ln M, \alpha(z)^{-1} \Delta \ln N \right].
@@
 \end{equation}
-where $q$ is the degeneracy exponent between $\sigma_8h^{-1}$ and $\Omega_m$, $\Delta \ln M$ is the mass scale uncertainty, $\Delta \ln N$ is the cluster statistical uncertainty, and $\alpha$ is slope of the cumulative HMF.
+where $q$ is the degeneracy exponent between $\sigma_8$ and $\Omega_m$, $\Delta \ln M$ is the mass scale uncertainty, $\Delta \ln N$ is the cluster statistical uncertainty, and $\alpha$ is slope of the cumulative HMF.
 Using the \cite{Tinker2008} HMF at $z\sim0.2$ and a limiting cluster mass of $10^{14}$ \Msol, \citetalias{Weinberg2013} estimate $q\sim0.4$, $\alpha\sim3$, and find that any cluster survey with more than 10-20 clusters is dominated by the uncertainty in the overall mass scale.
 
-For a survey such as HETDEX, we can estimate the constraints on $\sigma_8h^{-1}$ using Equation \ref{eq:sigElapprox}.
+For a survey such as HETDEX, we can estimate the constraints on $\sigma_8$ using Equation \ref{eq:sigElapprox}.
 If we consider clusters with masses above $10^{14}$ \Msol\ and with Perfect knowledge observations, the lowest mass scale uncertainty (given in Table~\ref{tbl:mass scatter}) is $\Delta_{log_{10}}M \sim 0.075$ dex or about 20\%.
-This gives a uncertainty on $\sigma_8h^{-1}$ of 7\%.
-For clusters above $10^{14}$ \Msol, Survey observations constrain the masses to about 51\% which, in turn, constrains $\sigma_8h^{-1}$ to 20\%.
-
-Because of the simplifying assumptions, and the superior quality of the data (no contamination, signal-to-noise issues, etc.), realistic expectations for HETDEX is to directly constrain $\sigma_8h^{-1}$ is not yet competitive with other methods (\eg, CMB, WL, X-ray).
-For example, \cite{DeHaan2016} constrain $\sigma_8h^{-1}$ to $\sim5$\% using a sample of 337 SZE detected clusters from the SPT-SZE survey.
-For the $\sim1500$ clusters detected with Survey observations to constrain $\sigma_8h^{-1}$ and to be dominated by cluster statistics alone ($\Delta \ln N \sim N^{-1/2}$), the absolute cluster calibration would need to be better than 2.5\%.
+This gives a uncertainty on $\sigma_8$ of 7\%.
+For clusters above $10^{14}$ \Msol, Survey observations constrain the masses to about 51\% which, in turn, constrains $\sigma_8$ to 20\%.
+
+Because of the simplifying assumptions, and the superior quality of the data (no contamination, signal-to-noise issues, etc.), realistic expectations for HETDEX is to directly constrain $\sigma_8$ is not yet competitive with other methods (\eg, CMB, WL, X-ray).
+For example, \cite{DeHaan2016} constrain $\sigma_8$ to $\sim5$\% using a sample of 337 SZE detected clusters from the SPT-SZE survey.
+For the $\sim1500$ clusters detected with Survey observations to constrain $\sigma_8$ and to be dominated by cluster statistics alone ($\Delta \ln N \sim N^{-1/2}$), the absolute cluster calibration would need to be better than 2.5\%.
 For a fully Targeted survey, about 14,000 clusters, this cluster mass calibration uncertainty reduces to $>1\%$.
-Nevertheless, while analysis of HETDEX clusters may not provide the most accurate constraint on $\sigma_8h^{-1}$, it will provide important systematics checks on other studies and will ultimately improve the measurements of $\sigma_8h^{-1}$.
+Nevertheless, while analysis of HETDEX clusters may not provide the most accurate constraint on $\sigma_8$, it will provide important systematics checks on other studies and will ultimately improve the measurements of $\sigma_8$.
 
@@
 
-One of the main goals of this study is to understand how well HETDEX will be able to measure the scatter in the richness-mass relationship.
-To this end, we choose to impose a richness-mass relation onto the clusters in the Buzzard catalogs.
-The true richness-mass relation could depend strongly on the number and types of environmental effects, because such effects have a strong impact on the number and types of galaxies observed in clusters \citeeg{Gunn1972,Balogh2000,White2010}.
+One of the main goals of this study is to understand how well HETDEX will be able to measure the scatter in the richness--mass relationship.
+To this end, we choose to impose a richness--mass relation onto the clusters in the Buzzard catalogs.
+The true richness--mass relation could depend strongly on the number and types of environmental effects, because such effects have a strong impact on the number and types of galaxies observed in clusters \citeeg{Gunn1972,Balogh2000,White2010}.
 Any environmental effects included in Buzzard could potentially impact our observed richness.
-The imposition of an empirical richness-mass relation ensures the richness values correspond correctly to the clusters in our sample, could provide direct observational tests in the future.
-
-We generate richnesses based on the true cluster masses, and for testing, we assume two versions of the richness-mass relationship.
+The imposition of an empirical richness--mass relation ensures the richness values correspond correctly to the clusters in our sample, could provide direct observational tests in the future.
+
+We generate richnesses based on the true cluster masses, and for testing, we assume two versions of the richness--mass relationship.
 \cite{Farahi2016} base the relation on stacked velocity dispersions, and \cite{Simet2016} use weak lensing measurements to construct their relation.
@@
 We do recover the expected scatter, often, to well within 0.01 dex.
-We repeat the process with both assumed richness-mass relationships and recover the expected scatter in both instances.
+We repeat the process with both assumed richness--mass relationships and recover the expected scatter in both instances.
 
 We use the lambda values generated above in combination with the $\mathrm{M}_{\sigma,z,N_{gal}}$ predicted cluster mass which have been bias corrected using the values in Table~\ref{tbl:mass bias} and denoted $\mathrm{M_{pred,corr}}$.
-The use of biased cluster mass predictions inhibits our ability to accurately recover any scatter in richness-mass relationship, and is discussed further below.
-
-Primarily, we are interested in the intrinsic scatter of the richness-mass relationship.
+The use of biased cluster mass predictions inhibits our ability to accurately recover any scatter in richness--mass relationship, and is discussed further below.
+
+Primarily, we are interested in the intrinsic scatter of the richness--mass relationship.
 This is because HETDEX is uniquely situated to estimate the scatter, whereas studies relying on stacked data \citeeg{Farahi2016,Simet2016} lose that information.
 We begin by attempting to constrain the absolute mass scale, and as part of our fitting process, we estimate the overall scatter in the relationship.
-In order to understand how HETDEX will constrain the absolute mass scale, we find the best fitting relation to our richness-mass data.
+In order to understand how HETDEX will constrain the absolute mass scale, we find the best fitting relation to our richness--mass data.
 To generate the best fitting lines, we follow the general procedure of \cite{Hogg2010}, by defining an objective function and then minimizing the loss.
@@
 Other observational studies \citeeg{Saro2015} which have lower limits on $\lambda$, so we exclude anything less than $\lambda=10$.
-For a richness-mass relation with an intrinsic scatter of $\langle \sigma_{M|\lambda} \rangle = 0.25$ dex, we find a best-fitting relation for the Targeted observations as
+For a richness--mass relation with an intrinsic scatter of $\langle \sigma_{M|\lambda} \rangle = 0.25$ dex, we find a best-fitting relation for the Targeted observations as
 \begin{equation}
-	\mathrm{Log}\ M_{200c}/\Msol = 12.46\pm0.02 + 1.07\pm0.02\ \mathrm{Log}\ \lambda
+	\log\ M_{200c}/\Msol = 12.46\pm0.02 + 1.07\pm0.02\ \log\ \lambda
 \end{equation} 
@@
 \begin{equation}
-	\mathrm{Log}\ M_{200c}/\Msol = 12.64\pm0.05 + 0.98\pm0.03\ \mathrm{Log}\ \lambda
+	\log\ M_{200c}/\Msol = 12.64\pm0.05 + 0.98\pm0.03\ \log\ \lambda
 \end{equation} 
@@
 We also estimate the intrinsic scatter.
-For observations with a richness-mass relation intrinsic scatter of $\langle \sigma_{M|\lambda} \rangle = 0.25$ dex, we recover $\langle \sigma_{M|\lambda} \rangle = 0.236\pm0.003$ dex and $\langle \sigma_{M|\lambda} \rangle = 0.257\pm0.007$ dex for the Targeted and Survey observations respectively.
+For observations with a richness--mass relation intrinsic scatter of $\langle \sigma_{M|\lambda} \rangle = 0.25$ dex, we recover $\langle \sigma_{M|\lambda} \rangle = 0.236\pm0.003$ dex and $\langle \sigma_{M|\lambda} \rangle = 0.257\pm0.007$ dex for the Targeted and Survey observations respectively.
 
@@
 Using a traditional power law-based, velocity dispersion, scaling relation along with more advanced probability and machine learning (ML) techniques, we estimate the total mass for each cluster.
-We discuss each cluster mass estimate's precision, and discuss the ability of HETDEX to constrain the cosmological parameter $\sigma_8 h^{-1}$ based on those predicted cluster masses.
+We discuss each cluster mass estimate's precision, and discuss the ability of HETDEX to constrain the cosmological parameter $\sigma_8$ based on those predicted cluster masses.
 In addition, we comment on how HETDEX may improve current and future photometric large-area sky surveys' cluster mass estimates derived from optical richness.
@@
 	\item After considering the observational limits of HETDEX, we find 14,189 clusters with at least five cluster members in the HETDEX survey volume.
-Of those, 1,760 clusters are detected with HETDEX-like survey observations.
+Of those, 1,760 clusters are detected with HETDEX-like survey observations, with the majority of failed recoveries due to the HETDEX tiling pattern.
 The number of cluster members recovered with Survey observations is almost exactly 4.5 times fewer than a fully Targeted survey, across both a wide range of redshifts and cluster masses.
@@
 
-	\item The $\sim51\%$ cluster mass accuracy of Survey observations places approximately a 20\% constraint on $\sigma_8 h^{-1}$.
+	\item The $\sim51\%$ cluster mass accuracy of Survey observations places approximately a 20\% constraint on $\sigma_8$.
 This can be tightened to approximately 12\% with follow-up targeted observations.
-Most importantly, the observations from HETDEX will provide systematics checks on other studies, ultimately improving all future measurements of $\sigma_8 h^{-1}$
-
-	\item HETDEX will be able to place important, independent constraints on the amount of scatter in the optical richness-mass relationship.
+Most importantly, the observations from HETDEX will provide systematics checks on other studies, ultimately improving all future measurements of $\sigma_8$
+
+	\item HETDEX will be able to place important, independent constraints on the amount of scatter in the optical richness--mass relationship.
 It will to a less extent constrain the overall normalization of the relation.
@@
 It is the author's hope that this work may be useful to others when conducting their own research.
-Because this work relies heavily on (often) complex data analysis, and in order to promote transparency and reproducible science, we provide all of the code used to conduct this study at https://github.com/boada/HETDEXCluster.
+Because this work relies heavily on (often) complex data analysis, and in order to promote transparency and reproducible science, we provide all of the code used to conduct this study at \url{https://github.com/boada/HETDEXCluster}.
 Regrettably, large file size prevents including the source data with the analysis routines.
@@
 Department of Energy, the National Aeronautics and Space Administration, the Japanese Monbukagakusho, the Max Planck Society, and the Higher Education Funding Council for England.
-The SDSS Web Site is http://www.sdss.org/.
+The SDSS Web Site is \url{http://www.sdss.org/}.
 
@@
 For example, the HETDEX observations overlap with the DES area and SDSS Stripe 82 which provides a wealth of external data.
-Using preexisting datasets, the observations from HETDEX, or through dedicated follow-up spectroscopic observations, I will be able to measure the absolute mass scale of the richness estimator and measure the scatter of the richness-mass relation, $\sigma_{M|\lambda}$.
+Using preexisting datasets, the observations from HETDEX, or through dedicated follow-up spectroscopic observations, I will be able to measure the absolute mass scale of the richness estimator and measure the scatter of the richness--mass relation, $\sigma_{M|\lambda}$.
 An accurate measure of this scatter can lead to a decrease on the error bar on cosmological measures ($\sigma_8$ and $\Omega_M$) by as much as 50\% \citep{Rozo2010}.
-An absolute calibration of the richness-mass relation will provide a much needed tool for future imaging surveys which will identify clusters to $z=1$ and beyond.
+An absolute calibration of the richness--mass relation will provide a much needed tool for future imaging surveys which will identify clusters to $z=1$ and beyond.
 

### 2016-09-26 paper1.tex
update paper
new figures and some tweaked text

@@
 WL estimates are, in principle, correct in the mean, but they suffer from signal-to-noise requirements, limiting their usefulness in low mass clusters (where the lensing signal is particularly weak), and potentially suffer from line-of-sight effects as WL is sensitive to all mass along the line-of-sight.
-Virial mass estimators which determine the cluster mass based on the motions of the member galaxies \citeeg{Ruel2014, Sifon2015} are promising in that it is a direct measurement of the depth of clusters potential well, but suffer from systematics due to cluster formation physics which disrupts the velocity field.
+Virial mass estimators which determine the cluster mass based on the motions of the member galaxies \citeeg{Ruel2014, Sifon2015} are promising in that it is a direct measurement of the depth of clusters potential well, but suffer from systematics due to cluster formation physics which disrupts the velocity field, such as cluster mergers \citeeg{Evrard2008} and tidal stripping \citeeg{Faltenbacher2006}.
 
@@
 \includegraphics[width=\columnwidth]{figures/pointings.pdf} 
-	\caption[HETDEX pointing strategy.]{Representative observation tiling scheme for the HETDEX $16' \times 16'$ pointings.
-Each turquoise square represents the position of a single VIRUS IFU, and the dashed octagons approximate the size of a single observation.
+	\caption[HETDEX pointing strategy.]{\emph{Top:} Representative observation tiling scheme for the HETDEX $16' \times 16'$ pointings over a small region of the sky.
+\emph{Bottom:} The simplified tiling pattern used in this study.
+In both schemes, the dashed octagons approximate the size of a single observation.
+Each observation consists of the 78 VIRUS IFUs, represented by the turquoise squares in the bottom panel.
 Inside each IFU HETDEX will achieve near complete coverage through three dithers.
@@
 Galaxies which lie between the IFUs are missed, as well as the galaxies which lie between the pointings, as there is no overlap between one pointing and the next.
+We use a pointing pattern which differs slightly from the expected final HETDEX observing pattern.
+See Figure~\ref{fig: ifu layout} for an illustration of the difference.
 To cover the 398.49 \degsq\ field of the Buzzard catalog we require 5370 pointings where 0.015 \degsq\ of each pointing is covered by an IFU.
-The total area of the sky covered by an IFU is 80.80 \degsq\ which gives a filling factor of 1/4.65, slightly decreased from the expected filling factor of 1/4.5.
+The total area of the sky covered by an IFU is 80.80 \degsq\ which gives a filling factor of 1/4.65, slightly (about 3\%) decreased from the expected filling factor of 1/4.5.
 
@@
 \section{Recovery of Parameters}\label{sec:recovery}
+In the following sections, we assume that we know a priori which galaxies belong to each individual cluster.
+So while our observations may include many field galaxies which are not belonging to the cluster in question, we exclude those galaxies during the analysis of the cluster parameters.
+Cluster membership is a critical issue which must be addressed when utilizing real observations.
+To that end, we assay a small sample of real galaxy clusters in a follow up work (Boada \etal\ in Preparation).
+
 \subsection{Cluster Redshift}
@@
 In simple terms, the cluster redshift is the mean of the redshifts of all galaxies associated with the cluster, where the mean is the first moment of the velocity (redshift) distribution function $P(z)$.
-In practice, the first moment is strongly subject to outliers, so we rely instead on the biweight location estimator \citep{Beers1990} through\footnote{Implemented as part of the {\sc astLib} Python library.
+In practice, the first moment is strongly subject to outliers, so we rely instead on the biweight location estimator \citep{Beers1990} through\footnote{Implemented as part of the {\sc astLib} Python library \citep{astlib}.
 See \hbox{\url{http://astlib.sourceforge.net}}}:
@@
 \begin{equation}\label{eq: Pm}
-	P(\log\ M_{200c}) = \int P(\log\ M_{200c}|\vec{x})\ P(\log\ \sigma)\ d\log\ \sigma\ P(z)\ dz
+	P(\log\ M_{200c}) = \int P(\log\ M_{200c}|\vec{x})\ P(\log\ \sigma, z)\ d\log\ \sigma\ dz
 \end{equation}
@@
 For example, \cite{DeHaan2016} constrain $\sigma_8$ to $\sim5$\% using a sample of 337 SZE detected clusters from the SPT-SZE survey.
-For the $\sim1500$ clusters detected with Survey observations to constrain $\sigma_8$ and to be dominated by cluster statistics alone ($\Delta \ln N \sim N^{-1/2}$), the absolute cluster calibration would need to be better than 2.5\%.
-For a fully Targeted survey, about 14,000 clusters, this cluster mass calibration uncertainty reduces to $>1\%$.
+
+We can use the rule-of-thumb calculations given in \citetalias{Weinberg2013} (Equations 154--155) to estimate the uncertainties required in both the absolute cluster mass scale and the intrinsic scatter to keep a cosmological analysis limited by cluster statistics.
+For the $\sim670$ clusters, with masses above $10^{14}$ \Msol, detected with Survey observations to constrain $\sigma_8$ and to be dominated by cluster statistics alone ($\Delta \ln N \sim N^{-1/2}$), the error on the  absolute cluster calibration would need to be better than 1.3\%.
+For a fully Targeted survey, about 1600 clusters with masses above $10^{14}$ \Msol, this cluster mass calibration uncertainty reduces to $<1\%$.
+Similarly, the uncertainty associate with the scatter must be approximately 2.2\% and 1.4\% for Survey and Targeted observations respectively, after assuming an intrinsic scatter of 20\%.
+Comparing these estimates to the uncertainties associated with the Targeted and Survey observations, we are dominated by the uncertainty associated with the absolute cluster mass scale calibration.
 Nevertheless, while analysis of HETDEX clusters may not provide the most accurate constraint on $\sigma_8$, it will provide important systematics checks on other studies and will ultimately improve the measurements of $\sigma_8$.
@@
 We find that we are able to accurately recover an average intrinsic scatter of $0.2 <\langle \sigma_{M|\lambda} \rangle <0.3$ dex, finding $\langle \sigma_{M|\lambda} \rangle = 0.257\pm0.007$ at $\sigma_{true} = 0.25$ with Survey observations.
-This is very promising as other observational studies have estimated the intrinsic scatter of real clusters to be $\sim0.25$ dex \citeeg{Rozo2014, Rozo2015}.
 As the intrinsic scatter increases or decreases, we fail to recover the scatter as accurately.
@@
 For the richness range $10 \leq \lambda < 130$ the intrinsic scatter in between the $\mathrm{M_{pred,corr}}$ predicted cluster masses and the true cluster mass (the basis of our richnesses) is $\sim0.15$ dex for Targeted observations and $\sim0.20$ dex for Survey observations.
-This forms an effective floor on the amount of scatter we are able to recover from our fitting process.
 As we reduce the overall scatter in our cluster mass recovery, this floor will lower.
@@
 Here, we present detailed simulations of the upcoming HETDEX survey's applicability to the detection and total mass measurement of galaxy clusters based on emission line and continuum redshifts for galaxies at z < 0.5.
-Using mock galaxy catalogs and HETDEX-like observational strategies and limits, we observe our simulated sky, estimate the number of clusters observed, and derive basic cluster parameters, redshift, line-of-sight velocity dispersion (LOSVD).
+Using mock galaxy catalogs and simple HETDEX-like observational strategies and limits, we observe our simulated sky, estimate the number of clusters observed, and derive basic cluster parameters, redshift, line-of-sight velocity dispersion (LOSVD).
 Using a traditional power law-based, velocity dispersion, scaling relation along with more advanced probability and machine learning (ML) techniques, we estimate the total mass for each cluster.

### 2016-11-28 paper1.tex
update author list

@@
 \author[S. Boada et al.]
-{\parbox{\textwidth}{Steven Boada,$^{1}$\thanks{E-mail: boada@physics.tamu.edu}
-C.~Papovich,$^{1}$
-R.~Wechsler,$^{2,3}$
-T. S.~Li,$^{1}$
-K.~Gebhardt,$^{5}$
-J.~DeRose,$^{2}$
-E.~Rozo,$^{2,4}$
-E. S.~Rykoff$^{2}$}\vspace{0.4cm}\
+{\parbox{\textwidth}{Steven~Boada,$^{1,2}$\thanks{E-mail: boada@physics.rutgers.edu}
+C.~Papovich,$^{2}$
+R.~Wechsler,$^{3,4}$
+T.~S.~Li,$^{7}$
+K.~Gebhardt,$^{6}$
+J.~DeRose,$^{3}$
+E.~Rozo,$^{3,5}$
+E. S.~Rykoff$^{3}$}\vspace{0.4cm}\
 \\
-\parbox{\textwidth}{$^{1}$George P.\ and Cynthia Woods Mitchell Institute for Fundamental Physics and Astronomy, and Department of Physics and Astronomy, Texas A\&M University, College Station, TX, 77843-4242, USA\\
-$^{2}$Kavli Institute for Particle Astrophysics and Cosmology, Department of Physics, Stanford University, Stanford, CA 94305, USA\\
-$^{3}$Department of Particle Physics and Astrophysics, SLAC National Accelerator Laboratory, Menlo Park, CA 94025, USA\\
-$^{4}$Department of Physics, University of Arizona, Tucson, AZ 85721, USA\\
-$^{5}$Department of Astronomy, The University of Texas at Austin, Austin, TX 78712, USA}}
+\parbox{\textwidth}{$^{1}$Physics and Astronomy Department, Rutgers University, Piscataway, NJ 08854-8019, USA\\
+$^{2}$George P.\ and Cynthia Woods Mitchell Institute for Fundamental Physics and Astronomy, and Department of Physics and Astronomy, Texas A\&M University, College Station, TX, 77843-4242, USA\\
+$^{3}$Kavli Institute for Particle Astrophysics and Cosmology, Department of Physics, Stanford University, Stanford, CA 94305, USA\\
+$^{4}$Department of Particle Physics and Astrophysics, SLAC National Accelerator Laboratory, Menlo Park, CA 94025, USA\\
+$^{5}$Department of Physics, University of Arizona, Tucson, AZ 85721, USA\\
+$^{6}$Department of Astronomy, The University of Texas at Austin, Austin, TX 78712, USA\\
+$^{7}$Fermi National Accelerator Laboratory, P. O. Box 500, Batavia, IL 60510, USA}}
 

### 2016-11-28 paper1.tex
final changes for co-authors

@@
 R.~Wechsler,$^{3,4}$
+J.~DeRose,$^{3}$
 T.~S.~Li,$^{7}$
 K.~Gebhardt,$^{6}$
-J.~DeRose,$^{3}$
+G.~Hill,$^{6}$
 E.~Rozo,$^{3,5}$
-E. S.~Rykoff$^{3}$}\vspace{0.4cm}\
+E. S.~Rykoff~$^{3}$}\vspace{0.4cm}\
 \\

### 2017-01-11 paper1.tex
first set of casey comments
more to come

@@
 % out the following line
-\usepackage{newtxtext,newtxmath}
+%\usepackage{newtxtext,newtxmath}
 \usepackage{times}
@@
 We use the SDSS DR12 \citep{Alam2015} catalogs to assign [\ion{O}{II}] emission line strengths to the galaxies in the Buzzard catalog.
-We use 503,113 objects classified as galaxies selected over $z = 0.02 - 0.2$ with {\sc zwarning $=0$} and a measured [\ion{O}{II}] line flux signal-to-noise of five.
+We use 503,113 objects classified as galaxies selected over $z = 0.02 - 0.2$ with {\sc zwarning $=0$} and a measured [\ion{O}{II}] line flux signal-to-noise of at least five.
 Figure~\ref{fig: oii sdss} shows the color-magnitude diagram (CMD) of $M_r$ and $g-r$ for these galaxies, and the following SQL query selects the appropriate galaxies:
@@
 In both schemes, the dashed octagons approximate the size of a single observation.
-Each observation consists of the 78 VIRUS IFUs, represented by the turquoise squares in the bottom panel.
+Each observation consists of the 78 VIRUS IFUs, represented by the turquoise squares in the bottom panel shown for one of the HETDEX pointings.
 Inside each IFU HETDEX will achieve near complete coverage through three dithers.
@@
 The spectral coverage allows for the detection of [\ion{O}{II}] ($\lambda\lambda 3727,3729$) emitters to $z\sim 0.5$ and Ca H ($\lambda 3968.5$) and K ($\lambda 3933.7$) absorption features to $z\sim 0.4$.
-The $10 \sigma$ detection threshold for spectral features will be $3.5\times10^{-17}$ \ergscm\ at 5000 \AAA, or equivalently, $g = 21.9$ mag for continuum objects.
+The $10 \sigma$ detection threshold for emission spectral features will be $3.5\times10^{-17}$ \ergscm\ at 5000 \AAA, or equivalently, $g = 21.9$ mag for continuum objects.
 
@@
 In practice, this is achieved by three dither positions at each pointing.
-Galaxies which lie between the IFUs are missed, as well as the galaxies which lie between the pointings, as there is no overlap between one pointing and the next.
+Because of the 1:3 fill factor, many galaxies will not receive spectroscopic coverage, including galaxies that lie between IFUs within a pointing, as well as galaxies between pointings.
 We use a pointing pattern which differs slightly from the expected final HETDEX observing pattern.
@@
 
-In this work we consider two separate observing strategies, Targeted and Survey.
-The Targeted observations use ``direct'' observations where each cluster is targeted individually, and every cluster member galaxy is assumed to be observed.
-The Survey observations mimic the HETDEX observation pattern across the sky, where no cluster is directly targeted and not all cluster member galaxies are observed.
+We measure cluster velocity dispersions using three different spectroscopic observing patterns.
+We consider three separate observing strategies, Targeted, Survey and Perfect.
+The Targeted observations use ``direct'' observations where each cluster is targeted individually with a 1:1 fill factor such that every cluster member galxay is assumed to be observed.
+The Survey observations mimic the HETDEX observation pattern across the sky, where no cluster is directly targeted.
+Each cluster is observed with the 1/4.5 fill factor, such that not all cluster member galaxies are observed.
 Both of these observations have HETDEX-like galaxy detection thresholds (described in the previous subsection), so while a galaxy may be observed, a redshift will only be measured if the galaxy satisfies the continuum brightness or emission line flux limits for the HETDEX survey.
 For comparison we also include a Perfect observation, in which we assume all galaxies in a field are observed and all redshifts measured.
-This provides a baseline where the cluster properties are calculated under the best possible conditions and against which we can compare the results of the ``Targeted'' and ``Survey'' observing strategies.
+This provides a baseline where the cluster velocity dispersion is calculated under the best possible conditions and against which we can compare the results of the ``Targeted'' and ``Survey'' observing strategies.
 
 \section{Recovery of Parameters}\label{sec:recovery}
-In the following sections, we assume that we know a priori which galaxies belong to each individual cluster.
-So while our observations may include many field galaxies which are not belonging to the cluster in question, we exclude those galaxies during the analysis of the cluster parameters.
+In the following sections, we assume that we know \textit{a priori} which galaxies belong to each individual cluster.
+So while our observations may include many field galaxies which do not belong to the cluster in question, we exclude those galaxies during the analysis of the cluster parameters.
 Cluster membership is a critical issue which must be addressed when utilizing real observations.
@@
 \end{equation}
-MAD is the median absolute deviation, also defined in \cite{Beers1990}, and $C$ is the a tuning constant.
-We choose $C=6$ (the suggested value) which balances computational speed and location accuracy.
+MAD is the median absolute deviation, also defined in \cite{Beers1990}, and $C$ is the a tuning constant. We choose $C=6$ (the \citealt{Beers1990} suggested value). 
 % Although this work assumes that we know each galaxy's redshift to infinite precision, in practice, we find a simple weighted mean provides a reliable estimate of $z_c$ when there are uncertainties on the individual galaxy redshifts.
@@
 \subsection{Line-of-Sight Velocity Dispersion}\label{sec: LOSVD}
-We calculate the LOSV to each galaxy, where
+We calculate the LOSV, $v_i$, to each galaxy, where
 \begin{equation}
-	\mathrm{LOSV} = c\frac{z - z_c}{1+z_c}
+	v_i = c\frac{z - z_c}{1+z_c}
 \end{equation}
@@
 In the following subsections we use two methods to predict the mass of a cluster based on other observables.
-Often the cluster mass is estimated based on a single observable, X-ray temperature, LOSVD, richness and others (see Section~\ref{sec: Introduction} for referenced examples).
+Often the cluster mass is estimated based on a single observable, \eg\ X-ray temperature, LOSVD, richness and others (see Section~\ref{sec: Introduction} for referenced examples).
 Here we combine many observables to attempt to correct the mass inferred solely from the velocity dispersion.
@@
 This prevents over-fitting.
-In the following subsections we take all of the observed clusters, our full sample, split them, and generate a \emph{training} and \emph{testing} set \citeeg{Ripley2007, Xu2013, Ntampaka2015, Ntampaka2015a, Acquaviva2016}.
+In the following subsections we take all of the simulated cluster observations, split them, and generate a \emph{training} and \emph{testing} set \citeeg{Ripley2007, Xu2013, Ntampaka2015, Ntampaka2015a, Acquaviva2016}.
 Traditionally, the training set is a set of data used to infer possibly predictive relationships.
 The test set of data is then used to assess the correctness of the predictive relationship.
-Our data is randomly split into 70\% training and 30\% testing.
+Our simulated observations are randomly split into 70\% training and 30\% testing.
 We follow the ML convention and refer to the individual clusters in each set as a ``sample'', and the parameters associated with the cluster ($z$, LOSVD, mass, etc.) as ``features''.
@@
 \emph{Left}: The two dimensional posterior probability distribution of LOSVD and redshift used to determine the correct cluster mass.
-The pink and green rectangles show the locations of two example galaxy clusters used to create the conditional probability distribution of the mass, $P(\log\ M_{200c}|z, \mathrm{Log}\, \sigma)$.
+The pink and green rectangles show the locations of two example galaxy, $\vec{x}_1 = \{z=0.16,\ \log~\sigma=2.4\}$ and $\vec{x}_2 = \{z=0.36,\ \log~\sigma=2.7\}$, clusters used to create the conditional probability distribution of the mass, $P(\log\ M_{200c}|z, \mathrm{Log}\, \sigma)$.
 \emph{Right}: The conditional probability distribution of the cluster mass for the two example galaxies.
@@
 We discuss the accuracy of cluster dynamical mass derived from both the power law scaling relation (see Equation \ref{eq:power law}) and through the probability and ML methods.
-We also compare the results from the Targeted and Survey observing strategies to the results of a ``Perfect'' survey, where the redshift of each galaxy, regardless of observational limits, in the cluster is known perfectly.
+We also benchmark the results from the Targeted and Survey observing strategies to the results of a ``Perfect'' survey, where the redshift of each galaxy, regardless of observational limits, in the cluster is known perfectly.
 
@@
 
-For the Targeted observations, shown in the left panel of Figure~\ref{fig: recovery}, the pattern of decreasing recovery fraction as a function of redshift (y-direction) is due to the observational limits imposed.
+For the Targeted observations, shown in the left panel of Figure~\ref{fig: recovery}, the decreasing recovery fraction as a function of redshift (y-direction) is due to the observational limits of the survey.
 Because the redshift success rate of HETDEX is limited by apparent magnitude, we expect to recover fewer galaxies at higher redshift, where the galaxies are often below our $5\sigma$ detection threshold.
-For example, we tested this by constructing an artificial HETDEX-like survey, limited by volume for all galaxies with $M_g < -11$.
+We tested this by constructing an artificial HETDEX-like survey, limited by volume for all galaxies with $M_g < -11$.
 In this case, our recovery fraction increases to $>70$\%, which shows that the flux limit is dominating the (lower) recovery of our flux-limited survey.
 
-For the recovery fraction as a function of true cluster mass (x-direction), we find a general decrease in the recovery fraction of member galaxies with increasing cluster mass.
+For the recovery fraction as a function of true cluster mass (x-direction), we find a general decrease in the number of member galaxies with increasing cluster mass.
 This  is entirely a result of the flux limited survey (see previous paragraph).
@@
 If we were to limit the Survey to $z<0.2$ we find the recovery fraction of clusters, across all masses, increases substantially, and we find a much more consistent detection fraction across all masses.
-However, doing so limits severely the number of clusters at masses greater than $10^{14}$ \Msol.
+However, doing so limits severely the number of clusters at masses greater than $10^{14}$ \Msol because of the limited survey volume.
 
@@
 The recovery fractions in Figure~\ref{fig: recovery} are an outcome of the magnitude limit and [\ion{O}{II}] line-flux limit of the survey.
-For Perfect observations, we would detect all members across all cluster masses and redshifts.
+For Perfect observations, we would measure redshifts for all members across all cluster masses and redshifts.
 Recovery fractions of clusters located a the low end of the redshift distribution will improve the most by follow-up targeted observations.
-But generally, the number of members observed (and subsequently more accurate cluster mass estimates) will benefit from follow-up observations regardless of the redshift.
-So follow-up observations should be tailored to the specific science goal.
+But generally, the number of members observed (and subsequently more accurate cluster mass estimates) will benefit from follow-up observations regardless of the redshift, which can be tailored for the specific scientific goal.
 
@@
 
-Because it represents the best possible scenario, the Perfect knowledge observations should serve as a baseline to compare the power law based, probability based and ML cluster mass recovery methods.
+Because it represents the best possible scenario, the Perfect knowledge observations should serve as a baseline against which to compare all other methods.
 And, while there are many possible metrics to evaluate performance, we compute two: the average bias (given in Table \ref{tbl:mass bias})
@@
 
-For the Targeted and Survey observations the power law predicted cluster masses give $\mu_{bias} =0.135\pm{0.003}$ dex, $\sigma_{bias} = 0.370\pm{0.002}$ and $\mu_{bias} =0.148\pm{0.008}$ dex, $\sigma_{bias} = 0.324\pm{0.006}$ , respectively.
+For the Targeted and Survey observations the power law predicted cluster masses give $\mu_{bias} =0.135\pm{0.003}$ dex, $\sigma_{bias} = 0.370\pm{0.002}$ dex and $\mu_{bias} =0.148\pm{0.008}$ dex, $\sigma_{bias} = 0.324\pm{0.006}$ dex, respectively.
 So for the clusters that we detect with Survey observations, we obtain similar levels of accuracy as to the Targeted observations, on the average.

### 2017-01-20 paper1.tex
a few more edits

@@
 	\caption[Recovery fractions for the Targeted and Survey observations.]{Recovery fractions ($N_{obs}/N_{True}$) of cluster member galaxies as a function of redshift and true cluster mass for the Targeted and Survey observing strategies.
-We have applied HETDEX-like observational limits on the cluster galaxy detection, and require at least five galaxies to be detected for a cluster to be recovered.
+The Targeted observations include HETDEX line and continuum flux limits and have a unity fill factor.
+The Survey observations again include HETDEX-like flux limits but a HETDEX-like fill factor, 1/4.5.
+We require at least five galaxies to be detected for a cluster to be recovered.
 The shading indicates the mean recovery fraction for clusters within each small bin of redshift and cluster mass.
@@
 \end{equation}
-where $M_{pred}$ is the predicted cluster mass and $M_{200c}$ is the true cluster mass. Higher values of $\epsilon$ indicate the predicted cluster mass exceeds the true cluster mass.
+where $M_{pred}$ is the predicted cluster mass and $M_{200c}$ is the true cluster mass. Positive values of $\epsilon$ indicate the predicted cluster mass exceeds the true cluster mass.
 
@@
 \caption[Mean scatter in cluster mass after bias correction for different bins of predicted cluster mass.]{Mean scatter (Eqn.~\ref{eqn: scatter}) in cluster mass after bias correction for different bins of predicted cluster mass.
-This table shows the scatter in the predicted cluster mass for the perfect (top section), Targeted (middle section), and Survey (bottom section) observations in different predicted mass bins.
-The different mass recovery strategies are given in the leftmost column.
-It can be used to understand how the predicted cluster mass differs from the true cluster masses.}
+This table shows the scatter in the predicted cluster mass for the Perfect (top section), Targeted (middle section), and Survey (bottom section) observations in different predicted mass bins.
+The different mass recovery methods are given in the leftmost column.
+It can be used to understand how the predicted cluster mass differs from the true cluster masses.
+Positive numbers indicate the predicted cluster mass is over estimated when compared to the true cluster mass.}
 \begin{tabular}{cccccccc} 
@@
 A few caveats apply to the numbers given in Table \ref{tbl:mass bias} and Table \ref{tbl:mass scatter}.
-While we provide corrections for cluster masses above $10^{15}$ \msol, they are estimated from only a handful of objects, and may not constitute a representative sample of clusters.
+While we provide corrections for cluster masses above $10^{15}$ \msol, they are estimated from only a handful of objects owing to the volume in the mock galaxy catalog.
+These may not constitute a representative sample of clusters due to the limited volume and range of possible features.
 This becomes particularly apparent for the probability methods with many features.
@@
 
-The method which produce the lowest scatter and bias depends on the mass of the cluster in question and the type of observations used.
+The method that produces the lowest scatter and bias depends on the mass of the cluster in question and the type of observations used.
 For the Targeted observations, the power law method outperforms all other methods, in terms of bias and scatter, for the highest mass clusters.
@@
 All simulations (including that used for Buzzard) use specific values for cosmological parameters.
-When using simulation data to train ML methods, we incorporate all of those assumptions into the learned feature associations.
+When using simulation data to train ML methods, our tests incorporate all of this specific cosmology into the learned feature associations.
 One could imagine that the specific values of the cosmological parameters in the training sample could bias the ML results when applied to data (real or simulated) created from an unknown true set of cosmological parameters.
@@
 The Millennium simulation adopts a flat cosmological model based of the values derived from the Two-degree Field Galaxy Redshift Survey \citep{Colless2001} and the first year data of the \emph{Wilkinson Microwave Anisotropy Probe} (WMAP; \citealt{Spergel2003}): $\Omega_\Lambda = 0.75$, $\Omega_M = 0.25$, $\sigma_8 = 0.9$, $n_s = 1$ and $H_0= 73$ \kms \mpc.
-As this cosmology differs dramatically from that assumed in the Buzzard catalogs (see Section~\ref{sec: Buzzard}, the clusters in Millennium provide a testing sample to understand how a training sample derived from Buzzard will impact the mass recovery on a wholly new dataset.
+As this cosmology differs dramatically from that assumed in the Buzzard catalogs (see Section~\ref{sec: Buzzard}, the clusters in Millennium provide an independent mock sample to understand how a training sample derived from Buzzard will impact the mass recovery on a wholly new dataset.
 

### 2017-01-23 paper1.tex
even more comments

@@
 
-One could use various simulations to attempt to calibrate this observable-mass relation \citeeg{Vanderlinde2010, Sehgal2011}.
+Previous studies have attempted to use various simulations to calibrate this observable-mass relation \citeeg{Vanderlinde2010, Sehgal2011}.
 However, the primary challenge to this method is the incomplete understanding of the baryonic physics which take place in galaxy cluster environments.
-While there have been (and continue to be) many improvements in the accuracy and power of simulations it is doubtful that in the coming years they will reach the accuracy level required where the observable--mass relation is dominated only by statistics \citep{Weinberg2013}.
+While there have been (and continue to be) many improvements in the accuracy and power of simulations it is doubtful that in the coming years they will reach the accuracy level required, due to limitations of the current models, where the observable--mass relation is dominated only by statistics \citep{Weinberg2013}.
 
 The second broad method is the direct calibration of cluster masses.
-This recipe has two distinct but not always independent tracks.
+This recipe has two distinct but often related tracks.
 The ``direct'' method uses observations of a relatively small set of clusters and then uses observable mass proxies, including X-ray temperatures and luminosities \citeeg{Mantz2010, Rykoff2014}, microwave observations \citeeg{Vanderlinde2010, Sehgal2011}, optical richness \citeeg{Abell1958, Rykoff2012} or weak lensing (WL; \eg\ \citealt{Rozo2010}) as examples, which provide a ``true'' mass.
@@
 WL estimates are, in principle, correct in the mean, but they suffer from signal-to-noise requirements, limiting their usefulness in low mass clusters (where the lensing signal is particularly weak), and potentially suffer from line-of-sight effects as WL is sensitive to all mass along the line-of-sight.
-Virial mass estimators which determine the cluster mass based on the motions of the member galaxies \citeeg{Ruel2014, Sifon2015} are promising in that it is a direct measurement of the depth of clusters potential well, but suffer from systematics due to cluster formation physics which disrupts the velocity field, such as cluster mergers \citeeg{Evrard2008} and tidal stripping \citeeg{Faltenbacher2006}.
+Virial mass estimators which determine the cluster mass based on the motions of member galaxies \citeeg{Ruel2014, Sifon2015} are promising in that it is a direct measurement of the depth of a cluster's potential well, but suffer from systematics due to cluster formation physics which disrupts the velocity field, such as cluster mergers \citeeg{Evrard2008} and tidal stripping \citeeg{Faltenbacher2006}.
+As all methods possess different strengths, systematics, and assumptions, it is important to compare multiple methods to understand how these affect the inferred cluster mass.
 
@@
 
-Large-area sky surveys, both on going and planned, are revolutionizing cluster cosmology using a large range of wavelengths.
+Large-area sky surveys, both on-going and planned, are revolutionizing cluster cosmology using a large range of wavelengths.
 The South Pole Telescope (SPT; \citealt{Carlstrom2011}) and the Atacama Cosmology Telescope (ACT; \citealt{Swetz2011}) are discovering many clusters through the SZE.
@@
 However, regardless of the discovery method used, spectroscopic follow-up is needed to further constrain $P(M|z,\vec{x})$.
-This follow-up becomes increasing important to help constrain the scatter in the mass estimates of other methods, and provides an additional, independent check of the observable-mass relationship used.
+This follow-up becomes increasingly important to help constrain the scatter in the mass estimates of other methods, and provides an additional, independent check of the observable-mass relationship used.
 But as the cluster dataset grows to many tens of thousands of clusters individual follow-up becomes increasingly impractical.
@@
 
-The Hobby Eberly Telescope Dark Energy eXperiment (HETDEX; \citealt{Hill2008}) will observe high-redshift large scale structures using cutting edge wide-field integral field unit (IFU) spectrographs.
-Designed to probe the evolution of the dark energy equation of state etched onto high redshift ($z>2$) galaxies by the Baryon Acoustic Oscillations (BAO) \citep{Eisenstein2005}, the survey will observe two fields for a total of 420 \degsq\ (300 \degsq, Spring field and 120 \degsq, Fall field).
-Tuned to find \lya\ emitting (LAE) galaxies at $1.9<z<3.5$, HETDEX expects to find 800,000 LAEs, and more than one million [\ion{O}{II}] emitting galaxies at $z<0.5$ masquerading as high-redshift galaxies \citep{Acquaviva2014}.
-
-While a large portion of the $\sim10^6$ interloping lower redshift galaxies will be field (not associated with a bound structure) galaxies, the large area covered by HETDEX is expected to contain as many as 50 Virgo-sized (halo mass $>10^{15}$ \msol) clusters at $z<0.5$.
-The near-complete spectroscopic coverage allows an unprecedentedly detailed look at a very large number of clusters ranging from group scales to the very massive.
-In addition to the recovery of accurate dynamical masses, detailed investigations of the of dynamical state of the clusters is possible.
-
-It is unclear how a blind spectroscopic survey with an IFU will effect the recovery of galaxy cluster dynamical properties.
-Unlike many previous large cluster surveys \citeeg{Milvang-Jensen2008, Robotham2011, Sifon2015} which use multi-object spectrographs, the Visible Integral-Field Replicable Unit Spectrograph (VIRUS; \citealt{Hill2012}) used by HETDEX samples the sky in a uniform but sparse way which could exclude member galaxies which would otherwise be included.
-Secondly, it is not straightforward to use spectroscopic redshifts predominately from emission-line galaxies to interpret the kinematic and dynamical states of the clusters.
+Here, we consider how a blind spectroscopic survey, such as the Hobby Eberly Telescope Dark Energy eXperiment (HETDEX; \citealt{Hill2008}) can be used to calibrate the observable--cluster mass relationship, and to further constrain the scatter in the calibration.
+We create and evaluate a HETDEX like selection ``function'' of galaxies over a similarly large portion of the sky and use well adopted techniques to recover the dynamical properties, such as velocity dispersion and cluster mass.
+In addition to standard techniques of cluster mass estimation, we investigate probability based and machine learning based approaches of cluster mass prediction.
+We compare these results to a series of targeted galaxy cluster observations, where each member galaxy is assumed to be observed.
+Each of these observations use realistic uncertainties from galaxy magnitude and line-flux limits.
+These strategies will better allow future work to predict the number and types of galaxy clusters which should be observed with VIRUS during both the HETDEX survey portion and through targeted follow up observations.
+
+We begin in Section \ref{sec:Data} by giving an overview of what data is used, how it is created, and how we make our ``observations.'' Details about the determination of cluster parameters, velocity dispersion, total mass, etc., are discussed in Section \ref{sec:recovery}.
+Next, we present the results of our study in Section \ref{sec:results} and discuss their implications in Section \ref{sec:discussion}.
+Finally we summarize our findings in Section \ref{sec:summary}.
+A follow-up to this work Boada \etal\ (in Preparation) will will apply these techniques to real data so as to empirically validate our conclusions.
+
+Throughout this paper, we adopt the following cosmological model: $\Omega_\Lambda = 0.714$, $\Omega_M = 0.286$, $\sigma_8 = 0.82$ and $H_0= 70$ \kms \mpc (taken from mock galaxy catalogs derived from an N-body simulation using this cosmology; see below), assume a Chabrier initial mass function (IMF; \citealt{Chabrier2003}), and use AB magnitudes \citep{Oke1974}.
 
@@
 
-This work plans to address these concerns in the following ways.
-We create and evaluate a HETDEX like selection ``function'' of galaxies over a similarly large portion of the sky and use well adopted techniques to recover the dynamical properties, such as velocity dispersion and cluster mass.
-In addition to standard techniques of cluster mass estimation, we investigate probability based and machine learning based approaches of cluster mass prediction.
-We compare these results to a series of targeted galaxy cluster observations, where each member galaxy is assumed to be observed.
-Each of these observations use realistic uncertainties from galaxy magnitude and line-flux limits.
-These strategies will better allow future work to predict the number and types of galaxy clusters which should be observed with VIRUS during both the HETDEX survey portion and through targeted follow up observations.
-
-We begin in Section \ref{sec:Data} by giving an overview of what data is used, how it is created, and how we make our ``observations.'' Details about the determination of cluster parameters, velocity dispersion, total mass, etc., are discussed in Section \ref{sec:recovery}.
-Next, we present the results of our study in Section \ref{sec:results} and discuss their implications in Section \ref{sec:discussion}.
-Finally we summarize our findings in Section \ref{sec:summary}.
-A follow-up to this work Boada \etal\ (in Preparation) will will apply these techniques to real data so as to empirically validate our conclusions.
-
-Throughout this paper, we adopt the following cosmological model: $\Omega_\Lambda = 0.714$, $\Omega_M = 0.286$, $\sigma_8 = 0.82$ and $H_0= 70$ \kms \mpc (taken from the Buzzard catalogs; see below), assume a Chabrier initial mass function (IMF; \citealt{Chabrier2003}), and use AB magnitudes \citep{Oke1974}.
-
 \section{Data and Mock Observations}\label{sec:Data}
 In this section, we describe the data products and the techniques used to replicate the HETDEX survey.
-We use the information from a large mock galaxy catalog enhanced by the emission line properties of galaxies in the SDSS to create a realistic ``sky'' and ``observe'' it with a HETDEX-like observing strategy.
+We use the information from a large mock galaxy catalog enhanced by the emission line properties of galaxies detected by the \textit{Sloan Digital Sky Survey} (SDSS; \citealt{Blanton2001a}) to create a realistic ``sky'' and ``observe'' it with a HETDEX-like observing strategy.
 
 \subsection{The Buzzard Mock Catalogs}\label{sec: Buzzard}
-The Buzzard mock galaxy catalogs provide a light cone covering 398.49 \degsq\ between $4^h< RA < 6^h$ and $-61\degree < DEC < -41\degree$ and are derived from a combination of Sub-halo Abundance Matching (ShAM) and ADDSEDs (Adding Density Dependent Spectral Energy Distributions) tied to an in house n-body cosmological simulation.
-A brief description of the catalog creation is described as follows.
+The Buzzard mock galaxy catalogs are designed to mimic the sky geometry of DES and provide a light cone covering 398.49 \degsq\ between $4^h< RA < 6^h$ and $-61\degree < DEC < -41\degree$.
+They are derived from an in-house n-body cosmological simulation.
 The initial conditions are generated with a second-order Lagrangian perturbation theory using {\sc 2LPTic} \citep{Crocce2006}.
@@
 
-Galaxy $M_r$ luminosities are added to the velocity peaks using ShAM \citep{Reddick2013}, and ADDSEDs assign luminosities in the other bands.
+Galaxy $M_r$ luminosities are added to the velocity peaks using Sub-halo Abundance Matching (ShAM) \citep{Reddick2013}, and ADDSEDs (Adding Density Dependent Spectral Energy Distributions) assign luminosities in the other bands.
 A $M_r$-density-SED relation is created using a SDSS training set, and for each mock galaxy the SED of a randomly selected training set galaxy which has a similar $M_r$ and density is assigned.
@@
 \subsection{Conditional {\rm[\ion{O}{II}]} Flux Probability Distribution Functions}\label{sec: oii luminosity}
-We use the SDSS DR12 \citep{Alam2015} catalogs to assign [\ion{O}{II}] emission line strengths to the galaxies in the Buzzard catalog.
+We use the SDSS Data Release 12 \citep{Alam2015} catalogs to assign [\ion{O}{II}] emission line strengths to the galaxies in the Buzzard catalog.
 We use 503,113 objects classified as galaxies selected over $z = 0.02 - 0.2$ with {\sc zwarning $=0$} and a measured [\ion{O}{II}] line flux signal-to-noise of at least five.
@@
 
-We designed the results of this study to be used in conjunction with HETDEX, a large, blind, spectroscopic survey.
+The Hobby Eberly Telescope Dark Energy eXperiment (HETDEX; \citealt{Hill2008}) will observe high-redshift large scale structures using cutting edge wide-field integral field unit (IFU) spectrographs.
+Designed to probe the evolution of the dark energy equation of state etched onto high redshift ($z>2$) galaxies by the Baryon Acoustic Oscillations (BAO) \citep{Eisenstein2005}, the survey will observe two fields for a total of 420 \degsq\ (300 \degsq, Spring field and 120 \degsq, Fall field).
+Tuned to find \lya\ emitting (LAE) galaxies at $1.9<z<3.5$, HETDEX expects to find 800,000 LAEs, and more than one million [\ion{O}{II}] emitting galaxies at $z<0.5$ masquerading as high-redshift galaxies \citep{Acquaviva2014}.
+
+While a large portion of the $\sim10^6$ interloping lower redshift galaxies will be field (not associated with a bound structure) galaxies, the large area covered by HETDEX is expected to contain as many as 50 Virgo-sized (halo mass $>10^{15}$ \msol) clusters at $z<0.5$.
+The near-complete spectroscopic coverage allows an unprecedentedly detailed look at a very large number of clusters ranging from group scales to the very massive.
+In addition to the recovery of accurate dynamical masses, detailed investigations of the dynamical state of the clusters is possible.
+
+It is unclear how a blind spectroscopic survey with an IFU will effect the recovery of galaxy cluster dynamical properties.
+Unlike many previous large cluster surveys \citeeg{Milvang-Jensen2008, Robotham2011, Sifon2015} which use multi-object spectrographs, the Visible Integral-Field Replicable Unit Spectrograph (VIRUS; \citealt{Hill2012}) used by HETDEX samples the sky in a uniform but sparse way which could exclude member galaxies which would otherwise be included.
+Secondly, it is not straightforward to use spectroscopic redshifts predominately from emission-line galaxies to interpret the kinematic and dynamical states of the clusters.
+
 HETDEX will measure the redshifts of $8 \times 10^5$ LAE galaxies between $1.9 < z < 3.5$ using a collection of 78 wide-field IFU spectrographs covering the wavelength region $3500 - 5500$~\AAA\ at R $\sim$ 750 \citep{Hill2008}.
@@
 The solid black line shows the 1:1 relation.
-The orange, dash-dotted line is the median predicted mass for perfect observations.
+The orange, dash-dotted line is the median predicted mass for Perfect observations.
 The solid, purple line is the median predicted mass for the Targeted observing, and the green, dashed line is the median recovered mass for the HETDEX-like observations.
@@
 \caption[Mean bias for different bins of predicted cluster mass.]{Mean bias (Eqn.~\ref{eqn: bias}) for different bins of predicted cluster mass.
-This table shows the bias in the predicted cluster mass for the perfect (top section), Targeted (middle section), and Survey (bottom section) observations in different predicted mass bins.
+This table shows the bias in the predicted cluster mass for the Perfect (top section), Targeted (middle section), and Survey (bottom section) observations in different predicted mass bins.
 The different mass recovery strategies are given in the leftmost column.
@@
 
-We repeat our analysis using cluster halo and galaxy catalogs from the Millennium simulation obtained via querying the Millennium online database\footnote{\url{http://gavo.mpa-garching.mpg.de/Millennium/}} \citep{Lemson2006}.
+We repeat our analysis using cluster halo and \cite{DeLucia2007} galaxy catalogs derived from the Millennium simulation and obtained via querying the Millennium online database\footnote{\url{http://gavo.mpa-garching.mpg.de/Millennium/}} \citep{Lemson2006}.
 The Millennium simulation tracks $2160^3$ dark matter particles of $8.6\times 10^8 ~h^{-1}$ \Msol\ inside a comoving 500 $(h^{-1} \mathrm{Mpc})^3$ box from $z=127$ to 0.
@@
 Second, the Millennium clusters are split into training-testing samples.
-This provides a test case where we have different cosmological choices between the training and testing samples, and the same cosmological assumptions in both samples.
+This provides a test case where we have different cosmological choices between the training and testing samples (Buzzard training; Millennium testing), and the same cosmological assumptions in both training and testing.
 In addition, it provides two different treatments of galaxy evolution in cluster environments.
@@
 The large amount of scatter (the shaded area) in the fractional error for the Buzzard-trained predictions is due to the training set including clusters with masses below the $M = 10^{13}$ \Msol\ threshold for the Millennium clusters.
-This allows the ML method to predict masses which can be significantly different, whereas the Millennium training set does not include $M < 10^{13}$ \Msol\ clusters, which reduces the scatter of the predicted masses.
+This allows the ML method to predict masses which can be significantly different, whereas the Millennium training set does not include $M < 10^{13}$ \Msol\ clusters, which artificially reduces the scatter of the predicted masses.
 
 Based on these tests, the choice of cosmological parameters does not cause any significant offset in the predicted cluster masses from the trained ML methods.
-This highlights the versatility of our chosen ML method.
+While we have only considered physically plausible cosmological models, this highlights the versatility of our chosen ML method.
 The ML method could be further diversified by including cluster measurements from a wide range of cosmological simulations (or observations) which, in affect, marginalizes over all the cosmological assumptions further reducing the dependence.
@@
 \subsection{Constraints on Cosmological Parameters}
-Galaxy clusters trace the peaks in the universal matter density, often referred to as the power spectrum of matter density fluctuations or the matter power spectrum.
+Galaxy clusters trace the peaks in the cosmic matter density distribution.
 This enables them to be sensitive probes of $\Omega_m$, the total mass ($\Omega_b + \Omega_c$) density, and $\sigma_8$, the normalization of the power spectrum.
@@
 
-To get a sense of how well observations of z < 0.5 galaxy clusters from HETDEX will be able to constrain cosmological parameters we follow the discussion of \defcitealias{Weinberg2013}{W13}\cite{Weinberg2013} (hereafter \citetalias{Weinberg2013}), and begin with a few simplifying assumptions.
-While sensitive to $\Omega_m$, the number density of clusters does not necessarily provide the strongest contraint, but combined with other data sets (\eg, CMB, BAO, supernovae, WL, etc.) it will constrain $\Omega_m$ to higher precision.
+To get a sense of how well observations of z < 0.5 galaxy clusters from HETDEX will be able to constrain cosmological parameters we follow the discussion of \defcitealias{Weinberg2013}{W13}\cite{Weinberg2013} (hereafter \citetalias{Weinberg2013}), and begin with a simplifying assumption.
+We choose to neglect $\Omega_m$ in the following discussion.
+While sensitive to $\Omega_m$, the number density of clusters does not necessarily provide the strongest constraint; we assume other data sets (\eg, CMB, BAO, supernovae, WL, etc.) will constrain $\Omega_m$ to higher precision and therefore focus solely on $\sigma_8$.
 
@@
 For a survey such as HETDEX, we can estimate the constraints on $\sigma_8$ using Equation \ref{eq:sigElapprox}.
-If we consider clusters with masses above $10^{14}$ \Msol\ and with Perfect knowledge observations, the lowest mass scale uncertainty (given in Table~\ref{tbl:mass scatter}) is $\Delta_{log_{10}}M \sim 0.075$ dex or about 20\%.
+If we consider clusters with masses above $10^{14}$ \Msol\ and with Perfect knowledge observations, the lowest mass scale uncertainty (given in Table~\ref{tbl:mass scatter}) is $\Delta_{log_{10}}M \sim 0.075$ dex, corresponding to fractional uncertainty of $\approx20\%$.
 This gives a uncertainty on $\sigma_8$ of 7\%.
@@
 
-Because of the simplifying assumptions, and the superior quality of the data (no contamination, signal-to-noise issues, etc.), realistic expectations for HETDEX is to directly constrain $\sigma_8$ is not yet competitive with other methods (\eg, CMB, WL, X-ray).
+Because we assume $\Omega_m$ is perfectly known from other data, and the superior quality of the data (no contamination, signal-to-noise issues, etc.), realistic expectations for HETDEX is to directly constrain $\sigma_8$ is not yet competitive with other methods (\eg, CMB, WL, X-ray).
 For example, \cite{DeHaan2016} constrain $\sigma_8$ to $\sim5$\% using a sample of 337 SZE detected clusters from the SPT-SZE survey.
 
-We can use the rule-of-thumb calculations given in \citetalias{Weinberg2013} (Equations 154--155) to estimate the uncertainties required in both the absolute cluster mass scale and the intrinsic scatter to keep a cosmological analysis limited by cluster statistics.
-For the $\sim670$ clusters, with masses above $10^{14}$ \Msol, detected with Survey observations to constrain $\sigma_8$ and to be dominated by cluster statistics alone ($\Delta \ln N \sim N^{-1/2}$), the error on the  absolute cluster calibration would need to be better than 1.3\%.
-For a fully Targeted survey, about 1600 clusters with masses above $10^{14}$ \Msol, this cluster mass calibration uncertainty reduces to $<1\%$.
-Similarly, the uncertainty associate with the scatter must be approximately 2.2\% and 1.4\% for Survey and Targeted observations respectively, after assuming an intrinsic scatter of 20\%.
+While analysis of HETDEX clusters may not provide the most accurate constraint on $\sigma_8$, it will provide important systematics checks on other studies and will ultimately improve the measurements of $\sigma_8$.
+We can use the calculations given in \citetalias{Weinberg2013} (Equations 154--155) to estimate the uncertainties required in both the absolute cluster mass scale and the intrinsic scatter to keep a cosmological analysis limited by cluster statistics.
+For the $\sigma_8$ estimate derived from the $\sim 670$ Buzzard catalog clusters detected with Survey observations, with masses above $10^{14}$ \Msol, to be dominated by cluster statistics alone ($\Delta \ln N \sim N^{-1/2}$), the error on the absolute cluster mass calibration would need to be better than 1.3\%.
+For a fully Targeted survey, about 1600 Buzzard catalog clusters with masses above $10^{14}$ \Msol, this cluster mass calibration uncertainty reduces to $<1\%$.
+Similarly, the uncertainty associated with the scatter must be approximately 2.2\% and 1.4\% for Survey and Targeted observations respectively, after assuming an intrinsic scatter of 20\%.
 Comparing these estimates to the uncertainties associated with the Targeted and Survey observations, we are dominated by the uncertainty associated with the absolute cluster mass scale calibration.
-Nevertheless, while analysis of HETDEX clusters may not provide the most accurate constraint on $\sigma_8$, it will provide important systematics checks on other studies and will ultimately improve the measurements of $\sigma_8$.
 
@@
 One of the main goals of this study is to understand how well HETDEX will be able to measure the scatter in the richness--mass relationship.
-To this end, we choose to impose a richness--mass relation onto the clusters in the Buzzard catalogs.
-The true richness--mass relation could depend strongly on the number and types of environmental effects, because such effects have a strong impact on the number and types of galaxies observed in clusters \citeeg{Gunn1972,Balogh2000,White2010}.
+To test our ability to accurately measure the scatter in the richness-mass relationship, we choose to impose a richness--mass relation onto the clusters in the Buzzard catalogs.
+In realaity, the true richness--mass relation could depend strongly on the number and types of environmental effects, because such effects have a strong impact on the number and types of galaxies observed in clusters \citeeg{Gunn1972,Balogh2000,White2010}.
 Any environmental effects included in Buzzard could potentially impact our observed richness.
@@
 The authors also wish to thank the anonymous referee whose comments and suggestions significantly improved both the quality and clarity of this work.
-This research made use of This research made use of the {\sc IPython} package \citep{Perez2007} and {\sc matplotlib}, a Python library for publication quality graphics \citep{Hunter2007}.
+This research made use of the {\sc IPython} package \citep{Perez2007} and {\sc matplotlib}, a Python library for publication quality graphics \citep{Hunter2007}.
 Funding for the SDSS and SDSS-II has been provided by the Alfred P.

### 2017-01-24 paper1.tex
more edits

@@
 
+The existing SDSS imaging will play an important role as the main HETDEX overlaps with the SDSS.
+
 \subsection{The Buzzard Mock Catalogs}\label{sec: Buzzard}
@@
 Dark matter (DM) n-body simulations are run using {\sc LGadget-2} (a version of {\sc Gadget-2}; \citealt{Springel2005}).
-The Buzzard catalogs adopt the following cosmological parameters: $\Omega_m = 0.286$, $\Omega_\Lambda = 0.714$, $H_0 = 70$ \kms \mpc, $\sigma_8 = 0.82$, and $n_s = 0.96$.
+The simulation adopts the following cosmological parameters: $\Omega_m = 0.286$, $\Omega_\Lambda = 0.714$, $H_0 = 70$ \kms \mpc, $\sigma_8 = 0.82$, and $n_s = 0.96$.
 The DM halos are identified using the {\sc ROCKSTAR} halo finder \citep{Behroozi2013} which also calculates halo masses.
@@
 % \begin{figure}
-% 	\includegraphics[width=\textwidth]{figures1/hmf.pdf}
+% 	\includegraphics[width=\columnwidth]{figures/hmf.pdf}
 % 	\caption{The cumulative MF (from \citealt{Tinker2008}) of halos above $M_{200c}$ at $z=0.1$}
@@
        g.oii_3726_flux_err, 
-       s.z 
+       s.z as redshift 
 FROM   galaxy AS GAL 
@@
 
-The Hobby Eberly Telescope Dark Energy eXperiment (HETDEX; \citealt{Hill2008}) will observe high-redshift large scale structures using cutting edge wide-field integral field unit (IFU) spectrographs.
-Designed to probe the evolution of the dark energy equation of state etched onto high redshift ($z>2$) galaxies by the Baryon Acoustic Oscillations (BAO) \citep{Eisenstein2005}, the survey will observe two fields for a total of 420 \degsq\ (300 \degsq, Spring field and 120 \degsq, Fall field).
+The Hobby Eberly Telescope Dark Energy eXperiment (HETDEX; \citealt{Hill2008}) is a blind spectroscopic survey of 420 \degsq\ (300 \degsq, Spring field and 120 \degsq, Fall field) of the northern sky.
+The Spring field is $42\times7$ degrees centered at 13$^h\, +53\degree$, and the Fall field is $28\times5$ degrees centered at $1.5^h\, +0\degree$.
+HETDEX will observe high-redshift large scale structures using cutting edge wide-field integral field unit (IFU) spectrographs.
+The survey is designed to probe the evolution of the dark energy equation of state etched onto high redshift ($z>2$) galaxies by the Baryon Acoustic Oscillations (BAO) \citep{Eisenstein2005}.
 Tuned to find \lya\ emitting (LAE) galaxies at $1.9<z<3.5$, HETDEX expects to find 800,000 LAEs, and more than one million [\ion{O}{II}] emitting galaxies at $z<0.5$ masquerading as high-redshift galaxies \citep{Acquaviva2014}.
 
-While a large portion of the $\sim10^6$ interloping lower redshift galaxies will be field (not associated with a bound structure) galaxies, the large area covered by HETDEX is expected to contain as many as 50 Virgo-sized (halo mass $>10^{15}$ \msol) clusters at $z<0.5$.
-The near-complete spectroscopic coverage allows an unprecedentedly detailed look at a very large number of clusters ranging from group scales to the very massive.
-In addition to the recovery of accurate dynamical masses, detailed investigations of the dynamical state of the clusters is possible.
-
-It is unclear how a blind spectroscopic survey with an IFU will effect the recovery of galaxy cluster dynamical properties.
-Unlike many previous large cluster surveys \citeeg{Milvang-Jensen2008, Robotham2011, Sifon2015} which use multi-object spectrographs, the Visible Integral-Field Replicable Unit Spectrograph (VIRUS; \citealt{Hill2012}) used by HETDEX samples the sky in a uniform but sparse way which could exclude member galaxies which would otherwise be included.
-Secondly, it is not straightforward to use spectroscopic redshifts predominately from emission-line galaxies to interpret the kinematic and dynamical states of the clusters.
-
-HETDEX will measure the redshifts of $8 \times 10^5$ LAE galaxies between $1.9 < z < 3.5$ using a collection of 78 wide-field IFU spectrographs covering the wavelength region $3500 - 5500$~\AAA\ at R $\sim$ 750 \citep{Hill2008}.
-The primary science goal of these observations is to provide $<1\%$ accuracy measurements of the Hubble expansion parameter and the angular diameter distance at $z\sim2$.
-This result will provide significant constraints on the evolution of the dark energy equation of state which is both competitive with, and independent of, constraints derived from observations of the \lya forest.
-
-The entire HETDEX survey will cover 420 \degsq\ with a 1/4.5 filling factor over two fields: a $\sim 300$ \degsq\ northern field, and a $\sim 140$ \degsq\ equatorial region.
-The spectral coverage allows for the detection of [\ion{O}{II}] ($\lambda\lambda 3727,3729$) emitters to $z\sim 0.5$ and Ca H ($\lambda 3968.5$) and K ($\lambda 3933.7$) absorption features to $z\sim 0.4$.
+The Visible Integral-Field Replicable Unit Spectrograph (VIRUS; \citealt{Hill2012}) employed by HETDEX consists of 78 wide-field IFU spectrographs covering the wavelength region $3500 - 5500$~\AAA\ at R $\sim$ 750 \citep{Hill2008}.
+The spectral coverage allows for the detection of [\ion{O}{II}] ($\lambda\lambda 3727,3729$) emitters to $z\sim 0.5$ and Ca$^+$ H ($\lambda 3968.5$) and K ($\lambda 3933.7$) absorption features to $z\sim 0.4$.
 The $10 \sigma$ detection threshold for emission spectral features will be $3.5\times10^{-17}$ \ergscm\ at 5000 \AAA, or equivalently, $g = 21.9$ mag for continuum objects.
@@
 The individual IFUs have a fill-factor of 1/3, which will be completely filled with three dithers of the telescope at each pointing.
+
+The primary science goal of these observations is to provide $<1\%$ accuracy measurements of the Hubble expansion parameter and the angular diameter distance at $z\sim2$.
+This result will provide significant constraints on the evolution of the dark energy equation of state which is both competitive with, and independent of, constraints derived from observations of the \lya forest.
+
+The objects of interest in this work are the low-$z$ [\ion{O}{II}] emitting galaxies, and while a large portion of the $\sim10^6$ interloping galaxies will be field (not associated with a bound structure) galaxies, the large area covered by HETDEX is expected to contain as many as 50 Virgo-sized (halo mass $>10^{15}$ \msol) clusters at $z<0.5$.
+The uniform spectroscopic coverage allows an unprecedentedly detailed look at a very large number of clusters ranging from group scales to the very massive.
+In addition to the recovery of accurate dynamical masses, detailed investigations of the dynamical state of the clusters becomes possible.
+However, it is unclear how a blind spectroscopic survey with an IFU will effect the recovery of galaxy cluster dynamical properties.
+Unlike many previous large cluster surveys \citeeg{Milvang-Jensen2008, Robotham2011, Sifon2015} which use multi-object spectrographs, the IFU spectrographs deployed by HETDEX sample the sky in a uniform but sparse pattern which could exclude member galaxies which would otherwise be included.
+Secondly, it is not straightforward to use spectroscopic redshifts predominately from emission-line galaxies to interpret the kinematic and dynamical states of the clusters.
+This work seeks to investigate both of these potential issues.
 

### 2017-01-27 paper1.tex
even more edits

@@
 We calculate the HMF at central redshifts of 0.1, 0.2, and 0.4 using {\sc HMFcalc} \citep{Murray2013} and compare it to galaxy clusters in a redshift window of $\Delta z\pm0.01$.
-We find a very good agreement between the predicted HMF and the observed distribution of clusters.
+In each of the three test cases we use a $\chi^2$-test, using clusters with masses $10^{10} - 10^{15}$ \msol.
+We find very good agreement between the predicted HMF and the observed distribution of clusters with the minimum $\chi^2$ statistic $\sim0.004$ and a corresponding p-value $>0.95$.
 
@@
 When selecting galaxies from the Buzzard catalog we assume an observation for all galaxies laying within a turquoise, IFU square in Figure~\ref{fig: ifu layout}.
-In practice, this is achieved by three dither positions at each pointing.
-Because of the 1:3 fill factor, many galaxies will not receive spectroscopic coverage, including galaxies that lie between IFUs within a pointing, as well as galaxies between pointings.
-We use a pointing pattern which differs slightly from the expected final HETDEX observing pattern.
-See Figure~\ref{fig: ifu layout} for an illustration of the difference.
-To cover the 398.49 \degsq\ field of the Buzzard catalog we require 5370 pointings where 0.015 \degsq\ of each pointing is covered by an IFU.
-The total area of the sky covered by an IFU is 80.80 \degsq\ which gives a filling factor of 1/4.65, slightly (about 3\%) decreased from the expected filling factor of 1/4.5.
+In practice the individual IFUs have a fill factor of 1:3, so a three position dither pattern at each pointing insures complete coverage.
+Galaxies which do not receive spectroscopic coverage include galaxies that lie between the IFUs within a single pointing, as well as galaxies between the pointings.
+We use a pointing pattern which is designed to mimic that of HETDEX but differs slightly from the expected final HETDEX observing pattern.
+See Figure~\ref{fig: ifu layout} for an illustration of the difference.To illustrate the difference between the pointing patterns, in order to cover the 398.49 \degsq\ field of the Buzzard catalog we require 5370 pointings where 0.015 \degsq\ of each pointing is covered by an IFU (\ie, a turquoise square in Figure~\ref{fig: ifu layout}).
+After completing the survey, the total area of the sky covered by an IFU is 80.80 \degsq\ which gives a filling factor of 1/4.65, slightly (about 3\%) decreased from the expected filling factor of 1/4.5.
 
@@
 We set the upper limit on the LOSVD as the LOSVD corresponding to a $10^{16}$ \Msol\ cluster at $z\sim0.0$, higher mass than any expected cluster in the Buzzard catalogs.
+The resulting estimates of LOSVD are not sensitive to these particular choices of priors.
 When the complete sampling of the posterior probability distribution is not used, the final LOSVD is quoted as the median value of the posterior probability distribution with 68\% error bars defined as the square root of second moment of the same distribution, the standard deviation.
@@
 As expected, the Targeted observing strategy where the individual clusters are targeted through several dithers to ensure near complete coverage, performs significantly better than the Survey observing strategy across all redshifts and cluster masses.
+The Targeted observations detect $\sim10\%$ of all possible clusters whereas the Survey observations detect only $\sim1\%$.
 By definition, with Perfect knowledge, recovery fraction would be unity across all redshifts and cluster masses where clusters exist.
@@
 Because there are few high mass ($M_{200c}>5\times10^{14}$ \Msol) clusters, many of which are at moderately high redshift, the higher redshift cluster members suffer from the limiting apparent magnitude and suppress the recovery fraction at fixed mass.
-If we were to limit the Survey to $z<0.2$ we find the recovery fraction of clusters, across all masses, increases substantially, and we find a much more consistent detection fraction across all masses.
+If we were to limit the Survey to $z<0.2$ we find the recovery fraction of clusters, at fixed masses, increases 40\%-50\%, and we find a much more consistent detection fraction across all masses.
 However, doing so limits severely the number of clusters at masses greater than $10^{14}$ \Msol because of the limited survey volume.
@@
 This does not mean that the Survey observations cannot be improved by Targeted observations.
-In fact, when comparing only the galaxies which overlap between the two samples the bias and scatter of the Targeted observations is significantly decreased as more cluster member galaxies are detected, better sampling the LOSVD probability distribution function.
+In fact, when comparing only the galaxies which overlap between the two samples the bias and scatter of the Targeted observations is significantly decreased as more cluster member galaxies are detected, owing to better sampling of the LOSVD probability distribution function.
 The Targeted observations perform similarly on the average because many lower mass clusters are included in the sample, increasing the bias of the overall sample.

### 2017-01-30 paper1.tex
more edits.

@@
 We use the SDSS Data Release 12 \citep{Alam2015} catalogs to assign [\ion{O}{II}] emission line strengths to the galaxies in the Buzzard catalog.
-We use 503,113 objects classified as galaxies selected over $z = 0.02 - 0.2$ with {\sc zwarning $=0$} and a measured [\ion{O}{II}] line flux signal-to-noise of at least five.
+We use 503,094 objects classified as galaxies selected over $z = 0.02 - 0.2$ with {\sc zwarning $=0$} and a measured [\ion{O}{II}] line flux of at least one.
 Figure~\ref{fig: oii sdss} shows the color-magnitude diagram (CMD) of $M_r$ and $g-r$ for these galaxies, and the following SQL query selects the appropriate galaxies:
 \begin{lstlisting}[language=SQL]
+SELECT GAL.objid,
 SELECT GAL.objid,
@@
        g.oii_3726_flux_err,
-       s.z as redshift 
+       s.z AS redshift
+INTO   mydb.sdsstraining
 FROM   galaxy AS GAL
@@
          ON g.specobjid = s.specobjid
-WHERE  oii_3726_flux > oii_3726_flux_err * 5 
+WHERE  oii_3726_flux > oii_3726_flux_err
        AND oii_3726_flux_err > 0
+       AND s.z BETWEEN 0.02 AND 0.2
        AND s.class = 'GALAXY'
@@
 \begin{tabular}{cccccccc}
-		&& \multic{6}{Bins -- Log $M_{pred}$} \\
+	\multic{8}{Mean Bias in the Recovered Cluster Mass Compared to the True Cluster Mass}\\
+	\hline
+	&& \multic{6}{Bins -- Log M$_{pred}/$\Msol} \\
 	\cline{3-8}
@@
 \begin{tabular}{cccccccc}
-		&& \multic{6}{Bins -- Log $M_{pred}$} \\
+	\multic{8}{Mean Scatter in the Recovered Cluster Mass}\\
+	\hline
+	&& \multic{6}{Bins -- Log M$_{pred}/$\Msol} \\
 	\cline{3-8}

### 2017-01-31 paper1.tex
only a single text change

@@
 This leads to highly skewed biases and scatters for the high mass clusters and probability methods.
-We do not report any bin where such small number statistics dominate in Tables~\ref{tbl:mass bias} and \ref{tbl:mass scatter}.
+We do not report biases and scatters (Tables~\ref{tbl:mass bias} and \ref{tbl:mass scatter}) of the Prob$_\sigma, z, N_gal$ method for high mass clusters because the predicted cluster masses are often based on $0-2$ training clusters.
 On the opposite end of the cluster mass spectrum, there are very few, if any, clusters detected with Targeted or Survey observations below $5\times10^{12}$ \msol.

### 2017-02-01 paper1.tex
a few more edits and a figure tweak

@@
 To test for this, we used the Millennium simulation \citep{Springel2005a} as an alternative data set.
-The Millennium simulation adopts a flat cosmological model based of the values derived from the Two-degree Field Galaxy Redshift Survey \citep{Colless2001} and the first year data of the \emph{Wilkinson Microwave Anisotropy Probe} (WMAP; \citealt{Spergel2003}): $\Omega_\Lambda = 0.75$, $\Omega_M = 0.25$, $\sigma_8 = 0.9$, $n_s = 1$ and $H_0= 73$ \kms \mpc.
+The Millennium simulation tracks $2160^3$ dark matter particles of $8.6\times 10^8 ~h^{-1}$ \Msol\ inside a comoving 500 $(h^{-1} \mathrm{Mpc})^3$ box from $z=127$ to 0.
+It adopts a flat cosmological model based of the values derived from the Two-degree Field Galaxy Redshift Survey \citep{Colless2001} and the first year data of the \emph{Wilkinson Microwave Anisotropy Probe} (WMAP; \citealt{Spergel2003}): $\Omega_\Lambda = 0.75$, $\Omega_M = 0.25$, $\sigma_8 = 0.9$, $n_s = 1$ and $H_0= 73$ \kms \mpc.
 As this cosmology differs dramatically from that assumed in the Buzzard catalogs (see Section~\ref{sec: Buzzard}, the clusters in Millennium provide an independent mock sample to understand how a training sample derived from Buzzard will impact the mass recovery on a wholly new dataset.
 
-We repeat our analysis using cluster halo and \cite{DeLucia2007} galaxy catalogs derived from the Millennium simulation and obtained via querying the Millennium online database\footnote{\url{http://gavo.mpa-garching.mpg.de/Millennium/}} \citep{Lemson2006}.
-The Millennium simulation tracks $2160^3$ dark matter particles of $8.6\times 10^8 ~h^{-1}$ \Msol\ inside a comoving 500 $(h^{-1} \mathrm{Mpc})^3$ box from $z=127$ to 0.
+We repeat our analysis using cluster halo and \cite{DeLucia2007} galaxy catalogs obtained via querying the Millennium on-line database\footnote{\url{http://gavo.mpa-garching.mpg.de/Millennium/}} \citep{Lemson2006}.
 The following SQL query selects the cluster halos:
@@
 	\includegraphics[width=\columnwidth]{figures/millBuzzComparison.pdf}
-	\caption[ML based cluster mass predictions in the Millennium Simulation]{\emph{Top:} ML based cluster mass predictions for the Millennium simulation clusters where the ML method has been trained with either a subset of the Millennium clusters (solid line) or the Buzzard catalog (dashed line).
+	\caption[ML based cluster mass predictions in the Millennium Simulation]{\emph{Top:} ML based cluster mass predictions for the clusters selected from the Millennium database where the ML method has been trained with either a subset of the Millennium clusters (solid line) or the Buzzard catalog (dashed line).
 The shaded areas show the 68\% scatter around the median.
@@
 \emph{Bottom:} The fractional error (Equation~\ref{eq: fractional error}) also as a function of true cluster mass.
-The similarity of the predictions with the different training sets demonstrates how the ML method is not sensitive to the underlying cosmological assumptions.} \label{fig: mill buzz comparison}
+The similarity of the predictions with different training sets demonstrates how the ML method is not sensitive to the underlying cosmological assumptions.} \label{fig: mill buzz comparison}
 \end{figure}
@@
 First, we use the full set of clusters detected in the Buzzard catalogs (14,000 clusters with $M > 10^{11}$ \msol) to train the ML.
-Second, the Millennium clusters are split into training-testing samples.
-This provides a test case where we have different cosmological choices between the training and testing samples (Buzzard training; Millennium testing), and the same cosmological assumptions in both training and testing.
-In addition, it provides two different treatments of galaxy evolution in cluster environments.
+This provides a test case where we have different cosmological choices between the training and testing samples (Buzzard training; Millennium testing).
+Second, the Millennium clusters are split into training-testing samples, which provides a benchmark to test against where the same cosmological assumptions are made in both training and testing.
+In addition, use of the Millennium simulation provides two different treatments of galaxy evolution in cluster environments.
 The differing galaxy evolution effects can impact observed galaxy magnitude and color evolution.
@@
 The median (solid and dashed lines) predicted cluster masses show similar trends regardless of the training data set used.
+A simple $\chi^2$-test indicates the two median lines are indistinguishable from one another, $\chi^2=0.004$.
 The bottom panel of Figure~\ref{fig: mill buzz comparison} shows the fraction error (Equation~\ref{eq: fractional error}) also as a function of true cluster mass.
 The large amount of scatter (the shaded area) in the fractional error for the Buzzard-trained predictions is due to the training set including clusters with masses below the $M = 10^{13}$ \Msol\ threshold for the Millennium clusters.
-This allows the ML method to predict masses which can be significantly different, whereas the Millennium training set does not include $M < 10^{13}$ \Msol\ clusters, which artificially reduces the scatter of the predicted masses.
+This allows the ML method to predict masses which can be significantly different, whereas the Millennium training set does not include $M < 10^{13}$ \Msol\ clusters, which artificially reduces the scatter of predicted masses.
+The ML method trained on Buzzard clusters has a mean scatter increase of $\sim0.05$ dex, a fractional increase of about 12\%, across all true cluster masses.
 
@@
 For a survey such as HETDEX, we can estimate the constraints on $\sigma_8$ using Equation \ref{eq:sigElapprox}.
-If we consider clusters with masses above $10^{14}$ \Msol\ and with Perfect knowledge observations, the lowest mass scale uncertainty (given in Table~\ref{tbl:mass scatter}) is $\Delta_{log_{10}}M \sim 0.075$ dex, corresponding to fractional uncertainty of $\approx20\%$.
-This gives a uncertainty on $\sigma_8$ of 7\%.
+If we consider clusters with masses above $10^{14}$ \Msol\ and with Perfect knowledge observations, the lowest mass scale uncertainty (given in Table~\ref{tbl:mass scatter}) is $\Delta_{log_{10}}M \sim 0.075$ dex, corresponding to fractional uncertainty of $\sim20\%$.
+This gives an uncertainty on $\sigma_8$ of 7\%.
 For clusters above $10^{14}$ \Msol, Survey observations constrain the masses to about 51\% which, in turn, constrains $\sigma_8$ to 20\%.
@@
 Because we assume $\Omega_m$ is perfectly known from other data, and the superior quality of the data (no contamination, signal-to-noise issues, etc.), realistic expectations for HETDEX is to directly constrain $\sigma_8$ is not yet competitive with other methods (\eg, CMB, WL, X-ray).
-For example, \cite{DeHaan2016} constrain $\sigma_8$ to $\sim5$\% using a sample of 337 SZE detected clusters from the SPT-SZE survey.
+For example, \cite{DeHaan2016} constrain $\sigma_8$ to $\sim5$\% using a sample of 337 SZE detected clusters from the SPT-SZE survey, compared to the 7\% uncertainty with HETDEX and Perfect observations.
 

### 2017-02-17 paper1.tex
a little quantification
this is an old change I'm just getting around to committing.
a couple more edits. needs more...

@@
 In this section, we describe the data products and the techniques used to replicate the HETDEX survey.
-We use the information from a large mock galaxy catalog enhanced by the emission line properties of galaxies detected by the \textit{Sloan Digital Sky Survey} (SDSS; \citealt{Blanton2001a}) to create a realistic ``sky'' and ``observe'' it with a HETDEX-like observing strategy.
+We use the information from a large mock galaxy catalog enhanced by the emission line properties of galaxies detected by the \textit{Sloan Digital Sky Survey} (SDSS; \citealt{York2000}) to create a realistic ``sky'' and ``observe'' it with a HETDEX-like observing strategy.
 
@@
 
-Galaxy $M_r$ luminosities are added to the velocity peaks using Sub-halo Abundance Matching (ShAM) \citep{Reddick2013}, and ADDSEDs (Adding Density Dependent Spectral Energy Distributions) assign luminosities in the other bands.
+Galaxy $M_r$ luminosities are added to the velocity peaks using Sub-halo Abundance Matching (ShAM) \citep{Reddick2013}, and the Adding Density Dependent Spectral Energy Distributions algorithm \citeeg{Cunha2012, Chang2015,Kwan2017} assign luminosities in the other bands.
 A $M_r$-density-SED relation is created using a SDSS training set, and for each mock galaxy the SED of a randomly selected training set galaxy which has a similar $M_r$ and density is assigned.
@@
 We use the SDSS Data Release 12 \citep{Alam2015} catalogs to assign [\ion{O}{II}] emission line strengths to the galaxies in the Buzzard catalog.
-We use 503,094 objects classified as galaxies selected over $z = 0.02 - 0.2$ with {\sc zwarning $=0$} and a measured [\ion{O}{II}] line flux of at least one.
+We use 503,094 objects classified as galaxies selected over $z = 0.02 - 0.2$ with {\sc zwarning $=0$} and a measured [\ion{O}{II}] line flux signal-to-noise of at least one.
 Figure~\ref{fig: oii sdss} shows the color-magnitude diagram (CMD) of $M_r$ and $g-r$ for these galaxies, and the following SQL query selects the appropriate galaxies:
@@
 Using a slice sampling technique \citep{Neal1997} we assign the catalog galaxy an [\ion{O}{II}] luminosity based on the distribution of SDSS galaxies in that bin.
-In very few cases (1.3\% of galaxies), the $g-r$ and $M_r$ magnitudes of the galaxies in the Buzzard catalog do not overlap with the distributions in SDSS.
+In very few cases (1.3\% of all galaxies), the $g-r$ and $M_r$ magnitudes of the galaxies in the Buzzard catalog do not overlap with the distributions in SDSS.
 For these objects, we assign them zero [\ion{O}{II}] flux, but this has no impact on our analysis.
 For catalog galaxies with have very few ($1\leq N<10$) SDSS galaxies in their respective bin, we assign it the mean [\ion{O}{II}] flux.
+
+We investigate potential biases introduced by requiring an [\ion{O}{II}] signal-to-noise of at least one and find little to no affect.
+This is due to the way our galaxies are selected, utilizing both continuum measurements and line flux limits (see Section \ref{sec: hetdex} and \ref{sec: recovery} for details).
+Relaxing the signal-to-noise requirements leads to many more SDSS galaxies selected, but these galaxies are often removed during a data preprocessing step.
+\editorial{this needs to be edited and tightened up.}
 
@@
 
-\subsection{Recovery of Cluster Members}
+\subsection{Recovery of Cluster Members}\label{sec: recovery}
 \begin{figure*}
@@
 To confirm that measuring the underlying scatter is possible, after generating richness values we calculate the scatter of the cluster masses at fixed $\lambda$, $\sigma_{M|\lambda}$, by comparing the true, unperturbed cluster masses against the richness.
-We do recover the expected scatter, often, to well within 0.01 dex.
+We do recover the expected scatter, 0.1 dex in this case, with a mean absolute error of 0.015 dex after 12000 trials.
 We repeat the process with both assumed richness--mass relationships and recover the expected scatter in both instances.
